### 2020-06-03 Paper/main.tex

\documentclass[12pt]{article}
% We can write notes using the percent symbol!
% The first line above is to announce we are beginning a document, an article in this case, and we want the default font size to be 12pt
\usepackage[utf8]{inputenc}
\usepackage[left=1.2in,top=.8in,right=1.2in,nohead,bottom=.5in]{geometry}
% This is a package to accept utf8 input.  I normally do not use it in my documents, but it was here by default in Overleaf.

\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{commath}
\usepackage{enumerate}
\newtheorem{theorem}{Theorem}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\graphicspath{ {./plots/} }
\DeclareMathOperator{\Tr}{Tr}
\newcommand{\dd}[1]{\mathrm{d}#1}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\B}{\mathcal{B}}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
\usepackage{comment}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.

\newtheorem{ass}{Assumption}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\setlength{\parskip}{0em}
% This gives us a full line break when we write a new paragraph
\usepackage[mathscr]{euscript}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\newcommand{\indep}{\perp \!\!\! \perp}
\title{Estimating autocorrelation from multiple Markov chains}

\author{
  Medha Agarwal \\
  \textit{Department of Mathematics and Statistics}\\
  \textit{IIT Kanpur}\\
  \texttt{medhaaga@iitk.ac.in} \\\\
  %% examples of more authors
 Dootika Vats \\
  \textit{Department of Mathematics and Statistics}\\
  \textit{IIT Kanpur}\\
  \texttt{dootika@iitk.ac.in} \\
}

\begin{document}

\maketitle

\begin{abstract}
    This is best abstract in the world.\\.\\.\\.\\.\\.
\end{abstract}

\section{Introduction} \label{sec:intro}

Markov chain Monte Carlo (MCMC) is a sampling method used to obtain correlated realizations from a stochastic process. Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones. Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains. Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain. A famous sample autovariance function is the empirical estimator, which unfortunately comes with its drawbacks. Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains for decently finite samples. We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.\\

Calculation of exact theoretical ACF has been done for simple models like autoregressive (AR), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models. However, for most of the complex processes, we rely on sample ACF to understand the correlation in the chain at a particular lag. For a slowly mixing Markov chain or a multi-modal target distribution, Markov chains explore the sample space only partially for even high sample size. In such situations, single chain empirical ACF will underestimate the autocovariance giving misleading inferences. With convenient multi-core computation resources, it is possible to get multiple Markov chains for a target distribution.  We propose a new autocovariance estimator called replicated autocovariance function (R-ACF) with a simple fix in centering a chain about the overall mean. An important application of ACF is in calculating the asymptotic variance in the CLT of a Markov chain process.   \\

Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in

\[
\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)
\]

Suppose we have $m$ replications of Markov chains with $n$ samples in each chain. Let $\{X_{st}\}_{t \geq 1}$ denote the $s^{th}$ Harris ergodic (aperiodic, F-irreducible, and positive Harris recurrent) Markov chain having invariant distribution $F$. We will use the following Monte Carlo estimator in order to estimate $\mu$ for the $s^{th}$ chain

\[
\hat{\mu}_s = \dfrac{1}{n}\sum_{i = 1}^{n} g(X_{si}) \xrightarrow{a.s.} \mu \textrm{ as } n \to \infty
\]

Throughout this paper, we will deal with the function $g(X) = X$. We denote the sample mean of $s^{th}$ Markov chain by $\overline{X}_s$ and the overall mean by $\overline{\overline{X}} = \sum_{s = 1}^{m}\overline{X}_s/m$. We are interested in Monte Carlo error, i.e. $\overline{\overline{X}} - \mu$ to assess the reliability of simulations. The sampling distribution for Monte Carlo error of $s^{th}$ chain is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that

\[
\sqrt{n}(\overline{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
\]

 With $m$ i.i.d. samples of $\overline{X}_s$, $s \in \{1,..., m\}$, the MCSE is given by $\Sigma/mn$. We are interested in consistent estimates of $\Sigma$ for two reasons. Firstly, to construct asymptotically valid confidence intervals and secondly, to determine when to stop the simulations. For this purpose, we use the class of Multivariate Spectral Variance Estimators (MSVE) wherein we use R-ACF to estimate the autocovariance. We call this replicated spectral variance (RSV) estimator (see \cite{arg:and:2006} for replicated batch means). \\

MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite. There are many criteria for terminating simulation like fixed-time rule, sequencial fixed-volume rule (see \cite{glynn1992asymptotic}), and using Gelman Rubin diagnostics (\cite{gelman1992inference}). The relative fixed-volume rule has been thoroughly discussed for MCMC by \cite{flegal2015relative} and \cite{gong2016practical}. We will use method of effective sample size (ESS) defined by \cite{vats2019multivariate} for terminating the simulations. The quality of estimation of $\Sigma$ is critical in determining that the simulations are not stopped prematurely. \\

Markov chains are serially correlated and therefore $\Var_F(X)$ is non-informative about the correlatons in Markov chain. It is important to construct an estimator for $\Sigma$ which is very close to underlying reality. There are many techniques for estimating $\Sigma$ like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE). Due to their highly accurate results, we will only focus on SV estimates in this paper. Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}. Bias and variance calculations for a variant of SV estimator with known mean is done by \cite{hannan2009multiple}. In this paper, we will address the asymptotic properties (basically strong consistency), bias and variance calculations for RSV estimator. \\

The most common practice would be to combine the SVE from $m$ chains by averaging over them. We call this technique average spectral variance (ASV) estimator. We will address the issue of slowly mixing Markov chains and show that RSV performs better than ASV. Whereas on one side RSV gives better estimates than ASV for a poor Markov chain, it is as good as ASV for a good Markov chain. We will exemplify this property of RSV for a bi-modal target distribution in subsection \ref{ex:boomerang}. This appeals intuitively because for a fast mixing Markov chain, all the chains will give almost same estimates for mean. \\

In the next section we introduce the new sample autocovariance estimator and calculate its bias for finite samples. We observe that the bias term for R-ACF is similar to the bias of empirical ACF except for a few small order end-effect terms that vanish as $n \to \infty$. In section \ref{sec:variance_est}, we introduce three estimators for $\Sigma$ and study the properties of RSV estimator through proof of strong consistency, bias, and variance calculations. We will elaborate on the estimator for ESS using RSV in section \ref{sec:ess}. Section \ref{sec:examples} gives a simulation study on three different examples for the proposed estimators. There are only a handful of stochastic processes where the true autocovariance and $\Sigma$ are known. To compare the estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)). We succesfully show in section \ref{ex:var} that our estimators yield better results as compared to the classical sample ACF and SVE. A more promising advantage of our estimators is observed when the target distribution is multi-modal. For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note} in section \ref{ex:boomerang}. All the important proofs are given in the Appendix.

\section{Replicated Autocovariance Function} \label{sec:R-ACF}

For a stationary stochastic process $\{X_t\}_{t \geq 1}$, let $\Gamma(k)$ denote the lag -k autocovariance. In time series literature, we generally encounter the following estimator for autocovariance.

\[
\hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{(t+\abs{k})} - \bar{X})^T
\]

\cite{priestley1981spectral} shows that this estimator is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$. An unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, say $\Gamma^*(k)$. Nevertheless, the biased estimator is preferred for its lower mean square error (\cite{priestley1981spectral}). For a small $k$ relative to $n$, the two estimators are almost the same. However, for larger relative $k$ the variance of $\hat{\Gamma}(k)$ compensates for larger bias rendering a smaller mean square error than $\Gamma^*(k)$. \\

A commonly faced problem with the MCMC algorithms is the slow mixing property. In case of multi modal target distributions, it has been observed that even decently mixing Markov chains fail to explore the sample space for the first few thousand observations. This leads to underestimation of autocovariance for a single Markov chain. We propose a simple and neat fix for estimating ACF while dealing with slow convergence. Suppose we have $m$ replications of Markov chains for same target distribution, the overall mean $\bar{\bar{X}} = \sum_{i = 1}^{m}\bar{X}_i/m$ provides a better estimate for the expectation value when the number of simulation per chain are not sufficient for the convergence to kick in. The replicated autocovariance estimator or $s^{th}$ Markov chain is given by:

\[
\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{\overline{X}})(X_{s(t+k)}-\overline{\overline{X}})^T
\]

If the starting points of these parallel Markov chains are sufficiently dispersed, R-ACF provides more realistic estimation of lag covariances. It is a known problem that getting true autocovariance in closed form for non-simple problems is difficult. In Figure \ref{fig:var_acf_ccf}, we will illustrate the comparison between ACF and R-ACF for a slowly mixing VAR-1 example, where the truth is known. We wish to make two points here: firstly, for small sample size, we observe that ACF gives extremely misleading estimates of autocovariance whereas R-ACF is very close to reality. Figure \ref{subfig:acf-500} depicts the scenario where the convergence is not achieved yet. Secondly, for a large sample size , the estimates from R-ACF as well as ACF are equivalent. Figure \ref{subfig:acf-5e4} depicts the scenario when convergence is achieved. This shows that R-ACF is at least as good as ACF; hence safe to use in any setting.

\begin{figure}
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{var-acf_5e2.pdf}
  \caption{$n = 500$}
  \label{subfig:acf-500}
\end{subfigure}\\
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{var-acf_5e4.pdf}
  \caption{$n = 5*10^4$}
  \label{subfig:acf-5e4}
\end{subfigure}
\caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains. First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n = 5 \times 10^4$, converged}
\label{fig:var_acf_ccf}
\end{figure}

The bias for R-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:RAC_expec}. Before getting to the bias results for $\hat{\Gamma}_{RAV}(k)$ for any lag k, we introduce an additional notation. For $q \geq 1$, we define
\[
\Phi^{(q)} = \sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\|
\]
We denote $\Phi^{(1)} \textrm{ by } \Phi$. 
\begin{theorem} \label{th:RAC_expec}
   \[
   \mathbb{E}[\hat{\Gamma}_{RAC}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
   \]
\end{theorem}

\begin{proof}
 The estimator for autocovariance with divisor $n$ is suggested by \cite{parzen1961approach} for its lesser mean square error despite having greater bias than the unbiased estimator with an $n - \abs{k}$ divisor. 
 We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as

 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k) = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)
 \end{equation}

By proposition 1 in \cite{song1995optimal} 
\begin{equation} \label{eq:song}
\Var(\overline{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
\end{equation}

As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{RAC}$ into four parts for all $k \geq 1$ as:
 \[
 \hat{\Gamma}_{RAC} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T
 \]

where $A_{st} = (X_{st}-\overline{X}_s)(\overline{X}_s - \overline{\overline{X}})^T$\\
The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms. The complete proof evaluating the expectation values of last three terms can be found in Appendix subsection \ref{appendix:bias}.
\end{proof}

\begin{remark} \label{rmrk:exp_racf_minus_acf}
Using theorem \ref{th:RAC_expec} and equation \ref{eq:priestly},
\[
\mathbb{E}[\hat{\Gamma}_{RAC}(k) - \hat{\Gamma}(k)] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
\]
We know that the sample autocovariance $\hat{\Gamma}(k)$ underestimates the truth due to a negative bias of $\abs{k}\Gamma(k)/n$ for finite $n$. However, in practice, it is preferred to overestimate the autocovariance for finite $n$ than to underestimate it in order to have a more realistic idea about the correlation in a Markov chain at a particular lag.  Note that the RHS in the above expression is positive. As a consequence, R-ACF will counter this negative bias and give more reliable estimates for ACF.

\end{remark}

\begin{corollary} \label{cor:lag0_expectation}, 
\[
\mathbb{E}[\hat{\Gamma}_{RAC}(0)] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
\]
\end{corollary}

\begin{proof}
 The proof is in Appendix subsection \ref{appendix:bias}.
\end{proof}

\section{Variance Estimators for multiple Markov chains} \label{sec:variance_est}

Let $\{X_t\}_{t \geq 1}$ be a stochastic process. Denote lag-k autocovariance matrix by $\Gamma(k)$, which is given by,

\[
\Gamma(k) = \Gamma(-k) = \E[(X_t - \E[X])(X_{t+k} - \E[X])^T]
\]

Recall that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by

\[
\hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \overline{X})(X_{t + \abs{k}} - \overline{X})^T
\]

The spectral variance estimator is the weighted and truncated sum of lag-k autocovariances, given by:

\[
\hat{\Sigma}_{SV} &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
\]

where $w_n(.)$ is the lag window and $b_n$ is the truncation point.\\

 Consider $m$ Markov chains where $\overline{X}_s$, $\hat{\Gamma}_s(k)$ and $\hat{\Sigma}_{SV, s}$ are the sample mean, sample lag-k autocovariance and spectral variance estimators respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$. We will consider two estimators for spectral variance calculations using multiple Markov chains.

\subsection{Average Spectral Variance } \label{sec:asv}

Recall that for $s^{th}$ Markov chain, the spectral variance estimator is given by,

\begin{align*}
    \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
    \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
\end{align*}

The average spectral variance ($\Sigma_{ASV}$) is computed by averaging the SV estimates from all $m$ Markov chains.

\[
\hat{\Sigma}_{ASV} = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}
\]

\subsection{Replicated Spectral Variance } \label{sec:rsv}

Now we introduce the Replicated Spectral Variance Estimator (RSV). $\hat{\Gamma}_{RAC,s}(k)$ is the sample replicated lag-k autocovariance estimator for the $s^{th}$ MC using overall mean $(\overline{\overline{X}})$ instead of $\overline{X}_s$ for centering. We construct an RSV estimator $\hat{\Sigma}_{RSV} $ using this replicated version of autocovariance estimator. Consider,

\begin{align*}
    \hat{\Sigma}_{RSV,s} &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{RAC,s}(k)\\
\end{align*}
$$\hat{\Sigma}_{RSV} &=  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{RSV,s}$$

The RSV estimator centers the data around the global mean. We are interested in proving the strong consistency, finding the bias and variance of RSV.

\begin{ass}[Strong Invariance Principle (SIP)] \label{ass:sip}
    We assume the SIP holds for the Markov chain. Here $\{X_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu = \mathbb{E}[X]$. Let $\|.\|$ denote the Euclidean norm. Through SIP, there exists a $p \times p$ lower triangular matrix L, an increasing function $\psi$ on the integers, a finite random variable D, and a  sufficiently rich probability space such that, with probability 1, \\
  $$\left\|\sum_{t=1}^{n}X_t - n\mu - LB(n)\right\| < D\psi(n)$$

  Let $\{B(n)\}_{n\geq 0}$ denotes a standard p-dim Brownian motion and $B^{(i)}$ denotes its $i^{th}$ component. As shown in the results \cite{kuelbs1980almost}, SIP will hold for $\psi(n) = n^{1/2 - \lambda, \; \lambda > 0}$ for Markov chains commonly encountered in MCMC settings. We know that $\psi(n)$ is an inherent property of the stochastic process that satisfies the CLT. This implies that $\psi(n)$ is at least $o(\sqrt{n})$. Using Law of Iterative Logarithms (LIL), a tighter bound for $\psi(n)$ is given by \cite{stra:1964} as $\mathcal{O}(\sqrt{n\log \log n})$.
\end{ass}

\bigskip

\begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true. As a consequence, 
\[
\hat{\Sigma}_{SV,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
\]
\end{ass}

\bigskip

We are going to consider a class of pseudo spectral variance estimator denoted by $\tilde{\Sigma}$ which uses data centered around the unobserved actual mean $\mu$. Such pseudo covariance estimator and autocovariance estimator for the $j^{th}$ chain is denoted by $\tilde{\Sigma}_s$ and $\tilde{\Gamma}_s$ respectively.

\begin{align*}
    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\tilde{\Gamma}_s(k)\\
    \tilde{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)(X_{s(t+k)}-\mu)^T
\end{align*}

The average pseudo spectral variance estimator (APSVE) is given by

\[
\tilde{\Sigma} = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
\]

\bigskip
\begin{theorem}
\label{th:consistency}
 Let the Assumptions \ref{ass:sip},\ref{ass:sve_consis} hold and $\dfrac{b_n \log \log n}{n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{RSV} \to \Sigma$ with probability 1, as $n \to \infty$.
\end{theorem}

\begin{proof}
We complete the proof by showing that $\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. We will show that

\[
\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
\]
where $D$ is the finite random variable associated with SIP. We will show that\\

\begin{align*}
    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]
\end{align*}

Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we will finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$. The proof is in Appendix subsection \ref{appendix:strong_consis}
\end{proof}

\bigskip

We are interested in the finding the bias for RSV estimator as a function of $n$. The proof below applies to all the important range of lag windows $w_n(x)$; where $w_n(x)$ is a continuous, even fnction with $w_n(0)=1, \abs{w_n(x)} < c$, and $\int_{-\infty}^{\infty}w_n^2(x)dx < \infty$. Define

\[
W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)
\]

We have $W_n < \infty$ for all the important lag windows.

\begin{ass} \label{ass:bias}
    Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w_n(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that
    \begin{enumerate} [a.]
        \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\| < \infty$
        \item $\lim _{x \to 0}\dfrac{1 - w_n(x)}{\abs{x}^q} = k_q < \infty$
        \item $\dfrac{b_n^q}{n} \to 0$ as $n \to \infty$
    \end{enumerate}

    If $k_q$ is finite for some $q_o$, then it is zero for $q < q_0$. $q$ is taken to be the largest number satisfying the first two conditions above.
\end{ass}

\begin{theorem}\label{th:rsv_bias}
The limiting bias of replicated spectral variance is given by:
\[
 \lim_{n \to \infty}b_n^q\mathbb{E}[\hat{\Sigma}_{RSV} - \Sigma] = -k_q\Phi^{(q)}
 \]
\end{theorem}

\begin{proof}

\[
\mathbb{E}[\hat{\Sigma}_{RSV} - \Sigma] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E}[\hat{\Gamma}_{RAC}(k)]-\sum_{k=-\infty}^{\infty}\Gamma(k)
\]

Using theorem \ref{th:RAC_expec}, we can write the expectation of $\hat{\Gamma}_{RAC}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
The proof is given in the Appendix subsection \ref{appendix:bias}.
\end{proof}

\begin{ass} \label{ass:variance_cal}
Let $\{X_{st}\}_{t \geq 1}$ be the $s^{th}$ Markov chain for which SIP holds. 
\begin{enumerate}[a.]
    \item $\E[D^4] < \infty$ where D is a finite random variable associated with the SIP
    \item $\E[X^4] < \infty$ where $\{X\}$ is the stochastic process
\end{enumerate}
\end{ass}

\bigskip

\begin{theorem} \label{th:rsv_variance}
 If Assumption \ref{ass:variance_cal} hold, $\dfrac{n}{b_n}\Var\hat{\Sigma}_{RSV}^{ij} = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
\end{theorem}

\begin{proof}
Recall that $\tilde{\Sigma}$ is the averaged pseudo spectral variance estimator which uses the unobserved mean. Further, let $\tilde{\Sigma}^{ij}$ be the $(i,j)^{th}$ element of this matrix. We will prove that the variance of $\hat{\Sigma}_{RSV} \textrm{ and } \tilde{\Sigma}$ are equivalent for large sample sizes. The proof is in Appendix subsection \ref{appendix:variance}
\end{proof}

\section{Effective sample size} \label{sec:ess}

Estimating the MCSE is crucial for determining when to terminate the simulations. The existing stopping rules rely on the strong consistency of the estimator of $\Sigma$. We will use the \textit{relative standard deviation fixed-volume sequential stopping rule} proposed in \cite{vats2019multivariate} when multivariate Markov chain central limit theorem holds. This stopping rule terminates the simulations on the basis of size of confidence interval relative to inherent variability in the target distribution. It terminates after the total number of samples, i.e. $mn$ exceed some pre-specified $n^*$ iterations to prevent pre-mature termination due to bad estimates of $\Sigma$ and $\Lambda$. The rule is given by

\[
\textrm{Volume of confidence region}^{1/p} + n^{-1} < \epsilon \abs{\Lambda_n}^{1/2p} 
\]

where $\epsilon$ is the tolerance level, $\abs{.}$ denotes the determinant and $\Lambda_n$ is the sample covariance matrix given by

\[
\dfrac{1}{mn-1}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st} - \overline{\overline{X}})(X_{st} - \overline{\overline{X}})^T
\]

The determinant of Monte Carlo standard error is called generalized variance in  \cite{wilks1932certain} and gives a metric for volume of confidence interval. \cite{vats2019multivariate} showed that if the estimator for $\Sigma$ is strongly consistent, the stopping rule is asymptotically valid, in that the confidence regions created at termination have the right coverage probability as $\epsilon \to 0$. Since $\hat{\Sigma}_{RSV}$ is a strongly consistent estimator of $\Sigma$, w

\[
\abs{\hat{\Sigma}_{RSV}}^{1/p} + (mn)^{-1} < \epsilon \abs{\Lambda_{mn}}^{1/2p}
\]

Another way to get more accurate stopping rule is to use RSV estimator for estimating Effective Sample Size (ESS) in multivariate settings. RSV estimator better captures the standard error of target distribution by considering the global sample mean across the Markov chains; which might otherwise get lost when considering a single localized slowly mixing Markov chain. We therefore define our ESS rule as

\[
ESS = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{RSV}}}\right)^{1/p}
\]

When there is no correlation in Markov chain $\hat{\Sigma}_{RSV} = \Lambda_{mn}$ and therefore, ESS = $n$. Both the rules involve the ratio of generalized variances and therefore the relative standard deviation fixed-volume sequential stopping rule is asymptotically equivalent to stopping when ESS is greater than $W_{p,\alpha,\epsilon}$ which depends on dimension of state-space, level of confidence of the confidence region, and the relative precision required.

\section{Examples} \label{sec:examples}

In the following examples we compare the performance of asymptotic variance estimators (ASVE and RSVE) for Markov chain CLT. We will successfully illustrate that the replicated spectral variance estimator performs better than the average spectral variance estimator in terms of ESS calculations, coverage probabilities , and sample distribution of $\Sigma$. We will also show that in case of nicely mixing Markov chains, these estimators give almost equivalent results. As a consequence, while out replicated version of variance estimator is better in cases where the Markov chains do not explore the entire sample space in finite time, it is harmless to be used in cases where they do.  
{\color{red}about this new FFT based method for faster RSVE calculations}

\subsection{Vector Autoregressive Process} \label{ex:var}

We examine the vector autoregressive process of order 1 (VAR(1)) where the true autocovariance in known in closed form. We have already illustrated the better performance of R-ACF over traditional ACF on a slowly mixing VAR(1) process in Figure \ref{fig:var_acf_ccf}. Here we will examine the performance of RSV estimator on the same process. Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that

\[
X_t = \Phi X_{t-1} + \epsilon_t
\]

where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{i.i.d.}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix. The invariant distribution for this Markov chain is $N(0, \Psi)$ where $\Vec{\Psi} = (I_{p^2} - \Phi \otimes \Phi)\Vec{\Omega}$. The lag-k autocovariance can be calculated easily for $k >0$ as

\begin{align*}
    \Gamma(k) &= \Phi^k\Psi\\
    \Gamma(-k) &= \Psi(\Phi^T)^k
\end{align*}

The Markov chain is geometrically ergodic when the spectral norm of $\Phi$ is less than 1 (\cite{10.2307/1427459}). The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is given by

\[
\Sigma = (1 - \Phi)^{-1}\Psi + \Psi(1 - \Phi^T)^{-1} - \Psi
\]

Let $\phi_{max}$ be the largest absolute eigenvalue of $\Phi$ such that $\abs{\phi_{max}} < 1$. The larger it is, the slower the Markov chain mixes. For our case, we require a slowly mixing VAR(1) process. We consider a bivariate example with $\phi_{max} = 0.9999$. We run five parallel Markov chains with their starting points evenly distributed about the center of invariant distribution. Figure \ref{subfig:var-sp_500} shows that for the first 500 samples, the chains have not explored the sample space well unlike Figure \ref{subfig:var-sp_50000} with $5\cdot 10^4$ samples.

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{0.4\textwidth}
         \centering
         \includegraphics[width=\textwidth]{var-sp_5e2.pdf}
         \caption{$n = 500$}
         \label{subfig:var-sp_500}
     \end{subfigure}
     \begin{subfigure}[h]{0.4\textwidth}
         \centering
         \includegraphics[width=\textwidth]{var-sp_5e4.pdf}
         \caption{$n = 5 \times 10^4$}
         \label{subfig:var-sp_50000}
     \end{subfigure}
    \caption{Scatter plot of five Markov chains for different sample sizes.}
    \label{fig:var-sp}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width = .5\textwidth]{plots/var-ess.pdf}
    \caption{Running plots for $\hat{ESS}/mn$ calculated using ASV (black) and RSV (blue). The true $ESS/mn$ (red) is known.}
    \label{fig:var-ess}
\end{figure}

\subsection{Boomerang Distribution} \label{ex:boomerang}

We will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions. This allows us to sample parallel Markov chains using the Gibbs sampler. Let $x$ and $y$ be two random variable that are jointly distributed as

\[
f(x, y) \propto \exp\left(-\dfrac{1}{2}[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y]\right)
\]

The conditional distribution of $x$ given $y$ and vice versa is a normal distribution given by:

\begin{align*}
    x_1 \mid x_2 &\sim N\left(\dfrac{Bx_2 + C_1}{Ax_2^2 + 1}, \dfrac{1}{Ax_2^2 + 1}\right)\\
    x_2 \mid x_1 &\sim N\left(\dfrac{Bx_1 + C_2}{Ax_1^2 + 1}, \dfrac{1}{Ax_1^2 + 1}\right)
\end{align*}

We use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ which ensures bimodality for our purpose.  Let $n$ be the number of samples in each chain and $m$ be the number of Markov chain replications. Finding the actual mean of this distribution in closed form is difficult. Therefore, we use numerical integration with fine tuning to calculate it. We sample two parallel Markov chains with well-separated starting values.

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{.4\textwidth}
        \centering
        \includegraphics[width = \textwidth]{plots/boom-pers_1_3_8.pdf}
        \caption{$A = 1, B = 3, C = 8$}
        \label{subfig:boom-pers_1_3_8}
    \end{subfigure}
    \begin{subfigure}[h]{.4\textwidth}
        \centering
        \includegraphics[width = \textwidth]{plots/boom-pers_1_10_7.pdf}
        \caption{$A = 1, B = 10, C = 7$}
        \label{subfig:boom-pers_1_10_7}
    \end{subfigure}
    \caption{Perspective plots of the target distribution for two different parameterizations.}
   \label{fig:3d_plot}
\end{figure}

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{.4\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/boom-sp_1e3.pdf}
      \caption{$n = 1000$}
      \label{subfig:boom-sp_1e3}
    \end{subfigure}
    \begin{subfigure}[h]{.4\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/boom-sp_1e4.pdf}
      \caption{$n = 10,000$}
      \label{boom-sp_1e4}
    \end{subfigure}
    \caption{The scatter plots for two parallel Markov chains. (a): Both the chains are stuck in one of the mode (b): Both the chains have travelled and explored both the modes.}
    \label{fig:boom-sp}
\end{figure}

In Figure \ref{fig:boom-sp}, we demonstrate the "sticky" nature of the Markov chains. For the first thousand samples, both the chains are oblivious of the existence of another mode. By ten thousand samples, both the Markov chains have explored the two modes. This property will affect the single chain estimators like ACF. In Figure \ref{subfig:boom-acf_1e3}, the ACF is severely underestimated because the chain-1 has not jumped to the other mode. Whereas, in Figure \ref{subfig:boom-acf_1e4}, both ACF and R-ACF give almost similar results indicating that both modes have been explored by chain-1.

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{.7\textwidth}
      \centering
      \includegraphics[width = \textwidth]{boom-acf_1e3.pdf}
      \caption{$n = 1000$}
      \label{subfig:boom-acf_1e3}
    \end{subfigure}
    \begin{subfigure}[h]{.7\textwidth}
      \centering
      \includegraphics[width = \textwidth]{boom-acf_1e4.pdf}
      \caption{$n = 10,000$}
      \label{subfig:boom-acf_1e4}
    \end{subfigure}
    \caption{ACF and R-ACF for component-1 of chain-1 at two different sample sizes. }
    \label{fig:boom-acf}
\end{figure}

We also run five parallel Markov chains with well-separated starting points. In Table \ref{table:boom-coverage_1_3_8}, we give the coverage probabilities for $95 \%$ confidence interval for both the estimator. We can see that the RSVE gives better coverage probabilities for all the $n$. For smaller sample size, the coverage probability of RSVE is significantly higher than ASVE. As the number of samples per chain increases, they start coming closer due to the strong consistency of both the estimators.

\begin{table}[h]
\centering
    \begin{tabular}{p{1cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}}
    \toprule
        n & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
        \hline
        & ASV & RSV & ASV & RSV\\
        \hline
        $10^3$ & 0.612 & 0.689 & 0.602 & 0.753   \\
        $2\cdot10^3$ & 0.693 & 0.751 & 0.735 & 0.827 \\
        $5 \cdot 10^3$  & 0.826 & 0.854 & 0.847 & 0.880 \\
        $10^4$  & 0.862 & 0.868 & 0.884 & 0.907 \\
        $2 \cdot 10^4$ & 0.899 & 0.906 & 0.922 & 0.934 &  &  \\
    \bottomrule
    \end{tabular}
    \caption{Coverage probabilities for parameter values $A = 1,\; B = 3,\; C = 8$. }
    \label{table:boom-coverage_1_3_8}
\end{table}

A good estimate of ESS is crucial to determine when to stop the simulations. We can see in Figure \ref{fig:run_ess} that for the first few thousand samples, ASVE gives misleadingly higher $\hat{ESS}/mn$ than RSVE. This can cause us to stop the sampling before the sample space has been explored by the chains. The inferences derived from this chain would then be severely non-informative.

\begin{figure}[h]
    \centering
    \includegraphics[width = .7\textwidth]{plots/boom-ess.pdf}
    \caption{Running plot for $\hat{ESS}/mn$ using ASV and RSV calculated for two chains (left) and five chains (right). The parameters for target distribution are $A == 1, \; B = 3, \; C = 8.$}
    \label{fig:run_ess}
\end{figure}

To examine the performance of RSV for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$. This is also a bimodal distribution, however, the two modes interact well with each other (Figure \ref{subfig:boom-pers_1_10_7}). In Figure \ref{fig:boom-ess_1_10_7}, we observe that both RSV and ASV give almost the same estimates for ESS. Similar is the case with coverage probabilities in Table \ref{table:boom-coverage_1_10_7} for a $95\%$ confidence region.

\begin{figure}
    \centering
    \includegraphics[width = .7\textwidth]{plots/boom-ess_1_10_7.pdf}
    \caption{Running plot for $\hat{ESS}/mn$ using ASV and RSV calculated for two chains (left) and five chains (right). The parameters of target distribution are $A = 1, \; B = 10, \; C = 7$}
    \label{fig:boom-ess_1_10_7}
\end{figure}

\begin{table}[h]
\centering
    \begin{tabular}{p{1cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}}
    \toprule
        n & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
        \hline
        & ASV & RSV & ASV & RSV\\
        \hline
        $10^3$ & 0.873 & 0.884 & 0.875 & 0.898   \\
        $2\cdot10^3$ & 0.881 &  0.888 & 0.897    & 0.914     \\
        $5 \cdot 10^3$  & 0.902 & 0.908 &  0.919 & 0.929\\
        $10^4$  & 0.923 & 0.927 & 0.925 & 0.926 \\
        $5 \cdot 10^4$ & 0.951& 0.952 & 0.939 & 0.939  \\
    \bottomrule
    \end{tabular}
    \caption{Coverage probabilities for parameter values $A = 1,\; B = 10,\; C = 7$. }
    \label{table:boom-coverage_1_10_7}
\end{table}

\section{Discussion} \label{sec:discussion}

\appendix

\section{Preliminaries} \label{apdx:preliminaries}

\begin{lemma}
\label{lemma: brownian}
(\cite{csorgo2014strong}). Suppose Assumption \ref{ass:sip} holds, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}$ and $\forall i = 1, ..., p$

\[
\sup_{0\leq t \leq n-b_n}\sup_{0 \leq s \leq b_n} \left| B^{\left(i\right)}\left(t+s\right) - B^{\left(i\right)}\left(t\right) \right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\; \log\; n\right)\right)^{1/2} ,
\]

\[
\sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \;and
\]

\[
\left|B^{\left(i\right)}\left(n\right)\right| < \left(1+\epsilon\right)\sqrt{2n\;\log \log n} \; . 
\]
\end{lemma}

\bigskip

\begin{lemma} \label{lemma:consis_1}
  Let the strong invariance principle hold. If $\dfrac{\psi(n)}{n} \to 0$ as $n \to \infty$, then $\|\overline\overline{{X}} - \mu\|_{\infty}, \|\overline{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
  \end{lemma}

\begin{proof}
Let $\|.\|$ denote the Euclidean norm. Assumption \ref{ass:sip} allows us to upper bound $\|\bar{X}_s - \mu\|_{\infty}$ using SIP. Following that, we show that the upper bound term converges to 0 as $n \to \infty$ using lemma \ref{lemma: brownian}.
 \begin{align*}
    \|\overline{X}_s - \mu\|_{\infty} & \leq \|\overline{X}_s - \mu\| \\
    &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\|\\
    &= \dfrac{1}{n}|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n)\|\\
    & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
    &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
    &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
    & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\\
    & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty
 \end{align*}

  Similarly one can easily show that $\|\bar{\bar{X}} - \mu\|_{\infty} \to 0$ as $n \to \infty$ using the same upper-bound as:

 \begin{align*}
    \|\overline{\overline{X}} - \mu\|_{\infty} & \leq \|\overline{\overline{X}} - \mu\|\\
    &= \dfrac{1}{m}\left\|\sum_{j=1}^{m}(\overline{X}_j- \mu) \right\|\\
    & \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\overline{X}_j - \mu\|\\
    & \xrightarrow{a.s.} 0\qquad \textrm{as n} \to \infty 
\end{align*}
\end{proof}

\section{Proof of Theorems} \label{appendix:A}

\subsection{Strong consistency argument} \label{appendix:strong_consis}

\bigskip

\begin{lemma} \label{lemma:rsv_breakdown}
    The RSV estimator can be written as the sum of average pseudo SVE and two terms given by:
    \[
    \hat{\Sigma}_{RSV} = \tilde{\Sigma} + (1) + (2)
    \]
    where \\
    Term (1): $\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[\left((X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right)+ \left((\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right\}$\\
Term (2): $(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)$
\end{lemma}

\begin{proof}
\begin{align*}
\hat{\Sigma}_{RSV}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\overline{\overline{X}})_i(X_{s(t+k)}-\overline{\overline{X}})_j\\
&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}[(X_{st}-\mu)_i+(\mu-\overline{\overline{X}})_i\}\{(X_{s(t+k)}-\mu)_j+(\mu-\overline{\overline{X}})_j]\\
&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}[(X_{st}-\mu)_i(X_{s(t+k)}-\mu)_j+ (X_{st} - \mu)_i(\mu - \overline{\overline{X}})_j \\  & \; + (\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j+(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j]\\
&= \tilde{\Sigma}^{ij} + \left[ \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}\left[\dfrac{1}{n}\left( (X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right)+\dfrac{1}{n} \left((\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right] \\
& \; + \left[(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)\right]
\end{align*}

Therefore we get the following two terms:\\\\
Term (1): $\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\left[\dfrac{1}{n}\left((X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right)+ \dfrac{1}{n}\left((\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right\}$\\
Term (2): $(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)$\\
\\\\
\end{proof}

\bigskip

\begin{lemma} \label{lemma:pseudo_consis}
If the Assumption \ref{ass:sip}, \ref{ass:sve_consis} hold and $\dfrac{b_n \log \log n}{n} \to 0$, then $\tilde{\Sigma}^{ij} \xrightarrow{a.s.} \Sigma^{ij} \textrm{ as } n \to \infty$
\end{lemma}

\begin{proof}
We have,
\begin{align*}
    \tilde{\Sigma}^{ij} & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)_i(X_{s(t+|k|)} - \mu)_j\\
    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st} \pm \overline{X}_s - \mu)_i(X_{s(t+|k|)} \pm \overline{X}_s - \mu)_j\\
    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[(X_{st} - \overline{X}_s)_i(\overline{X}_s - \mu)_j + (\overline{X}_s - \mu)_i(X_{s(t+k)} - \overline{X}_s)_j\right]\\
    & + \dfrac{1}{m}\sum_{s=1}^{m}(\overline{X}_s - \mu)_i(\overline{X}_s - \mu)_j\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)
\end{align*}
\\\\
Let Term (1*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum\limits_{t=1}^{n-|k|}\left[(X_{st} - \overline{X}_s)_i(\overline{X}_s - \mu)_j + (\overline{X}_s - \mu)_i(X_{s(t+k)} - \overline{X}_s)_j\right]$
Let Term (2*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}(\overline{X}_s - \mu)_i(\overline{X}_s - \mu)_j\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)$
\\\\
We will prove that Term (1*), Term (2*) $\xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$. From \cite{vats:fleg:jon:2018}, we have that $\hat{\Sigma}_{SV} \to 0$ with probability 1 as $n \to \infty$ for multivariate case. Assuming that all the assumptions made there hold true for our case, we will prove that $\tilde{\Sigma} \to 0$ with probability 1 as $n \to \infty$. 
\\\\

Firstly, we prove that Term (1*) $\xrightarrow{a.s.} 0$ as $n \to \infty$. We will prove this for the first part of Term (1*). It will hold true equivalently for the second part as well. The first part of the Term (1*) is,

\begin{align*}
    & \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum\limits_{t=1}^{n-|k|}\left[(X_{st} - \overline{X}_s)_i(\overline{X}_s - \mu)_j \right]\\
    & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{(\bar{X}_s - \mu)_j}{n}\left[\sum\limits_{t=1}^{|k|}(\overline{X}_s - X_{st})_i\right]\\
    & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{(\bar{X}_s - \mu)_j}{n}\left[\sum\limits_{t=1}^{|k|}(\mu - X_{st})_i + \abs{k}(\overline{X}_s - \mu)_i\right]\\
    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left\|\sum\limits_{t=1}^{|k|}(\mu - X_{st}) + \abs{k}\overline{X}_s - \mu)\right\|_{\infty}\\
    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left(\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} + \abs{k}\|\overline{X}_s - \mu\|_{\infty} \right)\\
    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left\|\sum\limits_{t=1}^{|k|}(\overline{X}_s - \mu)\right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
\end{align*}

Using SIP on the summation of k terms,
\begin{multline*}
    & < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2\\
    & < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
\end{multline*}

Using lemma \ref{lemma:consis_1}, the above term can be upper bounded by,

\begin{equation} \label{eq:PASVE_term-1}
  \left(2b_n - 1 + \dfrac{b_n^2}{n} + \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  
\end{equation}
\\
Using the bound on $\psi(n)$ given by \cite{stra:1964}, (\ref{eq:PASVE_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
\\
Similar to the above proof, second part of Term (1*) can also be written as a summation of k terms and the proof follows exactly as the first part. Now we prove that Term (2*) $\xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.

\begin{align*}
    &\dfrac{1}{m}\sum\limits_{s=1}^{m}(\overline{X}_s - \mu)_i(\overline{X}_s - \mu)_j\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)\\
    & < \dfrac{1}{m}\sum\limits_{s=1}^{m} \|\overline{X}_s - \mu\|_{\infty}^2 \sum\limits_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{b_n}\right)\right|\\
    & = \dfrac{b_n}{m}\sum\limits_{s=1}^{m} \|\overline{X}_s - \mu\|_{\infty}^2 \dfrac{1}{b_n} \sum\limits_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{b_n}\right)\right|\\
    & \leq \dfrac{b_n}{m}\sum\limits_{s=1}^{m} \|\overline{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w_n(x)}dx
\end{align*}
\\
Recall that the lag window is such that $\int_{-\infty}^{\infty} \abs{w_n(x)}dx = C$ for some constant C. Using lemma \ref{lemma:consis_1}, Term (2*) can be upper bounded by

\begin{equation} \label{eq:PASVE_term-2}
    Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2 
\end{equation}

(\ref{eq:PASVE_term-2}) is also $\mathcal{O}\left(\dfrac{b_n \log \log n}{n}\right)$, and hence converges to 0 as $n \to \infty$.

\end{proof}

\bigskip

\begin{proof}[Proof of theorem \ref{th:consistency}]
We first show that Term (1) $\xrightarrow{a.s} 0$ as $n \to \infty$ with the help of SIP and prior assumptions.
\begin{align*}
   & \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|} \dfrac{1}{n}\left[(X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j+ (\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right]\right\}\right| \\
   & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|}(X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right|}+\dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|}(\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right|} \right]\right\}
\end{align*}

\begin{align*}
    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum\limits_{t=1}^{n-|k|}(X_{st}- \mu)_i\right|\left|(\mu-\overline{\overline{X}})_j\right|+ \dfrac{1}{n}\left|(\mu-\overline{\overline{X}})_i\right|\left|\sum\limits_{t=1}^{n-|k|}(X_{j(t+k)}-\mu)_j\right|\right]\right\}\\
    & \leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=1}^{n-|k|}(X_{st}-\mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{n-|k|}(X_{s(t+k)}-\mu)\right\|_{\infty} \right]\\
    &\leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=n-|k|+1}^{n}(X_{st} - \mu) - n(\overline{X}_s - \mu) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu) - n(\overline{X}_s - \mu)\right\|_{\infty} \right]\\
    &\leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} + 2\|\overline{X}_s - \mu\|_{\infty} \right]\\
    & \leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\| + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu)\right\| \right]\\
    & \; \;+ 2(2b_n - 1)\|\overline{\overline{X}} - \mu\|_{\infty}\|\overline{X}_1 - \mu\|_{\infty} 
\end{align*}
\\
Using SIP on summation of $k$ terms, we obtain the following upper bound for Term (1)
\begin{align*}
    & < 2\|(\overline{\overline{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + 2(2b_n - 1)\|\overline{\overline{X}} - \mu\|_{\infty}\|\overline{X}_1 - \mu\|_{\infty} \\
    &\leq 2(2b_n - 1)\|(\overline{\overline{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right] + 2(2b_n - 1)\|\overline{\overline{X}} - \mu\|_{\infty}\|\overline{X}_1 - \mu\|_{\infty}
\end{align*}
\\
We use lemma \ref{lemma:consis_1} to upper bound the above term as
\begin{equation} \label{eq:strong_consis_term-1}
    4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2
\end{equation}
\\
Using the bound on $\psi(n)$ given by \cite{stra:1964}, equation (\ref{eq:strong_consis_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$. Now we will show that Term (2) $\xrightarrow{a.s.} 0$ as $n\to \infty$

\begin{align*}
    &\left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)\right\}\right|\\
    & \leq\|\overline{\overline{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)\right]\\
    &< \|\overline{\overline{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{n}\right)\right|\right]\\
    &= b_n\|\overline{\overline{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{n}\right)\right|\right]\\
    & \leq b_n\|\overline{\overline{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w_n(x)|dx \\
    & \leq Cb_n\|\overline{\overline{X}} - \mu \|^2
\end{align*}

Using lemma \ref{lemma:consis_1} to upper bound the above term as

\begin{equation} \label{eq:strong_consis_term-2}
     Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2
\end{equation}
\\
Equation (\ref{eq:strong_consis_term-2}) has the same order as equation (\ref{eq:strong_consis_term-1}), i.e. $\mathcal{O}\left(b_n \log \log n/n\right) \to 0 \textrm{ as } n \to \infty$.
We have already shown that Term (1) and Term (2) converge to 0 almost surely $\implies \hat{\Sigma}_{RSV} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$. Now we can find the functions $g_1(n), g_2(n) \textrm{ and, } g_3(n)$ by adding (\ref{eq:strong_consis_term-1}) and (\ref{eq:strong_consis_term-2}). After some simple algebra, we obtain the following results:\\

\begin{align*}
    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0
\end{align*}
\end{proof}

\\
\subsection{Bias Calculations} \label{appendix:bias}

\begin{lemma} \label{lemma:bias1}
$\mathbb{E}[(X_{11}-\overline{X}_1)(\overline{X}_1 - \overline{\overline{X}})^T] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
\end{lemma}
\begin{proof}
\begin{align*}
    &\mathbb{E}[(X_{11}-\overline{X}_1)(\overline{X}_1 - \overline{\overline{X}})^T] = \mathbb{E}[X_{11}\overline{X}_1^T] - \mathbb{E}[X_{11}\overline{\overline{X}}^T] + \mathbb{E}[\overline{X}_1\overline{\overline{X}}^T] - \mathbb{E}[\overline{X}_1\overline{X}_1^T]\\
    &= \mathbb{E}[X_{11}\overline{X}_1^T] - \dfrac{1}{m}\mathbb{E}[X_{11}\overline{X}_1^T] - \dfrac{m-1}{m}\mathbb{E}[X_{11}\overline{X}_2^T] + \dfrac{1}{m}\mathbb{E}[\overline{X}_1\overline{X}_1^T] + \dfrac{m-1}{m}\mathbb{E}[\overline{X}_1\overline{X}_2^T] - \mathbb{E}[\overline{X}_1\overline{X}_1^T]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E}[X_{11}\overline{X}_1^T] - \mathbb{E}[X_{11}\overline{X}_2^T] + \mathbb{E}[\overline{X}_1\overline{X}_2^T] - \mathbb{E}[\overline{X}_1\overline{X}_1^T]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{i=1}^{n}\mathbb{E}[X_{11}X_{1i}^T] - \mathbb{E}[X_{11}]\mathbb{E}[\overline{X}_2^T] + \mathbb{E}[\overline{X}_1]\mathbb{E}[\overline{X}_2^T] - Var[\overline{X}_1] - \mathbb{E}[\overline{X}_1]\mathbb{E}[\overline{X}_1^T]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \dfrac{\Sigma}{n} - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma\right)
\end{align*}
\\   
Similarly, we can show that $\mathbb{E}[A_{ij}^T] = \mathbb{E}[A_{ij}]$ using the symmetry of $\Gamma(k) \textrm{ and } \Sigma$ matrices.

\begin{align*}
    \mathbb{E}[(\bar{X}_1 - \bar{\bar{X}})(X_{11}-\bar{X}_1)^T] &= \mathbb{E}[(X_{11}-\bar{X}_1)(\bar{X}_1 - \bar{\bar{X}})^T]^T\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align*}
\end{proof}

\begin{lemma} \label{lemma:bias2}
$$\mathbb{E}\left[\sum\limits_{s=1}^{m}(\overline{X}_{s}-\overline{\overline{X}})(\overline{X}_{s}-\overline{\overline{X}})^{T}\right] =  (m-1)\Var(\overline{X_1})$$
\end{lemma}
\\
$\overline{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\overline{\overline{X}}) = \dfrac{1}{m} \Var(\overline{X}_1)$.

\begin{proof}
\begin{align*}
\mathbb{E}\left[\sum\limits_{s=1}^{m}(\overline{X}_{s}-\overline{\overline{X}})(\overline{X}_{s}-\overline{\overline{X}})^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\overline{X}_{s}\overline{X}_{s}^{T} -\sum_{s=1}^{m}\overline{X}_{s}\overline{\overline{X}}^{T} - \overline{\overline{X}}^{T}\sum_{s=1}^{m}\overline{X}_{s}^{T} + m\overline{\overline{X}}\overline{\overline{X}}^{T}\right]\\
&= \mathbb{E}\left[\sum_{s=1}^{m}\overline{X}_{s}\overline{X}_{s}^{T} - m\overline{\overline{X}}\overline{\overline{X}}^{T}\right]\\
&= m\left(\mathbb{E}\left[\overline{X}_{1}\overline{X}_{1}^{T}\right] - \mathbb{E}\left[\overline{\overline{X}}\overline{\overline{X}}^{T}\right]\right)\\
&= m\left(Var(\overline{X}_{1}) + \mu\mu^{T} - Var(\overline{\overline{X}}) - \mu\mu^{T}\right)\\
&= (m-1)\Var(\overline{X_1})
\end{align*}
\end{proof}

\begin{proof}[Proof of theorem \ref{th:RAC_expec}]
\begin{align*}
    \hat{\Gamma}_{RAC}(k) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|}(X_{st}-\overline{\overline{X}})(X_{s(t+k)}-\overline{\overline{X}})^T\\
    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T\right] + \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}(\overline{X}_s - \overline{\overline{X}})(\overline{X}_s - X_{st})^T\right]\\ 
    &+  \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}( \overline{X}_s - X_{st})(\overline{X_s}-\overline{\overline{X}})^T\right] + \left[\dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T\right]\\
    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T
\end{align*}

where $A_{st} = (X_{st}-\overline{X}_s)(\overline{X}_s - \overline{\overline{X}})^T$.\\

\\
Using equation \ref{eq:priestly}, lemma \ref{lemma:bias1}, and lemma \ref{lemma:bias2}, the expectation of $\hat{\Gamma}_{RAC}(k)$ can be written as

\begin{align*}
    &= \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \Var(\overline{X_1})\right) - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\overline{X_1})\\
    &= \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{1}{m}\Var(\overline{X_1})\right) - \dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma(h) - \Sigma\right)
\end{align*}
\\
Using the results of \cite{song1995optimal} given in equation \ref{eq:song} to expand $\Var(\overline{X}_1)$,
\[
\mathbb{E}[\hat{\Gamma}_{RAC}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
\]
\\
We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\overline{\overline{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
\end{proof}

\begin{proof}[Proof of corollary \ref{cor:lag0_expectation}]

\begin{align*}
    \hat{\Gamma}_{RAC}(k) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st}-\overline{\overline{X}})(X_{s(t+k)}-\overline{\overline{X}})^T\\
    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T\right]\\
    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k)  + \dfrac{1}{m}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T
\end{align*}
Using equation \ref{eq:priestly}, lemma \ref{lemma:bias2}, and equation \ref{eq:song} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as

\begin{align*}
    \mathbb{E}[\hat{\Gamma}_{RAC}(0)] &= \left(\Gamma(k) - \Var(\overline{X_1})\right) + \left(1-\dfrac{1}{m}\right)\Var(\overline{X_1})\\
    &= \Gamma(k) - \dfrac{1}{m}\Var(\overline{X_1})\\
    &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
\end{align*}

\end{proof}

\begin{proof}[Proof of theorem \ref{th:rsv_bias}]
The convoluted end effect terms in theorem \ref{th:RAC_expec} are all essentially $\mathcal{O}(1/n)$. We are interested in finding the asymptotic bias here. Therefore we can write the expection of replicated autocovariance as 
\begin{equation} \label{eq:rac_bias2}
\mathbb{E}[\hat{\Gamma}_{RAC}(k)] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + \left(1 - \dfrac{\abs{k}}{n}\right)\mathcal{O}(1/n) + \mathcal{O}(1/n)    
\end{equation}

The last term in (\ref{eq:rac_bias2}) is stated separately because it does not depend on $k$. 
\begin{align*}
    &\mathbb{E}[\hat{\Sigma}_{RSV} - \Sigma]\\
    &= \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E}[\hat{\Gamma}_{RAC}(k)]-\sum_{k=-\infty}^{\infty}\Gamma(k)\\
    &= \sum_{k=-b_n+1}^{b_n-1}\left\{ w_n\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\left[\left(\Gamma(k) + \mathcal{O}\left(\dfrac{1}{n}\right)\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right]\right\} - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
    &= \sum_{k=-b_n+1}^{b_n-1}\left\{ w_n\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right\} - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
    &+ \sum_{k=-b_n+1}^{b_n-1}\left\{ w_n\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \right\}
\end{align*}
Since $w_n\left(\dfrac{k}{b_n}\right) = 0$ for $|k| > b_n$, we can decompose the above term as:\\
Let Term \textbf{A}: $\sum\limits_{k=-n+1}^{n-1}\left\{w_n\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right\} - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)$\\

Let Term \textbf{B}: $\sum\limits_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \right\}$\\\\

\begin{enumerate}
    \item We first solve for term {\textbf{A}} by breaking it into three parts as in \cite{hannan2009multiple}.\\

$$-\sum_{|k|\geq n}\Gamma(k) + \sum_{k = -n+1}^{n-1}w_n\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w_n\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)$$\\

We deal with the three subterms of term \textbf{A} individually,
\begin{enumerate}
    \item 
    \begin{align*}
        \left\|{-\sum_{|k|\geq n}\Gamma(k)}\right\| &\leq   \abs{\dfrac{k}{n}}^q\sum_{|k|\geq n}\|\Gamma(k)\|\\
        &= \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q\underbrace{\sum_{|k|\geq n}|k|^q\|\Gamma(k)\|}_{<\infty}\\
        &= o\left(\dfrac{1}{b_n^q}\right)
    \end{align*}

    \item
\begin{align*}
   \left\| \sum_{k = -n+1}^{n-1}w_n\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)\right\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| 
\end{align*}

 \begin{enumerate}
     \item For q $\geq 1$, we have, $\sum_{k=-n+1}^{n-1}|k|^q\|\Gamma(k)\| < \infty$
     \begin{align*}
         \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\|\\
         &= \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\|\\
         &= o\left(\dfrac{1}{b_n^q}\right) 
     \end{align*}

     \item For q $<1$:\\
     \begin{align*}
         c\sum_{k =-n+1}^{n-1}\dfrac{|k|}{n}\|\Gamma(k)\| &\leq c\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q\|\Gamma(k)\|\\
         &= \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k =-n+1}^{n-1}|k|^q\|\Gamma(k)\|\\
         &= o\left(\dfrac{1}{b_n^q}\right) 
     \end{align*}
     \end{enumerate}
     \item 
     $$\sum_{k = -n+1}^{n-1}\left(1-w_n\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}\left[\dfrac{\left(1-w_n\left(\dfrac{|k|}{b_n}\right)\right)}{\left(\dfrac{|k|}{b_n}\right)^q}|k|^q \Gamma(k)\right]$$\\

     The condition 
     \[
     \lim_{\abs{x}\to 0}\dfrac{1 - w_n(x)}{\abs{x}^q} = k_q < \infty
     \]
     implies that $\dfrac{1-w_n(k/b_n)}{\abs{k/b_n}^q}$ converges boundedly to $k_q$ for each $k$; where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
     \[
     \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w_n\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
     \]
\end{enumerate}

 \item Solving for Term \circled{\textbf{B}}. We will find an upper bound and prove that it is $\mathcal{O}\left(\dfrac{1}{n}\right)$:
 \begin{align*}
     & \sum_{k=-n+1}^{n-1}\left\{w_n\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right) \right] \right\} \\
     &\leq \sum_{k=-n+1}^{n-1}w_n\left(\dfrac{|k|}{b_n}\right)\mathcal{O}\left(\dfrac{1}{n}\right)\\
     &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}w_n\left(\dfrac{|k|}{b_n}\right) \\
     &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
     &= \mathcal{O}\left(\dfrac{1}{n}\right) \\
     &= o\left(\dfrac{1}{b_n^q}\right) 
 \end{align*}
 \end{enumerate}  
 \\
 We have shown that all, but one, terms are $o(1/b_n^q)$. Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{RAC} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms. This is quite intuitive as we are using a strongly consistent estimator $\overline{\overline{X}}$ for $\mu$ in our replicated autovariance estimator. Similar to theorem \ref{th:RAC_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms. 
\end{proof}
\subsection{Variance Calculation}
\label{appendix:variance}
\textbf{Theorem } \ref{th:rsv_variance}
\begin{proof}
 Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
\begin{equation}
\label{eq:rsv_asv_consis}
 \left|\hat{\Sigma}_{RSV} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
\end{equation}
Further, we have defined $g_1(n), g_2(n), g_3(n)$ such that as $n \to \infty$,
\begin{align*}
    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0
\end{align*}

We have shown from the proof of strong consistency that,
\begin{align*}
 &\left| \hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right|\\
 & \leq \dfrac{1}{m} \ds\sum_{s=1}^m \left|\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}\left[\left( \dfrac{(X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j}{n}\right)+ \left(\dfrac{(\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j}{n}\right) \right] \\
& \quad \quad  + (\mu-\overline{\overline{X}})(\mu-\overline{\overline{X}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w_n\left(\dfrac{k}{n}\right) \right| \\ 
 & < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
\end{align*}

By \eqref{eq:rsv_asv_consis}, there exists an $N_0$ such that
\begin{align*}
\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
& \leq \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
& := g_n^*(X_{11}, \dots, X_{1n}, \dots, X_{m1}, \dots, X_{mn})\,.
\end{align*}
But since by assumption $\E D^4 <\infty$ and the fourth moment is finite,
\[
\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
\]
Thus, $\E \left| g_n^* \right| < \infty$ and further as $n \to \infty$, $g_n \to 0$ under the assumptions. Since $g_1, g_2, g_3 \to 0$, $\E g_n^* \to 0$. By the majorized convergence theorem \citep{zeid:2013}, as $n \to \infty$,
\begin{equation}
\label{eq:squared_mean_diff}
  \E \left[\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
\end{equation}
%
We will use \eqref{eq:squared_mean_diff} to show that the variances are equivalent. Define,
\[
\xi\left(\hat{\Sigma}_{RSV}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
\]
We will show that the above is $o(1)$. Using Cauchy-Schwarz inequality followed by \eqref{eq:squared_mean_diff},
\begin{align*}
& \left|  \xi\left(\hat{\Sigma}_{RSV}^{ij}, \tilde{\Sigma}^{ij} \right) \right|\\
& \leq \left| \Var\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\ 
& \leq \E\left[\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\ 
& = o(1) + 2\left(o(1) \left(O\left( \dfrac{b_n}{n}\right)  + o\left( \dfrac{b_n}{n}\right) \right)  \right) \\ 
& = o(1)\,.
\end{align*}

Finally,
\begin{align*}
 & \Var\left(\hat{\Sigma}_{RSV}^{ij} \right)\\
  & = \E \left[ \left(\hat{\Sigma}_{RSV}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
& = \E \left[ \left(\hat{\Sigma}_{RSV}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right)^2 \right]\\
& = \E\left[ \left( \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right)  \right)^2 \right] \\ 
& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right) \right)^2 \right] \\
& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)\right] + 2 \E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right)\right]\\
& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
& = \Var\left( \tilde{\Sigma}^{ij}\right) + o(1)
\end{align*}

\cite{hannan2009multiple} has given the calculations for variance of $\tilde{\Sigma}$ as 
\begin{equation} \label{eq:hannan_var}
\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = [\Sigma^{ii}\Sigma^{jj} + \Sigma^{ij}^2]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
\end{equation}
Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{RSV}$ gives the result of the theorem.

\end{proof}

\bibliographystyle{apalike}
\bibliography{sample}
\end{document}

### 2020-06-03 Paper/main.tex
Crisis diverted

@@
 \usepackage{enumerate}
-\newtheorem{theorem}{Theorem}
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
-\usepackage{caption}
+\usepackage{caption,setspace}
 \usepackage{subcaption}
@@
 % By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.
-
-\newtheorem{ass}{Assumption}
+\allowdisplaybreaks
+\newtheorem{theorem}{Theorem}
 \newtheorem{lemma}{Lemma}
 \newtheorem{corollary}{Corollary}
+
+\theoremstyle{remark}
+\newtheorem{ass}{Assumption}
 \newtheorem{remark}{Remark}
@@
 % This gives us a full line break when we write a new paragraph
-\usepackage[mathscr]{euscript}
+% \usepackage[mathscr]{euscript}
 \usepackage{tikz}
@@
             \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
-\newcommand{\indep}{\perp \!\!\! \perp}
+% \newcommand{\indep}{\perp \!\!\! \perp}
+
 \title{Estimating autocorrelation from multiple Markov chains}
@@
   Medha Agarwal \\
-  \textit{Department of Mathematics and Statistics}\\
-  \textit{IIT Kanpur}\\
-  \texttt{medhaaga@iitk.ac.in} \\\\
+  Department of Mathematics and Statistics\\
+  IIT Kanpur\\
+  \texttt{medhaaga@iitk.ac.in} \and
   %% examples of more authors
  Dootika Vats \\
-  \textit{Department of Mathematics and Statistics}\\
-  \textit{IIT Kanpur}\\
-  \texttt{dootika@iitk.ac.in} \\
+  Department of Mathematics and Statistics\\
+  IIT Kanpur\\
+  \texttt{dootika@iitk.ac.in}
 }
@@
 
+\onehalfspacing
 \begin{abstract}
@@
 Throughout this paper, we will deal with the function $g(X) = X$.
-We denote the sample mean of $s^{th}$ Markov chain by $\overline{X}_s$ and the overall mean by $\overline{\overline{X}} = \sum_{s = 1}^{m}\overline{X}_s/m$.
+We denote the sample mean of $s^{th}$ Markov chain by $\bar{X}_s$ and the overall mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$.
 We are interested in Monte Carlo error, i.e.
-$\overline{\overline{X}} - \mu$ to assess the reliability of simulations.
+$\bar{\bar{X}} - \mu$ to assess the reliability of simulations.
 The sampling distribution for Monte Carlo error of $s^{th}$ chain is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
@@
 \[
-\sqrt{n}(\overline{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
+\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
 \]
@@
  With $m$ i.i.d.
-samples of $\overline{X}_s$, $s \in \{1,..., m\}$, the MCSE is given by $\Sigma/mn$.
+samples of $\bar{X}_s$, $s \in \{1,..., m\}$, the MCSE is given by $\Sigma/mn$.
 We are interested in consistent estimates of $\Sigma$ for two reasons.
@@
 \[
-\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{\overline{X}})(X_{s(t+k)}-\overline{\overline{X}})^T
+\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
 \]
@@
   \centering
-  \includegraphics[width=.8\linewidth]{var-acf_5e2.pdf}
+  \includegraphics[width=.8\linewidth]{plots/acf-500.pdf}
   \caption{$n = 500$}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{var-acf_5e4.pdf}
+  \includegraphics[width=.8\linewidth]{plots/acf-5e4.pdf}
   \caption{$n = 5*10^4$}
@@
 \begin{equation} \label{eq:song}
-\Var(\overline{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
+\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
 \end{equation}
@@
  \[
- \hat{\Gamma}_{RAC} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T
- \]
-
-where $A_{st} = (X_{st}-\overline{X}_s)(\overline{X}_s - \overline{\overline{X}})^T$\\
+ \hat{\Gamma}_{RAC} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
+ \]
+%
+where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
 The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.
@@
 
-\begin{corollary} \label{cor:lag0_expectation}, 
+\begin{corollary} \label{cor:lag0_expectation}
 \[
@@
 \[
-\hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \overline{X})(X_{t + \abs{k}} - \overline{X})^T
+\hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
 \]
@@
 \[
-\hat{\Sigma}_{SV} &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
-\]
-
-where $w_n(.)$ is the lag window and $b_n$ is the truncation point.\\
-
- Consider $m$ Markov chains where $\overline{X}_s$, $\hat{\Gamma}_s(k)$ and $\hat{\Sigma}_{SV, s}$ are the sample mean, sample lag-k autocovariance and spectral variance estimators respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
+\hat{\Sigma}_{SV} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
+\]
+
+where $w(.)$ is the lag window and $b_n$ is the truncation point.\\
+
+ Consider $m$ Markov chains where $\bar{X}_s$, $\hat{\Gamma}_s(k)$ and $\hat{\Sigma}_{SV, s}$ are the sample mean, sample lag-k autocovariance and spectral variance estimators respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
 We will consider two estimators for spectral variance calculations using multiple Markov chains.
@@
 \begin{align*}
-    \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
+    \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
     \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
@@
 Now we introduce the Replicated Spectral Variance Estimator (RSV).
-$\hat{\Gamma}_{RAC,s}(k)$ is the sample replicated lag-k autocovariance estimator for the $s^{th}$ MC using overall mean $(\overline{\overline{X}})$ instead of $\overline{X}_s$ for centering.
+$\hat{\Gamma}_{RAC,s}(k)$ is the sample replicated lag-k autocovariance estimator for the $s^{th}$ MC using overall mean $(\bar{\bar{X}})$ instead of $\bar{X}_s$ for centering.
 We construct an RSV estimator $\hat{\Sigma}_{RSV} $ using this replicated version of autocovariance estimator.
@@
 \begin{align*}
-    \hat{\Sigma}_{RSV,s} &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{RAC,s}(k)\\
-\end{align*}
-$$\hat{\Sigma}_{RSV} &=  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{RSV,s}$$
+    \hat{\Sigma}_{RSV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{RAC,s}(k)
+\end{align*}
+\[
+\hat{\Sigma}_{RSV} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{RSV,s}
+\]
 
@@
 \begin{align*}
-    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\tilde{\Gamma}_s(k)\\
+    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Gamma}_s(k)\\
     \tilde{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)(X_{s(t+k)}-\mu)^T
@@
 \label{th:consistency}
- Let the Assumptions \ref{ass:sip},\ref{ass:sve_consis} hold and $\dfrac{b_n \log \log n}{n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{RSV} \to \Sigma$ with probability 1, as $n \to \infty$.
+ Let the Assumptions \ref{ass:sip},\ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{RSV} \to \Sigma$ with probability 1, as $n \to \infty$.
 \end{theorem}
@@
 \]
-where $D$ is the finite random variable associated with SIP. We will show that\\
-
+where $D$ is the finite random variable associated with SIP. We will show that
 \begin{align*}
@@
 
-\bigskip
-
 We are interested in the finding the bias for RSV estimator as a function of $n$.
-The proof below applies to all the important range of lag windows $w_n(x)$; where $w_n(x)$ is a continuous, even fnction with $w_n(0)=1, \abs{w_n(x)} < c$, and $\int_{-\infty}^{\infty}w_n^2(x)dx < \infty$.
+The proof below applies to all the important range of lag windows $w(x)$; where $w(x)$ is a continuous, even fnction with $w(0)=1, \abs{w(x)} < c$, and $\int_{-\infty}^{\infty}w^2(x)dx < \infty$.
 Define
@@
 \[
-W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)
+W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)
 \]
@@
 \begin{ass} \label{ass:bias}
-    Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w_n(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that
+    Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that
     \begin{enumerate} [a.]
         \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\| < \infty$
-        \item $\lim _{x \to 0}\dfrac{1 - w_n(x)}{\abs{x}^q} = k_q < \infty$
+        \item $\lim _{x \to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty$
         \item $\dfrac{b_n^q}{n} \to 0$ as $n \to \infty$
@@
 \[
- \lim_{n \to \infty}b_n^q\mathbb{E}[\hat{\Sigma}_{RSV} - \Sigma] = -k_q\Phi^{(q)}
+ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right] = -k_q\Phi^{(q)}
  \]
@@
 \begin{proof}
-
-\[
-\mathbb{E}[\hat{\Sigma}_{RSV} - \Sigma] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E}[\hat{\Gamma}_{RAC}(k)]-\sum_{k=-\infty}^{\infty}\Gamma(k)
+\[
+\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
 \]
@@
 \begin{theorem} \label{th:rsv_variance}
- If Assumption \ref{ass:variance_cal} hold, $\dfrac{n}{b_n}\Var\hat{\Sigma}_{RSV}^{ij} = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+ If Assumption \ref{ass:variance_cal} hold, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{RSV}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
 \end{theorem}
@@
 \]
-
+%
 where $\epsilon$ is the tolerance level, $\abs{.}$ denotes the determinant and $\Lambda_n$ is the sample covariance matrix given by
-
-\[
-\dfrac{1}{mn-1}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st} - \overline{\overline{X}})(X_{st} - \overline{\overline{X}})^T
-\]
-
+%
+\[
+\dfrac{1}{mn-1}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st} - \bar{\bar{X}})(X_{st} - \bar{\bar{X}})^T
+\]
+%
 The determinant of Monte Carlo standard error is called generalized variance in  \cite{wilks1932certain} and gives a metric for volume of confidence interval.
@@
 \[
-ESS = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{RSV}}}\right)^{1/p}
+\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{RSV}}}\right)^{1/p}
 \]
@@
 Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
-
+%
 \[
@@
 The lag-k autocovariance can be calculated easily for $k >0$ as
-
+%
 \begin{align*}
@@
 The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is given by
-
+%
 \[
@@
          \centering
-         \includegraphics[width=\textwidth]{var-sp_5e2.pdf}
+         \includegraphics[width=\textwidth]{scatter_plot_500.pdf}
          \caption{$n = 500$}
@@
          \centering
-         \includegraphics[width=\textwidth]{var-sp_5e4.pdf}
+         \includegraphics[width=\textwidth]{scatter_plot_50000.pdf}
          \caption{$n = 5 \times 10^4$}
@@
 Let $x$ and $y$ be two random variable that are jointly distributed as
-
+%
 \[
@@
 The conditional distribution of $x$ given $y$ and vice versa is a normal distribution given by:
-
+%
 \begin{align*}
@@
 
-In Figure \ref{fig:boom-sp}, we demonstrate the "sticky" nature of the Markov chains.
+In Figure \ref{fig:boom-sp}, we demonstrate the ``sticky'' nature of the Markov chains.
 For the first thousand samples, both the chains are oblivious of the existence of another mode.
@@
     \begin{tabular}{p{1cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}}
-    \toprule
+    % \toprule
         n & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
@@
         $10^4$  & 0.862 & 0.868 & 0.884 & 0.907 \\
-        $2 \cdot 10^4$ & 0.899 & 0.906 & 0.922 & 0.934 &  &  \\
-    \bottomrule
+        $2 \cdot 10^4$ & 0.899 & 0.906 & 0.922 & 0.934  \\
+    % \bottomrule
     \end{tabular}
@@
         $5 \cdot 10^4$ & 0.951& 0.952 & 0.939 & 0.939  \\
-    \bottomrule
+    % \bottomrule
     \end{tabular}
@@
 \]
-
+%
 \[
@@
   Let the strong invariance principle hold.
-If $\dfrac{\psi(n)}{n} \to 0$ as $n \to \infty$, then $\|\overline\overline{{X}} - \mu\|_{\infty}, \|\overline{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
+If $\dfrac{\psi(n)}{n} \to 0$ as $n \to \infty$, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
   \end{lemma}
@@
  \begin{align*}
-    \|\overline{X}_s - \mu\|_{\infty} & \leq \|\overline{X}_s - \mu\| \\
-    &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\|\\
-    &= \dfrac{1}{n}|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n)\|\\
+    \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| \\
+    &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| = \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
     & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
@@
  \end{align*}
-
+%
 Similarly one can easily show that $\|\bar{\bar{X}} - \mu\|_{\infty} \to 0$ as $n \to \infty$ using the same upper-bound as:
-
- \begin{align*}
-    \|\overline{\overline{X}} - \mu\|_{\infty} & \leq \|\overline{\overline{X}} - \mu\|\\
-    &= \dfrac{1}{m}\left\|\sum_{j=1}^{m}(\overline{X}_j- \mu) \right\|\\
-    & \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\overline{X}_j - \mu\|\\
-    & \xrightarrow{a.s.} 0\qquad \textrm{as n} \to \infty 
+% 
+\begin{align*}
+    \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as} n \to \infty
 \end{align*}
@@
     \[
-    \hat{\Sigma}_{RSV} = \tilde{\Sigma} + (1) + (2)
-    \]
-    where \\
-    Term (1): $\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[\left((X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right)+ \left((\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right\}$\\
-Term (2): $(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)$
+    \hat{\Sigma}_{RSV}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2\,,
+    \]
+    where 
+\begin{align*}
+  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[ \left(X_{st}-\mu \right)_i   \left(\mu-\bar{\bar{X}} \right)_j +    \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right]\right\}\,, \\
+  %
+M_2 &= \left(\mu-\bar{\bar{X}} \right)_i   \left(\mu-\bar{\bar{X}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\,.
+\end{align*}
 \end{lemma}
@@
 \begin{proof}
-\begin{align*}
-\hat{\Sigma}_{RSV}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\overline{\overline{X}})_i(X_{s(t+k)}-\overline{\overline{X}})_j\\
-&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}[(X_{st}-\mu)_i+(\mu-\overline{\overline{X}})_i\}\{(X_{s(t+k)}-\mu)_j+(\mu-\overline{\overline{X}})_j]\\
-&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}[(X_{st}-\mu)_i(X_{s(t+k)}-\mu)_j+ (X_{st} - \mu)_i(\mu - \overline{\overline{X}})_j \\  & \; + (\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j+(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j]\\
-&= \tilde{\Sigma}^{ij} + \left[ \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}\left[\dfrac{1}{n}\left( (X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right)+\dfrac{1}{n} \left((\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right] \\
-& \; + \left[(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)\right]
-\end{align*}
-
-Therefore we get the following two terms:\\\\
-Term (1): $\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\left[\dfrac{1}{n}\left((X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right)+ \dfrac{1}{n}\left((\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right\}$\\
-Term (2): $(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)$\\
-\\\\
-\end{proof}
-
-\bigskip
+The proof follows from standard algebraic calculations and is presented here for completeness. Consider,
+\begin{align*}
+&\hat{\Sigma}_{RSV}^{ij} \\
+&= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st}-\bar{\bar{X}} \right)_i \left(X_{s(t+k)}-\bar{\bar{X}} \right)_j\\
+&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left[  \left\{\left(X_{st}-\mu \right)_i + \left(\mu-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_j \right \} \right]\\
+&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left[ \left(X_{st}-\mu \right)_i  \left(X_{s(t+k)}-\mu \right)_j+  \left(X_{st} - \mu \right)_i    \left(\mu - \bar{\bar{X}} \right)_j \right.
+\\
+& \quad + \left. \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(\mu-\bar{\bar{X}}  \right)_j  \right]\\
+& = \tilde{\Sigma}^{ij} + \left[(\mu-\bar{\bar{X}})_i(\mu-\bar{\bar{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\right] \\ 
+& \quad  + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}  \left[\dfrac{1}{n} \left(X_{st} - \mu \right)_i \left(\mu - \bar{\bar{X}} \right)_j + \dfrac{1}{n} \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right] \\
+& = \tilde{\Sigma}^{ij} + M_1 + M_2\,.
+\end{align*}
+%
+% Therefore we get the following two terms:\\\\
+% Term (1): $\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\left[\dfrac{1}{n}\left((X_{st}-\mu)_i(\mu-\bar{\bar{X}})_j\right)+ \dfrac{1}{n}\left((\mu-\bar{\bar{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right\}$\\
+% Term (2): $(\mu-\bar{\bar{X}})_i(\mu-\bar{\bar{X}})_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)$\\
+% \\\\
+\end{proof}
 
 \begin{lemma} \label{lemma:pseudo_consis}
-If the Assumption \ref{ass:sip}, \ref{ass:sve_consis} hold and $\dfrac{b_n \log \log n}{n} \to 0$, then $\tilde{\Sigma}^{ij} \xrightarrow{a.s.} \Sigma^{ij} \textrm{ as } n \to \infty$
+If the Assumption \ref{ass:sip}, \ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n}\to 0$, then $\tilde{\Sigma}^{ij} \xrightarrow{a.s.} \Sigma^{ij} \textrm{ as } n \to \infty$
 \end{lemma}
@@
 \begin{align*}
-    \tilde{\Sigma}^{ij} & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)_i(X_{s(t+|k|)} - \mu)_j\\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st} \pm \overline{X}_s - \mu)_i(X_{s(t+|k|)} \pm \overline{X}_s - \mu)_j\\
-    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[(X_{st} - \overline{X}_s)_i(\overline{X}_s - \mu)_j + (\overline{X}_s - \mu)_i(X_{s(t+k)} - \overline{X}_s)_j\right]\\
-    & + \dfrac{1}{m}\sum_{s=1}^{m}(\overline{X}_s - \mu)_i(\overline{X}_s - \mu)_j\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)
-\end{align*}
-\\\\
-Let Term (1*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum\limits_{t=1}^{n-|k|}\left[(X_{st} - \overline{X}_s)_i(\overline{X}_s - \mu)_j + (\overline{X}_s - \mu)_i(X_{s(t+k)} - \overline{X}_s)_j\right]$
-Let Term (2*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}(\overline{X}_s - \mu)_i(\overline{X}_s - \mu)_j\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)$
-\\\\
-We will prove that Term (1*), Term (2*) $\xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
+    \tilde{\Sigma}^{ij} & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t+|k|)} - \mu \right)_j\\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} \pm \bar{X}_s - \mu \right)_i  \left(X_{s(t+|k|)} \pm \bar{X}_s - \mu \right)_j\\
+    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i   \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
+    & \quad + \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\\
+    & = \hat{\Sigma}_{SV}^{ij} + N_1 + N_2 \,,
+\end{align*}
+where
+\begin{align*}
+N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
+N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\,.
+\end{align*}
+% Let Term (1*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum\limits_{t=1}^{n-|k|}\left[(X_{st} - \bar{X}_s)_i(\bar{X}_s - \mu)_j + (\bar{X}_s - \mu)_i(X_{s(t+k)} - \bar{X}_s)_j\right]$
+% Let Term (2*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}(\bar{X}_s - \mu)_i(\bar{X}_s - \mu)_j\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)$
+% \\\\
+We will prove that $N_1, N_2\xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
 From \cite{vats:fleg:jon:2018}, we have that $\hat{\Sigma}_{SV} \to 0$ with probability 1 as $n \to \infty$ for multivariate case.
 Assuming that all the assumptions made there hold true for our case, we will prove that $\tilde{\Sigma} \to 0$ with probability 1 as $n \to \infty$.
-\\\\
-
-Firstly, we prove that Term (1*) $\xrightarrow{a.s.} 0$ as $n \to \infty$.
-We will prove this for the first part of Term (1*).
+
+Firstly, we prove that  $N_1 \xrightarrow{a.s.} 0$ as $n \to \infty$.
+We will prove this for the first part of $N_1$.
 It will hold true equivalently for the second part as well.
-The first part of the Term (1*) is,
-
-\begin{align*}
-    & \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum\limits_{t=1}^{n-|k|}\left[(X_{st} - \overline{X}_s)_i(\overline{X}_s - \mu)_j \right]\\
-    & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{(\bar{X}_s - \mu)_j}{n}\left[\sum\limits_{t=1}^{|k|}(\overline{X}_s - X_{st})_i\right]\\
-    & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{(\bar{X}_s - \mu)_j}{n}\left[\sum\limits_{t=1}^{|k|}(\mu - X_{st})_i + \abs{k}(\overline{X}_s - \mu)_i\right]\\
-    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left\|\sum\limits_{t=1}^{|k|}(\mu - X_{st}) + \abs{k}\overline{X}_s - \mu)\right\|_{\infty}\\
-    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left(\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} + \abs{k}\|\overline{X}_s - \mu\|_{\infty} \right)\\
-    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left\|\sum\limits_{t=1}^{|k|}(\overline{X}_s - \mu)\right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
+The first part of the $N_1$ is,
+
+\begin{align*}
+    & \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right]\\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{  \left(\bar{X}_s - \mu \right)_j}{n} \left[\sum\limits_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i\right]\\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{k}{b_n}\right) \dfrac{\left(\bar{X}_s - \mu \right)_j}{n} \left[\sum_{t=1}^{|k|} \left(\mu - X_{st} \right)_i + \abs{k} \left(\bar{X}_s - \mu \right)_i\right]\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right) + \abs{k} \left(\bar{X}_s - \mu \right)\right\|_{\infty}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left(\left\|\sum_{t=1}^{|k|}  \left(X_{st} - \mu \right)\right\|_{\infty} + \abs{k}\|\bar{X}_s - \mu\|_{\infty} \right)\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left\|\sum_{t=1}^{|k|} \left(\bar{X}_s - \mu\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{X}_s - \mu \right \|_{\infty}^2\,.
 \end{align*}
@@
 Using SIP on the summation of k terms,
-\begin{multline*}
+\begin{align*}
+    & \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right]\\
    &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2\\
    &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
-\end{multline*}
-
-Using lemma \ref{lemma:consis_1}, the above term can be upper bounded by,
+\end{align*}
+
+Using Lemma~\ref{lemma:consis_1}, the above term can be upper bounded by,
 
@@
 \\
-Similar to the above proof, second part of Term (1*) can also be written as a summation of k terms and the proof follows exactly as the first part.
-Now we prove that Term (2*) $\xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
-
-\begin{align*}
-    &\dfrac{1}{m}\sum\limits_{s=1}^{m}(\overline{X}_s - \mu)_i(\overline{X}_s - \mu)_j\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)\\
-    & < \dfrac{1}{m}\sum\limits_{s=1}^{m} \|\overline{X}_s - \mu\|_{\infty}^2 \sum\limits_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{b_n}\right)\right|\\
-    & = \dfrac{b_n}{m}\sum\limits_{s=1}^{m} \|\overline{X}_s - \mu\|_{\infty}^2 \dfrac{1}{b_n} \sum\limits_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{b_n}\right)\right|\\
-    & \leq \dfrac{b_n}{m}\sum\limits_{s=1}^{m} \|\overline{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w_n(x)}dx
-\end{align*}
-\\
-Recall that the lag window is such that $\int_{-\infty}^{\infty} \abs{w_n(x)}dx = C$ for some constant C. Using lemma \ref{lemma:consis_1}, Term (2*) can be upper bounded by
-
+Similar to the above proof, second part of $N_1$ can also be written as a summation of $k$ terms and the proof follows exactly as the first part.
+Now we prove that $N_2 \xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
+
+\begin{align*}
+    &\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu \right)_i \left(\bar{X}_s - \mu \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)\\
+    & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
+\end{align*}
+Recall that the lag window is such that $\int_{-\infty}^{\infty} \abs{w(x)}dx = C$ for some constant C. Using Lemma~\ref{lemma:consis_1}, $N_2$ can be upper bounded by
+%
 \begin{equation} \label{eq:PASVE_term-2}
@@
 \end{equation}
-
-(\ref{eq:PASVE_term-2}) is also $\mathcal{O}\left(\dfrac{b_n \log \log n}{n}\right)$, and hence converges to 0 as $n \to \infty$.
-
+%
+\eqref{eq:PASVE_term-2} is also $\mathcal{O}\left(n^{-1}{b_n \log \log n}\right)$, and hence converges to 0 as $n \to \infty$.
 \end{proof}
@@
 \begin{proof}[Proof of theorem \ref{th:consistency}]
-We first show that Term (1) $\xrightarrow{a.s} 0$ as $n \to \infty$ with the help of SIP and prior assumptions.
-\begin{align*}
-   & \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|} \dfrac{1}{n}\left[(X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j+ (\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right]\right\}\right| \\
-   & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|}(X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j\right|}+\dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|}(\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j\right|} \right]\right\}
-\end{align*}
-
-\begin{align*}
-    & \leq \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum\limits_{t=1}^{n-|k|}(X_{st}- \mu)_i\right|\left|(\mu-\overline{\overline{X}})_j\right|+ \dfrac{1}{n}\left|(\mu-\overline{\overline{X}})_i\right|\left|\sum\limits_{t=1}^{n-|k|}(X_{j(t+k)}-\mu)_j\right|\right]\right\}\\
-    & \leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=1}^{n-|k|}(X_{st}-\mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{n-|k|}(X_{s(t+k)}-\mu)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=n-|k|+1}^{n}(X_{st} - \mu) - n(\overline{X}_s - \mu) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu) - n(\overline{X}_s - \mu)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} + 2\|\overline{X}_s - \mu\|_{\infty} \right]\\
-    & \leq \dfrac{\|(\overline{\overline{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum\limits_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\| + \dfrac{1}{n}\left\|\sum\limits_{t=1}^{|k|}(X_{st} - \mu)\right\| \right]\\
-    & \; \;+ 2(2b_n - 1)\|\overline{\overline{X}} - \mu\|_{\infty}\|\overline{X}_1 - \mu\|_{\infty} 
+We first show that $M_1\xrightarrow{a.s} 0$ as $n \to \infty$ with the help of SIP and prior assumptions.
+\begin{align*}
+& M_1 \\ 
+   & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\
+   & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|} \left(X_{st} - \mu \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-|k|} \left(\mu-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu \right)_j\right|} \right]\right\}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t=1}^{n-|k|}(X_{st}- \mu)_i\right|\left|(\mu-\bar{\bar{X}})_j\right|+ \dfrac{1}{n}\left|(\mu-\bar{\bar{X}})_i\right|\left|\sum_{t=1}^{n-|k|}(X_{j(t+k)}-\mu)_j\right|\right]\right\}\\
+    & \leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(X_{st}-\mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(X_{s(t+k)}-\mu)\right\|_{\infty} \right]\\
+    &\leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \\
+    & \quad \times \sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu) - n(\bar{X}_s - \mu) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(X_{st} - \mu) - n(\bar{X}_s - \mu)\right\|_{\infty} \right]\\
+    &\leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} + 2\|\bar{X}_s - \mu\|_{\infty} \right]\\
+    & \leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \left\|\sum_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} \right]\\
+    & \; \;+ 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty} 
 \end{align*}
 \\
-Using SIP on summation of $k$ terms, we obtain the following upper bound for Term (1)
-\begin{align*}
-    & < 2\|(\overline{\overline{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + 2(2b_n - 1)\|\overline{\overline{X}} - \mu\|_{\infty}\|\overline{X}_1 - \mu\|_{\infty} \\
-    &\leq 2(2b_n - 1)\|(\overline{\overline{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right] + 2(2b_n - 1)\|\overline{\overline{X}} - \mu\|_{\infty}\|\overline{X}_1 - \mu\|_{\infty}
-\end{align*}
-\\
-We use lemma \ref{lemma:consis_1} to upper bound the above term as
+Using SIP on summation of $k$ terms, we obtain the following upper bound for $M_1$
+\begin{align*}
+& M_1\\
+    & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty} \\
+    &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right] + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\,.
+\end{align*}
+%
+We use Lemma~\ref{lemma:consis_1} to upper bound the above term as
 \begin{equation} \label{eq:strong_consis_term-1}
@@
 Using the bound on $\psi(n)$ given by \cite{stra:1964}, equation (\ref{eq:strong_consis_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
-Now we will show that Term (2) $\xrightarrow{a.s.} 0$ as $n\to \infty$
-
-\begin{align*}
-    &\left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{(\mu-\overline{\overline{X}})_i(\mu-\overline{\overline{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)\right\}\right|\\
-    & \leq\|\overline{\overline{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w_n\left(\dfrac{k}{n}\right)\right]\\
-    &< \|\overline{\overline{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{n}\right)\right|\right]\\
-    &= b_n\|\overline{\overline{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w_n\left(\dfrac{k}{n}\right)\right|\right]\\
-    & \leq b_n\|\overline{\overline{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w_n(x)|dx \\
-    & \leq Cb_n\|\overline{\overline{X}} - \mu \|^2
-\end{align*}
-
+Now we will show that $M_2 \xrightarrow{a.s.} 0$ as $n\to \infty$
+
+\begin{align*}
+   M_2 & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu - \bar{\bar{X}} \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\right\}\right|\\
+    & \leq\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\right]\\
+    &< \|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{n}\right)\right|\right]\\
+    &= b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{n}\right)\right|\right]\\
+    & \leq b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w(x)|dx \\
+    & \leq Cb_n\|\bar{\bar{X}} - \mu \|^2
+\end{align*}
+%
 Using lemma \ref{lemma:consis_1} to upper bound the above term as
@@
 \end{equation}
-\\
-Equation (\ref{eq:strong_consis_term-2}) has the same order as equation (\ref{eq:strong_consis_term-1}), i.e. $\mathcal{O}\left(b_n \log \log n/n\right) \to 0 \textrm{ as } n \to \infty$.
-We have already shown that Term (1) and Term (2) converge to 0 almost surely $\implies \hat{\Sigma}_{RSV} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$.
-Now we can find the functions $g_1(n), g_2(n) \textrm{ and, } g_3(n)$ by adding (\ref{eq:strong_consis_term-1}) and (\ref{eq:strong_consis_term-2}).
-After some simple algebra, we obtain the following results:\\
-
+%
+Equation~\eqref{eq:strong_consis_term-2} has the same order as equation \eqref{eq:strong_consis_term-1}, i.e. $\mathcal{O}\left(b_n \log \log n/n\right) \to 0 \textrm{ as } n \to \infty$.
+We have already shown that $M_1$ and $M_2$ converge to 0 almost surely $\implies \hat{\Sigma}_{RSV} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$.
+Now we can find the functions $g_1(n), g_2(n) \textrm{ and, } g_3(n)$ by adding \eqref{eq:strong_consis_term-1} and \eqref{eq:strong_consis_term-2}.
+After some simple algebra, we obtain the following results:
+%
 \begin{align*}
@@
 
-\\
 \subsection{Bias Calculations} \label{appendix:bias}
@@
 \begin{lemma} \label{lemma:bias1}
-$\mathbb{E}[(X_{11}-\overline{X}_1)(\overline{X}_1 - \overline{\overline{X}})^T] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
+$\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
 \end{lemma}
@@
 \begin{align*}
-    &\mathbb{E}[(X_{11}-\overline{X}_1)(\overline{X}_1 - \overline{\overline{X}})^T] = \mathbb{E}[X_{11}\overline{X}_1^T] - \mathbb{E}[X_{11}\overline{\overline{X}}^T] + \mathbb{E}[\overline{X}_1\overline{\overline{X}}^T] - \mathbb{E}[\overline{X}_1\overline{X}_1^T]\\
-    &= \mathbb{E}[X_{11}\overline{X}_1^T] - \dfrac{1}{m}\mathbb{E}[X_{11}\overline{X}_1^T] - \dfrac{m-1}{m}\mathbb{E}[X_{11}\overline{X}_2^T] + \dfrac{1}{m}\mathbb{E}[\overline{X}_1\overline{X}_1^T] + \dfrac{m-1}{m}\mathbb{E}[\overline{X}_1\overline{X}_2^T] - \mathbb{E}[\overline{X}_1\overline{X}_1^T]\\
-    &= \dfrac{m-1}{m}\left(\mathbb{E}[X_{11}\overline{X}_1^T] - \mathbb{E}[X_{11}\overline{X}_2^T] + \mathbb{E}[\overline{X}_1\overline{X}_2^T] - \mathbb{E}[\overline{X}_1\overline{X}_1^T]\right)\\
-    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{i=1}^{n}\mathbb{E}[X_{11}X_{1i}^T] - \mathbb{E}[X_{11}]\mathbb{E}[\overline{X}_2^T] + \mathbb{E}[\overline{X}_1]\mathbb{E}[\overline{X}_2^T] - Var[\overline{X}_1] - \mathbb{E}[\overline{X}_1]\mathbb{E}[\overline{X}_1^T]\right)\\
+    &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
+    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \dfrac{\Sigma}{n} - \mu \mu^T\right)\\
-    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma\right)
+    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma\right)\,.
+\end{align*}
+%
+Similarly, we can show that $\mathbb{E}[A_{ij}^T] = \mathbb{E}[A_{ij}]$ using the symmetry of $\Gamma(k) \textrm{ and } \Sigma$ matrices.
+%    
+\begin{align*}
+    \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
+    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
+\end{align*}
+\end{proof}
+
+\begin{lemma} \label{lemma:bias2}
+\[\mathbb{E}\left[\sum\limits_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right) \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] =  (m-1)\text{Var}(\bar{X}_1)\,.
+\]
+\end{lemma}
+
+% $\bar{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\bar{\bar{X}}) = \dfrac{1}{m} \Var(\bar{X}_1)$.
+
+\begin{proof}
+\begin{align*}
+\mathbb{E}\left[\sum_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} -\sum_{s=1}^{m}\bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}}^{T}\sum_{s=1}^{m}\bar{X}_{s}^{T} + m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+&= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} - m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+&= m\left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
+&= m\left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
+&= (m-1)\Var(\overline{X_1})\,.
+\end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{th:RAC_expec}]
+\begin{align*}
+    & \hat{\Gamma}_{RAC}(k) \\
+    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T\\
+    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]\\
+    & \quad +  \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-|k|}{mn}\sum_{s=1}^{m}  \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,,
+\end{align*}
+%
+where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$.
+Using \eqref{eq:priestly}, Lemma~\ref{lemma:bias1}, and Lemma~\ref{lemma:bias2}, the expectation of $\hat{\Gamma}_{RAC}(k)$ can be written as
+%
+\begin{align*}
+\hat{\Gamma}_{RAC}(k) &= \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \Var(\overline{X_1})\right) - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right)\\
+    & \quad  + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\right) - \dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma(h) - \Sigma\right)
 \end{align*}
 \\
-Similarly, we can show that $\mathbb{E}[A_{ij}^T] = \mathbb{E}[A_{ij}]$ using the symmetry of $\Gamma(k) \textrm{ and } \Sigma$ matrices.
-
-\begin{align*}
-    \mathbb{E}[(\bar{X}_1 - \bar{\bar{X}})(X_{11}-\bar{X}_1)^T] &= \mathbb{E}[(X_{11}-\bar{X}_1)(\bar{X}_1 - \bar{\bar{X}})^T]^T\\
-    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\\
-    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
-\end{align*}
-\end{proof}
-
-\begin{lemma} \label{lemma:bias2}
-$$\mathbb{E}\left[\sum\limits_{s=1}^{m}(\overline{X}_{s}-\overline{\overline{X}})(\overline{X}_{s}-\overline{\overline{X}})^{T}\right] =  (m-1)\Var(\overline{X_1})$$
-\end{lemma}
-\\
-$\overline{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\overline{\overline{X}}) = \dfrac{1}{m} \Var(\overline{X}_1)$.
-
-\begin{proof}
-\begin{align*}
-\mathbb{E}\left[\sum\limits_{s=1}^{m}(\overline{X}_{s}-\overline{\overline{X}})(\overline{X}_{s}-\overline{\overline{X}})^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\overline{X}_{s}\overline{X}_{s}^{T} -\sum_{s=1}^{m}\overline{X}_{s}\overline{\overline{X}}^{T} - \overline{\overline{X}}^{T}\sum_{s=1}^{m}\overline{X}_{s}^{T} + m\overline{\overline{X}}\overline{\overline{X}}^{T}\right]\\
-&= \mathbb{E}\left[\sum_{s=1}^{m}\overline{X}_{s}\overline{X}_{s}^{T} - m\overline{\overline{X}}\overline{\overline{X}}^{T}\right]\\
-&= m\left(\mathbb{E}\left[\overline{X}_{1}\overline{X}_{1}^{T}\right] - \mathbb{E}\left[\overline{\overline{X}}\overline{\overline{X}}^{T}\right]\right)\\
-&= m\left(Var(\overline{X}_{1}) + \mu\mu^{T} - Var(\overline{\overline{X}}) - \mu\mu^{T}\right)\\
-&= (m-1)\Var(\overline{X_1})
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of theorem \ref{th:RAC_expec}]
-\begin{align*}
-    \hat{\Gamma}_{RAC}(k) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|}(X_{st}-\overline{\overline{X}})(X_{s(t+k)}-\overline{\overline{X}})^T\\
-    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T\right] + \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}(\overline{X}_s - \overline{\overline{X}})(\overline{X}_s - X_{st})^T\right]\\
-    &+  \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}( \overline{X}_s - X_{st})(\overline{X_s}-\overline{\overline{X}})^T\right] + \left[\dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T\right]\\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T
-\end{align*}
-
-where $A_{st} = (X_{st}-\overline{X}_s)(\overline{X}_s - \overline{\overline{X}})^T$.\\
-
-\\
-Using equation \ref{eq:priestly}, lemma \ref{lemma:bias1}, and lemma \ref{lemma:bias2}, the expectation of $\hat{\Gamma}_{RAC}(k)$ can be written as
-
-\begin{align*}
-    &= \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \Var(\overline{X_1})\right) - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\overline{X_1})\\
-    &= \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{1}{m}\Var(\overline{X_1})\right) - \dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma(h) - \Sigma\right)
-\end{align*}
-\\
-Using the results of \cite{song1995optimal} given in equation \ref{eq:song} to expand $\Var(\overline{X}_1)$,
-\[
-\mathbb{E}[\hat{\Gamma}_{RAC}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
-\]
-\\
+Using the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$,
+\[
+\mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})\,.
+\]
+%
 We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
@@
 Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$.
-We have explicitly written the end effect term arising from using the estimator $\overline{\overline{X}}$ for $\mu$.
+We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$.
 These are small order terms that vanish as $n \to \infty$.
@@
 \begin{align*}
-    \hat{\Gamma}_{RAC}(k) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st}-\overline{\overline{X}})(X_{s(t+k)}-\overline{\overline{X}})^T\\
-    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T\right]\\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k)  + \dfrac{1}{m}\sum_{s=1}^{m}(\overline{X_s}-\overline{\overline{X}})(\overline{X_s}-\overline{\overline{X}})^T
-\end{align*}
-Using equation \ref{eq:priestly}, lemma \ref{lemma:bias2}, and equation \ref{eq:song} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as
-
-\begin{align*}
-    \mathbb{E}[\hat{\Gamma}_{RAC}(0)] &= \left(\Gamma(k) - \Var(\overline{X_1})\right) + \left(1-\dfrac{1}{m}\right)\Var(\overline{X_1})\\
-    &= \Gamma(k) - \dfrac{1}{m}\Var(\overline{X_1})\\
+    \hat{\Gamma}_{RAC}(k) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{s(t+k)} - \bar{\bar{X}}\right)^T\\
+    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{s(t+k)} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
+\end{align*}
+Using \eqref{eq:priestly}, Lemma~\ref{lemma:bias2}, and \eqref{eq:song} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as 
+%
+\begin{align*}
+    \mathbb{E} \left[\hat{\Gamma}_{RAC}(0) \right] &= \left(\Gamma(k) - \Var(\bar{X}_1)\right) + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\\
     &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
@@
 \begin{equation} \label{eq:rac_bias2}
-\mathbb{E}[\hat{\Gamma}_{RAC}(k)] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + \left(1 - \dfrac{\abs{k}}{n}\right)\mathcal{O}(1/n) + \mathcal{O}(1/n)    
+\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + \left(1 - \dfrac{\abs{k}}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)    \,.
 \end{equation}
 
-The last term in (\ref{eq:rac_bias2}) is stated separately because it does not depend on $k$. 
-\begin{align*}
-    &\mathbb{E}[\hat{\Sigma}_{RSV} - \Sigma]\\
-    &= \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E}[\hat{\Gamma}_{RAC}(k)]-\sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-b_n+1}^{b_n-1}\left\{ w_n\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\left[\left(\Gamma(k) + \mathcal{O}\left(\dfrac{1}{n}\right)\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right]\right\} - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-b_n+1}^{b_n-1}\left\{ w_n\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right\} - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &+ \sum_{k=-b_n+1}^{b_n-1}\left\{ w_n\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \right\}
-\end{align*}
-Since $w_n\left(\dfrac{k}{b_n}\right) = 0$ for $|k| > b_n$, we can decompose the above term as:\\
-Let Term \textbf{A}: $\sum\limits_{k=-n+1}^{n-1}\left\{w_n\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right\} - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)$\\
-
-Let Term \textbf{B}: $\sum\limits_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \right\}$\\\\
+Since $w\left(\dfrac{k}{b_n}\right) = 0$ for $|k| > b_n$. 
+The last term in \eqref{eq:rac_bias2} is stated separately because it does not depend on $k$. 
+\begin{align*}
+    &\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right]\\
+    &= \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\left[\left(\Gamma(k) + \mathcal{O}\left(\dfrac{1}{n}\right)\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    & \quad + \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \\ 
+    & = O_1 + O_2\,,
+\end{align*}
+%
+where 
+\begin{align*}
+O_1 & = \sum\limits_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right\} - \sum\limits_{k=-\infty}^{\infty}\Gamma(k) \\ 
+O_2 &= \sum\limits_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \right\}\,.
+\end{align*}
 
 \begin{enumerate}
-    \item We first solve for term {\textbf{A}} by breaking it into three parts as in \cite{hannan2009multiple}.\\
-
-$$-\sum_{|k|\geq n}\Gamma(k) + \sum_{k = -n+1}^{n-1}w_n\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w_n\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)$$\\
-
+\item We first solve for term $O_1$ by breaking it into three parts as in \cite{hannan2009multiple}.
+\[
+-\sum_{|k|\geq n}\Gamma(k) + \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)
+\]
+%
 We deal with the three subterms of term \textbf{A} individually,
@@
     \begin{align*}
-        \left\|{-\sum_{|k|\geq n}\Gamma(k)}\right\| &\leq   \abs{\dfrac{k}{n}}^q\sum_{|k|\geq n}\|\Gamma(k)\|\\
-        &= \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q\underbrace{\sum_{|k|\geq n}|k|^q\|\Gamma(k)\|}_{<\infty}\\
-        &= o\left(\dfrac{1}{b_n^q}\right)
+        \left\|{-\sum_{|k|\geq n}\Gamma(k)}\right\| &\leq   \abs{\dfrac{k}{n}}^q\sum_{|k|\geq n}\|\Gamma(k)\| = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q\underbrace{\sum_{|k|\geq n}|k|^q\|\Gamma(k)\|}_{<\infty} = o\left(\dfrac{1}{b_n^q}\right)
     \end{align*}
@@
 \begin{align*}
-   \left\| \sum_{k = -n+1}^{n-1}w_n\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)\right\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| 
-\end{align*}
-
- \begin{enumerate}
-     \item For q $\geq 1$, we have, $\sum_{k=-n+1}^{n-1}|k|^q\|\Gamma(k)\| < \infty$
-     \begin{align*}
-         \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\|\\
-         &= \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\|\\
-         &= o\left(\dfrac{1}{b_n^q}\right) 
-     \end{align*}
-
-     \item For q $<1$:\\
-     \begin{align*}
-         c\sum_{k =-n+1}^{n-1}\dfrac{|k|}{n}\|\Gamma(k)\| &\leq c\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q\|\Gamma(k)\|\\
-         &= \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k =-n+1}^{n-1}|k|^q\|\Gamma(k)\|\\
-         &= o\left(\dfrac{1}{b_n^q}\right) 
-     \end{align*}
+   \left\| \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)\right\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| 
+\end{align*}
+
+For $q \geq 1$, we have, $\sum_{k=-n+1}^{n-1}|k|^q\|\Gamma(k)\| < \infty$
+   \begin{align*}
+       \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\| = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\| = o\left(\dfrac{1}{b_n^q}\right)
+   \end{align*}
+
+For $q <1$:
+   \begin{align*}
+       c\sum_{k =-n+1}^{n-1}\dfrac{|k|}{n}\|\Gamma(k)\| &\leq c\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q\|\Gamma(k)\| = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k =-n+1}^{n-1}|k|^q\|\Gamma(k)\| = o\left(\dfrac{1}{b_n^q}\right)
+   \end{align*}
+
+  \item Next,
+     \[
+     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k)\,.
+     \]
+%     
+     The condition 
+     \[
+     \lim_{\abs{x}\to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty
+     \]
+     implies that $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$; where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
+     \[
+     \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
+     \]
 \end{enumerate}
-     \item 
-     $$\sum_{k = -n+1}^{n-1}\left(1-w_n\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}\left[\dfrac{\left(1-w_n\left(\dfrac{|k|}{b_n}\right)\right)}{\left(\dfrac{|k|}{b_n}\right)^q}|k|^q \Gamma(k)\right]$$\\
-
-     The condition 
-     \[
-     \lim_{\abs{x}\to 0}\dfrac{1 - w_n(x)}{\abs{x}^q} = k_q < \infty
-     \]
-     implies that $\dfrac{1-w_n(k/b_n)}{\abs{k/b_n}^q}$ converges boundedly to $k_q$ for each $k$; where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
-     \[
-     \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w_n\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
-     \]
+
+ \item Solving for $O_2$. We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
+ \begin{align*}
+     & \sum_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right) \right] \right\} \\
+     &\leq \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\mathcal{O}\left(\dfrac{1}{n}\right)\\
+     &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right) \\
+     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
+     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
+ \end{align*}
  \end{enumerate}  
-
- \item Solving for Term \circled{\textbf{B}}. We will find an upper bound and prove that it is $\mathcal{O}\left(\dfrac{1}{n}\right)$:
- \begin{align*}
-     & \sum_{k=-n+1}^{n-1}\left\{w_n\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right) \right] \right\} \\
-     &\leq \sum_{k=-n+1}^{n-1}w_n\left(\dfrac{|k|}{b_n}\right)\mathcal{O}\left(\dfrac{1}{n}\right)\\
-     &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}w_n\left(\dfrac{|k|}{b_n}\right) \\
-     &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
-     &= \mathcal{O}\left(\dfrac{1}{n}\right) \\
-     &= o\left(\dfrac{1}{b_n^q}\right) 
- \end{align*}
- \end{enumerate}  
- \\
+%
  We have shown that all, but one, terms are $o(1/b_n^q)$.
 Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{RAC} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
-This is quite intuitive as we are using a strongly consistent estimator $\overline{\overline{X}}$ for $\mu$ in our replicated autovariance estimator.
+This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu$ in our replicated autovariance estimator.
 Similar to theorem \ref{th:RAC_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
@@
  &\left| \hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right|\\
- & \leq \dfrac{1}{m} \ds\sum_{s=1}^m \left|\sum_{k=-b_n+1}^{b_n-1}w_n\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}\left[\left( \dfrac{(X_{st}-\mu)_i(\mu-\overline{\overline{X}})_j}{n}\right)+ \left(\dfrac{(\mu-\overline{\overline{X}})_i(X_{s(t+k)}-\mu)_j}{n}\right) \right] \\
-& \quad \quad  + (\mu-\overline{\overline{X}})(\mu-\overline{\overline{X}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w_n\left(\dfrac{k}{n}\right) \right| \\ 
+ & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t=1}^{n-|k|}   \left[ \left( \dfrac{(X_{st} - \mu)_i(\mu-\bar{\bar{X}})_j}{n}\right)+ \left(\dfrac{(\mu-\bar{\bar{X}})_i(X_{s(t+k)}-\mu)_j}{n}\right) \right] \right.\\
+& \quad \quad  \left. + (\mu-\bar{\bar{X}})(\mu-\bar{\bar{X}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right| \\ 
  & < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
@@
 \begin{align*}
-& \left|  \xi\left(\hat{\Sigma}_{RSV}^{ij}, \tilde{\Sigma}^{ij} \right) \right|\\
-& \leq \left| \Var\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\
+\left|  \xi\left(\hat{\Sigma}_{RSV}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\
 & \leq \E\left[\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\
@@
 \end{align*}
-
+%
 Finally,
@@
 \begin{equation} \label{eq:hannan_var}
-\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = [\Sigma^{ii}\Sigma^{jj} + \Sigma^{ij}^2]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
+\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = [\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right)2]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
 \end{equation}
@@
 
+\singlespacing
 \bibliographystyle{apalike}

### 2020-06-04 Paper/main.tex
Cleaned some plots and a little of the paper

@@
 % The first line above is to announce we are beginning a document, an article in this case, and we want the default font size to be 12pt
-\usepackage[utf8]{inputenc}
+% \usepackage[utf8]{inputenc}
 \usepackage[left=1.2in,top=.8in,right=1.2in,nohead,bottom=.5in]{geometry}
@@
 
-\usepackage{amssymb}
-\usepackage{amsthm}
+\usepackage{amssymb,amsthm,amsmath}
 \usepackage{commath}
-\usepackage{enumerate}
-\usepackage{amsmath}
+\usepackage{enumerate,xcolor}
 \usepackage{natbib}
@@
 \usepackage{subcaption}
-\graphicspath{ {./plots/} }
 \DeclareMathOperator{\Tr}{Tr}
@@
 \theoremstyle{remark}
+\newtheorem{example}{Example}
 \newtheorem{ass}{Assumption}
@@
 % \usepackage[mathscr]{euscript}
-\usepackage{tikz}
-\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
-            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
+% \usepackage{tikz}
+% \newcommand*\circled[1]{\tikz[baseline=(char.base)]{
+%             \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
 % \newcommand{\indep}{\perp \!\!\! \perp}
@@
 Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains for decently finite samples.
-We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.\\
+We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.
 
@@
 An important application of ACF is in calculating the asymptotic variance in the CLT of a Markov chain process.
-\\
 
 Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in
-
+%
 \[
@@
 We will use the following Monte Carlo estimator in order to estimate $\mu$ for the $s^{th}$ chain
-
+%
 \[
@@
 The sampling distribution for Monte Carlo error of $s^{th}$ chain is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
-
+%
 \[
@@
 We call this replicated spectral variance (RSV) estimator (see \cite{arg:and:2006} for replicated batch means).
-\\
 
@@
 The quality of estimation of $\Sigma$ is critical in determining that the simulations are not stopped prematurely.
-\\
 
@@
 In this paper, we will address the asymptotic properties (basically strong consistency), bias and variance calculations for RSV estimator.
-\\
 
@@
 This appeals intuitively because for a fast mixing Markov chain, all the chains will give almost same estimates for mean.
-\\
 
@@
 
+\begin{example}[Motivating example]
+  gj
+\begin{figure}
+\begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
+  \caption{$n = 500$}
+  \label{subfig:acf-500}
+\end{subfigure}\\
+\begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
+  \caption{$n = 10^4$}
+  \label{subfig:acf-5e4}
+\end{subfigure}
+\caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains.
+First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
+\label{fig:var_acf_ccf}
+\end{figure}
+
+\end{example}
 \section{Replicated Autocovariance Function} \label{sec:R-ACF}
@@
 In time series literature, we generally encounter the following estimator for autocovariance.
-
+%
 \[
@@
 However, for larger relative $k$ the variance of $\hat{\Gamma}(k)$ compensates for larger bias rendering a smaller mean square error than $\Gamma^*(k)$.
-\\
 
@@
 The replicated autocovariance estimator or $s^{th}$ Markov chain is given by:
-
+%
 \[
@@
 
-\begin{figure}
-\begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{plots/acf-500.pdf}
-  \caption{$n = 500$}
-  \label{subfig:acf-500}
-\end{subfigure}\\
-\begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{plots/acf-5e4.pdf}
-  \caption{$n = 5*10^4$}
-  \label{subfig:acf-5e4}
-\end{subfigure}
-\caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains.
-First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n = 5 \times 10^4$, converged}
-\label{fig:var_acf_ccf}
-\end{figure}
-
 The bias for R-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:RAC_expec}.
@@
 
-where $w(.)$ is the lag window and $b_n$ is the truncation point.\\
+where $w(.)$ is the lag window and $b_n$ is the truncation point.
 
@@
 Consider,
-
+%
 \begin{align*}
@@
 
-\bigskip
-
 \begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true. As a consequence, 
@@
 \end{ass}
-
-\bigskip
 
@@
 
-\bigskip
 \begin{theorem}
@@
 Define
-
+%
 \[
@@
 
-\bigskip
-
 \begin{theorem} \label{th:rsv_variance}
@@
       \centering
-      \includegraphics[width = \textwidth]{plots/boom-sp_1e3.pdf}
+      \includegraphics[width = \textwidth]{plots/scatter_n1000.pdf}
       \caption{$n = 1000$}
@@
       \centering
-      \includegraphics[width = \textwidth]{plots/boom-sp_1e4.pdf}
-      \caption{$n = 10,000$}
+      \includegraphics[width = \textwidth]{plots/scatter_n50000.pdf}
+      \caption{$n = 50000$}
       \label{boom-sp_1e4}
@@
       \centering
-      \includegraphics[width = \textwidth]{boom-acf_1e3.pdf}
+      \includegraphics[width = \textwidth]{plots/boom-acf,n=1000.pdf}
       \caption{$n = 1000$}
@@
       \centering
-      \includegraphics[width = \textwidth]{boom-acf_1e4.pdf}
-      \caption{$n = 10,000$}
+      \includegraphics[width = \textwidth]{plots/boom-acf,n=50000.pdf}
+      \caption{$n = 50000$}
       \label{subfig:boom-acf_1e4}
@@
 
-\bigskip
-
 \begin{lemma} \label{lemma:consis_1}
@@
 \begin{align*}
-    \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as} n \to \infty
+    \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as } n \to \infty
 \end{align*}
@@
 \subsection{Strong consistency argument} \label{appendix:strong_consis}
-
-\bigskip
 
@@
 \begin{align*}
-    \tilde{\Sigma}^{ij} & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t+|k|)} - \mu \right)_j\\
+    &\tilde{\Sigma}^{ij} \\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t+|k|)} - \mu \right)_j\\
     & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} \pm \bar{X}_s - \mu \right)_i  \left(X_{s(t+|k|)} \pm \bar{X}_s - \mu \right)_j\\
@@
 \end{proof}
-
-\bigskip
 
@@
 \begin{align*}
-& M_1\\
-    & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty} \\
-    &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right] + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\,.
+M_1
+    & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \\
+    & \quad + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty} \\
+    &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]\\
+    & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\,.
 \end{align*}
@@
 \end{align*}
-%
-Using lemma \ref{lemma:consis_1} to upper bound the above term as
+
+Using Lemma~\ref{lemma:consis_1} to upper bound the above term as
 
@@
 \begin{align*}
-    &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+    &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
+     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\

### 2020-06-04 Boomerang/acf_plots.R

@@ -3,7 +3,7 @@ source("functions.R")
 library(rep.acf.ccf)
 
 
-m <- 5
+m <- 2
 A <- 1
 B <- 3
 C <- 8
@@ -15,6 +15,7 @@ for(i in 1:floor(m/2)){
   start[m-i+1,] <- c(C*(2^(2-i)), 0)
 }
 
+lag.max <- 100
 ####################################
 nsim <- 500
 ########################################
@@ -27,10 +28,10 @@ for (i in 1:m){
 }
 global.mean <- global.mean/m
 
-acf.list <- combined_acf(mc.chain.list, chain = 1, component = c(1,2), lag.max = 150, type = "covariance")
-ccf.list <- combined_ccf(mc.chain.list, chain = 1, component = c(1,2), lag.max = 150, type = "covariance")
+acf.list <- combined_acf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
+ccf.list <- combined_ccf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
 
-pdf(file = paste(paste("Out/", A, B, C, "/acf, n=", sep = "_"), nsim, ".pdf", sep = ""), title = paste("Locally vs. globally centered ACF plot, nsim = ", nsim), height = 3)
+pdf(file = paste(paste("Out/", A, B, C, "/boom-acf,n=", sep = "_"), nsim, ".pdf", sep = ""), width = 8, height = 4)
 #par(mfrow = c(3,2))
 #for (i in 1:2){
 #  plot(acf.list[[i]][[1]], main = paste("ACF for component -", i ))
@@ -39,11 +40,16 @@ pdf(file = paste(paste("Out/", A, B, C, "/acf, n=", sep = "_"), nsim, ".pdf", se
 #plot(ccf.list[[1]], main = "CCF for component 1-2")
 #plot(ccf.list[[2]], main = "R-CCF for component 1-2")
 par(mfrow = c(1,2))
-plot(acf.list[[1]][[1]], main = paste("ACF for component - 1"))
-plot(acf.list[[1]][[2]], main = paste("R-ACF for component - 1"))
+plot(acf.list[[1]][[1]], main = expression(paste("Old ACF for chain 1")))
+plot(acf.list[[1]][[2]], main = expression(paste("New ACF for chain 1")))
 
 dev.off()
 
[…]

### 2020-06-04 Boomerang/output.R

@@ -55,11 +55,9 @@ for(i in 1:floor(m/2)){
     start[m-i+1,] <- c(C*(2^(2-i)), 0)
 }
 
-#load(file = paste(paste("Out/", A, B, C, "/conv_data", m, min, max, A, B, C, sep = "_"), ".Rdata", sep = ""))
-load(file = paste(paste("Out/tukey/", A, B, C, "/conv_data", m, min, max, A, B, C, sep = "_"), ".Rdata", sep = ""))
+load(file = paste(paste("Out/", A, B, C, "/conv_data", m, min, max, A, B, C, sep = "_"), ".Rdata", sep = ""))
 
-#pdf(file = paste(paste("Out/", A, B, C, "/run_plots", m, sep = "_"), ".pdf", sep = ""), height = 3)
-pdf(file = paste(paste("Out/tukey/", A, B, C, "/run_plots", m, sep = "_"), ".pdf", sep = ""), height = 3)
+pdf(file = paste(paste("Out/", A, B, C, "/run_plots", m, sep = "_"), ".pdf", sep = ""), height = 3)
 
 par(mfrow = c(1,3))
   
@@ -90,8 +88,7 @@ dev.off()
 
 ## 2.) Scatter and trace plots
 
-#pdf(file = paste(paste("Out/", A, B, C, "/scatter_plot", m, sep = "_"), ".pdf", sep = ""), height = 5)
-pdf(file = paste(paste("Out/tukey/", A, B, C, "/scatter_plot", m, sep = "_"), ".pdf", sep = ""), height = 5)
+pdf(file = paste(paste("Out/", A, B, C, "/scatter_plot", m, sep = "_"), ".pdf", sep = ""), height = 5)
 
 par(mfrow = c(2,3))
 
@@ -103,7 +100,7 @@ for (j in 1:r){
     chain[,,p] <- markov.chain(A, B, C, nsim, start[p,])
   }
 
-  plot(chain[,1,1], chain[,2,1], col = 2, xlim = c(-2,2*C), ylim = c(-2,2*C), main = paste("Scatter plot of m = ", m,  "Markov chains, n = ", nsim, ", A = ", A, ", B = ", B, ", C = ", C), xlab = "X", ylab = "Y")
[…]

### 2020-06-04 VAR-1/acf_plots.R

@@ -58,24 +58,29 @@ points(mc.chain.list[[4]], col = 4)
 points(mc.chain.list[[5]], col = 5)
 dev.off()
 
-acf.list <- combined_acf(mc.chain.list, chain = 2, component = seq(1,p), lag.max = 150, type = "correlation")
-ccf.list <- combined_ccf(mc.chain.list, chain = 2, component = c(1,2), lag.max = 150, type = "correlation")
+acf.list <- combined_acf(mc.chain.list, chain = 2, component = seq(1,p), lag.max = lag.max, type = "correlation")
+ccf.list <- combined_ccf(mc.chain.list, chain = 2, component = c(1,2), lag.max = lag.max, type = "correlation")
 
-pdf(file = paste("Out/acf, n = ", nsim, ".pdf", sep = ""), title = paste("Locally vs. globally centered ACF plot, nsim = ", nsim), height = 4)
-par(mfrow = c(2,2))
+# avg.acf <- (acf.list[[1]][[2]]$acf + acf.list[[2]][[2]]$acf)/2
+# com.acf <- acf.list
+# com.acf[[1]][[1]]$acf <- avg.acf
+pdf(file = paste("Out/acf,n=", nsim, ".pdf", sep = ""), width = 8, height = 4)
+par(mfrow = c(1,2))
 
-plot(acf.list[[1]][[1]], main = paste("ACF for component - 1"), xlim = range(0, lag.max), ylim =  c(0,1))#c(min(min(acf.list[[1]][[1]]$acf), min(true.acf[1,1,])), max(max(acf.list[[1]][[1]]$acf), max(true.acf[1,1,]))))
+plot(acf.list[[1]][[1]], main = expression(paste("Old ACF for chain 1")), xlim = range(0, lag.max), ylim =  c(0,1))#c(min(min(acf.list[[1]][[1]]$acf), min(true.acf[1,1,])), max(max(acf.list[[1]][[1]]$acf), max(true.acf[1,1,]))))
 lines(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red")
[…]

### 2020-06-11 Paper/main.tex
Proofs clean-up

@@
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
 % We can write notes using the percent symbol!
@@
 \newcommand{\B}{\mathcal{B}}
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
 % These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
@@
 \setlength{\parskip}{0em}
+\setlength{\parindent}{0in}
+\renewcommand{\arraystretch}{1.5}
+
 % This gives us a full line break when we write a new paragraph
@@
  \begin{equation} \label{eq:priestly}
-     \mathbb{E}[\hat{\Gamma}(k) = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
+     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
  \right)
@@
 
+\subsection{Bias of autocovariance} \label{appendix:bias}
+
+% \begin{lemma} \label{lemma:bias1}
+% $\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
+% \end{lemma}
+% \begin{proof}
+% \begin{align*}
+%     &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
+%      &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+%     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+%     &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
+%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
+%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
+%     &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,.
+% \end{align*}
+% %
+% Similarly,
+% %    
+% \begin{align*}
+%     \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
+%     % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
+% \end{align*}
+% \end{proof}
+
+% \begin{lemma} \label{lemma:bias2}
+% \[
+% \mathbb{E}\left[\sum\limits_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right) \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] =  (m-1)\text{Var}(\bar{X}_1)\,.
+% \]
+% \end{lemma}
+
+% % $\bar{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\bar{\bar{X}}) = \dfrac{1}{m} \Var(\bar{X}_1)$.
+
+% \begin{proof}
+% \begin{align*}
+% \mathbb{E}\left[\sum_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} -\sum_{s=1}^{m}\bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}}^{T}\sum_{s=1}^{m}\bar{X}_{s}^{T} + m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+% &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} - m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+% &= m\left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
+% &= m\left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
+% &= (m-1)\Var(\overline{X_1})\,.
+% \end{align*}
+% \end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{th:RAC_expec}]
+\begin{align*}
+    & \hat{\Gamma}_{RAC,s}(k) \\
+   & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
+    &= \left[\dfrac{1}{n} \sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\
+    & \quad +  \left[\dfrac{1}{n} \sum_{t=n-|k|+1}^{n}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-|k|}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{n}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
+\end{align*}
+%
+where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. We will study the expectations of the each of the above terms. Without loss of generality, consider $A_{11}$,
+\begin{align*}
+    &\E \left[A_{11} \right]\\
+     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
+     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
+    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
+    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
+    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
+\end{align*}
+%
+Similarly,
+%    
+\begin{align}
+\label{eq:acf_3}
+    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right] \right)^T\,.
+    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
+\end{align}
+
+Further,
+\begin{align*}
+\mathbb{E}\left[ \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{s}\bar{X}_{s}^{T} - \bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{s}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+&= \mathbb{E}\left[ \bar{X}_{s}\bar{X}_{s}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+&= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
+&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
+&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
+\end{align*}
+%
+Using \eqref{eq:priestly}, \eqref{eq:acf_2}, \eqref{eq:acf_3}, and \eqref{eq:acf_4} in \eqref{eq:acf_breakdown},
+\begin{align*}
+& \E \left[\hat{\Gamma}_{RAC,s}(k) \right] \\
+&= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - {\color{red}\dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma(h) - n \Var(\bar{X}_1)\right)} + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\,.
+\end{align*}
+{\color{red} DV: Instead of the ``2'', should it be something that has $\Gamma(h) + \Gamma(h)^T$?}
+
+Using the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$,
+\[
+\mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})\,.
+\]
+%
+We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
+This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.
+Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$.
+We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$.
+These are small order terms that vanish as $n \to \infty$.
+\end{proof}
+
+\begin{proof}[Proof of corollary \ref{cor:lag0_expectation}]
+
+\begin{align*}
+    \hat{\Gamma}_{RAC}(0) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(0) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{st} - \bar{\bar{X}}\right)^T\\
+    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{st} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
+\end{align*}
+Using \eqref{eq:priestly}, Lemma~\ref{lemma:bias2}, and \eqref{eq:song} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as 
+%
+\begin{align*}
+    \mathbb{E} \left[\hat{\Gamma}_{RAC}(0) \right] &= \left(\Gamma(k) - \Var(\bar{X}_1)\right) + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\\
+    &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
+\end{align*}
+
+\end{proof}
+
 \subsection{Strong consistency argument} \label{appendix:strong_consis}
@@
 
-\subsection{Bias Calculations} \label{appendix:bias}
-
-\begin{lemma} \label{lemma:bias1}
-$\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
-\end{lemma}
-\begin{proof}
-\begin{align*}
-    &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
-     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
-    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
-    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
-    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
-    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \dfrac{\Sigma}{n} - \mu \mu^T\right)\\
-    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma\right)\,.
-\end{align*}
-%
-Similarly, we can show that $\mathbb{E}[A_{ij}^T] = \mathbb{E}[A_{ij}]$ using the symmetry of $\Gamma(k) \textrm{ and } \Sigma$ matrices.
-%    
-\begin{align*}
-    \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
-    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
-\end{align*}
-\end{proof}
-
-\begin{lemma} \label{lemma:bias2}
-\[\mathbb{E}\left[\sum\limits_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right) \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] =  (m-1)\text{Var}(\bar{X}_1)\,.
-\]
-\end{lemma}
-
-% $\bar{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\bar{\bar{X}}) = \dfrac{1}{m} \Var(\bar{X}_1)$.
-
-\begin{proof}
-\begin{align*}
-\mathbb{E}\left[\sum_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} -\sum_{s=1}^{m}\bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}}^{T}\sum_{s=1}^{m}\bar{X}_{s}^{T} + m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
-&= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} - m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
-&= m\left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
-&= m\left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
-&= (m-1)\Var(\overline{X_1})\,.
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{th:RAC_expec}]
-\begin{align*}
-    & \hat{\Gamma}_{RAC}(k) \\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T\\
-    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]\\
-    & \quad +  \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-|k|}{mn}\sum_{s=1}^{m}  \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,,
-\end{align*}
-%
-where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$.
-Using \eqref{eq:priestly}, Lemma~\ref{lemma:bias1}, and Lemma~\ref{lemma:bias2}, the expectation of $\hat{\Gamma}_{RAC}(k)$ can be written as
-%
-\begin{align*}
-\hat{\Gamma}_{RAC}(k) &= \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \Var(\overline{X_1})\right) - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right)\\
-    & \quad  + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\right) - \dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma(h) - \Sigma\right)
-\end{align*}
-\\
-Using the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$,
-\[
-\mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})\,.
-\]
-%
-We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
-This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.
-Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$.
-We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$.
-These are small order terms that vanish as $n \to \infty$.
-\end{proof}
-
-\begin{proof}[Proof of corollary \ref{cor:lag0_expectation}]
-
-\begin{align*}
-    \hat{\Gamma}_{RAC}(k) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{s(t+k)} - \bar{\bar{X}}\right)^T\\
-    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{s(t+k)} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
-\end{align*}
-Using \eqref{eq:priestly}, Lemma~\ref{lemma:bias2}, and \eqref{eq:song} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as 
-%
-\begin{align*}
-    \mathbb{E} \left[\hat{\Gamma}_{RAC}(0) \right] &= \left(\Gamma(k) - \Var(\bar{X}_1)\right) + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\\
-    &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
-\end{align*}
-
-\end{proof}
+\subsection{RSV Bias}
 

### 2020-06-12 Paper/main.tex
Further organizing the appendix

@@
 
-We are going to consider a class of pseudo spectral variance estimator denoted by $\tilde{\Sigma}$ which uses data centered around the unobserved actual mean $\mu$.
-Such pseudo covariance estimator and autocovariance estimator for the $j^{th}$ chain is denoted by $\tilde{\Sigma}_s$ and $\tilde{\Gamma}_s$ respectively.
-
-\begin{align*}
-    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Gamma}_s(k)\\
-    \tilde{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)(X_{s(t+k)}-\mu)^T
-\end{align*}
-
-The average pseudo spectral variance estimator (APSVE) is given by
-
-\[
-\tilde{\Sigma} = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
-\]
-
 \begin{theorem}
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
@@
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
@@
 \begin{lemma} \label{lemma:consis_1}
-  Let the strong invariance principle hold.
-If $\dfrac{\psi(n)}{n} \to 0$ as $n \to \infty$, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
+  If Assumption~\ref{ass:sip} holds, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
   \end{lemma}
@@
 
-Using the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$,
-\[
-\mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})\,.
-\]
-%
-We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
+% Using the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$,
+% \[
+% \mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})\,.
+% \]
+%
+% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
 This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.
@@
 These are small order terms that vanish as $n \to \infty$.
+
+For a diagonal element of $\Gamma$,
+\begin{align*}
+& \E \left[ \hat{\Gamma}_{RAC,s}^{ii}\right]\\
+& = \mathbb{E}\left[\hat{\Gamma}_{s}^{ii}(k)\right] - {\color{red}\dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma^{ii}(h) - n \Var(\bar{X}_1)^{ii}\right)} + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)^{ii}\,.
+\end{align*}
+In the presence of positive correlation, the leftover term is positive. 
 \end{proof}
@@
     &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{st} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
-\end{align*}
-Using \eqref{eq:priestly}, Lemma~\ref{lemma:bias2}, and \eqref{eq:song} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as 
-%
-\begin{align*}
-    \mathbb{E} \left[\hat{\Gamma}_{RAC}(0) \right] &= \left(\Gamma(k) - \Var(\bar{X}_1)\right) + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\\
-    &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
+    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(0)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
+\end{align*}
+Using \eqref{eq:priestly} and \eqref{eq:acf_4} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as 
+%
+\begin{align*}
+    \mathbb{E} \left[\hat{\Gamma}_{RAC}(0) \right] &= \E\left[\hat{\Gamma}_1(0) \right] + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) \\
+    & = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\,.
+    % &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
 \end{align*}
@@
 
+We are going to consider a class of pseudo spectral variance estimator denoted by $\tilde{\Sigma}$ which uses data centered around the unobserved actual mean $\mu$.
+Such pseudo covariance estimator and autocovariance estimator for the $j^{th}$ chain is denoted by $\tilde{\Sigma}_s$ and $\tilde{\Gamma}_s$ respectively.
+
+\begin{align*}
+    \tilde{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)(X_{s(t+k)}-\mu)^T \\ 
+    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Gamma}_s(k) \,.
+\end{align*}
+%
+The average pseudo spectral variance estimator (APSVE) is given by
+\[
+\tilde{\Sigma} = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
+\]
+
+Further, let
+\begin{align*}
+  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[ \left(X_{st}-\mu \right)_i   \left(\mu-\bar{\bar{X}} \right)_j +    \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right]\right\}\,, \\
+  %
+M_2 &= \left(\mu-\bar{\bar{X}} \right)_i   \left(\mu-\bar{\bar{X}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\,.
+\end{align*}
 \begin{lemma} \label{lemma:rsv_breakdown}
-    The RSV estimator can be written as the sum of average pseudo SVE and two terms given by:
-    \[
-    \hat{\Sigma}_{RSV}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2\,,
+For the RSV estimator $\hat{\Sigma}_{RSV}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2$ and 
+\[
+|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,
 \]
@@
 \begin{align*}
-  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[ \left(X_{st}-\mu \right)_i   \left(\mu-\bar{\bar{X}} \right)_j +    \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right]\right\}\,, \\
-  %
-M_2 &= \left(\mu-\bar{\bar{X}} \right)_i   \left(\mu-\bar{\bar{X}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\,.
+    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
+    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
 \end{align*}
@@
 & \quad + \left. \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(\mu-\bar{\bar{X}}  \right)_j  \right]\\
-& = \tilde{\Sigma}^{ij} + \left[(\mu-\bar{\bar{X}})_i(\mu-\bar{\bar{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\right] \\ 
+& = \tilde{\Sigma}^{ij} + \left[(\mu-\bar{\bar{X}})_i(\mu-\bar{\bar{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] \\ 
 & \quad  + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}  \left[\dfrac{1}{n} \left(X_{st} - \mu \right)_i \left(\mu - \bar{\bar{X}} \right)_j + \dfrac{1}{n} \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right] \\
@@
 \end{align*}
-%
-% Therefore we get the following two terms:\\\\
-% Term (1): $\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\left[\dfrac{1}{n}\left((X_{st}-\mu)_i(\mu-\bar{\bar{X}})_j\right)+ \dfrac{1}{n}\left((\mu-\bar{\bar{X}})_i(X_{s(t+k)}-\mu)_j\right) \right]\right\}$\\
-% Term (2): $(\mu-\bar{\bar{X}})_i(\mu-\bar{\bar{X}})_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)$\\
-% \\\\
-\end{proof}
-
-\begin{lemma} \label{lemma:pseudo_consis}
-If the Assumption \ref{ass:sip}, \ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n}\to 0$, then $\tilde{\Sigma}^{ij} \xrightarrow{a.s.} \Sigma^{ij} \textrm{ as } n \to \infty$
-\end{lemma}
-
-\begin{proof}
-We have,
-\begin{align*}
-    &\tilde{\Sigma}^{ij} \\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t+|k|)} - \mu \right)_j\\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} \pm \bar{X}_s - \mu \right)_i  \left(X_{s(t+|k|)} \pm \bar{X}_s - \mu \right)_j\\
-    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i   \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
-    & \quad + \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\\
-    & = \hat{\Sigma}_{SV}^{ij} + N_1 + N_2 \,,
-\end{align*}
-where
-\begin{align*}
-N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
-N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\,.
-\end{align*}
-% Let Term (1*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum\limits_{t=1}^{n-|k|}\left[(X_{st} - \bar{X}_s)_i(\bar{X}_s - \mu)_j + (\bar{X}_s - \mu)_i(X_{s(t+k)} - \bar{X}_s)_j\right]$
-% Let Term (2*) be $\dfrac{1}{m}\sum\limits_{s=1}^{m}(\bar{X}_s - \mu)_i(\bar{X}_s - \mu)_j\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)$
-% \\\\
-We will prove that $N_1, N_2\xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
-From \cite{vats:fleg:jon:2018}, we have that $\hat{\Sigma}_{SV} \to 0$ with probability 1 as $n \to \infty$ for multivariate case.
-Assuming that all the assumptions made there hold true for our case, we will prove that $\tilde{\Sigma} \to 0$ with probability 1 as $n \to \infty$.
-
-Firstly, we prove that  $N_1 \xrightarrow{a.s.} 0$ as $n \to \infty$.
-We will prove this for the first part of $N_1$.
-It will hold true equivalently for the second part as well.
-The first part of the $N_1$ is,
-
-\begin{align*}
-    & \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right]\\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{  \left(\bar{X}_s - \mu \right)_j}{n} \left[\sum\limits_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i\right]\\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{k}{b_n}\right) \dfrac{\left(\bar{X}_s - \mu \right)_j}{n} \left[\sum_{t=1}^{|k|} \left(\mu - X_{st} \right)_i + \abs{k} \left(\bar{X}_s - \mu \right)_i\right]\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right) + \abs{k} \left(\bar{X}_s - \mu \right)\right\|_{\infty}\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left(\left\|\sum_{t=1}^{|k|}  \left(X_{st} - \mu \right)\right\|_{\infty} + \abs{k}\|\bar{X}_s - \mu\|_{\infty} \right)\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n}\left\|\sum_{t=1}^{|k|} \left(\bar{X}_s - \mu\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{X}_s - \mu \right \|_{\infty}^2\,.
-\end{align*}
-
-Using SIP on the summation of k terms,
-\begin{align*}
-    & \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right]\\
-   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2\\
-   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
-\end{align*}
-
-Using Lemma~\ref{lemma:consis_1}, the above term can be upper bounded by,
-
-\begin{equation} \label{eq:PASVE_term-1}
-  \left(2b_n - 1 + \dfrac{b_n^2}{n} + \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  
-\end{equation}
-\\
-Using the bound on $\psi(n)$ given by \cite{stra:1964}, (\ref{eq:PASVE_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
-\\
-Similar to the above proof, second part of $N_1$ can also be written as a summation of $k$ terms and the proof follows exactly as the first part.
-Now we prove that $N_2 \xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
-
-\begin{align*}
-    &\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu \right)_i \left(\bar{X}_s - \mu \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right)\\
-    & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
-    & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
-    & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
-\end{align*}
-Recall that the lag window is such that $\int_{-\infty}^{\infty} \abs{w(x)}dx = C$ for some constant C. Using Lemma~\ref{lemma:consis_1}, $N_2$ can be upper bounded by
-%
-\begin{equation} \label{eq:PASVE_term-2}
-    Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2 
-\end{equation}
-%
-\eqref{eq:PASVE_term-2} is also $\mathcal{O}\left(n^{-1}{b_n \log \log n}\right)$, and hence converges to 0 as $n \to \infty$.
-\end{proof}
-
-\begin{proof}[Proof of theorem \ref{th:consistency}]
-We first show that $M_1\xrightarrow{a.s} 0$ as $n \to \infty$ with the help of SIP and prior assumptions.
-\begin{align*}
-& M_1 \\ 
+
+Consequently
+\[
+\left|\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
+\]
+Consider,
+\begin{align*}
+& |M_1| \\ 
    & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\
@@
 \\
-Using SIP on summation of $k$ terms, we obtain the following upper bound for $M_1$
-\begin{align*}
-M_1
+Using SIP on summation of $k$ terms, we obtain the following upper bound for $|M_1|$
+\begin{align*}
+|M_1|
     & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \\
@@
 \begin{align*}
-   M_2 & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu - \bar{\bar{X}} \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\right\}\right|\\
-    & \leq\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{n}\right)\right]\\
-    &< \|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{n}\right)\right|\right]\\
-    &= b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{n}\right)\right|\right]\\
+   |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu - \bar{\bar{X}} \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
+    & \leq\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right]\\
+    &< \|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+    &= b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
     & \leq b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w(x)|dx \\
@@
 %
-Equation~\eqref{eq:strong_consis_term-2} has the same order as equation \eqref{eq:strong_consis_term-1}, i.e. $\mathcal{O}\left(b_n \log \log n/n\right) \to 0 \textrm{ as } n \to \infty$.
-We have already shown that $M_1$ and $M_2$ converge to 0 almost surely $\implies \hat{\Sigma}_{RSV} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$.
+% Equation~\eqref{eq:strong_consis_term-2} has the same order as equation \eqref{eq:strong_consis_term-1}, i.e. $\mathcal{O}\left(b_n \log \log n/n\right) \to 0 \textrm{ as } n \to \infty$.
+% We have already shown that $M_1$ and $M_2$ converge to 0 almost surely $\implies \hat{\Sigma}_{RSV} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$.
 Now we can find the functions $g_1(n), g_2(n) \textrm{ and, } g_3(n)$ by adding \eqref{eq:strong_consis_term-1} and \eqref{eq:strong_consis_term-2}.
@@
 %
+{\color{red} Complete the algebra here}
 \begin{align*}
@@
     g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0
-\end{align*}
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
+\end{align*}
+\end{proof}
+% \begin{lemma} \label{lemma:pseudo_consis}
+% If the Assumption \ref{ass:sip}, \ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n}\to 0$, then $\tilde{\Sigma}^{ij} \xrightarrow{a.s.} \Sigma^{ij} \textrm{ as } n \to \infty$
+% \end{lemma}
+%
+\begin{proof}[Proof of theorem \ref{th:consistency}]
+We have the following decomposition,
+\begin{align*}
+    &\tilde{\Sigma}^{ij} \\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t + k)} - \mu \right)_j\\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} \pm \bar{X}_s - \mu \right)_i  \left(X_{s(t + k)} \pm \bar{X}_s - \mu \right)_j\\
+    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i   \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
+    & \quad + \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\\
+    & = \hat{\Sigma}_{SV}^{ij} + N_1 + N_2 \,,
+\end{align*}
+where
+\begin{align*}
+N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
+N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\,.
+\end{align*}
+%
+Using the above and  Lemma~\ref{lemma:rsv_breakdown}, 
+\begin{align*}
+\left|\hat{\Sigma}_{RSV}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right| \\
+& \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right|
+\end{align*}
+%
+By Assumption~\ref{ass:sve_consis}, the first term goes to with probability 1 and by Lemma~\ref{lemma:rsv_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
+What is left to show is that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1
+%
+\begin{align*}
+|N_1| & = \left|\dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right] \right|\\
+& \leq \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right| \\
+& \quad + \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right] \right|
+\end{align*}
+%
+Both terms are similar and we will show that the first term goes to 0. The proof for the second term is similar. Consider
+\begin{align*}
+    & \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right| \\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left| w\left(\dfrac{k}{b_n}\right) \right| \dfrac{ \left|  \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right)_i \right| + \abs{k} \left|\left(\bar{X}_s - \mu \right)_i \right|\right]\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right) + \abs{k} \left(\bar{X}_s - \mu \right)\right\|_{\infty}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left(\left\|\sum_{t=1}^{|k|}  \left(X_{st} - \mu \right)\right\|_{\infty} + \abs{k}\|\bar{X}_s - \mu\|_{\infty} \right)\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(X_{st} - \mu\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{X}_s - \mu \right \|_{\infty}^2\,.
+\end{align*}
+
+Using SIP on the summation of k terms,
+\begin{align*}
+    & \left|\dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right|\\
+   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2\\
+   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
+\end{align*}
+
+Using Lemma~\ref{lemma:consis_1}, the above term can be upper bounded by,
+
+\begin{equation} \label{eq:PASVE_term-1}
+  \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2\,.  
+\end{equation}
+%
+Using the bound on $\psi(n)$ given by \cite{stra:1964}, (\ref{eq:PASVE_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
+
+Similar to the above proof, second part of $N_1$ can also be written as a summation of $k$ terms and the proof follows exactly as the first part.
+Now we prove that $N_2 \xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
+{\color{red} Remove the following proof maybe because repetitive}
+%
+\begin{align*}
+    |N_2|&= \left|\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu \right)_i \left(\bar{X}_s - \mu \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right|\\
+    & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
+\end{align*}
+Recall that the lag window is such that $\int_{-\infty}^{\infty} \abs{w(x)}dx = C$ for some constant C. Using Lemma~\ref{lemma:consis_1}, $N_2$ can be upper bounded by
+%
+\begin{equation} \label{eq:PASVE_term-2}
+    Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2 
+\end{equation}
+%
+\eqref{eq:PASVE_term-2} is also $\mathcal{O}\left({b_n \log \log n}/n\right)$, and hence converges to 0 as $n \to \infty$.
 \end{proof}

### 2020-06-24 Paper/main.tex
Cleaned the appendix!

@@
 To compare the estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
-We succesfully show in section \ref{ex:var} that our estimators yield better results as compared to the classical sample ACF and SVE.
+We successfully show in section \ref{ex:var} that our estimators yield better results as compared to the classical sample ACF and SVE.
 A more promising advantage of our estimators is observed when the target distribution is multi-modal.
@@
 
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[h]{0.4\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{scatter_plot_500.pdf}
-         \caption{$n = 500$}
-         \label{subfig:var-sp_500}
-     \end{subfigure}
-     \begin{subfigure}[h]{0.4\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{scatter_plot_50000.pdf}
-         \caption{$n = 5 \times 10^4$}
-         \label{subfig:var-sp_50000}
-     \end{subfigure}
-    \caption{Scatter plot of five Markov chains for different sample sizes.}
-    \label{fig:var-sp}
-\end{figure}
+% \begin{figure}[h]
+%     \centering
+%     \begin{subfigure}[h]{0.4\textwidth}
+%          \centering
+%          \includegraphics[width=\textwidth]{plots/scatter_plot_500.pdf}
+%          \caption{$n = 500$}
+%          \label{subfig:var-sp_500}
+%      \end{subfigure}
+%      \begin{subfigure}[h]{0.4\textwidth}
+%          \centering
+%          \includegraphics[width=\textwidth]{plots/scatter_plot_50000.pdf}
+%          \caption{$n = 5 \times 10^4$}
+%          \label{subfig:var-sp_50000}
+%      \end{subfigure}
+%     \caption{Scatter plot of five Markov chains for different sample sizes.}
+%     \label{fig:var-sp}
+% \end{figure}
 
@@
 
-\begin{lemma} \label{lemma:consis_1}
-  If Assumption~\ref{ass:sip} holds, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
-  \end{lemma}
-
-\begin{proof}
-Let $\|.\|$ denote the Euclidean norm.
+% \begin{lemma} \label{lemma:consis_1}
+%   If Assumption~\ref{ass:sip} holds, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
+%   \end{lemma}
+
+% \begin{proof}
+% Let $\|.\|$ denote the Euclidean norm.
 Assumption \ref{ass:sip} allows us to upper bound $\|\bar{X}_s - \mu\|_{\infty}$ using SIP.
 Following that, we show that the upper bound term converges to 0 as $n \to \infty$ using lemma \ref{lemma: brownian}.
- \begin{align*}
-    \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| \\
-    &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| = \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
-    & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
-    &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
-    &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
-    & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\\
-    & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty
- \end{align*}
-%
-Similarly one can easily show that $\|\bar{\bar{X}} - \mu\|_{\infty} \to 0$ as $n \to \infty$ using the same upper-bound as:
-% 
-\begin{align*}
-    \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as } n \to \infty
-\end{align*}
-\end{proof}
+%  \begin{align*}
+%     \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| \\
+%     &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| = \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
+%     & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
+%     &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
+%     &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
+%     & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\\
+%     & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty
+%  \end{align*}
+% %
+% Similarly one can easily show that $\|\bar{\bar{X}} - \mu\|_{\infty} \to 0$ as $n \to \infty$ using the same upper-bound as:
+% % 
+% \begin{align*}
+%     \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as } n \to \infty
+% \end{align*}
+% \end{proof}
 
@@
 \label{eq:acf_3}
-    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right] \right)^T\,.
+    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
     % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
@@
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - {\color{red}\dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma(h) - n \Var(\bar{X}_1)\right)} + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\,.
-\end{align*}
-{\color{red} DV: Instead of the ``2'', should it be something that has $\Gamma(h) + \Gamma(h)^T$?}
-
-% Using the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$,
-% \[
-% \mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})\,.
-% \]
-%
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - {\color{red}\dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right)} + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m}\,.
+\end{align*}
+%
+ We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{RAC,s}(k)$ can then broken down as following,
+ \begin{equation} \label{eq:rac_expec_breakdown}
+     \mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
+ \end{equation}
+%
+where,
+\begin{align*}
+    O_1 &= -\dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] \, ,\\
+    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
+\end{align*}
+%
+We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$.
+Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = \mathcal{O}(1/n)$.
+For a diagonal element of $\Gamma$,
 % We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
@@
 These are small order terms that vanish as $n \to \infty$.
-
-For a diagonal element of $\Gamma$,
+%
 \begin{align*}
 & \E \left[ \hat{\Gamma}_{RAC,s}^{ii}\right]\\
-& = \mathbb{E}\left[\hat{\Gamma}_{s}^{ii}(k)\right] - {\color{red}\dfrac{2|k|}{n}\dfrac{m-1}{mn}\left(\sum_{h=0}^{n-1}\Gamma^{ii}(h) - n \Var(\bar{X}_1)^{ii}\right)} + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)^{ii}\,.
+& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma^{ii}(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma^{ii}(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
 \end{align*}
@@
 \]
-Consider,
+%
+We first present a result which will be useful to use later. For any Markov chain $s$, 
+\begin{align*}
+  \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| = \dfrac{1}{mn}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| \\
+  &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
+  & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
+  &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
+  &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
+  & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\,. \numberthis \label{eq:xbars_bound}
+  % & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty 
+\end{align*}
+ %
+ Similarly,
+ \begin{equation}
+\label{eq:xbarbar_bound}
+   \| \bar{\bar{X}} - \mu\|_{\infty} \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\,.
+\end{equation}
+%  \begin{align*}
+%   \| \bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{n}\left\|\sum_{s=1}^{m} \left(\sum_{t=1}^{n}X_{st} - n\mu \right)\right\| \\
+%   &\leq \dfrac{1}{m}\sum_{s=1}^{m}\dfrac{1}{n}  \left \| \sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
+%   & \leq \dfrac{1}{m} \sum_{s=1}^{m} \dfrac{1}{n}\left\| \sum_{t=1}^{n}X_{st} - n \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
+%   &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
+%   &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
+%   & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\,. \numberthis \label{eq:xbarbar_bound}
+%   % & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty 
+% \end{align*}
+%
+Now consider,
 \begin{align*}
@@
     & \leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \left\|\sum_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} \right]\\
-    & \; \;+ 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty} 
-\end{align*}
-\\
+    & \; \;+ 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\,.
+\end{align*}
+%
 Using SIP on summation of $k$ terms, we obtain the following upper bound for $|M_1|$
@@
     &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]\\
-    & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\,.
-\end{align*}
-%
-We use Lemma~\ref{lemma:consis_1} to upper bound the above term as
-\begin{equation} \label{eq:strong_consis_term-1}
-    4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2
-\end{equation}
-\\
-Using the bound on $\psi(n)$ given by \cite{stra:1964}, equation (\ref{eq:strong_consis_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
+    & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\\
+    & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,.
+\numberthis \label{eq:strong_consis_term-1}
+\end{align*}
+%
+ %
+% We use Lemma~\ref{lemma:consis_1} to upper bound the above term as
+% \begin{equation} \label{eq:strong_consis_term-1}
+%     4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2
+% \end{equation}
+%
+% Using the bound on $\psi(n)$ given by \cite{stra:1964}, equation (\ref{eq:strong_consis_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
 Now we will show that $M_2 \xrightarrow{a.s.} 0$ as $n\to \infty$
-
+For $M_2$,
 \begin{align*}
@@
     & \leq b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w(x)|dx \\
-    & \leq Cb_n\|\bar{\bar{X}} - \mu \|^2
-\end{align*}
-
-Using Lemma~\ref{lemma:consis_1} to upper bound the above term as
-
-\begin{equation} \label{eq:strong_consis_term-2}
-     Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2
-\end{equation}
+    % & \leq Cb_n\|\bar{\bar{X}} - \mu \|^2 \\ 
+    & \leq Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 \quad \text{ (by \eqref{eq:xbarbar_bound})} \numberthis \label{eq:strong_consis_term-2} \,.
+\end{align*}
+%
+% Using Lemma~\ref{lemma:consis_1} to upper bound the above term as 
+%
+% \begin{equation} \label{eq:strong_consis_term-2}
+%      Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2
+% \end{equation}
 %
@@
 %
-{\color{red} Complete the algebra here}
-\begin{align*}
-    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
-\end{align*}
+Using \eqref{eq:strong_consis_term-1} and \eqref{eq:strong_consis_term-2},
+\begin{align*}
+  &|M_1 + M_2|\\
+  & \leq |M_1| + |M_2|\\
+  & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 + Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2\\
+  & = D^2g_1(n) + D g_2(n) + g_3(n)\,
+\end{align*}
+where
+\begin{align*}
+    g_1(n) &= (8 + C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
+    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(8 + C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(8 + C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]\,.
+\end{align*}
+Under our assumptions, $b_n\log \log n /n \to 0$ and $\psi(n) = o(\sqrt{n \log \log n})$.
+Consequently, $b_n \psi^2(n)/n^2 \to 0$, $\psi^2(n)/n^2 \to 0$, ${b_n\psi(n)\sqrt{n\log \log n}/n^2} \to 0$, and $\psi(n) \sqrt{n \log \log n}/n^2 \to 0$.
+Thus, $g_1(n), g_2(n)$ and $g_3(n) \to 0$ as $n \to \infty$.
+
 \end{proof}
@@
 \left|\hat{\Sigma}_{RSV}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right| \\
-& \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right|
+& \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:RSV_full_decomp}
 \end{align*}
@@
    &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2\\
-   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2
-\end{align*}
-
-Using Lemma~\ref{lemma:consis_1}, the above term can be upper bounded by,
-
-\begin{equation} \label{eq:PASVE_term-1}
-  \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2\,.  
-\end{equation}
-%
-Using the bound on $\psi(n)$ given by \cite{stra:1964}, (\ref{eq:PASVE_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
-
+   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2 \\
+   &  \leq   \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2 \quad \text{(by \eqref{eq:xbars_bound})} \\
+   & \to 0\,.
+\end{align*}
+%
+% Using Lemma~\ref{lemma:consis_1}, the above term can be upper bounded by,
+% 
+% \begin{equation} \label{eq:PASVE_term-1}
+%   \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2\,.  
+% \end{equation}
+%
+% Using the bound on $\psi(n)$ given by \cite{stra:1964}, (\ref{eq:PASVE_term-1}) becomes $\mathcal{O}\left(b_n \log \log n/n\right)$ which converges to 0 as $n \to \infty$.
+%
 Similar to the above proof, second part of $N_1$ can also be written as a summation of $k$ terms and the proof follows exactly as the first part.
 Now we prove that $N_2 \xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
-{\color{red} Remove the following proof maybe because repetitive}
-%
-\begin{align*}
-    |N_2|&= \left|\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu \right)_i \left(\bar{X}_s - \mu \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right|\\
-    & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
-    & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
-    & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
-\end{align*}
-Recall that the lag window is such that $\int_{-\infty}^{\infty} \abs{w(x)}dx = C$ for some constant C. Using Lemma~\ref{lemma:consis_1}, $N_2$ can be upper bounded by
-%
-\begin{equation} \label{eq:PASVE_term-2}
-    Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2 
-\end{equation}
-%
-\eqref{eq:PASVE_term-2} is also $\mathcal{O}\left({b_n \log \log n}/n\right)$, and hence converges to 0 as $n \to \infty$.
+%
+Following the steps in \eqref{eq:strong_consis_term-2}, we get
+\begin{align*}
+    |N_2| & \leq Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
+    % \left|\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu \right)_i \left(\bar{X}_s - \mu \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right|\\
+    % & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    % & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    % & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
+\end{align*}
+Thus, in \eqref{eq:RSV_full_decomp}, each of the terms goes to 0 with probability 1, and $\hat{\Sigma}_{RSV}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. 
 \end{proof}
@@
 We are interested in finding the asymptotic bias here.
-Therefore we can write the expection of replicated autocovariance as
-\begin{equation} \label{eq:rac_bias2}
-\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + \left(1 - \dfrac{\abs{k}}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)    \,.
+Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:rac_expec_breakdown} as,
+\begin{align*}
+&\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right]\\
+&  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
+& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:rac_bias2}  \,.
+\end{align*}
+%
+% \begin{equation} \label{eq:rac_bias2}
+% \mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
+% \end{equation}
+%
+where both $O_1 \textrm{ and } O_2$ are the small order terms.
+By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.
+Consider the RSV estimator,
+\begin{align*}
+    &\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right]\\
+    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\
+    & = P_1 + o \left( \dfrac{1}{n} \right)\,
+\end{align*}
+%
+where 
+\begin{align*}
+P_1 & = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
+% P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
+\end{align*}
+%
+We first solve for term $P_1$ by breaking it into three parts as in \cite{hannan2009multiple}.
+Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for each element of the matrix $A$.
+Consider,
+\begin{equation}
+\label{eq:P1_decomp}
+P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
 \end{equation}
-
-Since $w\left(\dfrac{k}{b_n}\right) = 0$ for $|k| > b_n$. 
-The last term in \eqref{eq:rac_bias2} is stated separately because it does not depend on $k$. 
-\begin{align*}
-    &\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right]\\
-    &= \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\left[\left(\Gamma(k) + \mathcal{O}\left(\dfrac{1}{n}\right)\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    & \quad + \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \\ 
-    & = O_1 + O_2\,,
-\end{align*}
-%
-where 
-\begin{align*}
-O_1 & = \sum\limits_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right\} - \sum\limits_{k=-\infty}^{\infty}\Gamma(k) \\ 
-O_2 &= \sum\limits_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right)\right] \right\}\,.
-\end{align*}
-
-\begin{enumerate}
-\item We first solve for term $O_1$ by breaking it into three parts as in \cite{hannan2009multiple}.
-\[
--\sum_{|k|\geq n}\Gamma(k) + \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)
-\]
-%
-We deal with the three subterms of term \textbf{A} individually,
-\begin{enumerate}
-    \item 
-    \begin{align*}
-        \left\|{-\sum_{|k|\geq n}\Gamma(k)}\right\| &\leq   \abs{\dfrac{k}{n}}^q\sum_{|k|\geq n}\|\Gamma(k)\| = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q\underbrace{\sum_{|k|\geq n}|k|^q\|\Gamma(k)\|}_{<\infty} = o\left(\dfrac{1}{b_n^q}\right)
-    \end{align*}
-
-    \item
-\begin{align*}
-   \left\| \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)\right\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| 
-\end{align*}
-
-For $q \geq 1$, we have, $\sum_{k=-n+1}^{n-1}|k|^q\|\Gamma(k)\| < \infty$
-   \begin{align*}
-       \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|\|\Gamma(k)\| &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\| = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k = -n+1}^{n-1}|k|^q\|\Gamma(k)\| = o\left(\dfrac{1}{b_n^q}\right)
-   \end{align*}
-
-For $q <1$:
-   \begin{align*}
-       c\sum_{k =-n+1}^{n-1}\dfrac{|k|}{n}\|\Gamma(k)\| &\leq c\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q\|\Gamma(k)\| = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n}c\sum_{k =-n+1}^{n-1}|k|^q\|\Gamma(k)\| = o\left(\dfrac{1}{b_n^q}\right)
-   \end{align*}
-
-  \item Next,
-     \[
-     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k)\,.
-     \]
-%     
-     The condition 
-     \[
-     \lim_{\abs{x}\to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty
-     \]
-     implies that $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$; where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
-     \[
-     \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
-     \]
-\end{enumerate}
-
- \item Solving for $O_2$. We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
- \begin{align*}
-     & \sum_{k=-n+1}^{n-1}\left\{w\left(\dfrac{|k|}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\mathcal{O}\left(\dfrac{1}{n}\right) + \mathcal{O}\left(\dfrac{1}{n}\right) \right] \right\} \\
-     &\leq \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\mathcal{O}\left(\dfrac{1}{n}\right)\\
-     &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right) \\
-     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
-     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
- \end{align*}
- \end{enumerate}  
-%
- We have shown that all, but one, terms are $o(1/b_n^q)$.
+%
+We deal with the three subterms of term $P_1$ individually. First,
+%    
+\begin{align*}
+ {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
+\end{align*}
+%
+since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
+%
+\begin{align*}
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
+\end{align*}
+For $q\geq 1$,
+\begin{align*}
+\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
+\end{align*}
+
+For $q <1$,
+\begin{align*}
+   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
+\end{align*}
+So,
+\begin{equation}
+\label{eq:P1_second}
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
+\end{equation}
+Lastly, by our assumptions, for $x \to 0$
+\[
+\dfrac{1 - w(x)}{\abs{x}^q} = k_q + o(1)\,.
+\]
+For $x = k/b_n$, $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$.
+ % where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
+     % \[
+     % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
+     % \]
+So,
+\begin{align*}
+     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
+     & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
+     & = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right) \numberthis \label{eq:P1_third}\,.
+\end{align*}
+%
+ % Finally, we will solve for $P_2$.
+Note that $O_2$ is independent of $k$.
+We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$.
+We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
+ % \begin{align*}
+ %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
+ %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
+ %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
+ %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
+ %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
+ % \end{align*}
+  %
+%
+Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
+\[
+\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
+\]
+which completes the result.
+%
+ % We have shown that all, but one, terms are $o(1/b_n^q)$.
 Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{RAC} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
@@
 \label{appendix:variance}
-\textbf{Theorem } \ref{th:rsv_variance}
-\begin{proof}
+
+\begin{proof}[Proof of Theorem~\ref{th:rsv_variance}]
  Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
@@
 \end{align*}
-
+%
 We have shown from the proof of strong consistency that,

### 2020-07-16 SensorNetwork/output.R
Plots for 5e5

@@ -43,7 +43,7 @@ Ys <- matrix(c(0, 0, 0, 0.9266,
                0.9266, 0.8524, 0, 0), ncol = 4)
 
 
-m <- 2
+m <- 5
 start <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
 aux <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
 j.scale <- rep(1,.08, 4)
@@ -58,12 +58,12 @@ r <- length(check.pts)
 freq <- 1e2
 c.prob <- .95
 min <- 500
-max <- 2e5
+max <- 5e5
 step <- 500
 conv.pts <- seq(min, max, step)
 
 ## 1.) Running plots
-
+p <- 8
 load(file = paste("Out/conv_data_m", m, "_min", min, "_max", max, ".Rdata", sep = ""))
 
 for (k in 1:p){
@@ -73,6 +73,12 @@ for (k in 1:p){
   legend("topright", legend=c("ASV", "RSV"),col=c("red", "blue"), lty=1, cex=.75)
   dev.off()
 }
+
+  pdf(file = paste("Out/run_plots-Frob.pdf", sep = ""))
+  plot(apply(asv[[1]], 3, norm, "F"), type = "l", col = "red", main = paste("Frobenius Norm"), xlab = "Simulation size", ylab = "Variance", ylim = range(apply(asv[[1]], 3, norm, "F"), apply(rsv[[1]], 3, norm, "F")) )
+  lines(apply(rsv[[1]], 3, norm, "F"), col="blue")
+  legend("topright", legend=c("ASV", "RSV"),col=c("red", "blue"), lty=1, cex=.75)
+  dev.off()
 #### 1c.) Determinant
 pdf(file = paste(paste("Out/run_plots_det", sep = "_"), ".pdf", sep = ""), height = 3)
 
@@ -80,8 +86,8 @@ det.rsv <- rep(0,length(conv.pts))
 det.asv <- rep(0,length(conv.pts))
 
 for (i in 1:length(conv.pts)){
-  det.rsv[i] <- (det(rsv[[1]][,,i]))
-  det.asv[i] <- (det(asv[[1]][,,i]))
+  det.rsv[i] <- (det(rsv[[1]][,,i]))^(1/p)
+  det.asv[i] <- (det(asv[[1]][,,i]))^(1/p)
 }
 
[…]

### 2020-07-16 SensorNetwork/simulations.R

@@ -161,7 +161,7 @@ convergence <- function(min, max, start, aux, j.scale, Ob, Os, Xb, Xs, Yb, Ys, m
     ess.asv[[r]] <- ess.asv.samp
     ess.rsv[[r]] <- ess.rsv.samp
     
-    save(master.chain, asv, rsv, ess.asv, ess.rsv, 
+    save(asv, rsv, ess.asv, ess.rsv, 
     file = paste("Out/conv_data_m", m, "_min", min, "_max", max, ".Rdata", sep = "")) 
   }
   
@@ -176,7 +176,7 @@ start2 <- c(0.0, 0.6, 0.1, 0.1, 0.2, 0.2, 1.0, 0.0)
 aux2 <- runif(n=8, min=min(start2), max=max(start2))
 start3 <- c(0.2, 0.7, 0.5, 0.4, 0.5, 0.3, 0.5, 0.5)
 aux3 <- runif(n=8, min=min(start3), max=max(start3))
-start4 <- c(0.4, 0.8, 0.8, 0.6, 0.co7, 0.4, 1.0, 1.0)
+start4 <- c(0.4, 0.8, 0.8, 0.6, 0.7, 0.4, 1.0, 1.0)
 aux4 <- runif(n=8, min=min(start4), max=max(start4))
 start5 <- c(0.7, 1.0, 1.2, 0.9, 0.9, 0.5, 1.5, 1.5)
 aux5 <- runif(n=8, min=min(start5), max=max(start5))
@@ -192,12 +192,12 @@ freq <- 10
 rep <- 1
 c.prob <- .95
 min <- 500
-max <- 2e5
+max <- 5e5
 step <- 500
 conv.pts <- seq(min, max, step)
 
-print("Carrying out 1000 repititions for each value of nsim in check.pts")
-create.output(start, aux, j.scale, Ob, Os, Xb, Xs, Yb, Ys, m, check.pts, freq, truth)
+# print("Carrying out 1000 repititions for each value of nsim in check.pts")
+# create.output(start, aux, j.scale, Ob, Os, Xb, Xs, Yb, Ys, m, check.pts, freq, truth)
 
 print("Carrying out simulations for convergence plots of ASV and RSV in the range(1e3, 1e5")
 

### 2020-07-18 Paper/main.tex
First push with ideas  on organization

@@
 
-\title{Estimating autocorrelation from multiple Markov chains}
+\title{Globally-centered autocovariances in MCMC}
 
@@
   \texttt{medhaaga@iitk.ac.in} \and
-  %% examples of more authors
  Dootika Vats \\
@@
 \begin{abstract}
-    This is best abstract in the world.\\.\\.\\.\\.\\.
+Autocovariances are the fundamental quantity in many features of Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain.
+Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth.
+For multiple chain MCMC sampling,  we propose a globally-centered estimate of the autocovariance that pools information from all Markov chains.
+We show the impact of these improved estimators in three aspects: (1) acf plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
 \end{abstract}
 
+{\color{blue} Main things to change
+\begin{itemize}
+  \item I don't want to call this ``Replicated autocovariance'' or ``Replicated spectral variance''.
+I think ``Globally-centered autocovariance'' is more appropriate and self-explanatory.
+So we will have to go over the whole document and change this.
+
+\end{itemize}
+
+A rough outline of the organization
+\begin{enumerate}
+  \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.
+
+  \item Globally-centered autocovariance
+    \begin{itemize}
+      \item Theoretical soundness
+    \end{itemize}
+
+  \item Variance of Monte Carlo averages
+
+    Describe MC averages and CLT
+    \begin{itemize}
+      \item Globally-centered Spectral variance estimators
+      \begin{itemize}
+        \item Theoretical results
+        \item Computational gains
+      \end{itemize}
+      \item Explore: Charlie's initial sequence estimators
+    \end{itemize}
+
+  \item Effective sample size
+
+  \item Examples
+
+  \item Appendix
+    \begin{itemize}
+      \item Proofs
+      \item ACF plots for other examples.
+    \end{itemize}
+
+\end{enumerate}
+}
 \section{Introduction} \label{sec:intro}
@@
 \end{example}
-\section{Replicated Autocovariance Function} \label{sec:R-ACF}
+\section{Globally-centered autocovariance} \label{sec:R-ACF}
 
@@
 
+\begin{comment}
 \begin{figure}[h]
@@
 \end{figure}
-
+\end{comment}
+
+\begin{comment}
 \begin{figure}[h]
@@
 \end{figure}
+\end{comment}
 
@@
     \centering
-    \begin{subfigure}[h]{.7\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-acf,n=1000.pdf}
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf,n=1000.pdf}
       \caption{$n = 1000$}
@@
     \end{subfigure}
-    \begin{subfigure}[h]{.7\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-acf,n=50000.pdf}
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf,n=50000.pdf}
       \caption{$n = 50000$}
@@
     \end{subfigure}
-    \caption{ACF and R-ACF for component-1 of chain-1 at two different sample sizes. }
+    \caption{ACF and R-ACF for component-1 of chain-1 at two different number of Monte Carlo samples. }
     \label{fig:boom-acf}
@@
 \end{table}
+
+\subsection{Sensor Network Localization}
+
+For our third example, we consider a real-life problem of sensor locations previously discussed by \cite{ihler2005nonparametric}.
+The goal is to identify unknown sensor locations using noisy distance data.
+This problem is specifically interesting in our case because the joint posterior distribution for missing sensor locations is multi-modal.
+\\
+
+\cite{tak2018repelling} modified the simulation settings of \cite{lan2014wormhole} to include only six sensor locations (four unknown and two unknown) out of eleven locations (eight known and three unknown).
+Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor.
+Let $y_{ij} = (y_{ji})$ denote the distance between the sensors $x_i$ and $x_j$.
+The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$.
+Let $z{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed.
+The probability model is then,
+
+\begin{align*}
+    z_{ij}|x_1, ..., x_6 &\sim Bernoulli\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
+    y_{ij}| w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
+\end{align*}
+
+\cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$.
+We use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$.
+$y_{ij}$ is specified only if $w_{ij} = 1$.
+The likelihood function is then,
+
+\begin{multline*}
+    L(x_1, x_2, x_3, x_4) \propto \\
+\prod_{j>i} \left[ \left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{w_{ij}} \left(1 - \exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{1 - w_{ij}} \exp \left(-\dfrac{y_{ij} - \|x_i - x_j\|^2}{2 \times 0.02^2}\right)\right]
+\end{multline*}
+
+The full posterior distribution with Gaussian prior is given by,
+\begin{equation} \label{ex:sensor_post}
+    \pi (x_1, x_2, x_3, x_4 | y, w) \propto 
+    L(x_1, x_2, x_3, x_4) \times \exp \left(- \dfrac{\sum_{i = 1}^{4} x_i^Tx_i}{2 \times 0.02^2}\right) 
+\end{equation}
+
+where $y = (y_{ij}, j>i)$ and $w = (w_{ij}, j>i)$.
+We follow the Markov chain structure as described by \cite{tak2018repelling} and sample from the four bivariate conditionals for each sensor location using a Gibbs sampler.
+In their paper on Repelling Attractive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of three different sampling techniques namely - Metropolis, RAM and Tempered Transitions (TT).
+RAM is shown to improve the acceptance rate by a factor of at least 5.5 over Metropolis using the same jumping scale.
+RAM algorithm supplies Markov chains with higher jumping frequency between the modes of a multimodal target distribution.\\
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = .7\textwidth]{plots/sensor-trace.pdf}
+    \caption{Trace plots for the x-component of all four locations of the third chain.}
+    \label{fig:sensor-trace-3}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth, height = 2in]{plots/sensor-acf-n1000.pdf}
+      \caption{$n = 10^3$}
+      \label{subfig:sensor-acf_n1e3}
+    \end{subfigure}
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth, height = 2in]{plots/sensor-acf-n1e5.pdf}
+      \caption{$n = 10^5$}
+      \label{subfig:sensor-acf_n1e5}
+    \end{subfigure}
+    \caption{ACF and R-ACF for component-3 of chain-3 at two different number of Monte Carlo samples. }
+    \label{fig:sensor-acf}
+\end{figure}
+
+We will use the RAM algorithm with a jumping scale equal to $0.5$ to sample five parallel Markov chains with well-separated starting points.
+The total simulation size for each chain is fixed at $100,000$.
+Figure \ref{fig:sensor-trace-3} demonstrates the trace plots of the first chain for the x-component of all four unknown locations.
+We observe the bi-modal nature of the marginal distribution for each component.
+The Markov chains get stuck at a particular mode for a long time before jumping to the other mode.
+Figure \ref{fig:sensor-acf} shows the effect of this "sticky" nature of Markov chains over the autocorrelations centered around the local and global mean.
+For a small sample size of 1000, it can be seen that the third chain has not explored the sample space well.
+As a consequence, the local mean differs a lot from the global mean (averaged over all five chains).
 
@@
     &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\inf}\Gamma(k)\\
     &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\
@@
 
+\section{Additional Examples}
+We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.
+In this section we will use two real-life datsets to exemplify the better performance of our replicated autocovariance estimator for multiple Markov chains.
+R packages already exist to create Markov chains for these examples.
+However, when these chains are started from different points, we will observe that they do not represent the target distribution well for finite samples.
+The traditional empirical ACF estimator fails in these cases, whereas our estimator shows promising results.
+We will not engage into full error analysis for these examples due to computational restrictions posed by high dimensional sample space.
+\subsection{Bayesian Poisson Change Point Model}
+
+\cite{pollins1996global} theorizes a cyclical pattern in the number of international conflicts.
+Four core theories by \cite{gilpin1981war}, \cite{wallerstein1983three}, \cite{goldstein1988long}, and \cite{modelski1988seapower} put different weights on the role of global economic and political order in explaining this cyclical pattern.
+See \cite{martin2011mcmcpack} for detailed discussion on the effect of these theories on the cyclic behavior of international disputes.\\
+
+In this example, we will fit a Poisson change-point model on the annual number of military conflicts from the militarized interstate dispute (MID) data.
+We wish to detect the number and timings of the cyclic phases in the international conflicts.
+\cite{chib1998estimation} describes the Poisson change-point as a Markov mixture model where observations are assumed to be drawn from latent states.
+Following \cite{martin2011mcmcpack}, we will use \texttt{MCMCpoissonChange} from \texttt{MCMCpack} to fit the model which samples the latent states based on the algorithm in \cite{chib1998estimation}.
+The Poisson change-point model in \texttt{MCMCpoissonChange} uses conjugate priors and can be written as:
+
+\begin{align*}
+    y_t &\sim \textit{Poisson}(\lambda_i), \qquad i = 1, ..., k\\
+    \lambda_i &\sim \textit{Gamma}(c_o, d_o), \qquad i = 1,..., k\\
+    p_{ii} &\sim \textit{Beta}(\alpha, \beta), \qquad i = 1,..., k
+\end{align*}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 0.8\textwidth, height = 4in]{plots/spatio-acf.pdf}
+    \caption{ACF and R-ACF for first component of first chain.
+ACF underestimates the autocorrelations for $10^3$ samples (top) whereas R-ACF gives more realistic estimates.
+They perform alike for $10^5$ samples (bottom).}
+    \label{fig:spatio-acf_racfl}
+\end{figure}
+The results of model comparison by \cite{martin2011mcmcpack} showed that the ratio of maximum likelihood for six change-point model is favored over the alternatives.
+We will use this information and present the ACF results for a six change-points model only.
+We will use the hyperparameters values $c_o = 13 \textrm{ and } d_o = 1$ because the mean of MID is around 13.
+\\
+
+We run two parallel Markov chains starting from random poits.
+In Figure \ref{fig:spatio-acf_racfl}, it is evident that the chains have not explored the sample space well.
+Hence for $10^3$ samples ACF severely underestimates the autocorrelations whereas R-ACF gives more realistic estimates.
+For a large sample size of $10^5$, the Markov chains have mixed properly and therefore, both the estimators are approximately alike.
+
+\subsection{High School Social Network}
+
+\cite{handcock2008statnet} implemented an exponential-family random graph modelling (ERGM) on network data in the package \texttt{ergm}.
+The \texttt{faux.magnolia.high} dataset available in the package represents a simulated within school friendship network based on Ad-Health data (\cite{resnick1997protecting}).
+The school communities represented by the network data are located in the southern United States.
+Each node represents a student and each edge represents a friendship between the nodes it connects.
+\cite{nilakanta2019ensuring} modified the data by removing 1,022 out of 1,461 nodes to obtain a well-connected graph.
+This resulting social network has 439 nodes and 573 edges.\\
+
+Let $V$ denote the non-empty set of countable nodes, $E \subseteq V \times V$ denote the set of edges, and $G = (V,E)$ denote the network.
+We are interested in exploring all the nodes uniformly, i.e.
+sample from a uniform distribution over $V$.
+Let $\lambda$ denote a uniform distribution over $V$  let $h: V \to \mathbb{R}^p$ map each node to certain features of interest.
+If $X \sim \lambda$, we wish to calculate the expected value of $h(X)$ with respect to $\lambda$ given by
+
+\[
+\mathbb{E}[h(X)]_{\lambda} = \dfrac{1}{n}\sum_{x \in V}h(x).
+\]
+
+Here n is the set cardinality of $V$.
+We use a Metropolis-Hastings algorithm with a simple random-walk (SRW) proposal suggested by \cite{gjoka2011practical}.
+The stationary distribution for this algorithm is a uniform distribution over $V$, i.e.
+$\lambda(i) = 1/n$ for all $i \in V$.
+The Metropolis-Hastings transition kernel for this method is
+
+\[
+P(i,j) = \left \{
+        \begin{array}{cc}
+             \dfrac{1}{d_i} min\left(1, \dfrac{d_i}{d_j}\right) & \textrm{if j is a neighbor of i}  \\
+             1 - \sum_{k \neq i} \dfrac{1}{d_i} min\left(1, \dfrac{d_i}{d_k}\right) & \textrm{if } j = i\\
+             0 & \textrm{otherwise}.
+        \end{array}
+\right.
+\]
+
+Table (blah) shows the population parameters we are interested in estimating using MCMC methods.
+The race and sex parameters are estimated as proportion of whites and females in the sample respectively.
+We start two parallel Markov chains from two students belonging to different races and study its impacts on the average features of their immediate social group.
+It is hypothesized that students from certain communities tend to engage more with students of same or other marginally represented communities.
+We believe that this "selective networking" might cause formation of clusters in the network wherein students within a cluster engage more with each other than with the students outside it.
+Given that the graph is well-connected, the Markov chains will eventually explore all the nodes.
+
 \singlespacing

### 2020-07-19 Paper/main.tex
Pushing reorganized setup.

@@
 
+  \item The contents are a bit messy right now, and I am having trouble organizing my thoughts.
+
 \end{itemize}
@@
 \begin{enumerate}
-  \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.
+  \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.:
+
+    Here, we will just explain the problem with the old ACF and what happens by using the new ACF.
+We will show a plot to illustrate the impact.
+Then we will summarize the three places this will have an impact: (1) ACF plots (2) estimators of the asymptotic variance-covariance matrix (3) estimating effective sample size.
 
@@
 
-    Describe MC averages and CLT
+    Describe MC averages and CLT here and not before
     \begin{itemize}
@@
         \item Theoretical results
-        \item Computational gains
+        \item Fast implementation
       \end{itemize}
-      \item Explore: Charlie's initial sequence estimators
     \end{itemize}
@@
   \item Examples
+
+  \item Discussion
+    \begin{itemize}
+      \item All plots have been made using the package:(name). The package can be found on GitHub.
+      \item One thing to discuss is that the new autocovariances can be used in the initial sequence estimators as well.
+    \end{itemize}
 
@@
 An important application of ACF is in calculating the asymptotic variance in the CLT of a Markov chain process.
-
-Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in
-%
-\[
-\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)
-\]
-
-Suppose we have $m$ replications of Markov chains with $n$ samples in each chain.
-Let $\{X_{st}\}_{t \geq 1}$ denote the $s^{th}$ Harris ergodic (aperiodic, F-irreducible, and positive Harris recurrent) Markov chain having invariant distribution $F$.
-We will use the following Monte Carlo estimator in order to estimate $\mu$ for the $s^{th}$ chain
-%
-\[
-\hat{\mu}_s = \dfrac{1}{n}\sum_{i = 1}^{n} g(X_{si}) \xrightarrow{a.s.} \mu \textrm{ as } n \to \infty
-\]
-
-Throughout this paper, we will deal with the function $g(X) = X$.
-We denote the sample mean of $s^{th}$ Markov chain by $\bar{X}_s$ and the overall mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$.
-We are interested in Monte Carlo error, i.e.
-$\bar{\bar{X}} - \mu$ to assess the reliability of simulations.
-The sampling distribution for Monte Carlo error of $s^{th}$ chain is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
-%
-\[
-\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
-\]
-
- With $m$ i.i.d.
-samples of $\bar{X}_s$, $s \in \{1,..., m\}$, the MCSE is given by $\Sigma/mn$.
-We are interested in consistent estimates of $\Sigma$ for two reasons.
-Firstly, to construct asymptotically valid confidence intervals and secondly, to determine when to stop the simulations.
-For this purpose, we use the class of Multivariate Spectral Variance Estimators (MSVE) wherein we use R-ACF to estimate the autocovariance.
-We call this replicated spectral variance (RSV) estimator (see \cite{arg:and:2006} for replicated batch means).
-
-MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite.
-There are many criteria for terminating simulation like fixed-time rule, sequencial fixed-volume rule (see \cite{glynn1992asymptotic}), and using Gelman Rubin diagnostics (\cite{gelman1992inference}).
-The relative fixed-volume rule has been thoroughly discussed for MCMC by \cite{flegal2015relative} and \cite{gong2016practical}.
-We will use method of effective sample size (ESS) defined by \cite{vats2019multivariate} for terminating the simulations.
-The quality of estimation of $\Sigma$ is critical in determining that the simulations are not stopped prematurely.
-
-Markov chains are serially correlated and therefore $\Var_F(X)$ is non-informative about the correlatons in Markov chain.
-It is important to construct an estimator for $\Sigma$ which is very close to underlying reality.
-There are many techniques for estimating $\Sigma$ like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
-Due to their highly accurate results, we will only focus on SV estimates in this paper.
-Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}.
-Bias and variance calculations for a variant of SV estimator with known mean is done by \cite{hannan2009multiple}.
-In this paper, we will address the asymptotic properties (basically strong consistency), bias and variance calculations for RSV estimator.
-
-The most common practice would be to combine the SVE from $m$ chains by averaging over them.
-We call this technique average spectral variance (ASV) estimator.
-We will address the issue of slowly mixing Markov chains and show that RSV performs better than ASV.
-Whereas on one side RSV gives better estimates than ASV for a poor Markov chain, it is as good as ASV for a good Markov chain.
-We will exemplify this property of RSV for a bi-modal target distribution in subsection \ref{ex:boomerang}.
-This appeals intuitively because for a fast mixing Markov chain, all the chains will give almost same estimates for mean.
 
@@
 
-\begin{example}[Motivating example]
-  gj
-\begin{figure}
-\begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
-  \caption{$n = 500$}
-  \label{subfig:acf-500}
-\end{subfigure}\\
-\begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
-  \caption{$n = 10^4$}
-  \label{subfig:acf-5e4}
-\end{subfigure}
-\caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains.
+{\color{blue} Dootika: The introduction above needs some rewrite based on my pointers in blue above.
+We should introduce the definition of autocovariance here and present the old and the new estimators of $\Gamma$ here.
+So take some of the details out of the next section and put them here.}
+
+\begin{example}[Demonstrative example]
+
+We demonstrate the striking difference in the ACF plots through mixture of Gaussian target density using a random-walk Metropolis-Hastings sampler.
+
+{\color{blue} Dootika: add new plots here when available for this target density. }
+% \begin{figure}
+% \begin{subfigure}{\textwidth}
+%   \centering
+%   \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
+%   \caption{$n = 500$}
+%   \label{subfig:acf-500}
+% \end{subfigure}\\
+% \begin{subfigure}{\textwidth}
+%   \centering
+%   \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
+%   \caption{$n = 10^4$}
+%   \label{subfig:acf-5e4}
+% \end{subfigure}
+% \caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains.
 First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
-\label{fig:var_acf_ccf}
-\end{figure}
+% \label{fig:var_acf_ccf}
+% \end{figure}
 
@@
 
+\subsection{Theoretical results} % (fold)
+\label{sub:theoretical_results}
+
+% subsection theoretical_results (end)
+
 The bias for R-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:RAC_expec}.
@@
 
+{\color{blue}Dootika: this section here needs to be much tighter in its presentation.
+We will need to remember that the paper is no longer about the SV estimators but about autocorrelations.
+So will have to present the discussion similarly.
+}
+
+Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in
+%
+\[
+\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)
+\]
+
+Suppose we have $m$ replications of Markov chains with $n$ samples in each chain.
+Let $\{X_{st}\}_{t \geq 1}$ denote the $s^{th}$ Harris ergodic (aperiodic, F-irreducible, and positive Harris recurrent) Markov chain having invariant distribution $F$.
+We will use the following Monte Carlo estimator in order to estimate $\mu$ for the $s^{th}$ chain
+%
+\[
+\hat{\mu}_s = \dfrac{1}{n}\sum_{i = 1}^{n} g(X_{si}) \xrightarrow{a.s.} \mu \textrm{ as } n \to \infty
+\]
+
+Throughout this paper, we will deal with the function $g(X) = X$.
+We denote the sample mean of $s^{th}$ Markov chain by $\bar{X}_s$ and the overall mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$.
+We are interested in Monte Carlo error, i.e.
+$\bar{\bar{X}} - \mu$ to assess the reliability of simulations.
+The sampling distribution for Monte Carlo error of $s^{th}$ chain is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
+%
+\[
+\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
+\]
+
+ With $m$ i.i.d.
+samples of $\bar{X}_s$, $s \in \{1,..., m\}$, the MCSE is given by $\Sigma/mn$.
+We are interested in consistent estimates of $\Sigma$ for two reasons.
+Firstly, to construct asymptotically valid confidence intervals and secondly, to determine when to stop the simulations.
+For this purpose, we use the class of Multivariate Spectral Variance Estimators (MSVE) wherein we use R-ACF to estimate the autocovariance.
+We call this replicated spectral variance (RSV) estimator (see \cite{arg:and:2006} for replicated batch means).
+
+MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite.
+There are many criteria for terminating simulation like fixed-time rule, sequencial fixed-volume rule (see \cite{glynn1992asymptotic}), and using Gelman Rubin diagnostics (\cite{gelman1992inference}).
+The relative fixed-volume rule has been thoroughly discussed for MCMC by \cite{flegal2015relative} and \cite{gong2016practical}.
+We will use method of effective sample size (ESS) defined by \cite{vats2019multivariate} for terminating the simulations.
+The quality of estimation of $\Sigma$ is critical in determining that the simulations are not stopped prematurely.
+
+Markov chains are serially correlated and therefore $\Var_F(X)$ is non-informative about the correlatons in Markov chain.
+It is important to construct an estimator for $\Sigma$ which is very close to underlying reality.
+There are many techniques for estimating $\Sigma$ like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
+Due to their highly accurate results, we will only focus on SV estimates in this paper.
+Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}.
+Bias and variance calculations for a variant of SV estimator with known mean is done by \cite{hannan2009multiple}.
+In this paper, we will address the asymptotic properties (basically strong consistency), bias and variance calculations for RSV estimator.
+
+The most common practice would be to combine the SVE from $m$ chains by averaging over them.
+We call this technique average spectral variance (ASV) estimator.
+We will address the issue of slowly mixing Markov chains and show that RSV performs better than ASV.
+Whereas on one side RSV gives better estimates than ASV for a poor Markov chain, it is as good as ASV for a good Markov chain.
+We will exemplify this property of RSV for a bi-modal target distribution in subsection \ref{ex:boomerang}.
+This appeals intuitively because for a fast mixing Markov chain, all the chains will give almost same estimates for mean.
+
+\subsection{Globally-centered spectral variance estimators} % (fold)
+\label{sub:globally_centered_spectral_variance_estimators}
+
+% subsection globally_centered_spectral_variance_estimators (end)
+
 Let $\{X_t\}_{t \geq 1}$ be a stochastic process. Denote lag-k autocovariance matrix by $\Gamma(k)$, which is given by,
@@
 
-\subsection{Average Spectral Variance } \label{sec:asv}
-
-Recall that for $s^{th}$ Markov chain, the spectral variance estimator is given by,
-
-\begin{align*}
-    \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
-    \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
-\end{align*}
-
-The average spectral variance ($\Sigma_{ASV}$) is computed by averaging the SV estimates from all $m$ Markov chains.
-
-\[
-\hat{\Sigma}_{ASV} = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}
-\]
-
-\subsection{Replicated Spectral Variance } \label{sec:rsv}
+% \subsection{Average Spectral Variance } \label{sec:asv}
+
+% Recall that for $s^{th}$ Markov chain, the spectral variance estimator is given by,
+
+% \begin{align*}
+%     \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
+%     \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
+% \end{align*}
+
+% The average spectral variance ($\Sigma_{ASV}$) is computed by averaging the SV estimates from all $m$ Markov chains.
+
+% \[
+% \hat{\Sigma}_{ASV} = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}
+% \]
 
@@
 \]
+
+\subsubsection{Theoretical results} \label{sec:rsv}
 
@@
 \end{proof}
+
+\subsubsection{Fast implementation} % (fold)
+\label{ssub:fast_implementation}
+
+% subsubsection fast_implementation (end)
 

### 2020-07-20 Boomerang/one_run.R
Five examples cleanup

@@ -1,117 +1,0 @@
-set.seed(1)
-library(cubature)
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-source("functions.R")
-sourceCpp("lag.cpp")
-
-
-######### Function calculates CCF with demean available
-ccf2 <- function (x, y, lag.max = NULL, type = c("correlation", "covariance"), 
-    plot = TRUE, demean = TRUE, na.action = na.fail, ...) 
-{
-    type <- match.arg(type)
-    if (is.matrix(x) || is.matrix(y)) 
-        stop("univariate time series only")
-    X <- ts.intersect(as.ts(x), as.ts(y))
-    colnames(X) <- c(deparse(substitute(x))[1L], deparse(substitute(y))[1L])
-    acf.out <- acf(X, lag.max = lag.max, plot = FALSE, type = type, 
-        na.action = na.action, demean = FALSE)
-    lag <- c(rev(acf.out$lag[-1, 2, 1]), acf.out$lag[, 1, 2])
-    y <- c(rev(acf.out$acf[-1, 2, 1]), acf.out$acf[, 1, 2])
-    acf.out$acf <- array(y, dim = c(length(y), 1L, 1L))
-    acf.out$lag <- array(lag, dim = c(length(y), 1L, 1L))
-    acf.out$snames <- paste(acf.out$snames, collapse = " & ")
-    if (plot) {
-        plot(acf.out, ...)
-        return(invisible(acf.out))
-    }
-    else return(acf.out)
-}
-#########
-
-A <- 1
-B <- 3
-C <- 8
-
-samples <- perspective(A, B, C, 1000)
-# pdf(file = "contour_plot.pdf")
-contour(samples$x, samples$y, samples$z, main="Contour Plot", nlevels = 20, asp = 1)
-# filled.contour(samples$x,samples$y,samples$z, color=terrain.colors, main="Contour Plot",)
-# dev.off()
-
-start <- matrix(c(C,1,1,C), 2, 2)
-
-nsim <- 1e3
-chain1 <- markov.chain(A, B, C, nsim, start[1,])
-chain2 <- markov.chain(A, B, C, nsim, start[2,])
-
-par(mfrow = c(1,1))
[…]

### 2020-07-20 Boomerang/output.R

@@ -1,6 +1,9 @@
+###################################################################
+##This code produces and saves all the plots in pdf and prints the
+##contents of tables using R objects generated in simulations.R
+###################################################################
+
 set.seed(1)
-library(fields)
-library(scatterplot3d)
 library(cubature)
 library(graphics)
 library(pracma)
@@ -9,45 +12,127 @@ library(RcppArmadillo)
 library(fftwtools)
 library(mcmcse)
 library(stats)
+library("RColorBrewer")
 sourceCpp("lag.cpp")
 source("functions.R")
 
 
-###############################################
-#####Visualization of distribution############
-###############################################
-# Uncomment to visualize through contour plots
-#Contour plot
+########################################################
+#####Visualization through perspective plots############
+########################################################
+
+#Perspective plots for both simulation settings
+
 A <- 1
 B <- 3
 C <- 8
-samples <- perspective(A, B, C, 500)
-#pdf(file = paste("Out/", A, B, C, "/3d_density_plot.pdf", sep = "_"), height = 4)
-pdf(file = paste("Out/tukey/", A, B, C, "/3d_density_plot.pdf", sep = "_"), height = 4)
-par(mfrow = c(1,2))
-contour(samples$x,samples$y,samples$z,main="Contour Plot")
-#filled.contour(samples$x,samples$y,samples$z,color=terrain.colors,main="Contour Plot",)
-persp(samples$x,samples$y,samples$z,main="Perspective Plot", col = "springgreen", shade = .5, theta = -45, phi = 0, xlab = "x", ylab = "y", zlab = "Density")
+
+pdf(file = paste("Out/", A, B, C, "/3d_density_plot.pdf", sep = "_"))
+samples <- perspective(A, B, C, 100)
+persp(samples$x, samples$y, samples$z, main="", col = "white", shade = .5, theta = -45, phi = 0, xlab = "x", ylab = "y", zlab = "Density")
 dev.off()
 
-###############################################
[…]

### 2020-07-20 Boomerang/sample_sve.R

@@ -1,67 +1,0 @@
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-sourceCpp("lag.cpp")
-
-
-# FFT function for SVE
-# Remember that A should be centered
-mSVEfft <- function (A, b, method = "bartlett")
-{
-  n <- nrow(A) # A must be centered matrix
-  p <- ncol(A)
-  w <- as.vector(lag2(1:b, n = n, b = b, method = method)) # calculate lags
-  w <- c(1, w[1:(n-1)], 0, w[(n-1):1])  # starting steps from FFT paper
-  w <- Re(fftw_r2c(w))            
-  FF <- matrix(0, ncol = p, nrow = 2*n)  
-  FF[1:n,] <- A    
-  if(p > 1)  # multivariate
-  {
-    FF <- mvfftw_r2c (FF)        
-    FF <- FF * matrix(w, nrow = 2*n, ncol = p) 
-    FF <- mvfftw_c2r(FF) / (2* n ) 
-    return ((t(A) %*% FF[1:n, ]) / n )    
-  } else if(p == 1)  ##univariate calls
-  {
-    FF <- fftw_r2c (FF)        
-    FF <- FF * matrix(w, nrow = 2*n, ncol = p) 
-    FF <- fftw_c2r(FF) / (2* n ) 
-    return ((t(A) %*% FF[1:n]) / n )
-  }              
-
-}
-
-
-n <- 1e2
-p <- 2
-b <- 10
-
-chain1 <- matrix(rnorm(n*p,mean = 2), ncol = 2, nrow = n)
-chain2 <- matrix(rnorm(n*p, mean = 2), ncol = 2, nrow = n)
-
-
-# ASV estimator
-c1.cen.loc <- scale(chain1, scale = FALSE)  ## X_st - bar(X)_s
-c2.cen.loc <- scale(chain2, scale = FALSE)
-
-sve1 <- mSVEfft(A = c1.cen.loc, b = b)
-sve2 <- mSVEfft(A = c2.cen.loc, b = b)
-
-(asv <- (sve1 + sve2)/2)
-
-# RSV estimator
-global.mean <- colMeans(rbind(chain1, chain2))
-
-c1.cen <- scale(chain1, center = global.mean, scale =FALSE)
-c2.cen <- scale(chain2, center = global.mean, scale =FALSE)
-
[…]

### 2020-07-20 Boomerang/simulations.R

@@ -1,3 +1,8 @@
+################################################################
+##This code is responsible for simulating and storing R objects 
+##that are later used for plotting figures and making tables.
+################################################################
+
 set.seed(1)
 library(cubature)
 library(Rcpp)
@@ -20,13 +25,12 @@ create.output <- function(A,B,C,m,check.pts,freq,c.prob){
     start[m-i+1,] <- c(C*(2^(2-i)), 0)
   }
 
-  critical <- qchisq(c.prob, df=2)
   T.mean <- true.mean(A,B,C)
 
   for (i in 1:length(check.pts)){
 
     nsim <- check.pts[i]
-
+    critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
     asv.samp <- array(0, dim = c(2,2,freq))
     rsv.samp <- array(0, dim = c(2,2,freq))
     asv.coverage <- rep(0,freq)
@@ -62,7 +66,7 @@ create.output <- function(A,B,C,m,check.pts,freq,c.prob){
       if (chi.sq.asv <= critical) {asv.coverage[j]=1}
       if (chi.sq.rsv <= critical) {rsv.coverage[j]=1}
     }
-    save(asv.samp,rsv.samp,asv.coverage,rsv.coverage, file = paste(paste("Out/", A, B, C, "/out", m,nsim,A,B,C, sep = "_"),".Rdata", sep = ""))
+    save(asv.samp, rsv.samp, asv.coverage, rsv.coverage, file = paste(paste("Out/", A, B, C, "/out", m, nsim, A, B, C, sep = "_"),".Rdata", sep = ""))
   }
 
 }
@@ -70,7 +74,8 @@ create.output <- function(A,B,C,m,check.pts,freq,c.prob){
 ##################################################
 #function for storing convergence plots data
 ##################################################
-convergence <- function(min, max, A, B, C, m, rep=100){
+
+convergence <- function(min, max, step, A, B, C, m, rep=100){
 
   p <- 2
   start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
@@ -88,7 +93,7 @@ convergence <- function(min, max, A, B, C, m, rep=100){
     }
   }
 
-  conv.pts <- seq(min, max,100)
+  conv.pts <- seq(min, max, step)
[…]

### 2020-07-20 MagnoliaNetwork/output.R

@@ -12,6 +12,8 @@ sourceCpp("lag.cpp")
 source("functions.R")
 library(ergm)
 
+
+#############Data Modification#####################
 data(faux.magnolia.high)
 magnolia = faux.magnolia.high
 
@@ -20,65 +22,42 @@ notwellconnected = which(component.largest(magnolia, connected="weak")==FALSE)
 delete.vertices(magnolia, notwellconnected)
 dp = dataPrepHighSchool(magnolia)
 
-
-
 ###################################################
-### Starting values
+### Model parameters
+
 start <- c(279, 360)
+p <- 5
 m <- 2   #no of parallel chains
-
-###############################################
-
-
-check.pts <- c(1e2, 5e2, 1e3, 5e3, 1e4)
-r <- length(check.pts)
-freq <- 20
 min <- 1e2
 max <- 1e4
 step <- 100
 conv.pts <- seq(min, max, step)
 
-## 1.) Running plots
+###################################################
+###################################################
+######log Frobenius norm running plots ###########
+###################################################
+###################################################
 
 load(file = paste(paste("Out/conv_data", min, max, sep = "_"), ".Rdata", sep = ""))
 
-pdf(file = paste(paste("Out/run_plots_grades", sep = "_"), ".pdf", sep = ""))
-plot(conv.pts,asv.samp[3,3,], type = "l", col = "red", main = "Variance of grades", xlab = "Simulation size", ylab = "Variance", ylim = range(rsv.samp[3,3,], asv.samp[3,3,]))
-lines(conv.pts, rsv.samp[3,3,], col="blue")
-legend("topright", legend=c("ASV", "RSV"),col=c("red", "blue"), lty=1, cex=.75)
+frob.asv <- log(apply(asv.samp[3:5, 3:5,], 3, norm, type = "F"))
+frob.rsv <- log(apply(rsv.samp[3:5, 3:5,], 3, norm, type = "F"))
+
+pdf(file = paste(paste("Out/run_plot-Frob", sep = "_"), ".pdf", sep = ""))
+plot(conv.pts, frob.asv, type = "l", col="coral", main = "", xlab = "Simulation size", 
[…]

### 2020-07-20 MagnoliaNetwork/simulations.R

@@ -9,71 +9,6 @@ source("functions.R")
 sourceCpp("lag.cpp")
 library(ergm)
 
-data(faux.magnolia.high)
-magnolia = faux.magnolia.high
-
-#Ensure well connected component only 
-notwellconnected = which(component.largest(magnolia, connected="weak")==FALSE)
-delete.vertices(magnolia, notwellconnected)
-dp = dataPrepHighSchool(magnolia)
-
-############################################################
-##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
-############################################################
-
-create.output <- function(start, m, check.pts, freq, truth){
-  
-  p <- 5
-  
-  for (i in 1:length(check.pts)){
-    
-    nsim <- check.pts[i]
-    critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
-    asv.samp <- array(0, dim = c(p,p,freq))
-    rsv.samp <- array(0, dim = c(p,p,freq))
-    asv.coverage <- rep(0,freq)
-    rsv.coverage <- rep(0,freq)
-    
-    
-    for (j in 1:freq){
-      
-      print(j)
-      if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2), "for nsim = ", nsim))
-      
-      chain <- array(0,dim = c(nsim,p,m))
-      sve <- array(0, dim = c(p,p,m))
-      rsve <- array(0, dim = c(p,p,m))
-      b <- rep(0,m)
-      
-      temp <- magnolia.mhrw.func(nrep = nsim, chains = m, start = start)
-      for (k in 1:m){
-        chain[,,k] <- as.matrix(MHRWestimation(temp[[k]])[,c(1,7,5,8,9)], nrow = nsim, ncol = p)
-        b[k] <- batchSize(chain[,,k], method = "bartlett")
-        }
-      
-      b.avg <- ceiling(mean(b))
-      global.mean <- apply(chain,2,mean)
-      
-      for (k in 1:m){
-        chain.cen.loc <- scale(chain[,,k], scale = FALSE)  ## X_st - bar(X)_s
-        sve[,,k] <- mSVEfft(A = chain.cen.loc, b = b.avg)
-        chain.cen <- scale(chain[,,k], center = global.mean, scale =FALSE)
[…]

### 2020-07-20 New_ACF_comparisons.R

@@ -1,0 +1,127 @@
+set.seed(1)
+source("functions.R")
+library(rep.acf.ccf)
+
+
+m <- 2
+A <- 1
+B <- 3
+C <- 8
+
+start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
+
+for(i in 1:floor(m/2)){
+  start[i,] <- c(0, C*(2^(2-i)))
+  start[m-i+1,] <- c(C*(2^(2-i)), 0)
+}
+
+lag.max <- 100
+
+####################################
+nsim <- 500
+########################################
+mc.chain.list <- list()
+global.mean <- c(0,0)
+
+for (i in 1:m){
+  chain <- markov.chain(A, B, C, nsim, start[i,])
+  global.mean <- global.mean + colMeans(chain)
+  mc.chain.list[[i]] = chain
+}
+global.mean <- global.mean/m
+sample_var <- rep(0, m)
+means <- rep(0, m)
+covariances <- matrix(0, nrow = lag.max+1, ncol = m)
+
+for (j in 1:m){
+  sample_var[j] <- var(mc.chain.list[[j]][,component])
+  means[j] <- mean(mc.chain.list[[j]][,component])
+  covariances[,j] <- as.vector(acf(mc.chain.list[[j]][,component], plot = FALSE, lag.max = lag.max, type = "covariance")$acf)
+}
+W <- mean(sample_var)
+B <- nsim * var(means)
+new_var <- ((nsim - 1)/nsim)*W + (1/nsim)*B
+avg.covariances <- as.matrix(rowMeans(covariances))
+new_corr <- 1 - (W/new_var) + (avg.covariances/new_var)
+
+acf.list <- combined_acf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
+ccf.list <- combined_ccf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
+
+pdf(file = "Boomerang.pdf", width = 8, height = 4)
+plot(acf.list[[1]][[1]], main = expression(paste("ACF comparison for chain 1")), type = "l", xlim = c(0,lag.max), ylim = c(-0.5,1))
+lines(seq(0,lag.max), acf.list[[1]][[2]]$acf, type = "l", col = "blue", xlim = c(0,lag.max), ylim = c(0,1))
+lines(seq(0, lag.max), new_corr, col = "green")
[…]

### 2020-07-20 PoissonChange/output.R

@@ -1,7 +1,5 @@
 set.seed(1)
-library(fields)
-library(scatterplot3d)
-library(cubature)
+library(fields)library(cubature)
 library(graphics)
 library(pracma)
 library(Rcpp)
@@ -13,9 +11,10 @@ sourceCpp("lag.cpp")
 source("functions.R")
 library("MCMCpack")
 load("mida.rda")
-library(rep.acf.ccf)
 
 
+###############################################
+##############Model parameters#################
 ###############################################
 
 c0 <- 13
@@ -23,50 +22,35 @@ d0 <- 1
 bars <- 6
 p <- bars+1
 m <- 2
-check.pts <- c(5e2, 1e3, 2e3, 5e3, 1e4, 2e4)
-r <- length(check.pts)
-freq <- 1e2
-c.prob <- .95
 min <- 5e2
 max <- 1e5
 step <- 500
 conv.pts <- seq(min, max, step)
 
-## 1.) Running plots
+##############################################
+##############################################
+## log Frobenius norm Running plots ##########
+##############################################
+##############################################
 
 load(file = paste(paste("Out/conv_data", min, max, sep = "_"), ".Rdata", sep = ""))
 
-pdf(file = paste(paste("Out/run_plots_components", sep = "_"), ".pdf", sep = ""), height = 3)
-par(mfrow=c(4,2))
-
-for (i in 1:(bars+1)){
-
-  plot(conv.pts,asv.samp[i,i,], type = "l", col = "red", main = paste("Variance of component -", i), xlab = "Simulation size", ylab = "Variance", ylim = range(rsv.samp[i,i,]))
-  lines(conv.pts, rsv.samp[i,i,], col="blue")
-  legend("topright", legend=c("ASV", "RSV"),col=c("red", "blue"), lty=1, cex=.75)
-
-}
-
-
-#### 1c.) Determinant
-pdf(file = paste(paste("Out/run_plots_det", sep = "_"), ".pdf", sep = ""), height = 3)
-
-det.rsv <- rep(0,length(conv.pts))
-det.asv <- rep(0,length(conv.pts))
-
-for (i in 1:length(conv.pts)){
-  det.rsv[i] <- det(rsv.samp[,,i])
-  det.asv[i] <- det(asv.samp[,,i])
-}
-
[…]

### 2020-07-20 PoissonChange/simulations.R

@@ -6,75 +6,33 @@ library(fftwtools)
 library(mcmcse)
 source("functions.R")
 sourceCpp("lag.cpp")
-
 library("MCMCpack")
-load("mida.rda")
+load(file = "mida.rda")
 
-############################################################
-##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
-############################################################
-
-create.output <- function(c0, d0, bars, m, check.pts, freq, c.prob, truth){
-
-  p <- bars+1
-
-  for (i in 1:length(check.pts)){
-
-    nsim <- check.pts[i]
-    critical <- ((p*(m*nsim - 1))/(m*nsim - p))*qf(c.prob, df1 = p, df2 = m*nsim-p)
-    asv.samp <- array(0, dim = c(p,p,freq))
-    rsv.samp <- array(0, dim = c(p,p,freq))
-    asv.coverage <- rep(0,freq)
-    rsv.coverage <- rep(0,freq)
-
-    for (j in 1:freq){
-      if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2), "for nsim = ", nsim))
-      chain <- array(0,dim = c(nsim,p,m))
-      sve <- array(0, dim = c(p,p,m))
-      rsve <- array(0, dim = c(p,p,m))
-      b <- rep(0,m)
-
-      for (k in 1:m){
-        chain[,,k] <- matrix(MCMCpoissonChange(mida~ 1, m=bars, c0=c0, d0=d0, marginal.likelihood="none", mcmc = nsim, burnin = 0, thin = 1, seed = round(1e3*runif(1))), nrow = nsim, ncol = p)
-        b[k] <- batchSize(chain[,,k], method = "bartlett")
-      }
-
-      b.avg <- mean(b)
-      global.mean <- apply(chain,2,mean)
-
-      for (k in 1:m){
-        chain.cen.loc <- scale(chain[,,k], scale = FALSE)  ## X_st - bar(X)_s
-        sve[,,k] <- mSVEfft(A = chain.cen.loc, b = b.avg)
-        chain.cen <- scale(chain[,,k], center = global.mean, scale =FALSE)
-        rsve[,,k] <- mSVEfft(A = chain.cen, b = b.avg)
-      }
-
-      asv.samp[,,j] <- apply(sve, c(1,2), mean)
-      rsv.samp[,,j] <- apply(rsve, c(1,2), mean)
-
[…]

### 2020-07-20 SensorNetwork/acf_plots.R

@@ -1,6 +1,5 @@
 set.seed(1)
-library(rep.acf.ccf)
-source("functions.R")
+
 ######## Data
 
 # Observation indicators from the fifth sensor (1st column) to the first four sensors
@@ -36,166 +35,65 @@ j.scale <- rep(1.08, 4)    # jump scale
 
 # Chain-1 with 5e3 samples
 
-nsim = 1e5
+nsim1 = 1e3
 
 start1 <- runif(8, min= -0.3, max = 0)
 aux1 <- runif(8, min = -0.3, max= 0)
-system.time(res.ram1 <- MHwG.RAM(start1, aux1, jump.scale = j.scale,
+system.time(nsim1.ram1 <- MHwG.RAM(start1, aux1, jump.scale = j.scale,
                                  Ob, Os, Xb, Xs, Yb, Ys,
-                                 n.sample = nsim, n.burn = 0))
+                                 n.sample = nsim1, n.burn = 0))
 
 # Chain-2 with 5e3 samples
 start2 <- runif(8, min = 0.7, max = 1.1)
 aux2 <- runif(8, min = 0.7, max= 1.1)
 
-system.time(res.ram2 <- MHwG.RAM(start2, aux2, jump.scale = j.scale,
+system.time(nsim1.ram2 <- MHwG.RAM(start2, aux2, jump.scale = j.scale,
                                     Ob, Os, Xb, Xs, Yb, Ys,
-                                    n.sample = nsim, n.burn = 0))
+                                    n.sample = nsim1, n.burn = 0))
 
-save(res.ram1, res.ram2, file = "Out/two_chains.Rdata")
-colMeans(mc.chain.list[[1]])
-colMeans(mc.chain.list[[2]])
+colMeans(nsim2.ram1$x)
+colMeans(nsim2.ram2$x)
 
-mc.chain.list <- list(res.ram1$x, res.ram2$x)
+# Chain-1 with 1e5 samples
+set.seed(1)
 
-###############################################
-###############################################
-# Scatter plots
-###############################################
-###############################################
-nsim1 <- 5e3-1
-nsim2 <- 1e5-1
[…]

### 2020-07-20 SensorNetwork/functions.R

@@ -134,38 +134,6 @@ ram <- function(x.initial, z.initial, var.cov, sample.size, burn.size,
 
 }
 
-############################ Example 3: Sensor location problem
-
-######## Data
-
-# Observation indicators from the fifth sensor (1st column) to the first four sensors
-# and those from the sixth sensor (2nd column) to the first four sensors.
-Ob <- matrix(c(1, 0, 1, 0, 1, 0, 1, 0), ncol = 2)
-
-# Observation indicators among the first four sensors.
-Os <- matrix(c(0, 0, 0, 1,
-               0, 0, 1, 1,
-               0, 1, 0, 0,
-               1, 1, 0, 0), ncol = 4)
-
-# Each row indicates the location of the known sensors (5th and 6th).
-Xb <- matrix(c(0.5, 0.3, 0.3, 0.7), ncol = 2)
-
-# Each row indicates the location of the unknown sensors (1st, 2nd, 3rd, and 4th).
-Xs <- matrix(c(0.5748, 0.0991, 0.2578, 0.8546,
-               0.9069, 0.3651, 0.1350, 0.0392), ncol = 2)
-
-# The observed distances from the fifth sensor (1st column) to the first four sensors
-# and those from the sixth sensor (2nd column) to the first four sensors.
-Yb <- matrix(c(0.6103, 0, 0.2995, 0,
-               0.3631, 0, 0.5656, 0), ncol = 2)
-
-# Observed distances among the first four sensors.
-Ys <- matrix(c(0, 0, 0, 0.9266,
-               0, 0, 0.2970, 0.8524,
-               0, 0.2970, 0, 0,
-               0.9266, 0.8524, 0, 0), ncol = 4)
-
 ######## Target joint posterior density
 
 norm2 <- function(loca, locb) {

### 2020-07-20 SensorNetwork/output.R

@@ -1,3 +1,8 @@
+###################################################################
+##This code produces and saves all the plots in pdf and prints the
+##contents of tables using R objects generated in simulations.R
+###################################################################
+
 set.seed(1)
 library(cubature)
 library(graphics)
@@ -11,7 +16,7 @@ sourceCpp("lag.cpp")
 source("functions.R")
 
 ###################################################
-### Data and model parameters
+### Data 
 ######################################################################
 
 # Observation indicators from the fifth sensor (1st column) to the first four sensors
@@ -42,112 +47,252 @@ Ys <- matrix(c(0, 0, 0, 0.9266,
                0, 0.2970, 0, 0,
                0.9266, 0.8524, 0, 0), ncol = 4)
 
+#######################################
+####Model Parameters#################
+######################################
 
 m <- 5
-start <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
-aux <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
-j.scale <- rep(1,.08, 4)
-truth <- c(0.5748, 0.9069, 0.0991, 0.3651, 0.2578, 0.1350, 0.8546, 0.0392)
+p <- 8
+j.scale <- rep(0.5, 4)
 
+####### Starting Values####################
 
-###############################################
+start1 <- c(-0.1, 0.5, -0.1, -0.2, 0.1, 0.1, -0.5, -0.5)
+aux1 <- runif(n=8, min=min(start1), max=max(start1))
+start2 <- c(0.0, 0.6, 0.1, 0.1, 0.2, 0.2, 1.0, 0.0)
+aux2 <- runif(n=8, min=min(start2), max=max(start2))
+start3 <- c(0.2, 0.7, 0.5, 0.4, 0.5, 0.3, 0.5, 0.5)
+aux3 <- runif(n=8, min=min(start3), max=max(start3))
+start4 <- c(0.4, 0.8, 0.8, 0.6, 0.7, 0.4, 1.0, 1.0)
[…]

### 2020-07-20 SensorNetwork/simulations.R

@@ -1,3 +1,8 @@
+################################################################
+##This code is responsible for simulating and storing R objects 
+##that are later used for plotting figures and making tables.
+################################################################
+
 set.seed(1)
 library(cubature)
 library(Rcpp)
@@ -6,91 +11,7 @@ library(fftwtools)
 library(mcmcse)
 source("functions.R")
 sourceCpp("lag.cpp")
-######## Data
 
-# Observation indicators from the fifth sensor (1st column) to the first four sensors
-# and those from the sixth sensor (2nd column) to the first four sensors.
-Ob <- matrix(c(1, 0, 1, 0, 1, 0, 1, 0), ncol = 2)
-
-# Observation indicators among the first four sensors.
-Os <- matrix(c(0, 0, 0, 1,
-               0, 0, 1, 1,
-               0, 1, 0, 0,
-               1, 1, 0, 0), ncol = 4)
-
-# Each row indicates the location of the known sensors (5th and 6th).
-Xb <- matrix(c(0.5, 0.3, 0.3, 0.7), ncol = 2)
-
-# Each row indicates the location of the unknown sensors (1st, 2nd, 3rd, and 4th).
-Xs <- matrix(c(0.5748, 0.0991, 0.2578, 0.8546,
-               0.9069, 0.3651, 0.1350, 0.0392), ncol = 2)
-
-# The observed distances from the fifth sensor (1st column) to the first four sensors
-# and those from the sixth sensor (2nd column) to the first four sensors.
-Yb <- matrix(c(0.6103, 0, 0.2995, 0,
-               0.3631, 0, 0.5656, 0), ncol = 2)
-
-# Observed distances among the first four sensors.
-Ys <- matrix(c(0, 0, 0, 0.9266,
-               0, 0, 0.2970, 0.8524,
-               0, 0.2970, 0, 0,
-               0.9266, 0.8524, 0, 0), ncol = 4)
-
-############################################################
-##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
-############################################################
-
-create.output <- function(start, aux, j.scale, Ob, Os, Xb, Xs, Yb, Ys, m, check.pts, freq,truth){
-
-  p <- 8
-
[…]

### 2020-07-20 VAR-1/New_ACF_comparisons.R

@@ -1,0 +1,116 @@
+set.seed(1)
+source("functions.R")
+library(rep.acf.ccf)
+
+m <- 5
+p <- 2
+omega <- diag(p)
+for (i in 1:(p-1)){
+  for (j in 1:(p-i)){
+    omega[j, j+i] <- .9^i
+    omega[j+i, j] <- .9^i
+  }
+}
+
+phi <- diag(c(.9999, .001))
+dummy <- matrix(1:p^2, nrow = p, ncol = p)
+dummy <- qr.Q(qr(dummy))
+phi <- dummy %*% phi %*% t(dummy)
+#phi <- phi/(max(eigen(phi)$values) + .1)
+
+target <- target.sigma(phi, omega)
+truth <- true.sigma(phi, var = target)
+
+lag.max <- 150
+true.acf <- array(0, dim = c(p, p, 2*lag.max + 1))
+true.acf[,,lag.max+1] <- target
+for (i in 1:lag.max){
+  true.acf[,,lag.max + 1 + i] <- phi %*% true.acf[,,lag.max + 1 + i - 1]
+  true.acf[,,lag.max + 1 - i] <- true.acf[,,lag.max + 1 - i + 1] %*% t(phi)
+}
+
+start <- matrix(0, nrow = m, ncol = p)  #only depends on C
+
+for(i in 1:floor(m/2)){
+  start[i,] <- 0.5*i*sqrt(diag(target))
+  start[m-i+1,] <- -0.5*i*sqrt(diag(target))
+}
+
+####################################
+nsim <- 500
+########################################
+mc.chain.list <- list()
+global.mean <- rep(0,p)
+lag.max <- 150
+for (i in 1:m){
+  chain <- markov.chain(phi, omega, nsim, start[i,])
+  global.mean <- global.mean + colMeans(chain)
+  mc.chain.list[[i]] = chain
+}
+global.mean <- global.mean/m
+sample_var <- rep(0, m)
+means <- rep(0, m)
+covariances <- matrix(0, nrow = lag.max+1, ncol = m)
+
+for (j in 1:m){
+  sample_var[j] <- var(mc.chain.list[[j]][,component])
+  means[j] <- mean(mc.chain.list[[j]][,component])
+  covariances[,j] <- as.vector(acf(mc.chain.list[[j]][,component], plot = FALSE, lag.max = lag.max, type = "covariance")$acf)
+}
+W <- mean(sample_var)
[…]

### 2020-07-20 VAR-1/output.R

@@ -1,0 +1,149 @@
+set.seed(1)
+library(fields)
+library(graphics)
+library(Rcpp)
+library(RcppArmadillo)
+library(fftwtools)
+library(mcmcse)
+library(stats)
+library("RColorBrewer")
+sourceCpp("lag.cpp")
+source("functions.R")
+
+
+###############################################
+##### Model parameters####################
+#########################################
+
+m <- 5
+p <- 2
+omega <- diag(p)
+for (i in 1:(p-1)){
+  for (j in 1:(p-i)){
+    omega[j, j+i] <- .9^i
+    omega[j+i, j] <- .9^i
+  }
+}
+
+phi <- diag(c(.9999, .001))
+dummy <- matrix(1:p^2, nrow = p, ncol = p)
+dummy <- qr.Q(qr(dummy))
+phi <- dummy %*% phi %*% t(dummy)
+
+############3Simuation settings###########
+
+truth <- true.sigma(phi, var = target)
+check.pts <- c(1e3, 5e3, 1e4, 5e4, 1e5)
+rep <- 50
+min <- 5e2
+max <- 1e5
+step <- 500
+conv.pts <- seq(min, max, step)
+
+start <- matrix(0, nrow = m, ncol = p)  #only depends on C
+
+for(i in floor(m/2):1){
+  start[i,] <- 2*i*sqrt(diag(target))
+  start[m-i+1,] <- -2*i*sqrt(diag(target))
+}
+
+###########################################################
+############## log Frobenius norm running plots ###########
+###########################################################
+
+
+load(file = paste(paste("Out/run_data", m, min, max, sep = "_"), ".Rdata", sep = ""))
+
+pdf(file = paste(paste("Out/run_plots", m, sep = "_"), ".pdf", sep = ""), height = 3)
+plot(conv.pts,log(apply(asv.samp, 3, norm, type = "F")), type = "l", col = "coral", lwd = 2,
+     main = "", xlab = "Simulation size", ylab = "Variance", 
+     ylim = range(c(log(apply(rsv.samp, 3, norm, type = "F"))), log(norm(truth, type = "F"))))
+lines(conv.pts, log(apply(rsv.samp, 3, norm, type = "F")), col="royalblue", lwd = 2)
+abline(h = log(norm(truth, type = "F")), col = "green")
+legend("bottomright", legend=c("ASV", "RSV"),col=c("coral", "royalblue"), lty=1, lwd = 2)
[…]

### 2020-07-20 VAR-1/plots.R

@@ -1,190 +1,0 @@
-set.seed(1)
-library(fields)
-library(scatterplot3d)
-library(graphics)
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-library(stats)
-sourceCpp("lag.cpp")
-source("functions.R")
-
-
-###############################################
-
-#parameters and initiate values
-
-m <- 5
-p <- 2
-omega <- diag(p)
-for (i in 1:(p-1)){
-  for (j in 1:(p-i)){
-    omega[j, j+i] <- .9^i
-    omega[j+i, j] <- .9^i
-  }
-}
-
-phi <- diag(c(.9999, .001))
-dummy <- matrix(1:p^2, nrow = p, ncol = p)
-dummy <- qr.Q(qr(dummy))
-phi <- dummy %*% phi %*% t(dummy)
-
-target <- target.sigma(phi, omega)
-truth <- true.sigma(phi, var = target)
-
-lag.max <- 150
-true.det <- det(truth)
-check.pts <- c(1e3, 5e3, 1e4, 5e4, 1e5)
-freq <- 1e3
-rep <- 50
-c.prob <- .95
-min <- 5e2
-max <- 1e5
-conv.pts <- seq(min, max, 500)
-r <- length(check.pts)
-start <- matrix(0, nrow = m, ncol = p)  #only depends on C
-
-for(i in floor(m/2):1){
-  start[i,] <- 2*i*sqrt(diag(target))
-  start[m-i+1,] <- -2*i*sqrt(diag(target))
-}
-
-#################################
-### Bartlett
-################################
-
-
-## 1.) Running plots
-
-
-load(file = paste(paste("Out/bartlett/run_data", m, min, max, sep = "_"), ".Rdata", sep = ""))
-
-#Calculate determinants
-
-det.rsv <- rep(0,length(conv.pts))
-det.asv <- rep(0,length(conv.pts))
-
-for (i in 1:length(conv.pts)){
-  det.rsv[i] <- det(rsv.samp[,,i])
-  det.asv[i] <- det(asv.samp[,,i])
-}
-
-#### 1a.) 2 - components
-
-pdf(file = paste(paste("Out/bartlett/run_plots", m, sep = "_"), ".pdf", sep = ""), height = 3)
-par(mfrow = c(1,3))
-
-for (k in 1:p){
[…]

### 2020-07-20 VAR-1/simulations.R

@@ -1,10 +1,14 @@
+################################################################
+##This code is responsible for simulating and storing R objects 
+##that are later used for plotting figures and making tables.
+################################################################
+
 set.seed(10)
 library(Rcpp)
 library(RcppArmadillo)
 library(fftwtools)
 library(mcmcse)
 source("functions.R")
-library(sandwich)
 sourceCpp("lag.cpp")
 
 ############################################################
@@ -22,11 +26,12 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
     start[m-i+1,] <- -2*i*sqrt(diag(truth))
   }
 
-  critical <- qchisq(c.prob, df=2)
   master.chain.rep <- list()
+  
   for (i in 1:freq){
     print(paste("Sampling percentage completion: ", i*100/freq))
     chains <- array(0, dim = c(max(check.pts), p, m))
+    
     for (j in 1:m){
       chains[,,j] <- markov.chain(phi, omega, max(check.pts), start[j,])
     }
@@ -36,7 +41,8 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
   for (i in 1:length(check.pts)){
 
     nsim <- check.pts[i]
-
+    critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
+    
     asv.samp <- array(0, dim = c(p,p,freq))
     rsv.samp <- array(0, dim = c(p,p,freq))
     asv.coverage <- rep(0,freq)
@@ -53,7 +59,7 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
         b[k] <- batchSize(chain[,,k], method = "bartlett")
       }
 
-      b.avg <- mean(b)
+      b.avg <- ceiling(mean(b))
       global.mean <- apply(chain, 2, mean)
 
       for (k in 1:m){
@@ -71,17 +77,16 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
       if (chi.sq.asv <= critical) {asv.coverage[j]=1}
       if (chi.sq.rsv <= critical) {rsv.coverage[j]=1}
     }
[…]

### 2020-07-20 SensorNetwork/acf_plots.R
Pushing Sensor plots

@@ -1,5 +1,6 @@
 set.seed(1)
-
+library(rep.acf.ccf)
+source("functions.R")
 ######## Data
 
 # Observation indicators from the fifth sensor (1st column) to the first four sensors
@@ -35,65 +36,166 @@ j.scale <- rep(1.08, 4)    # jump scale
 
 # Chain-1 with 5e3 samples
 
-nsim1 = 1e3
+nsim = 1e5
 
 start1 <- runif(8, min= -0.3, max = 0)
 aux1 <- runif(8, min = -0.3, max= 0)
-system.time(nsim1.ram1 <- MHwG.RAM(start1, aux1, jump.scale = j.scale,
+system.time(res.ram1 <- MHwG.RAM(start1, aux1, jump.scale = j.scale,
                                  Ob, Os, Xb, Xs, Yb, Ys,
-                                 n.sample = nsim1, n.burn = 0))
+                                 n.sample = nsim, n.burn = 0))
 
 # Chain-2 with 5e3 samples
 start2 <- runif(8, min = 0.7, max = 1.1)
 aux2 <- runif(8, min = 0.7, max= 1.1)
 
-system.time(nsim1.ram2 <- MHwG.RAM(start2, aux2, jump.scale = j.scale,
+system.time(res.ram2 <- MHwG.RAM(start2, aux2, jump.scale = j.scale,
                                     Ob, Os, Xb, Xs, Yb, Ys,
-                                    n.sample = nsim1, n.burn = 0))
+                                    n.sample = nsim, n.burn = 0))
 
-colMeans(nsim2.ram1$x)
-colMeans(nsim2.ram2$x)
+save(res.ram1, res.ram2, file = "Out/two_chains.Rdata")
+colMeans(mc.chain.list[[1]])
+colMeans(mc.chain.list[[2]])
 
-# Chain-1 with 1e5 samples
-set.seed(1)
+mc.chain.list <- list(res.ram1$x, res.ram2$x)
 
-nsim2 <- 1e5
+###############################################
+###############################################
+# Scatter plots
+###############################################
+###############################################
+nsim1 <- 5e3-1
+nsim2 <- 1e5-1
[…]

### 2020-07-20 SensorNetwork/functions.R

@@ -134,6 +134,38 @@ ram <- function(x.initial, z.initial, var.cov, sample.size, burn.size,
 
 }
 
+############################ Example 3: Sensor location problem
+
+######## Data
+
+# Observation indicators from the fifth sensor (1st column) to the first four sensors
+# and those from the sixth sensor (2nd column) to the first four sensors.
+Ob <- matrix(c(1, 0, 1, 0, 1, 0, 1, 0), ncol = 2)
+
+# Observation indicators among the first four sensors.
+Os <- matrix(c(0, 0, 0, 1,
+               0, 0, 1, 1,
+               0, 1, 0, 0,
+               1, 1, 0, 0), ncol = 4)
+
+# Each row indicates the location of the known sensors (5th and 6th).
+Xb <- matrix(c(0.5, 0.3, 0.3, 0.7), ncol = 2)
+
+# Each row indicates the location of the unknown sensors (1st, 2nd, 3rd, and 4th).
+Xs <- matrix(c(0.5748, 0.0991, 0.2578, 0.8546,
+               0.9069, 0.3651, 0.1350, 0.0392), ncol = 2)
+
+# The observed distances from the fifth sensor (1st column) to the first four sensors
+# and those from the sixth sensor (2nd column) to the first four sensors.
+Yb <- matrix(c(0.6103, 0, 0.2995, 0,
+               0.3631, 0, 0.5656, 0), ncol = 2)
+
+# Observed distances among the first four sensors.
+Ys <- matrix(c(0, 0, 0, 0.9266,
+               0, 0, 0.2970, 0.8524,
+               0, 0.2970, 0, 0,
+               0.9266, 0.8524, 0, 0), ncol = 4)
+
 ######## Target joint posterior density
 
 norm2 <- function(loca, locb) {

### 2020-07-20 SensorNetwork/output.R

@@ -1,8 +1,3 @@
-###################################################################
-##This code produces and saves all the plots in pdf and prints the
-##contents of tables using R objects generated in simulations.R
-###################################################################
-
 set.seed(1)
 library(cubature)
 library(graphics)
@@ -16,7 +11,7 @@ sourceCpp("lag.cpp")
 source("functions.R")
 
 ###################################################
-### Data 
+### Data and model parameters
 ######################################################################
 
 # Observation indicators from the fifth sensor (1st column) to the first four sensors
@@ -47,252 +42,152 @@ Ys <- matrix(c(0, 0, 0, 0.9266,
                0, 0.2970, 0, 0,
                0.9266, 0.8524, 0, 0), ncol = 4)
 
-#######################################
-####Model Parameters#################
-######################################
 
 m <- 5
-p <- 8
-j.scale <- rep(0.5, 4)
+start <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
+aux <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
+j.scale <- rep(1,.08, 4)
+truth <- c(0.5748, 0.9069, 0.0991, 0.3651, 0.2578, 0.1350, 0.8546, 0.0392)
 
-####### Starting Values####################
 
-start1 <- c(-0.1, 0.5, -0.1, -0.2, 0.1, 0.1, -0.5, -0.5)
-aux1 <- runif(n=8, min=min(start1), max=max(start1))
-start2 <- c(0.0, 0.6, 0.1, 0.1, 0.2, 0.2, 1.0, 0.0)
-aux2 <- runif(n=8, min=min(start2), max=max(start2))
-start3 <- c(0.2, 0.7, 0.5, 0.4, 0.5, 0.3, 0.5, 0.5)
-aux3 <- runif(n=8, min=min(start3), max=max(start3))
-start4 <- c(0.4, 0.8, 0.8, 0.6, 0.7, 0.4, 1.0, 1.0)
-aux4 <- runif(n=8, min=min(start4), max=max(start4))
-start5 <- c(0.7, 1.0, 1.2, 0.9, 0.9, 0.5, 1.5, 1.5)
[…]

### 2020-07-20 SensorNetwork/simulations.R

@@ -1,8 +1,3 @@
-################################################################
-##This code is responsible for simulating and storing R objects 
-##that are later used for plotting figures and making tables.
-################################################################
-
 set.seed(1)
 library(cubature)
 library(Rcpp)
@@ -11,7 +6,91 @@ library(fftwtools)
 library(mcmcse)
 source("functions.R")
 sourceCpp("lag.cpp")
+######## Data
 
+# Observation indicators from the fifth sensor (1st column) to the first four sensors
+# and those from the sixth sensor (2nd column) to the first four sensors.
+Ob <- matrix(c(1, 0, 1, 0, 1, 0, 1, 0), ncol = 2)
+
+# Observation indicators among the first four sensors.
+Os <- matrix(c(0, 0, 0, 1,
+               0, 0, 1, 1,
+               0, 1, 0, 0,
+               1, 1, 0, 0), ncol = 4)
+
+# Each row indicates the location of the known sensors (5th and 6th).
+Xb <- matrix(c(0.5, 0.3, 0.3, 0.7), ncol = 2)
+
+# Each row indicates the location of the unknown sensors (1st, 2nd, 3rd, and 4th).
+Xs <- matrix(c(0.5748, 0.0991, 0.2578, 0.8546,
+               0.9069, 0.3651, 0.1350, 0.0392), ncol = 2)
+
+# The observed distances from the fifth sensor (1st column) to the first four sensors
+# and those from the sixth sensor (2nd column) to the first four sensors.
+Yb <- matrix(c(0.6103, 0, 0.2995, 0,
+               0.3631, 0, 0.5656, 0), ncol = 2)
+
+# Observed distances among the first four sensors.
+Ys <- matrix(c(0, 0, 0, 0.9266,
+               0, 0, 0.2970, 0.8524,
+               0, 0.2970, 0, 0,
+               0.9266, 0.8524, 0, 0), ncol = 4)
+
+############################################################
+##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
+############################################################
+
+create.output <- function(start, aux, j.scale, Ob, Os, Xb, Xs, Yb, Ys, m, check.pts, freq,truth){
+
+  p <- 8
+
[…]

### 2020-07-21 GaussianMix/output.R
Gaussian mixture example

@@ -1,0 +1,121 @@
+set.seed(1)
+library(rep.acf.ccf)
+
+
+log.density <- function(x, p, mu1, mu2, sd1, sd2){
+  return(log(p*dnorm(x, mean = mu1, sd = sd1) + (1-p)*dnorm(x, mean = mu2, sd= sd2)))
+}
+
+
+mh.mcmc <- function(start, p, mu1, mu2, sd1, sd2, N, h){
+  
+  X <- rep(0, N)
+  acc <- 0
+  X[1] <- start
+  for (i in 2:N){
+    prop <- rnorm(1, mean = X[i-1], sd = 2)
+    ratio <- log.density(prop, p, mu1, mu2, sd1, sd2) - log.density(X[i-1], p, mu1, mu2, sd1, sd2)
+    
+    if(runif(1) < exp(ratio)){
+      X[i] <- prop
+      acc <- acc+1
+    } else {
+      X[i] <- X[i-1]
+    }
+  }
+  print(acc/N)
+  return (X)
+}
+
+
+N <- 1e5
+p <- 0.7
+mu1 <- -5
+mu2 <- 5
+sd1 <- 1
+sd2 <- 0.5
+
+
+chain1 <- mh.mcmc(start = -3, p, mu1, mu2, sd1, sd2, N, 1)
+chain2 <- mh.mcmc(start = 3, p, mu1, mu2, sd1, sd2, N, 1)
+
+mean(chain1)
+mean(chain2)
+
+##################################
+######Trace plots for n=1e4#######
+##################################
+
+pdf(file = "TargetTrace_n1e4.pdf", height = 5, width = 6)
+plot(x, 10000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-10000,3000), xlim = range(chain1,chain2), yaxt = 'n')
+par(new = TRUE)
+plot(x = chain1[1:1e4], y = seq(-1, -1e4, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e4, 3e3), , xlim = range(chain1,chain2), yaxt = 'n')
+lines(x = chain2[1:1e4], y = seq(-1, -1e4, -1), col = "plum3")
+mtext(side = 2, text = "Time", line = 1)
+legend("topleft", legend=c("Target", "Chain-1", "Chain-2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=0.7, lwd=2)
+dev.off()
+
[…]

### 2020-07-22 Paper/main.tex
First superficial change

--- 2020-07-18 Paper/main.tex
@@
 \usepackage{comment}
+\usepackage[linesnumbered, ruled]{algorithm2e}
 % By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.
@@
 
-{\color{blue} Main things to change
-\begin{itemize}
-  \item I don't want to call this ``Replicated autocovariance'' or ``Replicated spectral variance''.
+% {\color{blue} Main things to change
+% \begin{itemize}
+%   \item I don't want to call this ``Replicated autocovariance'' or ``Replicated spectral variance''.
 I think ``Globally-centered autocovariance'' is more appropriate and self-explanatory.
@@
 
-\end{itemize}
-
-A rough outline of the organization
-\begin{enumerate}
-  \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.
-
-  \item Globally-centered autocovariance
-    \begin{itemize}
-      \item Theoretical soundness
-    \end{itemize}
-
-  \item Variance of Monte Carlo averages
-
-    Describe MC averages and CLT
-    \begin{itemize}
-      \item Globally-centered Spectral variance estimators
-      \begin{itemize}
-        \item Theoretical results
-        \item Computational gains
-      \end{itemize}
-      \item Explore: Charlie's initial sequence estimators
-    \end{itemize}
-
-  \item Effective sample size
-
-  \item Examples
-
-  \item Appendix
-    \begin{itemize}
-      \item Proofs
-      \item ACF plots for other examples.
-    \end{itemize}
-
-\end{enumerate}
-}
+%   \item The contents are a bit messy right now, and I am having trouble organizing my thoughts.
+
+% \end{itemize}
+
+% A rough outline of the organization
+% \begin{enumerate}
+%   \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.:
+
+%     Here, we will just explain the problem with the old ACF and what happens by using the new ACF.
+We will show a plot to illustrate the impact.
+Then we will summarize the three places this will have an impact: (1) ACF plots (2) estimators of the asymptotic variance-covariance matrix (3) estimating effective sample size.
+
+%   \item Globally-centered autocovariance
+%     \begin{itemize}
+%       \item Theoretical soundness
+%     \end{itemize}
+
+%   \item Variance of Monte Carlo averages
+
+%     Describe MC averages and CLT here and not before
+%     \begin{itemize}
+%       \item Globally-centered Spectral variance estimators
+%       \begin{itemize}
+%         \item Theoretical results
+%         \item Fast implementation
+%       \end{itemize}
+%     \end{itemize}
+
+%   \item Effective sample size
+
+%   \item Examples
+
+%   \item Discussion
+%     \begin{itemize}
+%       \item All plots have been made using the package:(name). The package can be found on GitHub.
+%       \item One thing to discuss is that the new autocovariances can be used in the initial sequence estimators as well.
+%     \end{itemize}
+
+%   \item Appendix
+%     \begin{itemize}
+%       \item Proofs
+%       \item ACF plots for other examples.
+%     \end{itemize}
+
+% \end{enumerate}
+% }
+% \newpage
+
 \section{Introduction} \label{sec:intro}
@@
 Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones.
-Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains.
-Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain.
-A famous sample autovariance function is the empirical estimator, which unfortunately comes with its drawbacks.
+Therefore, it becomes imperative for an MCMC pG-titioner to have an idea about underlying dependence structure in the Markov chains.
+Autocovariance function (ACF) chaG-terizes this dependence for a stationary Markov chain.
+Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e.
+(1) $\mathbb{E}[X_t] = \mu$ is constant for all $t$, (2) $\mathbb{E}[X_t^2]$ is constant for all $t$, and (3) $\mathbb{E}[X_t X_{t+k}]$ is a function of $k$ only $\forall k,t \in \mathbb{Z}$.
+Then, the autocovariance function at lag-$k$ is defined as
+
+\[
+    \Gamma(k) = Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
+\]
+
+A popular sample autocovariance function is the empirical estimator. On a finite sample $X = (X_1, X_2, ..., X_n)^T$, the autocovariance at lag-$k$ is estimated as
+%
+\begin{equation} \label{eq:empirical_acf}
+    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{(t+\abs{k})} - \bar{X})^T
+\end{equation}
+
+where $\bar{X} = \sum_{t=1}^nX_t/n$.
+Calculation of exact ACF has been done for simple models like autoregressive (AR), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
+However, for most of the complex sampling algorithms, we rely on sample estimators for ACF.
+Unfortunately, the estimator given in equation \ref{eq:empirical_acf} has been observed to have a some drawbacks.
 Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains for decently finite samples.
 We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.
-
-Calculation of exact theoretical ACF has been done for simple models like autoregressive (AR), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
-However, for most of the complex processes, we rely on sample ACF to understand the correlation in the chain at a particular lag.
-For a slowly mixing Markov chain or a multi-modal target distribution, Markov chains explore the sample space only partially for even high sample size.
+With convenient multi-core computation resources, it is possible to get multiple Markov chains for a target distribution.
+Our goal is to combine the information from all the Markov chains while calculating the autocovariances\\
+
+ A commonly faced problem with the MCMC models is the slow mixing property.
+In case of multi modal target distributions, it has been observed that the Markov chains tend to get \textit{stuck} in a particular mode for a long time.
+As a consequence, the chain fails to explore the sample space.
 In such situations, single chain empirical ACF will underestimate the autocovariance giving misleading inferences.
-With convenient multi-core computation resources, it is possible to get multiple Markov chains for a target distribution.
-We propose a new autocovariance estimator called replicated autocovariance function (R-ACF) with a simple fix in centering a chain about the overall mean.
-An important application of ACF is in calculating the asymptotic variance in the CLT of a Markov chain process.
-
-Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in
-%
-\[
-\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)
-\]
-
-Suppose we have $m$ replications of Markov chains with $n$ samples in each chain.
-Let $\{X_{st}\}_{t \geq 1}$ denote the $s^{th}$ Harris ergodic (aperiodic, F-irreducible, and positive Harris recurrent) Markov chain having invariant distribution $F$.
-We will use the following Monte Carlo estimator in order to estimate $\mu$ for the $s^{th}$ chain
-%
-\[
-\hat{\mu}_s = \dfrac{1}{n}\sum_{i = 1}^{n} g(X_{si}) \xrightarrow{a.s.} \mu \textrm{ as } n \to \infty
-\]
-
-Throughout this paper, we will deal with the function $g(X) = X$.
-We denote the sample mean of $s^{th}$ Markov chain by $\bar{X}_s$ and the overall mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$.
-We are interested in Monte Carlo error, i.e.
-$\bar{\bar{X}} - \mu$ to assess the reliability of simulations.
-The sampling distribution for Monte Carlo error of $s^{th}$ chain is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
-%
-\[
-\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
-\]
-
- With $m$ i.i.d.
-samples of $\bar{X}_s$, $s \in \{1,..., m\}$, the MCSE is given by $\Sigma/mn$.
-We are interested in consistent estimates of $\Sigma$ for two reasons.
-Firstly, to construct asymptotically valid confidence intervals and secondly, to determine when to stop the simulations.
-For this purpose, we use the class of Multivariate Spectral Variance Estimators (MSVE) wherein we use R-ACF to estimate the autocovariance.
-We call this replicated spectral variance (RSV) estimator (see \cite{arg:and:2006} for replicated batch means).
+We propose an autocovariance estimator called globally-centered autocovariance function (G-ACF) with a simple fix in centering which has been observed to show drastically better results in many cases.
+We will further study the impact of G-ACF in calculation of two important applications of ACF (1) asymptotic variance of Markov chain average and (2) effective sample size (ESS).\\
 
@@
 The relative fixed-volume rule has been thoroughly discussed for MCMC by \cite{flegal2015relative} and \cite{gong2016practical}.
-We will use method of effective sample size (ESS) defined by \cite{vats2019multivariate} for terminating the simulations.
-The quality of estimation of $\Sigma$ is critical in determining that the simulations are not stopped prematurely.
-
-Markov chains are serially correlated and therefore $\Var_F(X)$ is non-informative about the correlatons in Markov chain.
-It is important to construct an estimator for $\Sigma$ which is very close to underlying reality.
-There are many techniques for estimating $\Sigma$ like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
-Due to their highly accurate results, we will only focus on SV estimates in this paper.
-Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}.
-Bias and variance calculations for a variant of SV estimator with known mean is done by \cite{hannan2009multiple}.
-In this paper, we will address the asymptotic properties (basically strong consistency), bias and variance calculations for RSV estimator.
-
-The most common practice would be to combine the SVE from $m$ chains by averaging over them.
-We call this technique average spectral variance (ASV) estimator.
-We will address the issue of slowly mixing Markov chains and show that RSV performs better than ASV.
-Whereas on one side RSV gives better estimates than ASV for a poor Markov chain, it is as good as ASV for a good Markov chain.
-We will exemplify this property of RSV for a bi-modal target distribution in subsection \ref{ex:boomerang}.
-This appeals intuitively because for a fast mixing Markov chain, all the chains will give almost same estimates for mean.
+We will use method of effective sample size (ESS) by \cite{vats2019multivariate} for terminating the simulations.
+The quality of estimation of $\Sigma$ is critical in estimating their ESS.
+We will successfully show that the G-SVE estimates the truth better and prevents the premature stopping of Markov chain.\\
 
 In the next section we introduce the new sample autocovariance estimator and calculate its bias for finite samples.
-We observe that the bias term for R-ACF is similar to the bias of empirical ACF except for a few small order end-effect terms that vanish as $n \to \infty$.
-In section \ref{sec:variance_est}, we introduce three estimators for $\Sigma$ and study the properties of RSV estimator through proof of strong consistency, bias, and variance calculations.
-We will elaborate on the estimator for ESS using RSV in section \ref{sec:ess}.
-Section \ref{sec:examples} gives a simulation study on three different examples for the proposed estimators.
-There are only a handful of stochastic processes where the true autocovariance and $\Sigma$ are known.
-To compare the estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
-We successfully show in section \ref{ex:var} that our estimators yield better results as compared to the classical sample ACF and SVE.
-A more promising advantage of our estimators is observed when the target distribution is multi-modal.
-For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note} in section \ref{ex:boomerang}.
+We observe that the bias term for G-ACF is similar to the bias of empirical ACF except for a few small order end-effect terms that vanish as $n \to \infty$.
+In section \ref{sec:variance_est}, we introduce the globally-centered SVE and give a proof of strong consistency, bias, and variance calculations.
+We will elaborate on the estimator for ESS using G-SVE in section \ref{sec:ess}.
+Section \ref{sec:examples} gives an experimental study on three different examples for the proposed estimators.
 All the important proofs are given in the Appendix.
 
-\begin{example}[Motivating example]
-  gj
-\begin{figure}
+\begin{example}[Demonstrative example]
+
+We demonstrate the striking difference in the ACF plots through mixture of Gaussian target density using a random-walk Metropolis-Hastings sampler.
+The target density has two well separated and non-equal modes.
+Two Markov chains are started close to each mode.
+It can be seen in Figure \ref{fig:gaussian-trace} that for the first $10^4$ samples, the chains do not communicate with the other mode.
+Whereas for a sample size of $10^5$, the chains have jumped modes and therefore, a single chain can give reliable information about the distribution.
+We wish to make two points here: firstly, for small sample size, we observe that ACF gives extremely misleading estimates of autocovariance whereas G-ACF is very close to reality (Figure \ref{subfig:gauss-acf-1e4}).
+Whereas, sharing the information about Monte Carlo average across chains leads to better estimation of autocovariances.
+Secondly, for a large sample size, the estimates from G-ACF as well as ACF are equivalent.
+Figure \ref{subfig:gauss-trace_1e5} depicts the scenario when convergence is achieved.
+This shows that G-ACF is at least as good as ACF; hence safe to use in any setting.
+
+\begin{figure}[htbp]
+    \begin{subfigure}{.5\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{plots/gaussian-Targettrace_n1e4.pdf}
+   \caption{$n = 10^4$}
+   \label{subfig:gauss-trace_1e4}
+ \end{subfigure}
+ \begin{subfigure}{0.5\textwidth}
+   \centering
+   \includegraphics[width=\linewidth]{plots/gaussian-Targettrace_n1e5.pdf} 
+   \caption{$n = 10^5$}
+   \label{subfig:gauss-trace_1e5}
+ \end{subfigure}
+    \caption{Target density and Density plot for two chains starting at different values for a Gaussian mixture model with mixture probability $= 0.7, \; \mu_1 = -5, \; \mu_2 = 5, \; \sigma_1 = 1, \textrm{ and } \sigma_2 = 0.5$.
+(a) $n = 10^4$; chains don't interact.
+(b) $n = 10^5$; chains interact.}
+    \label{fig:gaussian-trace}
+\end{figure}
+
+\begin{figure}[htbp]
 \begin{subfigure}{\textwidth}
    \centering
-  \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
-  \caption{$n = 500$}
-  \label{subfig:acf-500}
+   \includegraphics[width=.8\linewidth]{plots/gaussian-acf_n1e4.pdf}
+   \caption{$n = 10^4$}
+   \label{subfig:gauss-acf-1e4}
  \end{subfigure}\\
@@
    \centering
-  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
-  \caption{$n = 10^4$}
-  \label{subfig:acf-5e4}
+   \includegraphics[width=.8\linewidth]{plots/gaussian-acf_n1e5.pdf} 
+   \caption{$n = 10^5$}
+   \label{subfig:gauss-acf-1e5}
  \end{subfigure}
-\caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains.
-First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
-\label{fig:var_acf_ccf}
+ \caption{Autocorrelation plot for locally-centered ACF (left) and globally centered ACF (right) averaged over all chains. (a) $n = 10^4$, not converged yet; (b) $n =  10^5$, converged}
+ \label{fig:gauss:acf}
 \end{figure}
-
 \end{example}
-\section{Globally-centered autocovariance} \label{sec:R-ACF}
-
-For a stationary stochastic process $\{X_t\}_{t \geq 1}$, let $\Gamma(k)$ denote the lag -k autocovariance.
-In time series literature, we generally encounter the following estimator for autocovariance.
-%
-\[
-\hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{(t+\abs{k})} - \bar{X})^T
-\]
-
-\cite{priestley1981spectral} shows that this estimator is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
+
+\section{Globally-centered autocovariance} \label{sec:G-ACF}
+
+ Suppose we have $m$ replications of Markov chains for same target distribution and $\{X_{st}; \; t \in \mathbb{Z}\}$ denote the $s^{th}$ Markov chain.
+Let the sample mean of $s^{th}$ Markov chain be denoted by $\bar{X}_s$ and the global mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$.
+The global mean provides a better estimate for the expectation value when the number of simulation per chain are not sufficient for the convergence to kick in.
+The globally-centered autocovariance function (G-ACF) for the $s^{th}$ Markov chain is given by:
+%
+\[
+\hat{\Gamma}_{G}(k) = \dfrac{1}{mn} \sum_{s=1}^{m}\sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
+\]
+
+If the starting points of these parallel Markov chains are sufficiently dispersed, G-ACF provides more realistic estimation of lag covariances.
+\cite{priestley1981spectral} shows that the empirical estimator in Equation \ref{eq:empirical_acf} is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
 An unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, say $\Gamma^*(k)$.
@@
 
-A commonly faced problem with the MCMC algorithms is the slow mixing property.
-In case of multi modal target distributions, it has been observed that even decently mixing Markov chains fail to explore the sample space for the first few thousand observations.
-This leads to underestimation of autocovariance for a single Markov chain.
-We propose a simple and neat fix for estimating ACF while dealing with slow convergence.
-Suppose we have $m$ replications of Markov chains for same target distribution, the overall mean $\bar{\bar{X}} = \sum_{i = 1}^{m}\bar{X}_i/m$ provides a better estimate for the expectation value when the number of simulation per chain are not sufficient for the convergence to kick in.
-The replicated autocovariance estimator or $s^{th}$ Markov chain is given by:
-%
-\[
-\hat{\Gamma}_{RAC,s}(k) = \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
-\]
-
-If the starting points of these parallel Markov chains are sufficiently dispersed, R-ACF provides more realistic estimation of lag covariances.
-It is a known problem that getting true autocovariance in closed form for non-simple problems is difficult.
-In Figure \ref{fig:var_acf_ccf}, we will illustrate the comparison between ACF and R-ACF for a slowly mixing VAR-1 example, where the truth is known.
-We wish to make two points here: firstly, for small sample size, we observe that ACF gives extremely misleading estimates of autocovariance whereas R-ACF is very close to reality.
-Figure \ref{subfig:acf-500} depicts the scenario where the convergence is not achieved yet.
-Secondly, for a large sample size , the estimates from R-ACF as well as ACF are equivalent.
-Figure \ref{subfig:acf-5e4} depicts the scenario when convergence is achieved.
-This shows that R-ACF is at least as good as ACF; hence safe to use in any setting.
-
-The bias for R-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:RAC_expec}.
-Before getting to the bias results for $\hat{\Gamma}_{RAV}(k)$ for any lag k, we introduce an additional notation.
+\subsection{Theoretical results} % (fold)
+\label{sub:theoretical_results}
+
+% subsection theoretical_results (end)
+
+The bias for G-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:G-_expec}.
+Before getting to the bias results for $\hat{\Gamma}_{RAV}(k)$ for any lag $k$, we introduce an additional notation.
 For $q \geq 1$, we define
@@
 We denote $\Phi^{(1)} \textrm{ by } \Phi$. 
-\begin{theorem} \label{th:RAC_expec}
-   \[
-   \mathbb{E}[\hat{\Gamma}_{RAC}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
+\begin{theorem} \label{th:G-_expec}
+   \[
+   \mathbb{E}[\hat{\Gamma}_{G}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
    \]
@@
 
-As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{RAC}$ into four parts for all $k \geq 1$ as:
- \[
- \hat{\Gamma}_{RAC} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
+As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{G-}$ into four parts for all $k \geq 1$ as:
+ \[
+ \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
  \]
@@
 
-\begin{remark} \label{rmrk:exp_racf_minus_acf}
-Using theorem \ref{th:RAC_expec} and equation \ref{eq:priestly},
-\[
-\mathbb{E}[\hat{\Gamma}_{RAC}(k) - \hat{\Gamma}(k)] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
+\begin{remark} \label{rmrk:exp_G-f_minus_acf}
+Using theorem \ref{th:G_expec} and equation \ref{eq:priestly},
+\[
+\mathbb{E}[\hat{\Gamma}_{G}(k) - \hat{\Gamma}(k)] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
 \]
@@
 Note that the RHS in the above expression is positive.
-As a consequence, R-ACF will counter this negative bias and give more reliable estimates for ACF.
+As a consequence, G-ACF will counter this negative bias and give more reliable estimates for ACF.
 
@@
 \[
-\mathbb{E}[\hat{\Gamma}_{RAC}(0)] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
+\mathbb{E}[\hat{\Gamma}_{G}(0)] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
 \]
@@
 
-Let $\{X_t\}_{t \geq 1}$ be a stochastic process. Denote lag-k autocovariance matrix by $\Gamma(k)$, which is given by,
-
-\[
-\Gamma(k) = \Gamma(-k) = \E[(X_t - \E[X])(X_{t+k} - \E[X])^T]
-\]
-
-Recall that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
-
-\[
+{\color{blue}Dootika: this section here needs to be much tighter in its presentation.
+We will need to remember that the paper is no longer about the SV estimators but about autocorrelations.
+So will have to present the discussion similarly.
+}
+
+  Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in
+%
+\[
+\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)
+\]
+
+Let $\{X_{t}\}_{t \geq 1}$ denote the Harris ergodic (aperiodic, F-irreducible, and positive Harris recurrent) Markov chain having invariant distribution $F$.
+We will use the following Monte Carlo estimator in order to estimate $\mu$
+%
+\[
+\hat{\mu}_s = \dfrac{1}{n}\sum_{i = 1}^{n} g(X_{si}) \xrightarrow{a.s.} \mu \textrm{ as } n \to \infty
+\]
+
+We are interested in Markov chain average and therefore, throughout this paper, we will deal with the function $g(X) = X$.
+To assess the reliability of our simulations, we are interested in Monte Carlo error, i.e.
+$\bar{\bar{X}} - \mu$.
+The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
+%
+\[
+\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
+\]
+
+ It is important to construct an estimator for $\Sigma$ which is very close to underlying reality.
+There are many techniques for estimating $\Sigma$ like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
+Due to its nice statistical properties and heavy dependence on autocovariance, we will only focus on SVE in this paper.
+SVE involves a truncated and weighted sum of autocovariances.
+We will give theoretical as well as experimental results for the version of SVE that uses our globally centered autocovariances.
+We call this globally-centered SVE (G-SVE).
+
+Given m parallel Markov chains, we have $m$ i.i.d.
+samples of $\bar{X}_s$, $s \in \{1,..., m\}$.
+The Markov Chain standard error (MCSE) is given by $\Sigma/mn$.
+We are interested in consistent estimates of $\Sigma$ for two reasons.
+Firstly, to construct asymptotically valid confidence intervals and secondly, to determine when to stop the simulations.
+For this purpose, we use the class of Multivariate Spectral Variance Estimators (MSVE).
+The most common practice would be to combine the spectral variance estimates from $m$ chains by averaging over them.
+We call this technique average spectral variance estimator and denote it by $\hat{\Sigma}_A$).
+We propose using a globally-centered spectral variance estimator (G-SVE) wherein we use G-ACF to estimate the autocovariance.
+Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}.
+Bias and variance calculations for a variant of SVE with known mean is done by \cite{hannan2009multiple}.
+In this paper, we will address the asymptotic properties (strong consistency), bias and variance calculations for G-SVE.
+
+\subsection{Globally-centered spectral variance estimators} % (fold)
+\label{sub:globally_centered_spectral_variance_estimators}
+
+% subsection globally_centered_spectral_variance_estimators (end)
+
+Recall from Equation \ref{eq:empirical_acf} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
+
+\begin{equation}
     \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
-\]
+\end{equation}
 
@@
 
-\[
+\begin{equation} \label{eq:sve}
     \hat{\Sigma}_{SV} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
-\]
+\end{equation}
 
 where $w(.)$ is the lag window and $b_n$ is the truncation point.
-
- Consider $m$ Markov chains where $\bar{X}_s$, $\hat{\Gamma}_s(k)$ and $\hat{\Sigma}_{SV, s}$ are the sample mean, sample lag-k autocovariance and spectral variance estimators respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
-We will consider two estimators for spectral variance calculations using multiple Markov chains.
-
-\subsection{Average Spectral Variance } \label{sec:asv}
-
-Recall that for $s^{th}$ Markov chain, the spectral variance estimator is given by,
-
-\begin{align*}
-    \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
-    \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
-\end{align*}
-
-The average spectral variance ($\Sigma_{ASV}$) is computed by averaging the SV estimates from all $m$ Markov chains.
-
-\[
-\hat{\Sigma}_{ASV} = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}
-\]
-
-\subsection{Replicated Spectral Variance } \label{sec:rsv}
-
-Now we introduce the Replicated Spectral Variance Estimator (RSV).
-$\hat{\Gamma}_{RAC,s}(k)$ is the sample replicated lag-k autocovariance estimator for the $s^{th}$ MC using overall mean $(\bar{\bar{X}})$ instead of $\bar{X}_s$ for centering.
-We construct an RSV estimator $\hat{\Sigma}_{RSV} $ using this replicated version of autocovariance estimator.
+Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
+We construct the globally-centered SVE estimator $\hat{\Sigma}_{G}$ using the globally-centered ACF.
 Consider,
@@
 \begin{align*}
-    \hat{\Sigma}_{RSV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{RAC,s}(k)
-\end{align*}
-\[
-\hat{\Sigma}_{RSV} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{RSV,s}
-\]
-
-The RSV estimator centers the data around the global mean. We are interested in proving the strong consistency, finding the bias and variance of RSV.
+    \hat{\Sigma}_{G,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G,s}(k)
+\end{align*}
+\[
+\hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}
+\]
+
+\subsubsection{Theoretical results} \label{sec:G-SVE}
+
+The G-SVE estimator centers the data around the global mean. We are interested in proving the strong consistency, finding the bias and variance of G-SVE.
 
@@
     We assume the SIP holds for the Markov chain.
-Here $\{X_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu = \mathbb{E}[X]$.
+Here $\{X_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu$.
 Let $\|.\|$ denote the Euclidean norm.
@@
 \[
-\hat{\Sigma}_{SV,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
+\hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
 \]
@@
 \label{th:consistency}
- Let the Assumptions \ref{ass:sip},\ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{RSV} \to \Sigma$ with probability 1, as $n \to \infty$.
+ Let the Assumptions \ref{ass:sip},\ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \to \Sigma$ with probability 1, as $n \to \infty$.
 \end{theorem}
@@
 \begin{proof}
-We complete the proof by showing that $\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$.
+We complete the proof by showing that $\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$.
 We will show that
@@
 \[
-\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
+\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
 \]
@@
 
-Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we will finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$.
+Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we can finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$.
 The proof is in Appendix subsection \ref{appendix:strong_consis}
@@
 
-We are interested in the finding the bias for RSV estimator as a function of $n$.
+We are interested in the finding the bias for G-SVE estimator as a function of $n$.
 The proof below applies to all the important range of lag windows $w(x)$; where $w(x)$ is a continuous, even fnction with $w(0)=1, \abs{w(x)} < c$, and $\int_{-\infty}^{\infty}w^2(x)dx < \infty$.
@@
 \[
-W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)
+W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right).
 \]
@@
 \begin{ass} \label{ass:bias}
-    Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that
+    Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that for all $s$
     \begin{enumerate} [a.]
-        \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\| < \infty$
+        \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma_s(k)\| < \infty$
         \item $\lim _{x \to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty$
@@
 
-\begin{theorem}\label{th:rsv_bias}
+\begin{theorem}\label{th:G-SVE_bias}
 The limiting bias of replicated spectral variance is given by:
 \[
- \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right] = -k_q\Phi^{(q)}
+ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}
  \]
@@
 \[
-\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
-\]
-
-Using theorem \ref{th:RAC_expec}, we can write the expectation of $\hat{\Gamma}_{RAC}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
+\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
+\]
+
+Using theorem \ref{th:G-ACF_expec}, we can write the expectation of $\hat{\Gamma}_{G}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
 The proof is given in the Appendix subsection \ref{appendix:bias}.
@@
 
-\begin{theorem} \label{th:rsv_variance}
- If Assumption \ref{ass:variance_cal} hold, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{RSV}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+\begin{theorem} \label{th:G-SVE_variance}
+ If Assumption \ref{ass:variance_cal} hold, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
 \end{theorem}
@@
 Further, let $\tilde{\Sigma}^{ij}$ be the $(i,j)^{th}$ element of this matrix.
-We will prove that the variance of $\hat{\Sigma}_{RSV} \textrm{ and } \tilde{\Sigma}$ are equivalent for large sample sizes.
+We will prove that the variance of $\hat{\Sigma}_{G} \textrm{ and } \tilde{\Sigma}$ are equivalent for large sample sizes.
 The proof is in Appendix subsection \ref{appendix:variance}
@@
 
+\subsubsection{Fast implementation} % (fold)
+\label{ssub:fast_implementation}
+
+The multivariate spectral variance estimator (MSVE) despite having good statistical properties poses application limitations due to slow computation and high storage demands.
+Observe from equation \ref{eq:empirical_acf} and \ref{eq:sve}, the computation of spectral variance estimator has a complexity of $\mathcal{O}(b_n n p)$ where $n$ is the MCMC sample size, $p$ is the dimensionality and $b_n$ is the truncation point.
+To overcome this limitation for our experimental purposes, we used a fast Fourier transform based algorithm presented by \cite{heberle2017fast} for calculating the alternate formulation of MSVE given by Kyriakoulis (2005).\\
+
+Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = \dfrac{1}{n}\sum_{t=1}^{n}X_t$ is the MCMC average.
+Let $w_k$ denote the lag-window at lag-k, i.e.
+$w_k = w_n(k/b_n)$.
+The alternate formulation for MSVE is given by
+
+\begin{equation} \label{eq:Kyriakoulis_sv}
+    \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
+    X_1 - \overline{X}_n  & \dots & X_n - \overline{X}_n
+\end{pmatrix}^T
+\end{equation}
+
+and $T(w)$ is the $n \times n$ Toeplitz matrix of weights with the first column being $w = 
+\begin{pmatrix}
+    1 & w_1 & w_2 & \dots w_{n-1}
+\end{pmatrix}^T$.
+$T(w)$ is an $n \times n$ matrix which can be difficult to store.
+Therefore, \cite{heberle2017fast} computed $T(w)A$ directly using an FFT based algorithm.
+The algorithm requires embedding $T(w)$ in a $2n \times 2n$ circulation matrix $C(w^*)$.
+We write the spectral decomposition of $C(w^*)$ as $V\Lambda V^*$.
+A is extrapolated into a $2n \times p$ matrix $A^*$ such that
+\[
+    \hat{\Sigma}_{SV} = \dfrac{1}{n} A^T T(w) A = \dfrac{1}{n} A^T (C(w^*) A^*)_{1:n, :} = \dfrac{1}{n} A^T (V \Lambda V^* A^*)_{1:n, :}).
+\]
+The complete algorithm is as follows
+\\
+\begin{algorithm}[H]
+\DontPrintSemicolon
+\SetAlgoLined
+
+Construct $C(w^*) \textrm{ and } A^*$ from the MCMC samples.\\ Compute the DFT of the first column of $C(w^*)$. This gives the eigenvalues of $C(w^*)$.\;
+\For{$j = 1, 2, ..., p$}    
+    { 
+    Calculate $V^*A_j^*$ by FFT of $A_j$\;
+    Multiply the $i^{th}$ entry of the vector $V^* A_j^*$ with the eigenvalue $\lambda_i$ for all $i = 1, 2, ..., 2n$ in order to construct $\Lambda V^* A_j^*$.\;
+    Determine $C(w^*)A^* = V \Lambda V^* A_j^*$ by inverse FFT of $\Lambda V^* A_j^*$.\;
+    }
+ Select the first $n$ rows of $C(w^*)A^*$ to form $T(w)A$.\;
+ Premultiply by $A^T$ and divide by $n$.
+ \caption{Herberle's Algorithm}
+\end{algorithm}
+
+The algorithm has been implemented in the \texttt{R} package \texttt{mcmcse} for fast implementation of spectral variance estimators.
+We do a slight variation in the alternate formulation of SVE proposed by Kyriakoulis (2005) by centering the chain $\{X_{st}; \; t \in \mathbb{Z}\}$ around $\overline{\overline{X}}$ instead of $\overline{X}_s$ for all $s \in \{1, ..., m\}$.
+Herberle's algorithm is then applied on the formulation
+
+\[
+\hat{\Sigma}_{S,s} = \dfrac{1}{n}B^T T(w) B \qquad \textrm{ where } B = 
+\begin{pmatrix}
+    X_{s1} - \overline{\overline{X}} \; \dots \; X_{sn} - \overline{\overline{X}}
+\end{pmatrix}^T
+\].
+
+% subsubsection fast_implementation (end)
+
 \section{Effective sample size} \label{sec:ess}
@@
 The existing stopping rules rely on the strong consistency of the estimator of $\Sigma$.
-We will use the \textit{relative standard deviation fixed-volume sequential stopping rule} proposed in \cite{vats2019multivariate} when multivariate Markov chain central limit theorem holds.
-This stopping rule terminates the simulations on the basis of size of confidence interval relative to inherent variability in the target distribution.
-It terminates after the total number of samples, i.e.
-$mn$ exceed some pre-specified $n^*$ iterations to prevent pre-mature termination due to bad estimates of $\Sigma$ and $\Lambda$.
-The rule is given by
-
-\[
-\textrm{Volume of confidence region}^{1/p} + n^{-1} < \epsilon \abs{\Lambda_n}^{1/2p} 
-\]
-%
-where $\epsilon$ is the tolerance level, $\abs{.}$ denotes the determinant and $\Lambda_n$ is the sample covariance matrix given by
-%
-\[
-\dfrac{1}{mn-1}\sum_{s=1}^{m}\sum_{t=1}^{n}(X_{st} - \bar{\bar{X}})(X_{st} - \bar{\bar{X}})^T
-\]
-%
 The determinant of Monte Carlo standard error is called generalized variance in  \cite{wilks1932certain} and gives a metric for volume of confidence interval.
-\cite{vats2019multivariate} showed that if the estimator for $\Sigma$ is strongly consistent, the stopping rule is asymptotically valid, in that the confidence regions created at termination have the right coverage probability as $\epsilon \to 0$.
-Since $\hat{\Sigma}_{RSV}$ is a strongly consistent estimator of $\Sigma$, w
-
-\[
-\abs{\hat{\Sigma}_{RSV}}^{1/p} + (mn)^{-1} < \epsilon \abs{\Lambda_{mn}}^{1/2p}
-\]
-
-Another way to get more accurate stopping rule is to use RSV estimator for estimating Effective Sample Size (ESS) in multivariate settings.
-RSV estimator better captures the standard error of target distribution by considering the global sample mean across the Markov chains; which might otherwise get lost when considering a single localized slowly mixing Markov chain.
-We therefore define our ESS rule as
-
-\[
-\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{RSV}}}\right)^{1/p}
-\]
-
-When there is no correlation in Markov chain $\hat{\Sigma}_{RSV} = \Lambda_{mn}$ and therefore, ESS = $n$.
-Both the rules involve the ratio of generalized variances and therefore the relative standard deviation fixed-volume sequential stopping rule is asymptotically equivalent to stopping when ESS is greater than $W_{p,\alpha,\epsilon}$ which depends on dimension of state-space, level of confidence of the confidence region, and the relative precision required.
+
+We will use the multivariate effective sample size (m-ESS) by \cite{vats2019multivariate} to understand the effectiveness of simulations so far.
+m-ESS requires a strongly consistent estimator of $\Sigma$.
+G-SVE better captures the MCSE by considering the global sample mean across the Markov chains; which might otherwise get lost when considering a single localized slowly mixing Markov chain.
+We therefore define our ESS estimator as
+
+\[
+\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{G-SVE}}}\right)^{1/p}
+\]
+
+where $\Lambda_{mn}$ is the sample covariance of $mn$ samples. When there is no correlation in Markov chain $\hat{\Sigma}_{G} = \Lambda_{mn}$ and therefore, ESS = $n$.
 
@@
 
-In the following examples we compare the performance of asymptotic variance estimators (ASVE and RSVE) for Markov chain CLT.
-We will successfully illustrate that the replicated spectral variance estimator performs better than the average spectral variance estimator in terms of ESS calculations, coverage probabilities , and sample distribution of $\Sigma$.
-We will also show that in case of nicely mixing Markov chains, these estimators give almost equivalent results.
+There are only a handful of stochastic processes where the true autocovariance and $\Sigma$ are known.
+To compare the estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
+A more promising advantage of our estimators is observed when the target distribution is multi-modal.
+For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note} in section \ref{ex:boomerang}.
+Through this example, we will also show that in case of nicely mixing Markov chains, these estimators give almost equivalent results.
 As a consequence, while out replicated version of variance estimator is better in cases where the Markov chains do not explore the entire sample space in finite time, it is harmless to be used in cases where they do.
-{\color{red}about this new FFT based method for faster RSVE calculations}
+Lastly, we consider a real-life example of finding unknown locations of sensors using noisy distance data in section \ref{ex:sensor_post}.
+The posterior distribution is this case is marginally bimodal in all dimensions.
+All the examples have been selected to display some kind of \textit{sticky} nature in the Markov chains.
+In such scenario, we successfully show that our globally-centered estimators yield better results as compared to the classical autocovariance function, spectral variance estimator, and effective sample size.
 
@@
 
-We examine the vector autoregressive process of order 1 (VAR(1)) where the true autocovariance in known in closed form.
-We have already illustrated the better performance of R-ACF over traditional ACF on a slowly mixing VAR(1) process in Figure \ref{fig:var_acf_ccf}.
-Here we will examine the performance of RSV estimator on the same process.
-Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
+We examine the vector autoregressive process of order 1 (VAR(1)) where the true autocovariance in known in closed form. Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
 %
@@
 
+\begin{figure}
+ \begin{subfigure}{\textwidth}
+   \centering
+   \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
+   \caption{$n = 500$}
+   \label{subfig:acf-500}
+\end{subfigure}\\
+\begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
+  \caption{$n = 10^4$}
+  \label{subfig:acf-5e4}
+\end{subfigure}
+\caption{Autocorrelation plot for ACF and G-ACF for first chain out of two parallel Markov chains.
+First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
+\label{fig:var-acf}
+\end{figure}
+
 \begin{figure}[h]
@@
     \includegraphics[width = .5\textwidth]{plots/var-ess.pdf}
-    \caption{Running plots for $\hat{ESS}/mn$ calculated using ASV (black) and RSV (blue). The true $ESS/mn$ (red) is known.}
+    \caption{Running plots for $\hat{ESS}/mn$ calculated using ASV (black) and G-SVE (blue). The true $ESS/mn$ (red) is known.}
     \label{fig:var-ess}
@@
 
+%
 In Figure \ref{fig:boom-sp}, we demonstrate the ``sticky'' nature of the Markov chains.
@@
 By ten thousand samples, both the Markov chains have explored the two modes.
-This property will affect the single chain estimators like ACF.
-In Figure \ref{subfig:boom-acf_1e3}, the ACF is severely underestimated because the chain-1 has not jumped to the other mode.
-Whereas, in Figure \ref{subfig:boom-acf_1e4}, both ACF and R-ACF give almost similar results indicating that both modes have been explored by chain-1.
+This property will affect the estimation of ACF from a single chain.
+In Figure \ref{subfig:boom-acf_1e3}, the ACF is severely underestimated because the first chain has not jumped to the other mode.
+Whereas, in Figure \ref{subfig:boom-acf_1e4}, both ACF and G-ACF give almost similar results indicating that both modes have been explored by chain-1.
 
@@
     \end{subfigure}
-    \caption{ACF and R-ACF for component-1 of chain-1 at two different number of Monte Carlo samples. }
+    \caption{ACF and G-ACF for component-1 of chain-1 at two different number of Monte Carlo samples. }
     \label{fig:boom-acf}
@@
 In Table \ref{table:boom-coverage_1_3_8}, we give the coverage probabilities for $95 \%$ confidence interval for both the estimator.
-We can see that the RSVE gives better coverage probabilities for all the $n$.
-For smaller sample size, the coverage probability of RSVE is significantly higher than ASVE.
+We can see that the G-SVE gives better coverage probabilities for all the $n$.
+For smaller sample size, the coverage probability of G-SVE is significantly higher than A-SVE.
 As the number of samples per chain increases, they start coming closer due to the strong consistency of both the estimators.
@@
         \hline
-        & ASV & RSV & ASV & RSV\\
+        & ASV & G-SVE & ASV & G-SVE\\
         \hline
@@
 A good estimate of ESS is crucial to determine when to stop the simulations.
-We can see in Figure \ref{fig:run_ess} that for the first few thousand samples, ASVE gives misleadingly higher $\hat{ESS}/mn$ than RSVE.
+We can see in Figure \ref{fig:run_ess} that for the first few thousand samples, A-SVE gives misleadingly higher $\hat{ESS}/mn$ than G-SVE.
 This can cause us to stop the sampling before the sample space has been explored by the chains.
@@
 
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width = .7\textwidth]{plots/boom-ess.pdf}
-    \caption{Running plot for $\hat{ESS}/mn$ using ASV and RSV calculated for two chains (left) and five chains (right). The parameters for target distribution are $A == 1, \; B = 3, \; C = 8.$}
-    \label{fig:run_ess}
+\begin{figure}[h]
+    \centering
+
+    \begin{subfigure}[h]{.3\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-ess1.pdf}
+      \caption{$A = 1, \; B = 3, \; C = 8$}
+      \label{subfig:boom-ess1}
+    \end{subfigure}
+
+    \begin{subfigure}[h]{.3\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-ess2.pdf}
+      \caption{$A = 1, \; B=10, \; C = 7 $}
+      \label{subfig:boom-ess2}
+    \end{subfigure}
+    \caption{Running plot for $\hat{ESS}/mn$ using A-SVE and G-SVE calculated for two chains for two different parameterizations.}
+    \label{fig:boom-ess}
 \end{figure}
 
-To examine the performance of RSV for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$.
+To examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$.
 This is also a bimodal distribution, however, the two modes interact well with each other (Figure \ref{subfig:boom-pers_1_10_7}).
-In Figure \ref{fig:boom-ess_1_10_7}, we observe that both RSV and ASV give almost the same estimates for ESS.
+In Figure \ref{fig:boom-ess_1_10_7}, we observe that both G-SVE and A-SVE give almost the same estimates for ESS.
 Similar is the case with coverage probabilities in Table \ref{table:boom-coverage_1_10_7} for a $95\%$ confidence region.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width = .7\textwidth]{plots/boom-ess_1_10_7.pdf}
-    \caption{Running plot for $\hat{ESS}/mn$ using ASV and RSV calculated for two chains (left) and five chains (right). The parameters of target distribution are $A = 1, \; B = 10, \; C = 7$}
-    \label{fig:boom-ess_1_10_7}
-\end{figure}
 
@@
 We follow the Markov chain structure as described by \cite{tak2018repelling} and sample from the four bivariate conditionals for each sensor location using a Gibbs sampler.
-In their paper on Repelling Attractive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of three different sampling techniques namely - Metropolis, RAM and Tempered Transitions (TT).
+In their paper on Repelling AttG-tive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of three different sampling techniques namely - Metropolis, RAM and Tempered Transitions (TT).
 RAM is shown to improve the acceptance rate by a factor of at least 5.5 over Metropolis using the same jumping scale.
@@
     \includegraphics[width = .7\textwidth]{plots/sensor-trace.pdf}
-    \caption{Trace plots for the x-component of all four locations of the third chain.}
+    \caption{trace plots for the x-component of all four locations of the third chain.}
     \label{fig:sensor-trace-3}
@@
 
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth, height = 2in]{plots/sensor-acf-n1000.pdf}
-      \caption{$n = 10^3$}
-      \label{subfig:sensor-acf_n1e3}
-    \end{subfigure}
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth, height = 2in]{plots/sensor-acf-n1e5.pdf}
-      \caption{$n = 10^5$}
-      \label{subfig:sensor-acf_n1e5}
-    \end{subfigure}
-    \caption{ACF and R-ACF for component-3 of chain-3 at two different number of Monte Carlo samples. }
-    \label{fig:sensor-acf}
-\end{figure}
+% \begin{figure}[h]
+%     \centering
+%     \begin{subfigure}[h]{.8\textwidth}
+%       \centering
+%       \includegraphics[width = \textwidth, height = 2in]{plots/sensoG-ACF-n1000.pdf}
+%       \caption{$n = 10^3$}
+%       \label{subfig:sensoG-ACF_n1e3}
+%     \end{subfigure}
+%     \begin{subfigure}[h]{.8\textwidth}
+%       \centering
+%       \includegraphics[width = \textwidth, height = 2in]{plots/sensoG-ACF-n1e5.pdf}
+%       \caption{$n = 10^5$}
+%       \label{subfig:sensoG-ACF_n1e5}
+%     \end{subfigure}
+%     \caption{ACF and G-ACF for component-3 of chain-3 at two different number of Monte Carlo samples. }
+%     \label{fig:sensoG-ACF}
+% \end{figure}
 
@@
 The Markov chains get stuck at a particular mode for a long time before jumping to the other mode.
-Figure \ref{fig:sensor-acf} shows the effect of this "sticky" nature of Markov chains over the autocorrelations centered around the local and global mean.
+Figure \ref{fig:sensoG-ACF} shows the effect of this "sticky" nature of Markov chains over the autocorrelations centered around the local and global mean.
 For a small sample size of 1000, it can be seen that the third chain has not explored the sample space well.
@@
 
-\begin{proof}[Proof of Theorem~\ref{th:RAC_expec}]
-\begin{align*}
-    & \hat{\Gamma}_{RAC,s}(k) \\
+\begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
+\begin{align*}
+    & \hat{\Gamma}_{G-,s}(k) \\
    & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
@@
 \begin{align*}
-    & \E \left[\hat{\Gamma}_{RAC,s}(k) \right] \\
+    & \E \left[\hat{\Gamma}_{G-,s}(k) \right] \\
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
@@
 %
- We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{RAC,s}(k)$ can then broken down as following,
- \begin{equation} \label{eq:rac_expec_breakdown}
-     \mathbb{E}\left[\hat{\Gamma}_{RAC}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
+ We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{G-,s}(k)$ can then broken down as following,
+ \begin{equation} \label{eq:G-_expec_breakdown}
+     \mathbb{E}\left[\hat{\Gamma}_{G-}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
  \end{equation}
@@
 \begin{align*}
-& \E \left[ \hat{\Gamma}_{RAC,s}^{ii}\right]\\
+& \E \left[ \hat{\Gamma}_{G-,s}^{ii}\right]\\
 & = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma^{ii}(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma^{ii}(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
@@
 \begin{align*}
-    \hat{\Gamma}_{RAC}(0) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{RAC,s}(0) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{st} - \bar{\bar{X}}\right)^T\\
+    \hat{\Gamma}_{G-}(0) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{G-,s}(0) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{st} - \bar{\bar{X}}\right)^T\\
     &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{st} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
@@
 \end{align*}
-Using \eqref{eq:priestly} and \eqref{eq:acf_4} the expectation of $\hat{\Gamma}_{RAC}(0)$ can be written as 
-%
-\begin{align*}
-    \mathbb{E} \left[\hat{\Gamma}_{RAC}(0) \right] &= \E\left[\hat{\Gamma}_1(0) \right] + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) \\
+Using \eqref{eq:priestly} and \eqref{eq:acf_4} the expectation of $\hat{\Gamma}_{G-}(0)$ can be written as 
+%
+\begin{align*}
+    \mathbb{E} \left[\hat{\Gamma}_{G-}(0) \right] &= \E\left[\hat{\Gamma}_1(0) \right] + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) \\
     & = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\,.
@@
 \end{align*}
-\begin{lemma} \label{lemma:rsv_breakdown}
-For the RSV estimator $\hat{\Sigma}_{RSV}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2$ and 
+\begin{lemma} \label{lemma:G-SVE_breakdown}
+For the G-SVE estimator $\hat{\Sigma}_{G-SVE}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2$ and 
 \[
@@
 \begin{align*}
-&\hat{\Sigma}_{RSV}^{ij} \\
+&\hat{\Sigma}_{G-SVE}^{ij} \\
 &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st}-\bar{\bar{X}} \right)_i \left(X_{s(t+k)}-\bar{\bar{X}} \right)_j\\
@@
 \[
-\left|\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
+\left|\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
 \]
@@
 % Equation~\eqref{eq:strong_consis_term-2} has the same order as equation \eqref{eq:strong_consis_term-1}, i.e. $\mathcal{O}\left(b_n \log \log n/n\right) \to 0 \textrm{ as } n \to \infty$.
-% We have already shown that $M_1$ and $M_2$ converge to 0 almost surely $\implies \hat{\Sigma}_{RSV} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$.
+% We have already shown that $M_1$ and $M_2$ converge to 0 almost surely $\implies \hat{\Sigma}_{G-SVE} \xrightarrow{a.s.} \tilde{\Sigma}$ as $n \to \infty$.
 Now we can find the functions $g_1(n), g_2(n) \textrm{ and, } g_3(n)$ by adding \eqref{eq:strong_consis_term-1} and \eqref{eq:strong_consis_term-2}.
@@
 %
-Using the above and  Lemma~\ref{lemma:rsv_breakdown}, 
-\begin{align*}
-\left|\hat{\Sigma}_{RSV}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right| \\
-& \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:RSV_full_decomp}
-\end{align*}
-%
-By Assumption~\ref{ass:sve_consis}, the first term goes to with probability 1 and by Lemma~\ref{lemma:rsv_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
+Using the above and  Lemma~\ref{lemma:G-SVE_breakdown}, 
+\begin{align*}
+\left|\hat{\Sigma}_{G-SVE}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right| \\
+& \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
+\end{align*}
+%
+By Assumption~\ref{ass:sve_consis}, the first term goes to with probability 1 and by Lemma~\ref{lemma:G-SVE_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
 What is left to show is that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1
@@
 \end{align*}
-Thus, in \eqref{eq:RSV_full_decomp}, each of the terms goes to 0 with probability 1, and $\hat{\Sigma}_{RSV}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. 
+Thus, in \eqref{eq:G-SVE_full_decomp}, each of the terms goes to 0 with probability 1, and $\hat{\Sigma}_{G-SVE}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. 
 \end{proof}
 
-\subsection{RSV Bias}
-
-\begin{proof}[Proof of theorem \ref{th:rsv_bias}]
-The convoluted end effect terms in theorem \ref{th:RAC_expec} are all essentially $\mathcal{O}(1/n)$.
+\subsection{G-SVE Bias}
+
+\begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
+The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
 We are interested in finding the asymptotic bias here.
-Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:rac_expec_breakdown} as,
-\begin{align*}
-&\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right]\\
+Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:G-_expec_breakdown} as,
+\begin{align*}
+&\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right]\\
 &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:rac_bias2}  \,.
-\end{align*}
-%
-% \begin{equation} \label{eq:rac_bias2}
-% \mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
+& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:G-_bias2}  \,.
+\end{align*}
+%
+% \begin{equation} \label{eq:G-_bias2}
+% \mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
 % \end{equation}
@@
 By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.
-Consider the RSV estimator,
-\begin{align*}
-    &\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right]\\
-    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{RAC}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+Consider the G-SVE estimator,
+\begin{align*}
+    &\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right]\\
+    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
     &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\inf}\Gamma(k)\\
@@
 \[
-\mathbb{E} \left[\hat{\Sigma}_{RSV} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
+\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
 \]
@@
  % We have shown that all, but one, terms are $o(1/b_n^q)$.
-Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{RAC} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
+Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
 This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu$ in our replicated autovariance estimator.
-Similar to theorem \ref{th:RAC_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
+Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
 \end{proof}
@@
 
-\begin{proof}[Proof of Theorem~\ref{th:rsv_variance}]
+\begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
  Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
 \begin{equation}
-\label{eq:rsv_asv_consis}
- \left|\hat{\Sigma}_{RSV} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
+\label{eq:G-SVE_asv_consis}
+ \left|\hat{\Sigma}_{G-SVE} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
 \end{equation}
@@
 \begin{align*}
- &\left| \hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right|\\
+ &\left| \hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right|\\
  & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t=1}^{n-|k|}   \left[ \left( \dfrac{(X_{st} - \mu)_i(\mu-\bar{\bar{X}})_j}{n}\right)+ \left(\dfrac{(\mu-\bar{\bar{X}})_i(X_{s(t+k)}-\mu)_j}{n}\right) \right] \right.\\
@@
 
-By \eqref{eq:rsv_asv_consis}, there exists an $N_0$ such that
-\begin{align*}
-\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
-& \leq \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
+By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that
+\begin{align*}
+\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
+& \leq \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
 & := g_n^*(X_{11}, \dots, X_{1n}, \dots, X_{m1}, \dots, X_{mn})\,.
@@
 \[
-\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
+\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
 \]
@@
 \label{eq:squared_mean_diff}
-  \E \left[\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
+  \E \left[\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
 \end{equation}
@@
 \[
-\xi\left(\hat{\Sigma}_{RSV}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
+\xi\left(\hat{\Sigma}_{G-SVE}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
 \]
@@
 \begin{align*}
-\left|  \xi\left(\hat{\Sigma}_{RSV}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\
-& \leq \E\left[\left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\
+\left|  \xi\left(\hat{\Sigma}_{G-SVE}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\
+& \leq \E\left[\left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\
 & = o(1) + 2\left(o(1) \left(O\left( \dfrac{b_n}{n}\right)  + o\left( \dfrac{b_n}{n}\right) \right)  \right) \\ 
@@
 \begin{align*}
- & \Var\left(\hat{\Sigma}_{RSV}^{ij} \right)\\
-  & = \E \left[ \left(\hat{\Sigma}_{RSV}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
-& = \E \left[ \left(\hat{\Sigma}_{RSV}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right)^2 \right]\\
-& = \E\left[ \left( \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right)  \right)^2 \right] \\
-& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right) \right)^2 \right] \\
-& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right)\right] + 2 \E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{RSV}^{ij}  \right] \right)\right]\\
-& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{RSV}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{RSV}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
+ & \Var\left(\hat{\Sigma}_{G-SVE}^{ij} \right)\\
+  & = \E \left[ \left(\hat{\Sigma}_{G-SVE}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
+& = \E \left[ \left(\hat{\Sigma}_{G-SVE}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right)^2 \right]\\
+& = \E\left[ \left( \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right)  \right)^2 \right] \\
+& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right) \right)^2 \right] \\
+& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)\right] + 2 \E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right)\right]\\
+& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
 & = \Var\left( \tilde{\Sigma}^{ij}\right) + o(1)
@@
 \end{equation}
-Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{RSV}$ gives the result of the theorem.
+Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{G-SVE}$ gives the result of the theorem.
 
@@
     \includegraphics[width = 0.8\textwidth, height = 4in]{plots/spatio-acf.pdf}
-    \caption{ACF and R-ACF for first component of first chain.
-ACF underestimates the autocorrelations for $10^3$ samples (top) whereas R-ACF gives more realistic estimates.
+    \caption{ACF and G-ACF for first component of first chain.
+ACF underestimates the autocorrelations for $10^3$ samples (top) whereas G-ACF gives more realistic estimates.
 They perform alike for $10^5$ samples (bottom).}
-    \label{fig:spatio-acf_racfl}
+    \label{fig:spatio-acf_G-fl}
 \end{figure}
@@
 We run two parallel Markov chains starting from random poits.
-In Figure \ref{fig:spatio-acf_racfl}, it is evident that the chains have not explored the sample space well.
-Hence for $10^3$ samples ACF severely underestimates the autocorrelations whereas R-ACF gives more realistic estimates.
+In Figure \ref{fig:spatio-acf_G-fl}, it is evident that the chains have not explored the sample space well.
+Hence for $10^3$ samples ACF severely underestimates the autocorrelations whereas G-ACF gives more realistic estimates.
 For a large sample size of $10^5$, the Markov chains have mixed properly and therefore, both the estimators are approximately alike.
@@
 Table (blah) shows the population parameters we are interested in estimating using MCMC methods.
-The race and sex parameters are estimated as proportion of whites and females in the sample respectively.
-We start two parallel Markov chains from two students belonging to different races and study its impacts on the average features of their immediate social group.
+The G-e and sex parameters are estimated as proportion of whites and females in the sample respectively.
+We start two parallel Markov chains from two students belonging to different G-es and study its impacts on the average features of their immediate social group.
 It is hypothesized that students from certain communities tend to engage more with students of same or other marginally represented communities.

### 2020-07-22 Paper/main.tex
Modified the plots for GaussianMix a little.

@@
 \newcommand{\Var}{\text{Var}}
+\newcommand{\Cov}{\text{Cov}}
 \newcommand{\X}{\mathcal{X}}
@@
 Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones.
-Therefore, it becomes imperative for an MCMC pG-titioner to have an idea about underlying dependence structure in the Markov chains.
-Autocovariance function (ACF) chaG-terizes this dependence for a stationary Markov chain.
+Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains.
+Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain.
 Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e.
@@
 \[
-    \Gamma(k) = Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
+    \Gamma(k) = \Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
 \]

### 2020-07-22 Paper/main.tex
Day one of clean-up ends

@@
 \usepackage{amssymb,amsthm,amsmath}
-\usepackage{commath}
+\usepackage{commath,hyperref}
 \usepackage{enumerate,xcolor}
@@
    \centering
-   \includegraphics[width=.8\linewidth]{plots/gaussian-acf_n1e4.pdf}
+   \includegraphics[width=.9\linewidth]{plots/gaussian-acf_n1e4.pdf}
    \caption{$n = 10^4$}
@@
    \centering
-   \includegraphics[width=.8\linewidth]{plots/gaussian-acf_n1e5.pdf} 
+   \includegraphics[width=.9\linewidth]{plots/gaussian-acf_n1e5.pdf} 
    \caption{$n = 10^5$}
@@
 \[
-\hat{\Gamma}_{G}(k) = \dfrac{1}{mn} \sum_{s=1}^{m}\sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
+\hat{\Gamma}_{G,s}(k) = \dfrac{1}{n} \sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
 \]
@@
 
-\subsection{Theoretical results} % (fold)
-\label{sub:theoretical_results}
+% \subsection{Theoretical results} % (fold)
+% \label{sub:theoretical_results}
 
@@
 We denote $\Phi^{(1)} \textrm{ by } \Phi$.
-\begin{theorem} \label{th:G-_expec}
-   \[
-   \mathbb{E}[\hat{\Gamma}_{G}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
-   \]
+
+The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
+\begin{theorem} \label{th:G-_expec} Under stationarity,
+\[
+   \mathbb{E} \left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
+\]
+and consequently,
+\[
+\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,. 
+\]
+   % \[
+   % \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
+   % \]
 \end{theorem}
 
-\begin{proof}
- The estimator for autocovariance with divisor $n$ is suggested by \cite{parzen1961approach} for its lesser mean square error despite having greater bias than the unbiased estimator with an $n - \abs{k}$ divisor.
- We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as
-
- \begin{equation} \label{eq:priestly}
-     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
- \right)
- \end{equation}
-
-By proposition 1 in \cite{song1995optimal} 
-\begin{equation} \label{eq:song}
-\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
-\end{equation}
-
-As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{G-}$ into four parts for all $k \geq 1$ as:
- \[
- \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
- \]
-%
-where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
-The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.
+% \begin{proof}
+%  The estimator for autocovariance with divisor $n$ is suggested by \cite{parzen1961approach} for its lesser mean square error despite having greater bias than the unbiased estimator with an $n - \abs{k}$ divisor.
+%  We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as
+
+%  \begin{equation} \label{eq:priestly}
+%      \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
+%  \right)
+%  \end{equation}
+
+% By proposition 1 in \cite{song1995optimal} 
+% \begin{equation} \label{eq:song}
+% \Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
+% \end{equation}
+
+% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{G-}$ into four parts for all $k \geq 1$ as:
+%  \[
+%  \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
+%  \]
+% %
+% where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
+% The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.
 The complete proof evaluating the expectation values of last three terms can be found in Appendix subsection \ref{appendix:bias}.
-\end{proof}
-
-\begin{remark} \label{rmrk:exp_G-f_minus_acf}
-Using theorem \ref{th:G_expec} and equation \ref{eq:priestly},
-\[
-\mathbb{E}[\hat{\Gamma}_{G}(k) - \hat{\Gamma}(k)] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
-\]
-We know that the sample autocovariance $\hat{\Gamma}(k)$ underestimates the truth due to a negative bias of $\abs{k}\Gamma(k)/n$ for finite $n$.
+% \end{proof}
+
+% \begin{remark} \label{rmrk:exp_G-f_minus_acf}
+% Using theorem \ref{th:G_expec} and equation \ref{eq:priestly},
+% \[
+% \mathbb{E} \left[\hat{\Gamma}_{G}(k) - \hat{\Gamma}(k) \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
+% \]
+% We know that the sample autocovariance $\hat{\Gamma}(k)$ underestimates the truth due to a negative bias of $\abs{k}\Gamma(k)/n$ for finite $n$.
 However, in practice, it is preferred to overestimate the autocovariance for finite $n$ than to underestimate it in order to have a more realistic idea about the correlation in a Markov chain at a particular lag.
@@
 
-\end{remark}
+% \end{remark}
+
+When $m = 1$, $\hat{\Gamma}_G(k)$ corresponds to $\hat{\Gamma}(k)$, the expectation of which can be found in \cite{priestley1981spectral}.
+Theorem~\ref{th:G-_expec} implies that the globally-centered autocovariances are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered autocovariances.
+The consequences of this are particularly pertinent for the diagonals of $\Gamma$.
+Special interest is also in the lag-0 autocovariance, that is, the variance of the target distribution.
 
@@
 \[
-\mathbb{E}[\hat{\Gamma}_{G}(0)] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
+\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
 \]
@@
 
-\begin{proof}
- The proof is in Appendix subsection \ref{appendix:bias}.
-\end{proof}
+\subsection{Autocorrelation} % (fold)
+\label{sub:autocorrelation}
+
+% subsection autocorrelation (end)
+For any component $i$, the autocorrelation is
+\[
+\rho^{(i)}(k) = \dfrac{\Gamma^{(i)}(k)}{\Gamma^{(i)}(0)}\,,
+\]
+and is particularly useful for visualizing the serial correlation in components of the Markov chain.
+The typical estimate of the autocorrelation is constructed from  locally-centered autocovariance estimates which as was demonstrated in Section~\ref{sec:intro} can significantly underestimate the autocorrelation.
+\[
+\hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}
+\]
+{\color{blue} Add more about autocorrelation}
+
+% \begin{proof}
+%  The proof is in Appendix subsection \ref{appendix:bias}.
+% \end{proof}
 
@@
 
-\begin{proof}
-We complete the proof by showing that $\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$.
+% \begin{proof}
+% We complete the proof by showing that $\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$.
 We will show that
 
-\[
-\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
-\]
-where $D$ is the finite random variable associated with SIP. We will show that
-\begin{align*}
-    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]
-\end{align*}
-
-Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we can finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$.
+% \[
+% \hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
+% \]
+% where $D$ is the finite random variable associated with SIP. We will show that
+% \begin{align*}
+%     g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
+%     g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
+%     g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]
+% \end{align*}
+
+% Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we can finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$.
 The proof is in Appendix subsection \ref{appendix:strong_consis}
-\end{proof}
+% \end{proof}
 
@@
 
-\begin{proof}
-\[
-\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
-\]
-
-Using theorem \ref{th:G-ACF_expec}, we can write the expectation of $\hat{\Gamma}_{G}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
-The proof is given in the Appendix subsection \ref{appendix:bias}.
-\end{proof}
+% \begin{proof}
+% \[
+% \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
+% \]
+
+% Using theorem \ref{th:G-ACF_expec}, we can write the expectation of $\hat{\Gamma}_{G}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
+% The proof is given in the Appendix subsection \ref{appendix:bias}.
+% \end{proof}
 
@@
 
-\begin{proof}
-Recall that $\tilde{\Sigma}$ is the averaged pseudo spectral variance estimator which uses the unobserved mean.
+% \begin{proof}
+% Recall that $\tilde{\Sigma}$ is the averaged pseudo spectral variance estimator which uses the unobserved mean.
 Further, let $\tilde{\Sigma}^{ij}$ be the $(i,j)^{th}$ element of this matrix.
@@
 The proof is in Appendix subsection \ref{appendix:variance}
-\end{proof}
+% \end{proof}
 
@@
 
-\subsection{Bias of autocovariance} \label{appendix:bias}
+\subsection{Bias of Theorem~\ref{th:G-_expec}} 
+\label{appendix:bias}
 
@@
 \begin{align*}
-    & \hat{\Gamma}_{G-,s}(k) \\
-   & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
+\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
     &= \left[\dfrac{1}{n} \sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\
@@
      &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
-     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
+     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
@@
     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
-    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
+    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
     &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
@@
 \begin{align*}
-\mathbb{E}\left[ \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{s}\bar{X}_{s}^{T} - \bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{s}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
-&= \mathbb{E}\left[ \bar{X}_{s}\bar{X}_{s}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
-&= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
+\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
+% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
 &= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
@@
 %
+Additionally, the locally-centered autocovariance exhibits the following expectation
+ \begin{equation} \label{eq:priestly}
+     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
+ \right)\,.
+ \end{equation}
+%
 Using \eqref{eq:priestly}, \eqref{eq:acf_2}, \eqref{eq:acf_3}, and \eqref{eq:acf_4} in \eqref{eq:acf_breakdown},
 \begin{align*}
-    & \E \left[\hat{\Gamma}_{G-,s}(k) \right] \\
+    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - {\color{red}\dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right)} + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
     &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m}\,.

### 2020-07-23 Paper/main.tex
Morning cleanup, heading to office

@@
 %
- We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{G-,s}(k)$ can then broken down as following,
+ We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
  \begin{equation} \label{eq:G-_expec_breakdown}
-     \mathbb{E}\left[\hat{\Gamma}_{G-}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
+     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
  \end{equation}
@@
 We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$.
-Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = \mathcal{O}(1/n)$.
+Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\color{red}\mathcal{O}}(1/n)$.
 For a diagonal element of $\Gamma$,
@@
 \begin{align*}
-& \E \left[ \hat{\Gamma}_{G-,s}^{ii}\right]\\
-& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma^{ii}(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma^{ii}(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
+& \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
+& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
 \end{align*}
@@
 
-\begin{proof}[Proof of corollary \ref{cor:lag0_expectation}]
-
-\begin{align*}
-    \hat{\Gamma}_{G-}(0) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{G-,s}(0) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{st} - \bar{\bar{X}}\right)^T\\
-    &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{st} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(0)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
-\end{align*}
-Using \eqref{eq:priestly} and \eqref{eq:acf_4} the expectation of $\hat{\Gamma}_{G-}(0)$ can be written as 
-%
-\begin{align*}
-    \mathbb{E} \left[\hat{\Gamma}_{G-}(0) \right] &= \E\left[\hat{\Gamma}_1(0) \right] + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) \\
-    & = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\,.
-    % &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
-\end{align*}
-
-\end{proof}
+% \begin{proof}[Proof of corollary \ref{cor:lag0_expectation}]
+
+% \begin{align*}
+%     \hat{\Gamma}_{G-}(0) &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_{G-,s}(0) = \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n}  \left(X_{st} - \bar{\bar{X}}\right)  \left(X_{st} - \bar{\bar{X}}\right)^T\\
+%     &= \left[\dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{n} \left(X_{st} - \bar{X}_s \right)  \left(X_{st} - \bar{X}_s \right)^T\right] + \left[\dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right) \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+%     &= \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(0)  + \dfrac{1}{m}\sum_{s=1}^{m} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,.
+% \end{align*}
+% Using \eqref{eq:priestly} and \eqref{eq:acf_4} the expectation of $\hat{\Gamma}_{G-}(0)$ can be written as 
+% %
+% \begin{align*}
+%     \mathbb{E} \left[\hat{\Gamma}_{G-}(0) \right] &= \E\left[\hat{\Gamma}_1(0) \right] + \left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1) \\
+%     & = \Gamma(k) - \dfrac{1}{m}\Var(\bar{X}_1)\,.
+%     % &= \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
+% \end{align*}
+
+% \end{proof}
 
@@
 
-We are going to consider a class of pseudo spectral variance estimator denoted by $\tilde{\Sigma}$ which uses data centered around the unobserved actual mean $\mu$.
-Such pseudo covariance estimator and autocovariance estimator for the $j^{th}$ chain is denoted by $\tilde{\Sigma}_s$ and $\tilde{\Gamma}_s$ respectively.
-
+Consider pseudo spectral variance estimators for the $s$th chain, denoted by $\tilde{\Sigma}_s$ which uses data centered around the unobserved actual mean $\mu$:
 \begin{align*}
@@
 %
-The average pseudo spectral variance estimator (APSVE) is given by
+The average pseudo spectral variance estimator is
 \[
@@
 \end{align*}
+
 \begin{lemma} \label{lemma:G-SVE_breakdown}
-For the G-SVE estimator $\hat{\Sigma}_{G-SVE}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2$ and 
-\[
-|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,
+For the G-SVE estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2$ and 
+\[
+|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,,
 \]
@@
 \begin{align*}
-&\hat{\Sigma}_{G-SVE}^{ij} \\
-&= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st}-\bar{\bar{X}} \right)_i \left(X_{s(t+k)}-\bar{\bar{X}} \right)_j\\
-&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left[  \left\{\left(X_{st}-\mu \right)_i + \left(\mu-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_j \right \} \right]\\
+\hat{\Sigma}_{G}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st}-\bar{\bar{X}} \right)_i \left(X_{s(t+k)}-\bar{\bar{X}} \right)_j\\
+% &= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left[  \left\{\left(X_{st}-\mu \right)_i + \left(\mu-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_j \right \} \right]\\
 &= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left[ \left(X_{st}-\mu \right)_i  \left(X_{s(t+k)}-\mu \right)_j+  \left(X_{st} - \mu \right)_i    \left(\mu - \bar{\bar{X}} \right)_j \right.
@@
 \[
-\left|\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
+\left|\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
 \]

### 2020-07-23 Paper/main.tex
Down to 32 pages, trimmed the edges off the appendix. Done for the day most likely

@@
 Then, the autocovariance function at lag-$k$ is defined as
-
+%
 \[
@@
 \begin{theorem} \label{th:G-SVE_variance}
- If Assumption \ref{ass:variance_cal} hold, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+ If Assumption \ref{ass:variance_cal} holds, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
 \end{theorem}
@@
 The alternate formulation for MSVE is given by
-
-\begin{equation} \label{eq:Kyriakoulis_sv}
+%
+\[
     \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
@@
 \end{pmatrix}^T
-\end{equation}
-
-and $T(w)$ is the $n \times n$ Toeplitz matrix of weights with the first column being $w = 
-\begin{pmatrix}
-    1 & w_1 & w_2 & \dots w_{n-1}
-\end{pmatrix}^T$.
+\]
+
+and $T(w)$ is the $n \times n$ Toeplitz matrix of weights with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$
+%  $w = 
+% \begin{pmatrix}
+%     1 & w_1 & w_2 & \dots w_{n-1}
+% \end{pmatrix}^T$.
 $T(w)$ is an $n \times n$ matrix which can be difficult to store.
@@
 The complete algorithm is as follows
-\\
-\begin{algorithm}[H]
+
+\begin{algorithm}[htbp]
 \DontPrintSemicolon
 \SetAlgoLined
-
 Construct $C(w^*) \textrm{ and } A^*$ from the MCMC samples.\\ Compute the DFT of the first column of $C(w^*)$. This gives the eigenvalues of $C(w^*)$.\;
@@
 \[
-\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{G-SVE}}}\right)^{1/p}
+\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{G}}}\right)^{1/p}
 \]
@@
 
-\begin{figure}
+\begin{figure}[htbp]
  \begin{subfigure}{\textwidth}
    \centering
-   \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
+   \includegraphics[width=.6\linewidth]{plots/acf,n=500.pdf}
    \caption{$n = 500$}
@@
   \centering
-  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
+  \includegraphics[width=.6\linewidth]{plots/acf,n=10000.pdf} 
   \caption{$n = 10^4$}
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = .5\textwidth]{plots/var-ess.pdf}
-    \caption{Running plots for $\hat{ESS}/mn$ calculated using ASV (black) and G-SVE (blue). The true $ESS/mn$ (red) is known.}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = .35\textwidth]{plots/var-ess.pdf}
+    \caption{Running plots for $\hat{\text{ESS}}/mn$ calculated using ASV and G-SVE with the truth.}
     \label{fig:var-ess}
@@
 \[
-f(x, y) \propto \exp\left(-\dfrac{1}{2}[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y]\right)
+f(x, y) \propto \exp\left(-\dfrac{1}{2} \left[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y  \right]\right)
 \]
@@
 \begin{comment}
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
@@
       \centering
-      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf,n=1000.pdf}
+      \includegraphics[width = .8\textwidth]{plots/boom-acf,n=1000.pdf}
       \caption{$n = 1000$}
@@
       \centering
-      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf,n=50000.pdf}
+      \includegraphics[width = .8\textwidth]{plots/boom-acf,n=50000.pdf}
       \caption{$n = 50000$}
@@
 
-\begin{table}[h]
-\centering
-    \begin{tabular}{p{1cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}}
+\begin{table}[htbp]
+\centering
+    \begin{tabular}{|c|l|l|l|l|}
     % \toprule
-        n & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
+    \hline
+        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
         \hline
@@
         \hline
-        $10^3$ & 0.612 & 0.689 & 0.602 & 0.753   \\
-        $2\cdot10^3$ & 0.693 & 0.751 & 0.735 & 0.827 \\
-        $5 \cdot 10^3$  & 0.826 & 0.854 & 0.847 & 0.880 \\
-        $10^4$  & 0.862 & 0.868 & 0.884 & 0.907 \\
-        $2 \cdot 10^4$ & 0.899 & 0.906 & 0.922 & 0.934  \\
+        $1000$ & 0.612 & 0.689 & 0.602 & 0.753   \\
+        $2000$ & 0.693 & 0.751 & 0.735 & 0.827 \\
+        $5000$  & 0.826 & 0.854 & 0.847 & 0.880 \\
+        $10000$  & 0.862 & 0.868 & 0.884 & 0.907 \\
+        $20000$ & 0.899 & 0.906 & 0.922 & 0.934  \\ \hline
     % \bottomrule
@@
       \centering
-      \includegraphics[width = \textwidth]{plots/boom-ess1.pdf}
+      \includegraphics[width = 1.1\textwidth]{plots/boom-ess1.pdf}
       \caption{$A = 1, \; B = 3, \; C = 8$}
       \label{subfig:boom-ess1}
-    \end{subfigure}
-
+    \end{subfigure} \hspace{1cm}
     \begin{subfigure}[h]{.3\textwidth}
       \centering
-      \includegraphics[width = \textwidth]{plots/boom-ess2.pdf}
+      \includegraphics[width = 1.1\textwidth]{plots/boom-ess2.pdf}
       \caption{$A = 1, \; B=10, \; C = 7 $}
@@
     \end{subfigure}
-    \caption{Running plot for $\hat{ESS}/mn$ using A-SVE and G-SVE calculated for two chains for two different parameterizations.}
+    \caption{Running plot for $\hat{\text{ESS}}/mn$ using ASV and G-SVE  for $m = 2$.}
     \label{fig:boom-ess}
@@
         \hline
-        $10^3$ & 0.873 & 0.884 & 0.875 & 0.898   \\
-        $2\cdot10^3$ & 0.881 &  0.888 & 0.897    & 0.914     \\
-        $5 \cdot 10^3$  & 0.902 & 0.908 &  0.919 & 0.929\\
-        $10^4$  & 0.923 & 0.927 & 0.925 & 0.926 \\
-        $5 \cdot 10^4$ & 0.951& 0.952 & 0.939 & 0.939  \\
+        $10000$ & 0.873 & 0.884 & 0.875 & 0.898   \\
+        $2000$ & 0.881 &  0.888 & 0.897    & 0.914     \\
+        $5000$  & 0.902 & 0.908 &  0.919 & 0.929\\
+        $10000$  & 0.923 & 0.927 & 0.925 & 0.926 \\
+        $50000$ & 0.951& 0.952 & 0.939 & 0.939  \\ \hline
     % \bottomrule
@@
 This problem is specifically interesting in our case because the joint posterior distribution for missing sensor locations is multi-modal.
-\\
 
@@
 The probability model is then,
-
-\begin{align*}
-    z_{ij}|x_1, ..., x_6 &\sim Bernoulli\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
-    y_{ij}| w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
-\end{align*}
-
+%
+\begin{align*}
+    z_{ij} \mid x_1, ..., x_6 &\ sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
+    y_{ij} \mid w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
+\end{align*}
+%
 \cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$.
@@
 The likelihood function is then,
-
+%
 \begin{multline*}
@@
 
-\section{Preliminaries} \label{apdx:preliminaries}
+\section{Appendix}  \label{sec:appendix}
+\subsection{Preliminaries} \label{apdx:preliminaries}
 
@@
 
-\section{Proof of Theorems} \label{appendix:A}
-
-\subsection{Bias of Theorem~\ref{th:G-_expec}} 
+% \section{Proof of Theorems} \label{appendix:A}
+
+\subsection{Proof of Theorem~\ref{th:G-_expec}} 
 \label{appendix:bias}
 
+ % \begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
 % \begin{lemma} \label{lemma:bias1}
@@
 
-\begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
 \begin{align*}
@@
 In the presence of positive correlation, the leftover term is positive.
-\end{proof}
 
@@
   \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| = \dfrac{1}{mn}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| \\
-  &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
+  % &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
   & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
   &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
-  &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
+  &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(n)|^2\right)^{1/2}\\
   & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\,. \numberthis \label{eq:xbars_bound}
@@
 & |M_1| \\ 
-   & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\
-   & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|} \left(X_{st} - \mu \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-|k|} \left(\mu-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu \right)_j\right|} \right]\right\}\\
+   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\
+   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|} \left(X_{st} - \mu \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-|k|} \left(\mu-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu \right)_j\right|} \right]\right\}\\
     & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t=1}^{n-|k|}(X_{st}- \mu)_i\right|\left|(\mu-\bar{\bar{X}})_j\right|+ \dfrac{1}{n}\left|(\mu-\bar{\bar{X}})_i\right|\left|\sum_{t=1}^{n-|k|}(X_{j(t+k)}-\mu)_j\right|\right]\right\}\\
@@
 |M_1|
-    & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \\
-    & \quad + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty} \\
-    &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]\\
-    & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\\
+    & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \right]  + 2(2b_n - 1) \|\bar{X}_1 - \mu\|_{\infty} \\
+    &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{X}_1 - \mu\|_{\infty}  \right]\\
+    % & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\\
     & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,.
@@
    |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu - \bar{\bar{X}} \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
-    & \leq\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right]\\
-    &< \|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
-    &= b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+    & \leq\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+    % &= b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
     & \leq b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w(x)|dx \\
@@
 \begin{align*}
-  &|M_1 + M_2|\\
-  & \leq |M_1| + |M_2|\\
-  & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 + Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2\\
-  & = D^2g_1(n) + D g_2(n) + g_3(n)\,
+|M_1 + M_2  & \leq |M_1| + |M_2|
+  % & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 + Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2\\
+   = D^2g_1(n) + D g_2(n) + g_3(n)\,,
 \end{align*}
@@
 \end{align*}
-Under our assumptions, $b_n\log \log n /n \to 0$ and $\psi(n) = o(\sqrt{n \log \log n})$.
-Consequently, $b_n \psi^2(n)/n^2 \to 0$, $\psi^2(n)/n^2 \to 0$, ${b_n\psi(n)\sqrt{n\log \log n}/n^2} \to 0$, and $\psi(n) \sqrt{n \log \log n}/n^2 \to 0$.
+Under our assumptions, 
+$b_n\log \log n /n \to 0$ and $\psi(n) = o(\sqrt{n \log \log n})$. Consequently, 
+$b_n \psi^2(n)/n^2 \to 0$, $\psi^2(n)/n^2 \to 0$, ${b_n\psi(n)\sqrt{n\log \log n}/n^2} \to 0$, and $\psi(n) \sqrt{n \log \log n}/n^2 \to 0$.
 Thus, $g_1(n), g_2(n)$ and $g_3(n) \to 0$ as $n \to \infty$.
@@
 \begin{align*}
-    &\tilde{\Sigma}^{ij} \\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t + k)} - \mu \right)_j\\
+\tilde{\Sigma}^{ij}
+    % & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t + k)} - \mu \right)_j\\
     & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} \pm \bar{X}_s - \mu \right)_i  \left(X_{s(t + k)} \pm \bar{X}_s - \mu \right)_j\\
@@
 \begin{align*}
-\left|\hat{\Sigma}_{G-SVE}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right| \\
-& \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
-\end{align*}
-%
-By Assumption~\ref{ass:sve_consis}, the first term goes to with probability 1 and by Lemma~\ref{lemma:G-SVE_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
-What is left to show is that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1
+\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
+\end{align*}
+%
+By Assumption~\ref{ass:sve_consis}, the first term goes to 0 with probability 1 and by Lemma~\ref{lemma:G-SVE_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
+It is left to show that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1
 %
@@
 %
-Both terms are similar and we will show that the first term goes to 0. The proof for the second term is similar. Consider
+We will show that the first term goes to 0 and the proof for the second term is similar. Consider
 \begin{align*}
     & \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right| \\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
+    % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
     & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left| w\left(\dfrac{k}{b_n}\right) \right| \dfrac{ \left|  \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right)_i \right| + \abs{k} \left|\left(\bar{X}_s - \mu \right)_i \right|\right]\\
@@
 
-Using SIP on the summation of k terms,
+Using SIP on the summation of $k$ terms,
 \begin{align*}
@@
    &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2 \\
-   &  \leq   \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2 \quad \text{(by \eqref{eq:xbars_bound})} \\
-   & \to 0\,.
+   &  \leq   \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
+\quad  \text{(by \eqref{eq:xbars_bound})}
 \end{align*}
@@
 %
-Similar to the above proof, second part of $N_1$ can also be written as a summation of $k$ terms and the proof follows exactly as the first part.
-Now we prove that $N_2 \xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$.
-%
-Following the steps in \eqref{eq:strong_consis_term-2}, we get
+Similarly, the second part of $N_1 \to 0$ with probability 1. 
+% Now we prove that $N_2 \xrightarrow{a.s.} 0 \textrm{ as } n \to \infty$. 
+%
+Following the steps in \eqref{eq:strong_consis_term-2}, 
 \begin{align*}
@@
 \end{align*}
-Thus, in \eqref{eq:G-SVE_full_decomp}, each of the terms goes to 0 with probability 1, and $\hat{\Sigma}_{G-SVE}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. 
+Thus, in \eqref{eq:G-SVE_full_decomp}, every term goes to 0 and $\hat{\Sigma}_{G}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. 
 \end{proof}
 
-\subsection{G-SVE Bias}
-
-\begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
-The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
+\subsection{Proof of Theorem \ref{th:G-SVE_bias}}
+
+% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
+% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
 We are interested in finding the asymptotic bias here.
-Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:G-_expec_breakdown} as,
-\begin{align*}
-&\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right]\\
-&  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:G-_bias2}  \,.
+Therefore we can write the expectation of replicated autocovariance in form of
+By \ref{eq:G-_expec_breakdown},
+\begin{align*}
+\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
+% &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
+& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + o \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
 \end{align*}
@@
 %
-where both $O_1 \textrm{ and } O_2$ are the small order terms.
-By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.
+% where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  
 Consider the G-SVE estimator,
 \begin{align*}
-    &\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right]\\
-    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\inf}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\
-    & = P_1 + o \left( \dfrac{1}{n} \right)\,
+ \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + o\left(n^{-1} \right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    % &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  o\left(n^{-1}\right)\right] \\
+    & = P_1 + o \left( \dfrac{1}{n} \right)\,,
 \end{align*}
@@
 where 
-\begin{align*}
-P_1 & = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
+\[
+P_1  = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
 % P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
-\end{align*}
-%
-We first solve for term $P_1$ by breaking it into three parts as in \cite{hannan2009multiple}.
-Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for each element of the matrix $A$.
-Consider,
+\]
+%
+Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
 \begin{equation}
@@
 \[
-\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
+\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
 \]
@@
 Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
-\end{proof}
-\subsection{Variance Calculation}
+% \end{proof}
+
+\subsection{Proof of Theorem~\ref{th:G-SVE_variance}}
 \label{appendix:variance}
 
-\begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
+% \begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
  Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
@@
 \label{eq:G-SVE_asv_consis}
- \left|\hat{\Sigma}_{G-SVE} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
+ \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
 \end{equation}
@@
     g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
 \end{align*}
@@
 \begin{align*}
- &\left| \hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right|\\
+ &\left| \hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right|\\
  & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t=1}^{n-|k|}   \left[ \left( \dfrac{(X_{st} - \mu)_i(\mu-\bar{\bar{X}})_j}{n}\right)+ \left(\dfrac{(\mu-\bar{\bar{X}})_i(X_{s(t+k)}-\mu)_j}{n}\right) \right] \right.\\
-& \quad \quad  \left. + (\mu-\bar{\bar{X}})(\mu-\bar{\bar{X}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right| \\ 
- & < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
+& \quad \quad  \left. + (\mu-\bar{\bar{X}})(\mu-\bar{\bar{X}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
 \end{align*}
@@
 \begin{align*}
-\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
-& \leq \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
+\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 &= \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) + \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(n > N_0)\\
+& \leq \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
 & := g_n^*(X_{11}, \dots, X_{1n}, \dots, X_{m1}, \dots, X_{mn})\,.
@@
 \[
-\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
+\E \left| g_n^* \right| \leq  \E \left[\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}_{A}^{ij} \right)^2 \right] + \E \left[\left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 \right] < \infty\,.
 \]
@@
 \label{eq:squared_mean_diff}
-  \E \left[\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
+  \E \left[\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right] \to 0\,.
 \end{equation}
@@
 \[
-\xi\left(\hat{\Sigma}_{G-SVE}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
+\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
 \]
@@
 \begin{align*}
-\left|  \xi\left(\hat{\Sigma}_{G-SVE}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\
-& \leq \E\left[\left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\
-& = o(1) + 2\left(o(1) \left(O\left( \dfrac{b_n}{n}\right)  + o\left( \dfrac{b_n}{n}\right) \right)  \right) \\ 
-& = o(1)\,.
+\left|  \xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) \right| & \leq \left| \Var\left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \right| + \left| 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\right| \\
+& \leq \E\left[\left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right)^2 \right] + 2 \left| \left(\E\left[ \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \right]  \Var\left(\tilde{\Sigma}^{ij}  \right)   \right)^{1/2}\right| \\
+& = o(1) + 2\left(o(1) \left(O\left( \dfrac{b_n}{n}\right)  + o\left( \dfrac{b_n}{n}\right) \right)  \right) = o(1)\,.
 \end{align*}
@@
 \begin{align*}
- & \Var\left(\hat{\Sigma}_{G-SVE}^{ij} \right)\\
-  & = \E \left[ \left(\hat{\Sigma}_{G-SVE}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
-& = \E \left[ \left(\hat{\Sigma}_{G-SVE}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right)^2 \right]\\
-& = \E\left[ \left( \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right)  \right)^2 \right] \\
-& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right) \right)^2 \right] \\
-& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right)\right] + 2 \E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G-SVE}^{ij}  \right] \right)\right]\\
-& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G-SVE}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
-& = \Var\left( \tilde{\Sigma}^{ij}\right) + o(1)
+ \Var\left(\hat{\Sigma}_{G}^{ij} \right)  & = \E \left[ \left(\hat{\Sigma}_{G}^{ij}  - \E \left[\hat{\Sigma}_{R}^{ij}  \right] \right)^2 \right]\\
+& = \E \left[ \left(\hat{\Sigma}_{G}^{ij} \pm \tilde{\Sigma}^{ij} \pm \E \left[ \tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)^2 \right]\\
+& = \E\left[ \left( \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)  \right)^2 \right] \\
+& =  \E\left[ \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right)^2 \right] + \E \left[ \left(\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + \left(\E\left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right) \right)^2 \right] \\
+& \quad \quad + 2\E\left[\left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \left(\tilde{\Sigma}^{ij}  - \E\left[\tilde{\Sigma}^{ij}\right]\right) \left(\E \left[\tilde{\Sigma}^{ij}\right] - \E \left[\hat{\Sigma}_{G}^{ij}  \right] \right)\right]\\
+& = \Var\left( \tilde{\Sigma}^{ij}\right) + \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right] + o(1)\\
+& = \Var\left( \tilde{\Sigma}^{ij}\right) + o(1)\,.
 \end{align*}
@@
 \begin{equation} \label{eq:hannan_var}
-\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = [\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right)2]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
+\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = \left[\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right) \right]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
 \end{equation}
-Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{G-SVE}$ gives the result of the theorem.
-
-\end{proof}
+Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{G}$ gives the result of the theorem.
+
+% \end{proof}
 
 \section{Additional Examples}
-We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.
+We present two additional examples illustrating the difference between the ACF and G-ACF plots.
+% We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.
 In this section we will use two real-life datsets to exemplify the better performance of our replicated autocovariance estimator for multiple Markov chains.
@@
 
-\cite{pollins1996global} theorizes a cyclical pattern in the number of international conflicts.
+% \cite{pollins1996global} theorizes a cyclical pattern in the number of international conflicts.
 Four core theories by \cite{gilpin1981war}, \cite{wallerstein1983three}, \cite{goldstein1988long}, and \cite{modelski1988seapower} put different weights on the role of global economic and political order in explaining this cyclical pattern.
@@
 
-In this example, we will fit a Poisson change-point model on the annual number of military conflicts from the militarized interstate dispute (MID) data.
-We wish to detect the number and timings of the cyclic phases in the international conflicts.
-\cite{chib1998estimation} describes the Poisson change-point as a Markov mixture model where observations are assumed to be drawn from latent states.
-Following \cite{martin2011mcmcpack}, we will use \texttt{MCMCpoissonChange} from \texttt{MCMCpack} to fit the model which samples the latent states based on the algorithm in \cite{chib1998estimation}.
-The Poisson change-point model in \texttt{MCMCpoissonChange} uses conjugate priors and can be written as:
-
-\begin{align*}
-    y_t &\sim \textit{Poisson}(\lambda_i), \qquad i = 1, ..., k\\
-    \lambda_i &\sim \textit{Gamma}(c_o, d_o), \qquad i = 1,..., k\\
-    p_{ii} &\sim \textit{Beta}(\alpha, \beta), \qquad i = 1,..., k
-\end{align*}
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 0.8\textwidth, height = 4in]{plots/spatio-acf.pdf}
-    \caption{ACF and G-ACF for first component of first chain.
-ACF underestimates the autocorrelations for $10^3$ samples (top) whereas G-ACF gives more realistic estimates.
-They perform alike for $10^5$ samples (bottom).}
-    \label{fig:spatio-acf_G-fl}
-\end{figure}
-The results of model comparison by \cite{martin2011mcmcpack} showed that the ratio of maximum likelihood for six change-point model is favored over the alternatives.
+Consider the militarized interstate dispute (MID) data of \cite{martin2011mcmcpack} which describes the annual number of military conflicts in the United States.
+In order to detect the number and timings of the cyclic phases in international conflicts, we fit the following Bayesian Poisson change-point model:
+% The Poisson change-point model in \texttt{MCMCpoissonChange} uses conjugate priors and can be written as:
+%
+\begin{align*}
+    y_t &\sim \text{Poisson}(\lambda_i), \qquad i = 1, ..., k\\
+    \lambda_i &\sim \text{Gamma}(c_o, d_o), \qquad i = 1,..., k\\
+    p_{ii} &\sim \text{Beta}(\alpha, \beta), \qquad i = 1,..., k
+\end{align*}
+Following \cite{martin2011mcmcpack}, we will use \texttt{MCMCpoissonChange} from \texttt{MCMCpack} to fit the model with $k = 7$ which samples the latent states based on the algorithm in \cite{chib1998estimation}.
+% The results of model comparison by \cite{martin2011mcmcpack} showed that the ratio of maximum likelihood for six change-point model is favored over the alternatives.
 We will use this information and present the ACF results for a six change-points model only.
@@
 
-We run two parallel Markov chains starting from random poits.
-In Figure \ref{fig:spatio-acf_G-fl}, it is evident that the chains have not explored the sample space well.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 0.55\textwidth]{plots/spatio-acf.pdf}
+    \caption{ACF and G-ACF for the first component of the first chain.}
+    \label{fig:spatio-acf_G-fl}
+\end{figure}
+We run two parallel Markov chains from randomly chosen starting points and present the resulting ACF and G-ACF in Figure \ref{fig:spatio-acf_G-fl}.
+The early G-ACF estimates are far closer to the G-ACF and ACF estimates at $10^5$.
+
+ % it is evident that the chains have not explored the sample space well.
 Hence for $10^3$ samples ACF severely underestimates the autocorrelations whereas G-ACF gives more realistic estimates.
@@
 
-\subsection{High School Social Network}
-
-\cite{handcock2008statnet} implemented an exponential-family random graph modelling (ERGM) on network data in the package \texttt{ergm}.
-The \texttt{faux.magnolia.high} dataset available in the package represents a simulated within school friendship network based on Ad-Health data (\cite{resnick1997protecting}).
+\subsection{Network crawling}
+
+% \cite{handcock2008statnet} implemented an exponential-family random graph modelling (ERGM) on network data in the package .
+
+The \texttt{faux.magnolia.high} dataset available in the \texttt{ergm} \texttt{R} package represents a simulated within school friendship network based on Ad-Health data (\cite{resnick1997protecting}).
 The school communities represented by the network data are located in the southern United States.
 Each node represents a student and each edge represents a friendship between the nodes it connects.
+
+The goal is to draw each node uniformly from the network by using a network crawler.
 \cite{nilakanta2019ensuring} modified the data by removing 1,022 out of 1,461 nodes to obtain a well-connected graph.
-This resulting social network has 439 nodes and 573 edges.\\
-
-Let $V$ denote the non-empty set of countable nodes, $E \subseteq V \times V$ denote the set of edges, and $G = (V,E)$ denote the network.
+This resulting social network has 439 nodes and 573 edges.
+We use a Metropolis-Hastings algorithm with a simple random-walk  proposal suggested by \cite{gjoka2011practical}.
+The stationary distribution for this algorithm is a uniform distribution over the nodes.
+% , i.e. $\lambda(i) = 1/n$ for all $i \in V$.  The Metropolis-Hastings transition kernel for this method is
+
+% Let $V$ denote the non-empty set of countable nodes, $E \subseteq V \times V$ denote the set of edges, and $G = (V,E)$ denote the network.
 We are interested in exploring all the nodes uniformly, i.e.
@@
 
-\[
-\mathbb{E}[h(X)]_{\lambda} = \dfrac{1}{n}\sum_{x \in V}h(x).
-\]
-
-Here n is the set cardinality of $V$.
-We use a Metropolis-Hastings algorithm with a simple random-walk (SRW) proposal suggested by \cite{gjoka2011practical}.
-The stationary distribution for this algorithm is a uniform distribution over $V$, i.e.
-$\lambda(i) = 1/n$ for all $i \in V$.
-The Metropolis-Hastings transition kernel for this method is
-
-\[
-P(i,j) = \left \{
-        \begin{array}{cc}
-             \dfrac{1}{d_i} min\left(1, \dfrac{d_i}{d_j}\right) & \textrm{if j is a neighbor of i}  \\
-             1 - \sum_{k \neq i} \dfrac{1}{d_i} min\left(1, \dfrac{d_i}{d_k}\right) & \textrm{if } j = i\\
-             0 & \textrm{otherwise}.
-        \end{array}
-\right.
-\]
-
-Table (blah) shows the population parameters we are interested in estimating using MCMC methods.
+% \[
+% \mathbb{E}[h(X)]_{\lambda} = \dfrac{1}{n}\sum_{x \in V}h(x).
+% \]
+
+% Here n is the set cardinality of $V$.
+
+% \[
+% P(i,j) = \begin{cases}
+%              \dfrac{1}{d_i} \min\left\{1, d_i{d_j}^{-1}\right\} & \textrm{if $j$ is a neighbor of $i$}  \\
+%              1 - \sum_{k \neq i} d_i^{-1} \min \left\{1, {d_i}{d_k}^{-1}\right\} & \textrm{if } j = i\\
+%              0 & \textrm{otherwise}.
+%         \end{cases}
+% \]
+
+% Table (blah) shows the population parameters we are interested in estimating using MCMC methods.
 The G-e and sex parameters are estimated as proportion of whites and females in the sample respectively.
-We start two parallel Markov chains from two students belonging to different G-es and study its impacts on the average features of their immediate social group.
-It is hypothesized that students from certain communities tend to engage more with students of same or other marginally represented communities.
+
+We start two parallel Markov chains from two students belonging to different {\color{red}G-es ???} and study its impacts on the average features of their immediate social group. 
+% It is hypothesized that students from certain communities tend to engage more with students of same or other marginally represented communities.
 We believe that this "selective networking" might cause formation of clusters in the network wherein students within a cluster engage more with each other than with the students outside it.

### 2020-07-23 Paper/main.tex
I lied. Some more for today. Ab bas.

@@
 
-Recall from Equation \ref{eq:empirical_acf} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
-
-\begin{equation}
-    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
-\end{equation}
-
-The spectral variance estimator is the weighted and truncated sum of lag-k autocovariances, given by:
-
+% Recall from Equation \ref{eq:empirical_acf} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
+
+% \begin{equation}
+%     \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
+% \end{equation}
+
+Let $w_n: \mathbb{R} \to [-z,z]$ be a lag window function and let $b_n \in \mathbb{N}$ be a truncation point. The usual SV estimator is the weighted and truncated sum of lag-$k$ autocovariances:
 \begin{equation} \label{eq:sve}
@@
 
-where $w(.)$ is the lag window and $b_n$ is the truncation point.
-Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
-We construct the globally-centered SVE estimator $\hat{\Sigma}_{G}$ using the globally-centered ACF.
-Consider,
-%
-\begin{align*}
-    \hat{\Sigma}_{G,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G,s}(k)
-\end{align*}
-\[
-\hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}
+% Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
+Consider the globally-centered SV estimator (G-SVE) for the $s$th chain using G-ACF:
+%
+\begin{align*}
+    \hat{\Sigma}_{G,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G,s}(k)\,,
+\end{align*}
+and the combined G-SVE is
+\[
+\hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}\,.
 \]
@@
 
-\begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true. As a consequence, 
-\[
-\hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
-\]
+\begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true.
+As a consequence, $\hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma$ as $n \to \infty$ for all Markov chains $s$.
+% \[
+% \hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
+% \]
 \end{ass}

### 2020-07-23 GaussianMix/output.R

@@ -46,10 +46,11 @@ mean(chain2)
 ######Trace plots for n=1e4#######
 ##################################
 
+x <- seq(-10, 10, length = 1e3)
 pdf(file = "TargetTrace_n1e4.pdf", height = 5, width = 6)
-plot(x, 10000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-10000,3000), xlim = range(chain1,chain2), yaxt = 'n')
+plot(x, 20000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-10000,6000), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
-plot(x = chain1[1:1e4], y = seq(-1, -1e4, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e4, 3e3), , xlim = range(chain1,chain2), yaxt = 'n')
+plot(x = chain1[1:1e4], y = seq(-1, -1e4, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e4, 6e3), , xlim = range(chain1,chain2), yaxt = 'n')
 lines(x = chain2[1:1e4], y = seq(-1, -1e4, -1), col = "plum3")
 mtext(side = 2, text = "Time", line = 1)
 legend("topleft", legend=c("Target", "Chain-1", "Chain-2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=0.7, lwd=2)
@@ -61,9 +62,9 @@ dev.off()
 
 
 pdf(file = "TargetTrace_n1e5.pdf", height = 5, width = 6)
-plot(x, 100000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-1e5,3e4), xlim = range(chain1,chain2), yaxt = 'n')
+plot(x, 200000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-1e5,6e4), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
[…]

### 2020-07-24 Boomerang/acf_plots.R
Used updated package on Boomerang example

@@ -3,121 +3,154 @@ source("functions.R")
 library(rep.acf.ccf)
 
 
-m <- 2
+m <- 5
 A <- 1
 B <- 3
 C <- 8
 start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
-
 
 for(i in 1:floor(m/2)){
   start[i,] <- c(0, C*(2^(2-i)))
   start[m-i+1,] <- c(C*(2^(2-i)), 0)
 }
 
-lag.max <- 100
-####################################
-nsim <- 500
-########################################
 mc.chain.list <- list()
 global.mean <- c(0,0)
 for (i in 1:m){
-  chain <- markov.chain(A, B, C, nsim, start[i,])
+  chain <- markov.chain(A, B, C, 5e4, start[i,])
   global.mean <- global.mean + colMeans(chain)
   mc.chain.list[[i]] = chain
 }
 global.mean <- global.mean/m
+lag.max <- 100
+component <- 1
 
-acf.list <- combined_acf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
-ccf.list <- combined_ccf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
 
-pdf(file = paste(paste("Out/", A, B, C, "/boom-acf,n=", sep = "_"), nsim, ".pdf", sep = ""), width = 8, height = 4)
-#par(mfrow = c(3,2))
-#for (i in 1:2){
-#  plot(acf.list[[i]][[1]], main = paste("ACF for component -", i ))
-#  plot(acf.list[[i]][[2]], main = paste("R-ACF for component -", i ))
-#}
-#plot(ccf.list[[1]], main = "CCF for component 1-2")
-#plot(ccf.list[[2]], main = "R-CCF for component 1-2")
-par(mfrow = c(1,2))
-plot(acf.list[[1]][[1]], main = expression(paste("Old ACF for chain 1")))
-plot(acf.list[[1]][[2]], main = expression(paste("New ACF for chain 1")))
-
-dev.off()
-
-pdf(file = paste(paste("Out/", A, B, C, "/scatter_n", sep = "_"), nsim, ".pdf", sep = ""), width = 5, height = 5)
-par(mfrow = c(1,1))
-plot(mc.chain.list[[1]], xlim = c(0,11), ylim = c(0,11), col = 1, pch = 1)
[…]

### 2020-07-25 PoissonChange/acf_plots.R
New ACF plots for all examples

@@ -1,0 +1,90 @@
+set.seed(1)
+library("MCMCpack")
+library(rep.acf.ccf)
+load("mida.rda")
+
+c0 <- 13
+d0 <- 1
+bars <- 6
+m <- 2       #### Number of chains
+mc.chain.list <- list()
+
+for (i in 1:m)
+  (mc.chain.list[[i]] <- MCMCpoissonChange(mida~ 1, m=bars, c0=c0, d0=d0, marginal.likelihood="none", mcmc = 1e5, burnin = 0, thin = 1, seed = round(1e3*runif(1))))
+
+save(mc.chain.list, file = "Out/two_chains.Rdata")
+
+load(file = "Out/two_chains.Rdata")
+lag.max <- 150
+
+###########################################
+###########################################
+######## ACF and G-ACF ###################
+##########################################
+###########################################
+
+
+### ncrop = 1e3
+
+ncrop <- 1e3
+x <- list()
+for (i in 1:m){
+  x[[i]] <- mc.chain.list[[i]][1:ncrop,]
+}
+
+global.acf <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$'G-ACF'
+local.acf <- acf(x[[1]][, component], type = "correlation", lag.max = lag.max, plot = FALSE)
+
+for (i in 2:m)
+  local.acf$acf <- local.acf$acf + acf(x[[i]][, component], type = "correlation", lag.max = lag.max, plot = FALSE)$acf
+local.acf$acf <- local.acf$acf/m
+
+pdf(file = paste("Out/acf_n", ncrop, ".pdf", sep = ""), width = 8, height = 4)
+par(mfrow = c(1,2))
+plot(local.acf, main = expression(paste("Old ACF for chain 1")), xlim = range(0, lag.max), ylim =  c(0,1))#c(min(min(acf.list[[1]][[1]]$acf), min(true.acf[1,1,])), max(max(acf.list[[1]][[1]]$acf), max(true.acf[1,1,]))))
+plot(global.acf, main = expression(paste("New ACF for chain 1")), xlim = range(0, lag.max), ylim =  c(0,1))#c(min(min(acf.list[[1]][[2]]$acf), min(true.acf[1,1,])), max(max(acf.list[[1]][[2]]$acf), max(true.acf[1,1,]))))
+dev.off()
+
[…]

### 2020-07-25 SensorNetwork/acf_plots.R

@@ -35,28 +35,30 @@ Ys <- matrix(c(0, 0, 0, 0.9266,
 j.scale <- rep(1.08, 4)    # jump scale
 
 # Chain-1 with 5e3 samples
+m <- 5
+start1 <- c(-0.1, 0.5, -0.1, -0.2, 0.1, 0.1, -0.5, -0.5)
+aux1 <- runif(n=8, min=min(start1), max=max(start1))
+start2 <- c(0.0, 0.6, 0.1, 0.1, 0.2, 0.2, 1.0, 0.0)
+aux2 <- runif(n=8, min=min(start2), max=max(start2))
+start3 <- c(0.2, 0.7, 0.5, 0.4, 0.5, 0.3, 0.5, 0.5)
+aux3 <- runif(n=8, min=min(start3), max=max(start3))
+start4 <- c(0.4, 0.8, 0.8, 0.6, 0.7, 0.4, 1.0, 1.0)
+aux4 <- runif(n=8, min=min(start4), max=max(start4))
+start5 <- c(0.7, 1.0, 1.2, 0.9, 0.9, 0.5, 1.5, 1.5)
+aux5 <- runif(n=8, min=min(start5), max=max(start5))
 
-nsim = 1e5
+start <- rbind(start1, start2, start3, start4, start5)
+aux <- rbind(aux1, aux2, aux3, aux4, aux5)
+j.scale <- rep(0.5, 4)
+mc.chain.list <- list()
 
-start1 <- runif(8, min= -0.3, max = 0)
-aux1 <- runif(8, min = -0.3, max= 0)
-system.time(res.ram1 <- MHwG.RAM(start1, aux1, jump.scale = j.scale,
-                                 Ob, Os, Xb, Xs, Yb, Ys,
-                                 n.sample = nsim, n.burn = 0))
+for (k in 1:m){
+  temp <- MHwG.RAM(start[k,], aux[k,], jump.scale = j.scale,Ob, Os, Xb, Xs, Yb, Ys, n.sample = 1e4, n.burn = 0)
+  mc.chain.list[[k]] <- temp$x
+  print(colMeans(temp$accept))
+}
 
-# Chain-2 with 5e3 samples
-start2 <- runif(8, min = 0.7, max = 1.1)
-aux2 <- runif(8, min = 0.7, max= 1.1)
-
-system.time(res.ram2 <- MHwG.RAM(start2, aux2, jump.scale = j.scale,
-                                    Ob, Os, Xb, Xs, Yb, Ys,
[…]

### 2020-07-25 Paper/main.tex
Writing points down in blue.

@@
 The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
+
+{\color{blue} Fix the proof for this.}
 \begin{theorem} \label{th:G-_expec} Under stationarity,
@@
 \]
+
 \end{corollary}
@@
 \section{Variance Estimators for multiple Markov chains} \label{sec:variance_est}
-
-{\color{blue}Dootika: this section here needs to be much tighter in its presentation.
-We will need to remember that the paper is no longer about the SV estimators but about autocorrelations.
-So will have to present the discussion similarly.
-}
 
@@
 
+{\color{blue} Don't make this an assumption. Say this explicitly in Theorem 2. }
+
 \begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true.
@@
 
+{\color{blue}: Make the following an assumption. Is $2\pi$ needed? Is $W_n$ always finite? }
 We are interested in the finding the bias for G-SVE estimator as a function of $n$.
@@
 
+{\color{blue} Under what assumptions?}
 \begin{theorem}\label{th:G-SVE_bias}
@@
 
+{\color{blue} Don't make this a separate assumption. Include in the statement of the theorem}
 \begin{ass} \label{ass:variance_cal}
@@
 \begin{align*}
-    z_{ij} \mid x_1, ..., x_6 &\ sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
+    z_{ij} \mid x_1, ..., x_6 & \sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
     y_{ij} \mid w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)

### 2020-07-25 VAR-1/acf_plots.R
G-ACFs for VAR(1)

@@ -3,6 +3,10 @@ source("functions.R")
 library(rep.acf.ccf)
 
 
+######################################
+##### Model parameters ###############
+######################################
+
 m <- 5
 p <- 2
 omega <- diag(p)
@@ -17,12 +21,12 @@ phi <- diag(c(.9999, .001))
 dummy <- matrix(1:p^2, nrow = p, ncol = p)
 dummy <- qr.Q(qr(dummy))
 phi <- dummy %*% phi %*% t(dummy)
-#phi <- phi/(max(eigen(phi)$values) + .1)
 
 target <- target.sigma(phi, omega)
 truth <- true.sigma(phi, var = target)
 
 lag.max <- 150
+
 true.acf <- array(0, dim = c(p, p, 2*lag.max + 1))
 true.acf[,,lag.max+1] <- target
 for (i in 1:lag.max){
@@ -37,103 +41,122 @@ for(i in 1:floor(m/2)){
   start[m-i+1,] <- -0.5*i*sqrt(diag(target))
 }
 
-##################################
+mc.chain.list <- list()
+global.mean <- rep(0,p)
+for (i in 1:m){
+  chain <- markov.chain(phi, omega, 1e5, start[i,])
+  global.mean <- global.mean + colMeans(chain)
+  mc.chain.list[[i]] = chain
+  print(colMeans(chain))
+}
+global.mean <- global.mean/m
+save(mc.chain.list, file = "Out/five_chains.Rdata")
+
+load(file = "Out/five_chains.Rdata")
+
+
+########################################3
+#########################################
+####  Scatter plots #####################
+#########################################
+#########################################
+
+
 nsim <- 5e2
-##################################
-
-mc.chain.list <- list()
-global.mean <- rep(0,p)
-for (i in 1:m){
-  chain <- markov.chain(phi, omega, nsim, start[i,])
-  global.mean <- global.mean + colMeans(chain)
-  mc.chain.list[[i]] = chain
-}
-global.mean <- global.mean/m
 
 pdf(file = paste("Out/scatter_plot_", nsim, ".pdf", sep = ""), title = paste("Scatter plot, nsim = ", nsim))
[…]

### 2020-07-25 SpatialTemp/spatio_acf.R
Useless examples in trash

@@ -1,68 +1,0 @@
-set.seed(130290)
-library(mcmcse)
-library(mcmc)
-
-source("spatio_temp_function.R")
-load("spatio_temp_truth_2e6by1000")
-truth <- colMeans(spatio_truth)
-data(logit)
-level <- .90
-
-## Fitting model with intercept
-N <- 500
-p <- 2
-
-starting1 <- list("beta"=rep(30,N.t*p), "phi"=rep(3/(0.07*max.d), N.t),
-                  "sigma.sq"=rep(2,N.t), "tau.sq"=rep(1, N.t),
-                  "sigma.eta"=diag(rep(0.01, p)))
-
-starting2 <- list("beta"=rep(-30,N.t*p), "phi"=rep(3/(0.89*max.d), N.t),
-                  "sigma.sq"=rep(2,N.t), "tau.sq"=rep(1, N.t),
-                  "sigma.eta"=diag(rep(0.01, p)))
-
-chain1 <- spatio_temp(N = N, verbose = FALSE, starting1)
-chain2 <- spatio_temp(N = N, verbose = FALSE, starting2)
-
-chains <- list(chain1, chain2)
-
-plot(chain1[,1], chain1[,11], col = "blue", xlim = range(chain1[,1], 
-    chain1[,11], chain2[,1], chain2[,11]), ylim = range(chain1[,1], 
-                                                         chain1[,11], chain2[,1], chain2[,11]))
-points(chain2[,1], chain2[,11], col = "green", xlim = range(chain1[,1], 
-                                                           chain1[,11], chain2[,1], chain2[,11]), ylim = range(chain1[,1], 
-                                                                                                             chain1[,11], chain2[,1], chain2[,11]))
-
-#
-
-##############################
-ncrop <- 5e2
-##############################
-
-acf <- combined_acf(list(chains[[1]][1:ncrop,], chains[[2]][1:ncrop,]), chain = 1, component = (1:26), 
-                    lag.max = 100, type = "correlation")
-
-for (j in 1:26)
-{
-  pdf(file = paste("Out/acf_n", ncrop, "_component", j, ".pdf", sep = ""), height = 3, width = 4)
-  plot(acf[[j]][[1]], main = expression("Autocorrelation function"), type = "l")
-  lines(seq(0:lag.max), acf[[j]][[2]]$acf, main = expression("Globally centered ACF"), col = "red")
[…]

### 2020-07-25 SpatialTemp/spatio_temp_truth.R

@@ -1,60 +1,0 @@
-# source("spatio_temp_function.R")
-library(spBayes)
-library(parallel)
-data("NETemp.dat")
-ne.temp <- NETemp.dat
-
-ne.temp <- ne.temp[ne.temp[,"UTMX"] > 5500000 & ne.temp[,"UTMY"] > 3250000,]##subset first 2 years (Jan 2000 - Dec. 2002)
-y.t <- ne.temp[,4:15]
-N.t <- ncol(y.t) ##number of months
-n <- nrow(y.t) ##number of observation per months
-
-coords <- as.matrix(ne.temp[,c("UTMX", "UTMY")]/1000)
-max.d <- max(iDist(coords))
-
-##set starting and priors
-p <- 2 #number of regression parameters in each month
-starting <- list("beta"=rep(0,N.t*p), "phi"=rep(3/(0.5*max.d), N.t),
-"sigma.sq"=rep(2,N.t), "tau.sq"=rep(1, N.t),
-"sigma.eta"=diag(rep(0.01, p)))
-
-tuning <- list("phi"=rep(6, N.t))
-
-priors <- list("beta.0.Norm"=list(rep(0,p), diag(1000,p)),
-"phi.Unif"=list(rep(3/(0.9*max.d), N.t), rep(3/(0.05*max.d), N.t)),
-"sigma.sq.IG"=list(rep(2,N.t), rep(10,N.t)),
-"tau.sq.IG"=list(rep(2,N.t), rep(5,N.t)),
-"sigma.eta.IW"=list(2, diag(0.001,p)))
-
-##make symbolic model formula statement for each month
-mods <- lapply(paste(colnames(y.t),'elev',sep='~'), as.formula)
-n.samples <- 2e6
-
-
-beta0 <- 0
-beta <- 0
-theta <- 0
-sigma.eta <- 0
-u <- 0
-
-spatio_truth_loop <- function(i)
-{
-print(i)
-
-chain <- spDynLM(mods, data=cbind(y.t,ne.temp[,"elev",drop=FALSE]), coords=coords,
-starting=starting, tuning=tuning, priors=priors, get.fitted =FALSE,
-cov.model="exponential", n.samples=n.samples, n.report=1e4, verbose = FALSE)
-
-beta0 <- colMeans(chain$p.beta.0.samples)
-beta <- colMeans(chain$p.beta.samples)
-theta <- colMeans(chain$p.theta.samples)
[…]

### 2020-07-25 TimeDelays/RAM_original_paper_code/JCGS_RAM_code.R

@@ -1,2273 +1,0 @@
-
-############### RAM transition used at each iteration
-############### target function is defined as a function "target"
-############### See line 156 for example.
-
-ram.transition <- function(current.x, current.z, var.cov, epsilon) {
-
-  x.c <- current.x
-  z.c <- current.z
-  x.dim <- length(x.c)
-  x.c.den <- target(x.c)
-  z.c.den <- target(z.c)
-  accept <- 0
-
-  # downhill
-  x.p1 <- mvrnorm(1, mu = x.c, Sigma = var.cov)
-  x.p1.den <- target(x.p1)
-  N.d <- 1
-  while (-rexp(1) > log(x.c.den + epsilon) - log(x.p1.den + epsilon)) {
-    x.p1 <- mvrnorm(1, mu = x.c, Sigma = var.cov)
-    x.p1.den <- target(x.p1)
-    N.d <- N.d + 1
-  }
-
-  # uphill
-  x.p2 <- mvrnorm(1, mu = x.p1, Sigma = var.cov)
-  x.p2.den <- target(x.p2)
-  N.u <- 1
-  while (-rexp(1) > log(x.p2.den + epsilon) - log(x.p1.den + epsilon)) {
-    x.p2 <- mvrnorm(1, mu = x.p1, Sigma = var.cov)
-    x.p2.den <- target(x.p2)
-    N.u <- N.u + 1
-  }
-
-  # downhill for auxiliary variable z
-  z <- mvrnorm(1, mu = x.p2, Sigma = var.cov)
-  z.den <- target(z)
-  N.z <- 1  
-  while (-rexp(1) > log(x.p2.den + epsilon) - log(z.den + epsilon)) {
-    z <- mvrnorm(1, mu = x.p2, Sigma = var.cov)
-    z.den <- target(z)
-    N.z <- N.z + 1  
-  }
-
-
-  # accept or reject the proposal
-  min.nu <- min(1, (x.c.den + epsilon) / (z.c.den + epsilon))
-  min.de <- min(1, (x.p2.den + epsilon) / (z.den + epsilon))
-  l.mh <- log(x.p2.den) - log(x.c.den) + log(min.nu) - log(min.de)
-
-  if (l.mh > -rexp(1)) {
-    x.c <- x.p2
-    z.c <- z
-    accept <- 1
-  }
-
-  c(x.c, z.c, accept, N.d, N.u, N.z)
-
-}
-
-############### RAM algorithm
-
[…]

### 2020-07-25 TimeDelays/data.R

@@ -1,82 +1,0 @@
-data(simple)
-days <- c(4554.712, 4555.767,	4561.722,	4570.669,	4584.677,	4596.704,	4613.691,	4617.702, 4793.005,		
-          4802.980,	4807.929,	4829.857,	4833.894,	4839.966,	4846.758, 4862.882,	4877.716, 4883.932,	
-          4891.824, 4911.800,	4942.797,	4964.715,	4981.695, 4997.677,	5144.981, 5157.964,	5186.024,	
-          5201.946,	5208.993,	5241.874,	5261.687,	5296.691,	5311.690,	5320.745,	5324.729,	5332.717,	
-          5348.695,	5352.685,	5358.688,	5506.991,	5519.030,	5527.937,	5535.032, 5543.989, 5563.958,
-          5590.779, 5604.847, 5621.687, 5626.779, 5649.715,	5653.710, 5664.750, 5674.748,	5684.672, 
-          5702.677, 5712.673,	5733.651) 
-
-	
-  
-            
-
-
-seeing <- c(1.3,	1.4, 1.3,	1.5,	1.4,	1.4,	1.4,	1.3,	0.9,	1.4,	1.3,	1.3,	1.4,	1.6,	1.8,
-            1.2,	2.0, 1.1,	1.3,	1.1,	1.7,	1.2,	2.2,	1.2,	1.3,	1.1,	1.2,	1.2,	1.2,	2.1,
-            1.4,	0.8, 1.3,	0.9,	0.7,	1.1,	1.1,	0.9,	1.8,	1.4,	0.9,	1.7,	1.1,	1.0,	1.3,
-            1.0,	1.5,	1.0,	1.2, 1.1,	1.1,	1.2,	1.6,	1.3,	1.7,	1.0,	1.2)
-
-QSO <- c(2.671 , 0.004,	2.419 , 0.004,
-2.659 , 0.004,	2.412 , 0.004	,
-2.665 , 0.004,	2.417 , 0.004,
-2.669 , 0.004,	2.413 , 0.004,
-2.664 , 0.004,	2.378 , 0.004,
-2.682 , 0.004,	2.377 , 0.005,
-2.689 , 0.004,	2.392 , 0.004,
-2.691 , 0.004,	2.412 , 0.004	,
-2.733 , 0.004,	2.541 , 0.005,
[…]

### 2020-07-25 TimeDelays/output.R

@@ -1,116 +1,0 @@
-set.seed(1)
-library(fields)
-library(scatterplot3d)
-library(cubature)
-library(graphics)
-library(pracma)
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-library(stats)
-library(timedelay)
-sourceCpp("lag.cpp")
-source("functions.R")
-load("dataset")
-
-###################################################
-### Data and model parameters
-lcA <- data[, 1 : 3]
-lcB <- data[, c(1, 4, 5)]
-m <- 4
-delta.start <- c(300, 500, 700, 900)
-micro <- 0
-
-###############################################
-
-
-check.pts <- c(5e2, 1e3, 5e3, 1e4)
-r <- length(check.pts)
-freq <- 1e2
-c.prob <- .95
-min <- 5e2
-max <- 1e5
-step <- 500
-conv.pts <- seq(min, max, step)
-
-## 1.) Running plots
-
-load(file = paste(paste("Out/conv_data", min, max, sep = "_"), ".Rdata", sep = ""))
-
-pdf(file = paste(paste("Out/run_plots_time_delay", sep = "_"), ".pdf", sep = ""))
-plot(conv.pts,asv.samp[1,1,], type = "l", col = "red", main = "Variance of time delay", xlab = "Simulation size", ylab = "Variance", ylim = range(rsv.samp[1,1,], asv.samp[1,1,]))
-lines(conv.pts, rsv.samp[1,1,], col="blue")
-legend("topright", legend=c("ASV", "RSV"),col=c("red", "blue"), lty=1, cex=.75)
-dev.off()
-
-#### 1c.) Determinant
-pdf(file = paste(paste("Out/run_plots_det", sep = "_"), ".pdf", sep = ""), height = 3)
-
-det.rsv <- rep(0,length(conv.pts))
-det.asv <- rep(0,length(conv.pts))
-
-for (i in 1:length(conv.pts)){
-  det.rsv[i] <- (det(rsv.samp[,,i]))
-  det.asv[i] <- (det(asv.samp[,,i]))
-}
-
-plot(conv.pts,det.asv, type = "l", col="red", main = paste("Determinant"), xlab = "Simulation size", ylab = "Determinant", ylim = range(det.rsv))
-lines(conv.pts,det.rsv, col="blue")
[…]

### 2020-07-25 TimeDelays/simulations.R

@@ -1,170 +1,0 @@
-set.seed(1)
-library(cubature)
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-library(timedelay)
-source("functions.R")
-sourceCpp("lag.cpp")
-data <- read.csv("q0957usno.csv", header = TRUE)
-lcA <- data[, 1 : 3]
-lcB <- data[, c(1, 4, 5)]
-
-################################################3
-
-############################################################
-##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
-############################################################
-
-create.output <- function(lcA, lcB, micro, ram, delta.start, delta.jump, m, check.pts, freq){
-  
-  p <- 2
-  
-  for (i in 1:length(check.pts)){
-    
-    nsim <- check.pts[i]
-    #critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
-    asv.samp <- array(0, dim = c(p,p,freq))
-    rsv.samp <- array(0, dim = c(p,p,freq))
-    #asv.coverage <- rep(0,freq)
-    #rsv.coverage <- rep(0,freq)
-    
-    
-    for (j in 1:freq){
-      if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2), "for nsim = ", nsim))
-      chain <- array(0,dim = c(nsim,p,m))
-      sve <- array(0, dim = c(p,p,m))
-      rsve <- array(0, dim = c(p,p,m))
-      b <- rep(0,m)
-      
-      for(k in 1:m){
-        chain[,,k] <- markov.chain(lcA, lcB, nsim+1, delta.start[k], delta.jump, micro, ram, burn = 0)$samples
-        b[k] <- batchSize(chain[,,k], method = "bartlett")
-        }
-      
-      b.avg <- floor(mean(b))
-      global.mean <- apply(chain,2,mean)
-      
-      for (k in 1:m){
-        chain.cen.loc <- scale(chain[,,k], scale = FALSE)  ## X_st - bar(X)_s
-        sve[,,k] <- mSVEfft(A = chain.cen.loc, b = b.avg)
[…]

### 2020-07-25 Paper/main.tex
Pushing changes I made during the meeting.

@@
 
-% By proposition 1 in \cite{song1995optimal} 
-% \begin{equation} \label{eq:song}
-% \Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
-% \end{equation}
+By proposition 1 in \cite{song1995optimal} 
+\begin{equation} \label{eq:song}
+\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
+\end{equation}
 
@@
 
+{\color{blue} Below is a remark}
 \begin{corollary} \label{cor:lag0_expectation}
 \[
-\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
+\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
 \]
@@
 
-\subsection{Autocorrelation} % (fold)
-\label{sub:autocorrelation}
+% \subsection{Autocorrelation} % (fold)
+% \label{sub:autocorrelation}
 
 % subsection autocorrelation (end)
+{\color{blue}  Autocovariances will be used implictly in SVE estimators. But they are explicitly important in ACF plots via autocorrelations.
+
+Notation in the appendix is $\Gamma^{ii}_{G,s}$
+}
+
 For any component $i$, the autocorrelation is
@@
 \]
-{\color{blue} Add more about autocorrelation}
+{\color{blue} Add more about autocorrelation. Refer to Figure 2 above and the impacts of the correlation methods. }
 
@@
 %
+{\color{blue} }
 \[
@@
 
-Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = \dfrac{1}{n}\sum_{t=1}^{n}X_t$ is the MCMC average.
+Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = n^{-1}\sum_{t=1}^{n}X_t$ is the MCMC average.
 Let $w_k$ denote the lag-window at lag-k, i.e.
@@
 \begin{pmatrix}
-    X_{s1} - \overline{\overline{X}} \; \dots \; X_{sn} - \overline{\overline{X}}
-\end{pmatrix}^T
+    X_{s1} - \overline{\overline{X}} \; \dots \; X_{sn} - \overline{\overline{X}}\end{pmatrix}^T
 \].
@@
 %
-Additionally, the locally-centered autocovariance exhibits the following expectation
+Additionally, the locally-centered autocovariance exhibits the following expectation {\color{blue} + add small order term. Confirm with Priestly. }
  \begin{equation} \label{eq:priestly}
@@
 
-\subsection{Proof of Theorem \ref{th:G-SVE_bias}}
-
-% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
-% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
+\subsection{G-SVE Bias}
+
+\begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
+The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
 We are interested in finding the asymptotic bias here.
-Therefore we can write the expectation of replicated autocovariance in form of
-By \ref{eq:G-_expec_breakdown},
-\begin{align*}
-\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
-% &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + o \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
+Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:G-_expec_breakdown} as,
+\begin{align*}
+&\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right]\\
+&  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
+& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:G-_bias2}  \,.
 \end{align*}
@@
 %
-% where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  
+where both $O_1 \textrm{ and } O_2$ are the small order terms.
+By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.
 Consider the G-SVE estimator,
 \begin{align*}
- \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + o\left(n^{-1} \right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    % &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  o\left(n^{-1}\right)\right] \\
-    & = P_1 + o \left( \dfrac{1}{n} \right)\,,
+    &\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right]\\
+    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\inf}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\
+    & = P_1 + o \left( \dfrac{1}{n} \right)\,
 \end{align*}
@@
 where 
-\[
-P_1  = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
+\begin{align*}
+P_1 & = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
 % P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
-\]
-%
-Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
+\end{align*}
+%
+We first solve for term $P_1$ by breaking it into three parts as in \cite{hannan2009multiple}.
+Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for each element of the matrix $A$.
+Consider,
 \begin{equation}
@@
 \[
+\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
+\]
+which completes the result.
+%
+ % We have shown that all, but one, terms are $o(1/b_n^q)$.
+Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
+This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu$ in our replicated autovariance estimator.
+Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
+\end{proof}
+
+\subsection{Proof of Theorem \ref{th:G-SVE_bias}}
+
+% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
+% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
+We are interested in finding the asymptotic bias here.
+Therefore we can write the expectation of replicated autocovariance in form of
+By \ref{eq:G-_expec_breakdown},
+\begin{align*}
+\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
+% &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
+& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + o \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
+\end{align*}
+%
+\begin{equation} \label{eq:G-_bias2}
+\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
+\end{equation}
+%
+where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  
+Consider the G-SVE estimator,
+\begin{align*}
+ \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + o\left(n^{-1} \right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  o\left(n^{-1}\right)\right] \\
+    & = P_1 + o \left( \dfrac{1}{n} \right)\,,
+\end{align*}
+%
+where 
+\[
+P_1  = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
+% P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
+\]
+%
+Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
+\begin{equation}
+\label{eq:P1_decomp}
+P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
+\end{equation}
+%
+We deal with the three subterms of term $P_1$ individually. First,
+%    
+\begin{align*}
+ {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
+\end{align*}
+%
+since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
+%
+\begin{align*}
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
+\end{align*}
+For $q\geq 1$,
+\begin{align*}
+\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
+\end{align*}
+
+For $q <1$,
+\begin{align*}
+   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
+\end{align*}
+So,
+\begin{equation}
+\label{eq:P1_second}
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
+\end{equation}
+Lastly, by our assumptions, for $x \to 0$
+\[
+\dfrac{1 - w(x)}{\abs{x}^q} = k_q + o(1)\,.
+\]
+For $x = k/b_n$, $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$.
+ % where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
+     % \[
+     % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
+     % \]
+So,
+\begin{align*}
+     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
+     & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
+     & = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right) \numberthis \label{eq:P1_third}\,.
+\end{align*}
+%
+ % Finally, we will solve for $P_2$.
+Note that $O_2$ is independent of $k$.
+We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$.
+We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
+ % \begin{align*}
+ %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
+ %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
+ %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
+ %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
+ %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
+ % \end{align*}
+  %
+%
+Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
+\[
 \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,

### 2020-07-29 Paper/main.tex
Preliminary work on the introduction. Heading home.

@@
 
-Markov chain Monte Carlo (MCMC) is a sampling method used to obtain correlated realizations from a stochastic process.
-Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones.
-Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains.
-Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain.
-Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e.
-(1) $\mathbb{E}[X_t] = \mu$ is constant for all $t$, (2) $\mathbb{E}[X_t^2]$ is constant for all $t$, and (3) $\mathbb{E}[X_t X_{t+k}]$ is a function of $k$ only $\forall k,t \in \mathbb{Z}$.
-Then, the autocovariance function at lag-$k$ is defined as
-%
-\[
-    \Gamma(k) = \Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
-\]
-
-A popular sample autocovariance function is the empirical estimator. On a finite sample $X = (X_1, X_2, ..., X_n)^T$, the autocovariance at lag-$k$ is estimated as
+The power of the modern personal computer has made it easy to run parallel Markov chain Monte Carlo (MCMC) implementations.
+This is particularly useful for slow mixing or multi-modal target distributions, where the starting points of the chains are spread over the state-space in order to more accurately capture characteristics of the target distribution.
+Output from $m$ parallel chains are then summarized, visually and quantitatively, to assess the empirical mixing properties of the chains and the quality of Monte Carlo estimators.
+
+A key quantity of interest that drives MCMC output analysis is the autocovariance function (ACvF).
+From their use in autocorrelation plots to assessing Monte Carlo variability of estimates, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences users make from MCMC output.
+However, tools on estimating ACvF are largely constructed for output from one MCMC chain.
+
+% Markov chain Monte Carlo (MCMC) is a sampling method used to obtain serially correlated realizations from a desired probability distribution when i.i.d.
+sampling is difficult.
+Due to this serial correlation in samples, a larger number of MCMC samples are required to make inferences about the target distribution as compared to the independent ones.
+Therefore, it becomes imperative for an MCMC practitioner to have an idea about the underlying dependence structure in the Markov chains.
+Autocovariance function (ACF) characterizes this dependence at a particular lag $k$.
+
+Let $F$ be the target distribution with mean $\mu$ defined on the set $\X \subseteq \mathbb{R}^p$ equipped with a countably generated Borel $\sigma$-field $\mathcal{B}(\X)$.
+Let $\{X_1, X_2, ..., X_n\}$ be an $F$-Harris ergodic (aperiodic, $F$-irreducible, and positive Harris recurrent) Markov chain.
+% If $\bar{X} = n^{-1} \sum_{t=1}^{n}X_t$ , then with probability 1, $\bar{X} \to \mu$ as $n \to \infty$. \\
+
+For a stationary Markov chain, the autocovariance function at lag $k$ depends only on $k$ and is defined as 
+%
+\[
+    \Gamma(k) = \Cov(X_t, X_{t+k})= \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
+\]
+
+A popular sample autocovariance matrix at lag-$k$ is given by
 %
 \begin{equation} \label{eq:empirical_acf}
-    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{(t+\abs{k})} - \bar{X})^T
+    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{(t+\abs{k})} - \bar{X})^T.
 \end{equation}
 
-where $\bar{X} = \sum_{t=1}^nX_t/n$.
-Calculation of exact ACF has been done for simple models like autoregressive (AR), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
-However, for most of the complex sampling algorithms, we rely on sample estimators for ACF.
-Unfortunately, the estimator given in equation \ref{eq:empirical_acf} has been observed to have a some drawbacks.
-Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains for decently finite samples.
+It is a known fact that most of the Markov chains obtained from practical MCMC algorithms are not stationary.
+Regardless, Equation~\ref{eq:empirical_acf} provides the empirical estimator for ACF at a particular lag for the Markov chain with any initial distribution (\cite{geyer2011introduction}).\\
+
+Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
+However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
+Unfortunately, the estimator given in Equation~\ref{eq:empirical_acf} has been observed to have a some drawbacks.
+Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains.
 We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.
-With convenient multi-core computation resources, it is possible to get multiple Markov chains for a target distribution.
-Our goal is to combine the information from all the Markov chains while calculating the autocovariances\\
+This approach is especially relevant to MCMC wherein multiple chain sampling is computationally possible and statistically desirable for making informative inferences.
+Our goal is to pool in the information from all the Markov chains while estimating the autocovariances.
+\\
 
  A commonly faced problem with the MCMC models is the slow mixing property.
-In case of multi modal target distributions, it has been observed that the Markov chains tend to get \textit{stuck} in a particular mode for a long time.
-As a consequence, the chain fails to explore the sample space.
-In such situations, single chain empirical ACF will underestimate the autocovariance giving misleading inferences.
+Especially in case of multi modal target distributions, it has been observed that the Markov chains tend to get \textit{stuck} in a particular mode for a long time.
+In such situations, single chain empirical ACF will severely underestimate the autocovariance.
 We propose an autocovariance estimator called globally-centered autocovariance function (G-ACF) with a simple fix in centering which has been observed to show drastically better results in many cases.
+We also prove that our estimator compensates the negative bias of the empirical ACF estimator to give estimates that are closer to reality.
 We will further study the impact of G-ACF in calculation of two important applications of ACF (1) asymptotic variance of Markov chain average and (2) effective sample size (ESS).\\
 
- MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite.
+Let $g: \chi \to \mathbb{R}^d$ be an F-integrable function and suppose we are interested in estimating the expected value $\mu_g = \mathbb{E}_F[g(X)]$.
+We know that $\sum_{t=1}^{n}g(X_t)/n$ converges to $\mu_g$ as $n \to \infty$ almost surely.
+MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite and the Markov chain mixes slowly.
+One of the important criteria to determine the quality of estimation is the Monte Carlo aymptotic covariance matrix which is given by an infinite summation of autocovariance matrices for all lags.
+For a slowly mixing Markov chain, underestimated autocovariances will deliver underestimated asymptotic variance.
+There are many techniques for estimating it like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
+Due to its nice statistical properties, we will only focus on SVE in this paper.
+SVE involves a truncated and weighted sum of autocovariances.
+We propose a version of SVE that uses our globally centered autocovariances.
+We call this globally-centered SVE (G-SVE).\\
+
+A more powerful estimator of Monte Carlo asymptotic covariance matrix can enable us to estimate the effective sample size for the Markov chain which is closer to reality.
 There are many criteria for terminating simulation like fixed-time rule, sequencial fixed-volume rule (see \cite{glynn1992asymptotic}), and using Gelman Rubin diagnostics (\cite{gelman1992inference}).
@@
 We will use method of effective sample size (ESS) by \cite{vats2019multivariate} for terminating the simulations.
-The quality of estimation of $\Sigma$ is critical in estimating their ESS.
+The quality of estimation of asymptotic covariance matrix is critical in estimation of the ESS.
 We will successfully show that the G-SVE estimates the truth better and prevents the premature stopping of Markov chain.\\
 
-In the next section we introduce the new sample autocovariance estimator and calculate its bias for finite samples.
+The rest of the paper is arranged as follows.
+In Section~\ref{sec:G-ACF} we introduce the new sample autocovariance estimator and calculate its bias for finite samples.
 We observe that the bias term for G-ACF is similar to the bias of empirical ACF except for a few small order end-effect terms that vanish as $n \to \infty$.
-In section \ref{sec:variance_est}, we introduce the globally-centered SVE and give a proof of strong consistency, bias, and variance calculations.
-We will elaborate on the estimator for ESS using G-SVE in section \ref{sec:ess}.
-Section \ref{sec:examples} gives an experimental study on three different examples for the proposed estimators.
+In Section~\ref{sec:variance_est}, we introduce the globally-centered SVE and give a proof of strong consistency, bias, and variance calculations.
+We will elaborate on the estimator for ESS using G-SVE in Section~\ref{sec:ess}.
+Section~\ref{sec:examples} gives an experimental study on three different examples for the proposed estimators.
 All the important proofs are given in the Appendix.
@@
 The target density has two well separated and non-equal modes.
+The target distribution $F$ defined on $\mathbb{R}$ is given by
+\[
+F(x) = 0.7\:\textrm{N}(-5, 1) + 0.3\: \textrm{N}(5, 0.5)
+\]
 Two Markov chains are started close to each mode.
@@
 We wish to make two points here: firstly, for small sample size, we observe that ACF gives extremely misleading estimates of autocovariance whereas G-ACF is very close to reality (Figure \ref{subfig:gauss-acf-1e4}).
-Whereas, sharing the information about Monte Carlo average across chains leads to better estimation of autocovariances.
 Secondly, for a large sample size, the estimates from G-ACF as well as ACF are equivalent.
@@
 \[
-\hat{\Gamma}_{G,s}(k) = \dfrac{1}{n} \sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
-\]
-
+\hat{\Gamma}_{G,s}(k) = \dfrac{1}{n} \sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T,
+\]
+and the averaged globally-centered ACF over all $m$ chains is given by 
+\[
+\hat{\Gamma}_G(k) = \dfrac{1}{m}\sum_{s=1}^m \hat{\Gamma}_{G,s}(k)\;.
+\]
 If the starting points of these parallel Markov chains are sufficiently dispersed, G-ACF provides more realistic estimation of lag covariances.
 \cite{priestley1981spectral} shows that the empirical estimator in Equation \ref{eq:empirical_acf} is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
-An unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, say $\Gamma^*(k)$.
-Nevertheless, the biased estimator is preferred for its lower mean square error (\cite{priestley1981spectral}).
-For a small $k$ relative to $n$, the two estimators are almost the same.
-However, for larger relative $k$ the variance of $\hat{\Gamma}(k)$ compensates for larger bias rendering a smaller mean square error than $\Gamma^*(k)$.
+Though, an unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, the biased estimator is preferred for its lower mean square error for larger relative $k$  (\cite{priestley1981spectral})
 
@@
 \[
-\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,. 
+\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = -\dfrac{\abs{k}}{n}\Gamma(k) - \dfrac{1}{m}\left(1- \dfrac{|k|}{n}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
 \]
@@
 % \begin{proof}
-%  The estimator for autocovariance with divisor $n$ is suggested by \cite{parzen1961approach} for its lesser mean square error despite having greater bias than the unbiased estimator with an $n - \abs{k}$ divisor.
+
 %  We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as
@@
 %  \end{equation}
-
-By proposition 1 in \cite{song1995optimal} 
-\begin{equation} \label{eq:song}
-\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
-\end{equation}
 
@@
 
-{\color{blue} Below is a remark}
-\begin{corollary} \label{cor:lag0_expectation}
+\begin{remark} \label{rem:lag0_expectation}
 \[
@@
 
-\end{corollary}
+\end{remark}
 
@@
 % subsection autocorrelation (end)
-{\color{blue}  Autocovariances will be used implictly in SVE estimators. But they are explicitly important in ACF plots via autocorrelations.
-
-Notation in the appendix is $\Gamma^{ii}_{G,s}$
-}
-
-For any component $i$, the autocorrelation is
-\[
-\rho^{(i)}(k) = \dfrac{\Gamma^{(i)}(k)}{\Gamma^{(i)}(0)}\,,
-\]
-and is particularly useful for visualizing the serial correlation in components of the Markov chain.
+%{\color{blue}  Autocovariances will be used implictly in SVE estimators. But they are explicitly important in ACF plots via autocorrelations.
+
+%Notation in the appendix is $\Gamma^{ii}_{G,s}$
+%}
+Lag-0 autocovariance are particularly useful in calculating the autocorrelations.The variance of $i^{th}$ component given by $\Gamma^{ii}(0)$. For any component $i$, the autocorrelation is
+\[
+\rho^{ii}(k) = \dfrac{\Gamma^{ii}(k)}{\Gamma^{ii}(0)}\,,
+\]
+and is instrumental in visualizing the serial correlation in components of the Markov chain.
 The typical estimate of the autocorrelation is constructed from  locally-centered autocovariance estimates which as was demonstrated in Section~\ref{sec:intro} can significantly underestimate the autocorrelation.
-\[
-\hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}
-\]
-{\color{blue} Add more about autocorrelation. Refer to Figure 2 above and the impacts of the correlation methods. }
+Instead, we calculate the globally-centered autocorrelation using the formula
+\[
+\hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}.
+\]
+Despite using similar centering in both numerator and denominator, the globally-centered autocorrelation is far greater than locally-centered autocorrelation for each component as is evident from Figure~\ref{fig:gauss:acf}.
 
@@
 
-Suppose $F$ is the target distribution on support $\chi \subseteq \mathbb{R}^d$. For $g:\chi \longrightarrow \mathbb{R}^p$ be an F-integrable function. We are interested in
-%
-\[
-\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)
-\]
-
-Let $\{X_{t}\}_{t \geq 1}$ denote the Harris ergodic (aperiodic, F-irreducible, and positive Harris recurrent) Markov chain having invariant distribution $F$.
-We will use the following Monte Carlo estimator in order to estimate $\mu$
-%
-\[
-\hat{\mu}_s = \dfrac{1}{n}\sum_{i = 1}^{n} g(X_{si}) \xrightarrow{a.s.} \mu \textrm{ as } n \to \infty
-\]
-
-We are interested in Markov chain average and therefore, throughout this paper, we will deal with the function $g(X) = X$.
+Let $g:\chi \longrightarrow \mathbb{R}^d$ be an F-integrable function. We are interested in the expected value
+%
+\[
+\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)\;.
+\]
+
+Let $Y$ denote the random variable $g(X)$ where $X \sim F$.
+Since we have $m$ chains of $n$ samples each, let us make following notations: (1) $Y_{st} = g(X_{st})$ for $t \in \{1, 2, ..., n\}$ and $s \in \{1, 2, ..., m\}$; (2) $\bar{Y}_s = \sum_{t=1}^{n}g(X_{st})/n$; and (3) $\bar{\bar{Y}} = \sum_{s=1}^{m}\bar{Y}_s/m$.
 To assess the reliability of our simulations, we are interested in Monte Carlo error, i.e.
-$\bar{\bar{X}} - \mu$.
+$\bar{Y_s} - \mu$ for the $s^{th}$ chain.
 The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
@@
 \]
-
- It is important to construct an estimator for $\Sigma$ which is very close to underlying reality.
-There are many techniques for estimating $\Sigma$ like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
-Due to its nice statistical properties and heavy dependence on autocovariance, we will only focus on SVE in this paper.
-SVE involves a truncated and weighted sum of autocovariances.
-We will give theoretical as well as experimental results for the version of SVE that uses our globally centered autocovariances.
-We call this globally-centered SVE (G-SVE).
 
@@
 The most common practice would be to combine the spectral variance estimates from $m$ chains by averaging over them.
-We call this technique average spectral variance estimator and denote it by $\hat{\Sigma}_A$).
-We propose using a globally-centered spectral variance estimator (G-SVE) wherein we use G-ACF to estimate the autocovariance.
+We call this technique average spectral variance estimator (A-SVE) and denote it by $\hat{\Sigma}_A$.
+Let $\hat{\Sigma}_{SV,s}$ denote the SVE for the $s^{th}$ chain, then the A-SVE is given by
+
+\[
+\hat{\Sigma}_A = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}\;.
+\]
+ We propose a globally-centered spectral variance estimator (G-SVE) wherein we use G-ACF to estimate the autocovariance.
 Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}.
@@
 \]
+Define
+%
+\[
+W_n = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right).
+\]
+We will consider a range of lag windows $w(x)$; where $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$.
 
@@
 \begin{ass}[Strong Invariance Principle (SIP)] \label{ass:sip}
-    We assume the SIP holds for the Markov chain.
-Here $\{X_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu$.
+    We assume the SIP holds for the Markov chains $\{Y_{st}\}_{t \geq 1} \; \forall s$.
+Here $\{Y_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu_g$.
 Let $\|.\|$ denote the Euclidean norm.
 Through SIP, there exists a $p \times p$ lower triangular matrix L, an increasing function $\psi$ on the integers, a finite random variable D, and a  sufficiently rich probability space such that, with probability 1, \\
-  $$\left\|\sum_{t=1}^{n}X_t - n\mu - LB(n)\right\| < D\psi(n)$$
+  $$\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n)$$
 
@@
 
-{\color{blue} Don't make this an assumption. Say this explicitly in Theorem 2. }
-
-\begin{ass} \label{ass:sve_consis} We assume that all the conditions given by \cite{vats:fleg:jon:2018} for strong consistency of the spectral variance estimator hold true.
-As a consequence, $\hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma$ as $n \to \infty$ for all Markov chains $s$.
-% \[
-% \hat{\Sigma}_{S,s} \xrightarrow{a.s.} \Sigma \textrm{ as } n \to \infty \;\; \forall s \in \{1,..., m\}
-% \]
-\end{ass}
-
 \begin{theorem}
 \label{th:consistency}
- Let the Assumptions \ref{ass:sip},\ref{ass:sve_consis} hold and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \to \Sigma$ with probability 1, as $n \to \infty$.
+ Let the Assumptions \ref{ass:sip} hold, $\hat{\Sigma}_{SV,s} \xrightarrow{a.s.} \Sigma \; \forall s$, and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \to \Sigma$ with probability 1, as $n \to \infty$.
 \end{theorem}
@@
 
-{\color{blue}: Make the following an assumption. Is $2\pi$ needed? Is $W_n$ always finite? }
 We are interested in the finding the bias for G-SVE estimator as a function of $n$. 
-The proof below applies to all the important range of lag windows $w(x)$; where $w(x)$ is a continuous, even fnction with $w(0)=1, \abs{w(x)} < c$, and $\int_{-\infty}^{\infty}w^2(x)dx < \infty$.
-Define
-%
-\[
-W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right).
-\]
-
-We have $W_n < \infty$ for all the important lag windows.
-
 \begin{ass} \label{ass:bias}
@@
 
-{\color{blue} Under what assumptions?}
 \begin{theorem}\label{th:G-SVE_bias}
-The limiting bias of replicated spectral variance is given by:
+Let the Assumption~\ref{ass:bias} hold, then the limiting bias of G-SVE is given by:
 \[
@@
 
-{\color{blue} Don't make this a separate assumption. Include in the statement of the theorem}
-\begin{ass} \label{ass:variance_cal}
-Let $\{X_{st}\}_{t \geq 1}$ be the $s^{th}$ Markov chain for which SIP holds. 
-\begin{enumerate}[a.]
-    \item $\E[D^4] < \infty$ where D is a finite random variable associated with the SIP
-    \item $\E[X^4] < \infty$ where $\{X\}$ is the stochastic process
-\end{enumerate}
-\end{ass}
-
 \begin{theorem} \label{th:G-SVE_variance}
- If Assumption \ref{ass:variance_cal} holds, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+ Let Assumption~\ref{ass:sip} holds, $\E[D^4] < \infty$ where D is a finite random variable associated with the SIP, and  $\E[Y^4] < \infty$, then $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
 \end{theorem}
@@
 
+% \begin{proof}
+
+We can break $\hat{\Gamma}_{G,s}$ into four parts for all $k \geq 1$ as:
+%  \[
+%  \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
+%  \]
+% %
+% where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
+% The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.
+
  % \begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
@@
 %
-Additionally, the locally-centered autocovariance exhibits the following expectation {\color{blue} + add small order term. Confirm with Priestly. }
+Additionally, the locally-centered autocovariance exhibits the following expectation 
  \begin{equation} \label{eq:priestly}
@@
 %
+As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$.
 Using \eqref{eq:priestly}, \eqref{eq:acf_2}, \eqref{eq:acf_3}, and \eqref{eq:acf_4} in \eqref{eq:acf_breakdown},
@@
 %
- We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
+
+ We can use the results of \cite{song1995optimal} to expand $\Var(\bar{X}_1)$. By proposition 1 in \cite{song1995optimal} 
+\[
+\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
+\]
+
+As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
  \begin{equation} \label{eq:G-_expec_breakdown}
@@
 %
-where both $O_1 \textrm{ and } O_2$ are the small order terms.
-By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.
-Consider the G-SVE estimator,
+where both $O_1 \textrm{ and } O_2$ are $\mathcal{O}(n^{-1})$ terms. By our assumptions, $\sum_{k=-\infty}^{\infty}\abs{k}^q\|\Gamma(h)\| < \infty$.  Consider the G-SVE estimator,
 \begin{align*}
@@
     &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\
-    & = P_1 + o \left( \dfrac{1}{n} \right)\,
+    & = P_1 + P_2
 \end{align*}
@@
 P_1 & = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
-% P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
-\end{align*}
+P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
+\end{align*}
+{\color{blue} Dootika: Add something about $P_2$ here as well. And I don't think we need the $W_n < \infty$ assumption. }
 %
@@
 
-\subsection{Proof of Theorem \ref{th:G-SVE_bias}}
-
-% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
-% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
+% \subsection{Proof of Theorem \ref{th:G-SVE_bias}}
+
+% % \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
+% % The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
 We are interested in finding the asymptotic bias here.
 Therefore we can write the expectation of replicated autocovariance in form of
-By \ref{eq:G-_expec_breakdown},
-\begin{align*}
-\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
-% &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + o \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
-\end{align*}
-%
-\begin{equation} \label{eq:G-_bias2}
-\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
-\end{equation}
-%
-where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  
-Consider the G-SVE estimator,
-\begin{align*}
- \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + o\left(n^{-1} \right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  o\left(n^{-1}\right)\right] \\
-    & = P_1 + o \left( \dfrac{1}{n} \right)\,,
-\end{align*}
-%
-where 
-\[
-P_1  = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
-% P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
-\]
-%
-Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
-\begin{equation}
-\label{eq:P1_decomp}
-P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
-\end{equation}
-%
-We deal with the three subterms of term $P_1$ individually. First,
-%    
-\begin{align*}
- {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
-\end{align*}
-%
-since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
-%
-\begin{align*}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
-\end{align*}
-For $q\geq 1$,
-\begin{align*}
-\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
-\end{align*}
-
-For $q <1$,
-\begin{align*}
-   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
-\end{align*}
-So,
-\begin{equation}
-\label{eq:P1_second}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
-\end{equation}
-Lastly, by our assumptions, for $x \to 0$
-\[
-\dfrac{1 - w(x)}{\abs{x}^q} = k_q + o(1)\,.
-\]
-For $x = k/b_n$, $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$.
- % where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
+% By \ref{eq:G-_expec_breakdown},
+% \begin{align*}
+% \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
+% % &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
+% & = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + o \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
+% \end{align*}
+% %
+% \begin{equation} \label{eq:G-_bias2}
+% \mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
+% \end{equation}
+% %
+% where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  
+% Consider the G-SVE estimator,
+% \begin{align*}
+%  \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+%     &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + o\left(n^{-1} \right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+%     &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  o\left(n^{-1}\right)\right] \\
+%     & = P_1 + o \left( \dfrac{1}{n} \right)\,,
+% \end{align*}
+% %
+% where 
 % \[
-     % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
+% P_1  = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
+% % P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
 % \]
-So,
-\begin{align*}
-     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
-     & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
-     & = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right) \numberthis \label{eq:P1_third}\,.
-\end{align*}
-%
- % Finally, we will solve for $P_2$.
+% %
+% Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
+% \begin{equation}
+% \label{eq:P1_decomp}
+% P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
+% \end{equation}
+% %
+% We deal with the three subterms of term $P_1$ individually. First,
+% %    
+% \begin{align*}
+%  {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
+% \end{align*}
+% %
+% since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
+% %
+% \begin{align*}
+%  \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
+% \end{align*}
+% For $q\geq 1$,
+% \begin{align*}
+% \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
+% \end{align*}
+
+% For $q <1$,
+% \begin{align*}
+%    \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
+% \end{align*}
+% So,
+% \begin{equation}
+% \label{eq:P1_second}
+%  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
+% \end{equation}
+% Lastly, by our assumptions, for $x \to 0$
+% \[
+% \dfrac{1 - w(x)}{\abs{x}^q} = k_q + o(1)\,.
+% \]
+% For $x = k/b_n$, $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$.
+%  % where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
+%      % \[
+%      % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
+%      % \]
+% So,
+% \begin{align*}
+%      \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
+%      & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
+%      & = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right) \numberthis \label{eq:P1_third}\,.
+% \end{align*}
+% %
+%  % Finally, we will solve for $P_2$.
 Note that $O_2$ is independent of $k$.
@@
 We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
- % \begin{align*}
- %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
- %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
- %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
- %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
- %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
- % \end{align*}
-  %
-%
-Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
-\[
-\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
-\]
-which completes the result.
-%
- % We have shown that all, but one, terms are $o(1/b_n^q)$.
+%  % \begin{align*}
+%  %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
+%  %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
+%  %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
+%  %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
+%  %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
+%  % \end{align*}
+%   %
+% %
+% Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
+% \[
+% \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
+% \]
+% which completes the result.
+% %
+%  % We have shown that all, but one, terms are $o(1/b_n^q)$.
 Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
@@
 Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
-% \end{proof}
+% % \end{proof}
 

### 2020-08-03 Paper/main.tex
Introduction version 1 done.

@@
 However, tools on estimating ACvF are largely constructed for output from one MCMC chain.
+{\color{blue} a little bit more here}.
 
@@
 Let $F$ be the target distribution with mean $\mu$ defined on the set $\X \subseteq \mathbb{R}^p$ equipped with a countably generated Borel $\sigma$-field $\mathcal{B}(\X)$.
-Let $\{X_1, X_2, ..., X_n\}$ be an $F$-Harris ergodic (aperiodic, $F$-irreducible, and positive Harris recurrent) Markov chain.
+Let $\{X_t\}$ be an $F$-Harris ergodic stationary Markov chain \citep[see][for definitions]{meyn:twee:2009} employed to learn characteristics about $F$.
 % If $\bar{X} = n^{-1} \sum_{t=1}^{n}X_t$ , then with probability 1, $\bar{X} \to \mu$ as $n \to \infty$. \\
-
-For a stationary Markov chain, the autocovariance function at lag $k$ depends only on $k$ and is defined as 
-%
-\[
-    \Gamma(k) = \Cov(X_t, X_{t+k})= \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
-\]
-
-A popular sample autocovariance matrix at lag-$k$ is given by
+The Markov chain is covariance stationary so that
+th ACvF at lag $k$ depends only on $k$ and is defined as 
+%
+\[
+    \Gamma(k) = \Cov_F(X_1, X_{1+k})= \mathbb{E}_F \left[(X_1 - \mu)(X_{1+k} - \mu)^T \right]\,.
+\]
+Estimating $\Gamma(k)$ is critical to assessing the quality of the sampler and the quality of  sample statistics. The standard estimator is the sample autocovariance matrix at lag $k$
 %
 \begin{equation} \label{eq:empirical_acf}
-    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{(t+\abs{k})} - \bar{X})^T.
+    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}} \left(X_t - \bar{X} \right) \left(X_{t+\abs{k}} - \bar{X} \right)^T\,.
 \end{equation}
-
-It is a known fact that most of the Markov chains obtained from practical MCMC algorithms are not stationary.
+%
+% It is a known fact that most of the Markov chains obtained from practical MCMC algorithms are not stationary.
 Regardless, Equation~\ref{eq:empirical_acf} provides the empirical estimator for ACF at a particular lag for the Markov chain with any initial distribution (\cite{geyer2011introduction}).\\
 
-Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
+% Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
 However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
@@
 Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains.
-We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.
+For single-chain MCMC runs, the estimator $\hat{\Gamma}(k)$ is used to construct autocorrelation (ACF) plots, to estimate the long-run variance of Monte Carlo estimators \cite{hannan:1970,dame:1991}, and to estimate effective sample size for an estimation problem \cite{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
+
+However, there is no unified approach to constructing estimators of $\Gamma(k)$ for multiple-chain implementations.
+Specifically, parallel MCMC chains are often spread across the state space so as to adequately capture high density areas.
+For slow mixing Markov chains and multi-modal targets, the chains take time to traverse the space so that estimates of $\mu$ can be vastly different.
+The sample ACvF from each chain is typically underestimated yielding false sense of security about the quality of process.
+
+% We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.
 This approach is especially relevant to MCMC wherein multiple chain sampling is computationally possible and statistically desirable for making informative inferences.
 Our goal is to pool in the information from all the Markov chains while estimating the autocovariances.
-\\
-
- A commonly faced problem with the MCMC models is the slow mixing property.
+
+ % A commonly faced problem with the MCMC models is the slow mixing property.
 Especially in case of multi modal target distributions, it has been observed that the Markov chains tend to get \textit{stuck} in a particular mode for a long time.
 In such situations, single chain empirical ACF will severely underestimate the autocovariance.
-We propose an autocovariance estimator called globally-centered autocovariance function (G-ACF) with a simple fix in centering which has been observed to show drastically better results in many cases.
-We also prove that our estimator compensates the negative bias of the empirical ACF estimator to give estimates that are closer to reality.
-We will further study the impact of G-ACF in calculation of two important applications of ACF (1) asymptotic variance of Markov chain average and (2) effective sample size (ESS).\\
-
-Let $g: \chi \to \mathbb{R}^d$ be an F-integrable function and suppose we are interested in estimating the expected value $\mu_g = \mathbb{E}_F[g(X)]$.
+ We propose a globally-centered ACvF (G-ACvF) that centers the Markov chain around the overall mean vector from all $m$ chains.
+We show that the bias under stationarity for G-ACvF is lower than $\hat{\Gamma}(k)$ and through various examples empirically demonstrate improved estimation.
+We employ the G-ACvF estimators to construct autocorrelation plots which leads to remarkably improvements.
+A demonstrative example is at the end of this Section.
+
+% We will further study the impact of G-ACF in calculation of two important applications of ACF (1) asymptotic variance of Markov chain average and (2) effective sample size (ESS).
+
+ACvFs are required to estimate the log-run variance of Monte Carlo averages.
+Specifically, spectral variance estimators are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$.
+We replace $\hat{\Gamma}(k)$ with G-ACvF in spectral variance estimators and show strong consistency of this estimator under weak conditions.
+In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimator of $\Sigma$.
+Spectral variance estimators can be slow to prohibitively expensive to calculate \citep{liu:fleg:2018}.
+We relieve the computational burden, we adapt the fast algorithm of \cite{heberle2017fast} for G-ACvFs that dramatically reduces computation time.
+The globally-centered spectral variance estimators in employed in the computation of effective sample size and safeguards against early termination of the MCMC process and improved reliability of estimators.
+
+% Let $g: \X \to \mathbb{R}^d$ be an F-integrable function and suppose we are interested in estimating the expected value $\mu_g = \mathbb{E}_F[g(X)]$.
 We know that $\sum_{t=1}^{n}g(X_t)/n$ converges to $\mu_g$ as $n \to \infty$ almost surely.
 MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite and the Markov chain mixes slowly.
-One of the important criteria to determine the quality of estimation is the Monte Carlo aymptotic covariance matrix which is given by an infinite summation of autocovariance matrices for all lags.
+% One of the important criteria to determine the quality of estimation is the Monte Carlo aymptotic covariance matrix which is given by an infinite summation of autocovariance matrices for all lags.
 For a slowly mixing Markov chain, underestimated autocovariances will deliver underestimated asymptotic variance.
@@
 We propose a version of SVE that uses our globally centered autocovariances.
-We call this globally-centered SVE (G-SVE).\\
-
-A more powerful estimator of Monte Carlo asymptotic covariance matrix can enable us to estimate the effective sample size for the Markov chain which is closer to reality.
+We call this globally-centered SVE (G-SVE).
+
+% A more powerful estimator of Monte Carlo variability can enable us to estimate the effective sample size for the Markov chain which is closer to reality.
 There are many criteria for terminating simulation like fixed-time rule, sequencial fixed-volume rule (see \cite{glynn1992asymptotic}), and using Gelman Rubin diagnostics (\cite{gelman1992inference}).
@@
 The quality of estimation of asymptotic covariance matrix is critical in estimation of the ESS.
-We will successfully show that the G-SVE estimates the truth better and prevents the premature stopping of Markov chain.\\
-
-The rest of the paper is arranged as follows.
+We will successfully show that the G-SVE estimates the truth better and prevents the premature stopping of Markov chain.
+
+% The rest of the paper is arranged as follows.
 In Section~\ref{sec:G-ACF} we introduce the new sample autocovariance estimator and calculate its bias for finite samples.
@@
 
-\begin{example}[Demonstrative example]
-
-We demonstrate the striking difference in the ACF plots through mixture of Gaussian target density using a random-walk Metropolis-Hastings sampler.
-The target density has two well separated and non-equal modes.
-The target distribution $F$ defined on $\mathbb{R}$ is given by
-\[
-F(x) = 0.7\:\textrm{N}(-5, 1) + 0.3\: \textrm{N}(5, 0.5)
-\]
-Two Markov chains are started close to each mode.
-It can be seen in Figure \ref{fig:gaussian-trace} that for the first $10^4$ samples, the chains do not communicate with the other mode.
-Whereas for a sample size of $10^5$, the chains have jumped modes and therefore, a single chain can give reliable information about the distribution.
-We wish to make two points here: firstly, for small sample size, we observe that ACF gives extremely misleading estimates of autocovariance whereas G-ACF is very close to reality (Figure \ref{subfig:gauss-acf-1e4}).
-Secondly, for a large sample size, the estimates from G-ACF as well as ACF are equivalent.
-Figure \ref{subfig:gauss-trace_1e5} depicts the scenario when convergence is achieved.
-This shows that G-ACF is at least as good as ACF; hence safe to use in any setting.
+\subsection{Demonstrative example} % (fold)
+\label{sub:demonstrative_example}
+
+% subsection demonstrative_example (end)
+% \begin{example}[Demonstrative example]
+
+We demonstrate the striking difference in estimation of $\Gamma(k)$ via ACF plots.
+Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density.
+That is, $F$ is the distribution with density
+\[
+f(x) = 0.7\,f(x; -5, 1) + 0.3\,f(x; 5, 0.5)\,,
+\]
+where $f(x; a,b)$ is the density of a normal distribution with mean $a$ and variance $b$. 
+Two Markov chains are started at each mode.
+Figure~\ref{fig:gaussian-trace} indicates that in the first $10^4$ samples, the chains do not jump modes so that both Markov chains yield different estimates of the population mean, $\mu$.
+At $10^5$ sample size, both Markov chains have traversed the state space reasonably and yield similar estimates of $\mu$.
+We make two points here: first, for small sample size, we observe that the locally-centered ACF gives misleading estimates   whereas G-ACF accounts for the discrepancy in sample means.
+This is evident from the ACF plots  in Figure~\ref{subfig:gauss-acf-1e4}.
+Second, for a large sample size, the estimates from G-ACF as well as ACF are equivalent in Figure \ref{subfig:gauss-trace_1e5}.
 
@@
 \end{figure}
-\end{example}
 
@@
 
-There are only a handful of stochastic processes where the true autocovariance and $\Sigma$ are known.
-To compare the estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
-A more promising advantage of our estimators is observed when the target distribution is multi-modal.
-For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note} in section \ref{ex:boomerang}.
+In this section we consider three different target distributions and sample multiple Markov chains using MCMC to analyse the performance of our globally-centered estimators experimentally.
+We will make the following comparisons - (1) A-ACF and G-ACF; (2) A-SVE and G-SVE; (3) estimates of $ESS/mn$ using A-SVE and G-SVE.
+In all the examples we consider the function $g(x) = x$, which implies the Markov chain $\{Y_t\}$ and $\{X_t\}$ are the same.
+There are only a handful of MCMC chains where the true autocovariance and asymptotic variance are known.
+To compare the globally and locally-centered estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
+A distinct advantage of our estimators is observed when the target distribution is multi-modal.
+For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note}.
 Through this example, we will also show that in case of nicely mixing Markov chains, these estimators give almost equivalent results.
-As a consequence, while out replicated version of variance estimator is better in cases where the Markov chains do not explore the entire sample space in finite time, it is harmless to be used in cases where they do.
-Lastly, we consider a real-life example of finding unknown locations of sensors using noisy distance data in section \ref{ex:sensor_post}.
+Lastly, we consider a real-life example of finding unknown locations of sensors using noisy distance data.
 The posterior distribution is this case is marginally bimodal in all dimensions.
 All the examples have been selected to display some kind of \textit{sticky} nature in the Markov chains.
-In such scenario, we successfully show that our globally-centered estimators yield better results as compared to the classical autocovariance function, spectral variance estimator, and effective sample size.
+In such scenario, we successfully show that our globally-centered estimators yield better results as compared to the classical single-chain estimators for autocovariance, asymptotic variance, and effective sample size.
 
@@
 
-We examine the vector autoregressive process of order 1 (VAR(1)) where the true autocovariance in known in closed form. Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
+We examine the vector autoregressive process of order 1 (VAR(1)) where the true autocovariance in known in closed form.
+We want to deliberately make the Markov chains explore the sample space slowly.
+Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
 %
@@
 \]
+
+ \begin{figure}[h]
+     \centering
+     \begin{subfigure}[h]{0.4\textwidth}
+          \centering
+          \includegraphics[width=\textwidth]{plots/var-sp_n1e3.pdf}
+          \caption{$n = 1000$}
+          \label{subfig:var-sp_1000}
+      \end{subfigure}
+      \begin{subfigure}[h]{0.4\textwidth}
+          \centering
+          \includegraphics[width=\textwidth]{plots/var-sp_n1e4.pdf}
+          \caption{$n = 10000$}
+          \label{subfig:var-sp_10000}
+      \end{subfigure}
+     \caption{Scatter plot of two out of five slowly mixing Markov chains starting from opposite sides of known mean.  Sample size of $1000$ (left) and $10000$ (right).}
+     \label{fig:var-sp}
+ \end{figure}
 
@@
 We run five parallel Markov chains with their starting points evenly distributed about the center of invariant distribution.
-Figure \ref{subfig:var-sp_500} shows that for the first 500 samples, the chains have not explored the sample space well unlike Figure \ref{subfig:var-sp_50000} with $5\cdot 10^4$ samples.
-
-% \begin{figure}[h]
-%     \centering
-%     \begin{subfigure}[h]{0.4\textwidth}
-%          \centering
-%          \includegraphics[width=\textwidth]{plots/scatter_plot_500.pdf}
-%          \caption{$n = 500$}
-%          \label{subfig:var-sp_500}
-%      \end{subfigure}
-%      \begin{subfigure}[h]{0.4\textwidth}
-%          \centering
-%          \includegraphics[width=\textwidth]{plots/scatter_plot_50000.pdf}
-%          \caption{$n = 5 \times 10^4$}
-%          \label{subfig:var-sp_50000}
-%      \end{subfigure}
-%     \caption{Scatter plot of five Markov chains for different sample sizes.}
-%     \label{fig:var-sp}
-% \end{figure}
-
-\begin{figure}[htbp]
- \begin{subfigure}{\textwidth}
-   \centering
-   \includegraphics[width=.6\linewidth]{plots/acf,n=500.pdf}
-   \caption{$n = 500$}
-   \label{subfig:acf-500}
+There is very high correlation between the two components in the target distribution for the chosen value of $\Phi$ and $\Omega$.
+As a result, it takes a long time for the Markov chain to explore the sample space significantly.
+Let $\sigma_{ij}$ denote the $ij^{th}$ element of $\Sigma$.
+We sample five parallel chains and plot the first and fifth chain in Figure \ref{subfig:var-sp_500} for two different simulation sizes.
+The first chain starts at $(\sigma_{11}/2, \sigma_{22}/2)$ and the fifth chains starts from $(-\sigma_{11}/2, -\sigma_{22}/2)$.
+For a sample size of $1000$, the chains have not moved enough from their starting points.
+Whereas, for a $n = 10,000$, the chains seem to have explored the sample space fairly well.\\
+
+\begin{figure}[h]
+ \begin{subfigure}[h]{\textwidth}
+   \centering
+   \includegraphics[width=.7\linewidth, height = 2in]{plots/var-acf_n1000.pdf}
+   \caption{$n = 10^3$}
+   \label{subfig:var-acf_n1e3}
 \end{subfigure}\\
-\begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=.6\linewidth]{plots/acf,n=10000.pdf} 
+\begin{subfigure}[h]{\textwidth}
+  \centering
+  \includegraphics[width=.7\linewidth, height = 2in]{plots/var-acf_n10000.pdf} 
   \caption{$n = 10^4$}
-  \label{subfig:acf-5e4}
-\end{subfigure}
+  \label{subfig:var-acf_n1e5}
+\end{subfigure}
+
 \caption{Autocorrelation plot for ACF and G-ACF for first chain out of two parallel Markov chains.
-First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
+First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 10^3$, not converged yet; (b): $n =  10^4$, converged}
 \label{fig:var-acf}
@@
 
+The locally and globally-centered autocorrelations averaged over all the chains have been shown in Figure~\ref{var-acf} for two different simulation sizes where the true ACrF is shown in red.
+When the individual chains have not explored well, the local sample mean is closer to the samples and possibly far away from the true mean.
+As a consequence, the empirical ACrF estimator severely underestimate the known true autocorrelations.
+When the starting values are nicely dispersed, the global mean provides a more reliable estimate of actual mean and hence, G-ACrF is closer to reality.
+In subfigure~\ref{subfig:var-acf_n1e5}, the convergence property of sample means has kicked in for each chain.
+Therefore, both the estimators provide equivalent results.
+\\
+
 \begin{figure}[htbp]
     \centering
-    \includegraphics[width = .35\textwidth]{plots/var-ess.pdf}
-    \caption{Running plots for $\hat{\text{ESS}}/mn$ calculated using ASV and G-SVE with the truth.}
-    \label{fig:var-ess}
+    \begin{subfigure}{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/var-frob.pdf}
+      \caption{log-Frobenius norm}
+      \label{subfig:var-frob}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/var-ess.pdf}
+      \caption{$\log(\hat{ESS}/mn)$}
+      \label{subfig:var-frob}
+    \end{subfigure}
+    \caption{(a) Running plot for logarithm of Frobenius norm of A-SVE and G-SVE from $n = 500$ to $n = 10^5$.
+(b) Running plot for logarithm of $\hat{ESS}/mn$ calculated using A-SVE and G-SVE from $n=500$ to $n=10^5$.}
+    \label{fig:var-frob_n_ess}
 \end{figure}
 
+The quality of estimation of $\Sigma$ and $ESS/mn$ has been studied through two running plots - (a) convergence of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log(\|\hat{\Sigma}_G\|_F)$ as $n$ increases and (b) convergence of $\log(\hat{ESS}_A/mn)$ and $\log(\hat{ESS}_G/mn)$ as $n$ increases.
+In practice, it is preferred to slightly overestimate both the values than to underestimate.
+In Figure~\ref{fig:var-frob_n_ess}, both the running plots are shown along with the green horizontal line which marks the truth.
+We run the simulations for 50 replications for each value of $n$ and plot the average as well as the $95\%$ confidence interval.
+We run the simulations for a maximum sample size of $10^5$ until when, it can be seen that $\|\hat{\Sigma}_G\|_F$ and $\|\hat{\Sigma}_A\|_F$ have not converged.
+However, the globally-centered estimator is always closer to reality.
+Before actual convergence, it can be observed that $\hat{ESS}_G/mn$ overestimates the effective sample size but it is preferred to sample more as compared to premature stopping of the sampling process.\\
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{|c|c|c|}
+    n & A-SVE & G-SVE\\
+    \hline
+    1000 & 0.526 & 0.975\\
+    5000 & 0.622 & 0.963\\
+    10,000 & 0.694 & 0.953\\
+    50,000 & 0.864 & 0.944\\
+    100,000 & 0.901 & 0.943\\
+    \end{tabular}
+    \caption{Coverage probabilities for a $95$ percent confidence interval of global mean constructed using $A-SVE/mn$ and $G-SVE/mn$ as variance estimates around the known mean.}
+    \label{tab:var-coverage}
+\end{table}
+
+We also report the coverage probabilities for a $95\%$ confidence interval constructed using $\hat{\Sigma}_A$ and $\hat{\Sigma}_G$ because the true mean is known here.
+Table~\ref{tab:var-coverage} shows that for each sample size, the globally-centered SV estimator for variance gives better coverage than A-SVE.
+At $n=10^5$, the convergence nature starts appearing and both the estimators give good coverage probability.
+
 \subsection{Boomerang Distribution} \label{ex:boomerang}
 
-We will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions.
+Our estimators perform exceptionally better than the classical single-chain estimators in case of multimodal target distribution.
+To that end, we will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions.
 This allows us to sample parallel Markov chains using the Gibbs sampler.
@@
 
-We use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ which ensures bimodality for our purpose.
-Let $n$ be the number of samples in each chain and $m$ be the number of Markov chain replications.
-Finding the actual mean of this distribution in closed form is difficult.
-Therefore, we use numerical integration with fine tuning to calculate it.
-We sample two parallel Markov chains with well-separated starting values.
-
-\begin{comment}
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
@@
         \centering
-        \includegraphics[width = \textwidth]{plots/boom-pers_1_3_8.pdf}
+        \includegraphics[width = \textwidth]{plots/boom-3d_density_plot_1_3_8.pdf}
         \caption{$A = 1, B = 3, C = 8$}
@@
         \centering
-        \includegraphics[width = \textwidth]{plots/boom-pers_1_10_7.pdf}
+        \includegraphics[width = \textwidth]{plots/boom-3d_density_plot_1_10_7.pdf}
         \caption{$A = 1, B = 10, C = 7$}
@@
 \end{figure}
-\end{comment}
-
-\begin{comment}
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[h]{.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/scatter_n1000.pdf}
-      \caption{$n = 1000$}
-      \label{subfig:boom-sp_1e3}
-    \end{subfigure}
-    \begin{subfigure}[h]{.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/scatter_n50000.pdf}
-      \caption{$n = 50000$}
-      \label{boom-sp_1e4}
-    \end{subfigure}
-    \caption{The scatter plots for two parallel Markov chains. (a): Both the chains are stuck in one of the mode (b): Both the chains have travelled and explored both the modes.}
+
+We report results for two different bi-modal settings (parameterizations) in this example.
+Firstly, we use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ wherein the two modes are well-separated with a very low connection (Setting-1, Figure~\ref{subfig:boom-pers_1_3_8}).
+Secondly, to examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$ wherein the two model are closer and well-connected (Setting-2, Figure~\ref{subfig:boom-pers_1_10_7}).
+We sample five parallel chains with starting points dispersed uniformly in the first quadrant.
+Finding the actual mean of this distribution in closed form is difficult.
+Therefore, we use numerical integration with fine tuning to calculate it.
+To visualize the sticky nature of Markov chains in Setting-1, we show a scatter plot of two Markov chains starting near the two modes in Figure~\ref{fig:boom-sp}.
+Figure~\ref{fig:boom-sp} shows the scatter plot for both settings for $n=1000$.
+For the first thousand samples, both the chains are oblivious of the existence of another mode in setting-1.
+Whereas in setting-2, the chains have mixed fairly well even for $n=1000$.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[h]{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-sp_1_3_8.pdf}
+      \caption{$A = 1,\; B = 3, \; C = 8$}
+      \label{subfig:boom-sp_1_3_8}
+    \end{subfigure}
+    \begin{subfigure}[h]{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-sp_1_10_7.pdf}
+      \caption{$A = 1, \; B = 10, \; C = 7$}
+      \label{subfig:boom-sp_1_10_7}
+    \end{subfigure}
+    \caption{Scatter plots for Setting-1 (left) and Setting-2 (right) at a sample size $n = 1000$.}
     \label{fig:boom-sp}
 \end{figure}
-\end{comment}
-
-%
-In Figure \ref{fig:boom-sp}, we demonstrate the ``sticky'' nature of the Markov chains.
-For the first thousand samples, both the chains are oblivious of the existence of another mode.
-By ten thousand samples, both the Markov chains have explored the two modes.
-This property will affect the estimation of ACF from a single chain.
-In Figure \ref{subfig:boom-acf_1e3}, the ACF is severely underestimated because the first chain has not jumped to the other mode.
-Whereas, in Figure \ref{subfig:boom-acf_1e4}, both ACF and G-ACF give almost similar results indicating that both modes have been explored by chain-1.
+
+%
+ In Figure \ref{subfig:boom-acf_1_3_8_n1e3}, the autocorrelations are severely underestimated by A-ACF because the chains have not jumped modes.
+Whereas, in Figure \ref{subfig:boom-acf_1_3_8_n1e5}, both ACF and G-ACF give almost indistinguishable results indicating that A-ACF and G-ACF have converged.
+We can observe in Figure~\ref{fig:boom-acf_1_10_7_n1e3} that A-ACF and G-ACF give similar results for simulation setting-2.
+The Markov chains explore both the modes in 1000 iterations only.
+Therefore, the global and local means do not differ significantly.\\
 
@@
       \centering
-      \includegraphics[width = .8\textwidth]{plots/boom-acf,n=1000.pdf}
+      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf_1_3_8_n1000.pdf}
       \caption{$n = 1000$}
-      \label{subfig:boom-acf_1e3}
+      \label{subfig:boom-acf_1_3_8_n1e3}
     \end{subfigure}
@@
       \centering
-      \includegraphics[width = .8\textwidth]{plots/boom-acf,n=50000.pdf}
-      \caption{$n = 50000$}
-      \label{subfig:boom-acf_1e4}
-    \end{subfigure}
-    \caption{ACF and G-ACF for component-1 of chain-1 at two different number of Monte Carlo samples. }
+      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf_n_1_3_8_n1e+05.pdf}
+      \caption{$n = 100000$}
+      \label{subfig:boom-acf_1_3_8_n1e5}
+    \end{subfigure}
+    \caption{A-ACF and G-ACF of component-1 at two different sample size for simulation setting-1.  }
     \label{fig:boom-acf}
@@
 
-We also run five parallel Markov chains with well-separated starting points.
-In Table \ref{table:boom-coverage_1_3_8}, we give the coverage probabilities for $95 \%$ confidence interval for both the estimator.
-We can see that the G-SVE gives better coverage probabilities for all the $n$.
-For smaller sample size, the coverage probability of G-SVE is significantly higher than A-SVE.
-As the number of samples per chain increases, they start coming closer due to the strong consistency of both the estimators.
-
-\begin{table}[htbp]
-\centering
-    \begin{tabular}{|c|l|l|l|l|}
-    % \toprule
-    \hline
-        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
-        \hline
-        & ASV & G-SVE & ASV & G-SVE\\
-        \hline
-        $1000$ & 0.612 & 0.689 & 0.602 & 0.753   \\
-        $2000$ & 0.693 & 0.751 & 0.735 & 0.827 \\
-        $5000$  & 0.826 & 0.854 & 0.847 & 0.880 \\
-        $10000$  & 0.862 & 0.868 & 0.884 & 0.907 \\
-        $20000$ & 0.899 & 0.906 & 0.922 & 0.934  \\ \hline
-    % \bottomrule
-    \end{tabular}
-    \caption{Coverage probabilities for parameter values $A = 1,\; B = 3,\; C = 8$. }
-    \label{table:boom-coverage_1_3_8}
-\end{table}
-
-A good estimate of ESS is crucial to determine when to stop the simulations.
-We can see in Figure \ref{fig:run_ess} that for the first few thousand samples, A-SVE gives misleadingly higher $\hat{ESS}/mn$ than G-SVE.
-This can cause us to stop the sampling before the sample space has been explored by the chains.
-The inferences derived from this chain would then be severely non-informative.
+\begin{figure}
+    \centering
+    \includegraphics[width = 0.8\textwidth, height = 2in ]{plots/boom-acf_1_10_7_n1000.pdf}
+    \caption{A-ACF and G-ACF of component-1 for simulation setting-2}
+    \label{fig:boom-acf_1_10_7_n1e3}
+\end{figure}
 
@@
 
-    \begin{subfigure}[h]{.3\textwidth}
-      \centering
-      \includegraphics[width = 1.1\textwidth]{plots/boom-ess1.pdf}
+    \begin{subfigure}[h]{.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-ess_1_3_8.pdf}
       \caption{$A = 1, \; B = 3, \; C = 8$}
@@
     \end{subfigure} \hspace{1cm}
-    \begin{subfigure}[h]{.3\textwidth}
-      \centering
-      \includegraphics[width = 1.1\textwidth]{plots/boom-ess2.pdf}
+    \begin{subfigure}[h]{.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-ess_1_10_7.pdf}
       \caption{$A = 1, \; B=10, \; C = 7 $}
@@
 
-To examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$.
-This is also a bimodal distribution, however, the two modes interact well with each other (Figure \ref{subfig:boom-pers_1_10_7}).
-In Figure \ref{fig:boom-ess_1_10_7}, we observe that both G-SVE and A-SVE give almost the same estimates for ESS.
-Similar is the case with coverage probabilities in Table \ref{table:boom-coverage_1_10_7} for a $95\%$ confidence region.
+A good estimate of ESS is crucial to determine when to stop the simulations.
+We can see in Figure \ref{fig:boom-ess} that for the first few thousand samples, A-SVE gives misleadingly higher estimates of $ESS/mn$ than G-SVE.
+This can cause us to stop the sampling before each chain jumps to the other mode.
+As a consequence, each chain will correspond to a uni-modal target distribution.
+Whereas, as expected, the ESS estimates for setting-2 are almost same.\\
 
@@
 \centering
-    \begin{tabular}{|c|l|l|l|l|}
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
     % \toprule
     \hline
-        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
+         \multicolumn{5}{|c|}{Setting-1} & \multicolumn{5}{|c|}{Setting-2}\\
         \hline
-        & ASV & G-SVE & ASV & G-SVE\\
+        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$} & $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
         \hline
-        $10000$ & 0.873 & 0.884 & 0.875 & 0.898   \\
-        $2000$ & 0.881 &  0.888 & 0.897    & 0.914     \\
-        $5000$  & 0.902 & 0.908 &  0.919 & 0.929\\
-        $10000$  & 0.923 & 0.927 & 0.925 & 0.926 \\
-        $50000$ & 0.951& 0.952 & 0.939 & 0.939  \\ \hline
+        & A-SVE & G-SVE & A-SVE & G-SVE & & A-SVE & G-SVE & A-SVE & G-SVE\\
+        \hline
+        $1000$ & 0.800 & 0.877 & 0.145 & 0.268 & 1000 & 0.873 & 0.884 & 0.875 & 0.898  \\
+        $5000$ & 0.633 &  0.727 & 0.436 & 0.650 & 2000 & 0.881 & 0.888 & 0.897 & 0.914    \\
+        $10000$  & 0.585 & 0.690 &  0.552 & 0.750 & 5000 & 0.902 & 0.908 & 0.919 & 0.929\\
+        $50000$  & 0.778 & 0.815 & 0.805 & 0.872 & 10000 & 0.923 & 0.927 & 0.925 & 0.926\\
+        $100000$ & 0.851 & 0.867 & 0.863 & 0.897 & 50000 & 0.951 & 0.952 & 0.939 & 0.939\\ \hline
     % \bottomrule
     \end{tabular}
-    \caption{Coverage probabilities for parameter values $A = 1,\; B = 10,\; C = 7$. }
-    \label{table:boom-coverage_1_10_7}
+    \caption{Boomerang. Coverage probabilities for $m=2$ and $m=5$ for both the simulation settings. }
+    \label{table:boom-coverage}
 \end{table}
+
+Since a numerical approximation of the true mean is available, we construct $95\%$ confidence interval using A-SVE and G-SVE.
+We report the coverage probabilities for a 1000 replications at different sample sizes.
+For both the simulation settings, we provide coverage probabilities for $m=2$ and $m=5$.
+Table \ref{table:boom-coverage} reports all the results.
+In setting-1, it can be observed that G-SVE gives consistently higher coverage probability than A-SVE.
+Whereas for setting-2, the results are almost similar.
 
@@
 The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$.
-Let $z{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed.
+Let $z_{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed.
 The probability model is then,
@@
 We follow the Markov chain structure as described by \cite{tak2018repelling} and sample from the four bivariate conditionals for each sensor location using a Gibbs sampler.
-In their paper on Repelling AttG-tive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of three different sampling techniques namely - Metropolis, RAM and Tempered Transitions (TT).
+In their paper on Repelling Attractive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of three different sampling techniques namely - Metropolis, RAM and Tempered Transitions (TT).
 RAM is shown to improve the acceptance rate by a factor of at least 5.5 over Metropolis using the same jumping scale.
@@
 
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width = .7\textwidth]{plots/sensor-trace.pdf}
-    \caption{trace plots for the x-component of all four locations of the third chain.}
-    \label{fig:sensor-trace-3}
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[h]{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/sensor-sp_loc1.pdf}
+      \caption{Location-1; $n=10^5$}
+      \label{subfig:sensor-sp_loc1}
+    \end{subfigure}
+    \begin{subfigure}[h]{0.5\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/sensor-trace_loc1.pdf}
+      \caption{$x_{11}$ and $x_{12}$; $n=10^5$}
+      \label{subfig:sensor-trace_loc1}
+    \end{subfigure}
+    \caption{Sensor Network.
+(a) Scatter plot ($x_{12} \textrm{ vs } x_{11}$) for a Markov chain of length $n=10^5$; (b) Trace plots  of $x_{11}$ and $x_{12}$ for two chains started near the two modes.}
+    \label{fig:sensor-sp_n_tarce}
 \end{figure}
 
-% \begin{figure}[h]
-%     \centering
-%     \begin{subfigure}[h]{.8\textwidth}
-%       \centering
-%       \includegraphics[width = \textwidth, height = 2in]{plots/sensoG-ACF-n1000.pdf}
-%       \caption{$n = 10^3$}
-%       \label{subfig:sensoG-ACF_n1e3}
-%     \end{subfigure}
-%     \begin{subfigure}[h]{.8\textwidth}
-%       \centering
-%       \includegraphics[width = \textwidth, height = 2in]{plots/sensoG-ACF-n1e5.pdf}
-%       \caption{$n = 10^5$}
-%       \label{subfig:sensoG-ACF_n1e5}
-%     \end{subfigure}
-%     \caption{ACF and G-ACF for component-3 of chain-3 at two different number of Monte Carlo samples. }
-%     \label{fig:sensoG-ACF}
-% \end{figure}
+ \begin{figure}[h]
+     \centering
+     \begin{subfigure}[h]{.4\textwidth}
+       \centering
+       \includegraphics[width = \textwidth]{plots/sensor-acf_n5e3.pdf}
+       \caption{$n = 5 \times 10^3$}
+       \label{subfig:sensor-acf_n5e3}
+     \end{subfigure}
+     \begin{subfigure}[h]{.4\textwidth}
+       \centering
+       \includegraphics[width = \textwidth]{plots/sensor-acf_n5e4.pdf}
+       \caption{$n = 5 \times 10^4$}
+       \label{subfig:sensor-acf_n5e4}
+     \end{subfigure}
+     \caption{A-ACF and G-ACF for component-1 at two different sample size. The locally (light blue) and globally (light orange) centered ACF for individual chain has been plotted.}
+     \label{fig:sensor-acf}
+ \end{figure}
 
@@
 The total simulation size for each chain is fixed at $100,000$.
-Figure \ref{fig:sensor-trace-3} demonstrates the trace plots of the first chain for the x-component of all four unknown locations.
-We observe the bi-modal nature of the marginal distribution for each component.
-The Markov chains get stuck at a particular mode for a long time before jumping to the other mode.
-Figure \ref{fig:sensoG-ACF} shows the effect of this "sticky" nature of Markov chains over the autocorrelations centered around the local and global mean.
-For a small sample size of 1000, it can be seen that the third chain has not explored the sample space well.
-As a consequence, the local mean differs a lot from the global mean (averaged over all five chains).
+We sample five chains starting from dispersed starting values.
+Since the truth about actual mean and asymptotic variance is not known in this case, we are not interested in coverage probabilities.
+Instead, we will focus on a comparative study of local and global estimators in terms of - (1) autocorrelations, (2) log Frobenius norm of estimated $\Sigma$, and (3) log of estimated $ESS/mn$.\\
+
+Figure~\ref{subfig:sensor-sp_loc1} shows the scatter plot of location-1 for a single Markov chain.
+Similarly, the other three locations also have a bimodal marginal distribution in each component.
+To illustrate the \textit{sticky} nature of the Markov chains obtained from RAM sampling method, we plot the evolution of two chains (starting near different modes) with time.
+Observe that each chain explores one particular mode for a long time before jumping to another mode.
+\\
+
+Figure~\ref{fig:sensor-acf} plots the locally and globally centered ACrF estimators for individual chains as well as the average over all the chains.
+The thick lines represent the averaged estimator and the thin lines correspond to single chains.
+Figure~\ref{fig:sensor-fron_n_ess} presents the running plot of log Frobenius norm of A-ACF and G-ACF along with $95\%$ confidence interval calculated using $50$ replications for each value of $n$ (x-axis).
+In both the plots, G-SVE and $\hat{ESS}_G/mn$ prove to be drastically better than the classical single-chain estimators.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[h]{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/sensor-frob.pdf}
+      \caption{log Frobenius norm}
+      \label{subfig:sensor-frob}
+    \end{subfigure}
+    \begin{subfigure}[h]{0.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/sensor-ess.pdf}
+      \caption{$\log(\hat{ESS}/mn)$}
+      \label{subfig:sensor-ess}
+    \end{subfigure}
+    \caption{Sensor Network. Running plot for log of Frobenius norm of estimated $\Sigma$ (left) and log of estimated $ESS/mn$ (right) calculated using A-SVE and G-SVE.}
+    \label{fig:sensor-fron_n_ess}
+\end{figure}
 
 \section{Discussion} \label{sec:discussion}
+
+Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
+However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
+Unfortunately, the estimator given in Equation~\ref{eq:empirical_acf} has been observed to have a some drawbacks.
+Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains.
 
@@
 %
-Additionally, the locally-centered autocovariance exhibits the following expectation 
+Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
  \begin{equation} \label{eq:priestly}
@@
 As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
- \begin{equation} \label{eq:G-_expec_breakdown}
+ \begin{equation} \label{eq:G-ACF_expec_breakdown}
      \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
@@
 \begin{align*}
-    O_1 &= -\dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] \, ,\\
+    O_1 &= -\dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
     O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
@@
 We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$.
-Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\color{red}\mathcal{O}}(1/n)$.
+Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\mathcal{O}}(1/n)$.
 For a diagonal element of $\Gamma$,
@@
 
-\subsection{G-SVE Bias}
-
-\begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
-The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
+\subsection{Proof of Theorem \ref{th:G-SVE_bias}}
+
+% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
+% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
 We are interested in finding the asymptotic bias here.
-Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:G-_expec_breakdown} as,
-\begin{align*}
-&\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right]\\
-&  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:G-_bias2}  \,.
-\end{align*}
-%
-% \begin{equation} \label{eq:G-_bias2}
-% \mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
-% \end{equation}
-%
-where both $O_1 \textrm{ and } O_2$ are $\mathcal{O}(n^{-1})$ terms. By our assumptions, $\sum_{k=-\infty}^{\infty}\abs{k}^q\|\Gamma(h)\| < \infty$.  Consider the G-SVE estimator,
-\begin{align*}
-    &\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right]\\
-    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\inf}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\
-    & = P_1 + P_2
+Therefore we can write the expectation of replicated autocovariance in form of
+By Equation~\ref{eq:G-ACF_expec_breakdown},
+\begin{align*}
+\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
+% &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
+& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + \mathcal{O} \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
+\end{align*}
+%
+\begin{equation} \label{eq:G-_bias2}
+\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
+\end{equation}
+%
+where both $O_1 \textrm{ and } O_2$ are the small order terms.
+By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = n^{-1}\abs{k} \mathcal{O}(n^{-1}) \text{ and } O_2 = \mathcal{O}(n^{-1})$.
+Consider the G-SVE estimator,
+\begin{align*}
+ \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
+    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\
+    & = P_1 + P_2\,,
 \end{align*}
@@
 \begin{align*}
-P_1 & = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
+    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k) \textrm{ and }\\   
     P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
 \end{align*}
-{\color{blue} Dootika: Add something about $P_2$ here as well. And I don't think we need the $W_n < \infty$ assumption. }
-%
-We first solve for term $P_1$ by breaking it into three parts as in \cite{hannan2009multiple}.
-Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for each element of the matrix $A$.
-Consider,
+
+%
+Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
 \begin{equation}
@@
 \end{align*}
-%
- % Finally, we will solve for $P_2$.
+
+  Finally, we will solve for $P_2$.
 Note that $O_2$ is independent of $k$.
@@
 We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
- % \begin{align*}
- %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
- %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
- %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
- %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
- %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
- % \end{align*}
-  %
+  \begin{align*}
+      &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
+      & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right) W_n \\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
+ \end{align*}
+
 %
@@
 Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
-\end{proof}
-
-% \subsection{Proof of Theorem \ref{th:G-SVE_bias}}
-
-% % \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
-% % The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$.
-We are interested in finding the asymptotic bias here.
-Therefore we can write the expectation of replicated autocovariance in form of
-% By \ref{eq:G-_expec_breakdown},
-% \begin{align*}
-% \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
-% % &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-% & = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + o \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
-% \end{align*}
-% %
-% \begin{equation} \label{eq:G-_bias2}
-% \mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
-% \end{equation}
-% %
-% where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  
-% Consider the G-SVE estimator,
-% \begin{align*}
-%  \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-%     &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + o\left(n^{-1} \right)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-%     &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  o\left(n^{-1}\right)\right] \\
-%     & = P_1 + o \left( \dfrac{1}{n} \right)\,,
-% \end{align*}
-% %
-% where 
-% \[
-% P_1  = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
-% % P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
-% \]
-% %
-% Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
-% \begin{equation}
-% \label{eq:P1_decomp}
-% P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
-% \end{equation}
-% %
-% We deal with the three subterms of term $P_1$ individually. First,
-% %    
-% \begin{align*}
-%  {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
-% \end{align*}
-% %
-% since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
-% %
-% \begin{align*}
-%  \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
-% \end{align*}
-% For $q\geq 1$,
-% \begin{align*}
-% \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
-% \end{align*}
-
-% For $q <1$,
-% \begin{align*}
-%    \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
-% \end{align*}
-% So,
-% \begin{equation}
-% \label{eq:P1_second}
-%  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
-% \end{equation}
-% Lastly, by our assumptions, for $x \to 0$
-% \[
-% \dfrac{1 - w(x)}{\abs{x}^q} = k_q + o(1)\,.
-% \]
-% For $x = k/b_n$, $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$.
-%  % where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
-%      % \[
-%      % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
-%      % \]
-% So,
-% \begin{align*}
-%      \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
-%      & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
-%      & = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right) \numberthis \label{eq:P1_third}\,.
-% \end{align*}
-% %
-%  % Finally, we will solve for $P_2$.
-Note that $O_2$ is independent of $k$.
-We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$.
-We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
-%  % \begin{align*}
-%  %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
-%  %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
-%  %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
-%  %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
-%  %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
-%  % \end{align*}
-%   %
-% %
-% Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
-% \[
-% \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
-% \]
-% which completes the result.
-% %
-%  % We have shown that all, but one, terms are $o(1/b_n^q)$.
-Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
-This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu$ in our replicated autovariance estimator.
-Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
-% % \end{proof}
+% \end{proof}
 

### 2020-08-05 VAR-1/simulations.R
Simulations for VAR

@@ -1,5 +1,5 @@
 ################################################################
-##This code is responsible for simulating and storing R objects 
+##This code is responsible for simulating and storing R objects
 ##that are later used for plotting figures and making tables.
 ################################################################
 
@@ -26,23 +26,23 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
     start[m-i+1,] <- -2*i*sqrt(diag(truth))
   }
 
-  master.chain.rep <- list()
-  
-  for (i in 1:freq){
-    print(paste("Sampling percentage completion: ", i*100/freq))
-    chains <- array(0, dim = c(max(check.pts), p, m))
-    
-    for (j in 1:m){
-      chains[,,j] <- markov.chain(phi, omega, max(check.pts), start[j,])
-    }
-    master.chain.rep[[i]] <- chains
-  }
+  #master.chain.rep <- list()
+
+  #for (i in 1:freq){
+  #  print(paste("Sampling percentage completion: ", i*100/freq))
+   # chains <- array(0, dim = c(max(check.pts), p, m))
+
+  #  for (j in 1:m){
+   #   chains[,,j] <- markov.chain(phi, omega, max(check.pts), start[j,])
+  #  }
+   # master.chain.rep[[i]] <- chains
+  #}
 
   for (i in 1:length(check.pts)){
 
     nsim <- check.pts[i]
     critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
-    
+
     asv.samp <- array(0, dim = c(p,p,freq))
     rsv.samp <- array(0, dim = c(p,p,freq))
     asv.coverage <- rep(0,freq)
@@ -50,7 +50,12 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
 
     for (j in 1:freq){
       if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2), "for nsim = ", nsim))
-      chain <- master.chain.rep[[j]][1:nsim,,]
[…]

### 2020-08-05 VAR-1/simulations.R
It's a bit rushed up!

@@ -18,54 +18,49 @@ sourceCpp("lag.cpp")
 create.output <- function(phi, omega, m, check.pts, freq, c.prob){
 
   p <- ncol(phi)
-  truth <- target.sigma(phi, omega)
+  target <- target.sigma(phi, omega)
   start <- matrix(0, nrow = m, ncol = p)  #only depends on C
 
   for(i in floor(m/2):1){
-    start[i,] <- 2*i*sqrt(diag(truth))
-    start[m-i+1,] <- -2*i*sqrt(diag(truth))
+    start[i,] <- 2*i*sqrt(diag(target))
+    start[m-i+1,] <- -2*i*sqrt(diag(target))
   }
 
-  #master.chain.rep <- list()
-
-  #for (i in 1:freq){
-  #  print(paste("Sampling percentage completion: ", i*100/freq))
-   # chains <- array(0, dim = c(max(check.pts), p, m))
-
-  #  for (j in 1:m){
-   #   chains[,,j] <- markov.chain(phi, omega, max(check.pts), start[j,])
-  #  }
-   # master.chain.rep[[i]] <- chains
-  #}
+  asv.samples <- list()
+  gsv.samples <- list()
+  asv.coverage <- list()
+  gsv.coverage <- list()
 
   for (i in 1:length(check.pts)){
+    asv.samples[[i]] <- array(0, dim = c(p,p,freq))
+    gsv.samples[[i]] <- array(0, dim = c(p,p,freq))
+    asv.coverage[[i]] <- rep(0, freq)
+    gsv.coverage[[i]] <- rep(0, freq)
+  }
 
-    nsim <- check.pts[i]
-    critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
+  for (j in 1:freq){
+    if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2)))
 
-    asv.samp <- array(0, dim = c(p,p,freq))
-    rsv.samp <- array(0, dim = c(p,p,freq))
-    asv.coverage <- rep(0,freq)
-    rsv.coverage <- rep(0,freq)
+    master.chain <- array(0, dim = c(max(check.pts), p, m))
+    for (k in 1:m)
+      master.chain[,,k] <- markov.chain(phi, omega, max(check.pts), start[k,])
 
-    for (j in 1:freq){
[…]

### 2020-08-05 Paper/main.tex
Finished Section 2. Pizza time!

@@
 Let $F$ be the target distribution with mean $\mu$ defined on the set $\X \subseteq \mathbb{R}^p$ equipped with a countably generated Borel $\sigma$-field $\mathcal{B}(\X)$.
-Let $\{X_t\}$ be an $F$-Harris ergodic stationary Markov chain \citep[see][for definitions]{meyn:twee:2009} employed to learn characteristics about $F$.
+For $s = 1, \dots, m$, let $\{X_{st}; \; t \in \mathbb{Z}\}$ be the $s^{th}$ $F$-Harris ergodic stationary Markov chain \citep[see][for definitions]{meyn:twee:2009} employed to learn characteristics about $F$.
 % If $\bar{X} = n^{-1} \sum_{t=1}^{n}X_t$ , then with probability 1, $\bar{X} \to \mu$ as $n \to \infty$. \\
-The Markov chain is covariance stationary so that
-th ACvF at lag $k$ depends only on $k$ and is defined as 
-%
-\[
-    \Gamma(k) = \Cov_F(X_1, X_{1+k})= \mathbb{E}_F \left[(X_1 - \mu)(X_{1+k} - \mu)^T \right]\,.
-\]
-Estimating $\Gamma(k)$ is critical to assessing the quality of the sampler and the quality of  sample statistics. The standard estimator is the sample autocovariance matrix at lag $k$
+The process is covariance stationary so that
+the ACvF at lag $k$ depends only on $k$ and is defined as 
+%
+\[
+    \Gamma(k) = \Cov_F(X_{s1}, X_{s\,1+k})= \mathbb{E}_F \left[(X_{s1} - \mu)(X_{s\,1+k} - \mu)^T \right]\,.
+\]
+Estimating $\Gamma(k)$ is critical to assessing the quality of the sampler and the quality of sample statistics.
+Let $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ denote the Monte Carlo estimator of $\mu$ from the $s$th chain.
+The standard estimator is the sample autocovariance matrix at lag $k$ for the $s$th chain is
 %
 \begin{equation} \label{eq:empirical_acf}
-    \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}} \left(X_t - \bar{X} \right) \left(X_{t+\abs{k}} - \bar{X} \right)^T\,.
+    \hat{\Gamma}_s(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}} \left(X_{st} - \bar{X}_s \right) \left(X_{s t+\abs{k}} - \bar{X}_s \right)^T\,.
 \end{equation}
@@
  \end{subfigure}
-    \caption{Target density and Density plot for two chains starting at different values for a Gaussian mixture model with mixture probability $= 0.7, \; \mu_1 = -5, \; \mu_2 = 5, \; \sigma_1 = 1, \textrm{ and } \sigma_2 = 0.5$.
-(a) $n = 10^4$; chains don't interact.
-(b) $n = 10^5$; chains interact.}
+    \caption{Target density and trace plots for two chains starting at different values.}
     \label{fig:gaussian-trace}
@@
 
- Suppose we have $m$ replications of Markov chains for same target distribution and $\{X_{st}; \; t \in \mathbb{Z}\}$ denote the $s^{th}$ Markov chain.
-Let the sample mean of $s^{th}$ Markov chain be denoted by $\bar{X}_s$ and the global mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$.
-The global mean provides a better estimate for the expectation value when the number of simulation per chain are not sufficient for the convergence to kick in.
-The globally-centered autocovariance function (G-ACF) for the $s^{th}$ Markov chain is given by:
+Recall that we run $m$ independent $F$-ergodic Markov chains denoted by $\{X_{st}; \; t \in \mathbb{Z}\}$ for the $s^{th}$ chain.
+Let the sample mean of the $s^{th}$ Markov chain be $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ and the global mean by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
+The global mean is naturally superior estimator of $\mu$ than $\bar{X}_s$.
+We define the globally-centered autocovariance function (G-ACvF) estimator for the $s^{th}$ Markov chain as
 %
@@
 \]
-and the averaged globally-centered ACF over all $m$ chains is given by 
-\[
-\hat{\Gamma}_G(k) = \dfrac{1}{m}\sum_{s=1}^m \hat{\Gamma}_{G,s}(k)\;.
-\]
-If the starting points of these parallel Markov chains are sufficiently dispersed, G-ACF provides more realistic estimation of lag covariances.
+In the event that all $m$ Markov chains have been run long enough that $\bar{X}_s \approx \bar{\bar{X}}$ are similar, then  $\hat{\Gamma}_{s} (k) \approx \hat{\Gamma}_{G,s}(k)$.
+However, for shorter runs or for slow mixing chains, $\Gamma(k)$ is more appropriately estimated by $\hat{\Gamma}_{G,s}$ as it utilizes information from all chains and accounts for disparity between estimates of $\mu$.
+We quantify the gains in  bias  for the G-ACvF estimator below.
+% If the starting points of these parallel Markov chains are sufficiently dispersed, G-ACF provides more realistic estimation of lag covariances.
 \cite{priestley1981spectral} shows that the empirical estimator in Equation \ref{eq:empirical_acf} is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
 Though, an unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, the biased estimator is preferred for its lower mean square error for larger relative $k$  (\cite{priestley1981spectral})
-
-% \subsection{Theoretical results} % (fold)
-% \label{sub:theoretical_results}
-
-% subsection theoretical_results (end)
-
-The bias for G-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:G-_expec}.
-Before getting to the bias results for $\hat{\Gamma}_{RAV}(k)$ for any lag $k$, we introduce an additional notation.
-For $q \geq 1$, we define
-\[
-\Phi^{(q)} = \sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\|
-\]
-We denote $\Phi^{(1)} \textrm{ by } \Phi$.
-
-The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
-
-{\color{blue} Fix the proof for this.}
-\begin{theorem} \label{th:G-_expec} Under stationarity,
-\[
-   \mathbb{E} \left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
+Let 
+\[
+\Phi^{(q)} = \sum_{ k= -\infty}^{\infty}\abs{k}^q \Gamma(k)\,,
+\]
+and let $\Phi^{(1)}$ be denoted by $\Phi$.  The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
+
+\begin{theorem} \label{th:G-_expec} Let $\E_F \|X_{11}\|^{2 + \delta} < \infty$ for some $\delta > 0$.
+Let $P$ be a  polynomially ergodic Markov chain of order $\xi > (2 + \epsilon)/(1 + 2/\delta)$ for some $\epsilon > 0$.
+Then,
+\[
+   \mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
 \]
@@
 \[
-\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = -\dfrac{\abs{k}}{n}\Gamma(k) - \dfrac{1}{m}\left(1- \dfrac{|k|}{n}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
-\]
-   % \[
-   % \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
-   % \]
+\mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}_s(k) \right] = -\dfrac{\abs{k}}{n}\Gamma(k) - \dfrac{1}{m}\left(1- \dfrac{|k|}{n}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
+\]
 \end{theorem}
 
-% \begin{proof}
-
-%  We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as
-
-%  \begin{equation} \label{eq:priestly}
-%      \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
-%  \right)
-%  \end{equation}
-
-% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{G-}$ into four parts for all $k \geq 1$ as:
-%  \[
-%  \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
-%  \]
-% %
-% where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
-% The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.
-The complete proof evaluating the expectation values of last three terms can be found in Appendix subsection \ref{appendix:bias}.
-% \end{proof}
-
-% \begin{remark} \label{rmrk:exp_G-f_minus_acf}
-% Using theorem \ref{th:G_expec} and equation \ref{eq:priestly},
-% \[
-% \mathbb{E} \left[\hat{\Gamma}_{G}(k) - \hat{\Gamma}(k) \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
-% \]
-% We know that the sample autocovariance $\hat{\Gamma}(k)$ underestimates the truth due to a negative bias of $\abs{k}\Gamma(k)/n$ for finite $n$.
-However, in practice, it is preferred to overestimate the autocovariance for finite $n$ than to underestimate it in order to have a more realistic idea about the correlation in a Markov chain at a particular lag.
-Note that the RHS in the above expression is positive.
-As a consequence, G-ACF will counter this negative bias and give more reliable estimates for ACF.
-
-% \end{remark}
-
-When $m = 1$, $\hat{\Gamma}_G(k)$ corresponds to $\hat{\Gamma}(k)$, the expectation of which can be found in \cite{priestley1981spectral}.
-Theorem~\ref{th:G-_expec} implies that the globally-centered autocovariances are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered autocovariances.
-The consequences of this are particularly pertinent for the diagonals of $\Gamma$.
-Special interest is also in the lag-0 autocovariance, that is, the variance of the target distribution.
-
+\begin{remark}
+Polynomial ergodicity and the moment conditions are required to ensure $\Phi$ and $\Sigma$ are finite.
+The above result can be stated more generally for $\alpha$-mixing processes, but we limit our attention to Markov chains.
+\end{remark}
+
+When $m = 1$, $\hat{\Gamma}_{G,s}(k) = \hat{\Gamma}_{s}(k)
+$ the bias results for which can be found in \cite{priestley1981spectral}.
+Since lag-covariances are typically positive in MCMC, Theorem~\ref{th:G-_expec} implies that the G-ACvF estimators are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered ACvF estimators.
+The consequences of this are particularly pertinent for the diagonals of $\Gamma(k)$.
+ % Special interest is also in the lag-0 autocovariance, that is, the variance of the target distribution. 
 \begin{remark} \label{rem:lag0_expectation}
+The variance of the target distribution is the lag covariance at lag 0 and is of particular interest. The bias of the estimator reduces by a factor of $m$:
 \[
@@
 \]
-
 \end{remark}
 
-% \subsection{Autocorrelation} % (fold)
-% \label{sub:autocorrelation}
-
-% subsection autocorrelation (end)
-%{\color{blue}  Autocovariances will be used implictly in SVE estimators. But they are explicitly important in ACF plots via autocorrelations.
-
-%Notation in the appendix is $\Gamma^{ii}_{G,s}$
-%}
-Lag-0 autocovariance are particularly useful in calculating the autocorrelations.The variance of $i^{th}$ component given by $\Gamma^{ii}(0)$. For any component $i$, the autocorrelation is
+A first use of the ACvFs in MCMC is in constructing ACF plots. Let the target variance of $i${th} component be $\Gamma^{ii}(0)$. For any component $i$, the autocorrelation is defined as
 \[
@@
 and is instrumental in visualizing the serial correlation in components of the Markov chain.
-The typical estimate of the autocorrelation is constructed from  locally-centered autocovariance estimates which as was demonstrated in Section~\ref{sec:intro} can significantly underestimate the autocorrelation.
-Instead, we calculate the globally-centered autocorrelation using the formula
+The typical estimate of the autocorrelation is constructed from $\hat{\Gamma}_s(k)$.
+Instead, we advocate for using G-ACvF estimates so that,
 \[
@@
 \]
-Despite using similar centering in both numerator and denominator, the globally-centered autocorrelation is far greater than locally-centered autocorrelation for each component as is evident from Figure~\ref{fig:gauss:acf}.
-
-% \begin{proof}
-%  The proof is in Appendix subsection \ref{appendix:bias}.
-% \end{proof}
-
-\section{Variance Estimators for multiple Markov chains} \label{sec:variance_est}
-
-Let $g:\chi \longrightarrow \mathbb{R}^d$ be an F-integrable function. We are interested in the expected value
-%
-\[
-\mu_g = \mathbb{E}_F[g(X)] = \int_{\chi}g(x)F(dx)\;.
-\]
-
-Let $Y$ denote the random variable $g(X)$ where $X \sim F$.
-Since we have $m$ chains of $n$ samples each, let us make following notations: (1) $Y_{st} = g(X_{st})$ for $t \in \{1, 2, ..., n\}$ and $s \in \{1, 2, ..., m\}$; (2) $\bar{Y}_s = \sum_{t=1}^{n}g(X_{st})/n$; and (3) $\bar{\bar{Y}} = \sum_{s=1}^{m}\bar{Y}_s/m$.
-To assess the reliability of our simulations, we are interested in Monte Carlo error, i.e.
+The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gauss:acf}.
+
+We end this section by noting that we can obtain an average G-ACvF and G-ACF over all $m$ chains
+\[
+\hat{\Gamma}_G(k) = \dfrac{1}{m}\sum_{s=1}^m \hat{\Gamma}_{G,s}(k) \quad \text{ and } \quad \hat{\rho}^{(i)}_G(k) = \dfrac{1}{m}\sum_{s=1}^m \hat{\rho}^{(i)}_{G,s}(k)\,.
+\]
+The averaged estimators present a measure of the overall correlation structure induced by the Markov transition $P$.
+
+\section{Variance estimators for multiple Markov chains} \label{sec:variance_est}
+
+A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.
+Let $g:\X \longrightarrow \mathbb{R}^d$ be an $F$-integrable function so that we are interested in estimating
+%
+\[
+\mu_g = \mathbb{E}_F[g(X)] = \int_{\X}g(x)F(dx)\;.
+\]
+
+Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$ and set $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.
+
+To assess the reliability of simulations, we are interested in Monte Carlo error, i.e.
 $\bar{Y_s} - \mu$ for the $s^{th}$ chain.

### 2020-08-05 VAR-1/simulations.R

@@ -39,7 +39,7 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
   }
 
   for (j in 1:freq){
-    if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2)))
+    if(j %% (freq/1000) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2)))
 
     master.chain <- array(0, dim = c(max(check.pts), p, m))
     for (k in 1:m)
@@ -63,9 +63,9 @@ create.output <- function(phi, omega, m, check.pts, freq, c.prob){
       global.mean <- apply(chains, 2, mean)
 
       for (k in 1:m){
-        chain.cen.loc <- scale(chain[,,k], scale = FALSE)  ## X_st - bar(X)_s
+        chain.cen.loc <- scale(chains[,,k], scale = FALSE)  ## X_st - bar(X)_s
         sve[,,k] <- mSVEfft(A = chain.cen.loc, b = b.avg)
-        chain.cen <- scale(chain[,,k], center = global.mean, scale =FALSE)
+        chain.cen <- scale(chains[,,k], center = global.mean, scale =FALSE)
         rsve[,,k] <- mSVEfft(A = chain.cen, b = b.avg)
       }
       asv.samples[[i]][,,j] <- apply(sve, c(1,2), mean)

### 2020-08-06 Paper/main.tex
VAR-1 done dona done done done daara

@@
 A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.
-Let $g:\X \longrightarrow \mathbb{R}^d$ be an $F$-integrable function so that we are interested in estimating
+Let $g:\X \longrightarrow \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
 %
@@
 Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$ and set $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.
-
-To assess the reliability of simulations, we are interested in Monte Carlo error, i.e.
-$\bar{Y_s} - \mu$ for the $s^{th}$ chain.
-The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
-%
-{\color{blue} }
-\[
-\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
-\]
+By Birkhoff's ergodic theorem,  $\bar{\bar{Y}} \to \mu_g$ as $n \to \infty$ with probability 1.
+
+Reliability of $\bar{\bar{Y}}$ is assessed by its Monte Carlo variability via an asymptotic sampling distribution \citep{fleg:hara:jone:2008,roy:2019,vats:rob:fle:jon:2020}. 
+% To assess the reliability of simulations, we are interested in Monte Carlo error, i.e. $\bar{Y_s} - \mu$ for the $s^{th}$ chain. 
+% The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov})
+ A Markov chain central limit theorem (CLT) holds if there exists a $p \times p$ positive-definite matrix $\Sigma$ such that
+%
+\begin{equation}
+\label{eq:CLT}
+  \sqrt{mn}(\bar{\bar{Y}} - \mu) \xrightarrow{d} N(0,\Sigma)\,
+\end{equation}
+where
+\begin{equation}
+\label{eq:sigma}
+  \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right)
+\end{equation}
+%
+The goal in output analysis for MCMC is to estimate $\Sigma$in order to assess variability in $\bar{\bar{Y}}$.
+There is a rich literature of estimators of $\Sigma$ available for single-chain MCMC implementations.
+The most common are spectral variance estimators (SVE) \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \cite{chen:seila:1987,vats:fleg:jon:2019}.
+Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from multiple parallel chains.
+Batch means estimators are computationally more efficient than SVE, SVE estimators are more reliable \citep{fleg:jone:2010}.
+Here, we utilize G-ACvF estimators to construct globally-centered SV estimator (G-SVE) of $\Sigma$.
+Using the methods of \cite{heberle2017fast}, we also provide an efficient algorithm for obtaining the G-SV estimator.
 

### 2020-08-06 Paper/main.tex
Pushing updated Section 3 with notes. It's yours now.

@@
 
- Given m parallel Markov chains, we have $m$ i.i.d.
-samples of $\bar{X}_s$, $s \in \{1,..., m\}$.
-The Markov Chain standard error (MCSE) is given by $\Sigma/mn$.
-We are interested in consistent estimates of $\Sigma$ for two reasons.
-Firstly, to construct asymptotically valid confidence intervals and secondly, to determine when to stop the simulations.
-For this purpose, we use the class of Multivariate Spectral Variance Estimators (MSVE).
-The most common practice would be to combine the spectral variance estimates from $m$ chains by averaging over them.
-We call this technique average spectral variance estimator (A-SVE) and denote it by $\hat{\Sigma}_A$.
-Let $\hat{\Sigma}_{SV,s}$ denote the SVE for the $s^{th}$ chain, then the A-SVE is given by
-
+SV estimators are constructed as weighted and truncated sums of estimated lag covariances.
+Let $w: \mathbb{R} \to [-z,z]$ be a lag window function and let $b_n \in \mathbb{N}$ be a truncation point.
+The SV estimator of $\Sigma$ from a single chain is
+%
+{\color{blue} DV: limits should be $-n +1$ and $n - 1$.}
+\begin{equation} \label{eq:sve}
+    \hat{\Sigma}_{SV,s} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)
+\end{equation}
+An overall estimate of $\Sigma$ from all $m$ chains is the average SV estimator (ASV):
 \[
@@
 \]
- We propose a globally-centered spectral variance estimator (G-SVE) wherein we use G-ACF to estimate the autocovariance.
+%  We propose a globally-centered spectral variance estimator (G-SVE) wherein we use G-ACF to estimate the autocovariance.
 Strong consistency for MSVE has been addressed by \cite{vats:fleg:jon:2018}.
@@
 % \end{equation}
-
-Let $w_n: \mathbb{R} \to [-z,z]$ be a lag window function and let $b_n \in \mathbb{N}$ be a truncation point. The usual SV estimator is the weighted and truncated sum of lag-$k$ autocovariances:
-\begin{equation} \label{eq:sve}
-    \hat{\Sigma}_{SV} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_n(k)
-\end{equation}
-
+{\color{blue} DV: There are some issues.
+\begin{itemize}
+  \item $|w_n| < z$ or $|w_n| < c$?
+  \item Need new notation for $\Gamma(k)$ since $\Gamma(k)$ is for the $X$ and we need a new notation for $Y$. This change needs to be made for this whole section and the appendix!
+\end{itemize}
+}
+
+We define the globally-centered SV estimator as the weighted and truncated sum of G-ACvFs
+%
 % Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
-Consider the globally-centered SV estimator (G-SVE) for the $s$th chain using G-ACF:
-%
-\begin{align*}
-    \hat{\Sigma}_{G,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G,s}(k)\,,
-\end{align*}
-and the combined G-SVE is
-\[
-\hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}\,.
-\]
-Define
-%
-\[
-W_n = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right).
-\]
-We will consider a range of lag windows $w(x)$; where $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$.
+% Consider the globally-centered SV estimator (G-SVE) for the $s$th chain using G-ACF:
+%
+\begin{align*}
+    \hat{\Sigma}_{G} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G}(k)\,.
+\end{align*}
+% and the combined G-SVE is
+% \[
+% \hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}\,.
+% \]
+For $\hat{\Sigma}_{G}$ to accurately estimate $\Sigma$, conditions need to be imposed on the weight function, $w_n$.
+
+{\color{blue}DV: Did we discuss that $W_n$ should be define as an infinite sum and should be $W$?}
+
+%
+
+\begin{ass}
+\label{ass:lag_window}
+The lag window $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$ where
+\[
+W_n = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\,.
+\]
+\end{ass}
+% We will consider a range of lag windows $w(x)$; where $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$. 
+Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows.
+We will use the popular Bartlett lag window in our simulations.
+{\color{blue}DV: write the Bartlett lag window}.
 
@@
 
-The G-SVE estimator centers the data around the global mean. We are interested in proving the strong consistency, finding the bias and variance of G-SVE.
-
-\begin{ass}[Strong Invariance Principle (SIP)] \label{ass:sip}
-    We assume the SIP holds for the Markov chains $\{Y_{st}\}_{t \geq 1} \; \forall s$.
+We will present three main results for the G-SV estimator.
+First, we provide conditions for strong consistency.
+Strong consistency is particularly important to demonstrate for MCMC as it is required to ensure sequential stopping rules yield correct coverage at termination \citep{glyn:whit:1992}.
+A critical assumption is that of a strong invariance principle below.
+Let $B(n)$ denotes a standard $p$-dimensional Brownian motion.
+
+\begin{theorem}[\cite{kuel:1976,vats:fleg:jon:2018}]
+  \label{thm:kuelbs}
+Let $\E_F\|Y_{11}\|^{2+ \delta} < \infty$ for $\delta > 0$ and let $P$ be a polynomially ergodic Markov chain of order $\xi > (q + 1 + \epsilon)/(1 + 2/\delta)$ for $q \geq 1$.
+Then there exists a $p \times p$ lower triangular matrix $L$ such that $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for almost all $w \in \Omega$ such that for all $n > n_0$, with probability 1,
+\[
+\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n)\,.
+\]
+\end{theorem}
+
+% \begin{ass}[Strong Invariance Principle (SIP)] \label{ass:sip}
+%     We assume the SIP holds for the Markov chains $\{Y_{st}\}_{t \geq 1} \; \forall s$.
 Here $\{Y_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu_g$.
@@
 Through SIP, there exists a $p \times p$ lower triangular matrix L, an increasing function $\psi$ on the integers, a finite random variable D, and a  sufficiently rich probability space such that, with probability 1, \\
-  $$\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n)$$
-
-  Let $\{B(n)\}_{n\geq 0}$ denotes a standard p-dim Brownian motion and $B^{(i)}$ denotes its $i^{th}$ component.
+%   $$\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n)$$
+  % 
+%   Let $\{B(n)\}_{n\geq 0}$ denotes a standard p-dim Brownian motion and $B^{(i)}$ denotes its $i^{th}$ component.
 As shown in the results \cite{kuelbs1980almost}, SIP will hold for $\psi(n) = n^{1/2 - \lambda, \; \lambda > 0}$ for Markov chains commonly encountered in MCMC settings.
@@
 Using Law of Iterative Logarithms (LIL), a tighter bound for $\psi(n)$ is given by \cite{stra:1964} as $\mathcal{O}(\sqrt{n\log \log n})$.
-\end{ass}
+% \end{ass}
 
@@
 \label{th:consistency}
- Let the Assumptions \ref{ass:sip} hold, $\hat{\Sigma}_{SV,s} \xrightarrow{a.s.} \Sigma \; \forall s$, and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \to \Sigma$ with probability 1, as $n \to \infty$.
+ Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q = 1$.
+If $\hat{\Sigma}_{SV,s} \xrightarrow{a.s.} \Sigma$ for all $s$, and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \to \Sigma$ with probability 1, as $n \to \infty$.
 \end{theorem}
@@
 
-We are interested in the finding the bias for G-SVE estimator as a function of $n$. 
+% We are interested in the finding the bias for G-SVE estimator as a function of $n$. 
+{\color{blue} Move these two sub-assumptions into the theorem 4 below.}
 \begin{ass} \label{ass:bias}
@@
     \begin{enumerate} [a.]
-        \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma_s(k)\| < \infty$
+        \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma_s(k)\| < \infty$ {\color{blue} DV: This assumption is satisfied by the polynomial ergodicity, so can remove it.}
         \item $\lim _{x \to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty$ 
@@
 
-    If $k_q$ is finite for some $q_o$, then it is zero for $q < q_0$. $q$ is taken to be the largest number satisfying the first two conditions above.
+    % If $k_q$ is finite for some $q_o$, then it is zero for $q < q_0$. $q$ is taken to be the largest number satisfying the first two conditions above.
 \end{ass}
@@
 \begin{theorem}\label{th:G-SVE_bias}
-Let the Assumption~\ref{ass:bias} hold, then the limiting bias of G-SVE is given by:
+Let assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that {\color{blue}......} Let the Assumption~\ref{ass:bias} hold. Then
 \[
@@
 
-% \begin{proof}
-% \[
-% \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
-% \]
-
-% Using theorem \ref{th:G-ACF_expec}, we can write the expectation of $\hat{\Gamma}_{G}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
-% The proof is given in the Appendix subsection \ref{appendix:bias}.
-% \end{proof}
-
 \begin{theorem} \label{th:G-SVE_variance}
- Let Assumption~\ref{ass:sip} holds, $\E[D^4] < \infty$ where D is a finite random variable associated with the SIP, and  $\E[Y^4] < \infty$, then $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+ Let assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E \|Y_{11}\|^4 < \infty$, then $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
 \end{theorem}
+
+{\color{blue} I have not looked at it after here. }
 

### 2020-08-07 SensorNetwork/output.R
minESS

@@ -7,6 +7,7 @@ library(RcppArmadillo)
 library(fftwtools)
 library(mcmcse)
 library(stats)
+library(plotly)
 sourceCpp("lag.cpp")
 source("functions.R")
 
@@ -67,8 +68,6 @@ load(file = paste("Out/conv_data_m", m, "_min", min, "_max", max, ".Rdata", sep 
 ########################################
 ########################################
 
-ind <- seq(1,length(conv.pts), by = 2)
-
 a <- lapply(asv, function(x) log(apply(x, 3, norm, "F") ) )
 r <- lapply(rsv, function(x) log(apply(x, 3, norm, "F") ) )
 a <- Reduce("rbind", a)
@@ -102,11 +101,11 @@ se.r <- 2*apply(Reduce("rbind", r), 2, sd)/sqrt(length(r))
 a <- Reduce("+", a)/length(ess.asv)
 r <- Reduce("+", r)/length(ess.rsv)
 
-plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "log(ESS/mn)", ylim = range(a, r), lwd = 2)
+plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "log(ESS/mn)", ylim = range(a, r, log(minESS(p, alpha = .1, eps = .1)/(m*conv.pts))), lwd = 2)
 lines(conv.pts, r, col = "royalblue", lwd = 2)
-segments(x0 = conv.pts[ind], y0 = (a - se.a)[ind], y1 = (a + se.a)[ind], col = adjustcolor("darkorange", alpha.f = .50))
-segments(x0 = conv.pts[ind], y0 = (r - se.r)[ind], y1 = (r + se.r)[ind], col = adjustcolor("royalblue", alpha.f = .50))
-
+segments(x0 = conv.pts, y0 = (a - se.a), y1 = (a + se.a), col = adjustcolor("darkorange", alpha.f = .50))
+segments(x0 = conv.pts, y0 = (r - se.r), y1 = (r + se.r), col = adjustcolor("royalblue", alpha.f = .50))
+lines(conv.pts, log(minESS(p, alpha = .1, eps = 0.1)/(m*conv.pts)), col = "green3", lwd=2)
[…]

### 2020-08-07 VAR-1/output.R
minESS for VAR

@@ -24,64 +24,71 @@ for (i in 1:(p-1)){
   }
 }
 
-phi <- diag(c(.9999, .001))
+phi <- diag(c(.999, .001))
 dummy <- matrix(1:p^2, nrow = p, ncol = p)
 dummy <- qr.Q(qr(dummy))
 phi <- dummy %*% phi %*% t(dummy)
 
 ############3Simuation settings###########
 
+target <- target.sigma(phi, omega)
 truth <- true.sigma(phi, var = target)
-check.pts <- c(1e3, 5e3, 1e4, 5e4, 1e5)
+check.pts <- c(5e2, 1e3, 5e3, 1e4, 5e4, 1e5)
 rep <- 50
+freq <- 1000
 min <- 5e2
-max <- 1e5
+max <- 5e4
 step <- 500
 conv.pts <- seq(min, max, step)
-
-start <- matrix(0, nrow = m, ncol = p)  #only depends on C
-
-for(i in floor(m/2):1){
-  start[i,] <- 2*i*sqrt(diag(target))
-  start[m-i+1,] <- -2*i*sqrt(diag(target))
-}
 
 ###########################################################
 ############## log Frobenius norm running plots ###########
 ###########################################################
 
 
-load(file = paste(paste("Out/run_data", m, min, max, sep = "_"), ".Rdata", sep = ""))
+
+pdf(file = paste("Out/sensor-frob.pdf", sep = ""), height = 5, width = 5)
+dev.off()
+
+
+load(file = paste("Out/conv_data_min", min, "_max", max, ".Rdata", sep = ""))
+
+a <- lapply(asv, function(x) log(apply(x, 3, norm, "F") ) )
+r <- lapply(rsv, function(x) log(apply(x, 3, norm, "F") ) )
+a <- Reduce("rbind", a)
+r <- Reduce("rbind", r)
+
+se.a <- apply(a, 2, sd)/sqrt(length(asv))
+se.r <- apply(r, 2, sd)/sqrt(length(rsv))
+
+a <- colMeans(a)
+r <- colMeans(r)
 
 pdf(file = "Out/var-frob.pdf", height = 5, width = 5)
-plot(conv.pts,log(apply(asv.samp, 3, norm, type = "F")), type = "l", col = "darkorange", lwd = 2,
-     main = "", xlab = "Simulation size", ylab = "Variance",
-     ylim = range(c(log(apply(rsv.samp, 3, norm, type = "F"))), log(norm(truth, type = "F"))))
[…]

### 2020-08-07 Boomerang/output.R
New Boomerang objects and plots for setting-1. Will run for setting-2 tonight.

@@ -15,28 +15,35 @@ library(stats)
 sourceCpp("lag.cpp")
 source("functions.R")
 
+#################################################
+##### Model parameters for both setttings #######
+#################################################
+
+p <- 2
+
+A1 <- 1
+B1 <- 3
+C1 <- 8
+
+A2 <- 1
+B2 <- 10
+C2 <- 7
 
 ########################################################
 #####Visualization through perspective plots############
 ########################################################
 
-#Perspective plots for both simulation settings
+#### Setting-1
 
-A <- 1
-B <- 3
-C <- 8
-
-pdf(file = paste("Out/", A, B, C, "/3d_density_plot.pdf", sep = "_"), height = 5, width = 5)
-samples <- perspective(A, B, C, 100)
+pdf(file = paste(paste("Out/", A1, B1, C1, "/3d_density_plot", A1, B1, C1, sep = "_"), ".pdf", sep = ""), height = 5, width = 5)
+samples <- perspective(A1, B1, C1, 100)
 persp(samples$x, samples$y, samples$z, main="", col = "white", shade = .5, theta = -45, phi = 0, xlab = "x", ylab = "y", zlab = "Density")
 dev.off()
 
-A <- 1
-B <- 10
-C <- 7
+#### Setting-2
 
-pdf(file = paste("Out/", A, B, C, "/3d_density_plot.pdf", sep = "_"), height = 5, width = 5)
-samples <- perspective(A, B, C, 200)
+pdf(file = paste(paste("Out/", A2, B2, C2, "/3d_density_plot", A2, B2, C2, sep = "_"), ".pdf", sep = ""), height = 5, width = 5)
+samples <- perspective(A2, B2, C2, 200)
 persp(samples$x, samples$y, samples$z, main="", col = "white", shade = .5, theta = -45, phi = 0, xlab = "x", ylab = "y", zlab = "Density")
 dev.off()
 
@@ -47,55 +54,49 @@ dev.off()
 ########################################################
 ########################################################
 
-
-m <- 2
-
-########### A=1, B=3, C=8##############
+########### Setting-1 ##############
 
[…]

### 2020-08-07 Boomerang/simulations.R

@@ -16,137 +16,154 @@ sourceCpp("lag.cpp")
 ##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
 ############################################################
 
-create.output <- function(A,B,C,m,check.pts,freq,c.prob){
-
+create.output <- function(A, B, C, m, check.pts, freq, c.prob){
+  
+  p <- 2
   start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
-
+  T.mean <- true.mean(A, B, C)
+  
   for(i in 1:floor(m/2)){
     start[i,] <- c(0, C*(2^(2-i)))
     start[m-i+1,] <- c(C*(2^(2-i)), 0)
   }
-
-  T.mean <- true.mean(A,B,C)
-
+  
+  asv.samples <- list()
+  gsv.samples <- list()
+  asv.coverage <- list()
+  gsv.coverage <- list()
+  
   for (i in 1:length(check.pts)){
-
-    nsim <- check.pts[i]
-    critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
-    asv.samp <- array(0, dim = c(2,2,freq))
-    rsv.samp <- array(0, dim = c(2,2,freq))
-    asv.coverage <- rep(0,freq)
-    rsv.coverage <- rep(0,freq)
-
-    for (j in 1:freq){
-      if(j %% (freq/10) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2), "for nsim = ", nsim))
-      chain <- array(0,dim = c(nsim,2,m))
-      sve <- array(0, dim = c(2,2,m))
-      rsve <- array(0, dim = c(2,2,m))
+    asv.samples[[i]] <- array(0, dim = c(p,p,freq))
+    gsv.samples[[i]] <- array(0, dim = c(p,p,freq))
+    asv.coverage[[i]] <- rep(0, freq)
+    gsv.coverage[[i]] <- rep(0, freq)
+  }
+  
+  for (j in 1:freq){
+    if(j %% (freq/1000) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2)))
+    
+    master.chain <- array(0, dim = c(max(check.pts), p, m))
+    for (k in 1:m)
[…]

### 2020-08-07 SensorNetwork/output.R

@@ -101,11 +101,10 @@ se.r <- 2*apply(Reduce("rbind", r), 2, sd)/sqrt(length(r))
 a <- Reduce("+", a)/length(ess.asv)
 r <- Reduce("+", r)/length(ess.rsv)
 
-plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "log(ESS/mn)", ylim = range(a, r, log(minESS(p, alpha = .1, eps = .1)/(m*conv.pts))), lwd = 2)
+plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "log(ESS/mn)", ylim = range(a, r), lwd = 2)
 lines(conv.pts, r, col = "royalblue", lwd = 2)
 segments(x0 = conv.pts, y0 = (a - se.a), y1 = (a + se.a), col = adjustcolor("darkorange", alpha.f = .50))
 segments(x0 = conv.pts, y0 = (r - se.r), y1 = (r + se.r), col = adjustcolor("royalblue", alpha.f = .50))
-lines(conv.pts, log(minESS(p, alpha = .1, eps = 0.1)/(m*conv.pts)), col = "green3", lwd=2)
 legend("topright", legend=c("A-SVE", "G-SVE"),col=c("darkorange", "royalblue"), lty=1, cex=1.2, lwd=2)
 dev.off()
 

### 2020-08-07 VAR-1/acf_plots.R
VAR plots for the new simulations

@@ -17,14 +17,14 @@ for (i in 1:(p-1)){
   }
 }
 
-phi <- diag(c(.9999, .001))
+phi <- diag(c(.999, .001))
 dummy <- matrix(1:p^2, nrow = p, ncol = p)
 dummy <- qr.Q(qr(dummy))
 phi <- dummy %*% phi %*% t(dummy)
 
 target <- target.sigma(phi, omega)
 truth <- true.sigma(phi, var = target)
-
+lag.max <- 40
 
 true.acf <- array(0, dim = c(p, p, 2*lag.max + 1))
 true.acf[,,lag.max+1] <- target
@@ -33,23 +33,25 @@ for (i in 1:lag.max){
   true.acf[,,lag.max + 1 - i] <- true.acf[,,lag.max + 1 - i + 1] %*% t(phi)
 }
 
+################ Only for creating Markov chains. Don't run. ##################
 start <- matrix(0, nrow = m, ncol = p)  #only depends on C
 
 for(i in 1:floor(m/2)){
-  start[i,] <- 0.5*i*sqrt(diag(target))
-  start[m-i+1,] <- -0.5*i*sqrt(diag(target))
+  start[i,] <- i*sqrt(diag(target))
+  start[m-i+1,] <- -i*sqrt(diag(target))
 }
 
 mc.chain.list <- list()
 global.mean <- rep(0,p)
 for (i in 1:m){
-  chain <- markov.chain(phi, omega, 1e5, start[i,])
+  chain <- markov.chain(phi, omega, 5e4, start[i,])
   global.mean <- global.mean + colMeans(chain)
   mc.chain.list[[i]] = chain
   print(colMeans(chain))
 }
 global.mean <- global.mean/m
 save(mc.chain.list, file = "Out/five_chains.Rdata")
+#################################################################################
 
 load(file = "Out/five_chains.Rdata")
 #######################################################
@@ -57,6 +59,7 @@ load(file = "Out/five_chains.Rdata")
 #######################################################
 
 component <- 1
+
 ###############################
 ### ncrop = 1e3
 ##############################
@@ -67,11 +70,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, graph = FALSE)$'G-ACF'
[…]

### 2020-08-07 VAR-1/output.R

@@ -45,12 +45,6 @@ conv.pts <- seq(min, max, step)
 ############## log Frobenius norm running plots ###########
 ###########################################################
 
-
-
-pdf(file = paste("Out/sensor-frob.pdf", sep = ""), height = 5, width = 5)
-dev.off()
-
-
 load(file = paste("Out/conv_data_min", min, "_max", max, ".Rdata", sep = ""))
 
 a <- lapply(asv, function(x) log(apply(x, 3, norm, "F") ) )
@@ -69,7 +63,8 @@ plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation 
 lines(conv.pts, r, col="royalblue", lwd = 2)
 segments(x0 = conv.pts, y0 = (a - se.a), y1 = (a + se.a), col = adjustcolor("darkorange", alpha.f = .50))
 segments(x0 = conv.pts, y0 = (r - se.r), y1 = (r + se.r), col = adjustcolor("royalblue", alpha.f = .50))
-legend("bottomright", legend=c("A-SVE", "G-SVE"),col=c("darkorange", "royalblue"), lty=1, lwd = 2)
+abline(h = log(norm(truth, type = "F")), col = "green3", lwd = 2)
+legend("bottomright", legend=c("A-SVE", "G-SVE", "Truth"),col=c("darkorange", "royalblue", "green3"), lty=1, lwd = 2)
 dev.off()
 
 ###########################################################
@@ -84,11 +79,10 @@ a <- Reduce("+", a)/length(ess.asv)
 r <- Reduce("+", r)/length(ess.rsv)
 
 pdf(file = "Out/var-ess.pdf", height = 5, width = 5)
-plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "log(ESS/mn)", ylim = range(a, r, log(minESS(p)/(m*conv.pts))), lwd = 2)
+plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "log(ESS/mn)", ylim = range(a, r), lwd = 2)
 lines(conv.pts, r, col = "royalblue", lwd = 2)
 segments(x0 = conv.pts, y0 = (a - se.a), y1 = (a + se.a), col = adjustcolor("darkorange", alpha.f = .50))
[…]

### 2020-08-14 Boomerang/acf_plots.R
Revised plots

@@ -29,42 +29,28 @@ component <- 1
 lag.max <- 50
 
 ####################################
-nsim <- 1000
+nsim1 <- 1000
+nsim2 <- 1e5
 ########################################
 
 x <- list()
-for (i in 1:m)
-  x[[i]] <- mc.chain.list[[i]][1:nsim,]
+y <- list()
+for (i in 1:m){
+  x[[i]] <- mc.chain.list[[i]][1:nsim1,]
+  y[[i]] <- mc.chain.list[[i]][1:nsim2,]
+}
 
+global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
+global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
+local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
+local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
 
-global.acf <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
-local.acf <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
-
-pdf(file = paste(paste("Out/", A, B, C, "/boom-acf", A, B, C, "n", sep = "_"),  nsim, ".pdf", sep = ""), width = 10, height = 4)
+pdf(file = paste(paste("Out/", A, B, C, "/boom-acf", A, B, C, sep = "_"), ".pdf", sep = ""), width = 10, height = 4)
 par(mfrow = c(1,2))
-plot(local.acf, xlab = "Lag", ylab = "Autocorrelation", main = "")
-plot(global.acf, xlab = "Lag", ylab = "Autocorrelation", main = "")
-dev.off()
-
-
-
-####################################
-nsim <- 1e5
-########################################
-
-
-x <- list()
-for (i in 1:m)
-  x[[i]] <- mc.chain.list[[i]][1:nsim,]
-
-
-global.acf <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
[…]

### 2020-08-14 VAR-1/acf_plots.R

@@ -74,7 +74,7 @@ for (i in 1:m){
 global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
 local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
 
-pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 5, width = 10)
+pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
 plot(local.acf, main = expression("Locally centered ACF"))
 lines(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red")
@@ -95,7 +95,7 @@ for (i in 1:m){
 global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
 local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
 
-pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 5, width = 10)
+pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
 plot(local.acf, main = expression("Locally centered ACF"))
 lines(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red")

### 2020-08-16 Paper/main.tex
Sunday morning changes

@@
 The power of the modern personal computer has made it easy to run parallel Markov chain Monte Carlo (MCMC) implementations.
-This is particularly useful for slow mixing or multi-modal target distributions, where the starting points of the chains are spread over the state-space in order to more accurately capture characteristics of the target distribution.
-Output from $m$ parallel chains are then summarized, visually and quantitatively, to assess the empirical mixing properties of the chains and the quality of Monte Carlo estimators.
+This is particularly useful for slow mixing or multi-modal target distributions, where the starting points of the chains are spread over the state-space in order to capture characteristics of the target distribution more accurately.
+The output from $m$ parallel chains is then summarized, visually and quantitatively, to assess the empirical mixing properties of the chains and the quality of Monte Carlo estimators.
 
@@
 For $s = 1, \dots, m$, let $\{X_{st}; \; t \in \mathbb{Z}\}$ be the $s^{th}$ $F$-Harris ergodic stationary Markov chain \citep[see][for definitions]{meyn:twee:2009} employed to learn characteristics about $F$.
-% If $\bar{X} = n^{-1} \sum_{t=1}^{n}X_t$ , then with probability 1, $\bar{X} \to \mu$ as $n \to \infty$. \\
+% If $\bar{X} = n^{-1} \sum_{t=1}^{n}X_t$ , then with probability 1, $\bar{X} \to \mu_g$ as $n \to \infty$. \\
 The process is covariance stationary so that
@@
 \[
-    \Gamma(k) = \Cov_F(X_{s1}, X_{s\,1+k})= \mathbb{E}_F \left[(X_{s1} - \mu)(X_{s\,1+k} - \mu)^T \right]\,.
+    \Upsilon(k) = \Cov_F(X_{s1}, X_{s\,1+k})= \mathbb{E}_F \left[(X_{s1} - \mu)(X_{s\,1+k} - \mu)^T \right]\,.
 \]
@@
 Let $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ denote the Monte Carlo estimator of $\mu$ from the $s$th chain.
-The standard estimator is the sample autocovariance matrix at lag $k$ for the $s$th chain is
-%
-\begin{equation} \label{eq:empirical_acf}
-    \hat{\Gamma}_s(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}} \left(X_{st} - \bar{X}_s \right) \left(X_{s t+\abs{k}} - \bar{X}_s \right)^T\,.
+The standard estimator for $\Gamma(k)$ is the sample autocovariance matrix at lag $k$.
+For the $s$th chain, it is given by
+%
+\begin{equation} \label{eq:empirical_ACvF}
+    \hat{\Gamma}_s(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}} \left(X_{st} - \bar{X}_s \right) \left(X_{s\, t+\abs{k}} - \bar{X}_s \right)^T\,.
 \end{equation}
@@
 % It is a known fact that most of the Markov chains obtained from practical MCMC algorithms are not stationary.
-Regardless, Equation~\ref{eq:empirical_acf} provides the empirical estimator for ACF at a particular lag for the Markov chain with any initial distribution (\cite{geyer2011introduction}).\\
+Regardless, Equation~\ref{eq:empirical_ACvF} provides the empirical estimator for ACF at a particular lag for the Markov chain with any initial distribution (\cite{geyer2011introduction}).\\
 
@@
 However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
-Unfortunately, the estimator given in Equation~\ref{eq:empirical_acf} has been observed to have a some drawbacks.
+Unfortunately, the estimator given in Equation~\ref{eq:empirical_ACvF} has been observed to have a some drawbacks.
 Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains.
@@
  We propose a globally-centered ACvF (G-ACvF) that centers the Markov chain around the overall mean vector from all $m$ chains.
-We show that the bias under stationarity for G-ACvF is lower than $\hat{\Gamma}(k)$ and through various examples empirically demonstrate improved estimation.
-We employ the G-ACvF estimators to construct autocorrelation plots which leads to remarkably improvements.
+We show that the bias under stationarity for G-ACvF is lower than $\hat{\Gamma}(k)$, and through various examples, empirically demonstrate improved estimation.
+We employ the G-ACvF estimators to construct autocorrelation plots, which leads to remarkable improvements.
 A demonstrative example is at the end of this Section.
@@
 
-ACvFs are required to estimate the log-run variance of Monte Carlo averages.
+ACvFs are required to estimate the long-run variance of Monte Carlo averages.
 Specifically, spectral variance estimators are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$.
-We replace $\hat{\Gamma}(k)$ with G-ACvF in spectral variance estimators and show strong consistency of this estimator under weak conditions.
+We replace $\hat{\Gamma}(k)$ with G-ACvF in spectral variance estimators (SVE) and show strong consistency of this estimator under weak conditions.
 In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimator of $\Sigma$.
 Spectral variance estimators can be slow to prohibitively expensive to calculate \citep{liu:fleg:2018}.
-We relieve the computational burden, we adapt the fast algorithm of \cite{heberle2017fast} for G-ACvFs that dramatically reduces computation time.
-The globally-centered spectral variance estimators in employed in the computation of effective sample size and safeguards against early termination of the MCMC process and improved reliability of estimators.
+To relieve the computational burden, we adapt the fast algorithm of \cite{heberle2017fast} for G-ACvFs that dramatically reduces computation time.
+The globally-centered spectral variance estimator (G-SVE) is employed in the computation of effective sample size through the estimator given by \cite{vats2019multivariate}.
+We will show that using G-SVE for estimating $\Sigma$ safeguards us against early termination of the MCMC process and improves the reliability of estimators.
 
@@
 
-We demonstrate the striking difference in estimation of $\Gamma(k)$ via ACF plots.
+We demonstrate the striking difference in estimation of $\Gamma(k)$ via autocorrelation function (ACrF) plots.
 Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density.
-That is, $F$ is the distribution with density
+Let the target density be
 \[
@@
 Two Markov chains are started at each mode.
+Let $n$ denote the number of samples for each chain.
 Figure~\ref{fig:gaussian-trace} indicates that in the first $10^4$ samples, the chains do not jump modes so that both Markov chains yield different estimates of the population mean, $\mu$.
 At $10^5$ sample size, both Markov chains have traversed the state space reasonably and yield similar estimates of $\mu$.
-We make two points here: first, for small sample size, we observe that the locally-centered ACF gives misleading estimates   whereas G-ACF accounts for the discrepancy in sample means.
-This is evident from the ACF plots  in Figure~\ref{subfig:gauss-acf-1e4}.
-Second, for a large sample size, the estimates from G-ACF as well as ACF are equivalent in Figure \ref{subfig:gauss-trace_1e5}.
+We make two points here: first, for small sample size, we observe that the locally-centered ACF gives misleading estimates whereas G-ACF accounts for the discrepancy in sample means between two chains.
+This is evident from the ACF plots  in Figure~\ref{subfig:gauss-acf}.
+Second, for a large sample size, the estimates from G-ACrF as well as ACrF are equivalent.
+Therefore, G-ACF can be used in any situation with a promise of estimates that are at least as good as empirical ACF estimators.
 
@@
 \begin{figure}[htbp]
-\begin{subfigure}{\textwidth}
-   \centering
-   \includegraphics[width=.9\linewidth]{plots/gaussian-acf_n1e4.pdf}
+\centering
+\begin{subfigure}{.9\textwidth}
+   \centering
+   \includegraphics[width=.9\textwidth]{plots/gaussian-acf_hist.pdf}
+   \caption{$n-10^4$ (histogram) and $n = 5 \times 10^5$ (blue line)}
+   \label{subfig:gauss-acf_1e4_1e5}
+\end{subfigure}
+\begin{subfigure}{.9\textwidth}
+   \centering
+   \includegraphics[width=.9\textwidth]{plots/gaussian-acf_1e4.pdf} 
    \caption{$n = 10^4$}
-   \label{subfig:gauss-acf-1e4}
- \end{subfigure}\\
- \begin{subfigure}{\textwidth}
-   \centering
-   \includegraphics[width=.9\linewidth]{plots/gaussian-acf_n1e5.pdf} 
-   \caption{$n = 10^5$}
-   \label{subfig:gauss-acf-1e5}
- \end{subfigure}
- \caption{Autocorrelation plot for locally-centered ACF (left) and globally centered ACF (right) averaged over all chains. (a) $n = 10^4$, not converged yet; (b) $n =  10^5$, converged}
- \label{fig:gauss:acf}
+   \label{subfig:gauss-acf_1e4}
+\end{subfigure}
+\caption{ACF plots for locally-centered ACF (left) and globally centered ACF (right).
+(a) The histogram plots the estimates for $n = 10^4$ and the blue line plot the estimates for $n = 5 \times 10^4$ for chain-1.
+(b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
+\label{fig:gaussian-acf}
 \end{figure}
@@
 %
-\[
+\begin{equation} \label{eq:G-ACvF}
     \hat{\Gamma}_{G,s}(k) = \dfrac{1}{n} \sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T,
-\]
+\end{equation}
+
 In the event that all $m$ Markov chains have been run long enough that $\bar{X}_s \approx \bar{\bar{X}}$ are similar, then  $\hat{\Gamma}_{s} (k) \approx \hat{\Gamma}_{G,s}(k)$.
@@
 % If the starting points of these parallel Markov chains are sufficiently dispersed, G-ACF provides more realistic estimation of lag covariances.
-\cite{priestley1981spectral} shows that the empirical estimator in Equation \ref{eq:empirical_acf} is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
+\cite{priestley1981spectral} shows that the empirical estimator in Equation \ref{eq:empirical_ACvF} is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
 Though, an unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, the biased estimator is preferred for its lower mean square error for larger relative $k$  (\cite{priestley1981spectral})
@@
 
-\begin{theorem} \label{th:G-_expec} Let $\E_F \|X_{11}\|^{2 + \delta} < \infty$ for some $\delta > 0$.
+\begin{theorem} \label{th:G-ACF_bias} Let $\E_F \|X_{11}\|^{2 + \delta} < \infty$ for some $\delta > 0$.
 Let $P$ be a  polynomially ergodic Markov chain of order $\xi > (2 + \epsilon)/(1 + 2/\delta)$ for some $\epsilon > 0$.
@@
 \[
-\mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}_s(k) \right] = -\dfrac{\abs{k}}{n}\Gamma(k) - \dfrac{1}{m}\left(1- \dfrac{|k|}{n}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
+\mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}_s(k) \right] =  \left(1- \dfrac{|k|}{n}\right)\left(1- \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
 \]
 \end{theorem}
+
+{\color{orange}MA: I corrected the RHS for the abover equation. Or did you mean to write $\mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \Gamma(k) \right]as LHS?$}
 
@@
 $ the bias results for which can be found in \cite{priestley1981spectral}.
-Since lag-covariances are typically positive in MCMC, Theorem~\ref{th:G-_expec} implies that the G-ACvF estimators are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered ACvF estimators.
+Since lag-covariances are typically positive in MCMC, Theorem~\ref{th:G-ACF_bias} implies that the G-ACvF estimators are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered ACvF estimators.
 The consequences of this are particularly pertinent for the diagonals of $\Gamma(k)$.
@@
 \]
-The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gauss:acf}.
+The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gaussian:acf}.
 
@@
 
-Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$ and set $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.
+Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$.
+Let $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.
 By Birkhoff's ergodic theorem,  $\bar{\bar{Y}} \to \mu_g$ as $n \to \infty$ with probability 1.
@@
 \label{eq:CLT}
-  \sqrt{mn}(\bar{\bar{Y}} - \mu) \xrightarrow{d} N(0,\Sigma)\,
+  \sqrt{mn}(\bar{\bar{Y}} - \mu_g) \xrightarrow{d} N(0,\Sigma)\,
 \end{equation}
@@
 \label{eq:sigma}
-  \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right)
+  \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right) := \sum_{k = -\infty}^{\infty}\Upsilon (k)
 \end{equation}
 %
-The goal in output analysis for MCMC is to estimate $\Sigma$in order to assess variability in $\bar{\bar{Y}}$.
-There is a rich literature of estimators of $\Sigma$ available for single-chain MCMC implementations.
-The most common are spectral variance estimators (SVE) \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \cite{chen:seila:1987,vats:fleg:jon:2019}.
+The goal in output analysis for MCMC is to estimate $\Sigma$ in order to assess variability in $\bar{\bar{Y}}$.
+There is a rich literature on estimators of $\Sigma$ available for single-chain MCMC implementations.
+The most common are spectral variance estimators (SVE) \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \citep{chen:seila:1987,vats:fleg:jon:2019}.
 Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from multiple parallel chains.
-Batch means estimators are computationally more efficient than SVE, SVE estimators are more reliable \citep{fleg:jone:2010}.
+Batch means estimators are computationally more efficient than SVE, whereas SVE estimators are more reliable \citep{fleg:jone:2010}.
 Here, we utilize G-ACvF estimators to construct globally-centered SV estimator (G-SVE) of $\Sigma$.
@@
 SV estimators are constructed as weighted and truncated sums of estimated lag covariances.
-Let $w: \mathbb{R} \to [-z,z]$ be a lag window function and let $b_n \in \mathbb{N}$ be a truncation point.
+The locally and globally centered empirical estimators for $\Upsilon(k)$, $\hat{\Upsilon}_s(k)$ and $\hat{\Upsilon}_{G,s}(k)$, can be defined in a similar way as $\hat{\Gamma}_s$ and $\hat{\Gamma}_{G,s}$ in Equation~\ref{eq:empirical_ACvF},\ref{eq:G-ACvF} for the Markov chain $\{Y_{st}\}_{t \geq 1}$ for all $s$.
+Let $w: \mathbb{R} \to [-c,c]$ be a lag window function and $b_n \in \mathbb{N}$ be a truncation point.
 The SV estimator of $\Sigma$ from a single chain is
 %
-{\color{blue} DV: limits should be $-n +1$ and $n - 1$.}
+
 \begin{equation} \label{eq:sve}
-    \hat{\Sigma}_{SV,s} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)
+    \hat{\Sigma}_{s} = \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_s(k)
 \end{equation}
+
 An overall estimate of $\Sigma$ from all $m$ chains is the average SV estimator (ASV):
 \[
-\hat{\Sigma}_A = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}\;.
+\hat{\Sigma}_A = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{s}\;.
 \]
@@
 
-% Recall from Equation \ref{eq:empirical_acf} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
+% Recall from Equation \ref{eq:empirical_ACvF} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
 
@@
 % \end{equation}
-{\color{blue} DV: There are some issues.
-\begin{itemize}
-  \item $|w_n| < z$ or $|w_n| < c$?
-  \item Need new notation for $\Gamma(k)$ since $\Gamma(k)$ is for the $X$ and we need a new notation for $Y$. This change needs to be made for this whole section and the appendix!
-\end{itemize}
-}
 
@@
 \begin{align*}
-    \hat{\Sigma}_{G} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_{G}(k)\,.
+    \hat{\Sigma}_{G} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_{G}(k)\,.
 \end{align*}
@@
 % \]
-For $\hat{\Sigma}_{G}$ to accurately estimate $\Sigma$, conditions need to be imposed on the weight function, $w_n$.
-
-{\color{blue}DV: Did we discuss that $W_n$ should be define as an infinite sum and should be $W$?}
-
+For $\hat{\Sigma}_{G}$ to accurately estimate $\Sigma$, conditions need to be imposed on the weight function, $w$. 
 %
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$ where
-\[
-W_n = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\,.
-\]
+The lag window $w(x)$ is a continuous at $0$ and at all but finite number of points.
+It is bounded and even function with $w(0)=1, \; \abs{w(x)} < c$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W = \sum_{k = -\infty}^{\infty} w(k/b_n)$ is finite.
 \end{ass}
 % We will consider a range of lag windows $w(x)$; where $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$. 
-Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows.
-We will use the popular Bartlett lag window in our simulations.
-{\color{blue}DV: write the Bartlett lag window}.
+Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows. We will use the popular Bartlett lag window in our simulations. The function $w(.)$ is given by
+\[
+w(x) = \begin{cases}
+\left(1 - \abs{x}\right) & \textrm{for } \abs{x} \leq 1 \\
+0 & \textrm{otherwise}\,.
+\end{cases}
+\]
+
+In relation to lag window, we are interested in $w(k/b_n)$ for lag-$k$.
+Therefore, zero weightage is given to autocovariances for lag greater than the truncation point $b_n$.
+This is true for Bartlett but not true for the quadratic spectral lag window in \cite{andr:1991} for example.
 
@@
 Let $\E_F\|Y_{11}\|^{2+ \delta} < \infty$ for $\delta > 0$ and let $P$ be a polynomially ergodic Markov chain of order $\xi > (q + 1 + \epsilon)/(1 + 2/\delta)$ for $q \geq 1$.
-Then there exists a $p \times p$ lower triangular matrix $L$ such that $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for almost all $w \in \Omega$ such that for all $n > n_0$, with probability 1,
+Then there exists a $p \times p$ lower triangular matrix $L$ such that $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for almost all $\omega \in \Omega$ such that for all $n > n_0$, with probability 1,
 \[
@@
 % We are interested in the finding the bias for G-SVE estimator as a function of $n$. 
-{\color{blue} Move these two sub-assumptions into the theorem 4 below.}
-\begin{ass} \label{ass:bias}
-    Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that for all $s$
-    \begin{enumerate} [a.]
-        \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma_s(k)\| < \infty$ {\color{blue} DV: This assumption is satisfied by the polynomial ergodicity, so can remove it.}
-        \item $\lim _{x \to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty$ 
-        \item $\dfrac{b_n^q}{n} \to 0$ as $n \to \infty$
-    \end{enumerate}
+%\begin{ass} \label{ass:bias}
+    % Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that for all $s$
+    % \begin{enumerate} [a.]
+    %     \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma_s(k)\| < \infty$ {\color{blue} DV: This assumption is satisfied by the polynomial ergodicity, so can remove it.}
+    %     \item $\lim _{x \to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty$ 
+%        \item $\dfrac{b_n^q}{n} \to 0$ as $n \to \infty$
+%   \end{enumerate}
 
     % If $k_q$ is finite for some $q_o$, then it is zero for $q < q_0$. $q$ is taken to be the largest number satisfying the first two conditions above.
-\end{ass}
+%\end{ass}
 
 \begin{theorem}\label{th:G-SVE_bias}
-Let assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that {\color{blue}......} Let the Assumption~\ref{ass:bias} hold. Then
-\[
- \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}
+Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that $\lim _{x \to 0}{1 - w(x)}/\abs{x}^q = k_q < \infty$ and $b_n^q/n \to 0$ as $n \to \infty$. Then
+\[
+ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.
  \]
@@
 \begin{theorem} \label{th:G-SVE_variance}
- Let assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E \|Y_{11}\|^4 < \infty$, then $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+ Let the assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E \|Y_{11}\|^4 < \infty$, then $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
 \end{theorem}
-
-{\color{blue} I have not looked at it after here. }
 
@@
 
-The multivariate spectral variance estimator (MSVE) despite having good statistical properties poses application limitations due to slow computation and high storage demands.
-Observe from equation \ref{eq:empirical_acf} and \ref{eq:sve}, the computation of spectral variance estimator has a complexity of $\mathcal{O}(b_n n p)$ where $n$ is the MCMC sample size, $p$ is the dimensionality and $b_n$ is the truncation point.
-To overcome this limitation for our experimental purposes, we used a fast Fourier transform based algorithm presented by \cite{heberle2017fast} for calculating the alternate formulation of MSVE given by Kyriakoulis (2005).\\
-
-Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = n^{-1}\sum_{t=1}^{n}X_t$ is the MCMC average.
-Let $w_k$ denote the lag-window at lag-k, i.e.
-$w_k = w_n(k/b_n)$.
-The alternate formulation for MSVE is given by
-%
-\[
-    \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
-    X_1 - \overline{X}_n  & \dots & X_n - \overline{X}_n
+The SV estimator, despite good statistical properties, poses application limitations due to slow computation.
+From equation \ref{eq:empirical_ACvF} and \ref{eq:sve}, the computation of the SV estimator has a complexity of $\mathcal{O}(n^2 p^2)$ in general, and for Bartlett (and other truncated lag windows) $\mathcal{O}(b_n n p^2)$.
+In MCMC typically, $n$ is large, for highly-correlated processes, $b
+_n$ is large, and for high-dimensional target distributions, $p$ could also be large.
+
+To overcome this limitation, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast} for our purposes.
+Suppose $w_k = w(k/b_n)$ and let $T(w)$ be the $n \times n$ Toeplitz matrix of weights with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$.
+Notice an alternate formulation of SVE for the $s^{th}$ chain $\{Y_{st};\, t \in 1, ..., n\}$ i
+%
+\begin{equation} \label{eq:kyriakoulis}
+    \hat{\Sigma}_s = \dfrac{1}{n}A_s^T T(w) A_s, \qquad \textrm{ where } A_s = \begin{pmatrix}
+    Y_{s1} - \bar{Y}_s  & \dots & Y_{sn} - \bar{Y}_s
 \end{pmatrix}^T
-\]
-
-and $T(w)$ is the $n \times n$ Toeplitz matrix of weights with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$
-%  $w = 
-% \begin{pmatrix}
-%     1 & w_1 & w_2 & \dots w_{n-1}
-% \end{pmatrix}^T$.
-$T(w)$ is an $n \times n$ matrix which can be difficult to store.
-Therefore, \cite{heberle2017fast} computed $T(w)A$ directly using an FFT based algorithm.
+\end{equation}
+
+For computational efficiency, \cite{heberle2017fast} computed $T(w)A_s$ directly using an FFT based algorithm.
 The algorithm requires embedding $T(w)$ in a $2n \times 2n$ circulation matrix $C(w^*)$.
-We write the spectral decomposition of $C(w^*)$ as $V\Lambda V^*$.
-A is extrapolated into a $2n \times p$ matrix $A^*$ such that
-\[
-    \hat{\Sigma}_{SV} = \dfrac{1}{n} A^T T(w) A = \dfrac{1}{n} A^T (C(w^*) A^*)_{1:n, :} = \dfrac{1}{n} A^T (V \Lambda V^* A^*)_{1:n, :}).
-\]
-The complete algorithm is as follows
+We write the spectral decomposition of $C(w^*)$ as $V\Lambda V^*$ where the eigenvalues of $C(w^*)$ are given by the DFT of the first column of $C(w^*)$.
+$A_s$ is extrapolated into a $2n \times p$ matrix $A_s^*$ by appending $n$ rows of $0$ vector to write Equation~\ref{eq:kyriakoulis} in the following form
+\[
+    \hat{\Sigma}_s = \dfrac{1}{n} A_s^T T(w) A_s = \dfrac{1}{n} A_s^T (C(w^*) A_s^*)_{1:n, :} = \dfrac{1}{n} A_s^T (V \Lambda V^* A_s^*)_{1:n, :}).
+\]
+Here $M_{1:r, \, 1:c}$ denotes the matrix truncation up to first $r$ rows and $c$ columns.
+For our purpose, we center the chain $\{Y_{st}; \; t \in \mathbb{Z}\}$ around $\bar{\bar{Y}}$ instead of $\bar{Y}_s$ in Equation \ref{eq:kyriakoulis} for all $s \in \{1, ..., m\}$.
+Herberle's algorithm is then applied on the formulation
+
+\[
+\hat{\Sigma}_{G,s} = \dfrac{1}{n}B_s^T T(w) B_s \qquad \textrm{ where } B_s = 
+\begin{pmatrix}
+    Y_{s1} - \bar{\bar{Y}} \; \dots \; Y_{sn} - \bar{\bar{Y}}\end{pmatrix}^T.
+\]
+The complete algorithm leads to a tremendous reduction in time and storage requirements with a computational complexity of $\mathcal{O}(p n \log n)$.
+$B_s^*$ is constructed from $B_s$ in the similar way as $A_s^*$.
+In Algorithm~\ref{algo:herberle}, we use $v^{(i)}$ to denote the $i^{th}$ element of vector $v$ and $M_{(j)}$ to denote the $j^{th}$ column of matrix $M$.
+The algorithm is the following.
 
@@
 \SetAlgoLined
-Construct $C(w^*) \textrm{ and } A^*$ from the MCMC samples.\\ Compute the DFT of the first column of $C(w^*)$. This gives the eigenvalues of $C(w^*)$.\;
+Construct $C(w^*) \textrm{ and } B_s^*$ from $\{Y_{st};\, t = 1, ...,\, n\}$.\\ 
+Compute $\Lambda$ by DFT of $C(w^*)_{(1)}$\;
 \For{$j = 1, 2, ..., p$}    
     { 
-    Calculate $V^*A_j^*$ by FFT of $A_j$\;
-    Multiply the $i^{th}$ entry of the vector $V^* A_j^*$ with the eigenvalue $\lambda_i$ for all $i = 1, 2, ..., 2n$ in order to construct $\Lambda V^* A_j^*$.\;
-    Determine $C(w^*)A^* = V \Lambda V^* A_j^*$ by inverse FFT of $\Lambda V^* A_j^*$.\;
+    Calculate $V^*B_s^{*_{(j)}}$ by FFT of $B^*_{s(j)}$.\;
+    Multiply $V^* B_{s(j)}^{*^{(i)}}$ with the eigenvalue $\lambda_i$ for all $i = 1, ..., 2n$ to construct $\Lambda V^* B_{s(j)}^*$.\;
+    Calculate $C(w^*)B^*_{s(j)} = V \Lambda V^* B_{s(j)}^*$ by inverse FFT of $\Lambda V^* B_{s(j)}^*$.\;
     }
- Select the first $n$ rows of $C(w^*)A^*$ to form $T(w)A$.\;
- Premultiply by $A^T$ and divide by $n$.
+ Select the first $n$ rows of $C(w^*)B^*_s$ to form $T(w)B_s$.\;
+ Premultiply by $B_s^T$ and divide by $n$.
  \caption{Herberle's Algorithm}
+ \label{algo:herberle}
 \end{algorithm}
 
-The algorithm has been implemented in the \texttt{R} package \texttt{mcmcse} for fast implementation of spectral variance estimators.
-We do a slight variation in the alternate formulation of SVE proposed by Kyriakoulis (2005) by centering the chain $\{X_{st}; \; t \in \mathbb{Z}\}$ around $\overline{\overline{X}}$ instead of $\overline{X}_s$ for all $s \in \{1, ..., m\}$.
-Herberle's algorithm is then applied on the formulation
-
-\[
-\hat{\Sigma}_{S,s} = \dfrac{1}{n}B^T T(w) B \qquad \textrm{ where } B = 
-\begin{pmatrix}
-    X_{s1} - \overline{\overline{X}} \; \dots \; X_{sn} - \overline{\overline{X}}\end{pmatrix}^T
-\].
-
 % subsubsection fast_implementation (end)
@@
 
-Estimating the MCSE is crucial for determining when to terminate the simulations.
-The existing stopping rules rely on the strong consistency of the estimator of $\Sigma$.
-The determinant of Monte Carlo standard error is called generalized variance in  \cite{wilks1932certain} and gives a metric for volume of confidence interval.
-
-We will use the multivariate effective sample size (m-ESS) by \cite{vats2019multivariate} to understand the effectiveness of simulations so far.
-m-ESS requires a strongly consistent estimator of $\Sigma$.
-G-SVE better captures the MCSE by considering the global sample mean across the Markov chains; which might otherwise get lost when considering a single localized slowly mixing Markov chain.
-We therefore define our ESS estimator as
-
-\[
-\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{G}}}\right)^{1/p}
-\]
-
-where $\Lambda_{mn}$ is the sample covariance of $mn$ samples. When there is no correlation in Markov chain $\hat{\Sigma}_{G} = \Lambda_{mn}$ and therefore, ESS = $n$.
+An important method of quantifying the simulation efforts is to simulate until a desired effective sample size (ESS) is obtained.
+The key motivation behind using ESS as a termination criteria is to stop the simulations when the variance of Monte Carlo average is small relative to the inherent variance in $g$ with respect to $F$ by a pre-specified factor.
+\cite{wilks:1932} suggests the determinant of a covariance matrix as a viable metric to understand the variance of a multivariate process and calls it \textit{generalized variance}.
+For a $p$-dimensional stationary Markov chain, let $\Lambda := \Var_F(Y_1))$.
+\cite{vats2019multivariate} use the ratio of generalized variances to give the following formulation for multivariate ESS (m-ESS):
+
+\[
+\textrm{ESS} = n \left(\dfrac{\abs{\Lambda}}{\abs{\Sigma}}\right)^{1/p}\, .
+\]
+
+The simulation process is stopped once the ESS is greater than a pre-specified lower-bound $W_{p}$ which is function of dimension $p$ (see \cite{vats2019multivariate} for details).
+For a multi-modal target distribution, the single chain estimators for $\Sigma$ underestimate the true generalized variance; giving an unrealistic assurance of high ESS for a given $n$.
+
+In our setting of $m$ parallel chains of $n$ samples each, define
+
+\[
+\hat{\Lambda}_{mn} = \dfrac{1}{m(n-1)}\sum_{s=1}^{m}\sum_{t=1}^{n}(Y_{st} - \bar{Y}_s)(Y_{st} - \bar{Y}_s)^T\, .
+\]
+We estimate the m-ESS by using the strongly consistent average G-SV estimator $\hat{\Sigma}_G$ for $\Sigma$ as
+
+\[
+\widehat{\textrm{ESS}}_G = mn\left(\dfrac{\abs{\hat{\Lambda}_{mn}}}{\abs{\hat{\Sigma}_{G}}}\right)^{1/p}\, .
+\]
+
+For the sake of comparison, $\widehat{\textrm{ESS}}_A$ is constructed similarly using $\hat{\Sigma}_A$ instead of $\hat{\Sigma}_G$ to estimate $\Sigma$.
+We refrain from using the globally centered version of sample covariance matrix, i.e.
+$\hat{\Upsilon}(0)$ to estimate $\Lambda$ in both $\widehat{\textrm{ESS}}_A \textrm{ and } \widehat{\textrm{ESS}}_G $.
+This is because in practice, it is preferred to underestimate the ESS than do otherwise.
+Both $\hat{\Upsilon}(0)$ and $\hat{\Lambda}_{mn}$ converge to $\Lambda$; however $\abs{\hat{\Lambda}_{mn}}$ shall underestimate $\abs{\Lambda}$ in the beginning.
+We will compare $\widehat{\textrm{ESS}}_G$ to $\widehat{\textrm{ESS}}_A$ in the following Section.
+
+% {\color{blue} Define $\Lambda_{mn}$ explicitly.
+Also first define what ESS is in truth, and then explain why we are not using $\hat{\Upsilon}_G(0)$.
+Also explain why ESS is critical since simulation is terminated when ESS $>$ M.
+Also do a "backslash text" for ESS, so that it looks like $\widehat{\text{ESS}}_G$}.
 
@@
 
-In this section we consider three different target distributions and sample multiple Markov chains using MCMC to analyse the performance of our globally-centered estimators experimentally.
-We will make the following comparisons - (1) A-ACF and G-ACF; (2) A-SVE and G-SVE; (3) estimates of $ESS/mn$ using A-SVE and G-SVE.
+In this section we consider three different target distributions and sample multiple Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators.
+We will make the following three comparisons - (1) A-ACF vs G-ACF through ACrF plots; (2) A-SVE vs G-SVE; (3) $\widehat{\textrm{ESS}}_G$ vs $\widehat{\textrm{ESS}}_A$.
+The quality of estimation of $\Sigma$ is studied by coverage probabilities for a $95 \%$ confidence interval in cases where the true mean $\mu$ is known.
+The convergence of local and global estimators as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$ denoted by $\|M\|_F$ for a matrix $M$, and (2) logarithm of estimated ESS/$mn$.
 In all the examples we consider the function $g(x) = x$, which implies the Markov chain $\{Y_t\}$ and $\{X_t\}$ are the same.
-There are only a handful of MCMC chains where the true autocovariance and asymptotic variance are known.
+
+% There are only a handful of MCMC chains where the true autocovariance and asymptotic variance are known.
 To compare the globally and locally-centered estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
@@
 
-We examine the vector autoregressive process of order 1 (VAR(1)) where the true autocovariance in known in closed form.
+There are only a handful of MCMC methods where the true autocovariance and asymptotic variance are known in closed form.
+To compare the globally and locally-centered estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
 We want to deliberately make the Markov chains explore the sample space slowly.
-Consider a p-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
+Consider a $p$-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
 %
@@
 where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{i.i.d.}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix.
-The invariant distribution for this Markov chain is $N(0, \Psi)$ where $\Vec{\Psi} = (I_{p^2} - \Phi \otimes \Phi)\Vec{\Omega}$.
-The lag-k autocovariance can be calculated easily for $k >0$ as
-%
-\begin{align*}
-    \Gamma(k) &= \Phi^k\Psi\\
-    \Gamma(-k) &= \Psi(\Phi^T)^k
-\end{align*}
-
+The invariant distribution for this Markov chain is $N(0, \Psi)$ where $\mathcal{N}(.,.)$ stands for the Gaussian distribution.
+The lag-k autocovariance $\Gamma(k)$ can be calculated for $k >0$ as $\Gamma(k) = \Phi^k\Psi \textrm{ and } \Gamma(-k) = \Psi(\Phi^T)^k$.
 The Markov chain is geometrically ergodic when the spectral norm of $\Phi$ is less than 1 (\cite{10.2307/1427459}).
-The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is given by
-%
-\[
-\Sigma = (1 - \Phi)^{-1}\Psi + \Psi(1 - \Phi^T)^{-1} - \Psi
-\]
-
- \begin{figure}[h]
-     \centering
-     \begin{subfigure}[h]{0.4\textwidth}
-          \centering
-          \includegraphics[width=\textwidth]{plots/var-sp_n1e3.pdf}
-          \caption{$n = 1000$}
-          \label{subfig:var-sp_1000}
-      \end{subfigure}
-      \begin{subfigure}[h]{0.4\textwidth}
-          \centering
-          \includegraphics[width=\textwidth]{plots/var-sp_n1e4.pdf}
-          \caption{$n = 10000$}
-          \label{subfig:var-sp_10000}
-      \end{subfigure}
-     \caption{Scatter plot of two out of five slowly mixing Markov chains starting from opposite sides of known mean.  Sample size of $1000$ (left) and $10000$ (right).}
-     \label{fig:var-sp}
- \end{figure}
-
-Let $\phi_{max}$ be the largest absolute eigenvalue of $\Phi$ such that $\abs{\phi_{max}} < 1$.
+The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is known in closed form.\\
+
+Let $\phi_{\max}$ be the largest absolute eigenvalue of $\Phi$ such that $\abs{\phi_{\max}} < 1$.
 The larger it is, the slower the Markov chain mixes.
 For our case, we require a slowly mixing VAR(1) process.
-We consider a bivariate example with $\phi_{max} = 0.9999$.
-We run five parallel Markov chains with their starting points evenly distributed about the center of invariant distribution.
-There is very high correlation between the two components in the target distribution for the chosen value of $\Phi$ and $\Omega$.
+We consider a bivariate example with $\phi_{\max} = 0.999$.
+We run five parallel deterministically initialized Markov chains with their starting points evenly distributed in the sample space.
+The correlation between the two components in the target distribution is very high for the chosen value of $\Phi$ and $\Omega$.
 As a result, it takes a long time for the Markov chain to explore the sample space significantly.
-Let $\sigma_{ij}$ denote the $ij^{th}$ element of $\Sigma$.
-We sample five parallel chains and plot the first and fifth chain in Figure \ref{subfig:var-sp_500} for two different simulation sizes.
-The first chain starts at $(\sigma_{11}/2, \sigma_{22}/2)$ and the fifth chains starts from $(-\sigma_{11}/2, -\sigma_{22}/2)$.
-For a sample size of $1000$, the chains have not moved enough from their starting points.
-Whereas, for a $n = 10,000$, the chains seem to have explored the sample space fairly well.\\
+\\
 
@@
    \centering
-   \includegraphics[width=.7\linewidth, height = 2in]{plots/var-acf_n1000.pdf}
+   \includegraphics[width=.7\linewidth]{plots/var-acf_n1000.pdf}
    \caption{$n = 10^3$}
@@
   \centering
-  \includegraphics[width=.7\linewidth, height = 2in]{plots/var-acf_n10000.pdf} 
+  \includegraphics[width=.7\linewidth]{plots/var-acf_n10000.pdf} 
   \caption{$n = 10^4$}
-  \label{subfig:var-acf_n1e5}
-\end{subfigure}
-
-\caption{Autocorrelation plot for ACF and G-ACF for first chain out of two parallel Markov chains.
-First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 10^3$, not converged yet; (b): $n =  10^4$, converged}
+  \label{subfig:var-acf_n1e4}
+\end{subfigure}
+
+\caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m=5$. (a): $n = 10^3$, not converged yet; (b): $n =  10^4$, converged. The red line marks the true ACF.}
 \label{fig:var-acf}
@@
 
-The locally and globally-centered autocorrelations averaged over all the chains have been shown in Figure~\ref{var-acf} for two different simulation sizes where the true ACrF is shown in red.
-When the individual chains have not explored well, the local sample mean is closer to the samples and possibly far away from the true mean.
-As a consequence, the empirical ACrF estimator severely underestimate the known true autocorrelations.
-When the starting values are nicely dispersed, the global mean provides a more reliable estimate of actual mean and hence, G-ACrF is closer to reality.
-In subfigure~\ref{subfig:var-acf_n1e5}, the convergence property of sample means has kicked in for each chain.
+The locally and globally-centered autocorrelations for the second chain have been shown in Figure~\ref{fig:var-acf} for two different simulation sizes where the true ACF is shown by the red line.
+When the individual chains have not explored well, the local sample means have not converged to $\mu$.
+As a consequence, the single chain empirical ACF estimator severely underestimate the truth.
+Due to sufficiently dispersed starting values, G-ACF is closer to reality.
+In subfigure~\ref{subfig:var-acf_n1e4}, the convergence property of sample means has kicked in for each chain.
 Therefore, both the estimators provide equivalent results.
-\\
-
-\begin{figure}[htbp]
+Note that G-ACF reveals the true nature of ACF for almost ten times lesser chain length $n$.\\
+
+\begin{figure}[h]
     \centering
@@
       \includegraphics[width = \textwidth]{plots/var-frob.pdf}
-      \caption{log-Frobenius norm}
+      \caption{$log(\|\hat{\Sigma}\|_F)$}
       \label{subfig:var-frob}
@@
       \includegraphics[width = \textwidth]{plots/var-ess.pdf}
-      \caption{$\log(\hat{ESS}/mn)$}
-      \label{subfig:var-frob}
-    \end{subfigure}
-    \caption{(a) Running plot for logarithm of Frobenius norm of A-SVE and G-SVE from $n = 500$ to $n = 10^5$.
-(b) Running plot for logarithm of $\hat{ESS}/mn$ calculated using A-SVE and G-SVE from $n=500$ to $n=10^5$.}
+      \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
+      \label{subfig:var-ess}
+    \end{subfigure}
+    \caption{VAR(1).
+(a) Running plot for logarithm of Frobenius norm of A-SVE and G-SVE from $n = 500$ to $n = 10^5$.
+(b) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ calculated using A-SVE and G-SVE from $n=500$ to $n=10^5$.}
     \label{fig:var-frob_n_ess}
@@
 
-The quality of estimation of $\Sigma$ and $ESS/mn$ has been studied through two running plots - (a) convergence of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log(\|\hat{\Sigma}_G\|_F)$ as $n$ increases and (b) convergence of $\log(\hat{ESS}_A/mn)$ and $\log(\hat{ESS}_G/mn)$ as $n$ increases.
-In practice, it is preferred to slightly overestimate both the values than to underestimate.
+The quality of estimation of $\Sigma$ and $\text{ESS}/mn$ has been studied through convergence of - (a) $\log(\|\hat{\Sigma}_A\|_F)$ and $\log(\|\hat{\Sigma}_G\|_F)$ as $n$ increases and (b) $\log(\widehat{\textrm{ESS}}_A/mn)$ and $\log(\widehat{\textrm{ESS}}_G/mn)$ as $n$ increases.
+In practice, it is preferred to slightly overestimate the variance and underestimate the ESS than do otherwise.
 In Figure~\ref{fig:var-frob_n_ess}, both the running plots are shown along with the green horizontal line which marks the truth.
-We run the simulations for 50 replications for each value of $n$ and plot the average as well as the $95\%$ confidence interval.
-We run the simulations for a maximum sample size of $10^5$ until when, it can be seen that $\|\hat{\Sigma}_G\|_F$ and $\|\hat{\Sigma}_A\|_F$ have not converged.
-However, the globally-centered estimator is always closer to reality.
-Before actual convergence, it can be observed that $\hat{ESS}_G/mn$ overestimates the effective sample size but it is preferred to sample more as compared to premature stopping of the sampling process.\\
+We run the simulations for 50 replications for each value of $n$ and plot the average as well as standard errors.
+We run the simulations for a maximum chain length of $5 \times 10^4$ when the estimators seem to have almost converged.
+From Figure~\ref{subfig:var-frob}, it can be seen that for first $10000$ samples, A-SV estimates can be absurdly small giving false confidence in single chain estimates whereas G-SV gives a better understanding of reality.
+Similar comparative argument can can given for ESS.
 
@@
     \begin{tabular}{|c|c|c|}
+    \hline
     n & A-SVE & G-SVE\\
     \hline
-    1000 & 0.526 & 0.975\\
-    5000 & 0.622 & 0.963\\
-    10,000 & 0.694 & 0.953\\
-    50,000 & 0.864 & 0.944\\
-    100,000 & 0.901 & 0.943\\
+    1000 & 0.71 & 0.956\\
+    5000 & 0.843 & 0.937\\
+    10,000 & 0.885 & 0.924\\
+    50,000 & 0.928 & 0.945\\
+    100,000 & 0.944 & 0.952\\
+    \hline
     \end{tabular}
-    \caption{Coverage probabilities for a $95$ percent confidence interval of global mean constructed using $A-SVE/mn$ and $G-SVE/mn$ as variance estimates around the known mean.}
+    \caption{VAR(1). Coverage probabilities for a $95$ percent confidence interval of global mean constructed using A-SVE and G-SVE as variance estimates around the known mean.}
     \label{tab:var-coverage}
@@
 Table~\ref{tab:var-coverage} shows that for each sample size, the globally-centered SV estimator for variance gives better coverage than A-SVE.
-At $n=10^5$, the convergence nature starts appearing and both the estimators give good coverage probability.
+At $n=10^5$, both the estimators have converged and give equivalently good coverage probability.
 
@@
 
-Our estimators perform exceptionally better than the classical single-chain estimators in case of multimodal target distribution.
+Our globally-centered estimators perform exceptionally better than the single-chain estimators in case of multimodal target distribution.
 To that end, we will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions.
@@
     \centering
-    \begin{subfigure}[h]{.4\textwidth}
-        \centering
-        \includegraphics[width = \textwidth]{plots/boom-3d_density_plot_1_3_8.pdf}
-        \caption{$A = 1, B = 3, C = 8$}
-        \label{subfig:boom-pers_1_3_8}
-    \end{subfigure}
-    \begin{subfigure}[h]{.4\textwidth}
-        \centering
-        \includegraphics[width = \textwidth]{plots/boom-3d_density_plot_1_10_7.pdf}
-        \caption{$A = 1, B = 10, C = 7$}
-        \label{subfig:boom-pers_1_10_7}
-    \end{subfigure}
-    \caption{Perspective plots of the target distribution for two different parameterizations.}
-   \label{fig:3d_plot}
+    \begin{subfigure}[h]{.45\textwidth}
+        \centering
+        \includegraphics[width = \textwidth]{plots/boom-2d_density_plot_1_3_8.pdf}
+        \caption{Setting-1}
+        \label{subfig:boom-2D_1_3_8}
+    \end{subfigure}
+    \begin{subfigure}[h]{.45\textwidth}
+        \centering
+        \includegraphics[width = \textwidth]{plots/boom-2d_density_plot_1_10_7.pdf}
+        \caption{Setting-2}
+        \label{subfig:boom-2D_1_10_7}
+    \end{subfigure}
+    \caption{Boomerang. Contour plots of the target distribution for both settings. Overlayed scatter plot for two chains (in different colors) starting near each mode.}
+   \label{fig:boom-2D}
 \end{figure}
 
-We report results for two different bi-modal settings (parameterizations) in this example.
-Firstly, we use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ wherein the two modes are well-separated with a very low connection (Setting-1, Figure~\ref{subfig:boom-pers_1_3_8}).
-Secondly, to examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$ wherein the two model are closer and well-connected (Setting-2, Figure~\ref{subfig:boom-pers_1_10_7}).
-We sample five parallel chains with starting points dispersed uniformly in the first quadrant.
+We report results for two different bi-modal parameter settings in this example.
+Firstly, we use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ wherein the two modes are well-separated with a very low connection (Setting-1, Figure~\ref{subfig:boom-2D_1_3_8}).
+Secondly, to examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$ wherein the two modes are closer and well-connected (Setting-2, Figure~\ref{subfig:boom-2D_1_10_7}).
+We will make another point through this example.
+For a fast mixing Markov chain, the globally-centered and locally-centered estimators give equivalent results.
+Therefore, it is a better practice to globally center the chains in any situation.
+We sample five parallel deterministically initialized chains with starting points dispersed uniformly in the first quadrant.
 Finding the actual mean of this distribution in closed form is difficult.
 Therefore, we use numerical integration with fine tuning to calculate it.
-To visualize the sticky nature of Markov chains in Setting-1, we show a scatter plot of two Markov chains starting near the two modes in Figure~\ref{fig:boom-sp}.
-Figure~\ref{fig:boom-sp} shows the scatter plot for both settings for $n=1000$.
+
+ To visualize the sticky nature of Markov chains in Setting-1, we show a scatter plot of two Markov chains starting near the two modes for $n = 1000$ in Figure~\ref{fig:boom-2D}.
 For the first thousand samples, both the chains are oblivious of the existence of another mode in setting-1.
-Whereas in setting-2, the chains have mixed fairly well even for $n=1000$.
+Whereas in setting-2, the chains have mixed fairly well for just $n=1000$.
 
@@
     \centering
-    \begin{subfigure}[h]{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-sp_1_3_8.pdf}
-      \caption{$A = 1,\; B = 3, \; C = 8$}
-      \label{subfig:boom-sp_1_3_8}
-    \end{subfigure}
-    \begin{subfigure}[h]{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-sp_1_10_7.pdf}
-      \caption{$A = 1, \; B = 10, \; C = 7$}
-      \label{subfig:boom-sp_1_10_7}
-    \end{subfigure}
-    \caption{Scatter plots for Setting-1 (left) and Setting-2 (right) at a sample size $n = 1000$.}
-    \label{fig:boom-sp}
+    \includegraphics[width = .9\textwidth]{plots/boom-acf_1_3_8.pdf}
+    \caption{Boomerang (setting-I). A-ACF (left) and G-ACF (right) of component-1 for $n=1000$ (histogram) and $n=10000$ (blue line) }
+    \label{fig:boom-acf_1_3_8}
 \end{figure}
 
-%
- In Figure \ref{subfig:boom-acf_1_3_8_n1e3}, the autocorrelations are severely underestimated by A-ACF because the chains have not jumped modes.
-Whereas, in Figure \ref{subfig:boom-acf_1_3_8_n1e5}, both ACF and G-ACF give almost indistinguishable results indicating that A-ACF and G-ACF have converged.
-We can observe in Figure~\ref{fig:boom-acf_1_10_7_n1e3} that A-ACF and G-ACF give similar results for simulation setting-2.
-The Markov chains explore both the modes in 1000 iterations only.
-Therefore, the global and local means do not differ significantly.\\
-
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf_1_3_8_n1000.pdf}
-      \caption{$n = 1000$}
-      \label{subfig:boom-acf_1_3_8_n1e3}
-    \end{subfigure}
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf_n_1_3_8_n1e+05.pdf}
-      \caption{$n = 100000$}
-      \label{subfig:boom-acf_1_3_8_n1e5}
-    \end{subfigure}
-    \caption{A-ACF and G-ACF of component-1 at two different sample size for simulation setting-1.  }
-    \label{fig:boom-acf}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width = 0.9\textwidth ]{plots/boom-acf_1_10_7_n1000.pdf}
+    \caption{Boomerang. A-ACF (left) and G-ACF (right) of component-1 for $n=1000$}
+    \label{fig:boom-acf_1_10_7}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width = 0.8\textwidth, height = 2in ]{plots/boom-acf_1_10_7_n1000.pdf}
-    \caption{A-ACF and G-ACF of component-1 for simulation setting-2}
-    \label{fig:boom-acf_1_10_7_n1e3}
-\end{figure}
-
-\begin{figure}[htbp]
+ In Figure \ref{fig:boom-acf_1_3_8}, the autocorrelations are severely underestimated by A-ACF for $n=1000$ because the chains have not jumped modes.
+Whereas, for $n=10000$, both ACF and G-ACF give almost indistinguishable results indicating that A-ACF and G-ACF have converged to the truth.
+We can observe in Figure~\ref{fig:boom-acf_1_10_7} that A-ACF and G-ACF give similar results for just $n=1000$ under simulation setting-2.
+
+\begin{figure}[h]
     \centering
@@
       \centering
-      \includegraphics[width = \textwidth]{plots/boom-ess_1_3_8.pdf}
-      \caption{$A = 1, \; B = 3, \; C = 8$}
+      \includegraphics[width = \textwidth]{plots/boom-ess_1_3_8_m5.pdf}
+      \caption{Setting-1}
       \label{subfig:boom-ess1}
@@
       \centering
-      \includegraphics[width = \textwidth]{plots/boom-ess_1_10_7.pdf}
-      \caption{$A = 1, \; B=10, \; C = 7 $}
+      \includegraphics[width = \textwidth]{plots/boom-ess_1_10_7_m5.pdf}
+      \caption{Setting-2}
       \label{subfig:boom-ess2}
     \end{subfigure}
-    \caption{Running plot for $\hat{\text{ESS}}/mn$ using ASV and G-SVE  for $m = 2$.}
+    \caption{Boomerang. Running plot for $\log \hat{\text{ESS}}_A/mn$ and $\log \hat{\text{ESS}}_G/mn$ for $m = 5$.}
     \label{fig:boom-ess}
@@
 
-A good estimate of ESS is crucial to determine when to stop the simulations.
-We can see in Figure \ref{fig:boom-ess} that for the first few thousand samples, A-SVE gives misleadingly higher estimates of $ESS/mn$ than G-SVE.
+\begin{figure}[h]
+    \centering
+
+    \begin{subfigure}[h]{.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-frob_1_3_8_m5.pdf}
+      \caption{Setting-1}
+      \label{subfig:boom-frob1}
+    \end{subfigure} \hspace{1cm}
+    \begin{subfigure}[h]{.4\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/boom-frob_1_10_7_m5.pdf}
+      \caption{Setting-2}
+      \label{subfig:boom-frob2}
+    \end{subfigure}
+    \caption{Boomerang. Running plot for $\log \|\hat{\Sigma}_A\|_F$ and $\log \|\hat{\Sigma}_G\|_F$ for $m = 5$.}
+    \label{fig:boom-frob}
+\end{figure}
+
+The convergence of $\log \widehat{\textrm{ESS}}_G/mn$ and $\log \widehat{\textrm{ESS}}_A/mn$ as $n$ increases can be seen in Figure~\ref{fig:boom-ess}.
+We can see that in the beginning, A-SVE gives misleadingly higher estimates of ESS$/mn$ than G-SVE.
 This can cause us to stop the sampling before each chain jumps to the other mode.
 As a consequence, each chain will correspond to a uni-modal target distribution.
-Whereas, as expected, the ESS estimates for setting-2 are almost same.\\
-
-\begin{table}[htbp]
-\centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    % \toprule
+Whereas, as expected, the ESS estimates for setting-2 are almost same.
+Similarly, $\|\hat{\Sigma}_G\|_F$ reaches the convergence point in less than half the time as $\|\hat{\Sigma}_G\|_F$; as evidenced in Figure~\ref{subfig:boom-frob1}.
+No significant difference can be observed for setting-2 (Figure~\ref{subfig:boom-frob2}).
+
+\begin{table}[h]
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-         \multicolumn{5}{|c|}{Setting-1} & \multicolumn{5}{|c|}{Setting-2}\\
+ $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
  \hline
-        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$} & $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
+ & A-SVE & G-SVE & A-SVE & G-SVE \\
  \hline
-        & A-SVE & G-SVE & A-SVE & G-SVE & & A-SVE & G-SVE & A-SVE & G-SVE\\
+ 5000 & 0.595 &  0.7 & 0.402 &  0.64\\
+ 10000 & 0.563 &  0.665 & 0.59 &  0.739\\
+ 50000 & 0.775 &  0.814 & 0.807 &  0.864\\
+ 100000 & 0.847 &  0.864 & 0.884 &  0.902\\
 \hline
-        $1000$ & 0.800 & 0.877 & 0.145 & 0.268 & 1000 & 0.873 & 0.884 & 0.875 & 0.898  \\
-        $5000$ & 0.633 &  0.727 & 0.436 & 0.650 & 2000 & 0.881 & 0.888 & 0.897 & 0.914    \\
-        $10000$  & 0.585 & 0.690 &  0.552 & 0.750 & 5000 & 0.902 & 0.908 & 0.919 & 0.929\\
-        $50000$  & 0.778 & 0.815 & 0.805 & 0.872 & 10000 & 0.923 & 0.927 & 0.925 & 0.926\\
-        $100000$ & 0.851 & 0.867 & 0.863 & 0.897 & 50000 & 0.951 & 0.952 & 0.939 & 0.939\\ \hline
-    % \bottomrule
 \end{tabular}
-    \caption{Boomerang. Coverage probabilities for $m=2$ and $m=5$ for both the simulation settings. }
-    \label{table:boom-coverage}
+\caption{Setting-1}
+\label{tab:boom-coverage_1}
+}
+\hfill
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+ \hline
+ $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
+ \hline
+ & A-SVE & G-SVE & A-SVE & G-SVE \\
+ \hline
+ 1000 &  0.856 &  0.868 & 0.895 &  0.9100\\
+ 5000 & 0.921 &  0.925 & 0.91 &  0.915\\
+ 10000 & 0.928 &  0.93 & 0.919 &  0.926\\
+ 50000 & 0.943 &  0.944 & 0.951 &  0.952\\
+\hline
+\end{tabular}
+\caption{Setting-2}
+\label{tab:boom-coverage_2}
+}
 \end{table}
 
-Since a numerical approximation of the true mean is available, we construct $95\%$ confidence interval using A-SVE and G-SVE.
-We report the coverage probabilities for a 1000 replications at different sample sizes.
+Using the numerical approximation of the true mean, we construct the $95\%$ confidence interval using A-SVE and G-SVE.
+We report the coverage probabilities for a 1000 replications at different sample sizes $n$.
 For both the simulation settings, we provide coverage probabilities for $m=2$ and $m=5$.
-Table \ref{table:boom-coverage} reports all the results.
-In setting-1, it can be observed that G-SVE gives consistently higher coverage probability than A-SVE.
-Whereas for setting-2, the results are almost similar.
+Table \ref{tab:boom-coverage_1}, \ref{tab:boom-coverage_2} reports all these results.
+In setting-1, it can be observed that G-SVE gives higher coverage probability than A-SVE for all values of $n$.
+Whereas for setting-2, the results are almost similar indicating the equivalence of A-SVE and G-SVE.
 
@@
 
-For our third example, we consider a real-life problem of sensor locations previously discussed by \cite{ihler2005nonparametric}.
+For our third example, we consider a real-life example of sensor locations previously discussed by \cite{ihler2005nonparametric}.
 The goal is to identify unknown sensor locations using noisy distance data.
-This problem is specifically interesting in our case because the joint posterior distribution for missing sensor locations is multi-modal.
-
-\cite{tak2018repelling} modified the simulation settings of \cite{lan2014wormhole} to include only six sensor locations (four unknown and two unknown) out of eleven locations (eight known and three unknown).
+This problem is specifically interesting in our case because the marginal posterior distribution for missing sensor locations is multi-modal for all locations.
+
 Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor.
@@
 $y_{ij}$ is specified only if $w_{ij} = 1$.
-The likelihood function is then,
-%
-\begin{multline*}
-    L(x_1, x_2, x_3, x_4) \propto \\
-\prod_{j>i} \left[ \left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{w_{ij}} \left(1 - \exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{1 - w_{ij}} \exp \left(-\dfrac{y_{ij} - \|x_i - x_j\|^2}{2 \times 0.02^2}\right)\right]
-\end{multline*}
-
-The full posterior distribution with Gaussian prior is given by,
-\begin{equation} \label{ex:sensor_post}
-    \pi (x_1, x_2, x_3, x_4 | y, w) \propto 
-    L(x_1, x_2, x_3, x_4) \times \exp \left(- \dfrac{\sum_{i = 1}^{4} x_i^Tx_i}{2 \times 0.02^2}\right) 
-\end{equation}
-
-where $y = (y_{ij}, j>i)$ and $w = (w_{ij}, j>i)$.
 We follow the Markov chain structure as described by \cite{tak2018repelling} and sample from the four bivariate conditionals for each sensor location using a Gibbs sampler.
-In their paper on Repelling Attractive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of three different sampling techniques namely - Metropolis, RAM and Tempered Transitions (TT).
-RAM is shown to improve the acceptance rate by a factor of at least 5.5 over Metropolis using the same jumping scale.
-RAM algorithm supplies Markov chains with higher jumping frequency between the modes of a multimodal target distribution.\\
+In their paper on Repelling Attractive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of different sampling techniques and show that RAM improves the acceptance rate by a factor of at least 5.5 over Metropolis using the same jumping scale.
+RAM algorithm supplies Markov chains with higher jumping frequency between the modes.
 
@@
     \centering
-    \begin{subfigure}[h]{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/sensor-sp_loc1.pdf}
-      \caption{Location-1; $n=10^5$}
-      \label{subfig:sensor-sp_loc1}
-    \end{subfigure}
-    \begin{subfigure}[h]{0.5\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/sensor-trace_loc1.pdf}
-      \caption{$x_{11}$ and $x_{12}$; $n=10^5$}
-      \label{subfig:sensor-trace_loc1}
-    \end{subfigure}
-    \caption{Sensor Network.
-(a) Scatter plot ($x_{12} \textrm{ vs } x_{11}$) for a Markov chain of length $n=10^5$; (b) Trace plots  of $x_{11}$ and $x_{12}$ for two chains started near the two modes.}
-    \label{fig:sensor-sp_n_tarce}
+    \includegraphics[width = .9\textwidth]{sensor-trace_loc1.pdf}
+    \caption{Sensor Network. Trace plot of two chains for x (left) and y (right) coordinate of sensor location-1.}
+    \label{fig:sensor-trace}
 \end{figure}
 
+This is an 8-dimensional estimation problem where the components corresponds to x and y coordinates of four unknown sensor locations.
+We will use the RAM algorithm with a jumping scale equal to $0.5$ to sample five parallel Markov chains with well-separated starting points.
+The total simulation size for each chain is fixed at $100,000$.
+Since the truth about actual mean and asymptotic variance is not known in this case, we are not interested in coverage probabilities.\\
+
+To illustrate the \textit{sticky} nature of the Markov chains, we plot the evolution of two chains (starting near different modes) with time.
+Figure~\ref{fig:sensor-trace} shows the trace plot of x and y coordinate of sensor location-1.
+It is evident that the marginal posterior for both the components is bimodal.
+Similarly, the other three locations also have a bimodal marginal distribution in each component.
+Observe that each chain explores one particular mode for a long time before jumping to another mode.
+\\
+
 \begin{figure}[h]
     \centering
-     \begin{subfigure}[h]{.4\textwidth}
+    \begin{subfigure}[h]{.45\textwidth}
       \centering
@@
       \caption{$n = 5 \times 10^3$}
-       \label{subfig:sensor-acf_n5e3}
-     \end{subfigure}
-     \begin{subfigure}[h]{.4\textwidth}
+      \label{subfig:sensor-acf_5e3}
+    \end{subfigure}
+    \begin{subfigure}[h]{.45\textwidth}
       \centering
@@
       \caption{$n = 5 \times 10^4$}
-       \label{subfig:sensor-acf_n5e4}
-     \end{subfigure}
-     \caption{A-ACF and G-ACF for component-1 at two different sample size. The locally (light blue) and globally (light orange) centered ACF for individual chain has been plotted.}
+      \label{subfig:sensor-acf_5e4}
+    \end{subfigure}
+    \caption{Sensor Network. ACrF (orange) and G-ACrF (blue) for individual chains (dotted lines) and average over all chains (thick solid line).}
     \label{fig:sensor-acf}
 \end{figure}
-
-We will use the RAM algorithm with a jumping scale equal to $0.5$ to sample five parallel Markov chains with well-separated starting points.
-The total simulation size for each chain is fixed at $100,000$.
-We sample five chains starting from dispersed starting values.
-Since the truth about actual mean and asymptotic variance is not known in this case, we are not interested in coverage probabilities.
-Instead, we will focus on a comparative study of local and global estimators in terms of - (1) autocorrelations, (2) log Frobenius norm of estimated $\Sigma$, and (3) log of estimated $ESS/mn$.\\
-
-Figure~\ref{subfig:sensor-sp_loc1} shows the scatter plot of location-1 for a single Markov chain.
-Similarly, the other three locations also have a bimodal marginal distribution in each component.
-To illustrate the \textit{sticky} nature of the Markov chains obtained from RAM sampling method, we plot the evolution of two chains (starting near different modes) with time.
-Observe that each chain explores one particular mode for a long time before jumping to another mode.
-\\
-
-Figure~\ref{fig:sensor-acf} plots the locally and globally centered ACrF estimators for individual chains as well as the average over all the chains.
-The thick lines represent the averaged estimator and the thin lines correspond to single chains.
-Figure~\ref{fig:sensor-fron_n_ess} presents the running plot of log Frobenius norm of A-ACF and G-ACF along with $95\%$ confidence interval calculated using $50$ replications for each value of $n$ (x-axis).
-In both the plots, G-SVE and $\hat{ESS}_G/mn$ prove to be drastically better than the classical single-chain estimators.
 
@@
       \includegraphics[width = \textwidth]{plots/sensor-ess.pdf}
-      \caption{$\log(\hat{ESS}/mn)$}
+      \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
       \label{subfig:sensor-ess}
     \end{subfigure}
-    \caption{Sensor Network. Running plot for log of Frobenius norm of estimated $\Sigma$ (left) and log of estimated $ESS/mn$ (right) calculated using A-SVE and G-SVE.}
-    \label{fig:sensor-fron_n_ess}
+    \caption{Sensor Network. Running plot for $\log \|{\Sigma}\|_F$ (left) and $\log {\textrm{ESS}}/mn$ (right) estimated using A-SVE and G-SVE along with standard errors for 10 replications.}
+    \label{fig:sensor-frob_n_ess}
 \end{figure}
 
+Figure~\ref{fig:sensor-acf} plots the locally and globally centered ACF estimators for individual chains  as well as the average over all the chains.
+The thick solid line plots the averaged estimator and the thin dotted lines correspond to ACF calculated using single chains.
+Figure~\ref{fig:sensor-frob_n_ess} presents the running plot of $\log \|{\Sigma}\|_F$ and $\log \textrm{ESS}/mn$ estimated using A-SVE and G-SVE along with standard errors from $10$ replications for each value of $n$.
+In both the plots, G-SVE and $\widehat{\textrm{ESS}}_G/mn$ reach the convergence value faster.
+
 \section{Discussion} \label{sec:discussion}
 
-Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
-However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
-Unfortunately, the estimator given in Equation~\ref{eq:empirical_acf} has been observed to have a some drawbacks.
-Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains.
-
-\appendix
+In case of slowly mixing Markov chains or multimodal target distributions, the traditional single chain empirical estimator for ACvF can excruciatingly underestimate the truth.
+This will have serious impact on estimation of lag covariances, large sample variance of Monte Carlo averages, and determining when to stop the simulation process.
+It has been concluded in the paper that all of this can be significantly avoided by sampling multiple chains starting from dispersed points and pooling in the information from all chains to build consistent estimators for $\Gamma(k)$, $\Sigma$, and ESS.
+We have derived the bias of G-ACvF.
+We have shown that not only G-ACvF is asymptotically unbiased but also counters the negative bias of single chain ACF estimator by an amount proportional to the number of chains $m$.
+We have also proved the strong consistency of G-SVE and derived its limiting bias and variance results.
+Although the asymptotic results for G-SVE match those for SVE in \cite{andr:1991}, finite sample advantages are observed in terms of better coverage probability and faster convergence to truth.
+
+% Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
+We have already shown the impact of G-ACF for VAR(1) model where the truth is known.
+This gives us sufficient reason to believe that similar advantage will be observed for all the other models mentioned above in case of slowly mixing chains.
+Comparison to truth will reveal similar behavior However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
+
+For the purpose of experimentation in Section~\ref{sec:examples}, Bartlett lag window has been used throughout.
+Lag window comparisons done by \cite{andr:1991} reveal that quadratic spectral (QS) lag window gives consistently better coverage probabilities for any confidence interval.
+However, SVE gives poor coverage probability for all lag windows when the amount of autocorrelation is high in the Markov chain.
+Recently, \textit{lugsail} lag window has been proposed by \cite{vats2018lugsail} to deal with this issue by deliberately accentuating the autocovariance at smaller lags.
+We have refrained from doing lag window comparisons for G-SVE in our examples but we believe it can help improve the estimation quality significantly.
+%
+
+Another class of estimators for asymptotic variance of Monte Carlo averages are the multivariate initial sequence (mIS) estimators \citep{dai:jon:2017}.
+Similar to SV estimator, lag-covariances form the fundamental part of mIS estimators.
+In case of multi-modal target distributions, single chain mIS estimator will suffer from the same drawbacks as SVE.
+In this paper, we have chiefly focused on the usage of G-ACvF for estimating autocovariances in SVE; however the argument for a similar usage in mIS is straightforward.
+Following \cite{dai:jon:2017}, generalised variance estimates obtained from mIS consistently overestimate $\abs{\Sigma}$.
+From Theorem~\ref{th:G-ACF_bias}, one can prove that, on average, the eigenvalues of $\hat{\Gamma}_{G,s}(k)$ are greater than the eigenvalues of $\hat{\Gamma}_s(k)$.
+This supplies readers with sufficient motivation to believe that the generalized variance for mIS constructed from $\hat{\Gamma}_G(k)$ not only consistently overestimates $\abs{\Sigma}$ but also upper-bounds the mIS from empirical single chain estimator of $\Gamma(k)$ for finite samples.
+An valuable line of research would be to prove these observations and carry out the theoretical analysis of mIS estimators using G-ACvF.
+%
+
+The choice of starting vector is crucial for multiple chain sampling.
+In case the chains are started very near to each other, all the chains will explore nearly the same neighborhood in the state space.
+As a consequence, the G-ACvF will be equivalent to A-ACvF, and no significant improvement will be observed in estimation quality.
+We have used a deterministic initialization method in our examples using our prior knowledge about the location of modes in the target distribution.
+Comparing existing initialization methods {\color{orange} MA: maybe cite a few} and developing new ones could be an interesting direction for future research.
 
@@
 (\cite{csorgo2014strong}).
-Suppose Assumption \ref{ass:sip} holds, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}$ and $\forall i = 1, ..., p$
+Suppose the conditions of Theorem~\ref{thm:kuelbs} hold, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}$ and $\forall i = 1, ..., p$
 
@@
 
-\subsection{Proof of Theorem~\ref{th:G-_expec}} 
+\subsection{Proof of Theorem~\ref{th:G-ACF_bias}} 
 \label{appendix:bias}
@@
 % &= m\left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
-% &= (m-1)\Var(\overline{X_1})\,.
+% &= (m-1)\Var(\bar{X_1})\,.
 % \end{align*}
@@
 %
-where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. We will study the expectations of the each of the above terms. Without loss of generality, consider $A_{11}$,
+where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$.
+Under the assumption of stationarity, we will study the expectations of the each of the above terms.
+Without loss of generality, consider $A_{11}$,
 \begin{align*}
@@
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m}\,.
+    &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
 \end{align*}
@@
 & \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
-& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
+& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
 \end{align*}
@@
 
-Consider pseudo spectral variance estimators for the $s$th chain, denoted by $\tilde{\Sigma}_s$ which uses data centered around the unobserved actual mean $\mu$:
-\begin{align*}
-    \tilde{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(X_{st}-\mu)(X_{s(t+k)}-\mu)^T \\ 
-    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Gamma}_s(k) \,.
+Consider pseudo autocovariance and spectral variance estimators for the $s$th chain, denoted by $\tilde{\Upsilon}_s(k)$ and $\tilde{\Sigma}_s$ that use data centered around the unobserved actual mean $\mu$:
+\begin{align*}
+    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T \\ 
+    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Upsilon}_s(k) \,.
 \end{align*}
@@
 \begin{align*}
-  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[ \left(X_{st}-\mu \right)_i   \left(\mu-\bar{\bar{X}} \right)_j +    \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right]\right\}\,, \\
-  %
-M_2 &= \left(\mu-\bar{\bar{X}} \right)_i   \left(\mu-\bar{\bar{X}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\,.
+  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[ \left(Y_{st}-\mu_g \right)_i   \left(\mu_g-\bar{\bar{Y}} \right)_j +    \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j \right]\right\}\,, \\
+  %
+M_2 &= \left(\mu_g-\bar{\bar{Y}} \right)_i   \left(\mu_g-\bar{\bar{Y}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\,.
 \end{align*}
@@
 \begin{align*}
-\hat{\Sigma}_{G}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st}-\bar{\bar{X}} \right)_i \left(X_{s(t+k)}-\bar{\bar{X}} \right)_j\\
-% &= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left[  \left\{\left(X_{st}-\mu \right)_i + \left(\mu-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_j \right \} \right]\\
-&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left[ \left(X_{st}-\mu \right)_i  \left(X_{s(t+k)}-\mu \right)_j+  \left(X_{st} - \mu \right)_i    \left(\mu - \bar{\bar{X}} \right)_j \right.
+\hat{\Sigma}_{G}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(Y_{st}-\bar{\bar{Y}} \right)_i \left(Y_{s(t+k)}-\bar{\bar{Y}} \right)_j\\
+% &= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left[  \left\{\left(X_{st}-\mu_g \right)_i + \left(\mu_g-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu_g \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_j \right \} \right]\\
+&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left[ \left(Y_{st}-\mu_g \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j+  \left(Y_{st} - \mu_g \right)_i    \left(\mu_g - \bar{\bar{Y}} \right)_j \right.
 \\
-& \quad + \left. \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(\mu-\bar{\bar{X}}  \right)_j  \right]\\
-& = \tilde{\Sigma}^{ij} + \left[(\mu-\bar{\bar{X}})_i(\mu-\bar{\bar{X}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] \\ 
-& \quad  + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}  \left[\dfrac{1}{n} \left(X_{st} - \mu \right)_i \left(\mu - \bar{\bar{X}} \right)_j + \dfrac{1}{n} \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)}-\mu \right)_j \right] \\
+& \quad + \left. \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j + \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(\mu_g-\bar{\bar{Y}}  \right)_j  \right]\\
+& = \tilde{\Sigma}^{ij} + \left[(\mu_g-\bar{\bar{Y}})_i(\mu_g-\bar{\bar{Y}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] \\ 
+& \quad  + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}  \left[\dfrac{1}{n} \left(Y_{st} - \mu_g \right)_i \left(\mu_g - \bar{\bar{Y}} \right)_j + \dfrac{1}{n} \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j \right] \\
 & = \tilde{\Sigma}^{ij} + M_1 + M_2\,.
@@
 \begin{align*}
-  \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| = \dfrac{1}{mn}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| \\
-  % &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
-  & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
+  \|\bar{Y}_s - \mu_g\|_{\infty} & \leq \|\bar{Y}_s - \mu_g\| = \dfrac{1}{mn}\left\|\sum_{t=1}^{n}Y_{st} - n\mu_g\right\| \\
+  % &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu_g \pm L B(n) \right\|\\
+  & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}Y_{st} - n \mu_g - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
   &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
@@
 \label{eq:xbarbar_bound}
-   \| \bar{\bar{X}} - \mu\|_{\infty} \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\,.
+   \| \bar{\bar{Y}} - \mu_g\|_{\infty} \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\,.
 \end{equation}
 %  \begin{align*}
-%   \| \bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{n}\left\|\sum_{s=1}^{m} \left(\sum_{t=1}^{n}X_{st} - n\mu \right)\right\| \\
-%   &\leq \dfrac{1}{m}\sum_{s=1}^{m}\dfrac{1}{n}  \left \| \sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
-%   & \leq \dfrac{1}{m} \sum_{s=1}^{m} \dfrac{1}{n}\left\| \sum_{t=1}^{n}X_{st} - n \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
+%   \| \bar{\bar{X}} - \mu_g\|_{\infty} & \leq \|\bar{\bar{X}} - \mu_g\| = \dfrac{1}{n}\left\|\sum_{s=1}^{m} \left(\sum_{t=1}^{n}X_{st} - n\mu_g \right)\right\| \\
+%   &\leq \dfrac{1}{m}\sum_{s=1}^{m}\dfrac{1}{n}  \left \| \sum_{t=1}^{n}X_{st} - n\mu_g \pm L B(n) \right\|\\
+%   & \leq \dfrac{1}{m} \sum_{s=1}^{m} \dfrac{1}{n}\left\| \sum_{t=1}^{n}X_{st} - n \mu_g - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
 %   &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
@@
 & |M_1| \\ 
-   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\
-   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|} \left(X_{st} - \mu \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-|k|} \left(\mu-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu \right)_j\right|} \right]\right\}\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t=1}^{n-|k|}(X_{st}- \mu)_i\right|\left|(\mu-\bar{\bar{X}})_j\right|+ \dfrac{1}{n}\left|(\mu-\bar{\bar{X}})_i\right|\left|\sum_{t=1}^{n-|k|}(X_{j(t+k)}-\mu)_j\right|\right]\right\}\\
-    & \leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(X_{st}-\mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(X_{s(t+k)}-\mu)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \\
-    & \quad \times \sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu) - n(\bar{X}_s - \mu) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(X_{st} - \mu) - n(\bar{X}_s - \mu)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} + 2\|\bar{X}_s - \mu\|_{\infty} \right]\\
-    & \leq \dfrac{\|(\bar{\bar{X}} - \mu)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t=n-|k|+1}^{n}(X_{st} - \mu)\right\|_{\infty} + \left\|\sum_{t=1}^{|k|}(X_{st} - \mu)\right\|_{\infty} \right]\\
-    & \; \;+ 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\|\bar{X}_1 - \mu\|_{\infty}\,.
+   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu_g \right)_i  \left(\mu_g-\bar{\bar{X}} \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu_g \right)_j\right]\right\}\right| \\
+   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|} \left(X_{st} - \mu_g \right)_i  \left(\mu_g - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-|k|} \left(\mu_g-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu_g \right)_j\right|} \right]\right\}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t=1}^{n-|k|}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t=1}^{n-|k|}(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
+    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
+    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \\
+    & \quad \times \sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g)\right\|_{\infty} \right]\\
+    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
+    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t=n-|k|+1}^{n}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t=1}^{|k|}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
+    & \; \;+ 2(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_1 - \mu_g\|_{\infty}\,.
 \end{align*}
@@
 |M_1|
-    & < 2\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \right]  + 2(2b_n - 1) \|\bar{X}_1 - \mu\|_{\infty} \\
-    &\leq 2(2b_n - 1)\|(\bar{\bar{X}} - \mu)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{X}_1 - \mu\|_{\infty}  \right]\\
-    % & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu\|_{\infty}\\
+    & < 2\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \right]  + 2(2b_n - 1) \|\bar{Y}_1 - \mu_g\|_{\infty} \\
+    &\leq 2(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_1 - \mu_g\|_{\infty}  \right]\\
+    % & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu_g\|_{\infty}\\
     & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,.
@@
 \begin{align*}
-   |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu - \bar{\bar{X}} \right)_i  \left(\mu - \bar{\bar{X}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
-    & \leq\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
-    % &= b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
-    & \leq b_n\|\bar{\bar{X}} - \mu\|_{\infty}^2 \int_{-\infty}^{\infty}|w(x)|dx \\
-    % & \leq Cb_n\|\bar{\bar{X}} - \mu \|^2 \\ 
+   |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu_g - \bar{\bar{Y}} \right)_i  \left(\mu_g - \bar{\bar{Y}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
+    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+    % &= b_n\|\bar{\bar{X}} - \mu_g\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+    & \leq b_n\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2 \int_{-\infty}^{\infty}|w(x)|dx \\
+    % & \leq Cb_n\|\bar{\bar{X}} - \mu_g \|^2 \\ 
     & \leq Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 \quad \text{ (by \eqref{eq:xbarbar_bound})} \numberthis \label{eq:strong_consis_term-2} \,.
@@
 Thus, $g_1(n), g_2(n)$ and $g_3(n) \to 0$ as $n \to \infty$.
+{\color{orange} MA: Should we add a footnote here telling why $\phi(n)=o(\sqrt{n \log \log n})?$ It was earlier stated explicitly in Assumption-1 which is not Theorem-1.}
 
@@
 \tilde{\Sigma}^{ij}
-    % & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu \right)_i  \left(X_{s(t + k)} - \mu \right)_j\\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} \pm \bar{X}_s - \mu \right)_i  \left(X_{s(t + k)} \pm \bar{X}_s - \mu \right)_j\\
-    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i   \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
-    & \quad + \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\\
+    % & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu_g \right)_i  \left(X_{s(t + k)} - \mu_g \right)_j\\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(Y_{st} \pm \bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t + k)} \pm \bar{Y}_s - \mu_g \right)_j\\
+    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i   \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right]\\
+    & \quad + \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{Y}_s - \mu_g \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\\
     & = \hat{\Sigma}_{SV}^{ij} + N_1 + N_2 \,,
@@
 \begin{align*}
-N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right]\\
-N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{X}_s - \mu \right)_i  \left(\bar{X}_s - \mu \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\,.
+N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right]\\
+N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{Y}_s - \mu_g \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\,.
 \end{align*}
@@
 %
-By Assumption~\ref{ass:sve_consis}, the first term goes to 0 with probability 1 and by Lemma~\ref{lemma:G-SVE_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
+By the strong consistency of single-chain SV estimator, the first term goes to 0 with probability 1 and by Lemma~\ref{lemma:G-SVE_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
 It is left to show that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1
@@
 \begin{align*}
-|N_1| & = \left|\dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j + \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right] \right|\\
-& \leq \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right| \\
-& \quad + \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(\bar{X}_s - \mu \right)_i  \left(X_{s(t+k)} - \bar{X}_s \right)_j\right] \right|
+|N_1| & = \left|\dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right] \right|\\
+& \leq \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right| \\
+& \quad + \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right] \right|
 \end{align*}
@@
 \begin{align*}
-    & \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right| \\
-    % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left| w\left(\dfrac{k}{b_n}\right) \right| \dfrac{ \left|  \left(\bar{X}_s - \mu \right)_j \right| }{n} \left[ \left|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right)_i \right| + \abs{k} \left|\left(\bar{X}_s - \mu \right)_i \right|\right]\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(\mu - X_{st} \right) + \abs{k} \left(\bar{X}_s - \mu \right)\right\|_{\infty}\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left(\left\|\sum_{t=1}^{|k|}  \left(X_{st} - \mu \right)\right\|_{\infty} + \abs{k}\|\bar{X}_s - \mu\|_{\infty} \right)\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{X}_s - \mu\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(X_{st} - \mu\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{X}_s - \mu \right \|_{\infty}^2\,.
+    & \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right| \\
+    % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu_g \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left| w\left(\dfrac{k}{b_n}\right) \right| \dfrac{ \left|  \left(\bar{Y}_s - \mu_g \right)_j \right| }{n} \left[ \left|\sum_{t=1}^{|k|} \left(\mu_g - Y_{st} \right)_i \right| + \abs{k} \left|\left(\bar{Y}_s - \mu_g \right)_i \right|\right]\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(\mu_g - Y_{st} \right) + \abs{k} \left(\bar{Y}_s - \mu_g \right)\right\|_{\infty}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left(\left\|\sum_{t=1}^{|k|}  \left(Y_{st} - \mu_g \right)\right\|_{\infty} + \abs{k}\|\bar{Y}_s - \mu_g\|_{\infty} \right)\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.
 \end{align*}
@@
 \begin{align*}
-    & \left|\dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(X_{st} - \bar{X}_s \right)_i  \left(\bar{X}_s - \mu \right)_j \right] \right|\\
-   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2\\
-   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{X}_s - \mu\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{X}_s - \mu\|_{\infty}^2 \\
+    & \left|\dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right|\\
+   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2\\
+   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2 \\
    &  \leq   \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
@@
     |N_2| & \leq Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
-    % \left|\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu \right)_i \left(\bar{X}_s - \mu \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right|\\
-    % & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
-    % & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
-    % & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
+    % \left|\dfrac{1}{m} \sum_{s=1}^{m} \left(\bar{X}_s - \mu_g \right)_i \left(\bar{X}_s - \mu_g \right)_j\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right|\\
+    % & < \dfrac{1}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu_g\|_{\infty}^2 \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    % & = \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu_g\|_{\infty}^2\, \dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\\
+    % & \leq \dfrac{b_n}{m}\sum_{s=1}^{m} \|\bar{X}_s - \mu_g\|_{\infty}^2 \int_{-\infty}^{\infty} \abs{w(x)}dx\,.
 \end{align*}
@@
 By Equation~\ref{eq:G-ACF_expec_breakdown},
-\begin{align*}
-\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right]
-% &  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
-& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + \mathcal{O} \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
-\end{align*}
-%
-\begin{equation} \label{eq:G-_bias2}
-\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
-\end{equation}
-%
-where both $O_1 \textrm{ and } O_2$ are the small order terms.
-By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = n^{-1}\abs{k} \mathcal{O}(n^{-1}) \text{ and } O_2 = \mathcal{O}(n^{-1})$.
+%\begin{align*}
+%\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right]
+% &  = \left(1- \dfrac{|k|}{n}\right)\Upsilon(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m} \\
+% & = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + \mathcal{O} \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
+% \end{align*}
+%
+
+\[
+\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + O_1 + O_2    \,.
+\]
+%
+where both $O_1 \textrm{ and } O_2$ are the small order terms where $O_1 = n^{-1}\abs{k} \mathcal{O}(n^{-1}) \text{ and } O_2 = \mathcal{O}(n^{-1})$.
+By our assumptions, $\sum_{h=-\infty}^{\infty}\Upsilon(h) < \infty$.
 Consider the G-SVE estimator,
 \begin{align*}
- \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
-    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\
+ \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Upsilon(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
+    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Upsilon(k)\right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\
     & = P_1 + P_2\,,
@@
 \begin{align*}
-    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k) \textrm{ and }\\   
+    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Upsilon(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Upsilon(k) \textrm{ and }\\   
     P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
@@
 \label{eq:P1_decomp}
-P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
+P_1 = -\sum_{|k|\geq n}\Upsilon(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Upsilon(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Upsilon(k)\,.  
 \end{equation}
@@
 \begin{align*}
- {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
-\end{align*}
-%
-since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
-%
-\begin{align*}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
+ {-\sum_{|k|\geq n}\Upsilon(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Upsilon(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Upsilon(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
+\end{align*}
+%
+since $\sum_{|k|\geq n}|k|^q \Upsilon(k)  < \infty$. Next,
+%
+\begin{align*}
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Upsilon(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Upsilon(k)  \,.
 \end{align*}
@@
 \begin{align*}
-\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
+\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Upsilon(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Upsilon(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
 \end{align*}
@@
 \begin{align*}
-   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
+   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Upsilon(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Upsilon(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
 \end{align*}
@@
 \label{eq:P1_second}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Upsilon(k) = o \left(\dfrac{1}{b_n^q} \right)
 \end{equation}
@@
      % \[
-     % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
+     % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Upsilon(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
      % \]
@@
 \begin{align*}
-     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
+     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Upsilon(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Upsilon(k) \\
      & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
@@
 Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms.
-This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu$ in our replicated autovariance estimator.
-Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms.
+This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu_g$ in our replicated autovariance estimator.
+Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu_g$ contributes only $o(1)$ terms.
 % \end{proof}
@@
  &\left| \hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right|\\
- & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t=1}^{n-|k|}   \left[ \left( \dfrac{(X_{st} - \mu)_i(\mu-\bar{\bar{X}})_j}{n}\right)+ \left(\dfrac{(\mu-\bar{\bar{X}})_i(X_{s(t+k)}-\mu)_j}{n}\right) \right] \right.\\
-& \quad \quad  \left. + (\mu-\bar{\bar{X}})(\mu-\bar{\bar{X}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
+ & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t=1}^{n-|k|}   \left[ \left( \dfrac{(Y_{st} - \mu_g)_i(\mu_g-\bar{\bar{Y}})_j}{n}\right)+ \left(\dfrac{(\mu_g-\bar{\bar{Y}})_i(Y_{s(t+k)}-\mu_g)_j}{n}\right) \right] \right.\\
+& \quad \quad  \left. + (\mu_g-\bar{\bar{Y}})(\mu_g-\bar{\bar{Y}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
 \end{align*}
@@
 & \leq \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
-& := g_n^*(X_{11}, \dots, X_{1n}, \dots, X_{m1}, \dots, X_{mn})\,.
+& := g_n^*(X_{11}, \dots, Y_{1n}, \dots, Y_{m1}, \dots, Y_{mn})\,.
 \end{align*}
@@
 \section{Additional Examples}
-We present two additional examples illustrating the difference between the ACF and G-ACF plots.
+We present two additional real-world examples to illustrate the advantage of global autocorrelation estimator using ACF plots.
+For both the examples, we use a pre-established Markov chain structure and implement our estimator on the Markov chains obtained.
 % We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.
@@
 Consider the militarized interstate dispute (MID) data of \cite{martin2011mcmcpack} which describes the annual number of military conflicts in the United States.
-In order to detect the number and timings of the cyclic phases in international conflicts, we fit the following Bayesian Poisson change-point model:
-% The Poisson change-point model in \texttt{MCMCpoissonChange} uses conjugate priors and can be written as:
+In order to detect the number and timings of the cyclic phases in international conflicts, we fit a Bayesian Poisson change-point model.
+Following \cite{martin2011mcmcpack}, we will use \texttt{MCMCpoissonChange} from \texttt{MCMCpack} to fit the model with six change-points which samples the latent states based on the algorithm in \cite{chib1998estimation}.
+The Poisson change-point model in \texttt{MCMCpoissonChange} uses conjugate priors and is the following:
 %
@@
 \end{align*}
-Following \cite{martin2011mcmcpack}, we will use \texttt{MCMCpoissonChange} from \texttt{MCMCpack} to fit the model with $k = 7$ which samples the latent states based on the algorithm in \cite{chib1998estimation}.
+
 % The results of model comparison by \cite{martin2011mcmcpack} showed that the ratio of maximum likelihood for six change-point model is favored over the alternatives.
@@
     \centering
-    \includegraphics[width = 0.55\textwidth]{plots/spatio-acf.pdf}
-    \caption{ACF and G-ACF for the first component of the first chain.}
-    \label{fig:spatio-acf_G-fl}
+    \includegraphics[width = 0.9\textwidth]{plots/poisson-trace_n1e+05.pdf}
+    \caption{Trace plot for second (left) and third (right) component of two chains started from random points.The two colors denote the two different chains.}
+    \label{fig:poisson-trace}
 \end{figure}
-We run two parallel Markov chains from randomly chosen starting points and present the resulting ACF and G-ACF in Figure \ref{fig:spatio-acf_G-fl}.
-The early G-ACF estimates are far closer to the G-ACF and ACF estimates at $10^5$.
+
+This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature.
+Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second component.
+We will report the ACF plots for component-2.
+Similar behavior is observed for ACF plots of other components as well.\\
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/poisson-acf_n1000.pdf}
+      \caption{$n = 1000$}
+      \label{subfig:poisson-acf_n1e3}
+    \end{subfigure}
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/poisson-acf_n10000.pdf}
+      \caption{$n = 10000$}
+      \label{subfig:poisson-acf_n1e4}
+    \end{subfigure}
+    \caption{Poisson change point. ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for two chain lengths.}
+    \label{fig:poisson-acf}
+\end{figure}
+
+Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF in estimating the true autocorrelations.
+G-ACF gives a more realistic and accurate estimation of autocorrelations in almost ten times lesser chain length.
 
@@
 
-The goal is to draw each node uniformly from the network by using a network crawler.
+The goal is to draw nodes uniformly from the network by using a network crawler.
 \cite{nilakanta2019ensuring} modified the data by removing 1,022 out of 1,461 nodes to obtain a well-connected graph.
@@
 We use a Metropolis-Hastings algorithm with a simple random-walk  proposal suggested by \cite{gjoka2011practical}.
-The stationary distribution for this algorithm is a uniform distribution over the nodes.
+Each node is associated with five features namely - degree of connection, cluster coefficient, grade, binary sex indicator (1 for female, 0 for male), and binary race indicator (1 for white, 0 for others).\\
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/magnolia-acf_n100.pdf}
+      \caption{$n = 100$}
+      \label{subfig:magnolia-acf_n1e3}
+    \end{subfigure}
+    \begin{subfigure}[h]{.8\textwidth}
+      \centering
+      \includegraphics[width = \textwidth]{plots/magnolia-acf_n1000.pdf}
+      \caption{$n = 1000$}
+      \label{subfig:magnolia-acf_n1e4}
+    \end{subfigure}
+    \caption{Network crawling. ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for two chain lengths.}
+    \label{fig:magnolia-acf}
+\end{figure}
 % , i.e. $\lambda(i) = 1/n$ for all $i \in V$.  The Metropolis-Hastings transition kernel for this method is
@@
 % Table (blah) shows the population parameters we are interested in estimating using MCMC methods.
-The G-e and sex parameters are estimated as proportion of whites and females in the sample respectively.
-
-We start two parallel Markov chains from two students belonging to different {\color{red}G-es ???} and study its impacts on the average features of their immediate social group. 
+The race and sex parameters are estimated as proportion of whites and females in the sample respectively.
+
+We believe that the students from different races engage in a "selective networking" which might cause formation of clusters in the network wherein students within a cluster engage more with each other than with the students outside it.
+We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group.
+Figure~\ref{fig:magnolia-acf} shows the ACF and G-ACF plots for the third feature at two different simulation sizes.
+As evident, G-ACF displays a clear advantage over ACF in just $n=100$ samples.
+
 % It is hypothesized that students from certain communities tend to engage more with students of same or other marginally represented communities.

### 2020-08-17 Paper/main.tex
Pushing current version

@@
 \newcommand{\dd}[1]{\mathrm{d}#1}
+\newcommand{\ds}{\displaystyle}
 \newcommand{\E}{\mathbb{E}}
@@
 \[
-    \Upsilon(k) = \Cov_F(X_{s1}, X_{s\,1+k})= \mathbb{E}_F \left[(X_{s1} - \mu)(X_{s\,1+k} - \mu)^T \right]\,.
+    \Gamma(k) = \Cov_F(X_{s1}, X_{s\,1+k})= \mathbb{E}_F \left[(X_{s1} - \mu)(X_{s\,1+k} - \mu)^T \right]\,.
 \]
@@
 \end{equation}
+{\color{red} We need to figure out how we want to define autocovariance: with or without absolute value.}
 %
@@
 Let $g:\X \longrightarrow \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
-%
-\[
-\mu_g = \mathbb{E}_F[g(X)] = \int_{\X}g(x)F(dx)\;.
-\]
-
+$\mu_g = \mathbb{E}_F[g(X)]$.
+% \[
+% \mu_g = \mathbb{E}_F[g(X)] = \int_{\X}g(x)F(dx)\;.
+% \]
+ % 
 Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$.
@@
 
-Reliability of $\bar{\bar{Y}}$ is assessed by its Monte Carlo variability via an asymptotic sampling distribution \citep{fleg:hara:jone:2008,roy:2019,vats:rob:fle:jon:2020}. 
-% To assess the reliability of simulations, we are interested in Monte Carlo error, i.e. $\bar{Y_s} - \mu$ for the $s^{th}$ chain. 
-% The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov})
- A Markov chain central limit theorem (CLT) holds if there exists a $p \times p$ positive-definite matrix $\Sigma$ such that
+An asymptotic sampling distribution may be available via a Markov chain central limit theorem (CLT) if there exists a $p \times p$ positive-definite matrix $\Sigma$ such that
 %
@@
 %
-The goal in output analysis for MCMC is to estimate $\Sigma$ in order to assess variability in $\bar{\bar{Y}}$.
-There is a rich literature on estimators of $\Sigma$ available for single-chain MCMC implementations.
-The most common are spectral variance estimators (SVE) \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \citep{chen:seila:1987,vats:fleg:jon:2019}.
-Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from multiple parallel chains.
-Batch means estimators are computationally more efficient than SVE, whereas SVE estimators are more reliable \citep{fleg:jone:2010}.
+The goal in output analysis for MCMC is to estimate $\Sigma$ in order to assess variability in $\bar{\bar{Y}}$ \citep{fleg:hara:jone:2008,roy:2019,vats:rob:fle:jon:2020}.
+There is a rich literature on estimating $\Sigma$ for single-chain MCMC implementations.
+The most common are spectral variance (SV) estimators \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \citep{chen:seila:1987,vats:fleg:jon:2019}.
+Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from parallel chains.
+Batch means estimators are computationally more efficient than SV estimators, whereas SV estimators are more reliable \citep{fleg:jone:2010}.
 Here, we utilize G-ACvF estimators to construct globally-centered SV estimator (G-SVE) of $\Sigma$.
@@
 
+The locally and globally centered  estimators for $\Upsilon(k)$ are $\hat{\Upsilon}_s(k)$ and $\hat{\Upsilon}_{G,s}(k)$, respectively, where
+\[
+\hat{\Upsilon}_s(k) = \dfrac{1}{n} \ds \sum_{t=1}^{n - |k|} (Y_{st} - \bar{Y}_s)(Y_{s\,t+k} - \bar{Y}_s)^T \quad \text{ and } \quad \hat{\Upsilon}_{G,s}(k) = \dfrac{1}{n} \ds \sum_{t=1}^{n - |k|} (Y_{st} - \bar{\bar{Y}})(Y_{s\,t+k} - \bar{\bar{Y}})^T\,,
+\] 
+and let $\hat{\Upsilon}_G(k) = m^{-1} \sum_{k=1}^{m}\hat{\Upsilon}_{G,s}(k)$.
 SV estimators are constructed as weighted and truncated sums of estimated lag covariances.
-The locally and globally centered empirical estimators for $\Upsilon(k)$, $\hat{\Upsilon}_s(k)$ and $\hat{\Upsilon}_{G,s}(k)$, can be defined in a similar way as $\hat{\Gamma}_s$ and $\hat{\Gamma}_{G,s}$ in Equation~\ref{eq:empirical_ACvF},\ref{eq:G-ACvF} for the Markov chain $\{Y_{st}\}_{t \geq 1}$ for all $s$.
-Let $w: \mathbb{R} \to [-c,c]$ be a lag window function and $b_n \in \mathbb{N}$ be a truncation point.
-The SV estimator of $\Sigma$ from a single chain is
-%
-
+For some $c \geq 1$, let $w: \mathbb{R} \to [-c,c]$ be a lag window function and $b_n \in \mathbb{N}$ be a bandwidth.
+The SV estimator of $\Sigma$ for chain $s$ is
+%
+%
 \begin{equation} \label{eq:sve}
-    \hat{\Sigma}_{s} = \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_s(k)
+    \hat{\Sigma}_{s} = \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_s(k)\,.
 \end{equation}
-
-An overall estimate of $\Sigma$ from all $m$ chains is the average SV estimator (ASV):
+Large-sample properties of $\hat{\Sigma}_s$ have been studied widely.
+\cite{vats:fleg:jon:2018} provided conditions for strong consistency while \cite{fleg:jone:2010,vats:flegal:2018} provided large-sample bias and variance results.
+These results also extend naturally to an average SV (ASV) estimator
 \[
@@
 \]
+
 %  We propose a globally-centered spectral variance estimator (G-SVE) wherein we use G-ACF to estimate the autocovariance.
@@
 
-% Recall from Equation \ref{eq:empirical_ACvF} that $\hat{\Gamma}(k)$ is the empirical autocovariance function given by
-
-% \begin{equation}
-%     \hat{\Gamma}(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}}(X_t - \bar{X})(X_{t + \abs{k}} - \bar{X})^T
-% \end{equation}
-
-We define the globally-centered SV estimator as the weighted and truncated sum of G-ACvFs
-%
-% Consider $m$ Markov chains where $\hat{\Gamma}_s(k)$, $\hat{\Gamma}_{G,s}(k)$ and $\hat{\Sigma}_{S, s}$ are the lag-$k$ empirical ACF, G-ACF, and SVE respectively for $s^{th}$ Markov chain, $s\in {1,...,m}$.
-% Consider the globally-centered SV estimator (G-SVE) for the $s$th chain using G-ACF:
-%
-\begin{align*}
-    \hat{\Sigma}_{G} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_{G}(k)\,.
-\end{align*}
-% and the combined G-SVE is
-% \[
-% \hat{\Sigma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{G,s}\,.
-% \]
-For $\hat{\Sigma}_{G}$ to accurately estimate $\Sigma$, conditions need to be imposed on the weight function, $w$. 
+We define the G-SV estimator as the weighted and truncated sum of G-ACvFs
+%
+\begin{align*}
+    \hat{\Sigma}_{G} &= \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_{G}(k)\,.
+\end{align*}
+%
+To accurately estimate $\Sigma$, standard conditions are imposed on the lag window, $w$. 
 %
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is a continuous at $0$ and at all but finite number of points.
-It is bounded and even function with $w(0)=1, \; \abs{w(x)} < c$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W = \sum_{k = -\infty}^{\infty} w(k/b_n)$ is finite.
+The lag window $w(x)$ is continuous at $0$ at all but finite number of points.
+Further, $w(x)$ is a bounded and even function with $w(0)=1, \; {\color{red}\abs{w(x)} < c}$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W = \sum_{k = -\infty}^{\infty} w(k/b_n)$ is finite.
 \end{ass}
 % We will consider a range of lag windows $w(x)$; where $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$. 
-Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows. We will use the popular Bartlett lag window in our simulations. The function $w(.)$ is given by
+Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows. We will use the following popular Bartlett lag window in our simulations:
 \[
 w(x) = \begin{cases}
-\left(1 - \abs{x}\right) & \textrm{for } \abs{x} \leq 1 \\
+1 - \abs{x} & \textrm{for } \abs{x} \leq 1 \\
 0 & \textrm{otherwise}\,.
@@
 
-In relation to lag window, we are interested in $w(k/b_n)$ for lag-$k$.
-Therefore, zero weightage is given to autocovariances for lag greater than the truncation point $b_n$.
+% In relation to lag window, we are interested in $w(k/b_n)$ for lag-$k$.
+Therefore, zero weightage is given to autocovariances for lag greater than the bandwidth $b_n$.
 This is true for Bartlett but not true for the quadratic spectral lag window in \cite{andr:1991} for example.
@@
 First, we provide conditions for strong consistency.
-Strong consistency is particularly important to demonstrate for MCMC as it is required to ensure sequential stopping rules yield correct coverage at termination \citep{glyn:whit:1992}.
-A critical assumption is that of a strong invariance principle below.
+Strong consistency is particularly important to ensure sequential stopping rules yield correct coverage at termination \citep{glyn:whit:1992}.
+A critical assumption is that of a strong invariance principle which the following theorem establishes.
 Let $B(n)$ denotes a standard $p$-dimensional Brownian motion.
@@
  Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q = 1$.
-If $\hat{\Sigma}_{SV,s} \xrightarrow{a.s.} \Sigma$ for all $s$, and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \to \Sigma$ with probability 1, as $n \to \infty$.
+If $\hat{\Sigma}_{s} \xrightarrow{a.s.} \Sigma$ for all $s$, and $n^{-1}{b_n \log \log n} \to 0 \textrm{ as } n \to \infty$, then $\hat{\Sigma}_{G} \overset{a.s.}{\to} \Sigma$ as $n \to \infty$.
 \end{theorem}
 
-% \begin{proof}
-% We complete the proof by showing that $\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$.
-We will show that
-
+Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}.
+However, \cite{hannan:1970} proved the results assuming $\mu_g$ was known.
+Here, we present the results under mild conditions for when $\mu_g$ is replaced by $\bar{\bar{Y}}$.
+Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, repectively.
+
+\begin{theorem}\label{th:G-SVE_bias}
+Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that 
+\[
+\lim _{x \to 0} \dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty
+\] 
+and $b_n^q/n \to 0$ as $n \to \infty$. Then $ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.$
 % \[
-% \hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
+%  \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.
 %  \]
-% where $D$ is the finite random variable associated with SIP. We will show that
-% \begin{align*}
-%     g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
-%     g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
-%     g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]
-% \end{align*}
-
-% Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we can finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$.
-The proof is in Appendix subsection \ref{appendix:strong_consis}
-% \end{proof}
-
-% We are interested in the finding the bias for G-SVE estimator as a function of $n$. 
-%\begin{ass} \label{ass:bias}
-    % Let $\Gamma_s(k)$ be the lag-k autocovariance for $s^{th}$ Markov chain and $w(x)$ be the lag window. We assume that there exists a $q \geq 0$ such that for all $s$
-    % \begin{enumerate} [a.]
-    %     \item $\sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma_s(k)\| < \infty$ {\color{blue} DV: This assumption is satisfied by the polynomial ergodicity, so can remove it.}
-    %     \item $\lim _{x \to 0}\dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty$ 
-%        \item $\dfrac{b_n^q}{n} \to 0$ as $n \to \infty$
-%   \end{enumerate}
-
-    % If $k_q$ is finite for some $q_o$, then it is zero for $q < q_0$. $q$ is taken to be the largest number satisfying the first two conditions above.
-%\end{ass}
-
-\begin{theorem}\label{th:G-SVE_bias}
-Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that $\lim _{x \to 0}{1 - w(x)}/\abs{x}^q = k_q < \infty$ and $b_n^q/n \to 0$ as $n \to \infty$. Then
-\[
- \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.
- \]
 \end{theorem}
@@
 \begin{theorem} \label{th:G-SVE_variance}
- Let the assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E \|Y_{11}\|^4 < \infty$, then $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
+ Let the assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E \|Y_{11}\|^4 < \infty$, then $ \lim_{n \to \infty} b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx $.
 \end{theorem}
-
-% \begin{proof}
-% Recall that $\tilde{\Sigma}$ is the averaged pseudo spectral variance estimator which uses the unobserved mean.
-Further, let $\tilde{\Sigma}^{ij}$ be the $(i,j)^{th}$ element of this matrix.
-We will prove that the variance of $\hat{\Sigma}_{G} \textrm{ and } \tilde{\Sigma}$ are equivalent for large sample sizes.
-The proof is in Appendix subsection \ref{appendix:variance}
-% \end{proof}
 
@@
 The SV estimator, despite good statistical properties, poses application limitations due to slow computation.
-From equation \ref{eq:empirical_ACvF} and \ref{eq:sve}, the computation of the SV estimator has a complexity of $\mathcal{O}(n^2 p^2)$ in general, and for Bartlett (and other truncated lag windows) $\mathcal{O}(b_n n p^2)$.
-In MCMC typically, $n$ is large, for highly-correlated processes, $b
-_n$ is large, and for high-dimensional target distributions, $p$ could also be large.
-
-To overcome this limitation, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast} for our purposes.
+From \eqref{eq:empirical_ACvF} and \eqref{eq:sve}, the complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for Bartlett (and other truncated) lag window, the complexity is $\mathcal{O}(b_n n p^2)$.
+In MCMC, and especially for slow mixing Markov chains, $n$ and $b
+_n$ are large, limiting the use of SV estimators.
+
+To overcome this, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast} for our purposes.
 Suppose $w_k = w(k/b_n)$ and let $T(w)$ be the $n \times n$ Toeplitz matrix of weights with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$.
-Notice an alternate formulation of SVE for the $s^{th}$ chain $\{Y_{st};\, t \in 1, ..., n\}$ i
+Notice an alternate formulation of $\hat{\Sigma}_s$
 %

### 2020-08-19 Boomerang/acf_plots.R
All the changes for one run plots

@@ -25,6 +25,7 @@ for (i in 1:m){
   mc.chain.list[[i]] = chain
 }
 global.mean <- global.mean/m
+save(mc.chain.list, file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
 component <- 1
 lag.max <- 50
 
@@ -75,6 +76,7 @@ for (i in 1:m){
   mc.chain.list[[i]] = chain
 }
 
+save(mc.chain.list, file = "Out/_1_10_7_/boom-five_chains_1_10_7.Rdata")
 ####################################
 nsim <- 1000
 ########################################

### 2020-08-19 Boomerang/output.R

@@ -49,9 +49,10 @@ for(i in 1:floor(m/2)){
 chain <- array(0, dim = c(1e3, p, m))
 chain[,,1] <- markov.chain(A1, B1, C1, 1e3, start[1,])
 chain[,,2] <- markov.chain(A1, B1, C1, 1e3, start[2,])
+samples <- perspective(A1, B1, C1, 100)
+save(chain, samples, file = paste(paste("Out/", A1, B1, C1, "/boom-two_chains_sp", A1, B1, C1, sep = "_"), ".Rdata", sep = ""))
 
 pdf(file = paste(paste("Out/", A1, B1, C1, "/boom-2d_density_plot", A1, B1, C1, sep = "_"), ".pdf", sep = ""), height = 5, width = 5)
-samples <- perspective(A1, B1, C1, 100)
 contour2D(x=samples$x, y=samples$y, z=samples$z, colkey = FALSE, xlim=c(0,10), ylim=c(0,10))
 points(rbind(chain[,,1], chain[,,2]), cex=.2, col = c(rep("black",1e3), rep("darkorange",1e3)))
 dev.off()
@@ -72,9 +73,10 @@ for(i in 1:floor(m/2)){
 chain <- array(0, dim = c(1e3, p, m))
 chain[,,1] <- markov.chain(A2, B2, C2, 1e3, start[1,])
 chain[,,2] <- markov.chain(A2, B2, C2, 1e3, start[2,])
+samples <- perspective(A2, B2, C2, 100)
+save(chain, samples, file = paste(paste("Out/", A2, B2, C2, "/boom-two_chains_sp", A2, B2, C2, sep = "_"), ".Rdata", sep = ""))
 
 pdf(file = paste(paste("Out/", A2, B2, C2, "/boom-2d_density_plot", A2, B2, C2, sep = "_"), ".pdf", sep = ""), height = 5, width = 5)
-samples <- perspective(A2, B2, C2, 100)
 contour2D(x=samples$x, y=samples$y, z=samples$z, colkey = FALSE, xlim=c(0,10), ylim=c(0,10))
 points(rbind(chain[,,1], chain[,,2]), cex=.2, col = c(rep("black",1e3), rep("darkorange",1e3)))
 dev.off()
@@ -129,13 +131,14 @@ dev.off()
 m <- 5
[…]

### 2020-08-19 GaussianMix/output.R

@@ -38,6 +38,8 @@ sd2 <- 0.5
 
 chain1 <- mh.mcmc(start = -3, p, mu1, mu2, sd1, sd2, N, 1)
 chain2 <- mh.mcmc(start = 3, p, mu1, mu2, sd1, sd2, N, 1)
+mc.chain.list <- list(as.matrix(chain1), as.matrix(chain2))
+save(mc.chain.list, file = "gaussian-two_chains.Rdata")
 
 mean(chain1)
 mean(chain2)
@@ -93,9 +95,6 @@ dev.off()
 
 m <- 2
 lag.max <- 50
-mc.chain.list <- list(as.matrix(chain1), as.matrix(chain2))
-
-####################################
 nsim1 <- 1e4
 nsim2 <- 5e4
 ########################################
@@ -112,7 +111,7 @@ local.acf2 <- acf(y[[1]], type = "correlation", lag.max = lag.max, plot = FALSE)
 global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, graph = FALSE)[[1]]
 global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, graph = FALSE)[[1]]
 
-pdf(file = "gaussion-acf_hist.pdf", width = 10, height= 4)
+pdf(file = "gaussian-acf_hist.pdf", width = 10, height= 4)
 par(mfrow = c(1,2))
 plot(as.matrix(local.acf1$acf), type = 'h', ylab = "Autocorrelation", xlab = "Lag")
 lines(as.matrix(local.acf2$acf), type = 'l', col = "steelblue1", lwd = 2)

### 2020-08-19 MagnoliaNetwork/acf_plots.R

@@ -17,17 +17,18 @@ igraph::assortativity_degree(gmagnolia)
 
 
 #m chains length 1e5
-  set.seed(1)
-  m <- 2
-  start <- c(386, 244)
-  markovChains = magnolia.mhrw.func(nrep = 1e3, chains = m, start = start)
-  mc.chain.list <- list()
-  for(i in 1:m){
-    mc.chain.list[[i]] <- MHRWestimation(markovChains[[i]])
-    mc.chain.list[[i]] = mc.chain.list[[i]][,c(1,7,5,8,9)]
-  }
+set.seed(1)
+m <- 2
+start <- c(386, 244)
+markovChains = magnolia.mhrw.func(nrep = 1e3, chains = m, start = start)
+mc.chain.list <- list()
+for(i in 1:m){
+  mc.chain.list[[i]] <- MHRWestimation(markovChains[[i]])
+  mc.chain.list[[i]] = mc.chain.list[[i]][,c(1,7,5,8,9)]
+}
 
-  component = 3
+save(mc.chain.list, file = "Out/magnolia-two_chains.Rdata")
+component = 3
 
 ########################################
 ncrop <- 1e2

### 2020-08-19 PoissonChange/acf_plots.R

@@ -53,7 +53,13 @@ globalACF(x, chains=0, component = component, mean = "local", type = "correlatio
 globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
 dev.off()
 
-n <- 1e5
+#########################################
+#########################################
+########### Trace plots #################
+#########################################
+#########################################
+
+n <- 5e4
 pdf(file = paste("Out/poisson-trace_n", n, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
 plot.ts(mc.chain.list[[1]][1:n,2], col = "steelblue1", xlab = "Time", ylab = "Component-2", main = "")

### 2020-08-19 SensorNetwork/output.R

@@ -49,10 +49,6 @@ start <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
 aux <- rbind(runif(n=8, min=-0.3, max=0), runif(n=8, min=0.7, max=1))
 j.scale <- rep(1,.08, 4)
 
-check.pts <- c(5e3, 1e4, 5e4, 1e5)
-r <- length(check.pts)
-freq <- 1e2
-c.prob <- .95
 min <- 500
 max <- 2e5
 step <- 500
@@ -81,8 +77,8 @@ r <- colMeans(r)
 pdf(file = paste("Out/sensor-frob.pdf", sep = ""), height = 5, width = 5)
 plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "Log of Frobenium norm", ylim = range(c(a, r, r + se.r, a - se.a)), lwd = 2)
 lines(conv.pts, r, col="royalblue", lwd = 2)
-segments(x0 = conv.pts[ind], y0 = (a - se.a)[ind], y1 = (a + se.a)[ind], col = adjustcolor("darkorange", alpha.f = .50))
-segments(x0 = conv.pts[ind], y0 = (r - se.r)[ind], y1 = (r + se.r)[ind], col = adjustcolor("royalblue", alpha.f = .50))
+segments(x0 = conv.pts, y0 = (a - se.a), y1 = (a + se.a), col = adjustcolor("darkorange", alpha.f = .50))
+segments(x0 = conv.pts, y0 = (r - se.r), y1 = (r + se.r), col = adjustcolor("royalblue", alpha.f = .50))
 legend("bottomright", legend=c("A-SVE", "G-SVE"),col=c("darkorange", "royalblue"), lty=1, lwd = 2)
 dev.off()
 

### 2020-08-19 VAR-1/acf_plots.R

@@ -50,10 +50,10 @@ for (i in 1:m){
   print(colMeans(chain))
 }
 global.mean <- global.mean/m
-save(mc.chain.list, file = "Out/five_chains.Rdata")
+save(mc.chain.list, true.acf, file = "Out/var-five_chains.Rdata")
 #################################################################################
 
-load(file = "Out/five_chains.Rdata")
+load(file = "Out/var-five_chains.Rdata")
 #######################################################
 ############### ACF and G-ACF #########################
 #######################################################

### 2020-08-19 VAR-1/output.R

@@ -40,7 +40,7 @@ min <- 5e2
 max <- 5e4
 step <- 500
 conv.pts <- seq(min, max, step)
-
+save(target, truth, file = "Out/var-truth.Rdata")
 ###########################################################
 ############## log Frobenius norm running plots ###########
 ###########################################################

### 2020-08-19 one_run.R

@@ -1,0 +1,654 @@
+library(rep.acf.ccf)
+
+##########################################
+##########################################
+####### Ex1: Gaussian Mixtures ###########
+##########################################
+##########################################
+
+log.density <- function(x, p, mu1, mu2, sd1, sd2){
+  return(log(p*dnorm(x, mean = mu1, sd = sd1) + (1-p)*dnorm(x, mean = mu2, sd= sd2)))
+}
+
+m <- 2
+p <- 0.7
+mu1 <- -5
+mu2 <- 5
+sd1 <- 1
+sd2 <- 0.5
+
+load(file = "AllOut/gaussian-two_chains.Rdata")
+chain1 <- mc.chain.list[[1]]
+chain2 <- mc.chain.list[[2]]
+
+################### Figure 1 #######################
+
+## Figure 1a
+
+x <- seq(-10, 10, length = 1e3)
+pdf(file = "AllOut/gaussian-TargetTrace_n1e4.pdf", height = 5, width = 6)
+plot(x, 20000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-10000,6000), xlim = range(chain1,chain2), yaxt = 'n')
+par(new = TRUE)
+plot(x = chain1[1:1e4], y = seq(-1, -1e4, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e4, 6e3), , xlim = range(chain1,chain2), yaxt = 'n')
+lines(x = chain2[1:1e4], y = seq(-1, -1e4, -1), col = "plum3")
+mtext(side = 2, text = "Time", line = 1)
+legend("topleft", legend=c("Target", "Chain-1", "Chain-2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=0.7, lwd=2)
+dev.off()
+
+#Figure 1b
+pdf(file = "AllOut/gaussian-TargetTrace_n1e5.pdf", height = 5, width = 6)
+plot(x, 200000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-1e5,6e4), xlim = range(chain1,chain2), yaxt = 'n')
+par(new = TRUE)
[…]

### 2020-08-19 one_run.R
One teeny-tiny edit

@@ -187,10 +187,10 @@ legend("topright", legend=c("A-SVE", "G-SVE", "Truth"),col=c("darkorange", "roya
 dev.off()
 
 ################# Table 1 ######################
-
-load(file = paste("AllOut/var-out_check.pts_freq", freq, ".Rdata", sep = ""))
 check.pts <- c(5e2, 1e3, 5e3, 1e4, 5e4, 1e5)
 freq <- 1e3
+
+load(file = paste("AllOut/var-out_check.pts_freq", freq, ".Rdata", sep = ""))
 
 for (j in 1:length(check.pts)){
   
@@ -652,3 +652,4 @@ dev.off()
 
 
 ################# The End ########################
+

### 2020-08-19 Paper/main.tex
Down to 35 pages!

@@
 % \usepackage[utf8]{inputenc}
-\usepackage[left=1.2in,top=.8in,right=1.2in,nohead,bottom=.5in]{geometry}
+
 % This is a package to accept utf8 input.  I normally do not use it in my documents, but it was here by default in Overleaf.
@@
 We make two points here: first, for small sample size, we observe that the locally-centered ACF gives misleading estimates whereas G-ACF accounts for the discrepancy in sample means between two chains.
-This is evident from the ACF plots  in Figure~\ref{subfig:gauss-acf}.
+This is evident from the ACF plots  in Figure~\ref{fig:gaussian-acf}.
 Second, for a large sample size, the estimates from G-ACrF as well as ACrF are equivalent.
@@
 \begin{figure}[htbp]
-    \begin{subfigure}{.5\textwidth}
 \centering
-   \includegraphics[width=\linewidth]{plots/gaussian-Targettrace_n1e4.pdf}
-   \caption{$n = 10^4$}
-   \label{subfig:gauss-trace_1e4}
- \end{subfigure}
- \begin{subfigure}{0.5\textwidth}
-   \centering
-   \includegraphics[width=\linewidth]{plots/gaussian-Targettrace_n1e5.pdf} 
-   \caption{$n = 10^5$}
-   \label{subfig:gauss-trace_1e5}
- \end{subfigure}
-    \caption{Target density and trace plots for two chains starting at different values.}
+   \includegraphics[width=.35\linewidth]{plots/gaussian-Targettrace_n1e4.pdf}
+    \includegraphics[width=.35\linewidth]{plots/gaussian-Targettrace_n1e5.pdf} 
+    \caption{Target density and trace plots for two chains at $n = 10^4$ (left) and $n = 10^5$ (right)}
     \label{fig:gaussian-trace}
@@
 \centering
-\begin{subfigure}{.9\textwidth}
-   \centering
-   \includegraphics[width=.9\textwidth]{plots/gaussian-acf_hist.pdf}
-   \caption{$n-10^4$ (histogram) and $n = 5 \times 10^5$ (blue line)}
-   \label{subfig:gauss-acf_1e4_1e5}
-\end{subfigure}
-\begin{subfigure}{.9\textwidth}
-   \centering
-   \includegraphics[width=.9\textwidth]{plots/gaussian-acf_1e4.pdf} 
-   \caption{$n = 10^4$}
-   \label{subfig:gauss-acf_1e4}
-\end{subfigure}
-\caption{ACF plots for locally-centered ACF (left) and globally centered ACF (right).
-(a) The histogram plots the estimates for $n = 10^4$ and the blue line plot the estimates for $n = 5 \times 10^4$ for chain-1.
-(b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
+\includegraphics[width=.6\textwidth]{plots/gaussian-acf_hist.pdf} \\
+% \includegraphics[width=.6\textwidth]{plots/gaussian-acf_1e4.pdf}
+
+\caption{ACF plots using locally-centering (left) and global centering (right). Histogram estimates at $n = 10^4$ with the blue line plot being estimates from $n = 50000$ for chain 1.}
+ % (b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
 \label{fig:gaussian-acf}
@@
 The Markov chain is geometrically ergodic when the spectral norm of $\Phi$ is less than 1 (\cite{10.2307/1427459}).
-The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is known in closed form.\\
+The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is known in closed form.
 
@@
 As a result, it takes a long time for the Markov chain to explore the sample space significantly.
-\\
 
 \begin{figure}[h]
- \begin{subfigure}[h]{\textwidth}
 \centering
-   \includegraphics[width=.7\linewidth]{plots/var-acf_n1000.pdf}
-   \caption{$n = 10^3$}
-   \label{subfig:var-acf_n1e3}
-\end{subfigure}\\
-\begin{subfigure}[h]{\textwidth}
-  \centering
-  \includegraphics[width=.7\linewidth]{plots/var-acf_n10000.pdf} 
-  \caption{$n = 10^4$}
-  \label{subfig:var-acf_n1e4}
-\end{subfigure}
-
+   \includegraphics[width=.5\linewidth]{plots/var-acf_n1000.pdf}
+     \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
 \caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m=5$. (a): $n = 10^3$, not converged yet; (b): $n =  10^4$, converged. The red line marks the true ACF.}
@@
 Therefore, both the estimators provide equivalent results.
-Note that G-ACF reveals the true nature of ACF for almost ten times lesser chain length $n$.\\
+Note that G-ACF reveals the true nature of ACF for almost ten times lesser chain length $n$
 
@@
     \centering
-    \begin{subfigure}{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/var-frob.pdf}
-      \caption{$log(\|\hat{\Sigma}\|_F)$}
-      \label{subfig:var-frob}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/var-ess.pdf}
-      \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
-      \label{subfig:var-ess}
-    \end{subfigure}
+      \includegraphics[width = 2.2in]{plots/var-frob.pdf} 
+      \includegraphics[width = 2.2in]{plots/var-ess.pdf}         
+    % \begin{subfigure}{0.4\textwidth}
+    %   \centering
+
+    %   \caption{$log(\|\hat{\Sigma}\|_F)$}
+    %   \label{subfig:var-frob}
+    % \end{subfigure}
+    % \begin{subfigure}{0.4\textwidth}
+    %   \centering
+
+    %   \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
+    %   \label{subfig:var-ess}
+    % \end{subfigure}
     \caption{VAR(1).
@@
     \centering
-    \begin{tabular}{|c|c|c|}
+    \begin{tabular}{|c|ccccc|}
     \hline
-    n & A-SVE & G-SVE\\
-    \hline
-    1000 & 0.71 & 0.956\\
-    5000 & 0.843 & 0.937\\
-    10,000 & 0.885 & 0.924\\
-    50,000 & 0.928 & 0.945\\
-    100,000 & 0.944 & 0.952\\
-    \hline
+$n$  &  1000  & 5000  & 10000  & 50000  & 100000 \\  \hline
+A-SV  &    0.710 & 0.843 & .885 & .928 & .944 \\ 
+G-SV  &    0.956 & 0.937 & .924 & .945 & .952 \\ \hline
     \end{tabular}
-    \caption{VAR(1). Coverage probabilities for a $95$ percent confidence interval of global mean constructed using A-SVE and G-SVE as variance estimates around the known mean.}
+    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SVE and G-SVE.}
     \label{tab:var-coverage}
@@
     \centering
-    \begin{subfigure}[h]{.45\textwidth}
-        \centering
-        \includegraphics[width = \textwidth]{plots/boom-2d_density_plot_1_3_8.pdf}
-        \caption{Setting-1}
-        \label{subfig:boom-2D_1_3_8}
-    \end{subfigure}
-    \begin{subfigure}[h]{.45\textwidth}
-        \centering
-        \includegraphics[width = \textwidth]{plots/boom-2d_density_plot_1_10_7.pdf}
-        \caption{Setting-2}
-        \label{subfig:boom-2D_1_10_7}
-    \end{subfigure}
-    \caption{Boomerang. Contour plots of the target distribution for both settings. Overlayed scatter plot for two chains (in different colors) starting near each mode.}
+    \includegraphics[width = .8\textwidth]{plots/boom-all_1_3_8.pdf}\\
+    \includegraphics[width = .8\textwidth]{plots/boom-all_1_10_7.pdf}    
+    % \includegraphics[width = 0.6\textwidth ]{plots/boom-acf_1_10_7_n1000.pdf}
+
+    \caption{Boomerang. Contour plots of the target distributions  overlayed with scatter plots for two chains for Setting 1 (left) and Setting 2 (right).}
    \label{fig:boom-2D}
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = .9\textwidth]{plots/boom-acf_1_3_8.pdf}
-    \caption{Boomerang (setting-I). A-ACF (left) and G-ACF (right) of component-1 for $n=1000$ (histogram) and $n=10000$ (blue line) }
-    \label{fig:boom-acf_1_3_8}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = 0.9\textwidth ]{plots/boom-acf_1_10_7_n1000.pdf}
-    \caption{Boomerang. A-ACF (left) and G-ACF (right) of component-1 for $n=1000$}
-    \label{fig:boom-acf_1_10_7}
-\end{figure}
-
  In Figure \ref{fig:boom-acf_1_3_8}, the autocorrelations are severely underestimated by A-ACF for $n=1000$ because the chains have not jumped modes.
@@
     \centering
-
-    \begin{subfigure}[h]{.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-ess_1_3_8_m5.pdf}
-      \caption{Setting-1}
-      \label{subfig:boom-ess1}
-    \end{subfigure} \hspace{1cm}
-    \begin{subfigure}[h]{.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-ess_1_10_7_m5.pdf}
-      \caption{Setting-2}
-      \label{subfig:boom-ess2}
-    \end{subfigure}
-    \caption{Boomerang. Running plot for $\log \hat{\text{ESS}}_A/mn$ and $\log \hat{\text{ESS}}_G/mn$ for $m = 5$.}
+      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
+      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_10_7_m5.pdf}
+
+    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
     \label{fig:boom-ess}
@@
     \centering
-
-    \begin{subfigure}[h]{.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-frob_1_3_8_m5.pdf}
-      \caption{Setting-1}
-      \label{subfig:boom-frob1}
-    \end{subfigure} \hspace{1cm}
-    \begin{subfigure}[h]{.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/boom-frob_1_10_7_m5.pdf}
-      \caption{Setting-2}
-      \label{subfig:boom-frob2}
-    \end{subfigure}
-    \caption{Boomerang. Running plot for $\log \|\hat{\Sigma}_A\|_F$ and $\log \|\hat{\Sigma}_G\|_F$ for $m = 5$.}
+    \includegraphics[width = .30\textwidth]{plots/boom-frob_1_3_8_m5.pdf}  
+    \includegraphics[width = .30\textwidth]{plots/boom-frob_1_10_7_m5.pdf}
+
+    \caption{Boom: Running plot of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log (\|\hat{\Sigma}_G\|_F)$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
     \label{fig:boom-frob}
@@
  \hline
- & A-SVE & G-SVE & A-SVE & G-SVE \\
+ & A-SV & G-SV & A-SV & G-SV \\
  \hline
- 5000 & 0.595 &  0.7 & 0.402 &  0.64\\
+ 5000 & 0.595 &  0.700 & 0.402 &  0.640\\
  10000 & 0.563 &  0.665 & 0.59 &  0.739\\
@@
  \hline
- & A-SVE & G-SVE & A-SVE & G-SVE \\
+ & A-SV & G-SV & A-SV & G-SV \\
  \hline
- 1000 &  0.856 &  0.868 & 0.895 &  0.9100\\
- 5000 & 0.921 &  0.925 & 0.91 &  0.915\\
+ 1000 &  0.856 &  0.868 & 0.895 &  0.910\\
+ 5000 & 0.921 &  0.925 & 0.910 &  0.915\\
  10000 & 0.928 &  0.93 & 0.919 &  0.926\\
@@
     \centering
-    \includegraphics[width = .9\textwidth]{sensor-trace_loc1.pdf}
-    \caption{Sensor Network. Trace plot of two chains for x (left) and y (right) coordinate of sensor location-1.}
+    \includegraphics[width = .6\textwidth]{plots/sensor-trace_loc1.pdf}
+    \caption{Sensor: Trace plots for $x$ (left) and $y$ (right) coordinate of sensor location-1.}
     \label{fig:sensor-trace}
@@
 The total simulation size for each chain is fixed at $100,000$.
-Since the truth about actual mean and asymptotic variance is not known in this case, we are not interested in coverage probabilities.\\
+Since the truth about actual mean and asymptotic variance is not known in this case, we are not interested in coverage probabilities.
 
@@
 Observe that each chain explores one particular mode for a long time before jumping to another mode.
-\\
 
@@
     \centering
-    \begin{subfigure}[h]{.45\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/sensor-acf_n5e3.pdf}
-      \caption{$n = 5 \times 10^3$}
-      \label{subfig:sensor-acf_5e3}
-    \end{subfigure}
-    \begin{subfigure}[h]{.45\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/sensor-acf_n5e4.pdf}
-      \caption{$n = 5 \times 10^4$}
-      \label{subfig:sensor-acf_5e4}
-    \end{subfigure}
-    \caption{Sensor Network. ACrF (orange) and G-ACrF (blue) for individual chains (dotted lines) and average over all chains (thick solid line).}
+      \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e3.pdf}\includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e4.pdf}
+
+    \caption{Sensor: ACF (orange) and G-ACF (blue) for individual chains (dotted lines) and average over all chains (solid line) for $n = 5000$ (left) and $n = 50000$ (right).}
     \label{fig:sensor-acf}
@@
     \centering
-    \begin{subfigure}[h]{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/sensor-frob.pdf}
-      \caption{log Frobenius norm}
-      \label{subfig:sensor-frob}
-    \end{subfigure}
-    \begin{subfigure}[h]{0.4\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/sensor-ess.pdf}
-      \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
-      \label{subfig:sensor-ess}
-    \end{subfigure}
-    \caption{Sensor Network. Running plot for $\log \|{\Sigma}\|_F$ (left) and $\log {\textrm{ESS}}/mn$ (right) estimated using A-SVE and G-SVE along with standard errors for 10 replications.}
+      \includegraphics[width = .30\textwidth]{plots/sensor-frob.pdf} 
+      \includegraphics[width = .30\textwidth]{plots/sensor-ess.pdf}
+
+    \caption{Sensor: Running plot of $\log (\|{\Sigma}\|_F)$ (left) and $\log ({\textrm{ESS}})/mn$ (right) estimated using A-SV and G-SV along with standard errors for 10 replications.}
     \label{fig:sensor-frob_n_ess}
@@
     \lambda_i &\sim \text{Gamma}(c_o, d_o), \qquad i = 1,..., k\\
-    p_{ii} &\sim \text{Beta}(\alpha, \beta), \qquad i = 1,..., k
-\end{align*}
-
-% The results of model comparison by \cite{martin2011mcmcpack} showed that the ratio of maximum likelihood for six change-point model is favored over the alternatives.
-We will use this information and present the ACF results for a six change-points model only.
-We will use the hyperparameters values $c_o = 13 \textrm{ and } d_o = 1$ because the mean of MID is around 13.
-\\
+    p_{ii} &\sim \text{Beta}(\alpha, \beta), \qquad i = 1,..., k\,.
+\end{align*}
 
@@
     \centering
-    \includegraphics[width = 0.9\textwidth]{plots/poisson-trace_n1e+05.pdf}
+    \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
     \caption{Trace plot for second (left) and third (right) component of two chains started from random points.The two colors denote the two different chains.}
@@
 We will report the ACF plots for component-2.
-Similar behavior is observed for ACF plots of other components as well.\\
+Similar behavior is observed for ACF plots of other components as well
 
@@
     \centering
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/poisson-acf_n1000.pdf}
-      \caption{$n = 1000$}
-      \label{subfig:poisson-acf_n1e3}
-    \end{subfigure}
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/poisson-acf_n10000.pdf}
-      \caption{$n = 10000$}
-      \label{subfig:poisson-acf_n1e4}
-    \end{subfigure}
-    \caption{Poisson change point. ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for two chain lengths.}
+      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n1000.pdf}    
+      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
+    \caption{Change point: ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for $n = 1000$ (left) and $n = 10000$ (right).}
     \label{fig:poisson-acf}
@@
 We use a Metropolis-Hastings algorithm with a simple random-walk  proposal suggested by \cite{gjoka2011practical}.
-Each node is associated with five features namely - degree of connection, cluster coefficient, grade, binary sex indicator (1 for female, 0 for male), and binary race indicator (1 for white, 0 for others).\\
+Each node is associated with five features namely - degree of connection, cluster coefficient, grade, binary sex indicator (1 for female, 0 for male), and binary race indicator (1 for white, 0 for others)
 
@@
     \centering
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/magnolia-acf_n100.pdf}
-      \caption{$n = 100$}
-      \label{subfig:magnolia-acf_n1e3}
-    \end{subfigure}
-    \begin{subfigure}[h]{.8\textwidth}
-      \centering
-      \includegraphics[width = \textwidth]{plots/magnolia-acf_n1000.pdf}
-      \caption{$n = 1000$}
-      \label{subfig:magnolia-acf_n1e4}
-    \end{subfigure}
-    \caption{Network crawling. ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for two chain lengths.}
+      \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n100.pdf}
+      \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n1000.pdf}
+
+    \caption{Crawling: ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for $n = 1000$ (left) and $n = 10000$ (right).}
     \label{fig:magnolia-acf}

### 2020-08-19 one_run.R

@@ -27,22 +27,22 @@ chain2 <- mc.chain.list[[2]]
 
 x <- seq(-10, 10, length = 1e3)
 pdf(file = "AllOut/gaussian-TargetTrace_n1e4.pdf", height = 5, width = 6)
-plot(x, 20000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-10000,6000), xlim = range(chain1,chain2), yaxt = 'n')
+plot(x, 20000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd = 1.5, xlab = "x", ylab = "", ylim = c(-10000,6000), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
 plot(x = chain1[1:1e4], y = seq(-1, -1e4, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e4, 6e3), , xlim = range(chain1,chain2), yaxt = 'n')
 lines(x = chain2[1:1e4], y = seq(-1, -1e4, -1), col = "plum3")
 mtext(side = 2, text = "Time", line = 1)
-legend("topleft", legend=c("Target", "Chain-1", "Chain-2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=0.7, lwd=2)
+legend("top", legend=c("Target", "Chain 1", "Chain 2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=1, lwd=2, bty = "n")
 dev.off()
 
 #Figure 1b
 pdf(file = "AllOut/gaussian-TargetTrace_n1e5.pdf", height = 5, width = 6)
-plot(x, 200000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2, xlab = "x", ylab = "", ylim = c(-1e5,6e4), xlim = range(chain1,chain2), yaxt = 'n')
+plot(x, 200000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd = 1.5, xlab = "x", ylab = "", ylim = c(-1e5,6e4), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
 plot(x = chain1, y = seq(-1, -1e5, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e5, 6e4), , xlim = range(chain1,chain2), yaxt = 'n')
[…]

### 2020-08-19 Paper/main.tex
End of the day. End at 34 pages. Haven't started examples yet.

@@
   Medha Agarwal \\
-  Department of Mathematics and Statistics\\
+  Dept. of Mathematics and Statistics\\
   IIT Kanpur\\
@@
  Dootika Vats \\
-  Department of Mathematics and Statistics\\
+  Dept.of Mathematics and Statistics\\
   IIT Kanpur\\
@@
 
-The SV estimator, despite good statistical properties, poses application limitations due to slow computation.
-From \eqref{eq:empirical_ACvF} and \eqref{eq:sve}, the complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for Bartlett (and other truncated) lag window, the complexity is $\mathcal{O}(b_n n p^2)$.
-In MCMC, and especially for slow mixing Markov chains, $n$ and $b
-_n$ are large, limiting the use of SV estimators.
-
-To overcome this, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast} for our purposes.
-Suppose $w_k = w(k/b_n)$ and let $T(w)$ be the $n \times n$ Toeplitz matrix of weights with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$.
+The SV estimator, despite good statistical properties, poses limitations due to slow computation.
+From \eqref{eq:empirical_ACvF} and \eqref{eq:sve}, the complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for the Bartlett lag window, it is $\mathcal{O}(b_n n p^2)$.
+For slow mixing Markov chains, $n$ and $b_n$ are large, limiting the use of SV estimators.
+To overcome this, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast}.
+Suppose $w_k = w(k/b_n)$ and let $T(w)$ be the $n \times n$ Toeplitz matrix with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$.
 Notice an alternate formulation of $\hat{\Sigma}_s$
@@
 \end{equation}
-
-For computational efficiency, \cite{heberle2017fast} computed $T(w)A_s$ directly using an FFT based algorithm.
-The algorithm requires embedding $T(w)$ in a $2n \times 2n$ circulation matrix $C(w^*)$.
-We write the spectral decomposition of $C(w^*)$ as $V\Lambda V^*$ where the eigenvalues of $C(w^*)$ are given by the DFT of the first column of $C(w^*)$.
-$A_s$ is extrapolated into a $2n \times p$ matrix $A_s^*$ by appending $n$ rows of $0$ vector to write Equation~\ref{eq:kyriakoulis} in the following form
-\[
-    \hat{\Sigma}_s = \dfrac{1}{n} A_s^T T(w) A_s = \dfrac{1}{n} A_s^T (C(w^*) A_s^*)_{1:n, :} = \dfrac{1}{n} A_s^T (V \Lambda V^* A_s^*)_{1:n, :}).
-\]
-Here $M_{1:r, \, 1:c}$ denotes the matrix truncation up to first $r$ rows and $c$ columns.
-For our purpose, we center the chain $\{Y_{st}; \; t \in \mathbb{Z}\}$ around $\bar{\bar{Y}}$ instead of $\bar{Y}_s$ in Equation \ref{eq:kyriakoulis} for all $s \in \{1, ..., m\}$.
-Herberle's algorithm is then applied on the formulation
-
-\[
-\hat{\Sigma}_{G,s} = \dfrac{1}{n}B_s^T T(w) B_s \qquad \textrm{ where } B_s = 
-\begin{pmatrix}
-    Y_{s1} - \bar{\bar{Y}} \; \dots \; Y_{sn} - \bar{\bar{Y}}\end{pmatrix}^T.
-\]
-The complete algorithm leads to a tremendous reduction in time and storage requirements with a computational complexity of $\mathcal{O}(p n \log n)$.
-$B_s^*$ is constructed from $B_s$ in the similar way as $A_s^*$.
-In Algorithm~\ref{algo:herberle}, we use $v^{(i)}$ to denote the $i^{th}$ element of vector $v$ and $M_{(j)}$ to denote the $j^{th}$ column of matrix $M$.
-The algorithm is the following.
+ \cite{heberle2017fast} compute the $n \times 1$ vector $T(w)A_s$  using an algorithm based on fast Fourier transforms.
+Let $w^* = (1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1}, ~0, ~w_{n-1}, \dots, w_1)^T$ and set $C(w^*)$ to be a symmetric circulant matrix such that $C(w^*)_{1:n, 1:n} = T(w)$.
+With inputs $C(w^*)$ and $A_s$, Algorithm~\ref{algo:herberle} produces $\hat{\Sigma}_s$ exactly.
+For more details, see \cite{heberle2017fast}.
+ % Let $C(w^*) = V\Lambda V^*$ be the spectral decomposition of $C(w^*)$, then $\Lambda$ is determined by a discrete Fourier transform of the first column of $C(w^*)$. 
+% $A_s$ is extrapolated into a $2n \times p$ matrix $A_s^*$ by appending $n$ rows of $0$ vector to write Equation~\ref{eq:kyriakoulis} in the following form
+% \[
+%     \hat{\Sigma}_s = \dfrac{1}{n} A_s^T T(w) A_s = \dfrac{1}{n} A_s^T (C(w^*) A_s^*)_{1:n, :} = \dfrac{1}{n} A_s^T (V \Lambda V^* A_s^*)_{1:n, :}).
+% \]
+% Here $M_{1:r, \, 1:c}$ denotes the matrix truncation up to first $r$ rows and $c$ columns.
 
 \begin{algorithm}[htbp] 
+\KwIn{$C(w^*)$ and $A_s$}
 \DontPrintSemicolon
 \SetAlgoLined
-Construct $C(w^*) \textrm{ and } B_s^*$ from $\{Y_{st};\, t = 1, ...,\, n\}$.\\ 
-Compute $\Lambda$ by DFT of $C(w^*)_{(1)}$\;
-\For{$j = 1, 2, ..., p$}    
+% Construct $C(w^*) \textrm{ and } B_s^*$ from $\{Y_{st};\, t = 1, ...,\, n\}$.\\ 
+Compute eigenvalues $\lambda_i$ of  $C(w^*)_{(1)}$ using a discrete Fourier transform, $i = 1, \dots, 2n$\;
+Construct $2n \times p$ matrix $A^*_s = (A^T  \quad 0_{n \times q})^T$\;
+
+\For{$j = 1, 2, \dots, p$}    
     { 
-    Calculate $V^*B_s^{*_{(j)}}$ by FFT of $B^*_{s(j)}$.\;
-    Multiply $V^* B_{s(j)}^{*^{(i)}}$ with the eigenvalue $\lambda_i$ for all $i = 1, ..., 2n$ to construct $\Lambda V^* B_{s(j)}^*$.\;
-    Calculate $C(w^*)B^*_{s(j)} = V \Lambda V^* B_{s(j)}^*$ by inverse FFT of $\Lambda V^* B_{s(j)}^*$.\;
+    Calculate $V^*A_s^{*_{(j)}}$ by DFT of $A^*_{s(j)}$.\;
+    Multiply $V^* A_{s(j)}^{*^{(i)}}$ with the eigenvalue $\lambda_i$ for all $i = 1, ..., 2n$ to construct $\Lambda V^* A_{s(j)}^*$.\;
+    Calculate $C(w^*)A^*_{s(j)} = V \Lambda V^* A_{s(j)}^*$ by inverse FFT of $\Lambda V^* A_{s(j)}^*$.\;
     }
- Select the first $n$ rows of $C(w^*)B^*_s$ to form $T(w)B_s$.\;
- Premultiply by $B_s^T$ and divide by $n$.
- \caption{Herberle's Algorithm}
+ Select the first $n$ rows of $C(w^*)A^*_s$ to form $T(w)A_s$.\;
+ Premultiply by $A_s^T$ and divide by $n$.\;
+ \KwOut{$\hat{\Sigma}_s$}
+ \caption{\cite{heberle2017fast} Algorithm}
  \label{algo:herberle}
@@
 
+% For our purpose, we center the chain $\{Y_{st}; \; t \in \mathbb{Z}\}$ around $\bar{\bar{Y}}$ instead of $\bar{Y}_s$ in Equation \ref{eq:kyriakoulis} for all $s \in \{1, ..., m\}$.
+Herberle's algorithm is then applied on the formulation
+We note a similar decomposition is possible for the G-SV estimator.
+Setting $B_s = (Y_{s1} - \bar{\bar{Y}} \; \dots \; Y_{sn} - \bar{\bar{Y}})^T$ and calling Algorithm~\ref{algo:herberle} with inputs $C(w^*)$ and $B_s$ yields $\hat{\Sigma}_{G,s}$.
+This algorithm has complexity $\mathcal{O}(p n \log n)$ and is thus orders of magnitude faster.
+Of particular importance is the fact that the bandwidth $b_n$ has close to no impact on the computation time.
 % subsubsection fast_implementation (end)
@@
 
-An important method of quantifying the simulation efforts is to simulate until a desired effective sample size (ESS) is obtained.
-The key motivation behind using ESS as a termination criteria is to stop the simulations when the variance of Monte Carlo average is small relative to the inherent variance in $g$ with respect to $F$ by a pre-specified factor.
-\cite{wilks:1932} suggests the determinant of a covariance matrix as a viable metric to understand the variance of a multivariate process and calls it \textit{generalized variance}.
-For a $p$-dimensional stationary Markov chain, let $\Lambda := \Var_F(Y_1))$.
-\cite{vats2019multivariate} use the ratio of generalized variances to give the following formulation for multivariate ESS (m-ESS):
-
-\[
-\textrm{ESS} = n \left(\dfrac{\abs{\Lambda}}{\abs{\Sigma}}\right)^{1/p}\, .
-\]
-
-The simulation process is stopped once the ESS is greater than a pre-specified lower-bound $W_{p}$ which is function of dimension $p$ (see \cite{vats2019multivariate} for details).
-For a multi-modal target distribution, the single chain estimators for $\Sigma$ underestimate the true generalized variance; giving an unrealistic assurance of high ESS for a given $n$.
-
+An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to simulate until a desired effective sample size (ESS) is obtained.
+ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$.
+Let $|\cdot|$ denote determinant.
+A multiple chain version of the ESS as defined by \cite{vats2019multivariate} is
+\[
+\textrm{ESS} = mn \left(\dfrac{|\Upsilon(0)|}{|\Sigma|}\right)^{1/p}\, .
+\]
+
+The simulation terminates when the ESS is greater than a pre-specified, theoretically motivated, lower-bound $W_{p}$. 
+% For a multi-modal target distribution, the single chain estimators for $\Sigma$ underestimate the true generalized variance; giving an unrealistic assurance of high ESS for a given $n$. 
+%
 In our setting of $m$ parallel chains of $n$ samples each, define
-
-\[
-\hat{\Lambda}_{mn} = \dfrac{1}{m(n-1)}\sum_{s=1}^{m}\sum_{t=1}^{n}(Y_{st} - \bar{Y}_s)(Y_{st} - \bar{Y}_s)^T\, .
-\]
-We estimate the m-ESS by using the strongly consistent average G-SV estimator $\hat{\Sigma}_G$ for $\Sigma$ as
-
-\[
-\widehat{\textrm{ESS}}_G = mn\left(\dfrac{\abs{\hat{\Lambda}_{mn}}}{\abs{\hat{\Sigma}_{G}}}\right)^{1/p}\, .
-\]
+%
+\[
+\hat{\Lambda}_{mn} = \dfrac{1}{m(n-1)}\sum_{s=1}^{m}\sum_{t=1}^{n}(Y_{st} - \bar{Y}_s)(Y_{st} - \bar{Y}_s)^T\, ,
+\]
+and estimate ESS with
+\[
+\widehat{\textrm{ESS}}_G = mn\left(\dfrac{|\hat{\Upsilon}(0)|}{|\hat{\Sigma}_{G}|}\right)^{1/p}\, .
+\]
+We use the locally-centered $\hat{\Upsilon}(0)$ to estimate $\Upsilon(0)$ instead of $\hat{\Upsilon}_G(0)$ when calculating ESS.
+Both $\hat{\Upsilon}(0)$ and $\hat{\Upsilon}_G(0)$ are consistent  for $\Upsilon(0)$; however using $\hat{\Upsilon}(0)$ produces lower sample sizes when the parallel chains do not agree, indicating that more MCMC draws are needed.
 
 For the sake of comparison, $\widehat{\textrm{ESS}}_A$ is constructed similarly using $\hat{\Sigma}_A$ instead of $\hat{\Sigma}_G$ to estimate $\Sigma$.  
-We refrain from using the globally centered version of sample covariance matrix, i.e.
-$\hat{\Upsilon}(0)$ to estimate $\Lambda$ in both $\widehat{\textrm{ESS}}_A \textrm{ and } \widehat{\textrm{ESS}}_G $.
-This is because in practice, it is preferred to underestimate the ESS than do otherwise.
-Both $\hat{\Upsilon}(0)$ and $\hat{\Lambda}_{mn}$ converge to $\Lambda$; however $\abs{\hat{\Lambda}_{mn}}$ shall underestimate $\abs{\Lambda}$ in the beginning.
-We will compare $\widehat{\textrm{ESS}}_G$ to $\widehat{\textrm{ESS}}_A$ in the following Section.
+% We will compare $\widehat{\textrm{ESS}}_G$ to $\widehat{\textrm{ESS}}_A$ in the following Section.
 
@@
 
-In case of slowly mixing Markov chains or multimodal target distributions, the traditional single chain empirical estimator for ACvF can excruciatingly underestimate the truth.
-This will have serious impact on estimation of lag covariances, large sample variance of Monte Carlo averages, and determining when to stop the simulation process.
-It has been concluded in the paper that all of this can be significantly avoided by sampling multiple chains starting from dispersed points and pooling in the information from all chains to build consistent estimators for $\Gamma(k)$, $\Sigma$, and ESS.
+For slowly mixing Markov chains, the traditional single chain empirical estimator for ACvF can dramatically underestimate the truth.
+This has a severe impact on ACF plots, Monte Carlo variance, and stopping time of MCMC algorithms.
+We provide a globally-centered estimate of the ACvF that leads to improvements in all three aspects of MCMC output analysis.
+
+% It has been concluded in the paper that all of this can be significantly avoided by sampling multiple chains starting from dispersed points and pooling in the information from all chains to build consistent estimators for $\Gamma(k)$, $\Sigma$, and ESS.
 We have derived the bias of G-ACvF.
@@
 
-For the purpose of experimentation in Section~\ref{sec:examples}, Bartlett lag window has been used throughout.
-Lag window comparisons done by \cite{andr:1991} reveal that quadratic spectral (QS) lag window gives consistently better coverage probabilities for any confidence interval.
+In our simulations, we use the Bartlett lag window, which is convenient but not optimal.
+The untruncated quadratic spectral lag window of \cite{andr:1991} is known to be mean-squared optimal and could easily be used here to obtain $\hat{\Sigma}_G$.
+The quadratic spectral lag window is typically slow to compute, but by adapting  \citeauthor{heberle2017fast}'s algorithm, the implementation is similar to that of Bartlett's.
+
+% Lag window comparisons done by  reveal that quadratic spectral (QS) lag window gives consistently better coverage probabilities for any confidence interval.
 However, SVE gives poor coverage probability for all lag windows when the amount of autocorrelation is high in the Markov chain.

### 2020-08-19 one_run.R

@@ -66,7 +66,7 @@ global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, typ
 global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, graph = FALSE)[[1]]
 
 #### Figure 2a
-pdf(file = "AllOut/gaussian-acf_hist.pdf", width = 10, height= 4)
+pdf(file = "AllOut/gaussian-acf_hist.pdf", width = 8, height= 4)
 par(mfrow = c(1,2))
 plot(as.matrix(local.acf1$acf), type = 'h', ylab = "Autocorrelation", xlab = "Lag")
 lines(as.matrix(local.acf2$acf), type = 'l', col = "steelblue1", lwd = 2)
@@ -75,7 +75,7 @@ lines(as.matrix(global.acf2$acf), type = 'l', col = "steelblue1", lwd = 2)
 dev.off()
 
 ### Figure 2b
-pdf(file = "AllOut/gaussian-acf_1e4.pdf", width = 10, height= 4)
+pdf(file = "AllOut/gaussian-acf_1e4.pdf", width = 8, height= 4)
 par(mfrow = c(1,2))
 l <- globalACF(x, chains = 0, component = 1, lag.max = lag.max, mean = "local", type = "correlation", col = "royalblue", leg = FALSE)
 g <- globalACF(x, chains = 0, component = 1, lag.max = lag.max, mean = "global", type = "correlation", col = "darkorange", leg = FALSE)
@@ -107,7 +107,7 @@ for (i in 1:m){
 global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
 local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
 
-pdf(file = paste("AllOut/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
+pdf(file = paste("AllOut/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 8)
 par(mfrow = c(1,2))
 plot(local.acf, main = expression("Locally centered ACF"))
 lines(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red")
@@ -126,7 +126,7 @@ for (i in 1:m){
[…]

### 2020-08-20 Paper/main.tex
Only left with Sensor netwrok example now.

@@
 
-An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to simulate until a desired effective sample size (ESS) is obtained.
+An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to calculate the effective sample size (ESS).
 ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$.
@@
 
-There are only a handful of MCMC methods where the true autocovariance and asymptotic variance are known in closed form.
-To compare the globally and locally-centered estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
-We want to deliberately make the Markov chains explore the sample space slowly.
+Our first example is one where the $\Upsilon$ and $\Sigma$ are available in closed-form, so we can compare quality of estimation against a known truth.
 Consider a $p$-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
@@
 \]
-
+%
 where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{i.i.d.}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix.
-The invariant distribution for this Markov chain is $N(0, \Psi)$ where $\mathcal{N}(.,.)$ stands for the Gaussian distribution.
-The lag-k autocovariance $\Gamma(k)$ can be calculated for $k >0$ as $\Gamma(k) = \Phi^k\Psi \textrm{ and } \Gamma(-k) = \Psi(\Phi^T)^k$.
-The Markov chain is geometrically ergodic when the spectral norm of $\Phi$ is less than 1 (\cite{10.2307/1427459}).
-The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is known in closed form.
-
-Let $\phi_{\max}$ be the largest absolute eigenvalue of $\Phi$ such that $\abs{\phi_{\max}} < 1$.
-The larger it is, the slower the Markov chain mixes.
-For our case, we require a slowly mixing VAR(1) process.
-We consider a bivariate example with $\phi_{\max} = 0.999$.
-We run five parallel deterministically initialized Markov chains with their starting points evenly distributed in the sample space.
-The correlation between the two components in the target distribution is very high for the chosen value of $\Phi$ and $\Omega$.
-As a result, it takes a long time for the Markov chain to explore the sample space significantly.
-
-\begin{figure}[h]
+We fix $\Omega$ be a AR correlation matrix with parameter .9.
+The invariant distribution for this Markov chain is $N(0, \Psi)$, where $vec(\Psi) = (I_{p^2} - \Phi \times \Phi)^{-1} vec(W)$.
+We are interested in estimating the mean of the stationary distribution, so $g$ is the identity function.
+For $k > 0$, the lag-$k$ autocovariance is $\Upsilon(k) = \Gamma(k) = \Phi^k\Psi$.
+The process satisfies a CLT for $\bar{X} = n^{-1} \sum_{t=1}^{n} X_t$ if the spectral norm of $\Phi$ is less than 1 \citep{10.2307/1427459} and the limiting covariance, $\Sigma$ is known in closed form \citep{dai:jon:2017}.
+We set $p = 2$ and set $\Phi$ such that its eigenvalues are .999 and .001.
+The resulting process is slowly mixing and allows us to highlight the difference in the estimation of ACvF.We further set $m = 5$ with starting values dispersed across the state space.
+\begin{figure}[htbp]
 \centering
@@
      \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
-\caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m=5$. (a): $n = 10^3$, not converged yet; (b): $n =  10^4$, converged. The red line marks the true ACF.}
+\caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m = 5$. (Top) $n = 10^3$  and (bottom) $n =  10^4$. The red line is the true ACF.}
 \label{fig:var-acf}
@@
 
-The locally and globally-centered autocorrelations for the second chain have been shown in Figure~\ref{fig:var-acf} for two different simulation sizes where the true ACF is shown by the red line.
-When the individual chains have not explored well, the local sample means have not converged to $\mu$.
-As a consequence, the single chain empirical ACF estimator severely underestimate the truth.
-Due to sufficiently dispersed starting values, G-ACF is closer to reality.
-In subfigure~\ref{subfig:var-acf_n1e4}, the convergence property of sample means has kicked in for each chain.
-Therefore, both the estimators provide equivalent results.
-Note that G-ACF reveals the true nature of ACF for almost ten times lesser chain length $n$
-
-\begin{figure}[h]
+We compare the the locally and globally-centered autocorrelations against the truth.
+In Figure~\ref{fig:var-acf} are the estimated ACF plots for the first component of the second chain against the truth in red.
+For a run length of $10^3$ (top row), the commonly used locally centered ACF underestimates the true correlation structure giving a false sense of security about the mixing of the chain.
+The G-ACF, on the other hand, is much closer to the truth.
+This difference is negligible at the larger run length of $n = 10^4$ when each of the 5 chains have sufficiently explored the state space.
+
+Since $\mu_g$ is known, we assess the performance of ASV and GSV by assessing coverage probabilities of $95\%$ Wald confidence regions over 1000 replications.
+Table~\ref{tab:var-coverage} shows that for each sample size, the $\hat{\Sigma}_G$ results in close to nominal coverage probability, whereas $\hat{\Sigma}_A$ yields critically low coverage.
+The low coverage is a consequence of underestimating the autocovariances.
+It is only at the sample size of $n=10^5$ that $\hat{\Sigma}_A$ yields close to nominal coverage.
+
+\begin{table}[htbp]
     \centering
-      \includegraphics[width = 2.2in]{plots/var-frob.pdf} 
-      \includegraphics[width = 2.2in]{plots/var-ess.pdf}         
-    % \begin{subfigure}{0.4\textwidth}
-    %   \centering
-
-    %   \caption{$log(\|\hat{\Sigma}\|_F)$}
-    %   \label{subfig:var-frob}
-    % \end{subfigure}
-    % \begin{subfigure}{0.4\textwidth}
-    %   \centering
-
-    %   \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
-    %   \label{subfig:var-ess}
-    % \end{subfigure}
-    \caption{VAR(1).
-(a) Running plot for logarithm of Frobenius norm of A-SVE and G-SVE from $n = 500$ to $n = 10^5$.
-(b) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ calculated using A-SVE and G-SVE from $n=500$ to $n=10^5$.}
-    \label{fig:var-frob_n_ess}
-\end{figure}
-
-The quality of estimation of $\Sigma$ and $\text{ESS}/mn$ has been studied through convergence of - (a) $\log(\|\hat{\Sigma}_A\|_F)$ and $\log(\|\hat{\Sigma}_G\|_F)$ as $n$ increases and (b) $\log(\widehat{\textrm{ESS}}_A/mn)$ and $\log(\widehat{\textrm{ESS}}_G/mn)$ as $n$ increases.
-In practice, it is preferred to slightly overestimate the variance and underestimate the ESS than do otherwise.
-In Figure~\ref{fig:var-frob_n_ess}, both the running plots are shown along with the green horizontal line which marks the truth.
-We run the simulations for 50 replications for each value of $n$ and plot the average as well as standard errors.
-We run the simulations for a maximum chain length of $5 \times 10^4$ when the estimators seem to have almost converged.
-From Figure~\ref{subfig:var-frob}, it can be seen that for first $10000$ samples, A-SV estimates can be absurdly small giving false confidence in single chain estimates whereas G-SV gives a better understanding of reality.
-Similar comparative argument can can given for ESS.
-
-\begin{table}[h]
-    \centering
+    \small
     \begin{tabular}{|c|ccccc|}
@@
 
-We also report the coverage probabilities for a $95\%$ confidence interval constructed using $\hat{\Sigma}_A$ and $\hat{\Sigma}_G$ because the true mean is known here.
-Table~\ref{tab:var-coverage} shows that for each sample size, the globally-centered SV estimator for variance gives better coverage than A-SVE.
-At $n=10^5$, both the estimators have converged and give equivalently good coverage probability.
+The quality of estimation of $\Sigma$ and $\text{ESS}$ is assessed by running plots from 50 replications of run length 50000. 
+ In Figure~\ref{fig:var-frob_n_ess}, we present running plots of $\log(\|\hat{\Sigma}\|_F)$ for both $\hat{\Sigma}_G$ and $\hat{\Sigma}_A$ and the running plots of $\log(\widehat{\text{ESS}})$ for both  $\widehat{\text{ESS}}_G$ and $\widehat{\text{ESS}}_A$.
+It is evident that the locally centered estimator of $\Sigma$ severely underestimates the truth, leading to an overestimation of ESS.
+The GSV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS.
+\begin{figure}[htbp]
+    \centering
+      \includegraphics[width = 2.2in]{plots/var-frob.pdf} 
+      \includegraphics[width = 2.2in]{plots/var-ess.pdf}         
+    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV.(Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV.}
+    \label{fig:var-frob_n_ess}
+\end{figure}
 
@@
 
-Our globally-centered estimators perform exceptionally better than the single-chain estimators in case of multimodal target distribution.
-To that end, we will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions.
-This allows us to sample parallel Markov chains using the Gibbs sampler.
-Let $x$ and $y$ be two random variable that are jointly distributed as
-%
-\[
-f(x, y) \propto \exp\left(-\dfrac{1}{2} \left[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y  \right]\right)
-\]
-
-The conditional distribution of $x$ given $y$ and vice versa is a normal distribution given by:
-%
-\begin{align*}
-    x_1 \mid x_2 &\sim N\left(\dfrac{Bx_2 + C_1}{Ax_2^2 + 1}, \dfrac{1}{Ax_2^2 + 1}\right)\\
-    x_2 \mid x_1 &\sim N\left(\dfrac{Bx_1 + C_2}{Ax_1^2 + 1}, \dfrac{1}{Ax_1^2 + 1}\right)
+Consider the following family of bimodal bivariate distributions introduced by \cite{gelman1991note}, which term as a boomerang distribution.
+For $A \geq 0$ and $B, C  \in \mathbb{R}$, the target density is
+%
+\[
+f(x, y) \propto \exp\left(-\dfrac{1}{2} \left[Ax^2y^2 + x^2 + y^2 -2Bxy  -2Cx - 2Cy  \right]\right)\,.
+\]
+We run a deterministic scan Gibbs sampler to sample from this target using the following full conditional densities
+%
+\begin{align*}
+    x \mid y &\sim N\left(\dfrac{By + C}{Ay^2 + 1}, \dfrac{1}{Ay^2 + 1}\right)\\
+    y \mid x &\sim N\left(\dfrac{Bx + C}{Ax^2 + 1}, \dfrac{1}{Ax^2 + 1}\right)\,.
 \end{align*}
@@
 
-    \caption{Boomerang. Contour plots of the target distributions  overlayed with scatter plots for two chains for Setting 1 (left) and Setting 2 (right).}
+    \caption{Boomerang.
+Top row is Setting 1 and bottom row is Setting 2.
+Contour plots of the target distributions  overlaid with scatter plots for two chains for both settings.
+Locally-centered ACF (middle) and G-ACF (right) plots for one chain for $n = 1000$ with the blue line being the respectie ACF at $n = 10^4$.
+}
    \label{fig:boom-2D}
@@
 
-We report results for two different bi-modal parameter settings in this example.
-Firstly, we use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ wherein the two modes are well-separated with a very low connection (Setting-1, Figure~\ref{subfig:boom-2D_1_3_8}).
-Secondly, to examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$ wherein the two modes are closer and well-connected (Setting-2, Figure~\ref{subfig:boom-2D_1_10_7}).
-We will make another point through this example.
-For a fast mixing Markov chain, the globally-centered and locally-centered estimators give equivalent results.
-Therefore, it is a better practice to globally center the chains in any situation.
-We sample five parallel deterministically initialized chains with starting points dispersed uniformly in the first quadrant.
-Finding the actual mean of this distribution in closed form is difficult.
-Therefore, we use numerical integration with fine tuning to calculate it.
-
- To visualize the sticky nature of Markov chains in Setting-1, we show a scatter plot of two Markov chains starting near the two modes for $n = 1000$ in Figure~\ref{fig:boom-2D}.
-For the first thousand samples, both the chains are oblivious of the existence of another mode in setting-1.
-Whereas in setting-2, the chains have mixed fairly well for just $n=1000$.
-
- In Figure \ref{fig:boom-acf_1_3_8}, the autocorrelations are severely underestimated by A-ACF for $n=1000$ because the chains have not jumped modes.
-Whereas, for $n=10000$, both ACF and G-ACF give almost indistinguishable results indicating that A-ACF and G-ACF have converged to the truth.
-We can observe in Figure~\ref{fig:boom-acf_1_10_7} that A-ACF and G-ACF give similar results for just $n=1000$ under simulation setting-2.
-
-\begin{figure}[h]
-    \centering
-      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
-      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_10_7_m5.pdf}
-
-    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
-    \label{fig:boom-ess}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width = .30\textwidth]{plots/boom-frob_1_3_8_m5.pdf}  
-    \includegraphics[width = .30\textwidth]{plots/boom-frob_1_10_7_m5.pdf}
-
-    \caption{Boom: Running plot of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log (\|\hat{\Sigma}_G\|_F)$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
-    \label{fig:boom-frob}
-\end{figure}
-
-The convergence of $\log \widehat{\textrm{ESS}}_G/mn$ and $\log \widehat{\textrm{ESS}}_A/mn$ as $n$ increases can be seen in Figure~\ref{fig:boom-ess}.
-We can see that in the beginning, A-SVE gives misleadingly higher estimates of ESS$/mn$ than G-SVE.
-This can cause us to stop the sampling before each chain jumps to the other mode.
-As a consequence, each chain will correspond to a uni-modal target distribution.
-Whereas, as expected, the ESS estimates for setting-2 are almost same.
-Similarly, $\|\hat{\Sigma}_G\|_F$ reaches the convergence point in less than half the time as $\|\hat{\Sigma}_G\|_F$; as evidenced in Figure~\ref{subfig:boom-frob1}.
-No significant difference can be observed for setting-2 (Figure~\ref{subfig:boom-frob2}).
+We consider two settings; in setting 1 we let
+$A = 1,\; B = 3,\; C = 8$ which results in well-separated models.
+In setting 2, we let $A = 1, \; B = 10, \; C=7$ which yields in a boomerang shape for the contours.
+The contour plots for these two settings are in the left in Figure~\ref{fig:boom-2D}, overlaid with scatter plots of two parallel draws of the Gibbs sampler.
+Setting 2 is chosen specifically to illustrate that the locally and globally centered ACvFs perform similarly when the Markov chain moves freely across the state space.
+{\color{red} what is m here?}
+
+ For Setting 1, when the Markov chains have not been able to jump modes, locally-centered ACF severely underestimates autocorrelation.
+This is seen in the middle column in Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$.
+Somewhere between $n = 1000$ and $n = 10^4$, the Markov chains jump modes and it is only then that the locally-centered ACFs provide better estimates.
+The G-ACFs,  on the other hand, produce similar ACF estimates at $n = 1000$ and $n = 10^4$ by measuring deviations about the global mean.
+For setting 2, both methods yield similar ACF estimates reinforcing our claim that there is much to gain by using G-ACvF and nothing to lose.
 
@@
 \centering
+\small
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-Using the numerical approximation of the true mean, we construct the $95\%$ confidence interval using A-SVE and G-SVE.
-We report the coverage probabilities for a 1000 replications at different sample sizes $n$.
-For both the simulation settings, we provide coverage probabilities for $m=2$ and $m=5$.
-Table \ref{tab:boom-coverage_1}, \ref{tab:boom-coverage_2} reports all these results.
-In setting-1, it can be observed that G-SVE gives higher coverage probability than A-SVE for all values of $n$.
-Whereas for setting-2, the results are almost similar indicating the equivalence of A-SVE and G-SVE.
+The true mean of the target distribution can be obtained using numerical approximation.
+Using this and both the A-SV and G-SV estimators, we construct $95\%$ confidence regions and report coverage probabilities for 1000 replications for both $m=2$ and $m=5$.
+Table \ref{tab:boom-coverage_1}, \ref{tab:boom-coverage_2} reports all  results.
+In setting 1, systematically, the G-SV estimator yields far superior coverage than the A-SV estimator for all values of $n$.
+Whereas for setting 2, the results are almost similar indicating the equivalence of A-SV and G-SV for fast mixing Markov chains.
+
+\begin{figure}[h]
+    \centering
+      \includegraphics[width = .35\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
+      \includegraphics[width = .35\textwidth]{plots/boom-ess_1_10_7_m5.pdf}
+
+    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
+    \label{fig:boom-ess}
+\end{figure}
+
+In Figure~\ref{fig:boom-ess} we present running plots of estimates of $\log \textrm{ESS}/mn$ for both setting 1 and setting 2.
+As the sample size increases, $\widehat{\text{ESS}}_G$ and  $\widehat{\text{ESS}}_A$ become closer, but early on for setting 1, $\widehat{\text{ESS}}_G$ estimates are much smaller giving more adequate estimates of ESS.
+
+ % and $\log \widehat{\textrm{ESS}}_A/mn$ as $n$ increases can be seen in Figure~\ref{fig:boom-ess}.
+We can see that in the beginning, A-SVE gives misleadingly higher estimates of ESS$/mn$ than G-SVE.
+This can cause us to stop the sampling before each chain jumps to the other mode.
+As a consequence, each chain will correspond to a uni-modal target distribution.
+Whereas, as expected, the ESS estimates for setting-2 are almost same.
+Similarly, $\|\hat{\Sigma}_G\|_F$ reaches the convergence point in less than half the time as $\|\hat{\Sigma}_G\|_F$; as evidenced in Figure~\ref{subfig:boom-frob1}.
+No significant difference can be observed for setting-2 (Figure~\ref{subfig:boom-frob2}).
+
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width = .30\textwidth]{plots/boom-frob_1_3_8_m5.pdf}  
+%     \includegraphics[width = .30\textwidth]{plots/boom-frob_1_10_7_m5.pdf}
+
+%     \caption{Boom: Running plot of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log (\|\hat{\Sigma}_G\|_F)$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
+%     \label{fig:boom-frob}
+% \end{figure}
 
@@
     \centering
-    \includegraphics[width = .6\textwidth]{plots/sensor-trace_loc1.pdf}
+    \includegraphics[width = .32\textwidth]{plots/sensor-trace_loc1.pdf}
+      \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e3.pdf}
+      \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e4.pdf}    
     \caption{Sensor: Trace plots for $x$ (left) and $y$ (right) coordinate of sensor location-1.}
@@
 
-\begin{figure}[h]
-    \centering
-      \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e3.pdf}\includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e4.pdf}
-
-    \caption{Sensor: ACF (orange) and G-ACF (blue) for individual chains (dotted lines) and average over all chains (solid line) for $n = 5000$ (left) and $n = 50000$ (right).}
-    \label{fig:sensor-acf}
-\end{figure}
+% \begin{figure}[h]
+%     \centering
+%       \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e3.pdf}
+%       \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e4.pdf}
+
+%     \caption{Sensor: ACF (orange) and G-ACF (blue) for individual chains (dotted lines) and average over all chains (solid line) for $n = 5000$ (left) and $n = 50000$ (right).}
+%     \label{fig:sensor-acf}
+% \end{figure}
 

### 2020-08-20 one_run.R

@@ -458,15 +458,15 @@ nsim1 <- 1e5
 
 ### Trace plot - Location-1
 
-pdf(file = "AllOut/sensor-trace_loc1.pdf", height = 5, width = 10)
-par(mfrow = c(1,2))
+pdf(file = "AllOut/sensor-trace_loc1.pdf", height = 4, width = 4)
+par(mfrow = c(1,1))
 plot.ts(mc.chain.list[[1]][1:nsim1,1], ylim = range(mc.chain.list[[1]][,1], mc.chain.list[[5]][,1]), ylab = expression(x[11]), col = rgb(8, 69, 148, maxColorValue = 255))
 par(new = TRUE)
 plot.ts(mc.chain.list[[5]][1:nsim1,1], ylim = range(mc.chain.list[[1]][,1], mc.chain.list[[5]][,1]), yaxt='n', xaxt='n', ylab = "", col = rgb(107, 174, 214, maxColorValue = 255))
 
-plot.ts(mc.chain.list[[1]][1:nsim1,2], ylim = range(mc.chain.list[[1]][,2], mc.chain.list[[5]][,2]), ylab = expression(x[12]), col = rgb(8, 69, 148, maxColorValue = 255))
-par(new = TRUE)
-plot.ts(mc.chain.list[[5]][1:nsim1,2], ylim = range(mc.chain.list[[1]][,2], mc.chain.list[[5]][,2]), yaxt='n', xaxt='n', ylab = "", col = rgb(107, 174, 214, maxColorValue = 255))
+# plot.ts(mc.chain.list[[1]][1:nsim1,2], ylim = range(mc.chain.list[[1]][,2], mc.chain.list[[5]][,2]), ylab = expression(x[12]), col = rgb(8, 69, 148, maxColorValue = 255))
+# par(new = TRUE)
+# plot.ts(mc.chain.list[[5]][1:nsim1,2], ylim = range(mc.chain.list[[1]][,2], mc.chain.list[[5]][,2]), yaxt='n', xaxt='n', ylab = "", col = rgb(107, 174, 214, maxColorValue = 255))
 dev.off()
 
 ######################## Figure 11 ############################

### 2020-08-21 Paper/main.tex
Done with round 1. Finished with 31.5 pages. Stopping for today.

@@
 \end{equation}
-{\color{red} We need to figure out how we want to define autocovariance: with or without absolute value.}
+
 %
@@
 Specifically, parallel MCMC chains are often spread across the state space so as to adequately capture high density areas.
-For slow mixing Markov chains and multi-modal targets, the chains take time to traverse the space so that estimates of $\mu$ can be vastly different.
-The sample ACvF from each chain is typically underestimated yielding false sense of security about the quality of process.
+For slow mixing chains and multi-modal targets, the chains take time to traverse the space so that estimates of $\mu$ are vastly different.
+The ACvF from each chain is typically underestimated yielding false sense of security about the quality of process.
 
@@
 We quantify the gains in  bias  for the G-ACvF estimator below.
-% If the starting points of these parallel Markov chains are sufficiently dispersed, G-ACF provides more realistic estimation of lag covariances.
-\cite{priestley1981spectral} shows that the empirical estimator in Equation \ref{eq:empirical_ACvF} is biased with the main bias term equal to $\abs{k}\Gamma(k)/n$, ignoring the small order terms arising due to estimation of $\mu$.
-Though, an unbiased estimator with a divisor of $n - \abs{k}$ instead of $n$ exists, the biased estimator is preferred for its lower mean square error for larger relative $k$  (\cite{priestley1981spectral})
 Let
@@
 \end{theorem}
-
-{\color{orange}MA: I corrected the RHS for the abover equation. Or did you mean to write $\mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \Gamma(k) \right]as LHS?$}
 
@@
 By Birkhoff's ergodic theorem,  $\bar{\bar{Y}} \to \mu_g$ as $n \to \infty$ with probability 1.
-
 An asymptotic sampling distribution may be available via a Markov chain central limit theorem (CLT) if there exists a $p \times p$ positive-definite matrix $\Sigma$ such that
@@
 \label{eq:CLT}
-  \sqrt{mn}(\bar{\bar{Y}} - \mu_g) \xrightarrow{d} N(0,\Sigma)\,
+  \sqrt{mn}(\bar{\bar{Y}} - \mu_g) \xrightarrow{d} N(0,\Sigma)\, \quad \text{ where, }
 \end{equation}
-where
+% where
 \begin{equation}
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is continuous at $0$ at all but finite number of points.
-Further, $w(x)$ is a bounded and even function with $w(0)=1, \; {\color{red}\abs{w(x)} < c}$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W = \sum_{k = -\infty}^{\infty} w(k/b_n)$ is finite.
+The lag window $w(x)$ is continuous at $0$ at all but finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} w(k/b_n) < \infty$.
 \end{ass}
-% We will consider a range of lag windows $w(x)$; where $w(x)$ is a continuous, even function with $w(0)=1, \abs{w(x)} < c$, $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $W_n < \infty$. 
+
 Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows. We will use the following popular Bartlett lag window in our simulations:
@@
 %
-In our setting of $m$ parallel chains of $n$ samples each, define
-%
-\[
-\hat{\Lambda}_{mn} = \dfrac{1}{m(n-1)}\sum_{s=1}^{m}\sum_{t=1}^{n}(Y_{st} - \bar{Y}_s)(Y_{st} - \bar{Y}_s)^T\, ,
-\]
-and estimate ESS with
+In our setting of $m$ parallel chains of $n$ samples each, we
+%
+% \[
+% \hat{\Lambda}_{mn} = \dfrac{1}{m(n-1)}\sum_{s=1}^{m}\sum_{t=1}^{n}(Y_{st} - \bar{Y}_s)(Y_{st} - \bar{Y}_s)^T\, ,
+% \]
+ estimate ESS with
 \[
@@
     \centering
-      \includegraphics[width = 2.2in]{plots/var-frob.pdf} 
-      \includegraphics[width = 2.2in]{plots/var-ess.pdf}         
+      \includegraphics[width = 2.0in]{plots/var-frob.pdf} 
+      \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
     \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV.(Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV.}
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width = .8\textwidth]{plots/boom-all_1_3_8.pdf}\\
-    \includegraphics[width = .8\textwidth]{plots/boom-all_1_10_7.pdf}    
+    \includegraphics[width = .75\textwidth]{plots/boom-all_1_3_8.pdf}\\
+    \includegraphics[width = .75\textwidth]{plots/boom-all_1_10_7.pdf}    
     % \includegraphics[width = 0.6\textwidth ]{plots/boom-acf_1_10_7_n1000.pdf}
@@
 
-\begin{table}[h]
+\begin{table}[htbp]
 \parbox{.45\linewidth}{
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
-      \includegraphics[width = .35\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
-      \includegraphics[width = .35\textwidth]{plots/boom-ess_1_10_7_m5.pdf}
+      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
+      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_10_7_m5.pdf}
 
@@
 
-For our third example, we consider a real-life example of sensor locations previously discussed by \cite{ihler2005nonparametric}.
-The goal is to identify unknown sensor locations using noisy distance data.
-This problem is specifically interesting in our case because the marginal posterior distribution for missing sensor locations is multi-modal for all locations.
-
-Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor.
-Let $y_{ij} = (y_{ji})$ denote the distance between the sensors $x_i$ and $x_j$.
-The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$.
-Let $z_{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed.
-The probability model is then,
-%
-\begin{align*}
-    z_{ij} \mid x_1, ..., x_6 & \sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
-    y_{ij} \mid w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
-\end{align*}
-%
-\cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$.
-We use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$.
+Consider the sensor network localization problem discussed in \cite{ihler2005nonparametric}. The goal is to identify unknown sensor locations using noisy distance data. We use the data
+% This problem is specifically interesting in our case because the marginal posterior distribution for missing sensor locations is multi-modal for all locations. 
+%
+We use the data and the model as specified by \cite{tak2018repelling}.
+There are four sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denotes the coordinates of the $i${th} sensor.
+Let $y_{ij} = (y_{ij})$ denotes the distance between the sensors $x_i$ and $x_j$ and if observed yields $z_{ij} = 1$, otherwise, $z_{ij} = 0$.
+The complete model is then,
+\begin{align*}
+    z_{ij} \mid x_1, ..., x_4 & \sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
+    y_{ij} \mid z_{ij} = 1, x_i,x_j &\sim N(\|x_i - x_j\|^2, \sigma^2)
+\end{align*}
+%
+\cite{tak2018repelling} set $R = 0.3$ and $\sigma = 0.02$ and use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$.
 $y_{ij}$ is specified only if $w_{ij} = 1$.
-We follow the Markov chain structure as described by \cite{tak2018repelling} and sample from the four bivariate conditionals for each sensor location using a Gibbs sampler.
-In their paper on Repelling Attractive Metropolis (RAM) algorithms, \cite{tak2018repelling} compare the performance of different sampling techniques and show that RAM improves the acceptance rate by a factor of at least 5.5 over Metropolis using the same jumping scale.
-RAM algorithm supplies Markov chains with higher jumping frequency between the modes.
-
-\begin{figure}[h]
+The resulting $8$-dimensional posterior of $(x_1, \dots, x_4)$ is intractable with unknown full conditionals.
+A Metropolis-within-Gibbs type sampler is implemented with each full conditional employing the repelling attractive Metropolis (RAM) algorithm of \cite{tak2018repelling}.
+The RAM algorithm supplies Markov chains with higher jumping frequency between the modes.
+
+\begin{figure}[htbp]
     \centering
@@
       \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e4.pdf}    
-    \caption{Sensor: Trace plots for $x$ (left) and $y$ (right) coordinate of sensor location-1.}
+    \caption{Sensor: Trace plot of $x_{11}$ (left).
+Locally-centered ACF (solid orange) and G-ACF (solid blue) at $n = 5000$ (middle) and $n = 50000$ (right).
+Dashed lines are single-chain estimated ACFs.}
     \label{fig:sensor-trace}
 \end{figure}
-
-This is an 8-dimensional estimation problem where the components corresponds to x and y coordinates of four unknown sensor locations.
-We will use the RAM algorithm with a jumping scale equal to $0.5$ to sample five parallel Markov chains with well-separated starting points.
-The total simulation size for each chain is fixed at $100,000$.
-Since the truth about actual mean and asymptotic variance is not known in this case, we are not interested in coverage probabilities.
-
-To illustrate the \textit{sticky} nature of the Markov chains, we plot the evolution of two chains (starting near different modes) with time.
-Figure~\ref{fig:sensor-trace} shows the trace plot of x and y coordinate of sensor location-1.
-It is evident that the marginal posterior for both the components is bimodal.
-Similarly, the other three locations also have a bimodal marginal distribution in each component.
-Observe that each chain explores one particular mode for a long time before jumping to another mode.
-
-% \begin{figure}[h]
-%     \centering
-%       \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e3.pdf}
-%       \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e4.pdf}
-
-%     \caption{Sensor: ACF (orange) and G-ACF (blue) for individual chains (dotted lines) and average over all chains (solid line) for $n = 5000$ (left) and $n = 50000$ (right).}
-%     \label{fig:sensor-acf}
-% \end{figure}
 
@@
 
-Figure~\ref{fig:sensor-acf} plots the locally and globally centered ACF estimators for individual chains  as well as the average over all the chains.
-The thick solid line plots the averaged estimator and the thin dotted lines correspond to ACF calculated using single chains.
-Figure~\ref{fig:sensor-frob_n_ess} presents the running plot of $\log \|{\Sigma}\|_F$ and $\log \textrm{ESS}/mn$ estimated using A-SVE and G-SVE along with standard errors from $10$ replications for each value of $n$.
-In both the plots, G-SVE and $\widehat{\textrm{ESS}}_G/mn$ reach the convergence value faster.
+We run $m = 5$ parallel Markov chains with well-separated starting points.
+The total simulation size for each chain is fixed at $10^5$.
+Coverage probabilities are not estimable since the true posterior mean is unknown.
+Trace plot of $x_{11}$ for two Markov chains is shown in Figure~\ref{fig:sensor-trace}.
+Figure~\ref{fig:sensor-trace} also  plots locally and globally centered ACFs.
+As seen in previous examples, early estimates of locally-centered ACFs are must smaller than later estimates.
+The globally-centered ACFs, on the other hand are similar at small and large sample sizes.
+Figure~\ref{fig:sensor-frob_n_ess} presents the running plot of $\log \|{\Sigma}\|_F$ and $\log \textrm{ESS}/mn$ using A-SV and G-SV  estimators along with standard errors from $10$ replications.
+In both the plots, G-SV and $\widehat{\textrm{ESS}}_G/mn$ reaches stability significantly earlier than A-SV.
 
@@
 
-\begin{figure}[h]
+This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature.
+Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second component.
+We will report the ACF plots for component-2.
+Similar behavior is observed for ACF plots of other components as well
+
+\begin{figure}[htbp]
     \centering
@@
 \end{figure}
-
-This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature.
-Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second component.
-We will report the ACF plots for component-2.
-Similar behavior is observed for ACF plots of other components as well
-
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
-      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n1000.pdf}    
+      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n1000.pdf}  \\ \vspace{-.5cm}
       \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
@@
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
-      \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n100.pdf}
+      \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n100.pdf}\\ \vspace{-.5cm}
       \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n1000.pdf}

### 2020-08-23 Paper/main.tex
It's yours now

@@
 \documentclass[11pt]{article}
-% We can write notes using the percent symbol!
-% The first line above is to announce we are beginning a document, an article in this case, and we want the default font size to be 12pt
+
 % \usepackage[utf8]{inputenc}
@@
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
-% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
+
 \usepackage{fullpage}
@@
   \texttt{medhaaga@iitk.ac.in} \and
- Dootika Vats \\
+ Dootika Vats\footnote{Corresponding author}\\
   Dept.of Mathematics and Statistics\\
@@
 
-% {\color{blue} Main things to change
-% \begin{itemize}
-%   \item I don't want to call this ``Replicated autocovariance'' or ``Replicated spectral variance''.
-I think ``Globally-centered autocovariance'' is more appropriate and self-explanatory.
-So we will have to go over the whole document and change this.
-
-%   \item The contents are a bit messy right now, and I am having trouble organizing my thoughts.
-
-% \end{itemize}
-
-% A rough outline of the organization
-% \begin{enumerate}
-%   \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.:
-
-%     Here, we will just explain the problem with the old ACF and what happens by using the new ACF.
-We will show a plot to illustrate the impact.
-Then we will summarize the three places this will have an impact: (1) ACF plots (2) estimators of the asymptotic variance-covariance matrix (3) estimating effective sample size.
-
-%   \item Globally-centered autocovariance
-%     \begin{itemize}
-%       \item Theoretical soundness
-%     \end{itemize}
-
-%   \item Variance of Monte Carlo averages
-
-%     Describe MC averages and CLT here and not before
-%     \begin{itemize}
-%       \item Globally-centered Spectral variance estimators
-%       \begin{itemize}
-%         \item Theoretical results
-%         \item Fast implementation
-%       \end{itemize}
-%     \end{itemize}
-
-%   \item Effective sample size
-
-%   \item Examples
-
-%   \item Discussion
-%     \begin{itemize}
-%       \item All plots have been made using the package:(name). The package can be found on GitHub.
-%       \item One thing to discuss is that the new autocovariances can be used in the initial sequence estimators as well.
-%     \end{itemize}
-
-%   \item Appendix
-%     \begin{itemize}
-%       \item Proofs
-%       \item ACF plots for other examples.
-%     \end{itemize}
-
-% \end{enumerate}
-% }
-% \newpage
-
 \section{Introduction} \label{sec:intro}
 
-The power of the modern personal computer has made it easy to run parallel Markov chain Monte Carlo (MCMC) implementations.
-This is particularly useful for slow mixing or multi-modal target distributions, where the starting points of the chains are spread over the state-space in order to capture characteristics of the target distribution more accurately.
+Advancements in modern personal computing have made it easy to run parallel Markov chain Monte Carlo (MCMC) implementations.
+This is particularly useful for slow mixing Markov chains where the starting points of the chains are spread over the state-space in order to more accurately capture characteristics of the target distribution.
 The output from $m$ parallel chains is then summarized, visually and quantitatively, to assess the empirical mixing properties of the chains and the quality of Monte Carlo estimators.
 
-A key quantity of interest that drives MCMC output analysis is the autocovariance function (ACvF).
-From their use in autocorrelation plots to assessing Monte Carlo variability of estimates, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences users make from MCMC output.
-However, tools on estimating ACvF are largely constructed for output from one MCMC chain.
-{\color{blue} a little bit more here}.
-
-% Markov chain Monte Carlo (MCMC) is a sampling method used to obtain serially correlated realizations from a desired probability distribution when i.i.d.
-sampling is difficult.
-Due to this serial correlation in samples, a larger number of MCMC samples are required to make inferences about the target distribution as compared to the independent ones.
-Therefore, it becomes imperative for an MCMC practitioner to have an idea about the underlying dependence structure in the Markov chains.
-Autocovariance function (ACF) characterizes this dependence at a particular lag $k$.
-
-Let $F$ be the target distribution with mean $\mu$ defined on the set $\X \subseteq \mathbb{R}^p$ equipped with a countably generated Borel $\sigma$-field $\mathcal{B}(\X)$.
-For $s = 1, \dots, m$, let $\{X_{st}; \; t \in \mathbb{Z}\}$ be the $s^{th}$ $F$-Harris ergodic stationary Markov chain \citep[see][for definitions]{meyn:twee:2009} employed to learn characteristics about $F$.
-% If $\bar{X} = n^{-1} \sum_{t=1}^{n}X_t$ , then with probability 1, $\bar{X} \to \mu_g$ as $n \to \infty$. \\
+A key quantity that drives MCMC output analysis is the autocovariance function (ACvF).
+From their use in autocorrelation (ACF) plots to assessing Monte Carlo variability of estimators, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences from MCMC output.
+However, estimators of ACvF are only available for single-chain implementations, with multiple-chain obtained by naive averaging.
+As we will demonstrate, this defeats the purpose of running parallel Markov chains from dispersed starting values.
+
+Let $F$ be the target distribution with mean $\mu$ defined on a space $\X \subseteq \mathbb{R}^d$ equipped with a countably generated $\sigma$-field $\mathcal{B}(\X)$.
+For $s = 1, \dots, m$, let $\{X_{st}\}_{t\geq1}$ be the $s${th} Harris ergodic $F$-invariant Markov chain \citep[see][for definitions]{meyn:twee:2009} employed to learn characteristics about $F$.
 The process is covariance stationary so that
-the ACvF at lag $k$ depends only on $k$ and is defined as 
+the ACvF at lag $k$ is defined as 
 %
@@
 \]
-Estimating $\Gamma(k)$ is critical to assessing the quality of the sampler and the quality of sample statistics.
+Estimating $\Gamma(k)$ is critical to assessing the quality of the sampler and the reliability of Monte Carlo estimators.
 Let $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ denote the Monte Carlo estimator of $\mu$ from the $s$th chain.
-The standard estimator for $\Gamma(k)$ is the sample autocovariance matrix at lag $k$.
-For the $s$th chain, it is given by
+The standard estimator for $\Gamma(k)$ is the sample autocovariance matrix at lag $k \geq 0$:
 %
 \begin{equation} \label{eq:empirical_ACvF}
-    \hat{\Gamma}_s(k) = \dfrac{1}{n}\sum_{t=1}^{n-\abs{k}} \left(X_{st} - \bar{X}_s \right) \left(X_{s\, t+\abs{k}} - \bar{X}_s \right)^T\,.
+    \hat{\Gamma}_s(k) = \dfrac{1}{n}\sum_{t=1}^{n-k} \left(X_{st} - \bar{X}_s \right) \left(X_{s\, t + k} - \bar{X}_s \right)^T\,,
 \end{equation}
-
-%
-% It is a known fact that most of the Markov chains obtained from practical MCMC algorithms are not stationary.
-Regardless, Equation~\ref{eq:empirical_ACvF} provides the empirical estimator for ACF at a particular lag for the Markov chain with any initial distribution (\cite{geyer2011introduction}).\\
-
-% Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
-However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
-Unfortunately, the estimator given in Equation~\ref{eq:empirical_ACvF} has been observed to have a some drawbacks.
-Firstly, it is not immune to outliers (see \cite{ma2000highly}) and secondly, it is usually non-informative in case of slowly mixing Markov chains.
-For single-chain MCMC runs, the estimator $\hat{\Gamma}(k)$ is used to construct autocorrelation (ACF) plots, to estimate the long-run variance of Monte Carlo estimators \cite{hannan:1970,dame:1991}, and to estimate effective sample size for an estimation problem \cite{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
-
+and for $k < 0$, $\hat{\Gamma}_s(k) = \hat{\Gamma}_s(-k)^T$.
+For single-chain MCMC runs, the estimator $\hat{\Gamma}_s(k)$ is used to construct ACF plots, to estimate the long-run variance of Monte Carlo estimators \cite{hannan:1970,dame:1991}, and to estimate effective sample size (ESS) \cite{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
 However, there is no unified approach to constructing estimators of $\Gamma(k)$ for multiple-chain implementations.
 Specifically, parallel MCMC chains are often spread across the state space so as to adequately capture high density areas.
-For slow mixing chains and multi-modal targets, the chains take time to traverse the space so that estimates of $\mu$ are vastly different.
-The ACvF from each chain is typically underestimated yielding false sense of security about the quality of process.
-
-% We address the second issue in this paper by using multiple representative samples of the target distribution via parallel Markov chains.
-This approach is especially relevant to MCMC wherein multiple chain sampling is computationally possible and statistically desirable for making informative inferences.
-Our goal is to pool in the information from all the Markov chains while estimating the autocovariances.
-
- % A commonly faced problem with the MCMC models is the slow mixing property.
-Especially in case of multi modal target distributions, it has been observed that the Markov chains tend to get \textit{stuck} in a particular mode for a long time.
-In such situations, single chain empirical ACF will severely underestimate the autocovariance.
- We propose a globally-centered ACvF (G-ACvF) that centers the Markov chain around the overall mean vector from all $m$ chains.
-We show that the bias under stationarity for G-ACvF is lower than $\hat{\Gamma}(k)$, and through various examples, empirically demonstrate improved estimation.
-We employ the G-ACvF estimators to construct autocorrelation plots, which leads to remarkable improvements.
+For slow mixing chains, the chains take time to traverse the space so that $\bar{X}_s$  are all vastly different.
+Consequently, $\hat{\Gamma}_s$ typically underestimates $\Gamma$ leading to a false sense of security about the quality of process.
+
+ We propose a globally-centered estimator of ACvF (G-ACvF) that centers the Markov chain around the overall mean vector from all $m$ chains.
+We show that the bias under stationarity for G-ACvF is lower than $\hat{\Gamma}_s(k)$, and through various examples, empirically demonstrate improved estimation.
+We employ the G-ACvF estimators to construct ACF plots, which leads to remarkable improvements.
 A demonstrative example is at the end of this Section.
@@
 
-ACvFs are required to estimate the long-run variance of Monte Carlo averages.
-Specifically, spectral variance estimators are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$.
-We replace $\hat{\Gamma}(k)$ with G-ACvF in spectral variance estimators (SVE) and show strong consistency of this estimator under weak conditions.
-In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimator of $\Sigma$.
-Spectral variance estimators can be slow to prohibitively expensive to calculate \citep{liu:fleg:2018}.
+Estimators of ACvFs are often needed to estimate the long-run variance of Monte Carlo averages.
+Specifically, spectral variance (SV) estimators  are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$ \citep{andr:1991,dame:1991,fleg:jone:2010}.
+We replace $\hat{\Gamma}(k)$ with G-ACvF in SV estimators and demonstrate strong consistency under weak conditions.
+In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimators.
+SV estimators can be prohibitively slow to  compute \citep{liu:fleg:2018}.
 To relieve the computational burden, we adapt the fast algorithm of \cite{heberle2017fast} for G-ACvFs that dramatically reduces computation time.
-The globally-centered spectral variance estimator (G-SVE) is employed in the computation of effective sample size through the estimator given by \cite{vats2019multivariate}.
-We will show that using G-SVE for estimating $\Sigma$ safeguards us against early termination of the MCMC process and improves the reliability of estimators.
-
-% Let $g: \X \to \mathbb{R}^d$ be an F-integrable function and suppose we are interested in estimating the expected value $\mu_g = \mathbb{E}_F[g(X)]$.
-We know that $\sum_{t=1}^{n}g(X_t)/n$ converges to $\mu_g$ as $n \to \infty$ almost surely.
-MCMC ensures asymptotic convergence, however this is not practically very useful where the number of samples is finite and the Markov chain mixes slowly.
-% One of the important criteria to determine the quality of estimation is the Monte Carlo aymptotic covariance matrix which is given by an infinite summation of autocovariance matrices for all lags.
-For a slowly mixing Markov chain, underestimated autocovariances will deliver underestimated asymptotic variance.
-There are many techniques for estimating it like batch means (BM), overlapping bath means (OBM), and spectral variance estimator (SVE).
-Due to its nice statistical properties, we will only focus on SVE in this paper.
-SVE involves a truncated and weighted sum of autocovariances.
-We propose a version of SVE that uses our globally centered autocovariances.
-We call this globally-centered SVE (G-SVE).
-
-% A more powerful estimator of Monte Carlo variability can enable us to estimate the effective sample size for the Markov chain which is closer to reality.
-There are many criteria for terminating simulation like fixed-time rule, sequencial fixed-volume rule (see \cite{glynn1992asymptotic}), and using Gelman Rubin diagnostics (\cite{gelman1992inference}).
-The relative fixed-volume rule has been thoroughly discussed for MCMC by \cite{flegal2015relative} and \cite{gong2016practical}.
-We will use method of effective sample size (ESS) by \cite{vats2019multivariate} for terminating the simulations.
-The quality of estimation of asymptotic covariance matrix is critical in estimation of the ESS.
-We will successfully show that the G-SVE estimates the truth better and prevents the premature stopping of Markov chain.
-
-% The rest of the paper is arranged as follows.
-In Section~\ref{sec:G-ACF} we introduce the new sample autocovariance estimator and calculate its bias for finite samples.
-We observe that the bias term for G-ACF is similar to the bias of empirical ACF except for a few small order end-effect terms that vanish as $n \to \infty$.
-In Section~\ref{sec:variance_est}, we introduce the globally-centered SVE and give a proof of strong consistency, bias, and variance calculations.
-We will elaborate on the estimator for ESS using G-SVE in Section~\ref{sec:ess}.
-Section~\ref{sec:examples} gives an experimental study on three different examples for the proposed estimators.
-All the important proofs are given in the Appendix.
+The globally-centered spectral variance estimator (G-SVE) is employed in the computation of ESS.
+We will show that using G-SVE for estimating $\Sigma$ safeguards users against early termination of the MCMC process.
 
@@
 
-We demonstrate the striking difference in estimation of $\Gamma(k)$ via autocorrelation function (ACrF) plots.
+We demonstrate the striking difference in estimation of $\Gamma(k)$ via ACF plots.
 Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density.
@@
 where $f(x; a,b)$ is the density of a normal distribution with mean $a$ and variance $b$. 
-Two Markov chains are started at each mode.
-Let $n$ denote the number of samples for each chain.
-Figure~\ref{fig:gaussian-trace} indicates that in the first $10^4$ samples, the chains do not jump modes so that both Markov chains yield different estimates of the population mean, $\mu$.
+We set $m = 2$ with starting values distributed to the two modes.
+The trace plots in Figure~\ref{fig:gaussian-trace} indicates that in the first $10^4$ steps, the chains do not jump modes so that both Markov chains yield significantly different estimates of the population mean, $\mu$.
 At $10^5$ sample size, both Markov chains have traversed the state space reasonably and yield similar estimates of $\mu$.
-We make two points here: first, for small sample size, we observe that the locally-centered ACF gives misleading estimates whereas G-ACF accounts for the discrepancy in sample means between two chains.
-This is evident from the ACF plots  in Figure~\ref{fig:gaussian-acf}.
-Second, for a large sample size, the estimates from G-ACrF as well as ACrF are equivalent.
-Therefore, G-ACF can be used in any situation with a promise of estimates that are at least as good as empirical ACF estimators.
+
+In Figure~\ref{fig:gaussian-acf} for $n = 10^4$, we present the ACF plots using the usual locally-centered ACvF and our proposed G-ACF estimator.
+The blue curve are the respective estimates at $n = 10^5$.
+At $n = 10^5$ when the chains have similar means, the G-ACF and locally-centered ACF are equivalent.
+However, for $n = 10^4$, the locally-centered ACFs critically underestimate the correlation giving user a misleading visual quality of the Markov chain.
+The G-ACF estimator accounts for the discrepancy in sample means between two chains leading to a far improved quality of estimation.
 
@@
 
-\caption{ACF plots using locally-centering (left) and global centering (right). Histogram estimates at $n = 10^4$ with the blue line plot being estimates from $n = 50000$ for chain 1.}
+\caption{ACF plots using local-centering (left) and global-centering (right).
+Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 50000$ {\color{red}can you do this at $10^5$?} for chain 1.}
  % (b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
@@
 
-Recall that we run $m$ independent $F$-ergodic Markov chains denoted by $\{X_{st}; \; t \in \mathbb{Z}\}$ for the $s^{th}$ chain.
-Let the sample mean of the $s^{th}$ Markov chain be $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ and the global mean by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
-The global mean is naturally superior estimator of $\mu$ than $\bar{X}_s$.
-We define the globally-centered autocovariance function (G-ACvF) estimator for the $s^{th}$ Markov chain as
+% Recall that we run $m$ independent $F$-ergodic Markov chains denoted by $\{X_{st}; \; t \in \mathbb{Z}\}$ for the $s^{th}$ chain. 
+Let $P$ denote the Markov transition kernel that uniquely determines the ACvF under stationarity.
+Recall the sample mean of the $s^{th}$ Markov chain is $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ and denote the global mean by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
+The global mean is a naturally superior estimator of $\mu$ than $\bar{X}_s$.
+For $k \geq 0$, we define the globally-centered ACvF (G-ACvF) estimator for the $s${th} Markov chain as
 %
@@
 \end{equation}
-
-In the event that all $m$ Markov chains have been run long enough that $\bar{X}_s \approx \bar{\bar{X}}$ are similar, then  $\hat{\Gamma}_{s} (k) \approx \hat{\Gamma}_{G,s}(k)$.
+with $\hat{\Gamma}_{G,s}(k) = \hat{\Gamma}_{G,s}(-k)^T$ for $k < 0$. 
+In the event that all $m$ Markov chains have been run long enough that $\bar{X}_s \approx \bar{\bar{X}}$, then  $\hat{\Gamma}_{s} (k) \approx \hat{\Gamma}_{G,s}(k)$.
 However, for shorter runs or for slow mixing chains, $\Gamma(k)$ is more appropriately estimated by $\hat{\Gamma}_{G,s}$ as it utilizes information from all chains and accounts for disparity between estimates of $\mu$.
-We quantify the gains in  bias  for the G-ACvF estimator below.
+% We quantify the gains in  bias  for the G-ACvF estimator below. 
 Let 
@@
 \begin{theorem} \label{th:G-ACF_bias} Let $\E_F \|X_{11}\|^{2 + \delta} < \infty$ for some $\delta > 0$.
-Let $P$ be a  polynomially ergodic Markov chain of order $\xi > (2 + \epsilon)/(1 + 2/\delta)$ for some $\epsilon > 0$.
-Then,
-\[
-   \mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
-\]
-and consequently,
-\[
-\mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}_s(k) \right] =  \left(1- \dfrac{|k|}{n}\right)\left(1- \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
-\]
+If $P$ is polynomially ergodic of order $\xi > (2 + \epsilon)/(1 + 2/\delta)$ for some $\epsilon > 0$,  then,
+\[
+   \mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,.
+\]
+% and consequently,
+% \[
+% \mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}_s(k) \right] =  \left(1- \dfrac{|k|}{n}\right)\left(1- \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,.
+% \]
 \end{theorem}
@@
  % Special interest is also in the lag-0 autocovariance, that is, the variance of the target distribution. 
-\begin{remark} \label{rem:lag0_expectation}
-The variance of the target distribution is the lag covariance at lag 0 and is of particular interest. The bias of the estimator reduces by a factor of $m$:
-\[
-\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
-\]
-\end{remark}
-
-A first use of the ACvFs in MCMC is in constructing ACF plots. Let the target variance of $i${th} component be $\Gamma^{ii}(0)$. For any component $i$, the autocorrelation is defined as
-\[
-\rho^{ii}(k) = \dfrac{\Gamma^{ii}(k)}{\Gamma^{ii}(0)}\,,
+% The covariance matrix of the target distribution is the lag-0 covariance and is of particular interest.
+%  The bias of the estimator reduces by a factor of $m$:
+% \[
+% \mathbb{E} \left[\hat{\Gamma}_{G,s}(0) \right] = \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
+% \]
+
+% A first use of the ACvFs in MCMC is in constructing ACF plots. 
+Let the target variance of $i${th} component be $\Gamma^{ii}(k)$. For any component $i$, the autocorrelation is defined as
+\[
+\rho^{(i)}(k) = \dfrac{\Gamma^{ii}(k)}{\Gamma^{ii}(0)}\,,
 \]
@@
 \]
-The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gaussian:acf}.
+The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gaussian-acf}.
 
@@
 
-A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.
-Let $g:\X \longrightarrow \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
+A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.  Let $g:\X \to \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
 $\mu_g = \mathbb{E}_F[g(X)]$.
@@
 Let $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.
-By Birkhoff's ergodic theorem,  $\bar{\bar{Y}} \to \mu_g$ as $n \to \infty$ with probability 1.
+By Birkhoff's ergodic theorem,  $\bar{\bar{Y}} \to \mu_g$ with probability 1 as $n \to \infty$.
 An asymptotic sampling distribution may be available via a Markov chain central limit theorem (CLT) if there exists a $p \times p$ positive-definite matrix $\Sigma$ such that
@@
 There is a rich literature on estimating $\Sigma$ for single-chain MCMC implementations.
-The most common are spectral variance (SV) estimators \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \citep{chen:seila:1987,vats:fleg:jon:2019}.
+The most common are SV estimators \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \citep{chen:seila:1987,vats:fleg:jon:2019}.
 Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from parallel chains.
-Batch means estimators are computationally more efficient than SV estimators, whereas SV estimators are more reliable \citep{fleg:jone:2010}.
-Here, we utilize G-ACvF estimators to construct globally-centered SV estimator (G-SVE) of $\Sigma$.
+Batch means estimators are computationally more efficient than SV estimators, whereas SV estimators are more reliable \citep{damerdji:1995,fleg:jone:2010}.
+Here, we utilize G-ACvF estimators to construct globally-centered SV (G-SV) estimator of $\Sigma$.
 Using the methods of \cite{heberle2017fast}, we also provide an efficient algorithm for obtaining the G-SV estimator.
 
-The locally and globally centered  estimators for $\Upsilon(k)$ are $\hat{\Upsilon}_s(k)$ and $\hat{\Upsilon}_{G,s}(k)$, respectively, where
-\[
-\hat{\Upsilon}_s(k) = \dfrac{1}{n} \ds \sum_{t=1}^{n - |k|} (Y_{st} - \bar{Y}_s)(Y_{s\,t+k} - \bar{Y}_s)^T \quad \text{ and } \quad \hat{\Upsilon}_{G,s}(k) = \dfrac{1}{n} \ds \sum_{t=1}^{n - |k|} (Y_{st} - \bar{\bar{Y}})(Y_{s\,t+k} - \bar{\bar{Y}})^T\,,
+The locally and globally-centered  estimators of $\Upsilon(k)$ are $\hat{\Upsilon}_s(k)$ and $\hat{\Upsilon}_{G,s}(k)$, respectively, where for $k \geq 0$
+\[
+\hat{\Upsilon}_s(k) = \dfrac{1}{n} \ds \sum_{t=1}^{n - k} (Y_{st} - \bar{Y}_s)(Y_{s\,t+k} - \bar{Y}_s)^T \quad \text{ and } \quad \hat{\Upsilon}_{G,s}(k) = \dfrac{1}{n} \ds \sum_{t=1}^{n - k} (Y_{st} - \bar{\bar{Y}})(Y_{s\,t+k} - \bar{\bar{Y}})^T\,,
 \] 
 and let $\hat{\Upsilon}_G(k) = m^{-1} \sum_{k=1}^{m}\hat{\Upsilon}_{G,s}(k)$.
-SV estimators are constructed as weighted and truncated sums of estimated lag covariances.
+SV estimators are constructed as weighted and truncated sums of estimated ACvFs.
 For some $c \geq 1$, let $w: \mathbb{R} \to [-c,c]$ be a lag window function and $b_n \in \mathbb{N}$ be a bandwidth.
-The SV estimator of $\Sigma$ for chain $s$ is
+The (locally-centered) SV estimator of $\Sigma$ for chain $s$ is
 %
@@
 \cite{vats:fleg:jon:2018} provided conditions for strong consistency while \cite{fleg:jone:2010,vats:flegal:2018} provided large-sample bias and variance results.
-These results also extend naturally to an average SV (ASV) estimator
-\[
-\hat{\Sigma}_A = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{s}\;.
-\]
+These results also extend naturally to an average SV (ASV) estimator $\hat{\Sigma}_A = m^{-1} \sum_{s=1}^{m}\hat{\Sigma}_{s}$.
+% \[
+% \hat{\Sigma}_A = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{s}\;.
+% \]
 
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is continuous at $0$ at all but finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} w(k/b_n) < \infty$.
+The lag window $w(x)$ is continuous at $0$ at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} w(k/b_n) < \infty$.
 \end{ass}
@@
 
-We will present three main results for the G-SV estimator.
 First, we provide conditions for strong consistency.
@@
   \label{thm:kuelbs}
-Let $\E_F\|Y_{11}\|^{2+ \delta} < \infty$ for $\delta > 0$ and let $P$ be a polynomially ergodic Markov chain of order $\xi > (q + 1 + \epsilon)/(1 + 2/\delta)$ for $q \geq 1$.
-Then there exists a $p \times p$ lower triangular matrix $L$ such that $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for almost all $\omega \in \Omega$ such that for all $n > n_0$, with probability 1,
-\[
-\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n)\,.
+Let $\E_F\|Y_{11}\|^{2+ \delta} < \infty$ for $\delta > 0$ and let $P$ be polynomially ergodic of order $\xi > (q + 1 + \epsilon)/(1 + 2/\delta)$ for $q \geq 1$.
+Then there exists a $p \times p$ lower triangular matrix $L$ such that $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for almost all $\omega \in \Omega$ and for all $n > n_0$,
+\[
+\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n) \qquad \text{  with probability 1}\,.
 \]
@@
 Another class of estimators for asymptotic variance of Monte Carlo averages are the multivariate initial sequence (mIS) estimators \citep{dai:jon:2017}.
-Similar to SV estimator, lag-covariances form the fundamental part of mIS estimators.
-In case of multi-modal target distributions, single chain mIS estimator will suffer from the same drawbacks as SVE.
-In this paper, we have chiefly focused on the usage of G-ACvF for estimating autocovariances in SVE; however the argument for a similar usage in mIS is straightforward.
-Following \cite{dai:jon:2017}, generalised variance estimates obtained from mIS consistently overestimate $\abs{\Sigma}$.
+Similar to SV estimator, ACvFs are a  fundamental part of mIS estimators and underestimation in ACvFs yields underestimates of $\Sigma$.
+% In this paper, we have chiefly focused on the usage of G-ACvF for estimating autocovariances in SVE; however the argument for a similar usage in mIS is straightforward.  
+Following \cite{dai:jon:2017}, it is easy to show that $\hat{\Upsilon}_{G,s}(k)$ are strongly consistent for $\Upsilon(k)$ and replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following \citep[][Lemma 5]{dai:jon:2017} will yield consistent overestimation of $\Sigma$ using a globally-centered version of the mIS estimator.
+
+% generalised variance estimates obtained from mIS consistently overestimate $\abs{\Sigma}$.
 From Theorem~\ref{th:G-ACF_bias}, one can prove that, on average, the eigenvalues of $\hat{\Gamma}_{G,s}(k)$ are greater than the eigenvalues of $\hat{\Gamma}_s(k)$.
@@
 
-The choice of starting vector is crucial for multiple chain sampling.
+% The choice of starting vector is crucial for multiple chain sampling.
 In case the chains are started very near to each other, all the chains will explore nearly the same neighborhood in the state space.

### 2020-08-25 Paper/main.tex
Layer-1 edits.

@@
 From their use in autocorrelation (ACF) plots to assessing Monte Carlo variability of estimators, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences from MCMC output.
-However, estimators of ACvF are only available for single-chain implementations, with multiple-chain obtained by naive averaging.
+However, estimators of ACvF are only available for single-chain implementations, with multiple-chain version obtained by naive averaging.
 As we will demonstrate, this defeats the purpose of running parallel Markov chains from dispersed starting values.
@@
 and for $k < 0$, $\hat{\Gamma}_s(k) = \hat{\Gamma}_s(-k)^T$.
-For single-chain MCMC runs, the estimator $\hat{\Gamma}_s(k)$ is used to construct ACF plots, to estimate the long-run variance of Monte Carlo estimators \cite{hannan:1970,dame:1991}, and to estimate effective sample size (ESS) \cite{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
+For single-chain MCMC runs, the estimator $\hat{\Gamma}_s(k)$ is used to construct ACF plots, to estimate the long-run variance of Monte Carlo estimators \citep{hannan:1970,dame:1991}, and to estimate effective sample size (ESS) \citep{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
 However, there is no unified approach to constructing estimators of $\Gamma(k)$ for multiple-chain implementations.
@@
 Specifically, spectral variance (SV) estimators  are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$ \citep{andr:1991,dame:1991,fleg:jone:2010}.
-We replace $\hat{\Gamma}(k)$ with G-ACvF in SV estimators and demonstrate strong consistency under weak conditions.
-In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimators.
+We replace $\hat{\Gamma}(k)$ with G-ACvF in SV estimators to obtain globally-centered SV (G-SV) estimator and demonstrate strong consistency under weak conditions.
+In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimator.
 SV estimators can be prohibitively slow to  compute \citep{liu:fleg:2018}.
-To relieve the computational burden, we adapt the fast algorithm of \cite{heberle2017fast} for G-ACvFs that dramatically reduces computation time.
-The globally-centered spectral variance estimator (G-SVE) is employed in the computation of ESS.
-We will show that using G-SVE for estimating $\Sigma$ safeguards users against early termination of the MCMC process.
+To relieve the computational burden, we adapt the fast algorithm of \cite{heberle2017fast} for G-SV estimator that dramatically reduces computation time.
+The G-SV estimator  is employed in the computation of ESS.
+We will show that using G-SV estimator for estimating $\Sigma$ safeguards users against early termination of the MCMC process.
 
@@
 
-\caption{ACF plots using local-centering (left) and global-centering (right).
-Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 50000$ {\color{red}can you do this at $10^5$?} for chain 1.}
+\caption{ACF plots using local-centering (left) and global-centering (right). Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 10^5$ for chain 1.}
  % (b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
@@
 Here, we utilize G-ACvF estimators to construct globally-centered SV (G-SV) estimator of $\Sigma$.
-Using the methods of \cite{heberle2017fast}, we also provide an efficient algorithm for obtaining the G-SV estimator.
+Using the method of \cite{heberle2017fast}, we also provide a computationally efficient algorithm for obtaining the G-SV estimator.
 
@@
 \cite{vats:fleg:jon:2018} provided conditions for strong consistency while \cite{fleg:jone:2010,vats:flegal:2018} provided large-sample bias and variance results.
-These results also extend naturally to an average SV (ASV) estimator $\hat{\Sigma}_A = m^{-1} \sum_{s=1}^{m}\hat{\Sigma}_{s}$.
+These results also extend naturally to an average SV (ASV) estimator defined as $\hat{\Sigma}_A := m^{-1} \sum_{s=1}^{m}\hat{\Sigma}_{s}$.
 % \[
@@
 
-The SV estimator, despite good statistical properties, poses limitations due to slow computation.
+The SV estimator, despite having good statistical properties, poses limitations due to slow computation.
 From \eqref{eq:empirical_ACvF} and \eqref{eq:sve}, the complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for the Bartlett lag window, it is $\mathcal{O}(b_n n p^2)$.
@@
  \cite{heberle2017fast} compute the $n \times 1$ vector $T(w)A_s$  using an algorithm based on fast Fourier transforms.
-Let $w^* = (1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1}, ~0, ~w_{n-1}, \dots, w_1)^T$ and set $C(w^*)$ to be a symmetric circulant matrix such that $C(w^*)_{1:n, 1:n} = T(w)$.
+Let $w^* = (1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1}, ~0, ~w_{n-1}, \dots, w_1)^T$ and set $C(w^*)$ to be a symmetric circulant matrix such that the matrix truncation $C(w^*)_{1:n, 1:n} = T(w)$.
 With inputs $C(w^*)$ and $A_s$, Algorithm~\ref{algo:herberle} produces $\hat{\Sigma}_s$ exactly.
@@
     { 
-    Calculate $V^*A_s^{*_{(j)}}$ by DFT of $A^*_{s(j)}$.\;
+    Calculate $V^*A^*_{s(j)}$ by DFT of $A^*_{s(j)}$.\;
     Multiply $V^* A_{s(j)}^{*^{(i)}}$ with the eigenvalue $\lambda_i$ for all $i = 1, ..., 2n$ to construct $\Lambda V^* A_{s(j)}^*$.\;
@@
 Herberle's algorithm is then applied on the formulation
-We note a similar decomposition is possible for the G-SV estimator.
+We observe that a similar decomposition is possible for the G-SV estimator.
 Setting $B_s = (Y_{s1} - \bar{\bar{Y}} \; \dots \; Y_{sn} - \bar{\bar{Y}})^T$ and calling Algorithm~\ref{algo:herberle} with inputs $C(w^*)$ and $B_s$ yields $\hat{\Sigma}_{G,s}$.
@@
 
-In this section we consider three different target distributions and sample multiple Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators.
+In this section we consider three different target distributions and sample $m$ parallel Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators.
 We will make the following three comparisons - (1) A-ACF vs G-ACF through ACrF plots; (2) A-SVE vs G-SVE; (3) $\widehat{\textrm{ESS}}_G$ vs $\widehat{\textrm{ESS}}_A$.
-The quality of estimation of $\Sigma$ is studied by coverage probabilities for a $95 \%$ confidence interval in cases where the true mean $\mu$ is known.
-The convergence of local and global estimators as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$ denoted by $\|M\|_F$ for a matrix $M$, and (2) logarithm of estimated ESS/$mn$.
-In all the examples we consider the function $g(x) = x$, which implies the Markov chain $\{Y_t\}$ and $\{X_t\}$ are the same.
+The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence interval in cases where the true mean $\mu$ is known.
+The convergence of local and global estimators of $\Sigma$ and $\widehat{\textrm{ESS}}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$.
+In all the examples we are interested in estimating the mean of the stationary distribution $\mu$, so $g$ is the identity function.
+The batch size $b_n$ is obtained from the function \texttt{batchSize} from \texttt{R} package \texttt{mcmcse}.
 
@@
 For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note}.
-Through this example, we will also show that in case of nicely mixing Markov chains, these estimators give almost equivalent results.
+Through this example, we will also show that in case of nicely mixing Markov chains, these estimat give almost equivalent results.
 Lastly, we consider a real-life example of finding unknown locations of sensors using noisy distance data.
@@
 The invariant distribution for this Markov chain is $N(0, \Psi)$, where $vec(\Psi) = (I_{p^2} - \Phi \times \Phi)^{-1} vec(W)$.
-We are interested in estimating the mean of the stationary distribution, so $g$ is the identity function.
 For $k > 0$, the lag-$k$ autocovariance is $\Upsilon(k) = \Gamma(k) = \Phi^k\Psi$.
@@
 
-Since $\mu_g$ is known, we assess the performance of ASV and GSV by assessing coverage probabilities of $95\%$ Wald confidence regions over 1000 replications.
+Since $\mu$ is known, we assess the performance of A-SV and G-SV estimatiors by assessing coverage probabilities of $95\%$ Wald confidence regions over 1000 replications.
 Table~\ref{tab:var-coverage} shows that for each sample size, the $\hat{\Sigma}_G$ results in close to nominal coverage probability, whereas $\hat{\Sigma}_A$ yields critically low coverage.
@@
 It is evident that the locally centered estimator of $\Sigma$ severely underestimates the truth, leading to an overestimation of ESS.
-The GSV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS.
+The G-SV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS.
 \begin{figure}[htbp]
@@
 
-Consider the following family of bimodal bivariate distributions introduced by \cite{gelman1991note}, which term as a boomerang distribution.
+Consider the following family of bimodal bivariate distributions introduced by \cite{gelman1991note}, which we term as a boomerang distribution.
 For $A \geq 0$ and $B, C  \in \mathbb{R}$, the target density is
@@
 We consider two settings; in setting 1 we let
-$A = 1,\; B = 3,\; C = 8$ which results in well-separated models.
+$A = 1,\; B = 3,\; C = 8$ which results in well-separated modes.
 In setting 2, we let $A = 1, \; B = 10, \; C=7$ which yields in a boomerang shape for the contours.
@@
 Setting 2 is chosen specifically to illustrate that the locally and globally centered ACvFs perform similarly when the Markov chain moves freely across the state space.
-{\color{red} what is m here?}
-
+
+We run $m=5$ parallel Markov chains with starting points evenly distributed across the state space.
 For Setting 1, when the Markov chains have not been able to jump modes, locally-centered ACF severely underestimates autocorrelation.
-This is seen in the middle column in Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$.
+This is seen in the top-middle plot of Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$ (overlayed blue line).
 Somewhere between $n = 1000$ and $n = 10^4$, the Markov chains jump modes and it is only then that the locally-centered ACFs provide better estimates.
@@
 In setting 1, systematically, the G-SV estimator yields far superior coverage than the A-SV estimator for all values of $n$.
-Whereas for setting 2, the results are almost similar indicating the equivalence of A-SV and G-SV for fast mixing Markov chains.
+Whereas for setting 2, the results are almost similar indicating the equivalence of A-SV and G-SV estimator for fast mixing Markov chains.
 
@@
 
-Consider the sensor network localization problem discussed in \cite{ihler2005nonparametric}. The goal is to identify unknown sensor locations using noisy distance data. We use the data
-% This problem is specifically interesting in our case because the marginal posterior distribution for missing sensor locations is multi-modal for all locations. 
-%
+Consider the sensor network localization problem discussed in \cite{ihler2005nonparametric}.
+The goal is to identify unknown sensor locations using noisy distance data.
 We use the data and the model as specified by \cite{tak2018repelling}.
 There are four sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denotes the coordinates of the $i${th} sensor.
-Let $y_{ij} = (y_{ij})$ denotes the distance between the sensors $x_i$ and $x_j$ and if observed yields $z_{ij} = 1$, otherwise, $z_{ij} = 0$.
+Let $y_{ij} = (y_{ij})$ denotes the distance between the sensors $x_i$ and $x_j$ and if observed, yields $z_{ij} = 1$ otherwise, $z_{ij} = 0$.
 The complete model is then,
@@
     z_{ij} \mid x_1, ..., x_4 & \sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
-    y_{ij} \mid z_{ij} = 1, x_i,x_j &\sim N(\|x_i - x_j\|^2, \sigma^2)
+    y_{ij} \mid z_{ij} = 1, x_i,x_j &\sim N(\|x_i - x_j\|^2, \sigma^2)\,.
 \end{align*}
@@
       \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e4.pdf}    
-    \caption{Sensor: Trace plot of $x_{11}$ (left).
-Locally-centered ACF (solid orange) and G-ACF (solid blue) at $n = 5000$ (middle) and $n = 50000$ (right).
-Dashed lines are single-chain estimated ACFs.}
+    \caption{Sensor: Trace plot of $x_{11}$ (left) for two parallel chains.
+Average locally-centered ACF (solid orange) and G-ACF (solid blue) at $n = 5000$ (middle) and $n = 50000$ (right).
+Dashed lines are single-chain estimated ACFs (orange) and G-ACFs (blue).}
     \label{fig:sensor-trace}
@@
 Figure~\ref{fig:sensor-trace} also  plots locally and globally centered ACFs.
-As seen in previous examples, early estimates of locally-centered ACFs are must smaller than later estimates.
+As seen in previous examples, early estimates of locally-centered ACFs are much smaller than later estimates.
 The globally-centered ACFs, on the other hand are similar at small and large sample sizes.
 Figure~\ref{fig:sensor-frob_n_ess} presents the running plot of $\log \|{\Sigma}\|_F$ and $\log \textrm{ESS}/mn$ using A-SV and G-SV  estimators along with standard errors from $10$ replications.
-In both the plots, G-SV and $\widehat{\textrm{ESS}}_G/mn$ reaches stability significantly earlier than A-SV.
+In both the plots, G-SV estimator and $\widehat{\textrm{ESS}}_G/mn$ reach stability significantly earlier than A-SV estimator and $\widehat{\textrm{ESS}}_A/mn$.
 
@@
 % In this paper, we have chiefly focused on the usage of G-ACvF for estimating autocovariances in SVE; however the argument for a similar usage in mIS is straightforward.  
-Following \cite{dai:jon:2017}, it is easy to show that $\hat{\Upsilon}_{G,s}(k)$ are strongly consistent for $\Upsilon(k)$ and replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following \citep[][Lemma 5]{dai:jon:2017} will yield consistent overestimation of $\Sigma$ using a globally-centered version of the mIS estimator.
+It is easy to show that $\hat{\Upsilon}_{G,s}(k)$ is a strongly consistent estimators for $\Upsilon(k)$.
+Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following the proof of Theorem~2 in \citep{dai:jon:2017} will yield consistent overestimation of generalized variance $\abs{\Sigma}$ estimated using a globally-centered version of the mIS estimator.
+A valuable line of research would be to carry out the theoretical and experimental analysis of mIS estimators using G-ACvF.
 
@@
 This supplies readers with sufficient motivation to believe that the generalized variance for mIS constructed from $\hat{\Gamma}_G(k)$ not only consistently overestimates $\abs{\Sigma}$ but also upper-bounds the mIS from empirical single chain estimator of $\Gamma(k)$ for finite samples.
-An valuable line of research would be to prove these observations and carry out the theoretical analysis of mIS estimators using G-ACvF.
 %

### 2020-08-25 GaussianMix/output.R

@@ -1,5 +1,5 @@
 set.seed(1)
-library(rep.acf.ccf)
+library(multichainACF)
 
 
 log.density <- function(x, p, mu1, mu2, sd1, sd2){
@@ -8,22 +8,15 @@ log.density <- function(x, p, mu1, mu2, sd1, sd2){
 
 
 mh.mcmc <- function(start, p, mu1, mu2, sd1, sd2, N, h){
-
   X <- rep(0, N)
-  acc <- 0
   X[1] <- start
   for (i in 2:N){
     prop <- rnorm(1, mean = X[i-1], sd = 2)
     ratio <- log.density(prop, p, mu1, mu2, sd1, sd2) - log.density(X[i-1], p, mu1, mu2, sd1, sd2)
-
-    if(runif(1) < exp(ratio)){
-      X[i] <- prop
-      acc <- acc+1
-    } else {
-      X[i] <- X[i-1]
-    }
+    if(runif(1) < exp(ratio))
+      X[i] <- prop else
+        X[i] <- X[i-1]
   }
-  print(acc/N)
   return (X)
 }
 
@@ -38,11 +31,13 @@ sd2 <- 0.5
 
 chain1 <- mh.mcmc(start = -3, p, mu1, mu2, sd1, sd2, N, 1)
 chain2 <- mh.mcmc(start = 3, p, mu1, mu2, sd1, sd2, N, 1)
+mean(chain1)
+mean(chain2)
 mc.chain.list <- list(as.matrix(chain1), as.matrix(chain2))
 save(mc.chain.list, file = "gaussian-two_chains.Rdata")
 
-mean(chain1)
-mean(chain2)
+load(file = "gaussian-two_chains.Rdata")
+
 
 ##################################
 ######Trace plots for n=1e4#######
@@ -96,7 +91,7 @@ dev.off()
 m <- 2
 lag.max <- 50
 nsim1 <- 1e4
-nsim2 <- 5e4
+nsim2 <- 1e5
 ########################################
 
 x <- list()
@@ -108,8 +103,8 @@ for (i in 1:m){
 
 local.acf1 <- acf(x[[1]], type = "correlation", lag.max = lag.max, plot = FALSE)
 local.acf2 <- acf(y[[1]], type = "correlation", lag.max = lag.max, plot = FALSE)
-global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, graph = FALSE)[[1]]
[…]

### 2020-08-25 one_run.R

@@ -1,4 +1,4 @@
-library(rep.acf.ccf)
+library(multichainACF)
 
 ##########################################
 ##########################################
@@ -49,7 +49,7 @@ dev.off()
 
 lag.max <- 50
 nsim1 <- 1e4
-nsim2 <- 5e4
+nsim2 <- 1e5
 
 x <- list()
 y <- list()
@@ -62,8 +62,8 @@ for (i in 1:m){
 
 local.acf1 <- acf(as.matrix(x[[1]]), type = "correlation", lag.max = lag.max, plot = FALSE)
 local.acf2 <- acf(as.matrix(y[[1]]), type = "correlation", lag.max = lag.max, plot = FALSE)
-global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, graph = FALSE)[[1]]
-global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, graph = FALSE)[[1]]
+global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
+global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 
 #### Figure 2a
 pdf(file = "AllOut/gaussian-acf_hist.pdf", width = 8, height= 4)

### 2020-08-27 Paper/main.tex
Layer2 and a bit of Layer3
I will give it one last read today and then give it back to you.

@@
 
-% This gives us a full line break when we write a new paragraph
-% \usepackage[mathscr]{euscript}
-% \usepackage{tikz}
-% \newcommand*\circled[1]{\tikz[baseline=(char.base)]{
-%             \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
-% \newcommand{\indep}{\perp \!\!\! \perp}
-
 \title{Globally-centered autocovariances in MCMC}
@@
 Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth.
-For multiple chain MCMC sampling,  we propose a globally-centered estimate of the autocovariance that pools information from all Markov chains.
-We show the impact of these improved estimators in three aspects: (1) acf plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
+For multiple chain MCMC sampling,  we propose a globally-centered estimator of autocovariance function (G-ACvF) that pools information from all Markov chains.
+G-ACvF is also shown to correct the negative bias of single chain empirical autocovariance.
+We show the impact of this improved estimator in three aspects: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
+We have established the strong consistency of our improved asymptotic variance estimator, and obtained its large sample bias and variance.
 \end{abstract}
@@
 From their use in autocorrelation (ACF) plots to assessing Monte Carlo variability of estimators, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences from MCMC output.
-However, estimators of ACvF are only available for single-chain implementations, with multiple-chain version obtained by naive averaging.
+However, estimators of ACvF are only available for single-chain implementations, with parallel-chain version obtained by naive averaging.
 As we will demonstrate, this defeats the purpose of running parallel Markov chains from dispersed starting values.
@@
 For single-chain MCMC runs, the estimator $\hat{\Gamma}_s(k)$ is used to construct ACF plots, to estimate the long-run variance of Monte Carlo estimators \citep{hannan:1970,dame:1991}, and to estimate effective sample size (ESS) \citep{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
-However, there is no unified approach to constructing estimators of $\Gamma(k)$ for multiple-chain implementations.
+However, there is no unified approach to constructing estimators of $\Gamma(k)$ for parallel-chain implementations.
 Specifically, parallel MCMC chains are often spread across the state space so as to adequately capture high density areas.
@@
 and let $\Phi^{(1)}$ be denoted by $\Phi$.  The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
+
+{\color{orange} I don't think that the RHS below is correct. In the formulation below, $o(n^{-2})$ is be $o(n^{-1})$}
 
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is continuous at $0$ at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} w(k/b_n) < \infty$.
+The lag window $w(x)$ is continuous at $0$ at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} \abs{w(k/b_n)} < \infty$.
 \end{ass}
@@
 Let $w^* = (1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1}, ~0, ~w_{n-1}, \dots, w_1)^T$ and set $C(w^*)$ to be a symmetric circulant matrix such that the matrix truncation $C(w^*)_{1:n, 1:n} = T(w)$.
+Let $M_{(j)}$ denote the $j$th column of matrix $M$ and $v^{(i)}$ denote the $i$th element of the vector $v$.
 With inputs $C(w^*)$ and $A_s$, Algorithm~\ref{algo:herberle} produces $\hat{\Sigma}_s$ exactly.
@@
 In all the examples we are interested in estimating the mean of the stationary distribution $\mu$, so $g$ is the identity function.
-The batch size $b_n$ is obtained from the function \texttt{batchSize} from \texttt{R} package \texttt{mcmcse}.
+The batch size $b_n$ is obtained from the function \texttt{batchSize} from \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.
 
@@
 \label{lemma: brownian}
-(\cite{csorgo2014strong}).
-Suppose the conditions of Theorem~\ref{thm:kuelbs} hold, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}$ and $\forall i = 1, ..., p$
+(\cite{csorgo1981strong}).
+Suppose the conditions of Theorem~\ref{thm:kuelbs} hold, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}(\epsilon)$ and $\forall i = 1, ..., p$
 
@@
 \[
-\sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \;and
+\sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \; \textrm{and}
 \]
@@
 % \section{Proof of Theorems} \label{appendix:A}
+
+For the purpose of generalizing summations for positive and negative lags in the following proofs, we define the sets $I_k, J_{k1} \text{ and } J_{k2}$ as $ I_k := \{1, \dots, n-k\}, J_{k1} := \{n-k+1, \dots , n\}, J_{k2} := \{1, \dots, k\}$ for $k > 0$ and  $I_k := \{1-k, \dots, n\}, J_{k1} := \{1, \dots , -k\}, J_{k2} := \{n+k+1, \dots, n\}$ for $k < 0$.
+For $k=0$, $J_{k1}$ and $J_{k2}$ are empty sets and $I_k := \{1, \dots, n\}$.
+Notice that the empirical autocovariance estimator at lag-$k$ requires a summation over $I_k$.
 
@@
 \begin{align*}
-\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
-    &= \left[\dfrac{1}{n} \sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\
-    & \quad +  \left[\dfrac{1}{n} \sum_{t=n-|k|+1}^{n}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-|k|}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{n}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
+\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
+    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\
+    & \quad +  \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
 \end{align*}
@@
 where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$.
-Under the assumption of stationarity, we will study the expectations of the each of the above terms.
+Under the assumption of stationarity, we will study the expectations of each of the above terms.
 Without loss of generality, consider $A_{11}$,
@@
 %
-As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$.
-Using \eqref{eq:priestly}, \eqref{eq:acf_2}, \eqref{eq:acf_3}, and \eqref{eq:acf_4} in \eqref{eq:acf_breakdown},
+Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
 \begin{align*}
     & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
-    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] + \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
 \end{align*}
@@
  \begin{equation} \label{eq:G-ACF_expec_breakdown}
-     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
+     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2\,.
  \end{equation}
@@
 \begin{align*}
-    O_1 &= -\dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
+    O_1 &= -\dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
     O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
@@
 We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$.
-Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\mathcal{O}}(1/n)$.
+Here, $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\mathcal{O}}(1/n)$.
 For a diagonal element of $\Gamma$,
@@
 & \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
-& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
+& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
 \end{align*}
@@
 \begin{align*}
-    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-|k|}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T \\ 
+    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t \in I_k}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T \\ 
     \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Upsilon}_s(k) \,.
@@
 \[
-\tilde{\Sigma} = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
+\tilde{\Sigma}_A = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
 \]
@@
 \begin{align*}
-  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t=1}^{n-|k|}\dfrac{1}{n}\left[ \left(Y_{st}-\mu_g \right)_i   \left(\mu_g-\bar{\bar{Y}} \right)_j +    \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j \right]\right\}\,, \\
-  %
-M_2 &= \left(\mu_g-\bar{\bar{Y}} \right)_i   \left(\mu_g-\bar{\bar{Y}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\,.
+  M_1 & = \dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{\sum\limits_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum\limits_{t \in I_k}\dfrac{1}{n}\left[ \left(Y_{st}-\mu_g \right)_i   \left(\mu_g-\bar{\bar{Y}} \right)_j +    \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j \right]\right\}\,, \\
+  %
+M_2 &= \left(\mu_g-\bar{\bar{Y}} \right)_i   \left(\mu_g-\bar{\bar{Y}} \right)_j\sum\limits_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\,.
 \end{align*}
@@
 \begin{lemma} \label{lemma:G-SVE_breakdown}
-For the G-SVE estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}^{ij} + M_1 + M_2$ and 
+For the G-SVE estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
 \[
@@
 \]
-where
-\begin{align*}
-    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
+where for some constant $C$,
+\begin{align*}
+    g_1(n) &= (4+C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
+    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
 \end{align*}
@@
 \begin{align*}
-\hat{\Sigma}_{G}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(Y_{st}-\bar{\bar{Y}} \right)_i \left(Y_{s(t+k)}-\bar{\bar{Y}} \right)_j\\
-% &= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|} \left[  \left\{\left(X_{st}-\mu_g \right)_i + \left(\mu_g-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu_g \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_j \right \} \right]\\
-&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left[ \left(Y_{st}-\mu_g \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j+  \left(Y_{st} - \mu_g \right)_i    \left(\mu_g - \bar{\bar{Y}} \right)_j \right.
+\hat{\Sigma}_{G}^{ij} &= \dfrac{1}{m}\sum_{s=1}^{m} \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k} \left(Y_{st}-\bar{\bar{Y}} \right)_i \left(Y_{s(t+k)}-\bar{\bar{Y}} \right)_j\\
+% &= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-k} \left[  \left\{\left(X_{st}-\mu_g \right)_i + \left(\mu_g-\bar{\bar{X}} \right)_i \right \}  \left\{ \left(X_{s(t+k)}-\mu_g \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_j \right \} \right]\\
+&= \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k}  \left[ \left(Y_{st}-\mu_g \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j+  \left(Y_{st} - \mu_g \right)_i    \left(\mu_g - \bar{\bar{Y}} \right)_j \right.
 \\
 & \quad + \left. \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j + \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(\mu_g-\bar{\bar{Y}}  \right)_j  \right]\\
-& = \tilde{\Sigma}^{ij} + \left[(\mu_g-\bar{\bar{Y}})_i(\mu_g-\bar{\bar{Y}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] \\ 
-& \quad  + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|}  \left[\dfrac{1}{n} \left(Y_{st} - \mu_g \right)_i \left(\mu_g - \bar{\bar{Y}} \right)_j + \dfrac{1}{n} \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j \right] \\
-& = \tilde{\Sigma}^{ij} + M_1 + M_2\,.
+& = \tilde{\Sigma}^{ij}_A + \left[(\mu_g-\bar{\bar{Y}})_i(\mu_g-\bar{\bar{Y}})_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] \\ 
+& \quad  + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\sum_{t \in I_k}  \left[\dfrac{1}{n} \left(Y_{st} - \mu_g \right)_i \left(\mu_g - \bar{\bar{Y}} \right)_j + \dfrac{1}{n} \left(\mu_g-\bar{\bar{Y}} \right)_i  \left(Y_{s(t+k)}-\mu_g \right)_j \right] \\
+& = \tilde{\Sigma}^{ij}_A + M_1 + M_2\,.
 \end{align*}
@@
 \[
-\left|\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
+\left|\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}_{A}^{ij}  \right| = |M_1 + M_2| \leq |M_1| + |M_2|\,.
 \]
@@
 \begin{align*}
-  \|\bar{Y}_s - \mu_g\|_{\infty} & \leq \|\bar{Y}_s - \mu_g\| = \dfrac{1}{mn}\left\|\sum_{t=1}^{n}Y_{st} - n\mu_g\right\| \\
+  \|\bar{Y}_s - \mu_g\|_{\infty} & \leq \|\bar{Y}_s - \mu_g\| = \dfrac{1}{n}\left\|\sum_{t=1}^{n}Y_{st} - n\mu_g\right\| \\
   % &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu_g \pm L B(n) \right\|\\
@@
 & |M_1| \\ 
-   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu_g \right)_i  \left(\mu_g-\bar{\bar{X}} \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu_g \right)_j\right]\right\}\right| \\
-   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-|k|} \left(X_{st} - \mu_g \right)_i  \left(\mu_g - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-|k|} \left(\mu_g-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu_g \right)_j\right|} \right]\right\}\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t=1}^{n-|k|}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t=1}^{n-|k|}(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
-    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{n-|k|}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
+   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-k} \dfrac{1}{n}\left[ \left(X_{st} - \mu_g \right)_i  \left(\mu_g-\bar{\bar{X}} \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu_g \right)_j\right]\right\}\right| \\
+   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-k} \left(X_{st} - \mu_g \right)_i  \left(\mu_g - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-k} \left(\mu_g-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu_g \right)_j\right|} \right]\right\}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t \in I_k}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t \in I_k }(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
+    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
     &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \\
-    & \quad \times \sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t=n-|k|+1}^{n}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t=1}^{|k|}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
-    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t=n-|k|+1}^{n}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t=1}^{|k|}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
-    & \; \;+ 2(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_1 - \mu_g\|_{\infty}\,.
+    & \quad \times \sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g)\right\|_{\infty} \right]\\
+    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
+    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
+    & \; \;+ 2(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_h - \mu_g\|_{\infty} \textrm{ for some } h \in \{1, \dots, m\} \,.
 \end{align*}
@@
 |M_1|
-    & < 2\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] \right]  + 2(2b_n - 1) \|\bar{Y}_1 - \mu_g\|_{\infty} \\
-    &\leq 2(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_1 - \mu_g\|_{\infty}  \right]\\
+    & < 2\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right]  + (2b_n - 1) \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
+    &\leq 2(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
     % & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu_g\|_{\infty}\\
@@
 \begin{align*}
-   |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu_g - \bar{\bar{Y}} \right)_i  \left(\mu_g - \bar{\bar{Y}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
-    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{|k|}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+   |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu_g - \bar{\bar{Y}} \right)_i  \left(\mu_g - \bar{\bar{Y}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
+    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
     % &= b_n\|\bar{\bar{X}} - \mu_g\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
@@
     % & \leq Cb_n\|\bar{\bar{X}} - \mu_g \|^2 \\ 
-    & \leq Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 \quad \text{ (by \eqref{eq:xbarbar_bound})} \numberthis \label{eq:strong_consis_term-2} \,.
+    & \leq Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 \quad \text{ for some constant $C$ (by \eqref{eq:xbarbar_bound})} \numberthis \label{eq:strong_consis_term-2} \,.
 \end{align*}
@@
 \begin{align*}
-|M_1 + M_2  & \leq |M_1| + |M_2|
+|M_1 + M_2|  & \leq |M_1| + |M_2|
   % & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2 + Cb_n\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2\\
@@
 \end{align*}
-Under our assumptions, 
-$b_n\log \log n /n \to 0$ and $\psi(n) = o(\sqrt{n \log \log n})$. Consequently, 
+Under the assumptions of Theorem~\ref{thm:kuelbs}, $\psi(n) = o(n^{1/2})$.
+Using Law of Iterative Logarithms (LIL), a tighter bound for $\psi(n)$ is given by \cite{stra:1964} as $o(\sqrt{n\log \log n})$.
+We have already assumed that $b_n \log \log n / n \to 0$ as $n \to \infty$.
+Consequently,
 $b_n \psi^2(n)/n^2 \to 0$, $\psi^2(n)/n^2 \to 0$, ${b_n\psi(n)\sqrt{n\log \log n}/n^2} \to 0$, and $\psi(n) \sqrt{n \log \log n}/n^2 \to 0$.
 Thus, $g_1(n), g_2(n)$ and $g_3(n) \to 0$ as $n \to \infty$.
-{\color{orange} MA: Should we add a footnote here telling why $\phi(n)=o(\sqrt{n \log \log n})?$ It was earlier stated explicitly in Assumption-1 which is not Theorem-1.}
-
 \end{proof}
@@
 \begin{align*}
-\tilde{\Sigma}^{ij}
-    % & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(X_{st} - \mu_g \right)_i  \left(X_{s(t + k)} - \mu_g \right)_j\\
-    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}  \left(Y_{st} \pm \bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t + k)} \pm \bar{Y}_s - \mu_g \right)_j\\
-    & = \hat{\Sigma}_{SV}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i   \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right]\\
+\tilde{\Sigma}_{A}^{ij}
+    % & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-k}  \left(X_{st} - \mu_g \right)_i  \left(X_{s(t + k)} - \mu_g \right)_j\\
+    & = \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k}  \left(Y_{st} \pm \bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t + k)} \pm \bar{Y}_s - \mu_g \right)_j\\
+    & = \hat{\Sigma}_{A}^{ij} + \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k}\left[ \left(Y_{st} - \bar{Y}_s \right)_i   \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right]\\
     & \quad + \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{Y}_s - \mu_g \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\\
-    & = \hat{\Sigma}_{SV}^{ij} + N_1 + N_2 \,,
+    & = \hat{\Sigma}_{A}^{ij} + N_1 + N_2 \,,
 \end{align*}
@@
 \begin{align*}
-N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right]\\
-N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{Y}_s - \mu_g \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\,.
-\end{align*}
-%
-Using the above and  Lemma~\ref{lemma:G-SVE_breakdown}, 
-\begin{align*}
-\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
+N_1 & = \dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t \in I_k}  \left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right]\\
+N_2 & = \left[\dfrac{1}{m}  \sum_{s=1}^{m}  \left(\bar{Y}_s - \mu_g \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right]  \left[\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left(1 - \dfrac{\abs{k}}{b_n}\right) \right]\;.
+\end{align*}
+%
+Using the above breakdown and  Lemma~\ref{lemma:G-SVE_breakdown}, 
+\begin{align*}
+\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
 \end{align*}
@@
 By the strong consistency of single-chain SV estimator, the first term goes to 0 with probability 1 and by Lemma~\ref{lemma:G-SVE_breakdown}, the third term goes to 0 with probability 1 as $n \to \infty$.
-It is left to show that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1
-%
-\begin{align*}
-|N_1| & = \left|\dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t=1}^{n-|k|}  \left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right] \right|\\
-& \leq \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right| \\
-& \quad + \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right] \right|
+It is left to show that $|N_1| \to 0$ and $|N_2| \to 0$ with probability 1.
+Consider,
+%
+\begin{align*}
+|N_1| & = \left|\dfrac{1}{m}\sum_{s=1}^{m}  \sum_{k=-b_n+1}^{b_n-1}  w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}  \sum_{t \in I_k}  \left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j + \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right] \right|\\
+& \leq \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right| \\
+& \quad + \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k}\left[ \left(\bar{Y}_s - \mu_g \right)_i  \left(Y_{s(t+k)} - \bar{Y}_s \right)_j\right] \right|\,.
 \end{align*}
@@
 \begin{align*}
-    & \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right| \\
-    % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu_g \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{|k|} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left| w\left(\dfrac{k}{b_n}\right) \right| \dfrac{ \left|  \left(\bar{Y}_s - \mu_g \right)_j \right| }{n} \left[ \left|\sum_{t=1}^{|k|} \left(\mu_g - Y_{st} \right)_i \right| + \abs{k} \left|\left(\bar{Y}_s - \mu_g \right)_i \right|\right]\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(\mu_g - Y_{st} \right) + \abs{k} \left(\bar{Y}_s - \mu_g \right)\right\|_{\infty}\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left(\left\|\sum_{t=1}^{|k|}  \left(Y_{st} - \mu_g \right)\right\|_{\infty} + \abs{k}\|\bar{Y}_s - \mu_g\|_{\infty} \right)\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t=1}^{|k|} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.
+    & \left| \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t \in I_k}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right| \\
+    % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right)  \right|\dfrac{  \left| \left(\bar{X}_s - \mu_g \right)_j \right| }{n} \left[ \left|  \sum_{t=1}^{k} \left(\bar{X}_s - X_{st} \right)_i  \right| \right]\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left| w\left(\dfrac{k}{b_n}\right) \right| \dfrac{ \left| \left(\bar{Y}_s - \mu_g \right)_j \right| }{n} \left| \sum_{t \in J_{k1}} \left(\mu_g - Y_{st} \right)_i  + \abs{k} \left(\bar{Y}_s - \mu_g \right)_i \right|\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}  \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t \in J_{k1}} \left(\mu_g - Y_{st} \right) + \abs{k} \left(\bar{Y}_s - \mu_g \right)\right\|_{\infty}\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left(\left\|\sum_{t \in J_{k1}}  \left(Y_{st} - \mu_g \right)\right\|_{\infty} + \abs{k}\|\bar{Y}_s - \mu_g\|_{\infty} \right)\\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t \in J_{k1}} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.
 \end{align*}
@@
 \begin{align*}
-    & \left|\dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-|k|}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right|\\
-   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2\\
-   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2 \\
-   &  \leq   \left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
+    & \left|\dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-k}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right|\\
+   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2\\
+   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2 \\
+   &  \leq   \left(2b_n - 1 + \dfrac{cb_n^2}{n} - \dfrac{cb_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
 \quad  \text{(by \eqref{eq:xbars_bound})}
@@
 %\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right]
-% &  = \left(1- \dfrac{|k|}{n}\right)\Upsilon(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m} \\
+% &  = \left(1- \dfrac{k}{n}\right)\Upsilon(k) - \dfrac{k}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m} \\
 % & = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + \mathcal{O} \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
@@
  \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
-    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Upsilon(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
-    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Upsilon(k)\right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\
+    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{k}{n}\right)\Upsilon(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
+    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k)\right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\
     & = P_1 + P_2\,,
@@
 \begin{align*}
-    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Upsilon(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Upsilon(k) \textrm{ and }\\   
+    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Upsilon(k) \textrm{ and }\\   
     P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
@@
 \label{eq:P1_decomp}
-P_1 = -\sum_{|k|\geq n}\Upsilon(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Upsilon(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Upsilon(k)\,.  
+P_1 = -\sum_{\abs{k}\geq n}\Upsilon(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{n}\right)\right)\Upsilon(k)\,.  
 \end{equation}
@@
 \begin{align*}
- {-\sum_{|k|\geq n}\Upsilon(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Upsilon(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Upsilon(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
-\end{align*}
-%
-since $\sum_{|k|\geq n}|k|^q \Upsilon(k)  < \infty$. Next,
-%
-\begin{align*}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Upsilon(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Upsilon(k)  \,.
+ {-\sum_{\abs{k}\geq n}\Upsilon(k)} &\leq  \sum_{\abs{k}\geq n} \abs{\dfrac{k}{n}}^q   \Upsilon(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{k\geq n}\abs{k}^q  \Upsilon(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
+\end{align*}
+%
+since $\sum_{\abs{k}\geq n}\abs{k}^q \Upsilon(k)  < \infty$. Next,
+%
+\begin{align*}
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}\abs{k} \Upsilon(k)  \,.
 \end{align*}
@@
 \begin{align*}
-\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Upsilon(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Upsilon(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
+\dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k}  \Upsilon(k) &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k}^q  \Upsilon(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} c\sum_{k = -n+1}^{n-1}\abs{k}^q  \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
 \end{align*}
@@
 \begin{align*}
-   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Upsilon(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Upsilon(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
+   \dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k} \Upsilon(k)  &\leq c\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Upsilon(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} c \sum_{k =-n+1}^{n-1}\abs{k}^q \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
 \end{align*}
@@
 \label{eq:P1_second}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Upsilon(k) = o \left(\dfrac{1}{b_n^q} \right)
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Upsilon(k) = o \left(\dfrac{1}{b_n^q} \right)
 \end{equation}
@@
 \begin{align*}
-     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Upsilon(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Upsilon(k) \\
+     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Upsilon(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{k}{b_n}\right)\right)}|k|^q \Upsilon(k) \\
      & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
@@
 We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$.
-We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
-  \begin{align*}
-      &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
-      & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right) W_n \\
+We will find an upper bound and prove that it is $o\left(b_n^{-q}\right)$:
+  \begin{align*}
+      &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)( O_1 + O_2) \\
+      & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)}\\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)}\\
       &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
@@
 \begin{align*}
-    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
+    g_1(n) &= (4+C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
+    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
 \end{align*}
@@
  &\left| \hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right|\\
- & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t=1}^{n-|k|}   \left[ \left( \dfrac{(Y_{st} - \mu_g)_i(\mu_g-\bar{\bar{Y}})_j}{n}\right)+ \left(\dfrac{(\mu_g-\bar{\bar{Y}})_i(Y_{s(t+k)}-\mu_g)_j}{n}\right) \right] \right.\\
+ & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t \in I_k}   \left[ \left( \dfrac{(Y_{st} - \mu_g)_i(\mu_g-\bar{\bar{Y}})_j}{n}\right)+ \left(\dfrac{(\mu_g-\bar{\bar{Y}})_i(Y_{s(t+k)}-\mu_g)_j}{n}\right) \right] \right.\\
 & \quad \quad  \left. + (\mu_g-\bar{\bar{Y}})(\mu_g-\bar{\bar{Y}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
@@
 & \leq \left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right)^2 \, I(0 \leq n \leq N_0) +  \left(D^2g_1(n) + Dg_2(n) + g_3(n) \right)^2 I(n > N_0)\\
-& := g_n^*(X_{11}, \dots, Y_{1n}, \dots, Y_{m1}, \dots, Y_{mn})\,.
+& := g_n^*(Y_{11}, \dots, Y_{1n}, \dots, Y_{m1}, \dots, Y_{mn})\,.
 \end{align*}
@@
 This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature.
-Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second component.
+Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second and third component.
 We will report the ACF plots for component-2.
-Similar behavior is observed for ACF plots of other components as well
+Similar behavior is observed for ACF plots of other components as well.
 
@@
 Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF in estimating the true autocorrelations.
-G-ACF gives a more realistic and accurate estimation of autocorrelations in almost ten times lesser chain length.
+G-ACF gives a more realistic and accurate estimation of autocorrelations in almost ten times lesser samples per chain.
 

### 2020-08-28 Paper/main.tex
Layer-3

@@
 \begin{abstract}
-Autocovariances are the fundamental quantity in many features of Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain.
+Autocovariances are the fundamental quantity of interest in many features of Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain.
 Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth.
@@
 We show the impact of this improved estimator in three aspects: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
-We have established the strong consistency of our improved asymptotic variance estimator, and obtained its large sample bias and variance.
+We also establish the strong consistency of our improved asymptotic covariance estimator under weak conditions, and obtain its large sample bias and variance.
 \end{abstract}
@@
 In this section we consider three different target distributions and sample $m$ parallel Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators.
-We will make the following three comparisons - (1) A-ACF vs G-ACF through ACrF plots; (2) A-SVE vs G-SVE; (3) $\widehat{\textrm{ESS}}_G$ vs $\widehat{\textrm{ESS}}_A$.
+We will make the following three comparisons - (1) ACF vs G-ACF estimator, (2) SV vs G-SV estimator, and (3) $\widehat{\textrm{ESS}}_A$ vs $\widehat{\textrm{ESS}}_G$.
 The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence interval in cases where the true mean $\mu$ is known.
@@
     \end{tabular}
-    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SVE and G-SVE.}
+    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SV and G-SV estimator.}
     \label{tab:var-coverage}
@@
       \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
-    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV.(Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV.}
+    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV estimator. (Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV estimator.}
     \label{fig:var-frob_n_ess}
@@
 \hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
-    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\
-    & \quad +  \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
+    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
+    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
 \end{align*}
@@
     & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
-    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] + \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(+ \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
@@
 \begin{lemma} \label{lemma:G-SVE_breakdown}
-For the G-SVE estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
+Let Assumption~\ref{ass:lag_window} holds, then for the G-SV estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
 \[
@@
 \begin{align*}
-    g_1(n) &= (4+C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
+    g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
+    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
 \end{align*}
@@
    % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-k} \left(X_{st} - \mu_g \right)_i  \left(\mu_g - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-k} \left(\mu_g-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu_g \right)_j\right|} \right]\right\}\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t \in I_k}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t \in I_k }(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
-    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \\
+    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\left[ \dfrac{1}{n}\left|\sum_{t \in I_k}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t \in I_k }(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
+    & \leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
+    &\leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \\
     & \quad \times \sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g) \right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g) - n(\bar{Y}_s - \mu_g)\right\|_{\infty} \right]\\
-    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
-    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
-    & \; \;+ 2(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_h - \mu_g\|_{\infty} \textrm{ for some } h \in \{1, \dots, m\} \,.
+    &\leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
+    & \leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
+    & \; \;+ 2c(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_h - \mu_g\|_{\infty} \textrm{ for some } h \in \{1, \dots, m\} \,.
 \end{align*}
@@
 |M_1|
-    & < 2\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right]  + (2b_n - 1) \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
-    &\leq 2(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
+    & < 2c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right]  + (2b_n - 1) \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
+    &\leq 2c(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
     % & \quad  + 2(2b_n - 1)\|\bar{\bar{X}} - \mu_g\|_{\infty}\\
-    & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,.
+    & \leq 4c(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,.
 \numberthis \label{eq:strong_consis_term-1}
@@
 \begin{align*}
-    g_1(n) &= (8 + C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(8 + C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(8 + C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]\,.
+    g_1(n) &= (8c + C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2}\\
+    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(8c + C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(8c + C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right]\,.
 \end{align*}
@@
     & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1} \left|w\left(\dfrac{k}{b_n}\right) \right|\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left(\left\|\sum_{t \in J_{k1}}  \left(Y_{st} - \mu_g \right)\right\|_{\infty} + \abs{k}\|\bar{Y}_s - \mu_g\|_{\infty} \right)\\
-    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t \in J_{k1}} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.
+    & \leq \dfrac{c}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t \in J_{k1}} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{c}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.
 \end{align*}
@@
     & \left|\dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\dfrac{1}{n}\sum_{t=1}^{n-k}\left[ \left(Y_{st} - \bar{Y}_s \right)_i  \left(\bar{Y}_s - \mu_g \right)_j \right] \right|\\
-   &  < \dfrac{1}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2\\
-   &  < \dfrac{(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2 \\
-   &  \leq   \left(2b_n - 1 + \dfrac{cb_n^2}{n} - \dfrac{cb_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
+   &  < \dfrac{c}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right] + \dfrac{c}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2\\
+   &  < \dfrac{c(2b_n-1)}{m}\sum\limits_{s=1}^{m}\|\bar{Y}_s - \mu_g\|_{\infty}\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right] + \dfrac{c}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n}\|\bar{Y}_s - \mu_g\|_{\infty}^2 \\
+   &  \leq   c\left(2b_n - 1 + \dfrac{b_n^2}{n} - \dfrac{b_n}{n}\right)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}}{n}  \right]^2  \to 0\,.
 \quad  \text{(by \eqref{eq:xbars_bound})}
@@
 where both $O_1 \textrm{ and } O_2$ are the small order terms where $O_1 = n^{-1}\abs{k} \mathcal{O}(n^{-1}) \text{ and } O_2 = \mathcal{O}(n^{-1})$.
-By our assumptions, $\sum_{h=-\infty}^{\infty}\Upsilon(h) < \infty$.
-Consider the G-SVE estimator,
+By our assumptions, $\sum_{k=-\infty}^{\infty}\Upsilon(k) < \infty$.
+For a truncation point $b_n$, $w(k/b_n)=0$ for all $\abs{k} > b_n$.
+Therefore, SV estimator can be written as a weighted sum of estimated autocovariances from lag $-n+1$ to $n-1$.
+Consider the G-SV estimator,
 \begin{align*}
@@
 \end{equation}
-Further, we have defined $g_1(n), g_2(n), g_3(n)$ such that as $n \to \infty$,
-\begin{align*}
-    g_1(n) &= (4+C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
-    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
-\end{align*}
-%
 We have shown from the proof of strong consistency that,
@@
  & \leq \dfrac{1}{m} \sum_{s=1}^m \left| \sum_{k=-b_n+1}^{b_n-1} w \left(\dfrac{k}{b_n} \right) \sum_{t \in I_k}   \left[ \left( \dfrac{(Y_{st} - \mu_g)_i(\mu_g-\bar{\bar{Y}})_j}{n}\right)+ \left(\dfrac{(\mu_g-\bar{\bar{Y}})_i(Y_{s(t+k)}-\mu_g)_j}{n}\right) \right] \right.\\
-& \quad \quad  \left. + (\mu_g-\bar{\bar{Y}})(\mu_g-\bar{\bar{Y}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,.
-\end{align*}
+& \quad \quad  \left. + (\mu_g-\bar{\bar{Y}})(\mu_g-\bar{\bar{Y}})^T\sum_{k=-b_n+1}^{b_n-1}\left(\dfrac{n-|k|}{n}\right)w\left(\dfrac{k}{n}\right) \right|  < D^2g_1(n) + Dg_2(n) + g_3(n)\,,
+\end{align*}
+where $g_1(n), g_2(n), g_3(n)$ are defined such that as $n \to \infty$,  $g_1(n), g_2(n), g_3(n) \to 0$.
+%\begin{align*}
+%   g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
+%    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
+%    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
+%\end{align*}
+%
 
@@
 Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second and third component.
-We will report the ACF plots for component-2.
-Similar behavior is observed for ACF plots of other components as well.
+We report the ACF plots for the second component component only, however, similar behavior is observed in ACF plots of other components as well.
 
@@
     \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
-    \caption{Trace plot for second (left) and third (right) component of two chains started from random points.The two colors denote the two different chains.}
+    \caption{Trace plot for second (left) and third (right) component of two chains started from random points. The two colors denote the two different chains.}
     \label{fig:poisson-trace}
@@
       \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
-    \caption{Change point: ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for $n = 1000$ (left) and $n = 10000$ (right).}
+    \caption{Change point: ACF plots using local-centering (left) and global-centering (right) for $m=2$ parallel Markov chains.
+The individual chains are shown through dashed lines and average over $m$ chains is the solid line.
+The chain lengths are $n = 1000$ (top row) and $n = 10000$ (bottom row).}
     \label{fig:poisson-acf}
@@
 
-Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF in estimating the true autocorrelations.
+Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF against locally-centered ACF in estimating the autocorrelations.
+For a chain length of $n=1000$, locally-centered ACF gives a false sense of security about the Markov chains whereas in reality, the process is highgly correlated.
 G-ACF gives a more realistic and accurate estimation of autocorrelations in almost ten times lesser samples per chain.
@@
 
-    \caption{Crawling: ACF (left) and G-ACF (right) for individual chains and average over $m$ chains for $n = 1000$ (left) and $n = 10000$ (right).}
+    \caption{Crawling:  ACF plots using local-centering (left) and global-centering (right) for $m=2$ parallel Markov chains.
+The individual chains are shown through dashed lines and average over $m$ chains is the solid line.
+The chain lengths are $n = 100$ (top row) and $n = 1000$ (bottom row).}
     \label{fig:magnolia-acf}
@@
 
-We believe that the students from different races engage in a "selective networking" which might cause formation of clusters in the network wherein students within a cluster engage more with each other than with the students outside it.
-We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group.
-Figure~\ref{fig:magnolia-acf} shows the ACF and G-ACF plots for the third feature at two different simulation sizes.
-As evident, G-ACF displays a clear advantage over ACF in just $n=100$ samples.
+We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking" which might cause formation of clusters in the social network.
+We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group, especially their grades.
+Due to cluster formation in the network, a Markov chain will land on students within a cluster more often than on students outside it.
+As a consequence, the sample averages for the two chains will differ for a relatively shorter chain length.
+
+Figure~\ref{fig:magnolia-acf} shows the ACF plots for the \textit{grade} feature at two different simulation sizes for $m=2$ parallel Markov chains.
+For a shorter chain length, both the chains have explored different clusters and as a consequence, the local and global mean do not agree.
+Regardless, G-ACF displays a clear advantage over locally-centered ACF for a chain length of $n=100$ samples whereas the latter takes $n=1000$ samples to reach the truth.
 

### 2020-08-30 Boomerang/acf_plots.R
ACF plots using multichainACF

@@ -1,6 +1,6 @@
 set.seed(1)
 source("functions.R")
-library(rep.acf.ccf)
+library(multichainACF)
 
 #######################################
 ##### Setting-1
@@ -26,6 +26,8 @@ for (i in 1:m){
 }
 global.mean <- global.mean/m
 save(mc.chain.list, file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
+
+load(file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
 component <- 1
 lag.max <- 50
 
@@ -41,10 +43,10 @@ for (i in 1:m){
   y[[i]] <- mc.chain.list[[i]][1:nsim2,]
 }
 
-global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
-global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
-local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
-local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
+global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, plot = FALSE)$"avgACF"
+global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, plot = FALSE)$"avgACF"
+local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, plot = FALSE)$"avgACF"
+local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, plot = FALSE)$"avgACF"
 
 pdf(file = paste(paste("Out/", A, B, C, "/boom-acf", A, B, C, sep = "_"), ".pdf", sep = ""), width = 10, height = 4)
 par(mfrow = c(1,2))
@@ -63,8 +65,10 @@ m <- 5
 A <- 1
 B <- 10
 C <- 7
-start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
 
+################ for geneting chains. Don't run ###########################
+start <- matrix(0, nrow = m, ncol = 2)  #only depends on C                #
+                                                                          #
[…]

### 2020-08-30 MagnoliaNetwork/acf_plots.R

@@ -1,5 +1,5 @@
 
-library(rep.acf.ccf)
+library(multichainACF)
 source("functions.R")
 library(ergm)
 
@@ -28,6 +28,8 @@ for(i in 1:m){
 }
 
 save(mc.chain.list, file = "Out/magnolia-two_chains.Rdata")
+
+load(file = "Out/magnolia-two_chains.Rdata")
 component = 3
 
 ########################################
@@ -41,8 +43,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/magnolia-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 #######################################
@@ -56,6 +58,6 @@ for (i in 1:m){
 
 pdf(file = paste("Out/magnolia-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()

### 2020-08-30 PoissonChange/acf_plots.R

@@ -1,6 +1,6 @@
 set.seed(1)
 library("MCMCpack")
-library(rep.acf.ccf)
+library(multichainACF)
 load("mida.rda")
 
 c0 <- 13
@@ -34,8 +34,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/poisson-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 ### ncrop = 1e4

### 2020-08-30 SensorNetwork/acf_plots.R

@@ -1,5 +1,5 @@
 set.seed(1)
-library(rep.acf.ccf)
+library(multichainACF)
 source("functions.R")
 ######## Data
 
@@ -81,9 +81,9 @@ for (i in 1:m){
 
 
 pdf(file = "Out/sensor-acf_n5e3.pdf", height = 4, width = 4)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", col = "darkorange")
 par(new = TRUE)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 
@@ -97,9 +97,9 @@ for (i in 1:m){
 
 
 pdf(file = "Out/sensor-acf_n5e4.pdf", height = 4, width = 4)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", col = "darkorange")
 par(new = TRUE)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 

### 2020-08-30 VAR-1/acf_plots.R

@@ -1,6 +1,6 @@
 set.seed(10)
 source("functions.R")
-library(rep.acf.ccf)
+library(multichainACF)
 
 
 ######################################
@@ -71,8 +71,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
-local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
+local.acf <- globalACF(x, type = "correlation", component = 1, mean="local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
@@ -92,8 +92,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
-local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
+local.acf <- globalACF(x, type = "correlation", component = 1, mean="local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))

### 2020-08-30 Boomerang/acf_plots.R
Revert "ACF plots using multichainACF"
This reverts commit d727ddd0f751ccae70b2352c2d0ed53226978abd.

@@ -1,6 +1,6 @@
 set.seed(1)
 source("functions.R")
-library(multichainACF)
+library(rep.acf.ccf)
 
 #######################################
 ##### Setting-1
@@ -26,8 +26,6 @@ for (i in 1:m){
 }
 global.mean <- global.mean/m
 save(mc.chain.list, file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
-
-load(file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
 component <- 1
 lag.max <- 50
 
@@ -43,10 +41,10 @@ for (i in 1:m){
   y[[i]] <- mc.chain.list[[i]][1:nsim2,]
 }
 
-global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, plot = FALSE)$"avgACF"
-global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, plot = FALSE)$"avgACF"
-local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, plot = FALSE)$"avgACF"
-local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, plot = FALSE)$"avgACF"
+global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
+global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
+local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
+local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
 
 pdf(file = paste(paste("Out/", A, B, C, "/boom-acf", A, B, C, sep = "_"), ".pdf", sep = ""), width = 10, height = 4)
 par(mfrow = c(1,2))
@@ -65,10 +63,8 @@ m <- 5
 A <- 1
 B <- 10
 C <- 7
+start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
 
-################ for geneting chains. Don't run ###########################
-start <- matrix(0, nrow = m, ncol = 2)  #only depends on C                #
-                                                                          #
[…]

### 2020-08-30 MagnoliaNetwork/acf_plots.R

@@ -1,5 +1,5 @@
 
-library(multichainACF)
+library(rep.acf.ccf)
 source("functions.R")
 library(ergm)
 
@@ -28,8 +28,6 @@ for(i in 1:m){
 }
 
 save(mc.chain.list, file = "Out/magnolia-two_chains.Rdata")
-
-load(file = "Out/magnolia-two_chains.Rdata")
 component = 3
 
 ########################################
@@ -43,8 +41,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/magnolia-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
 dev.off()
 
 #######################################
@@ -58,6 +56,6 @@ for (i in 1:m){
 
 pdf(file = paste("Out/magnolia-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
 dev.off()

### 2020-08-30 PoissonChange/acf_plots.R

@@ -1,6 +1,6 @@
 set.seed(1)
 library("MCMCpack")
-library(multichainACF)
+library(rep.acf.ccf)
 load("mida.rda")
 
 c0 <- 13
@@ -34,8 +34,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/poisson-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
 dev.off()
 
 ### ncrop = 1e4

### 2020-08-30 SensorNetwork/acf_plots.R

@@ -1,5 +1,5 @@
 set.seed(1)
-library(multichainACF)
+library(rep.acf.ccf)
 source("functions.R")
 ######## Data
 
@@ -81,9 +81,9 @@ for (i in 1:m){
 
 
 pdf(file = "Out/sensor-acf_n5e3.pdf", height = 4, width = 4)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
 par(new = TRUE)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", col = "royalblue")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
 dev.off()
 
 
@@ -97,9 +97,9 @@ for (i in 1:m){
 
 
 pdf(file = "Out/sensor-acf_n5e4.pdf", height = 4, width = 4)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
 par(new = TRUE)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", col = "royalblue")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
 dev.off()
 
 

### 2020-08-30 VAR-1/acf_plots.R

@@ -1,6 +1,6 @@
 set.seed(10)
 source("functions.R")
-library(multichainACF)
+library(rep.acf.ccf)
 
 
 ######################################
@@ -71,8 +71,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
-local.acf <- globalACF(x, type = "correlation", component = 1, mean="local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
+local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
@@ -92,8 +92,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
-local.acf <- globalACF(x, type = "correlation", component = 1, mean="local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
+local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))

### 2020-08-30 Paper/main.tex

@@
 \begin{abstract}
-Autocovariances are the fundamental quantity of interest in many features of Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain.
+Autocovariances are a fundamental quantity of interest in Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain.
 Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth.
-For multiple chain MCMC sampling,  we propose a globally-centered estimator of autocovariance function (G-ACvF) that pools information from all Markov chains.
-G-ACvF is also shown to correct the negative bias of single chain empirical autocovariance.
-We show the impact of this improved estimator in three aspects: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
-We also establish the strong consistency of our improved asymptotic covariance estimator under weak conditions, and obtain its large sample bias and variance.
+For multiple chain MCMC sampling,  we propose a globally-centered estimator of the autocovariance function (G-ACvF) that exhibits theoretical and empirical improvements.
+We show that the bias of the G-ACvF estimator is smaller than the bias of the current state-of-the-art.
+The impact of this improved estimator is evident in three critical output analysis applications: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
+Under weak conditions, we establish strong consistency of an improved asymptotic covariance estimator, and obtain its large sample bias and variance.
 \end{abstract}
@@
 A key quantity that drives MCMC output analysis is the autocovariance function (ACvF).
-From their use in autocorrelation (ACF) plots to assessing Monte Carlo variability of estimators, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences from MCMC output.
-However, estimators of ACvF are only available for single-chain implementations, with parallel-chain version obtained by naive averaging.
+ % From their use in autocorrelation (ACF) plots to assessing Monte Carlo variability of estimators, to determining when to stop MCMC simulation, autocovariances drive many visual and quantitative inferences from MCMC output.
+However,
+ Estimators of ACvF are only available for single-chain implementations, with a parallel-chain version obtained by naive averaging.
 As we will demonstrate, this defeats the purpose of running parallel Markov chains from dispersed starting values.
@@
 and for $k < 0$, $\hat{\Gamma}_s(k) = \hat{\Gamma}_s(-k)^T$.
-For single-chain MCMC runs, the estimator $\hat{\Gamma}_s(k)$ is used to construct ACF plots, to estimate the long-run variance of Monte Carlo estimators \citep{hannan:1970,dame:1991}, and to estimate effective sample size (ESS) \citep{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
+For a single-chain MCMC run, the estimator $\hat{\Gamma}_s(k)$ is used to construct ACF plots, to estimate the long-run variance of Monte Carlo estimators \citep{hannan:1970,dame:1991}, and to estimate effective sample size (ESS) \citep{kass:carlin:gelman:neal:1998,gong:fleg:2016,vats:fleg:jon:2019}.
 However, there is no unified approach to constructing estimators of $\Gamma(k)$ for parallel-chain implementations.
-Specifically, parallel MCMC chains are often spread across the state space so as to adequately capture high density areas.
+Specifically, parallel chains are often spread across the state space so as to adequately capture high density areas.
 For slow mixing chains, the chains take time to traverse the space so that $\bar{X}_s$  are all vastly different.
-Consequently, $\hat{\Gamma}_s$ typically underestimates $\Gamma$ leading to a false sense of security about the quality of process.
-
- We propose a globally-centered estimator of ACvF (G-ACvF) that centers the Markov chain around the overall mean vector from all $m$ chains.
-We show that the bias under stationarity for G-ACvF is lower than $\hat{\Gamma}_s(k)$, and through various examples, empirically demonstrate improved estimation.
-We employ the G-ACvF estimators to construct ACF plots, which leads to remarkable improvements.
-A demonstrative example is at the end of this Section.
+Consequently, $\hat{\Gamma}_s(k)$ typically underestimates $\Gamma(k)$ leading to a false sense of security about the quality of process.
+
+ We propose a globally-centered estimator of ACvF (G-ACvF) that centers the Markov chains around the global mean from all $m$ chains.
+We show that the bias for G-ACvF is lower than $\hat{\Gamma}_s(k)$, and through various examples, demonstrate improved estimation.
+We employ the G-ACvF estimators to construct ACF plots and a demonstrative example is at the end of this Section.
 
@@
 
-Estimators of ACvFs are often needed to estimate the long-run variance of Monte Carlo averages.
+Estimators of ACvFs are used to estimate the long-run variance of Monte Carlo averages.
 Specifically, spectral variance (SV) estimators  are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$ \citep{andr:1991,dame:1991,fleg:jone:2010}.
-We replace $\hat{\Gamma}(k)$ with G-ACvF in SV estimators to obtain globally-centered SV (G-SV) estimator and demonstrate strong consistency under weak conditions.
+We replace $\hat{\Gamma}_s(k)$ with G-ACvF in SV estimators to obtain globally-centered SV (G-SV) estimator and demonstrate strong consistency under weak conditions.
 In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimator.
@@
 
-We demonstrate the striking difference in estimation of $\Gamma(k)$ via ACF plots.
-Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density.
-Let the target density be
+We demonstrate the striking difference in estimation of $\Gamma(k)$ via ACF plots. Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density. Let
 \[
@@
 \]
-where $f(x; a,b)$ is the density of a normal distribution with mean $a$ and variance $b$. 
+be the target density where $f(x; a,b)$ is the density of a normal distribution with mean $a$ and variance $b$. 
 We set $m = 2$ with starting values distributed to the two modes.
-The trace plots in Figure~\ref{fig:gaussian-trace} indicates that in the first $10^4$ steps, the chains do not jump modes so that both Markov chains yield significantly different estimates of the population mean, $\mu$.
+The trace plots in Figure~\ref{fig:gaussian-trace} indicate that in the first $10^4$ steps, the chains do not jump modes so that both Markov chains yield significantly different estimates of the population mean, $\mu$.
 At $10^5$ sample size, both Markov chains have traversed the state space reasonably and yield similar estimates of $\mu$.
 
-In Figure~\ref{fig:gaussian-acf} for $n = 10^4$, we present the ACF plots using the usual locally-centered ACvF and our proposed G-ACF estimator.
-The blue curve are the respective estimates at $n = 10^5$.
+In Figure~\ref{fig:gaussian-acf} for $n = 10^4$, we present the ACF plots using $\hat{\Gamma}_s(k)$ and our proposed G-ACF estimator.
+The blue curves are the respective estimates at $n = 10^5$.
 At $n = 10^5$ when the chains have similar means, the G-ACF and locally-centered ACF are equivalent.
-However, for $n = 10^4$, the locally-centered ACFs critically underestimate the correlation giving user a misleading visual quality of the Markov chain.
+However, for $n = 10^4$, $\hat{\Gamma}_s(k)$ critically underestimate the correlation giving user a misleading visual of the quality of the Markov chain.
 The G-ACF estimator accounts for the discrepancy in sample means between two chains leading to a far improved quality of estimation.
@@
 
-\caption{ACF plots using local-centering (left) and global-centering (right). Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 10^5$ for chain 1.}
+\caption{ACF plots using local-centering (left) and global-centering (right). Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 10^5$ for the first chain.}
  % (b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
@@
 
-% Recall that we run $m$ independent $F$-ergodic Markov chains denoted by $\{X_{st}; \; t \in \mathbb{Z}\}$ for the $s^{th}$ chain. 
 Let $P$ denote the Markov transition kernel that uniquely determines the ACvF under stationarity.
-Recall the sample mean of the $s^{th}$ Markov chain is $\bar{X}_s = n^{-1} \sum_{t=1}^{n} X_{st}$ and denote the global mean by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
-The global mean is a naturally superior estimator of $\mu$ than $\bar{X}_s$.
+Recall that the sample mean of the $s^{th}$ Markov chain is $\bar{X}_s$ and denote the global mean vector by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
+The global mean is a naturally superior estimator of $\mu$ compared to $\bar{X}_s$.
 For $k \geq 0$, we define the globally-centered ACvF (G-ACvF) estimator for the $s${th} Markov chain as
@@
 with $\hat{\Gamma}_{G,s}(k) = \hat{\Gamma}_{G,s}(-k)^T$ for $k < 0$.
-In the event that all $m$ Markov chains have been run long enough that $\bar{X}_s \approx \bar{\bar{X}}$, then  $\hat{\Gamma}_{s} (k) \approx \hat{\Gamma}_{G,s}(k)$.
+In the event that all $m$ Markov chains have been run long enough, $\bar{X}_s \approx \bar{\bar{X}}$, and hence  $\hat{\Gamma}_{s} (k) \approx \hat{\Gamma}_{G,s}(k)$.
 However, for shorter runs or for slow mixing chains, $\Gamma(k)$ is more appropriately estimated by $\hat{\Gamma}_{G,s}$ as it utilizes information from all chains and accounts for disparity between estimates of $\mu$.
@@
 Let 
-\[
+\begin{equation*}
 \Phi^{(q)} = \sum_{ k= -\infty}^{\infty}\abs{k}^q \Gamma(k)\,,  
-\]
-and let $\Phi^{(1)}$ be denoted by $\Phi$.  The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
-
-{\color{orange} I don't think that the RHS below is correct. In the formulation below, $o(n^{-2})$ is be $o(n^{-1})$}
+\end{equation*}
+%
+and let $\Phi^{(1)}$ be denoted by $\Phi$.  The proof of the following theorem is available in Appendix~\ref{appendix:bias}. Let $\|\cdot\|$ denote Euclidean norm.
+
+% {\color{orange} I don't think that the RHS below is correct. In the formulation below, $o(n^{-2})$ is be $o(n^{-1})$}
 
@@
 $ the bias results for which can be found in \cite{priestley1981spectral}.
-Since lag-covariances are typically positive in MCMC, Theorem~\ref{th:G-ACF_bias} implies that the G-ACvF estimators are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered ACvF estimators.
+Since lag-covariances are typically positive in MCMC, Theorem~\ref{th:G-ACF_bias} implies that the G-ACvF estimators are asymptotically unbiased and exhibit reduced bias in finite samples compared to $\hat{\Gamma}_s(k)$.
 The consequences of this are particularly pertinent for the diagonals of $\Gamma(k)$.
- % Special interest is also in the lag-0 autocovariance, that is, the variance of the target distribution. 
-% The covariance matrix of the target distribution is the lag-0 covariance and is of particular interest.
-%  The bias of the estimator reduces by a factor of $m$:
-% \[
-% \mathbb{E} \left[\hat{\Gamma}_{G,s}(0) \right] = \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
-% \]
-
-% A first use of the ACvFs in MCMC is in constructing ACF plots. 
-Let the target variance of $i${th} component be $\Gamma^{ii}(k)$. For any component $i$, the autocorrelation is defined as
+
+Let $\Gamma^{ii}(k)$ be the $i${th} component of $\Gamma(k)$. For component $i$, the autocorrelation is defined as
 \[
@@
 and is instrumental in visualizing the serial correlation in components of the Markov chain.
-The typical estimate of the autocorrelation is constructed from $\hat{\Gamma}_s(k)$.
+A standard estimator of the autocorrelation is constructed from $\hat{\Gamma}_s(k)$.
 Instead, we advocate for using G-ACvF estimates so that,
-\[
+\begin{equation}
+\label{eq:acf}
  \hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}. 
-\]
+\end{equation}
 The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gaussian-acf}.
@@
 
-\section{Variance estimators for multiple Markov chains} \label{sec:variance_est}
+\section{Long-run variance estimators} \label{sec:variance_est}
 
@@
 \label{eq:sigma}
-  \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right) := \sum_{k = -\infty}^{\infty}\Upsilon (k)
+  \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right) := \sum_{k = -\infty}^{\infty}\Upsilon (k)\,.
 \end{equation}
@@
 \end{equation}
-Large-sample properties of $\hat{\Sigma}_s$ have been studied widely.
-\cite{vats:fleg:jon:2018} provided conditions for strong consistency while \cite{fleg:jone:2010,vats:flegal:2018} provided large-sample bias and variance results.
+Large-sample properties of $\hat{\Sigma}_s$ have been widely studied.
+\cite{vats:fleg:jon:2018} provide conditions for strong consistency while \cite{fleg:jone:2010,hannan:1970} provide large-sample bias and variance results.
 These results also extend naturally to an average SV (ASV) estimator defined as $\hat{\Sigma}_A := m^{-1} \sum_{s=1}^{m}\hat{\Sigma}_{s}$.
@@
 %
-To accurately estimate $\Sigma$, standard conditions are imposed on the lag window, $w$. 
+Standard conditions are imposed on the lag window, $w$. 
 %
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is continuous at $0$ at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} \abs{w(k/b_n)} < \infty$.
+The lag window $w(x)$ is continuous at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} \abs{w(k/b_n)} < \infty$.
 \end{ass}
 
-Assumption~\ref{ass:lag_window} is standard \citep[see]{ande:1971} and is satisfied by most lag windows. We will use the following popular Bartlett lag window in our simulations:
+Assumption~\ref{ass:lag_window} is standard \citep[see][]{ande:1971} and is satisfied by most lag windows. We will use the following popular Bartlett lag window in our simulations:
 \[
@@
 First, we provide conditions for strong consistency.
-Strong consistency is particularly important to ensure sequential stopping rules yield correct coverage at termination \citep{glyn:whit:1992}.
+Strong consistency is particularly important to ensure sequential stopping rules in MCMC yield correct coverage at termination \citep{fleg:gong:2015,glyn:whit:1992}.
 A critical assumption is that of a strong invariance principle which the following theorem establishes.
@@
 Let $\E_F\|Y_{11}\|^{2+ \delta} < \infty$ for $\delta > 0$ and let $P$ be polynomially ergodic of order $\xi > (q + 1 + \epsilon)/(1 + 2/\delta)$ for $q \geq 1$.
-Then there exists a $p \times p$ lower triangular matrix $L$ such that $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for almost all $\omega \in \Omega$ and for all $n > n_0$,
+Then there exists a $p \times p$ lower triangular matrix $L$ with $LL^T = \Sigma$, a non-negative function $\psi(n) = n^{1/2 - \lambda}$ for some $\lambda > 0$, a finite random variable $D$, and a sufficiently rich probability space $\Omega$ such that for all $n > n_0$,
 \[
@@
 \end{theorem}
-
-% \begin{ass}[Strong Invariance Principle (SIP)] \label{ass:sip}
-%     We assume the SIP holds for the Markov chains $\{Y_{st}\}_{t \geq 1} \; \forall s$.
-Here $\{Y_t\}_{t\geq 1}$ is the stochastic process that follows SIP with mean $\mu_g$.
-Let $\|.\|$ denote the Euclidean norm.
-Through SIP, there exists a $p \times p$ lower triangular matrix L, an increasing function $\psi$ on the integers, a finite random variable D, and a  sufficiently rich probability space such that, with probability 1, \\
-%   $$\left\|\sum_{t=1}^{n}Y_t - n\mu_g - LB(n)\right\| < D\psi(n)$$
-  % 
-%   Let $\{B(n)\}_{n\geq 0}$ denotes a standard p-dim Brownian motion and $B^{(i)}$ denotes its $i^{th}$ component.
-As shown in the results \cite{kuelbs1980almost}, SIP will hold for $\psi(n) = n^{1/2 - \lambda, \; \lambda > 0}$ for Markov chains commonly encountered in MCMC settings.
-We know that $\psi(n)$ is an inherent property of the stochastic process that satisfies the CLT.
-This implies that $\psi(n)$ is at least $o(\sqrt{n})$.
-Using Law of Iterative Logarithms (LIL), a tighter bound for $\psi(n)$ is given by \cite{stra:1964} as $\mathcal{O}(\sqrt{n\log \log n})$.
-% \end{ass}
 
@@
 
+Conditions for strong consistency of $\hat{\Sigma}_s$ for polynomially ergodic Markov chains are in \cite{vats:fleg:jon:2018}.
+Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.
+
 Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}.
@@
 Here, we present the results under mild conditions for when $\mu_g$ is replaced by $\bar{\bar{Y}}$.
-Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, repectively.
+Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, respectively.
 
@@
 \end{theorem}
+For the Bartlett lag window, $q = 1$ with $k_q = 1$ and $\int w(x)^2 dx = 2/3$. For other popular lag windows, see \cite{ande:1971}.
 
@@
 The SV estimator, despite having good statistical properties, poses limitations due to slow computation.
-From \eqref{eq:empirical_ACvF} and \eqref{eq:sve}, the complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for the Bartlett lag window, it is $\mathcal{O}(b_n n p^2)$.
-For slow mixing Markov chains, $n$ and $b_n$ are large, limiting the use of SV estimators.
+The complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for the Bartlett lag window, it is $\mathcal{O}(b_n n p^2)$.
+For slow mixing Markov chains, $n$ and $b_n$ can be prohibitively large, limiting the use of SV estimators.
 To overcome this, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast}.
@@
     Y_{s1} - \bar{Y}_s  & \dots & Y_{sn} - \bar{Y}_s
-\end{pmatrix}^T
+\end{pmatrix}^T \,.
 \end{equation}
@@
 Setting $B_s = (Y_{s1} - \bar{\bar{Y}} \; \dots \; Y_{sn} - \bar{\bar{Y}})^T$ and calling Algorithm~\ref{algo:herberle} with inputs $C(w^*)$ and $B_s$ yields $\hat{\Sigma}_{G,s}$.
-This algorithm has complexity $\mathcal{O}(p n \log n)$ and is thus orders of magnitude faster.
+Algorithm~\ref{algo:herberle} has complexity $\mathcal{O}(p n \log n)$ and is thus orders of magnitude faster.
 Of particular importance is the fact that the bandwidth $b_n$ has close to no impact on the computation time.
@@
 An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to calculate the effective sample size (ESS).
-ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$.
+ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$ with $\bar{\bar{Y}}$.
 Let $|\cdot|$ denote determinant.
-A multiple chain version of the ESS as defined by \cite{vats2019multivariate} is
+A multiple chain version of the ESS as defined by \cite{vats:fleg:jon:2019} is
 \[
@@
 We use the locally-centered $\hat{\Upsilon}(0)$ to estimate $\Upsilon(0)$ instead of $\hat{\Upsilon}_G(0)$ when calculating ESS.
-Both $\hat{\Upsilon}(0)$ and $\hat{\Upsilon}_G(0)$ are consistent  for $\Upsilon(0)$; however using $\hat{\Upsilon}(0)$ produces lower sample sizes when the parallel chains do not agree, indicating that more MCMC draws are needed.
+Both $\hat{\Upsilon}(0)$ and $\hat{\Upsilon}_G(0)$ are consistent  for $\Upsilon(0)$; however the typical underestimation witnessed $\Upsilon(0)$ allows a safeguard against early termination.
 
@@
 
-In this section we consider three different target distributions and sample $m$ parallel Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators.
-We will make the following three comparisons - (1) ACF vs G-ACF estimator, (2) SV vs G-SV estimator, and (3) $\widehat{\textrm{ESS}}_A$ vs $\widehat{\textrm{ESS}}_G$.
-The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence interval in cases where the true mean $\mu$ is known.
+In this section we consider three different target distributions and sample $m$ parallel Markov chains to assess the performance of our proposed estimators.
+We will make the following three comparisons - (1) locally-centered ACF vs G-ACF estimator, (2) A-SV vs G-SV estimator, and (3) $\widehat{\textrm{ESS}}_A$ vs $\widehat{\textrm{ESS}}_G$.
+The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence region when the true mean $\mu_g$ is known.
 The convergence of local and global estimators of $\Sigma$ and $\widehat{\textrm{ESS}}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$.
 In all the examples we are interested in estimating the mean of the stationary distribution $\mu$, so $g$ is the identity function.
-The batch size $b_n$ is obtained from the function \texttt{batchSize} from \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.
+The bandwidth $b_n$ are the defaults available in the \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.
 
@@
 
-\subsection{Vector Autoregressive Process} \label{ex:var}
+\subsection{Vector autoregressive process} \label{ex:var}
 
@@
 %
-where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{i.i.d.}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix.
+where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{iid}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix.
 We fix $\Omega$ be a AR correlation matrix with parameter .9.
 The invariant distribution for this Markov chain is $N(0, \Psi)$, where $vec(\Psi) = (I_{p^2} - \Phi \times \Phi)^{-1} vec(W)$.
-For $k > 0$, the lag-$k$ autocovariance is $\Upsilon(k) = \Gamma(k) = \Phi^k\Psi$.
+For $k \geq 0$, the lag-$k$ autocovariance is $\Upsilon(k) = \Gamma(k) = \Phi^k\Psi$.
 The process satisfies a CLT for $\bar{X} = n^{-1} \sum_{t=1}^{n} X_t$ if the spectral norm of $\Phi$ is less than 1 \citep{10.2307/1427459} and the limiting covariance, $\Sigma$ is known in closed form \citep{dai:jon:2017}.
 We set $p = 2$ and set $\Phi$ such that its eigenvalues are .999 and .001.
-The resulting process is slowly mixing and allows us to highlight the difference in the estimation of ACvF.We further set $m = 5$ with starting values dispersed across the state space.
+The resulting process mixes slowly and allows us to highlight the difference in the estimation of ACvF.
+We further set $m = 5$ with starting values dispersed across the state space.
 \begin{figure}[htbp]
@@
      \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
-\caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m = 5$. (Top) $n = 10^3$  and (bottom) $n =  10^4$. The red line is the true ACF.}
+\caption{VAR. ACF (left) and G-ACF (right) for the second chain for $m = 5$. (Top) $n = 10^3$  and (bottom) $n =  10^4$. The red line is the true ACF.}
 \label{fig:var-acf}
@@
 For a run length of $10^3$ (top row), the commonly used locally centered ACF underestimates the true correlation structure giving a false sense of security about the mixing of the chain.
-The G-ACF, on the other hand, is much closer to the truth.
+The G-ACF estimator, on the other hand, is able to more accurately measure the ACF of the chain.
 This difference is negligible at the larger run length of $n = 10^4$ when each of the 5 chains have sufficiently explored the state space.
@@
     \end{tabular}
-    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SV and G-SV estimator.}
+    \caption{VAR. Coverage probabilities at $95 \%$ nominal level. Replications $= 10^3$.}
     \label{tab:var-coverage}
@@
 The quality of estimation of $\Sigma$ and $\text{ESS}$ is assessed by running plots from 50 replications of run length 50000. 
- In Figure~\ref{fig:var-frob_n_ess}, we present running plots of $\log(\|\hat{\Sigma}\|_F)$ for both $\hat{\Sigma}_G$ and $\hat{\Sigma}_A$ and the running plots of $\log(\widehat{\text{ESS}})$ for both  $\widehat{\text{ESS}}_G$ and $\widehat{\text{ESS}}_A$.
-It is evident that the locally centered estimator of $\Sigma$ severely underestimates the truth, leading to an overestimation of ESS.
+ In Figure~\ref{fig:var-frob_n_ess}, we present running plots of $\log(\|\hat{\Sigma}\|_F)$ for both $\hat{\Sigma}_G$ and $\hat{\Sigma}_A$ and the running plots of $\log(\widehat{\text{ESS}})/mn$ for both  $\widehat{\text{ESS}}_G$ and $\widehat{\text{ESS}}_A$.
+It is evident that $\hat{\Sigma}_A$ severely underestimates the truth, leading to an overestimation of ESS.
 The G-SV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS.
+
 \begin{figure}[htbp]
@@
 
-We consider two settings; in setting 1 we let
+We consider two settings; in setting 1,
 $A = 1,\; B = 3,\; C = 8$ which results in well-separated modes.
-In setting 2, we let $A = 1, \; B = 10, \; C=7$ which yields in a boomerang shape for the contours.
-The contour plots for these two settings are in the left in Figure~\ref{fig:boom-2D}, overlaid with scatter plots of two parallel draws of the Gibbs sampler.
-Setting 2 is chosen specifically to illustrate that the locally and globally centered ACvFs perform similarly when the Markov chain moves freely across the state space.
+In setting 2, we let $A = 1, \; B = 10, \; C=7$ which yields a boomerang shape for the contours.
+The contour plots for these two settings are in the left in Figure~\ref{fig:boom-2D}, overlaid with scatter plots of two parallel runs of the Gibbs sampler.
+Setting 2 is chosen specifically to illustrate that the locally and globally-centered ACvFs perform similarly when the Markov chain moves freely in the state space.
 
 We run $m=5$ parallel Markov chains with starting points evenly distributed across the state space.
-For Setting 1, when the Markov chains have not been able to jump modes, locally-centered ACF severely underestimates autocorrelation.
-This is seen in the top-middle plot of Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$ (overlayed blue line).
+For setting 1, when the Markov chains have not been able to jump modes, locally-centered ACF severely underestimates autocorrelation.
+This is seen in the top-middle plot of Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$ (overlaid blue line).
 Somewhere between $n = 1000$ and $n = 10^4$, the Markov chains jump modes and it is only then that the locally-centered ACFs provide better estimates.
 The G-ACFs,  on the other hand, produce similar ACF estimates at $n = 1000$ and $n = 10^4$ by measuring deviations about the global mean.
-For setting 2, both methods yield similar ACF estimates reinforcing our claim that there is much to gain by using G-ACvF and nothing to lose.
+For setting 2, both methods yield similar ACFs  reinforcing our claim that there is much to gain by using G-ACvF and nothing to lose.
+{\color{orange} At what sample size?}
 
@@
 \end{tabular}
-\caption{Setting-1}
+\caption{Setting 1: Coverage probabilities from $10^3$ replications.}
 \label{tab:boom-coverage_1}
@@
 \end{tabular}
-\caption{Setting-2}
+\caption{Setting 2: Coverage probabilities from $10^3$ replications.}
 \label{tab:boom-coverage_2}
@@
 The true mean of the target distribution can be obtained using numerical approximation.
-Using this and both the A-SV and G-SV estimators, we construct $95\%$ confidence regions and report coverage probabilities for 1000 replications for both $m=2$ and $m=5$.
-Table \ref{tab:boom-coverage_1}, \ref{tab:boom-coverage_2} reports all  results.
+Using  the A-SV and G-SV estimators, we construct $95\%$ confidence regions and report coverage probabilities for 1000 replications for both $m=2$ and $m=5$.
+Tables~\ref{tab:boom-coverage_1} and~\ref{tab:boom-coverage_2} reports all  results.
 In setting 1, systematically, the G-SV estimator yields far superior coverage than the A-SV estimator for all values of $n$.
@@
 
-    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
+    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for setting 1 (left) and setting 2 (right).}
     \label{fig:boom-ess}
@@
 
-In Figure~\ref{fig:boom-ess} we present running plots of estimates of $\log \textrm{ESS}/mn$ for both setting 1 and setting 2.
-As the sample size increases, $\widehat{\text{ESS}}_G$ and  $\widehat{\text{ESS}}_A$ become closer, but early on for setting 1, $\widehat{\text{ESS}}_G$ estimates are much smaller giving more adequate estimates of ESS.
+In Figure~\ref{fig:boom-ess} we present running plots of estimates of $\log(\textrm{ESS})/mn$ for both setting 1 and setting 2.
+As the sample size increases, $\widehat{\text{ESS}}_G$ and  $\widehat{\text{ESS}}_A$ become closer, but early on for setting 1, $\widehat{\text{ESS}}_G$ estimates are much smaller, safeguarding users against early termination.
 
@@
 
-\subsection{Sensor Network Localization}
-
-Consider the sensor network localization problem discussed in \cite{ihler2005nonparametric}.
-The goal is to identify unknown sensor locations using noisy distance data.
+\subsection{Sensor network localization}
+
+Consider the sensor network localization problem Overleaf \cite{ihler2005nonparametric} where the goal is to identify unknown sensor locations using noisy distance data.
 We use the data and the model as specified by \cite{tak2018repelling}.
 There are four sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denotes the coordinates of the $i${th} sensor.
-Let $y_{ij} = (y_{ij})$ denotes the distance between the sensors $x_i$ and $x_j$ and if observed, yields $z_{ij} = 1$ otherwise, $z_{ij} = 0$.
+Let $y_{ij}$ denote the distance between the sensors $x_i$ and $x_j$ and if observed, yields $z_{ij} = 1$ otherwise, $z_{ij} = 0$.
 The complete model is then,
@@
     z_{ij} \mid x_1, ..., x_4 & \sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
-    y_{ij} \mid z_{ij} = 1, x_i,x_j &\sim N(\|x_i - x_j\|^2, \sigma^2)\,.
-\end{align*}
-%
-\cite{tak2018repelling} set $R = 0.3$ and $\sigma = 0.02$ and use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$.
-$y_{ij}$ is specified only if $w_{ij} = 1$.
-The resulting $8$-dimensional posterior of $(x_1, \dots, x_4)$ is intractable with unknown full conditionals.
+    y_{ij} \mid z_{ij} = 1, x_i,x_j &\sim N \left(\|x_i - x_j\|^2, \sigma^2 \right)\,.
+\end{align*}
+%
+\cite{tak2018repelling} set $R = 0.3$ and $\sigma = 0.02$ and use independent $N(0, 100I_2)$ priors on the locations.
+Distance $y_{ij}$ is specified only if $z_{ij} = 1$.
+The $8$-dimensional posterior of $(x_1, x_2, x_3, x_4)$ is intractable with unknown full conditionals.
 A Metropolis-within-Gibbs type sampler is implemented with each full conditional employing the repelling attractive Metropolis (RAM) algorithm of \cite{tak2018repelling}.
-The RAM algorithm supplies Markov chains with higher jumping frequency between the modes.
-
-\begin{figure}[htbp]
+The RAM algorithm runs Markov chains with higher jumping frequency between the modes.
+
+\begin{figure}[h]
     \centering
@@
 Average locally-centered ACF (solid orange) and G-ACF (solid blue) at $n = 5000$ (middle) and $n = 50000$ (right).
-Dashed lines are single-chain estimated ACFs (orange) and G-ACFs (blue).}
+Dashed lines are individual  chain estimates.}
     \label{fig:sensor-trace}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
@@
 We run $m = 5$ parallel Markov chains with well-separated starting points.
-The total simulation size for each chain is fixed at $10^5$.
 Coverage probabilities are not estimable since the true posterior mean is unknown.
 Trace plot of $x_{11}$ for two Markov chains is shown in Figure~\ref{fig:sensor-trace}.
-Figure~\ref{fig:sensor-trace} also  plots locally and globally centered ACFs.
+Figure~\ref{fig:sensor-trace} also  plots locally and globally-centered ACFs.
 As seen in previous examples, early estimates of locally-centered ACFs are much smaller than later estimates.
@@
 
-For slowly mixing Markov chains, the traditional single chain empirical estimator for ACvF can dramatically underestimate the truth.
+For slow mixing Markov chains, a naive average of locally-centered ACvFs can dramatically underestimate the truth.
 This has a severe impact on ACF plots, Monte Carlo variance, and stopping time of MCMC algorithms.
@@
 It is easy to show that $\hat{\Upsilon}_{G,s}(k)$ is a strongly consistent estimators for $\Upsilon(k)$.
-Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following the proof of Theorem~2 in \citep{dai:jon:2017} will yield consistent overestimation of generalized variance $\abs{\Sigma}$ estimated using a globally-centered version of the mIS estimator.
+Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following the proof of Theorem~2 in \citep{dai:jon:2017} will yield consistent overestimation of the generalized variance $\abs{\Sigma}$ estimated using a globally-centered version of the mIS estimator.
 A valuable line of research would be to carry out the theoretical and experimental analysis of mIS estimators using G-ACvF.
@@
 %
-Similar to \cite{hannan2009multiple}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
+Similar to \cite{hannan:1970}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
 \begin{equation}
@@
 
-\cite{hannan2009multiple} has given the calculations for variance of $\tilde{\Sigma}$ as 
+\cite{hannan:1970} has given the calculations for variance of $\tilde{\Sigma}$ as 
 \begin{equation} \label{eq:hannan_var}

### 2020-08-31 Paper/main.tex
Final appendix edits

@@
     & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
-    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(+ \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
+    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
@@
 
-Consider pseudo autocovariance and spectral variance estimators for the $s$th chain, denoted by $\tilde{\Upsilon}_s(k)$ and $\tilde{\Sigma}_s$ that use data centered around the unobserved actual mean $\mu$:
+Consider pseudo autocovariance and spectral variance estimators for the $s$th chain, denoted by $\tilde{\Upsilon}_s(k)$ and $\tilde{\Sigma}_s$ that use data centered around the unobserved actual mean $\mu_g$:
 \begin{align*}
@@
 %
-We first present a result which will be useful to use later. For any Markov chain $s$, 
+We first present a result which will be useful later. For any Markov chain $s$, 
 \begin{align*}
@@
 & |M_1| \\ 
-   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-k} \dfrac{1}{n}\left[ \left(X_{st} - \mu_g \right)_i  \left(\mu_g-\bar{\bar{X}} \right)_j + \left(\mu_g-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu_g \right)_j\right]\right\}\right| \\
-   % & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}{\left|\sum\limits_{t=1}^{n-k} \left(X_{st} - \mu_g \right)_i  \left(\mu_g - \bar{\bar{X}} \right)_j\right|} + \dfrac{1}{n}{\left|\sum_{t=1}^{n-k} \left(\mu_g-\bar{\bar{X}} \right)_i\left(X_{s(t+k)} - \mu_g \right)_j\right|} \right]\right\}\\
     & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\left[ \dfrac{1}{n}\left|\sum_{t \in I_k}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t \in I_k }(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
@@
    |M_2| & = \left|\dfrac{1}{m}\sum\limits_{s=1}^{m}\left\{ \left(\mu_g - \bar{\bar{Y}} \right)_i  \left(\mu_g - \bar{\bar{Y}} \right)_j\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\right\}\right|\\
-    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)\right] < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
+    & \leq\|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\abs{\sum_{k=-b_n+1}^{b_n-1}\left(1-\dfrac{\abs{k}}{n}\right)w\left(\dfrac{k}{b_n}\right)} < \|\bar{\bar{Y}} - \mu_g\|_{\infty}^2\left[\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
     % &= b_n\|\bar{\bar{X}} - \mu_g\|_{\infty}^2\left[\dfrac{1}{b_n}\sum_{k=-b_n+1}^{b_n-1}\left|w\left(\dfrac{k}{b_n}\right)\right|\right]\\
@@
 \end{align*}
-where $g_1(n), g_2(n), g_3(n)$ are defined such that as $n \to \infty$,  $g_1(n), g_2(n), g_3(n) \to 0$.
-%\begin{align*}
-%   g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
-%    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-%    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
-%\end{align*}
-%
-
-By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that
+where it has been shown already that $g_1(n), g_2(n), g_3(n) \to 0$ as $n \to \infty$. By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that
 \begin{align*}
@@
 \section{Additional Examples}
-We present two additional real-world examples to illustrate the advantage of global autocorrelation estimator using ACF plots.
+We present two additional real-world examples to illustrate the advantage of global autocovariance estimator using ACF plots.
 For both the examples, we use a pre-established Markov chain structure and implement our estimator on the Markov chains obtained.
@@
       \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
-    \caption{Change point: ACF plots using local-centering (left) and global-centering (right) for $m=2$ parallel Markov chains.
+    \caption{Change point: ACF plots using local (left) and global (right) centering for $m=2$ parallel Markov chains.
 The individual chains are shown through dashed lines and average over $m$ chains is the solid line.
@@
 Figure~\ref{fig:poisson-acf} demonstrates a striking advantage of G-ACF against locally-centered ACF in estimating the autocorrelations.
-For a chain length of $n=1000$, locally-centered ACF gives a false sense of security about the Markov chains whereas in reality, the process is highgly correlated.
-G-ACF gives a more realistic and accurate estimation of autocorrelations in almost ten times lesser samples per chain.
+For a chain length of $n=1000$, locally-centered ACF gives a false sense of security about the Markov chains whereas in reality, the process is highly correlated.
+G-ACF gives a more accurate estimation of autocorrelations in almost ten times lesser samples per chain.
 
@@
 
-We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking" which might cause formation of clusters in the social network.
+We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking".
+This might cause formation of clusters in the social network.
 We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group, especially their grades.

### 2020-08-31 MagnoliaNetwork/acf_plots.R

@@ -1,5 +1,5 @@
 
-library(rep.acf.ccf)
+library(multichainACF)
 source("functions.R")
 library(ergm)
 
@@ -28,6 +28,7 @@ for(i in 1:m){
 }
 
 save(mc.chain.list, file = "Out/magnolia-two_chains.Rdata")
+load(file = "Out/magnolia-two_chains.Rdata")
 component = 3
 
 ########################################
@@ -41,8 +42,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/magnolia-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 #######################################
@@ -56,6 +57,6 @@ for (i in 1:m){
 
 pdf(file = paste("Out/magnolia-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()

### 2020-08-31 PoissonChange/acf_plots.R

@@ -1,6 +1,6 @@
 set.seed(1)
 library("MCMCpack")
-library(rep.acf.ccf)
+library(multichainACF)
 load("mida.rda")
 
 c0 <- 13
@@ -34,8 +34,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/poisson-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 ### ncrop = 1e4
@@ -49,8 +49,8 @@ for (i in 1:m){
 
 pdf(file = paste("Out/poisson-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-globalACF(x, chains=0, component = component, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
-globalACF(x, chains=0, component = component, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains=0, component = component, mean = "local", type = "correlation", col = "darkorange")
+globalACF(x, chains=0, component = component, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 #########################################

### 2020-09-01 Paper/main.tex
Preliminary appendix fix

@@
 
+Let $B^{(i)}$ denote the $i$th component of the $p$-dimensional standard Brownian motion $B$.
 \begin{lemma}
@@
 (\cite{csorgo1981strong}).
-Suppose the conditions of Theorem~\ref{thm:kuelbs} hold, then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}(\epsilon)$ and $\forall i = 1, ..., p$
-
-\[
-\sup_{0\leq t \leq n-b_n}\sup_{0 \leq s \leq b_n} \left| B^{\left(i\right)}\left(t+s\right) - B^{\left(i\right)}\left(t\right) \right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\; \log\; n\right)\right)^{1/2} ,
-\]
-%
-\[
-\sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right| < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \; \textrm{and}
-\]
-%
-\[
-\left|B^{\left(i\right)}\left(n\right)\right| < \left(1+\epsilon\right)\sqrt{2n\;\log \log n} \; . 
-\]
+Let $b_n$ be a sequence such that $b_n$ and $n/b_n \to \infty$ as $n \to \infty$.
+Then for all $\epsilon > 0$ and for almost all sample paths, there exists $n_{0}\left(\epsilon\right)$ such that $\forall n\geq n_{0}(\epsilon)$
+\begin{align*}
+ \sup_{0\leq t \leq n-b_n}\sup_{0 \leq s \leq b_n} \left| B^{\left(i\right)}\left(t+s\right) - B^{\left(i\right)}\left(t\right) \right| & < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\; \log\; n\right)\right)^{1/2} , \\
+  \sup_{0 \leq s \leq b_n} \left|B^{\left(i\right)}\left(n\right) - B^{\left(i\right)}\left(n - s\right)\right|& < \left(1+ \epsilon\right)\left(2b_n\left(\log\dfrac{n}{b_n} + \log\;\log\;n\right)\right)^{1/2} , \; \textrm{and} \\
+  \left|B^{\left(i\right)}\left(n\right)\right|& < \left(1+\epsilon\right)\sqrt{2n\;\log \log n} \; . 
+\end{align*}
+%
 \end{lemma}
 
-% \begin{lemma} \label{lemma:consis_1}
-%   If Assumption~\ref{ass:sip} holds, then $\| \bar{\bar{X}} - \mu\|_{\infty}, \|\bar{X}_s - \mu\|_{\infty} \xrightarrow[]{a.s.} 0$ as $n \to \infty$ for all $s \in \{1,..., m\}$\\
-%   \end{lemma}
-
-% \begin{proof}
-% Let $\|.\|$ denote the Euclidean norm.
-Assumption \ref{ass:sip} allows us to upper bound $\|\bar{X}_s - \mu\|_{\infty}$ using SIP.
-Following that, we show that the upper bound term converges to 0 as $n \to \infty$ using lemma \ref{lemma: brownian}.
-%  \begin{align*}
-%     \|\bar{X}_s - \mu\|_{\infty} & \leq \|\bar{X}_s - \mu\| \\
-%     &= \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - n\mu\right\| = \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\
-%     & \leq \dfrac{1}{n}\left\|\sum_{t=1}^{n}X_{st} - \mu - L B(n)\right\| + \dfrac{\left\|L B(n)\right\|}{n}\\
-%     &< \dfrac{D\psi(n)}{n} + \dfrac{\|L B(n)\|}{n}\\
-%     &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\
-%     & \leq \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| p^{1/2}(1+\epsilon)\sqrt{2n \log\log n}\\
-%     & \xrightarrow[]{a.s.} 0\;\; as \;\; n\to \infty
-%  \end{align*}
-% %
-% Similarly one can easily show that $\|\bar{\bar{X}} - \mu\|_{\infty} \to 0$ as $n \to \infty$ using the same upper-bound as:
-% % 
-% \begin{align*}
-%     \|\bar{\bar{X}} - \mu\|_{\infty} & \leq \|\bar{\bar{X}} - \mu\| = \dfrac{1}{m}\left \|\sum_{j=1}^{m}(\bar{X}_j- \mu) \right\| \leq \dfrac{1}{m}\sum_{j=1}^{m}\|\bar{X}_j - \mu\| \xrightarrow{a.s.} 0 \, \textrm{as } n \to \infty
-% \end{align*}
-% \end{proof}
-
 % \section{Proof of Theorems} \label{appendix:A}
 
-For the purpose of generalizing summations for positive and negative lags in the following proofs, we define the sets $I_k, J_{k1} \text{ and } J_{k2}$ as $ I_k := \{1, \dots, n-k\}, J_{k1} := \{n-k+1, \dots , n\}, J_{k2} := \{1, \dots, k\}$ for $k > 0$ and  $I_k := \{1-k, \dots, n\}, J_{k1} := \{1, \dots , -k\}, J_{k2} := \{n+k+1, \dots, n\}$ for $k < 0$.
+In order to generalize summations for positive and negative lags in the following proofs, we define the sets $I_k, J_{k1} \text{ and } J_{k2}$ as $ I_k := \{1, \dots, n-k\}, J_{k1} := \{n-k+1, \dots , n\}, J_{k2} := \{1, \dots, k\}$ for $k > 0$ and  $I_k := \{1-k, \dots, n\}, J_{k1} := \{1, \dots , -k\}, J_{k2} := \{n+k+1, \dots, n\}$ for $k < 0$.
 For $k=0$, $J_{k1}$ and $J_{k2}$ are empty sets and $I_k := \{1, \dots, n\}$.
@@
 We can break $\hat{\Gamma}_{G,s}$ into four parts for all $k \geq 1$ as:
-%  \[
-%  \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
-%  \]
-% %
-% where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
-% The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms.
-
- % \begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
-% \begin{lemma} \label{lemma:bias1}
-% $\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
-% \end{lemma}
-% \begin{proof}
-% \begin{align*}
-%     &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
-%      &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
-%     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
-%     &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
-%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
-%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
-%     &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,.
-% \end{align*}
-% %
-% Similarly,
-% %    
-% \begin{align*}
-%     \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
-%     % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
-% \end{align*}
-% \end{proof}
-
-% \begin{lemma} \label{lemma:bias2}
-% \[
-% \mathbb{E}\left[\sum\limits_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right) \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] =  (m-1)\text{Var}(\bar{X}_1)\,.
-% \]
-% \end{lemma}
-
-% % $\bar{X}_i$ are independently and identically distributed for all $i$; this implies $\Var(\bar{\bar{X}}) = \dfrac{1}{m} \Var(\bar{X}_1)$.
-
-% \begin{proof}
-% \begin{align*}
-% \mathbb{E}\left[\sum_{s=1}^{m} \left(\bar{X}_{s} - \bar{\bar{X}} \right)  \left(\bar{X}_{s} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} -\sum_{s=1}^{m}\bar{X}_{s}\bar{\bar{X}}^{T} - \bar{\bar{X}}^{T}\sum_{s=1}^{m}\bar{X}_{s}^{T} + m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
-% &= \mathbb{E}\left[\sum_{s=1}^{m}\bar{X}_{s}\bar{X}_{s}^{T} - m\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
-% &= m\left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
-% &= m\left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
-% &= (m-1)\Var(\bar{X_1})\,.
-% \end{align*}
-% \end{proof}
-
+%
 \begin{align*}
@@
 Similarly,
-%    
 \begin{align}
@@
 % &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
-&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
-&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
-\end{align*}
-%
-Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
+&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
+\end{align*}
+%
+Additionally, $\hat{\Gamma}_s(k)$ exhibits the following expectation (from \cite{priestley1981spectral})
  \begin{equation} \label{eq:priestly}
-     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
+     \mathbb{E}[\hat{\Gamma}_s(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
  \right)\,.
@@
 
- We can use the results of \cite{song1995optimal} to expand $\Var(\bar{X}_1)$. By proposition 1 in \cite{song1995optimal} 
+By \cite[Proposition 1]{song1995optimal} 
 \[
@@
 
-As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
+% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
+Consequently,
  \begin{equation} \label{eq:G-ACF_expec_breakdown}
@@
 %
-We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$.
-Here, $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\mathcal{O}}(1/n)$.
-For a diagonal element of $\Gamma$,
+Here $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \to 0 \textrm{ and } O_2 = {\mathcal{O}}(1/n) \to 0$ as $n \to \infty$. For a diagonal element of $\Gamma$,
 % We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.

### 2020-09-01 Paper/main.tex
Appendix edits: Theorem1

@@
 \[
-   \mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,.
+   \mathbb{E}_F\left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-1} \right)\,.
 \]
@@
  \begin{equation} \label{eq:priestly}
-     \mathbb{E}[\hat{\Gamma}_s(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
+     \mathbb{E}[\hat{\Gamma}_s(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X}_s)}
  \right)\,.
@@
     &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
-    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
-\end{align*}
-%
-
-By \cite[Proposition 1]{song1995optimal} 
-\[
-\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
-\]
-
+   &= \left(1- \dfrac{\abs{k}}{n}\right)\left( \Gamma(k) - \dfrac{\Var (\bar{X}_1)}{m} \right) + o(n^{-1})%\\
+  %  &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
+\end{align*}
+%
+
+By \cite[Proposition 1]{song1995optimal},
+\[
+\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})\,.
+\]
+As a consequence, we get the result 
+\[
+ \E \left[\hat{\Gamma}_{G,s}(k) \right] =  \left(1- \dfrac{\abs{k}}{n}\right)\left( \Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} \right) + o(n^{-1})\,.
+\]
 % As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
-Consequently,
+Note that we can also break down $ \E \left[\hat{\Gamma}_{G,s}(k) \right]$ as
  \begin{equation} \label{eq:G-ACF_expec_breakdown}
@@
 \end{align*}
-In the presence of positive correlation, the leftover term is positive.
+Note that $ \hat{\Gamma}_{G,s}(k)$ is less negatively biased as compared to $\hat{\Gamma}_s(k)$.
+In the presence of positive correlation, the leftover $o(n^{-1})$ term is positive which further counters the negative bias of $\hat{\Gamma}_{G,s}(k)$.
 

### 2020-09-01 Examples/Boomerang/acf_plots.R
Examples clean-up

@@ -1,6 +1,6 @@
 set.seed(1)
 source("functions.R")
-library(rep.acf.ccf)
+library(multichainACF)
 
 #######################################
 ##### Setting-1
@@ -10,6 +10,8 @@ m <- 5
 A <- 1
 B <- 3
 C <- 8
+
+############# Run only for simulating Markov chains. ############
 start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
 
 for(i in 1:floor(m/2)){
@@ -26,6 +28,9 @@ for (i in 1:m){
 }
 global.mean <- global.mean/m
 save(mc.chain.list, file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
+#####################################################################
+
+load(file = "Out/_1_3_8_/boom-five_chains_1_3_8.Rdata")
 component <- 1
 lag.max <- 50
 
@@ -41,10 +46,10 @@ for (i in 1:m){
   y[[i]] <- mc.chain.list[[i]][1:nsim2,]
 }
 
-global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
-global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, graph = FALSE)$"avg_ACF"
-local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
-local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, graph = FALSE)$"avg_ACF"
+global.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, component = 1, plot = FALSE)$"avgACF"
+global.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, component = 1, plot = FALSE)$"avgACF"
+local.acf1 <- globalACF(x, type = "correlation", lag.max = lag.max, mean = "local", component = 1, plot = FALSE)$"avgACF"
+local.acf2 <- globalACF(y, type = "correlation", lag.max = lag.max, mean = "local", component = 1, plot = FALSE)$"avgACF"
 
 pdf(file = paste(paste("Out/", A, B, C, "/boom-acf", A, B, C, sep = "_"), ".pdf", sep = ""), width = 10, height = 4)
 par(mfrow = c(1,2))
[…]

### 2020-09-01 Examples/GaussianMix/output.R

@@ -68,22 +68,6 @@ legend("topleft", legend=c("Target", "Chain-1", "Chain-2"),col=c("black", "light
 dev.off()
 
 
-###############################################
-##############Density plots ####################
-###############################################
-
-pdf(file = "density.pdf", height = 5, width = 5)
-x <- seq(-10, 10, .01)
-plot(density(chain1[1:1e4]), col = "lightskyblue", type = "l", lwd=2, xlim = range(chain1, chain2), ylim = c(0, 1), xlab = "x", ylab = "density", main = "")
-polygon(density(chain1[1:1e4]), col = rgb(135, 206, 250, max = 255, alpha = 100, names = "lsb50"))
-lines(density(chain2[1:1e4]), col = "plum3", lwd=2)
-polygon(density(chain2[1:1e4]), col = rgb(205, 150, 205, max = 255, alpha = 100, names = "p350"))
-lines(x, exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd=2)
-legend("topleft", legend=c("Target", "Chain-1", "Chain-2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=0.8, lwd=2)
-
-dev.off()
-
-
 ##############################################
 ########## ACF and G-ACF ####################
 #############################################
@@ -101,8 +85,8 @@ for (i in 1:m){
   y[[i]] <- as.matrix(mc.chain.list[[i]][1:nsim2,])
 }
 
-local.acf1 <- acf(x[[1]], type = "correlation", lag.max = lag.max, plot = FALSE)
-local.acf2 <- acf(y[[1]], type = "correlation", lag.max = lag.max, plot = FALSE)
+local.acf1 <- globalACF(x, chains = c(1), component = 1, mean = "local", lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
+local.acf2 <- globalACF(y, chains = c(1), component = 1, mean = "local", lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 
[…]

### 2020-09-01 Examples/SensorNetwork/acf_plots.R

@@ -1,5 +1,5 @@
 set.seed(1)
-library(rep.acf.ccf)
+library(multichainACF)
 source("functions.R")
 ######## Data
 
@@ -50,6 +50,8 @@ aux5 <- runif(n=8, min=min(start5), max=max(start5))
 start <- rbind(start1, start2, start3, start4, start5)
 aux <- rbind(aux1, aux2, aux3, aux4, aux5)
 j.scale <- rep(0.5, 4)
+
+############# Run only for simulating marov chains #####################
 mc.chain.list <- list()
 
 for (k in 1:m){
@@ -59,6 +61,7 @@ for (k in 1:m){
 }
 
 save(mc.chain.list, file = "Out/five_chains.Rdata")
+######################################################################
 
 load(file = "Out/five_chains.Rdata")
 
@@ -81,9 +84,9 @@ for (i in 1:m){
 
 
 pdf(file = "Out/sensor-acf_n5e3.pdf", height = 4, width = 4)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", col = "darkorange")
 par(new = TRUE)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 
@@ -97,9 +100,9 @@ for (i in 1:m){
 
 
 pdf(file = "Out/sensor-acf_n5e4.pdf", height = 4, width = 4)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", leg = FALSE, col = "darkorange")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "local", type = "correlation", col = "darkorange")
 par(new = TRUE)
-globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", leg = FALSE, col = "royalblue")
+globalACF(x, chains = 0, component = component, lag.max = lag.max, mean = "global", type = "correlation", col = "royalblue")
 dev.off()
 
 

### 2020-09-01 Examples/VAR-1/acf_plots.R

@@ -1,6 +1,6 @@
 set.seed(10)
 source("functions.R")
-library(rep.acf.ccf)
+library(multichainACF)
 
 
 ######################################
@@ -71,8 +71,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
-local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
+local.acf <- globalACF(x, type = "correlation", component = 1, mean = "local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
@@ -92,8 +92,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
-local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
+local.acf <- globalACF(x, type = "correlation", component = 1, mean = "local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))

### 2020-09-01 New_ACF_comparisons.R

@@ -1,127 +1,0 @@
-set.seed(1)
-source("functions.R")
-library(rep.acf.ccf)
-
-
-m <- 2
-A <- 1
-B <- 3
-C <- 8
-
-start <- matrix(0, nrow = m, ncol = 2)  #only depends on C
-
-for(i in 1:floor(m/2)){
-  start[i,] <- c(0, C*(2^(2-i)))
-  start[m-i+1,] <- c(C*(2^(2-i)), 0)
-}
-
-lag.max <- 100
-
-####################################
-nsim <- 500
-########################################
-mc.chain.list <- list()
-global.mean <- c(0,0)
-
-for (i in 1:m){
-  chain <- markov.chain(A, B, C, nsim, start[i,])
-  global.mean <- global.mean + colMeans(chain)
-  mc.chain.list[[i]] = chain
-}
-global.mean <- global.mean/m
-sample_var <- rep(0, m)
-means <- rep(0, m)
-covariances <- matrix(0, nrow = lag.max+1, ncol = m)
-
-for (j in 1:m){
-  sample_var[j] <- var(mc.chain.list[[j]][,component])
-  means[j] <- mean(mc.chain.list[[j]][,component])
-  covariances[,j] <- as.vector(acf(mc.chain.list[[j]][,component], plot = FALSE, lag.max = lag.max, type = "covariance")$acf)
-}
-W <- mean(sample_var)
-B <- nsim * var(means)
-new_var <- ((nsim - 1)/nsim)*W + (1/nsim)*B
-avg.covariances <- as.matrix(rowMeans(covariances))
-new_corr <- 1 - (W/new_var) + (avg.covariances/new_var)
-
-acf.list <- combined_acf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
-ccf.list <- combined_ccf(mc.chain.list, chain = 1, component = c(1,2), lag.max = lag.max, type = "correlation")
-
-pdf(file = "Boomerang.pdf", width = 8, height = 4)
-plot(acf.list[[1]][[1]], main = expression(paste("ACF comparison for chain 1")), type = "l", xlim = c(0,lag.max), ylim = c(-0.5,1))
-lines(seq(0,lag.max), acf.list[[1]][[2]]$acf, type = "l", col = "blue", xlim = c(0,lag.max), ylim = c(0,1))
-lines(seq(0, lag.max), new_corr, col = "green")
[…]

### 2020-09-01 VAR-1/New_ACF_comparisons.R

@@ -1,116 +1,0 @@
-set.seed(1)
-source("functions.R")
-library(rep.acf.ccf)
-
-m <- 5
-p <- 2
-omega <- diag(p)
-for (i in 1:(p-1)){
-  for (j in 1:(p-i)){
-    omega[j, j+i] <- .9^i
-    omega[j+i, j] <- .9^i
-  }
-}
-
-phi <- diag(c(.9999, .001))
-dummy <- matrix(1:p^2, nrow = p, ncol = p)
-dummy <- qr.Q(qr(dummy))
-phi <- dummy %*% phi %*% t(dummy)
-#phi <- phi/(max(eigen(phi)$values) + .1)
-
-target <- target.sigma(phi, omega)
-truth <- true.sigma(phi, var = target)
-
-lag.max <- 150
-true.acf <- array(0, dim = c(p, p, 2*lag.max + 1))
-true.acf[,,lag.max+1] <- target
-for (i in 1:lag.max){
-  true.acf[,,lag.max + 1 + i] <- phi %*% true.acf[,,lag.max + 1 + i - 1]
-  true.acf[,,lag.max + 1 - i] <- true.acf[,,lag.max + 1 - i + 1] %*% t(phi)
-}
-
-start <- matrix(0, nrow = m, ncol = p)  #only depends on C
-
-for(i in 1:floor(m/2)){
-  start[i,] <- 0.5*i*sqrt(diag(target))
-  start[m-i+1,] <- -0.5*i*sqrt(diag(target))
-}
-
-####################################
-nsim <- 500
-########################################
-mc.chain.list <- list()
-global.mean <- rep(0,p)
-lag.max <- 150
-for (i in 1:m){
-  chain <- markov.chain(phi, omega, nsim, start[i,])
-  global.mean <- global.mean + colMeans(chain)
-  mc.chain.list[[i]] = chain
-}
-global.mean <- global.mean/m
-sample_var <- rep(0, m)
-means <- rep(0, m)
-covariances <- matrix(0, nrow = lag.max+1, ncol = m)
-
-for (j in 1:m){
-  sample_var[j] <- var(mc.chain.list[[j]][,component])
-  means[j] <- mean(mc.chain.list[[j]][,component])
-  covariances[,j] <- as.vector(acf(mc.chain.list[[j]][,component], plot = FALSE, lag.max = lag.max, type = "covariance")$acf)
-}
-W <- mean(sample_var)
[…]

### 2020-09-01 one_run.R

@@ -65,20 +65,13 @@ local.acf2 <- acf(as.matrix(y[[1]]), type = "correlation", lag.max = lag.max, pl
 global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 
-#### Figure 2a
+#### Figure 2
 pdf(file = "AllOut/gaussian-acf_hist.pdf", width = 8, height= 4)
 par(mfrow = c(1,2))
 plot(as.matrix(local.acf1$acf), type = 'h', ylab = "Autocorrelation", xlab = "Lag")
 lines(as.matrix(local.acf2$acf), type = 'l', col = "steelblue1", lwd = 2)
 plot(as.matrix(global.acf1$acf), type = 'h', ylim = c(min(local.acf1$acf), 1), ylab = "Autocorrelation", xlab = "Lag")
 lines(as.matrix(global.acf2$acf), type = 'l', col = "steelblue1", lwd = 2)
-dev.off()
-
-### Figure 2b
-pdf(file = "AllOut/gaussian-acf_1e4.pdf", width = 8, height= 4)
-par(mfrow = c(1,2))
-l <- globalACF(x, chains = 0, component = 1, lag.max = lag.max, mean = "local", type = "correlation", col = "royalblue", leg = FALSE)
-g <- globalACF(x, chains = 0, component = 1, lag.max = lag.max, mean = "global", type = "correlation", col = "darkorange", leg = FALSE)
 dev.off()
 
 
@@ -104,8 +97,8 @@ for (i in 1:m){
   x[[i]] <- mc.chain.list[[i]][1:ncrop,]
 }
 
-global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), graph = FALSE, avg = FALSE)[[1]]
-local.acf <- acf(x[[2]][, component], lag.max = lag.max, type = "correlation", plot = FALSE)
+global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
[…]

### 2020-09-02 Paper/main.tex
Wednesday morning prelim edits. 31 pages.

@@
 % As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
-Note that we can also break down $ \E \left[\hat{\Gamma}_{G,s}(k) \right]$ as
+Although this completes the proof of Theorem~\ref{th:G-ACF_bias}, we will require the following decomposition
  \begin{equation} \label{eq:G-ACF_expec_breakdown}
@@
 %
-Here $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \to 0 \textrm{ and } O_2 = {\mathcal{O}}(1/n) \to 0$ as $n \to \infty$. For a diagonal element of $\Gamma$,
+% Here $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \to 0 \textrm{ and } O_2 = {\mathcal{O}}(1/n) \to 0$ as $n \to \infty$. For a diagonal element of $\Gamma$,
 % We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term.
@@
 %
-\begin{align*}
-& \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
-& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
-\end{align*}
-Note that $ \hat{\Gamma}_{G,s}(k)$ is less negatively biased as compared to $\hat{\Gamma}_s(k)$.
+% \begin{align*}
+% & \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
+% & = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
+% \end{align*}
+% Note that $ \hat{\Gamma}_{G,s}(k)$ is less negatively biased as compared to $\hat{\Gamma}_s(k)$.
 In the presence of positive correlation, the leftover $o(n^{-1})$ term is positive which further counters the negative bias of $\hat{\Gamma}_{G,s}(k)$.
@@
 \begin{align*}
-    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t \in I_k}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T \\ 
-    \tilde{\Sigma}_s &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Upsilon}_s(k) \,.
-\end{align*}
-%
-The average pseudo spectral variance estimator is
-\[
-\tilde{\Sigma}_A = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
-\]
-
+    \tilde{\Upsilon}_s(k) &= \dfrac{1}{n}\sum_{t \in I_k}(Y_{st}-\mu_g)(Y_{s(t+k)}-\mu_g)^T  \quad \text{and} \quad 
+    \tilde{\Sigma}_s = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\tilde{\Upsilon}_s(k) \,.
+\end{align*}
+%
+The average pseudo spectral variance estimator is $\tilde{\Sigma}_A = m^{-1}\sum_{s=1}^{m}\tilde{\Sigma}_s$
+% \[
+% \tilde{\Sigma}_A = \dfrac{1}{m}\sum\limits_{s=1}^{m}\tilde{\Sigma}_s
+% \]
+% 
 Further, let
@@
 Under the assumptions of Theorem~\ref{thm:kuelbs}, $\psi(n) = o(n^{1/2})$.
-Using Law of Iterative Logarithms (LIL), a tighter bound for $\psi(n)$ is given by \cite{stra:1964} as $o(\sqrt{n\log \log n})$.
-We have already assumed that $b_n \log \log n / n \to 0$ as $n \to \infty$.
-Consequently,
+Using the law of iterative logarithms (LIL), a tighter bound for $\psi(n)$ is given by \cite{stra:1964} as $o(\sqrt{n\log \log n})$.
+Since $b_n \log \log n / n \to 0$ as $n \to \infty$, consequently,
 $b_n \psi^2(n)/n^2 \to 0$, $\psi^2(n)/n^2 \to 0$, ${b_n\psi(n)\sqrt{n\log \log n}/n^2} \to 0$, and $\psi(n) \sqrt{n \log \log n}/n^2 \to 0$.
@@
 %
-\begin{proof}[Proof of theorem \ref{th:consistency}]
+\begin{proof}[Proof of Theorem \ref{th:consistency}]
 We have the following decomposition,
@@
 %
-
+%
 \[
@@
 % \begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
- Due to the strong consistency proof from theorem \ref{th:consistency}, as $n \to \infty$,
+ Due to the strong consistency proof from Theorem \ref{th:consistency}, as $n \to \infty$,
 \begin{equation}
@@
 \section{Additional Examples}
-We present two additional real-world examples to illustrate the advantage of global autocovariance estimator using ACF plots.
-For both the examples, we use a pre-established Markov chain structure and implement our estimator on the Markov chains obtained.
+We present two additional examples to illustrate the advantage of the G-ACF estimator. 
+% For both the examples, we use a pre-established Markov chain structure and implement our estimator on the Markov chains obtained.
 % We have established that estimating autocovariance is crucial to estimate the Markov chain standard error.
@@
 
-This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature.
-Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second and third component.
+This yields a 7-dimensional posterior distribution in $\lambda = (\lambda_1, \dots, \lambda_7)^T$.
+Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points for the second and third component.
 We report the ACF plots for the second component component only, however, similar behavior is observed in ACF plots of other components as well.
@@
     \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
-    \caption{Trace plot for second (left) and third (right) component of two chains started from random points. The two colors denote the two different chains.}
+    \caption{Trace plot for second (left) and third (right) component of two chains.}
     \label{fig:poisson-trace}
@@
 For a chain length of $n=1000$, locally-centered ACF gives a false sense of security about the Markov chains whereas in reality, the process is highly correlated.
-G-ACF gives a more accurate estimation of autocorrelations in almost ten times lesser samples per chain.
+G-ACF gives a more accurate estimation of autocorrelations even at short run lengths.
 
@@
 
-The \texttt{faux.magnolia.high} dataset available in the \texttt{ergm} \texttt{R} package represents a simulated within school friendship network based on Ad-Health data (\cite{resnick1997protecting}).
+The \texttt{faux.magnolia.high} dataset available in the \texttt{ergm} \texttt{R} package represents a simulated friendship network based on Ad-Health data (\cite{resnick1997protecting}).
 The school communities represented by the network data are located in the southern United States.
@@
 
-We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking".
+% We believe that the students from different races experience different socio-political conditions which causes them to engage in a "selective networking".
 This might cause formation of clusters in the social network.
-We sample two parallel Markov chains starting from two students belonging to different races and study its impacts on the average features of their immediate social group, especially their grades.
+We sample two parallel Markov chains starting from two students belonging to different races.
+ % and study its impacts on the average features of their immediate social group, especially their grades.
 Due to cluster formation in the network, a Markov chain will land on students within a cluster more often than on students outside it.
 As a consequence, the sample averages for the two chains will differ for a relatively shorter chain length.
-
+% 
 Figure~\ref{fig:magnolia-acf} shows the ACF plots for the \textit{grade} feature at two different simulation sizes for $m=2$ parallel Markov chains.

### 2020-09-02 Paper/main.tex
Chal chale apne ghar

@@
     & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
-    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
+    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
 \end{align*}
@@
 \[
-\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})\,.
+\Var(\bar{X}_s) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})\,.
 \]
@@
 
-\subsection{Strong consistency argument} \label{appendix:strong_consis}
+\subsection{Strong consistency of G-SV estimator} \label{appendix:strong_consis}
 
@@
     g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
-    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
+    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0 \quad \text{as }n \to \infty\,.
 \end{align*}
@@
 \begin{align*}
-\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
+\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}
 \end{align*}
@@
     &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k)\right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\
-    & = P_1 + P_2\,,
+    & = P_1 + P_2\,, \numberthis \label{eq:bias_gsve}
 \end{align*}
@@
 \end{align*}
-
+%
 %
@@
 \begin{align*}
- \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}\abs{k} \Upsilon(k)  \,.
+ \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)   &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k} \Upsilon(k)  \,.
 \end{align*}
@@
 
-  Finally, we will solve for $P_2$.
-Note that $O_2$ is independent of $k$.
-We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$.
-We will find an upper bound and prove that it is $o\left(b_n^{-q}\right)$:
-  \begin{align*}
-      &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)( O_1 + O_2) \\
-      & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)}\\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)}\\
+Finally, we will solve for $P_2$. Note that $O_1 = (\abs{k}/n)\mathcal{O}(1/n)$ and $O_2 = \mathcal{O}(1/n)$. So,
+  \begin{align*}
+    P_2  & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{k}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
+      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
       &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
@@
 %
-Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
+Using \eqref{eq:P1_decomp},\eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:bias_gsve},
 \[

### 2020-09-02 Paper/main.tex
zzzzz (done with the appendix)

@@
 Conditions for strong consistency of $\hat{\Sigma}_s$ for polynomially ergodic Markov chains are in \cite{vats:fleg:jon:2018}.
-Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.
-
-Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}.
-However, \cite{hannan:1970} proved the results assuming $\mu_g$ was known.
-Here, we present the results under mild conditions for when $\mu_g$ is replaced by $\bar{\bar{Y}}$.
+Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}.
 Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, respectively.
@@
 \[
-\lim _{x \to 0} \dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty
-\] 
-and $b_n^q/n \to 0$ as $n \to \infty$. Then $ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.$
+\lim _{x \to 0} \dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty\,
+\] 
+and $b_n^{q+1}/n \to 0$ as $n \to \infty$. Then $ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.$
 % \[
@@
 \end{theorem}
+\cite{hannan:1970} proved a similar bias result assuming $\mu_g$ was known with the rate $b_n^q/n \to 0$ as $n \to \infty$.
+Similar to \cite{ande:1971} for the univariate case, in Theorem~\ref{th:G-SVE_bias}, we require $b_n^{q+1}/n \to 0$ as $n\to \infty$ for the multivariate case for when $\mu_g$ is replaced by $\bar{\bar{Y}}$.
 
@@
     P_2  & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{k}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
-      &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
- \end{align*}
-
-%
-Using \eqref{eq:P1_decomp},\eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:bias_gsve},
+      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{k}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
+      &= \mathcal{O}\left(\dfrac{b_n}{n}\right)\dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
+      &= \mathcal{O}\left(\dfrac{b_n}{n}\right) = o\left(\dfrac{b_n}{b_n^{q+1}}\right) = o\left(\dfrac{1}{b_n^{q}}\right) \,. \numberthis \label{eq:P_2}
+ \end{align*}
+
+%
+Using \eqref{eq:P1_decomp},\eqref{eq:P1_first}, \eqref{eq:P1_second}, \eqref{eq:P1_third}, and \eqref{eq:P_2} in \eqref{eq:bias_gsve},
 \[
@@
 % \begin{proof}[Proof of Theorem~\ref{th:G-SVE_variance}]
- Due to the strong consistency proof from Theorem \ref{th:consistency}, as $n \to \infty$,
-\begin{equation}
-\label{eq:G-SVE_asv_consis}
- \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
-\end{equation}
-We have shown from the proof of strong consistency that,
+%  Due to the strong consistency proof from Theorem \ref{th:consistency}, as $n \to \infty$,
+% \begin{equation}
+% \label{eq:G-SVE_asv_consis}
+%  \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
+% \end{equation}
+% We have shown from the proof of strong consistency that,
+By Lemma~\ref{lemma:G-SVE_breakdown},
 \begin{align*}
@@
 \end{align*}
-where it has been shown already that $g_1(n), g_2(n), g_3(n) \to 0$ as $n \to \infty$. By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that
+where $g_1(n), g_2(n), g_3(n) \to 0$ as $n \to \infty$ as defined in Lemma~\ref{lemma:G-SVE_breakdown}. Then there exists an $N_0$ such that
 \begin{align*}
@@
 \[
-\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]
+\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\,.
 \]
@@
 \begin{equation} \label{eq:hannan_var}
-\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = \left[\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right) \right]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
+\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = \left[\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right) \right]\int_{-\infty}^{\infty}w^2(x)dx + o(1)\,.
 \end{equation}

### 2020-09-03 Paper/main.tex
Reviewed first two sections. Heading to ze office.

@@
 \begin{abstract}
-Autocovariances are a fundamental quantity of interest in Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain.
+Autocovariances are a fundamental quantity of interest in Markov chain Monte Carlo (MCMC) simulations with autocorrelation function (ACF) plots being an integral performance assessment visualization tool.
 Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth.
-For multiple chain MCMC sampling,  we propose a globally-centered estimator of the autocovariance function (G-ACvF) that exhibits theoretical and empirical improvements.
+For multiple chain MCMC sampling,  we propose a globally-centered estimator of the autocovariance function (G-ACvF) that exhibits significant theoretical and empirical improvements.
 We show that the bias of the G-ACvF estimator is smaller than the bias of the current state-of-the-art.
@@
 Under weak conditions, we establish strong consistency of an improved asymptotic covariance estimator, and obtain its large sample bias and variance.
+The performance of the new G-ACvF estimator is demonstrated through various examples.
 \end{abstract}
@@
 For slow mixing chains, the chains take time to traverse the space so that $\bar{X}_s$  are all vastly different.
-Consequently, $\hat{\Gamma}_s(k)$ typically underestimates $\Gamma(k)$ leading to a false sense of security about the quality of process.
+Consequently, $\hat{\Gamma}_s(k)$ typically underestimates $\Gamma(k)$ leading to a false sense of security about the quality of the process.
 
@@
 Specifically, spectral variance (SV) estimators  are used to estimate $\Sigma = \sum_{k=-\infty}^{\infty} \Gamma(k)$ \citep{andr:1991,dame:1991,fleg:jone:2010}.
-We replace $\hat{\Gamma}_s(k)$ with G-ACvF in SV estimators to obtain globally-centered SV (G-SV) estimator and demonstrate strong consistency under weak conditions.
+We replace $\hat{\Gamma}_s(k)$ with G-ACvF in SV estimators to obtain a globally-centered SV (G-SV) estimator and demonstrate strong consistency under weak conditions.
 In the spirit of \cite{andr:1991}, we also obtain large-sample bias and variance of the resulting estimator.
@@
 
-In Figure~\ref{fig:gaussian-acf} for $n = 10^4$, we present the ACF plots using $\hat{\Gamma}_s(k)$ and our proposed G-ACF estimator.
+In Figure~\ref{fig:gaussian-trace} for $n = 10^4$, we present the ACF plots using $\hat{\Gamma}_s(k)$ and our proposed G-ACvF estimator.
 The blue curves are the respective estimates at $n = 10^5$.
 At $n = 10^5$ when the chains have similar means, the G-ACF and locally-centered ACF are equivalent.
-However, for $n = 10^4$, $\hat{\Gamma}_s(k)$ critically underestimate the correlation giving user a misleading visual of the quality of the Markov chain.
+However, for $n = 10^4$, $\hat{\Gamma}_s(k)$ critically underestimates the correlation giving users a misleading visual of the quality of the Markov chain.
 The G-ACF estimator accounts for the discrepancy in sample means between two chains leading to a far improved quality of estimation.
@@
 \centering
-   \includegraphics[width=.35\linewidth]{plots/gaussian-Targettrace_n1e4.pdf}
-    \includegraphics[width=.35\linewidth]{plots/gaussian-Targettrace_n1e5.pdf} 
-    \caption{Target density and trace plots for two chains at $n = 10^4$ (left) and $n = 10^5$ (right)}
+   \includegraphics[width=.62\linewidth]{plots/gaussian-Targettrace.pdf}\\
+\vspace{-.5cm}
+    \includegraphics[width=.62\textwidth]{plots/gaussian-acf_hist.pdf} 
+    \caption{Top: Target density and trace plots for two chains at $n = 10^4$ (left) and $n = 10^5$ (right).
+Bottom: ACF plots for the first chain using local-centering (left) and global-centering (right).
+Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 10^5$.}
     \label{fig:gaussian-trace}
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.6\textwidth]{plots/gaussian-acf_hist.pdf} \\
-% \includegraphics[width=.6\textwidth]{plots/gaussian-acf_1e4.pdf}
-
-\caption{ACF plots using local-centering (left) and global-centering (right). Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 10^5$ for the first chain.}
+% \begin{figure}[htbp]
+% \centering
+% \includegraphics[width=.6\textwidth]{plots/gaussian-acf_hist.pdf} \\
+% % \includegraphics[width=.6\textwidth]{plots/gaussian-acf_1e4.pdf}
+
+% \caption{ACF plots using local-centering (left) and global-centering (right). Histogram estimates at $n = 10^4$ with the blue curve being estimates from $n = 10^5$ for the first chain.}
  % (b) $n = 10^4$; the dotted lines are ACF for each chain and the thick solid line is the ACF averaged over both chains.}
-\label{fig:gaussian-acf}
-\end{figure}
+% \label{fig:gaussian-acf}
+% \end{figure}
 
@@
 Let $P$ denote the Markov transition kernel that uniquely determines the ACvF under stationarity.
-Recall that the sample mean of the $s^{th}$ Markov chain is $\bar{X}_s$ and denote the global mean vector by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
+Recall that the sample mean of the $s${th} Markov chain is $\bar{X}_s$ and denote the global mean vector by $\bar{\bar{X}} = m^{-1}\sum_{s = 1}^{m}\bar{X}_s$.
 The global mean is a naturally superior estimator of $\mu$ compared to $\bar{X}_s$.
@@
 %
-and let $\Phi^{(1)}$ be denoted by $\Phi$.  The proof of the following theorem is available in Appendix~\ref{appendix:bias}. Let $\|\cdot\|$ denote Euclidean norm.
+and let $\Phi^{(1)}$ be denoted by $\Phi$.  The proof of the following theorem is in Appendix~\ref{appendix:bias}. Let $\|\cdot\|$ denote Euclidean norm.
 
@@
 
-Let $\Gamma^{ii}(k)$ be the $i${th} component of $\Gamma(k)$. For component $i$, the autocorrelation is defined as
+Let $\Gamma^{ii}(k)$ and $\hat{\Gamma}_{G,s}^{ii}(k)$ be the $i${th} component of $\Gamma(k)$ and $\hat{\Gamma}_{G,s}(k)$, respectively. For component $i$, the autocorrelation is defined as
 \[
@@
 \]
-and is instrumental in visualizing the serial correlation in components of the Markov chain.
+and is instrumental in visualizing the serial correlation in the components of the Markov chain.
 A standard estimator of the autocorrelation is constructed from $\hat{\Gamma}_s(k)$.
@@
 \label{eq:acf}
- \hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}. 
+ \hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{ii}_{G,s} (k)}{\hat{\Gamma}^{ii}_{G,s} (0)}. 
 \end{equation}
-The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of marginal components of the chain  as evidenced in Figure~\ref{fig:gaussian-acf}.
+The globally-centered autocorrelation provides a far more realistic assessment of the correlation structure of the marginal components of the chain  as evidenced in Figure~\ref{fig:gaussian-trace}.
 

### 2020-09-03 one_run.R

@@ -26,17 +26,16 @@ chain2 <- mc.chain.list[[2]]
 ## Figure 1a
 
 x <- seq(-10, 10, length = 1e3)
-pdf(file = "AllOut/gaussian-TargetTrace_n1e4.pdf", height = 5, width = 6)
+pdf(file = "AllOut/gaussian-TargetTrace.pdf", height = 5, width = 10)
+par(mfrow = c(1,2))
 plot(x, 20000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd = 1.5, xlab = "x", ylab = "", ylim = c(-10000,6000), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
 plot(x = chain1[1:1e4], y = seq(-1, -1e4, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e4, 6e3), , xlim = range(chain1,chain2), yaxt = 'n')
 lines(x = chain2[1:1e4], y = seq(-1, -1e4, -1), col = "plum3")
 mtext(side = 2, text = "Time", line = 1)
 legend("top", legend=c("Target", "Chain 1", "Chain 2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=1, lwd=2, bty = "n")
-dev.off()
 
 #Figure 1b
-pdf(file = "AllOut/gaussian-TargetTrace_n1e5.pdf", height = 5, width = 6)
 plot(x, 200000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd = 1.5, xlab = "x", ylab = "", ylim = c(-1e5,6e4), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
 plot(x = chain1, y = seq(-1, -1e5, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e5, 6e4), , xlim = range(chain1,chain2), yaxt = 'n')
@@ -45,7 +44,7 @@ mtext(side = 2, text = "Time", line = 1)
 legend("top", legend=c("Target", "Chain 1", "Chain 2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=1, lwd=2, bty = "n")
 dev.off()
 
-#################### Figure 2 #######################
+#################### Figure 1 (bottom) #######################
 
 lag.max <- 50
 nsim1 <- 1e4
[…]

### 2020-09-03 Paper/Submissions/JCGS/First/arxiv/main.tex
Pushing submission to JCGS changes

--- 2020-09-03 Paper/main.tex
@@
 \begin{abstract}
-Autocovariances are a fundamental quantity of interest in Markov chain Monte Carlo (MCMC) simulations with autocorrelation function (ACF) plots being an integral performance assessment visualization tool.
+Autocovariances are a fundamental quantity of interest in Markov chain Monte Carlo (MCMC) simulations with autocorrelation function (ACF) plots being an integral visualization tool for performance assessment.
 Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth.
-For multiple chain MCMC sampling,  we propose a globally-centered estimator of the autocovariance function (G-ACvF) that exhibits significant theoretical and empirical improvements.
+For multiple-chain MCMC sampling,  we propose a globally-centered estimator of the autocovariance function (G-ACvF) that exhibits significant theoretical and empirical improvements.
 We show that the bias of the G-ACvF estimator is smaller than the bias of the current state-of-the-art.
 The impact of this improved estimator is evident in three critical output analysis applications: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
-Under weak conditions, we establish strong consistency of an improved asymptotic covariance estimator, and obtain its large sample bias and variance.
-The performance of the new G-ACvF estimator is demonstrated through various examples.
+Under weak conditions, we establish strong consistency of an improved asymptotic covariance estimator, and obtain its large-sample bias and variance.
+The performance of the new estimators is demonstrated through various examples.
 \end{abstract}
@@
 
-A critical use of autocovariances is in the assessment of Monte Carlo variability of estimators.  Let $g:\X \to \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
+A critical need of autocovariances is in the assessment of Monte Carlo variability of estimators.  Let $g:\X \to \mathbb{R}^p$ be an $F$-integrable function so that interest is in estimating
 $\mu_g = \mathbb{E}_F[g(X)]$.
@@
  % 
-Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for all $s = 1, \dots, m$.
+Set $\{Y_{st}\}_{t \geq 1} = \{g(X_{st})\}_{t \geq 1}$ for $s = 1, \dots, m$.
 Let $\bar{Y}_s = n^{-1}\sum_{t=1}^{n}Y_{st}$  and  $\bar{\bar{Y}} = m^{-1}\sum_{s=1}^{m}\bar{Y}_s$.
@@
 %
-\begin{equation}
-\label{eq:CLT}
-  \sqrt{mn}(\bar{\bar{Y}} - \mu_g) \xrightarrow{d} N(0,\Sigma)\, \quad \text{ where, }
-\end{equation}
-% where
-\begin{equation}
-\label{eq:sigma}
+\begin{align*}
+  \sqrt{mn}(\bar{\bar{Y}} - \mu_g) \xrightarrow{d} N(0,\Sigma)\, \quad \text{ where }  \quad 
   \Sigma = \sum_{k = -\infty}^{\infty} \Cov_F \left( Y_{11}, Y_{1(1+k)} \right) := \sum_{k = -\infty}^{\infty}\Upsilon (k)\,.
-\end{equation}
+\end{align*}
+% \begin{equation}
+% \label{eq:CLT}
+
+% \end{equation}
+% % where
+% \begin{equation}
+% \label{eq:sigma}
+
+% \end{equation}
 %
@@
 Here, we utilize G-ACvF estimators to construct globally-centered SV (G-SV) estimator of $\Sigma$.
-Using the method of \cite{heberle2017fast}, we also provide a computationally efficient algorithm for obtaining the G-SV estimator.
-
-The locally and globally-centered  estimators of $\Upsilon(k)$ are $\hat{\Upsilon}_s(k)$ and $\hat{\Upsilon}_{G,s}(k)$, respectively, where for $k \geq 0$
+Using the method of \cite{heberle2017fast}, we also provide a computationally efficient implementation of the G-SV estimator.
+
+For $k \geq 0$, the locally and globally-centered  estimators of $\Upsilon(k)$ are
 \[
@@
 \] 
-and let $\hat{\Upsilon}_G(k) = m^{-1} \sum_{k=1}^{m}\hat{\Upsilon}_{G,s}(k)$.
+respectively.
+Let $\hat{\Upsilon}_G(k) = m^{-1} \sum_{k=1}^{m}\hat{\Upsilon}_{G,s}(k)$.
 SV estimators are constructed as weighted and truncated sums of estimated ACvFs.
-For some $c \geq 1$, let $w: \mathbb{R} \to [-c,c]$ be a lag window function and $b_n \in \mathbb{N}$ be a bandwidth.
+For some $c \geq 1$, let $w: \mathbb{R} \to [-c,c]$ be a lag window function and $b_n \in \mathbb{N}$ be a truncation point.
 The (locally-centered) SV estimator of $\Sigma$ for chain $s$ is
@@
 \begin{equation} \label{eq:sve}
-    \hat{\Sigma}_{s} = \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_s(k)\,.
+    \hat{\Sigma}_{s} = \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_s(k)\,.
 \end{equation}
 Large-sample properties of $\hat{\Sigma}_s$ have been widely studied.
-\cite{vats:fleg:jon:2018} provide conditions for strong consistency while \cite{fleg:jone:2010,hannan:1970} provide large-sample bias and variance results.
+\cite{vats:fleg:jon:2018} provide conditions for strong consistency while \cite{fleg:jone:2010,hannan:1970} obtain bias and variance.
 These results also extend naturally to an average SV (ASV) estimator defined as $\hat{\Sigma}_A := m^{-1} \sum_{s=1}^{m}\hat{\Sigma}_{s}$.
@@
 %
-\begin{align*}
-    \hat{\Sigma}_{G} &= \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_{G}(k)\,.
-\end{align*}
-%
-Standard conditions are imposed on the lag window, $w$. 
+\begin{equation}
+\label{eq:gsve_estimator}
+    \hat{\Sigma}_{G} = \sum_{k= -b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Upsilon}_{G}(k)\,.
+\end{equation}
+%
+% Standard conditions are imposed on the lag window, $w$. 
 %
@@
 \label{ass:lag_window}
-The lag window $w(x)$ is continuous at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\sum_{k = -\infty}^{\infty} \abs{w(k/b_n)} < \infty$.
+The lag window $w(x)$ is continuous at all but a finite number of points, is a bounded and even function with $w(0)=1$, \; $\int_{-\infty}^{\infty}w^2(x)dx < \infty$, and $\int_{-\infty}^{\infty} \abs{w(x)} < \infty$.
 \end{ass}
 
-Assumption~\ref{ass:lag_window} is standard \citep[see][]{ande:1971} and is satisfied by most lag windows. We will use the following popular Bartlett lag window in our simulations:
-\[
-w(x) = \begin{cases}
-1 - \abs{x} & \textrm{for } \abs{x} \leq 1 \\
-0 & \textrm{otherwise}\,.
-\end{cases}
-\]
+Assumption~\ref{ass:lag_window} is standard \citep[see][]{ande:1971} and is satisfied by most lag windows.
+We will the popular Bartlett lag window in our simulations for which $w(x) = 1-|x|$ for $|x| \leq 1$ and 0 otherwise.
+% \[
+% w(x) = \begin{cases}
+% 1 - \abs{x} & \textrm{for } \abs{x} \leq 1 \\
+% 0 & \textrm{otherwise}\,.
+% \end{cases}
+% \]
 
@@
 
+The proof the result below is in Appendix~\ref{appendix:strong_consis}.
 \begin{theorem}
@@
 Conditions for strong consistency of $\hat{\Sigma}_s$ for polynomially ergodic Markov chains are in \cite{vats:fleg:jon:2018}.
-Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}.
+Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.
+Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}.
 Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, respectively.
+The proofs of the results below can be found in Appendix~\ref{appendix:gsv_bias} and Appendix~\ref{appendix:variance}, respectively.
 
@@
 \cite{hannan:1970} proved a similar bias result assuming $\mu_g$ was known with the rate $b_n^q/n \to 0$ as $n \to \infty$.
-Similar to \cite{ande:1971} for the univariate case, in Theorem~\ref{th:G-SVE_bias}, we require $b_n^{q+1}/n \to 0$ as $n\to \infty$ for the multivariate case for when $\mu_g$ is replaced by $\bar{\bar{Y}}$.
+Similar to \cite{ande:1971} for the univariate case, if $\mu_g$ is replaced by $\bar{\bar{Y}}$, we require $b_n^{q+1}/n \to 0$ as $n\to \infty$ for the multivariate case.
 
 \begin{theorem} \label{th:G-SVE_variance}
- Let the assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E \|Y_{11}\|^4 < \infty$, then $ \lim_{n \to \infty} b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx $.
+ Let the assumptions of Theorem~\ref{thm:kuelbs} hold and let $\E[D^4] < \infty$  and  $\E_F \|Y_{11}\|^4 < \infty$, then $ \lim_{n \to \infty} b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx $.
 \end{theorem}
@@
 The SV estimator, despite having good statistical properties, poses limitations due to slow computation.
-The complexity of the SV estimator is $\mathcal{O}(n^2 p^2)$ in general, and for the Bartlett lag window, it is $\mathcal{O}(b_n n p^2)$.
+The complexity of the SV estimator is $\mathcal{O}(b_n n p^2)$.
 For slow mixing Markov chains, $n$ and $b_n$ can be prohibitively large, limiting the use of SV estimators.
-To overcome this, we adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast}.
-Suppose $w_k = w(k/b_n)$ and let $T(w)$ be the $n \times n$ Toeplitz matrix with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$.
-Notice an alternate formulation of $\hat{\Sigma}_s$
-%
-\begin{equation} \label{eq:kyriakoulis}
-    \hat{\Sigma}_s = \dfrac{1}{n}A_s^T T(w) A_s, \qquad \textrm{ where } A_s = \begin{pmatrix}
+We adapt the  fast Fourier transform based algorithm of \cite{heberle2017fast} to calculate the G-SV estimator.
+
+ Suppose $w_k = w(k/b_n)$ and let $T(w)$ be the $n \times n$ Toeplitz matrix with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$. Notice an alternate formulation of $\hat{\Sigma}_s$
+%
+\begin{equation*} \label{eq:kyriakoulis}
+    \hat{\Sigma}_s = \dfrac{1}{n}A_s^T T(w) A_s, \qquad \textrm{ where } \quad  A_s = \begin{pmatrix}
     Y_{s1} - \bar{Y}_s  & \dots & Y_{sn} - \bar{Y}_s
 \end{pmatrix}^T \,.
-\end{equation}
- \cite{heberle2017fast} compute the $n \times 1$ vector $T(w)A_s$  using an algorithm based on fast Fourier transforms.
+\end{equation*}
+ % \cite{heberle2017fast} compute the $n \times 1$ vector $T(w)A_s$  using an algorithm based on fast Fourier transforms. 
  Let $w^* = (1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1}, ~0, ~w_{n-1}, \dots, w_1)^T$ and set $C(w^*)$ to be a symmetric circulant matrix such that the matrix truncation $C(w^*)_{1:n, 1:n} = T(w)$.
-Let $M_{(j)}$ denote the $j$th column of matrix $M$ and $v^{(i)}$ denote the $i$th element of the vector $v$.
+Let $M_{(j)}$ denote the $j$th column of a matrix $M$ and $v^{(i)}$ denote the $i$th element of a vector $v$.
 With inputs $C(w^*)$ and $A_s$, Algorithm~\ref{algo:herberle} produces $\hat{\Sigma}_s$ exactly.
@@
 Compute eigenvalues $\lambda_i$ of  $C(w^*)_{(1)}$ using a discrete Fourier transform, $i = 1, \dots, 2n$\;
-Construct $2n \times p$ matrix $A^*_s = (A^T  \quad 0_{n \times q})^T$\;
+Construct $2n \times p$ matrix $A^*_s = (A_s^T  \quad 0_{n \times q})^T$\;
 
@@
     Calculate $V^*A^*_{s(j)}$ by DFT of $A^*_{s(j)}$.\;
-    Multiply $V^* A_{s(j)}^{*^{(i)}}$ with the eigenvalue $\lambda_i$ for all $i = 1, ..., 2n$ to construct $\Lambda V^* A_{s(j)}^*$.\;
+    Multiply $V^* A_{s(j)}^{*^{(i)}}$ with the eigenvalue $\lambda_i$ for all $i = 1, \dots, 2n$ to construct $\Lambda V^* A_{s(j)}^*$.\;
     Calculate $C(w^*)A^*_{s(j)} = V \Lambda V^* A_{s(j)}^*$ by inverse FFT of $\Lambda V^* A_{s(j)}^*$.\;
@@
 Setting $B_s = (Y_{s1} - \bar{\bar{Y}} \; \dots \; Y_{sn} - \bar{\bar{Y}})^T$ and calling Algorithm~\ref{algo:herberle} with inputs $C(w^*)$ and $B_s$ yields $\hat{\Sigma}_{G,s}$.
-Algorithm~\ref{algo:herberle} has complexity $\mathcal{O}(p n \log n)$ and is thus orders of magnitude faster.
+Algorithm~\ref{algo:herberle} has complexity $\mathcal{O}(n \log n p)$ and is thus orders of magnitude faster.
 Of particular importance is the fact that the bandwidth $b_n$ has close to no impact on the computation time.
@@
 
-An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to calculate the effective sample size (ESS).
-ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$ with $\bar{\bar{Y}}$.
+An useful method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is effective sample size (ESS).
+ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability in $\bar{\bar{Y}}$ as this correlated sample.
 Let $|\cdot|$ denote determinant.
@@
 We use the locally-centered $\hat{\Upsilon}(0)$ to estimate $\Upsilon(0)$ instead of $\hat{\Upsilon}_G(0)$ when calculating ESS.
-Both $\hat{\Upsilon}(0)$ and $\hat{\Upsilon}_G(0)$ are consistent  for $\Upsilon(0)$; however the typical underestimation witnessed $\Upsilon(0)$ allows a safeguard against early termination.
-
-For the sake of comparison, $\widehat{\textrm{ESS}}_A$ is constructed similarly using $\hat{\Sigma}_A$ instead of $\hat{\Sigma}_G$ to estimate $\Sigma$.  
+Both $\hat{\Upsilon}(0)$ and $\hat{\Upsilon}_G(0)$ are consistent  for $\Upsilon(0)$; however the typical underestimation witnessed in $\Upsilon(0)$ allows a safeguard against early termination.
+For comparison, $\widehat{\textrm{ESS}}_A$ is constructed similarly using $\hat{\Sigma}_A$ instead of $\hat{\Sigma}_G$ to estimate $\Sigma$.
 % We will compare $\widehat{\textrm{ESS}}_G$ to $\widehat{\textrm{ESS}}_A$ in the following Section.
@@
 
-In this section we consider three different target distributions and sample $m$ parallel Markov chains to assess the performance of our proposed estimators.
-We will make the following three comparisons - (1) locally-centered ACF vs G-ACF estimator, (2) A-SV vs G-SV estimator, and (3) $\widehat{\textrm{ESS}}_A$ vs $\widehat{\textrm{ESS}}_G$.
+For three different target distributions we sample $m$ parallel Markov chains to assess the performance of our proposed estimators.
+We make the following three comparisons - (1) locally-centered ACF vs G-ACF estimator, (2) A-SV vs G-SV estimator, and (3) $\widehat{\textrm{ESS}}_A$ vs $\widehat{\textrm{ESS}}_G$.
 The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence region when the true mean $\mu_g$ is known.
 The convergence of local and global estimators of $\Sigma$ and $\widehat{\textrm{ESS}}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$.
-In all the examples we are interested in estimating the mean of the stationary distribution $\mu$, so $g$ is the identity function.
-The bandwidth $b_n$ are the defaults available in the \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.
-
-% There are only a handful of MCMC chains where the true autocovariance and asymptotic variance are known.
-To compare the globally and locally-centered estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)).
-A distinct advantage of our estimators is observed when the target distribution is multi-modal.
-For this purpose we use a bivariate bi-modal probability distribution introduced by \cite{gelman1991note}.
-Through this example, we will also show that in case of nicely mixing Markov chains, these estimat give almost equivalent results.
-Lastly, we consider a real-life example of finding unknown locations of sensors using noisy distance data.
-The posterior distribution is this case is marginally bimodal in all dimensions.
-All the examples have been selected to display some kind of \textit{sticky} nature in the Markov chains.
-In such scenario, we successfully show that our globally-centered estimators yield better results as compared to the classical single-chain estimators for autocovariance, asymptotic variance, and effective sample size.
+In all three examples, we estimate the mean of the stationary distribution, so $g$ is the identity function.
+The truncation point $b_n$ are the defaults available in the \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.
 
@@
 
-Our first example is one where the $\Upsilon$ and $\Sigma$ are available in closed-form, so we can compare quality of estimation against a known truth.
+Our first example is one where the $\Upsilon$ and $\Sigma$ are available in closed-form, to allow a comparison of quality of estimation.
 Consider a $p$-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
 %
-\[
-X_t = \Phi X_{t-1} + \epsilon_t
-\]
-%
-where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{iid}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix.
+\begin{equation*}
+X_t = \Phi X_{t-1} + \epsilon_t\,,  
+\end{equation*}
+%
+where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{\text{iid}}{\sim} N(0, \Omega)$, and $\Omega$ is a positive-definite $p \times p$ matrix.
 We fix $\Omega$ be a AR correlation matrix with parameter .9.
@@
 For $k \geq 0$, the lag-$k$ autocovariance is $\Upsilon(k) = \Gamma(k) = \Phi^k\Psi$.
-The process satisfies a CLT for $\bar{X} = n^{-1} \sum_{t=1}^{n} X_t$ if the spectral norm of $\Phi$ is less than 1 \citep{10.2307/1427459} and the limiting covariance, $\Sigma$ is known in closed form \citep{dai:jon:2017}.
-We set $p = 2$ and set $\Phi$ such that its eigenvalues are .999 and .001.
-The resulting process mixes slowly and allows us to highlight the difference in the estimation of ACvF.
+The process satisfies a CLT if the spectral norm of $\Phi$ is less than 1 \citep{tjos:1990} and the limiting covariance, $\Sigma$, is known in closed form \citep{dai:jon:2017}.
+We set $p = 2$ and set $\Phi$ to have eigenvalues .999 and .001.
+% The resulting process mixes slowly and allows us to highlight the difference in the estimation of ACvF. 
 We further set $m = 5$ with starting values dispersed across the state space.
+
+We compare the the locally and globally-centered autocorrelations against the truth.
+In Figure~\ref{fig:var-acf} are the estimated ACF plots for the first component of the second chain against the truth in red.
+For a run length of $10^3$ (top row), the commonly used locally-centered ACF underestimates the true correlation giving a false sense of security about the mixing of the chain.
+The G-ACF estimator, on the other hand, is far more accurate.
+This difference is negligible at the larger run length of $n = 10^4$ when each of the 5 chains have sufficiently explored the state space.
+
 \begin{figure}[htbp]
@@
 
-We compare the the locally and globally-centered autocorrelations against the truth.
-In Figure~\ref{fig:var-acf} are the estimated ACF plots for the first component of the second chain against the truth in red.
-For a run length of $10^3$ (top row), the commonly used locally centered ACF underestimates the true correlation structure giving a false sense of security about the mixing of the chain.
-The G-ACF estimator, on the other hand, is able to more accurately measure the ACF of the chain.
-This difference is negligible at the larger run length of $n = 10^4$ when each of the 5 chains have sufficiently explored the state space.
-
 Since $\mu$ is known, we assess the performance of A-SV and G-SV estimatiors by assessing coverage probabilities of $95\%$ Wald confidence regions over 1000 replications.
-Table~\ref{tab:var-coverage} shows that for each sample size, the $\hat{\Sigma}_G$ results in close to nominal coverage probability, whereas $\hat{\Sigma}_A$ yields critically low coverage.
+Table~\ref{tab:var-coverage} shows that irrespective of sample size, $\hat{\Sigma}_G$ results in close to nominal coverage probability, whereas $\hat{\Sigma}_A$ yields critically low coverage.
 The low coverage is a consequence of underestimating the autocovariances.
@@
     \end{tabular}
-    \caption{VAR. Coverage probabilities at $95 \%$ nominal level. Replications $= 10^3$.}
+    \caption{VAR. Coverage probabilities at $95 \%$ nominal level. Replications $= 1000$.}
     \label{tab:var-coverage}
@@
       \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
-    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV estimator. (Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV estimator.}
+    \caption{VAR. (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV estimator. (Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV estimator.}
     \label{fig:var-frob_n_ess}
@@
 
-\subsection{Boomerang Distribution} \label{ex:boomerang}
+\subsection{Boomerang target distribution} \label{ex:boomerang}
 
@@
 \end{align*}
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width = .75\textwidth]{plots/boom-all_1_3_8.pdf}\\
-    \includegraphics[width = .75\textwidth]{plots/boom-all_1_10_7.pdf}    
-    % \includegraphics[width = 0.6\textwidth ]{plots/boom-acf_1_10_7_n1000.pdf}
-
-    \caption{Boomerang.
-Top row is Setting 1 and bottom row is Setting 2.
-Contour plots of the target distributions  overlaid with scatter plots for two chains for both settings.
-Locally-centered ACF (middle) and G-ACF (right) plots for one chain for $n = 1000$ with the blue line being the respectie ACF at $n = 10^4$.
-}
-   \label{fig:boom-2D}
-\end{figure}
 
@@
 
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width = .70\textwidth]{plots/boom-all_1_3_8.pdf}\\
+    \includegraphics[width = .70\textwidth]{plots/boom-all_1_10_7.pdf}    
+    \caption{Boomerang.
+Top row is Setting 1 and bottom row is Setting 2.
+Contour plots of the target distributions  overlaid with scatter plots for two chains.
+Locally-centered ACF (middle) and G-ACF (right) plots for one chain for $n = 10^3$ with the blue line being the ACF at $n = 10^4$.
+}
+   \label{fig:boom-2D}
+\end{figure}
+
 We run $m=5$ parallel Markov chains with starting points evenly distributed across the state space.
 For setting 1, when the Markov chains have not been able to jump modes, locally-centered ACF severely underestimates autocorrelation.
-This is seen in the top-middle plot of Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$ (overlaid blue line).
+This is seen in the top-middle plot of Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ are drastically different from the locally-centered autocorrelations at $n = 10^4$.
 Somewhere between $n = 1000$ and $n = 10^4$, the Markov chains jump modes and it is only then that the locally-centered ACFs provide better estimates.
 The G-ACFs,  on the other hand, produce similar ACF estimates at $n = 1000$ and $n = 10^4$ by measuring deviations about the global mean.
-For setting 2, both methods yield similar ACFs  reinforcing our claim that there is much to gain by using G-ACvF and nothing to lose.
-{\color{orange} At what sample size?}
+For setting 2, at $n = 1000$, both methods yield similar ACFs  reinforcing our claim that there is much to gain by using G-ACvF and nothing to lose.
 
@@
 
+In Figure~\ref{fig:boom-ess} we present running plots of estimates of $\log(\textrm{ESS})/mn$ for both setting 1 and setting 2.
+As the sample size increases, $\widehat{\text{ESS}}_G$ and  $\widehat{\text{ESS}}_A$ become closer, but early on for setting 1, $\widehat{\text{ESS}}_G$ estimates are much smaller, safeguarding users against early termination.
+
 \begin{figure}[htbp]
@@
 
-In Figure~\ref{fig:boom-ess} we present running plots of estimates of $\log(\textrm{ESS})/mn$ for both setting 1 and setting 2.
-As the sample size increases, $\widehat{\text{ESS}}_G$ and  $\widehat{\text{ESS}}_A$ become closer, but early on for setting 1, $\widehat{\text{ESS}}_G$ estimates are much smaller, safeguarding users against early termination.
-
- % and $\log \widehat{\textrm{ESS}}_A/mn$ as $n$ increases can be seen in Figure~\ref{fig:boom-ess}.
-We can see that in the beginning, A-SVE gives misleadingly higher estimates of ESS$/mn$ than G-SVE.
-This can cause us to stop the sampling before each chain jumps to the other mode.
-As a consequence, each chain will correspond to a uni-modal target distribution.
-Whereas, as expected, the ESS estimates for setting-2 are almost same.
-Similarly, $\|\hat{\Sigma}_G\|_F$ reaches the convergence point in less than half the time as $\|\hat{\Sigma}_G\|_F$; as evidenced in Figure~\ref{subfig:boom-frob1}.
-No significant difference can be observed for setting-2 (Figure~\ref{subfig:boom-frob2}).
-
-% \begin{figure}[h]
-%     \centering
-%     \includegraphics[width = .30\textwidth]{plots/boom-frob_1_3_8_m5.pdf}  
-%     \includegraphics[width = .30\textwidth]{plots/boom-frob_1_10_7_m5.pdf}
-
-%     \caption{Boom: Running plot of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log (\|\hat{\Sigma}_G\|_F)$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
-%     \label{fig:boom-frob}
-% \end{figure}
-
 \subsection{Sensor network localization}
 
-Consider the sensor network localization problem Overleaf \cite{ihler2005nonparametric} where the goal is to identify unknown sensor locations using noisy distance data.
+Consider the sensor network localization problem of \cite{ihler2005nonparametric} where the goal is to identify unknown sensor locations using noisy distance data.
 We use the data and the model as specified by \cite{tak2018repelling}.
@@
 
-\begin{figure}[h]
+We run $m = 5$ parallel Markov chains with well-separated starting points.
+Coverage probabilities are not estimable since the true posterior mean is unknown.
+Trace plot of $x_{11}$ for two Markov chains is shown in Figure~\ref{fig:sensor-trace}.
+Figure~\ref{fig:sensor-trace} also  plots locally and globally-centered ACFs.
+As seen in previous examples, early estimates of locally-centered ACFs are much smaller than later estimates.
+The globally-centered ACFs, on the other hand are similar at small and large sample sizes.
+Figure~\ref{fig:sensor-frob_n_ess} presents the running plot of $\log \|{\Sigma}\|_F$ and $\log \textrm{ESS}/mn$ using A-SV and G-SV  estimators along with standard errors from $10$ replications.
+In both the plots, G-SV estimator and $\widehat{\textrm{ESS}}_G/mn$ reach stability significantly earlier than A-SV estimator and $\widehat{\textrm{ESS}}_A/mn$.
+
+\begin{figure}[htbp]
     \centering
@@
 
-We run $m = 5$ parallel Markov chains with well-separated starting points.
-Coverage probabilities are not estimable since the true posterior mean is unknown.
-Trace plot of $x_{11}$ for two Markov chains is shown in Figure~\ref{fig:sensor-trace}.
-Figure~\ref{fig:sensor-trace} also  plots locally and globally-centered ACFs.
-As seen in previous examples, early estimates of locally-centered ACFs are much smaller than later estimates.
-The globally-centered ACFs, on the other hand are similar at small and large sample sizes.
-Figure~\ref{fig:sensor-frob_n_ess} presents the running plot of $\log \|{\Sigma}\|_F$ and $\log \textrm{ESS}/mn$ using A-SV and G-SV  estimators along with standard errors from $10$ replications.
-In both the plots, G-SV estimator and $\widehat{\textrm{ESS}}_G/mn$ reach stability significantly earlier than A-SV estimator and $\widehat{\textrm{ESS}}_A/mn$.
-
 \section{Discussion} \label{sec:discussion}
@@
 We provide a globally-centered estimate of the ACvF that leads to improvements in all three aspects of MCMC output analysis.
-
-% It has been concluded in the paper that all of this can be significantly avoided by sampling multiple chains starting from dispersed points and pooling in the information from all chains to build consistent estimators for $\Gamma(k)$, $\Sigma$, and ESS.
-We have derived the bias of G-ACvF.
-We have shown that not only G-ACvF is asymptotically unbiased but also counters the negative bias of single chain ACF estimator by an amount proportional to the number of chains $m$.
-We have also proved the strong consistency of G-SVE and derived its limiting bias and variance results.
-Although the asymptotic results for G-SVE match those for SVE in \cite{andr:1991}, finite sample advantages are observed in terms of better coverage probability and faster convergence to truth.
-
-% Calculation of exact ACF has been done for simple stationary stochastic models like autoregressive (AR) models (under assumption of stationarity), moving average (MA) (\cite{quenouille1947notes}), and autoregressive-moving-average (ARMA) (\cite{box2015time}) models.
-We have already shown the impact of G-ACF for VAR(1) model where the truth is known.
-This gives us sufficient reason to believe that similar advantage will be observed for all the other models mentioned above in case of slowly mixing chains.
-Comparison to truth will reveal similar behavior However, for most of the complex sampling algorithms (including MCMC), we rely on sample estimators for ACF.
-
-In our simulations, we use the Bartlett lag window, which is convenient but not optimal.
-The untruncated quadratic spectral lag window of \cite{andr:1991} is known to be mean-squared optimal and could easily be used here to obtain $\hat{\Sigma}_G$.
-The quadratic spectral lag window is typically slow to compute, but by adapting  \citeauthor{heberle2017fast}'s algorithm, the implementation is similar to that of Bartlett's.
-
-% Lag window comparisons done by  reveal that quadratic spectral (QS) lag window gives consistently better coverage probabilities for any confidence interval.
-However, SVE gives poor coverage probability for all lag windows when the amount of autocorrelation is high in the Markov chain.
-Recently, \textit{lugsail} lag window has been proposed by \cite{vats2018lugsail} to deal with this issue by deliberately accentuating the autocovariance at smaller lags.
-We have refrained from doing lag window comparisons for G-SVE in our examples but we believe it can help improve the estimation quality significantly.
-%
-
-Another class of estimators for asymptotic variance of Monte Carlo averages are the multivariate initial sequence (mIS) estimators \citep{dai:jon:2017}.
-Similar to SV estimator, ACvFs are a  fundamental part of mIS estimators and underestimation in ACvFs yields underestimates of $\Sigma$.
-% In this paper, we have chiefly focused on the usage of G-ACvF for estimating autocovariances in SVE; however the argument for a similar usage in mIS is straightforward.  
+All ACF plots in this manuscript have been constructed using the \texttt{R} package \texttt{multichainACF} \footnote{\texttt{https://github.com/medhaaga/multichainACF}}.
+
+%
+
+Another class of estimators for $\Sigma$ for reversible Markov chains are the multivariate initial sequence (mIS) estimators \citep{dai:jon:2017}.
+Similar to SV estimators, ACvFs are a critical part of mIS estimators and underestimation in ACvFs yields underestimates of $\Sigma$.
 It is easy to show that $\hat{\Upsilon}_{G,s}(k)$ is a strongly consistent estimators for $\Upsilon(k)$.
-Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following the proof of Theorem~2 in \citep{dai:jon:2017} will yield consistent overestimation of the generalized variance $\abs{\Sigma}$ estimated using a globally-centered version of the mIS estimator.
-A valuable line of research would be to carry out the theoretical and experimental analysis of mIS estimators using G-ACvF.
-
-% generalised variance estimates obtained from mIS consistently overestimate $\abs{\Sigma}$.
-From Theorem~\ref{th:G-ACF_bias}, one can prove that, on average, the eigenvalues of $\hat{\Gamma}_{G,s}(k)$ are greater than the eigenvalues of $\hat{\Gamma}_s(k)$.
-This supplies readers with sufficient motivation to believe that the generalized variance for mIS constructed from $\hat{\Gamma}_G(k)$ not only consistently overestimates $\abs{\Sigma}$ but also upper-bounds the mIS from empirical single chain estimator of $\Gamma(k)$ for finite samples.
-%
-
-% The choice of starting vector is crucial for multiple chain sampling.
-In case the chains are started very near to each other, all the chains will explore nearly the same neighborhood in the state space.
-As a consequence, the G-ACvF will be equivalent to A-ACvF, and no significant improvement will be observed in estimation quality.
-We have used a deterministic initialization method in our examples using our prior knowledge about the location of modes in the target distribution.
-Comparing existing initialization methods {\color{orange} MA: maybe cite a few} and developing new ones could be an interesting direction for future research.
-
+Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following \cite[Theorem~2]{dai:jon:2017} will yield consistent overestimation of the generalized variance $\abs{\Sigma}$ estimated using a globally-centered version of the mIS estimator.
+A valuable line of research would be to study the theoretical and experimental analysis of mIS estimators using G-ACvF.
+
+\section{Acknowledgements} % (fold)
+\label{sec:acknowledgements}
+The authors are thankful to Haema Nilakanta for sharing useful \texttt{R} code.
+% section acknowledgements (end)
+
+\appendix
 \section{Appendix}  \label{sec:appendix}
@@
 
-\subsection{Strong consistency of G-SV estimator} \label{appendix:strong_consis}
+\subsection{Strong consistency of the G-SV estimator} \label{appendix:strong_consis}
 
@@
 \subsection{Proof of Theorem \ref{th:G-SVE_bias}}
+\label{appendix:gsv_bias}
 

### 2020-09-03 Paper/Submissions/JCGS/First/jcgs-template/jcgs-template.tex
Pushing submission to JCGS changes

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Title}
  \author{Author 1\thanks{
    The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
    Department of YYY, University of XXX\\
    and \\
    Author 2 \\
    Department of ZZZ, University of WWW}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
The text of your abstract.  200 or fewer words.
\end{abstract}

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.5} % DON'T change the spacing!
\section{Introduction}
\label{sec:intro}

Body of paper.  Margins in this document are roughly 0.75 inches all
around, letter size paper.

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig1.pdf}
\end{center}
\caption{Consistency comparison in fitting surrogate model in the tidal
power example. \label{fig:first}}
\end{figure}

\begin{table}
\caption{D-optimality values for design $X$ under five different scenarios.  \label{tab:tabone}}
\begin{center}
\begin{tabular}{rrrrr}
one & two & three & four & five\\\hline
1.23 & 3.45 & 5.00 & 1.21 & 3.41 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.42 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.43 \\
\end{tabular}
\end{center}
\end{table}

\begin{itemize}
\item Note that figures and tables (such as Figure~\ref{fig:first} and
Table~\ref{tab:tabone}) should appear in the paper, not at the end or
in separate files.
\item In the latex source, near the top of the file the command
\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
acknowledgements, producing the required blinded version.
\item Remember that in the blind version, you should not identify authors
indirectly in the text.  That is, don't say ``In Smith et. al.  (2009) we
showed that ...''.  Instead, say ``Smith et. al. (2009) showed that ...''.
\item These points are only intended to remind you of some requirements.
Please refer to the instructions for authors
at \url{http://amstat.tandfonline.com/action/authorSubmission?journalCode=ubes20&page=instructions#}
\item For more about ASA\ style, please see \url{http://journals.taylorandfrancis.com/amstat/asa-style-guide/}
\item If you have supplementary material (e.g., software, data, technical
proofs), identify them in the section below.  In early stages of the
submission process, you may be unsure what to include as supplementary
material.  Don't worry---this is something that can be worked out at later stages.
\end{itemize}

\section{Methods}
\label{sec:meth}
Don't take any of these section titles seriously.  They're just for
illustration.

\section{Verifications}
\label{sec:verify}
This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

\cite{Campbell02}, \cite{Schubert13}, \cite{Chi81}

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
{\bf With this spacing we have 30 lines per page.}
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

\section{Conclusion}
\label{sec:conc}

\bigskip
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{description}

\item[Title:] Brief description. (file type)

\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article. The package also contains all datasets used as examples in the article. (GNU zipped tar file)

\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)

\end{description}

\section{BibTeX}

We hope you've chosen to use BibTeX!\ If you have, please feel free to use the package natbib with any bibliography style you're comfortable with. The .bst file Chicago was used here, and agsm.bst has been included here for your convenience.

\bibliographystyle{Chicago}

\bibliography{Bibliography-MM-MC}
\end{document}

### 2020-09-03 Paper/Submissions/JCGS/First/main.tex
Pushing submission to JCGS changes

--- 2020-09-03 Paper/Submissions/JCGS/First/arxiv/main.tex
@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
 % This is a package to accept utf8 input.  I normally do not use it in my documents, but it was here by default in Overleaf.
-
-\usepackage{amssymb,amsthm,amsmath}
+\usepackage{amsmath}
+\usepackage{graphicx}
+%\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
+
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
+
+\usepackage{amssymb,amsthm}
 \usepackage{commath,hyperref}
@@
 \usepackage{graphicx}
-\usepackage{caption,setspace}
+% \usepackage{caption,setspace}
 \usepackage{subcaption}
@@
 
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Globally-centered autocovariances in MCMC}
+  \author{Medha Agarwal\hspace{.2cm}\\
+    Department of Mathematics and Statistics, IIT Kanpur\\
+    and \\
+    Dootika Vats \\
+    Department of Mathematics and Statistics, IIT Kanpur}
   \maketitle
-
-\onehalfspacing
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Title}
+\end{center}
+  \medskip
+} \fi
+
+\bigskip
 \begin{abstract}
@@
 \end{abstract}
+
+\noindent%
+{\it Keywords:}  Markov chain Monte Carlo, autocorrelation plots, spectral variance estimators, visualization
+\vfill
+
+\newpage
+\spacingset{1.5} % DON'T change the spacing!
 
@@
 \centering
-   \includegraphics[width=.5\linewidth]{plots/var-acf_n1000.pdf}
-     \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
+   \includegraphics[width=.60\linewidth]{plots/var-acf_n1000.pdf}
+     \includegraphics[width=.60\linewidth]{plots/var-acf_n10000.pdf} 
 \caption{VAR. ACF (left) and G-ACF (right) for the second chain for $m = 5$. (Top) $n = 10^3$  and (bottom) $n =  10^4$. The red line is the true ACF.}
@@
     \centering
-      \includegraphics[width = 2.0in]{plots/var-frob.pdf} 
-      \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
+      \includegraphics[width = 2.3in]{plots/var-frob.pdf} 
+      \includegraphics[width = 2.3in]{plots/var-ess.pdf}         
     \caption{VAR. (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV estimator. (Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV estimator.}
@@
 
+\bigskip
+\begin{center}
+{\large\bf SUPPLEMENTARY MATERIAL}
+\end{center}
+
+\begin{description}
+
+\item[R Code:] Contains R code that reproduces the simulations, figured, and tables (.zip file).
+
+\end{description}
+
 \appendix
@@
 We sample two parallel Markov chains starting from two students belonging to different races.
- % and study its impacts on the average features of their immediate social group, especially their grades.
-Due to cluster formation in the network, a Markov chain will land on students within a cluster more often than on students outside it.
-As a consequence, the sample averages for the two chains will differ for a relatively shorter chain length.
+
 % 
@@
 
-% It is hypothesized that students from certain communities tend to engage more with students of same or other marginally represented communities.
-We believe that this "selective networking" might cause formation of clusters in the network wherein students within a cluster engage more with each other than with the students outside it.
-Given that the graph is well-connected, the Markov chains will eventually explore all the nodes.
-
-\singlespacing
 \bibliographystyle{apalike}

### 2020-09-03 one_run.R
readme.txt and one_run.R updated to match the figure numbers.

@@ -23,7 +23,7 @@ chain2 <- mc.chain.list[[2]]
 
 ################### Figure 1 #######################
 
-## Figure 1a
+## Figure 1 (top) a
 
 x <- seq(-10, 10, length = 1e3)
 pdf(file = "AllOut/gaussian-TargetTrace.pdf", height = 5, width = 10)
@@ -35,7 +35,8 @@ lines(x = chain2[1:1e4], y = seq(-1, -1e4, -1), col = "plum3")
 mtext(side = 2, text = "Time", line = 1)
 legend("top", legend=c("Target", "Chain 1", "Chain 2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=1, lwd=2, bty = "n")
 
-#Figure 1b
+## Figure 1 (top) b
+
 plot(x, 200000*exp(log.density(x, p, mu1, mu2, sd1, sd2)), type = "l", lwd = 1.5, xlab = "x", ylab = "", ylim = c(-1e5,6e4), xlim = range(chain1,chain2), yaxt = 'n')
 par(new = TRUE)
 plot(x = chain1, y = seq(-1, -1e5, -1), col = "lightskyblue", xlab = "", ylab = "", type = "l", ylim = c(-1e5, 6e4), , xlim = range(chain1,chain2), yaxt = 'n')
@@ -44,7 +45,6 @@ mtext(side = 2, text = "Time", line = 1)
 legend("top", legend=c("Target", "Chain 1", "Chain 2"),col=c("black", "lightskyblue", "plum3"), lty=1, cex=1, lwd=2, bty = "n")
 dev.off()
 
-#################### Figure 1 (bottom) #######################
 
 lag.max <- 50
 nsim1 <- 1e4
@@ -65,6 +65,7 @@ global.acf1 <- globalACF(x, chains = c(1), component = 1, lag.max = lag.max, typ
 global.acf2 <- globalACF(y, chains = c(1), component = 1, lag.max = lag.max, type = "correlation", avg = FALSE, plot = FALSE)[[1]]
 
 #### Figure 1 (bottom)
+
 pdf(file = "AllOut/gaussian-acf_hist.pdf", width = 10, height= 5)
 par(mfrow = c(1,2))
 plot(as.matrix(local.acf1$acf), type = 'h', ylab = "Autocorrelation", xlab = "Lag")
@@ -80,7 +81,7 @@ dev.off()
 ##########################################
 ##########################################
 
-##################Figure 3 ###############
+################## Figure 2 ###############
 
[…]

### 2020-09-03 one_run.R
Final submitted finals. Phew.
Job well done Medha. You should be really proud of your work here.

@@ -322,34 +322,6 @@ segments(x0 = conv.pts, y0 = (r - se.r), y1 = (r + se.r), col = adjustcolor("roy
 legend("topright", legend=c("A-SVE", "G-SVE"),col=c("darkorange", "royalblue"), lty=1, cex=1, lwd = 2, bty = "n")
 dev.off()
 
-####################### Figure 9 ####################
-
-#### Figure 9a
-min <- 5e2
-max <- 1e5
-step <- 5e2
-conv.pts <- seq(min, max, step)
-m <- 5
-load(file = paste(paste("AllOut/boom1-conv_data_m", sep = "_"), m, "_min", min, "_max", max, ".Rdata", sep = ""))
-
-a <- lapply(asv[1:10], function(x) log(apply(x, 3, norm, "F") ) )
-r <- lapply(rsv[1:10], function(x) log(apply(x, 3, norm, "F") ) )
-a <- Reduce("rbind", a)
-r <- Reduce("rbind", r)
-
-se.a <- apply(a, 2, sd)/sqrt(10)
-se.r <- apply(r, 2, sd)/sqrt(10)
-
-a <- colMeans(a)
-r <- colMeans(r)
-
-pdf(file = paste(paste("AllOut/boom-frob", A1, B1, C1, "m", sep = "_"), m, ".pdf", sep = ""), height = 5, width = 5)
-plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "Log of Frobenium norm", ylim = range(c(a, r, r + se.r, a - se.a)), lwd = 2)
-lines(conv.pts, r, col="royalblue", lwd = 2)
-segments(x0 = conv.pts, y0 = (a - se.a), y1 = (a + se.a), col = adjustcolor("darkorange", alpha.f = .50))
-segments(x0 = conv.pts, y0 = (r - se.r), y1 = (r + se.r), col = adjustcolor("royalblue", alpha.f = .50))
-legend("bottomright", legend=c("A-SVE", "G-SVE"),col=c("darkorange", "royalblue"), lty=1, lwd = 2, bty = "n")
-dev.off()
 
 
 ##################### Table 2 ########################

### 2021-07-21 Examples/negVAR-1/acf_plots.R
VAR with negative ACF

@@ -1,0 +1,104 @@
+set.seed(10)
+source("functions.R")
+library(multichainACF)
+
+
+######################################
+##### Model parameters ###############
+######################################
+
+m <- 5
+p <- 2
+omega <- diag(p)
+for (i in 1:(p-1)){
+  for (j in 1:(p-i)){
+    omega[j, j+i] <- .9^i
+    omega[j+i, j] <- .9^i
+  }
+}
+
+phi <- diag(c(.999, .001))
+dummy <- matrix(1:p^2, nrow = p, ncol = p)
+dummy <- qr.Q(qr(dummy))
+phi <- dummy %*% phi %*% t(dummy)
+
+target <- target.sigma(phi, omega)
+truth <- true.sigma(phi, var = target)
+lag.max <- 40
+
+true.acf <- array(0, dim = c(p, p, 2*lag.max + 1))
+true.acf[,,lag.max+1] <- target
+for (i in 1:lag.max){
+  true.acf[,,lag.max + 1 + i] <- phi %*% true.acf[,,lag.max + 1 + i - 1]
+  true.acf[,,lag.max + 1 - i] <- true.acf[,,lag.max + 1 - i + 1] %*% t(phi)
+}
+
+################ Only for creating Markov chains. Don't run. ##################
+start <- matrix(0, nrow = m, ncol = p)  #only depends on C
+
+for(i in 1:floor(m/2)){
+  start[i,] <- i*sqrt(diag(target))
+  start[m-i+1,] <- -i*sqrt(diag(target))
+}
+
+mc.chain.list <- list()
+global.mean <- rep(0,p)
+for (i in 1:m){
+  chain <- markov.chain(phi, omega, 5e4, start[i,])
+  global.mean <- global.mean + colMeans(chain)
+  mc.chain.list[[i]] = chain
+  print(colMeans(chain))
+}
+global.mean <- global.mean/m
+save(mc.chain.list, true.acf, file = "Out/var-five_chains.Rdata")
+#################################################################################
+
+load(file = "Out/var-five_chains.Rdata")
+#######################################################
+############### ACF and G-ACF #########################
+#######################################################
+
+component <- 1
+lag.max <- 40
+
+###############################
+### ncrop = 1e3
+##############################
+
+ncrop <- 1e3
+x <- list()
+for (i in 1:m){
[…]

### 2021-07-21 Examples/negVAR-1/output.R

@@ -1,0 +1,135 @@
+set.seed(1)
+library(fields)
+library(graphics)
+library(Rcpp)
+library(RcppArmadillo)
+library(fftwtools)
+library(mcmcse)
+library(stats)
+sourceCpp("lag.cpp")
+source("functions.R")
+
+
+###############################################
+##### Model parameters####################
+#########################################
+
+m <- 5
+p <- 2
+omega <- diag(p)
+for (i in 1:(p-1)){
+  for (j in 1:(p-i)){
+    omega[j, j+i] <- .9^i
+    omega[j+i, j] <- .9^i
+  }
+}
+
+phi <- diag(c(.999, .001))
+dummy <- matrix(1:p^2, nrow = p, ncol = p)
+dummy <- qr.Q(qr(dummy))
+phi <- dummy %*% phi %*% t(dummy)
+
+############3Simuation settings###########
+
+target <- target.sigma(phi, omega)
+truth <- true.sigma(phi, var = target)
+check.pts <- c(5e2, 1e3, 5e3, 1e4, 5e4, 1e5)
+rep <- 50
+freq <- 1000
+min <- 5e2
+max <- 5e4
+step <- 500
+conv.pts <- seq(min, max, step)
+save(target, truth, file = "Out/var-truth.Rdata")
+###########################################################
+############## log Frobenius norm running plots ###########
+###########################################################
+
+load(file = paste("Out/conv_data_min", min, "_max", max, ".Rdata", sep = ""))
+
+a <- lapply(asv, function(x) log(apply(x, 3, norm, "F") ) )
+r <- lapply(rsv, function(x) log(apply(x, 3, norm, "F") ) )
+a <- Reduce("rbind", a)
+r <- Reduce("rbind", r)
+
+se.a <- apply(a, 2, sd)/sqrt(length(asv))
+se.r <- apply(r, 2, sd)/sqrt(length(rsv))
+
+a <- colMeans(a)
+r <- colMeans(r)
+
+pdf(file = "Out/var-frob.pdf", height = 5, width = 5)
+plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "Log of Frobenium norm", ylim = range(c(a, r, r + se.r, a - se.a, log(norm(truth, type = "F")))), lwd = 2)
+lines(conv.pts, r, col="royalblue", lwd = 2)
[…]

### 2021-07-21 Examples/negVAR-1/simulations.R

@@ -1,0 +1,204 @@
+################################################################
+##This code is responsible for simulating and storing R objects
+##that are later used for plotting figures and making tables.
+################################################################
+
+set.seed(10)
+library(Rcpp)
+library(RcppArmadillo)
+library(fftwtools)
+library(mcmcse)
+source("functions.R")
+sourceCpp("lag.cpp")
+
+############################################################
+##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
+############################################################
+
+create.output <- function(phi, omega, m, check.pts, freq, c.prob){
+
+  p <- ncol(phi)
+  target <- target.sigma(phi, omega)
+  start <- matrix(0, nrow = m, ncol = p)  #only depends on C
+
+  for(i in floor(m/2):1){
+    start[i,] <- 2*i*sqrt(diag(target))
+    start[m-i+1,] <- -2*i*sqrt(diag(target))
+  }
+
+  asv.samples <- list()
+  gsv.samples <- list()
+  asv.coverage <- list()
+  gsv.coverage <- list()
+
+  for (i in 1:length(check.pts)){
+    asv.samples[[i]] <- array(0, dim = c(p,p,freq))
+    gsv.samples[[i]] <- array(0, dim = c(p,p,freq))
+    asv.coverage[[i]] <- rep(0, freq)
+    gsv.coverage[[i]] <- rep(0, freq)
+  }
+
+  for (j in 1:freq){
+    if(j %% (freq/1000) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2)))
+
+    master.chain <- array(0, dim = c(max(check.pts), p, m))
+    for (k in 1:m)
+      master.chain[,,k] <- markov.chain(phi, omega, max(check.pts), start[k,])
+
+    for (i in 1:length(check.pts))
+    {
+      nsim <- check.pts[i]
+      critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
+      chains <- master.chain[1:nsim,,]
+
+      sve <- array(0, dim = c(p,p,m))
+      rsve <- array(0, dim = c(p,p,m))
+      b <- rep(0,m)
+
[…]

### 2021-07-21 Paper/Submissions/JCGS/First/arxiv/main.tex

@@
 
-\onehalfspacing
+\doublespacing
 \begin{abstract}
@@
 The impact of this improved estimator is evident in three critical output analysis applications: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size.
-Under weak conditions, we establish strong consistency of an improved asymptotic covariance estimator, and obtain its large-sample bias and variance.
+Under weak conditions, we establish strong consistency of our improved asymptotic covariance estimator, and obtain its large-sample bias and variance.
 The performance of the new estimators is demonstrated through various examples.
@@
 
-We demonstrate the striking difference in estimation of $\Gamma(k)$ via ACF plots. Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density. Let
+We use ACF plots to demonstrate the striking difference in the estimation of $\Gamma(k)$. Consider a random-walk Metropolis-Hastings sampler for a univariate mixture of Gaussians target density. Let
 \[
@@
 \centering
-   \includegraphics[width=.62\linewidth]{plots/gaussian-Targettrace.pdf}\\
+   \includegraphics[width=.62\linewidth]{gaussian-TargetTrace.pdf}\\
 \vspace{-.5cm}
-    \includegraphics[width=.62\textwidth]{plots/gaussian-acf_hist.pdf} 
+    \includegraphics[width=.62\textwidth]{gaussian-acf_hist.pdf} 
     \caption{Top: Target density and trace plots for two chains at $n = 10^4$ (left) and $n = 10^5$ (right).
@@
 % \centering
-% \includegraphics[width=.6\textwidth]{plots/gaussian-acf_hist.pdf} \\
-% % \includegraphics[width=.6\textwidth]{plots/gaussian-acf_1e4.pdf}
+% \includegraphics[width=.6\textwidth]{gaussian-acf_hist.pdf} \\
+% % \includegraphics[width=.6\textwidth]{gaussian-acf_1e4.pdf}
 
@@
 
-We end this section by noting that we can obtain an average G-ACvF and G-ACF over all $m$ chains
+We end this section by noting that we can obtain an average G-ACvF and G-ACF over all $m$ chains as,
 \[
@@
 The most common are SV estimators \citep{andr:1991,vats:fleg:jon:2018} and batch means estimators \citep{chen:seila:1987,vats:fleg:jon:2019}.
-Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from parallel chains.
+Recently, \cite{gupta:vats:2020} constructed a replicated batch means estimator for estimating $\Sigma$ from parallel Markov chains.
 Batch means estimators are computationally more efficient than SV estimators, whereas SV estimators are more reliable \citep{damerdji:1995,fleg:jone:2010}.
@@
 
-\begin{theorem}[\cite{kuel:1976,vats:fleg:jon:2018}]
+\begin{theorem}[\cite{kuel:phil:1980,vats:fleg:jon:2018}]
   \label{thm:kuelbs}
@@
 Compute eigenvalues $\lambda_i$ of  $C(w^*)_{(1)}$ using a discrete Fourier transform, $i = 1, \dots, 2n$\;
-Construct $2n \times p$ matrix $A^*_s = (A_s^T  \quad 0_{n \times q})^T$\;
+Construct $2n \times p$ matrix $A^*_s = (A_s^T  \quad 0_{n \times p})^T$\;
 
@@
 The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence region when the true mean $\mu_g$ is known.
-The convergence of local and global estimators of $\Sigma$ and $\widehat{\textrm{ESS}}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$.
+The convergence of local and global estimators of $\Sigma$ and $\textrm{ESS}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$.
 In all three examples, we estimate the mean of the stationary distribution, so $g$ is the identity function.
@@
 \centering
-   \includegraphics[width=.5\linewidth]{plots/var-acf_n1000.pdf}
-     \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
+   \includegraphics[width=.60\linewidth]{var-acf_n1000.pdf}
+     \includegraphics[width=.60\linewidth]{var-acf_n10000.pdf} 
 \caption{VAR. ACF (left) and G-ACF (right) for the second chain for $m = 5$. (Top) $n = 10^3$  and (bottom) $n =  10^4$. The red line is the true ACF.}
@@
     \centering
-      \includegraphics[width = 2.0in]{plots/var-frob.pdf} 
-      \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
+      \includegraphics[width = 2.3in]{var-frob.pdf} 
+      \includegraphics[width = 2.3in]{var-ess.pdf}         
     \caption{VAR. (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV estimator. (Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV estimator.}
@@
     \centering
-    \includegraphics[width = .70\textwidth]{plots/boom-all_1_3_8.pdf}\\
-    \includegraphics[width = .70\textwidth]{plots/boom-all_1_10_7.pdf}    
+    \includegraphics[width = .70\textwidth]{boom-all_1_3_8.pdf}\\
+    \includegraphics[width = .70\textwidth]{boom-all_1_10_7.pdf}    
     \caption{Boomerang.
@@
     \centering
-      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
-      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_10_7_m5.pdf}
-
-    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for setting 1 (left) and setting 2 (right).}
+      \includegraphics[width = .30\textwidth]{boom-ess_1_3_8_m5.pdf}
+      \includegraphics[width = .30\textwidth]{boom-ess_1_10_7_m5.pdf}
+
+    \caption{Boomerang. Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for setting 1 (left) and setting 2 (right).}
     \label{fig:boom-ess}
@@
     \centering
-    \includegraphics[width = .32\textwidth]{plots/sensor-trace_loc1.pdf}
-      \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e3.pdf}
-      \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e4.pdf}    
+    \includegraphics[width = .32\textwidth]{sensor-trace_loc1.pdf}
+      \includegraphics[width = .32\textwidth]{sensor-acf_n5e3.pdf}
+      \includegraphics[width = .32\textwidth]{sensor-acf_n5e4.pdf}    
     \caption{Sensor: Trace plot of $x_{11}$ (left) for two parallel chains.
@@
     \centering
-      \includegraphics[width = .30\textwidth]{plots/sensor-frob.pdf} 
-      \includegraphics[width = .30\textwidth]{plots/sensor-ess.pdf}
+      \includegraphics[width = .30\textwidth]{sensor-frob.pdf} 
+      \includegraphics[width = .30\textwidth]{sensor-ess.pdf}
 
@@
 It is easy to show that $\hat{\Upsilon}_{G,s}(k)$ is a strongly consistent estimators for $\Upsilon(k)$.
-Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following \cite[Theorem~2]{dai:jon:2017} will yield consistent overestimation of the generalized variance $\abs{\Sigma}$ estimated using a globally-centered version of the mIS estimator.
-A valuable line of research would be to study the theoretical and experimental analysis of mIS estimators using G-ACvF.
+Replacing $\hat{\Upsilon}_s(k)$ for $\hat{\Upsilon}_{G,s}(k)$ and following \cite[Theorem~2]{dai:jon:2017} will yield consistent overestimation of the generalized variance $\abs{\Sigma}$ resulting in a globally-centered version of the mIS estimator.
+A valuable line of research would be to study the theoretical and empirical properties of the globally-centered mIS estimators.
 
@@
 % section acknowledgements (end)
+
+% \bigskip
+% \begin{center}
+% {\large\bf SUPPLEMENTARY MATERIAL}
+% \end{center}
+
+% \begin{description}
+
+% \item[R Code:] Contains R code that reproduces the simulations, figured, and tables (.zip file).
+
+% \end{description}
 
@@
     \centering
-    \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
-    \caption{Trace plot for second (left) and third (right) component of two chains.}
+    \includegraphics[width = 0.7\textwidth]{poisson-trace_n50000.pdf}
+    \caption{Change point: Trace plots for second (left) and third (right) component.}
     \label{fig:poisson-trace}
@@
     \centering
-      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n1000.pdf}  \\ \vspace{-.5cm}
-      \includegraphics[width = .6\textwidth]{plots/poisson-acf_n10000.pdf}      
+      \includegraphics[width = .6\textwidth]{poisson-acf_n1000.pdf}  \\ \vspace{-.5cm}
+      \includegraphics[width = .6\textwidth]{poisson-acf_n10000.pdf}      
     \caption{Change point: ACF plots using local (left) and global (right) centering for $m=2$ parallel Markov chains.
@@
 We use a Metropolis-Hastings algorithm with a simple random-walk  proposal suggested by \cite{gjoka2011practical}.
-Each node is associated with five features namely - degree of connection, cluster coefficient, grade, binary sex indicator (1 for female, 0 for male), and binary race indicator (1 for white, 0 for others)
+Each node is associated with five features namely - degree of connection, cluster coefficient, grade, binary sex indicator (1 for female, 0 for male), and binary race indicator (1 for white, 0 for others).
+We sample two parallel Markov chains starting from two students belonging to different races.
 
@@
     \centering
-      \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n100.pdf}\\ \vspace{-.5cm}
-      \includegraphics[width = .6\textwidth]{plots/magnolia-acf_n1000.pdf}
+      \includegraphics[width = .6\textwidth]{magnolia-acf_n100.pdf}\\ \vspace{-.5cm}
+      \includegraphics[width = .6\textwidth]{magnolia-acf_n1000.pdf}
 
@@
 This might cause formation of clusters in the social network.
-We sample two parallel Markov chains starting from two students belonging to different races.
- % and study its impacts on the average features of their immediate social group, especially their grades.
-Due to cluster formation in the network, a Markov chain will land on students within a cluster more often than on students outside it.
-As a consequence, the sample averages for the two chains will differ for a relatively shorter chain length.
+
 % 

### 2021-07-21 Paper/Submissions/JCGS/First/main.tex

@@
 
-    \caption{Boom: Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for setting 1 (left) and setting 2 (right).}
+    \caption{Boomerang. Running plot of $\log (\widehat{\text{ESS}}_A )/mn$ and $\log (\widehat{\text{ESS}}_G )/mn$ with $m = 5$ for setting 1 (left) and setting 2 (right).}
     \label{fig:boom-ess}
@@
     \includegraphics[width = 0.7\textwidth]{plots/poisson-trace_n50000.pdf}
-    \caption{Trace plot for second (left) and third (right) component of two chains.}
+    \caption{Change point: Trace plots for second (left) and third (right) component.}
     \label{fig:poisson-trace}
@@
 This might cause formation of clusters in the social network.
-We sample two parallel Markov chains starting from two students belonging to different races.
 

### 2021-07-22 Examples/negVAR-1/acf_plots.R
oops

@@ -21,6 +21,7 @@ phi <- diag(c(.999, .001))
 dummy <- matrix(1:p^2, nrow = p, ncol = p)
 dummy <- qr.Q(qr(dummy))
 phi <- dummy %*% phi %*% t(dummy)
+diag(phi) <- -diag(phi)
 
 target <- target.sigma(phi, omega)
 truth <- true.sigma(phi, var = target)
@@ -44,7 +45,7 @@ for(i in 1:floor(m/2)){
 mc.chain.list <- list()
 global.mean <- rep(0,p)
 for (i in 1:m){
-  chain <- markov.chain(phi, omega, 5e4, start[i,])
+  chain <- markov.chain(phi, omega, 1e4, start[i,])
   global.mean <- global.mean + colMeans(chain)
   mc.chain.list[[i]] = chain
   print(colMeans(chain))
@@ -76,10 +77,10 @@ local.acf <- globalACF(x, type = "correlation", component = 1, mean = "local", l
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-plot(local.acf, main = expression("Locally centered ACF"))
-lines(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red")
-plot(global.acf, main = expression("Globally centered ACF"))
-lines(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red")
+plot(local.acf, main = expression("Locally centered ACF"), ylim = c(-1,1))
+points(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red", pch = 19, cex=.7)
+plot(global.acf, main = expression("Globally centered ACF"), ylim = c(-1,1))
+points(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red", pch = 19, cex=.7)
 dev.off()
 
 ###############################
@@ -97,8 +98,8 @@ local.acf <- globalACF(x, type = "correlation", component = 1, mean = "local", l
 
 pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
 par(mfrow = c(1,2))
-plot(local.acf, main = expression("Locally centered ACF"))
[…]

### 2021-07-22 Examples/negVAR-1/acf_plots.R
Both positive and negative ACF plots

@@ -51,10 +51,10 @@ for (i in 1:m){
   print(colMeans(chain))
 }
 global.mean <- global.mean/m
-save(mc.chain.list, true.acf, file = "Out/var-five_chains.Rdata")
+save(mc.chain.list, true.acf, file = "Out/var-neg_five_chains.Rdata")
 #################################################################################
 
-load(file = "Out/var-five_chains.Rdata")
+load(file = "Out/var-neg_five_chains.Rdata")
 #######################################################
 ############### ACF and G-ACF #########################
 #######################################################
@@ -75,7 +75,7 @@ for (i in 1:m){
 global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 local.acf <- globalACF(x, type = "correlation", component = 1, mean = "local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 
-pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
+pdf(file = paste("Out/var-neg_acf_n", ncrop, ".pdf", sep = ""), height = 5, width = 10)
 par(mfrow = c(1,2))
 plot(local.acf, main = expression("Locally centered ACF"), ylim = c(-1,1))
 points(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red", pch = 19, cex=.7)
@@ -96,7 +96,7 @@ for (i in 1:m){
 global.acf <- globalACF(x, type = "correlation", component = 1, lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 local.acf <- globalACF(x, type = "correlation", component = 1, mean = "local", lag.max = lag.max, chains = c(2), plot = FALSE, avg = FALSE)[[1]]
 
-pdf(file = paste("Out/var-acf_n", ncrop, ".pdf", sep = ""), height = 4, width = 10)
+pdf(file = paste("Out/var-neg_acf_n", ncrop, ".pdf", sep = ""), height = 5, width = 10)
 par(mfrow = c(1,2))
 plot(local.acf, main = expression("Locally centered ACF"), ylim = c(-1,1))
 points(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red", pch = 19, cex=.7)

### 2021-07-22 Examples/negVAR-1/output.R

@@ -1,135 +1,0 @@
-set.seed(1)
-library(fields)
-library(graphics)
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-library(stats)
-sourceCpp("lag.cpp")
-source("functions.R")
-
-
-###############################################
-##### Model parameters####################
-#########################################
-
-m <- 5
-p <- 2
-omega <- diag(p)
-for (i in 1:(p-1)){
-  for (j in 1:(p-i)){
-    omega[j, j+i] <- .9^i
-    omega[j+i, j] <- .9^i
-  }
-}
-
-phi <- diag(c(.999, .001))
-dummy <- matrix(1:p^2, nrow = p, ncol = p)
-dummy <- qr.Q(qr(dummy))
-phi <- dummy %*% phi %*% t(dummy)
-
-############3Simuation settings###########
-
-target <- target.sigma(phi, omega)
-truth <- true.sigma(phi, var = target)
-check.pts <- c(5e2, 1e3, 5e3, 1e4, 5e4, 1e5)
-rep <- 50
-freq <- 1000
-min <- 5e2
-max <- 5e4
-step <- 500
-conv.pts <- seq(min, max, step)
-save(target, truth, file = "Out/var-truth.Rdata")
-###########################################################
-############## log Frobenius norm running plots ###########
-###########################################################
-
-load(file = paste("Out/conv_data_min", min, "_max", max, ".Rdata", sep = ""))
-
-a <- lapply(asv, function(x) log(apply(x, 3, norm, "F") ) )
-r <- lapply(rsv, function(x) log(apply(x, 3, norm, "F") ) )
-a <- Reduce("rbind", a)
-r <- Reduce("rbind", r)
-
-se.a <- apply(a, 2, sd)/sqrt(length(asv))
-se.r <- apply(r, 2, sd)/sqrt(length(rsv))
-
-a <- colMeans(a)
-r <- colMeans(r)
-
-pdf(file = "Out/var-frob.pdf", height = 5, width = 5)
-plot(conv.pts, a, type = "l", col = "darkorange", main = "", xlab = "Simulation size", ylab = "Log of Frobenium norm", ylim = range(c(a, r, r + se.r, a - se.a, log(norm(truth, type = "F")))), lwd = 2)
-lines(conv.pts, r, col="royalblue", lwd = 2)
[…]

### 2021-07-22 Examples/negVAR-1/simulations.R

@@ -1,204 +1,0 @@
-################################################################
-##This code is responsible for simulating and storing R objects
-##that are later used for plotting figures and making tables.
-################################################################
-
-set.seed(10)
-library(Rcpp)
-library(RcppArmadillo)
-library(fftwtools)
-library(mcmcse)
-source("functions.R")
-sourceCpp("lag.cpp")
-
-############################################################
-##creates freq=1000 replications of ASV and RSV for each value of nsim from check.pts
-############################################################
-
-create.output <- function(phi, omega, m, check.pts, freq, c.prob){
-
-  p <- ncol(phi)
-  target <- target.sigma(phi, omega)
-  start <- matrix(0, nrow = m, ncol = p)  #only depends on C
-
-  for(i in floor(m/2):1){
-    start[i,] <- 2*i*sqrt(diag(target))
-    start[m-i+1,] <- -2*i*sqrt(diag(target))
-  }
-
-  asv.samples <- list()
-  gsv.samples <- list()
-  asv.coverage <- list()
-  gsv.coverage <- list()
-
-  for (i in 1:length(check.pts)){
-    asv.samples[[i]] <- array(0, dim = c(p,p,freq))
-    gsv.samples[[i]] <- array(0, dim = c(p,p,freq))
-    asv.coverage[[i]] <- rep(0, freq)
-    gsv.coverage[[i]] <- rep(0, freq)
-  }
-
-  for (j in 1:freq){
-    if(j %% (freq/1000) == 0) print(paste("Percentage completion: ", round(j/freq*100, 2)))
-
-    master.chain <- array(0, dim = c(max(check.pts), p, m))
-    for (k in 1:m)
-      master.chain[,,k] <- markov.chain(phi, omega, max(check.pts), start[k,])
-
-    for (i in 1:length(check.pts))
-    {
-      nsim <- check.pts[i]
-      critical <- ((nsim*m - 1)*p/(nsim*m  - p))*qf(.95, df1 = p, df2 = (nsim*m-p))
-      chains <- master.chain[1:nsim,,]
-
-      sve <- array(0, dim = c(p,p,m))
-      rsve <- array(0, dim = c(p,p,m))
-      b <- rep(0,m)
-
[…]

### 2021-07-22 Examples/negVAR-1/acf_plots.R
Scatter plots

@@ -103,3 +103,40 @@ points(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "
 plot(global.acf, main = expression("Globally centered ACF"), ylim = c(-1,1))
 points(seq(-lag.max, lag.max), true.acf[1,1,]/true.acf[1,1,lag.max + 1], col = "red", pch = 19, cex=.7)
 dev.off()
+
+##########################################
+###### Scatter plots ######################
+############################################
+
+
+load(file = "Out/var-neg_five_chains.Rdata") 
+m <- 5
+nsim <- 1e3
+
+pdf(file = ("Out/var-sp_n1e3.pdf"), height = 5, width = 5)
+plot(mc.chain.list[[1]][1:nsim,], xlim = c(-(m/2)*sqrt(diag(target)[1]), (m/2)*sqrt(diag(target)[1])),
+     ylim = c(-(m/2)*sqrt(diag(target)[2]), (m/2)*sqrt(diag(target)[2])), xlab = "X component",
+     ylab = "Y component", main = "", col = "dodgerblue4")
+#points(mc.chain.list[[2]][1:nsim,], col = "pink")
+#points(mc.chain.list[[3]][1:nsim,], col = "orange")
+#points(mc.chain.list[[4]][1:nsim,], col = "green3")
+points(mc.chain.list[[5]][1:nsim,], col = "steelblue1")
+legend("topright", legend = c("Chain-1", "Chain-2", "Chain-3", "Chain-4", "Chain-5"), col = c("dodgerblue4", "pink", "orange", "green3", "steelblue1"), pch = 19)
+dev.off()
+
+
+nsim <- 1e4
+
+
+pdf(file = ("Out/var-sp_n1e4.pdf"), height = 5, width = 5)
+plot(mc.chain.list[[1]][1:nsim,], xlim = c(-(m/2)*sqrt(diag(target)[1]), (m/2)*sqrt(diag(target)[1])),
+     ylim = c(-(m/2)*sqrt(diag(target)[2]), (m/2)*sqrt(diag(target)[2])), xlab = "X component",
+     ylab = "Y component", main = "", col = "dodgerblue4")
+#points(mc.chain.list[[2]][1:nsim,], col = "pink")
+#points(mc.chain.list[[3]][1:nsim,], col = "orange")
+#points(mc.chain.list[[4]][1:nsim,], col = "green3")
[…]
